### 2023-01-18 paper/main.tex
basic paper setup, draft of abstract

\documentclass[10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage[font=small,labelfont=bf]{caption}
\usepackage{geometry}
\usepackage[sort&compress, numbers]{natbib}
\usepackage{pxfonts}
\usepackage{graphicx}
\usepackage{setspace}
\usepackage{hyperref}
\usepackage{lineno}

\newcommand{\demo}{S1}

\doublespacing
\linenumbers

\title{Geometric models reveal the hidden structure of conceptual knowledge}

\author{Paxton C. Fitzpatrick\textsuperscript{1} and Jeremy R.
Manning\textsuperscript{*, 1}\\\textsuperscript{1}Dartmouth
College\\\textsuperscript{*}Corresponding author:
jeremy.r.manning@dartmouth.edu}

\date{}

\begin{document}
\maketitle

\begin{abstract} We develop a mathematical framework, based on natural language
processing models, for tracking and characterizing the acquisition of
conceptual knowledge. Our approach embeds each concept in a high dimensional
representation space, where nearby coordinates reflect similar or related
concepts. We tested our approach using behavioral data collected from a group
of college students. In the experiment, we asked the participants to answer
sets of quiz questions interleaved between watching two course videos from the
Khan Academy platform. We applied our framework to the videos' transcripts, and
to text of the quiz questions, to quantify the content of each moment of video
and each quiz question. We used these embeddings, along with participants' quiz
responses, to track how the learners' knowledge changed after watching each
video. Our findings show how a limited set of quiz questions may be used to
construct rich and meaningful representations of what each learner knows, and
how their knowledge changes over time as they learn.

\textbf{Keywords: education, learning, knowledge, concepts, natural language processing}

\end{abstract}

\section*{Main text}

\begin{figure}[tp]
\centering
\includegraphics[width=0.8\textwidth]{figs/content-mastery}
\caption{\textbf{Caption.} Placeholder text.}
\label{fig:demo}
\end{figure}

Insert text here (Figs.~\ref{fig:demo}, \demo).

\bibliographystyle{apa}
\bibliography{CDL-bibliography/cdl}
\end{document}

### 2023-01-18 paper/supplement.tex
basic paper setup, draft of abstract

--- 2023-01-18 paper/main.tex
@@
 \usepackage{geometry}
-\usepackage[sort&compress, numbers]{natbib}
+\usepackage{natbib}
 \usepackage{pxfonts}
 \usepackage{graphicx}
+\usepackage{newfloat}
 \usepackage{setspace}
 \usepackage{hyperref}
-\usepackage{lineno}
+\usepackage{placeins}
 
-\newcommand{\demo}{S1}
+\newcommand{\argmax}{\mathop{\mathrm{argmax}}\limits}
+\newcommand{\argmin}{\mathop{\mathrm{argmin}}\limits}
 
-\doublespacing
-\linenumbers
+\newcommand{\demo}{1}
 
-\title{Geometric models reveal the hidden structure of conceptual knowledge}
+\title{\textit{Supplementary materials for}: Geometric models reveal the hidden structure of conceptual knowledge}
 
@@
 \begin{document}
+
+\renewcommand{\figurename}{Supplementary Figure}
+
+\setcounter{equation}{0}
+\setcounter{figure}{0}
+\setcounter{table}{0}
+\setcounter{page}{1}
+\setcounter{section}{0}
+\makeatletter
+\renewcommand{\theequation}{S\arabic{equation}}
+\renewcommand{\thefigure}{S\arabic{figure}}
+\renewcommand{\bibnumfmt}[1]{[S#1]}
+\renewcommand{\citenumfont}[1]{S#1}
+
+% \newcommand{\demo}{1}
+
 \maketitle
-
-\begin{abstract} We develop a mathematical framework, based on natural language
-processing models, for tracking and characterizing the acquisition of
-conceptual knowledge. Our approach embeds each concept in a high dimensional
-representation space, where nearby coordinates reflect similar or related
-concepts. We tested our approach using behavioral data collected from a group
-of college students. In the experiment, we asked the participants to answer
-sets of quiz questions interleaved between watching two course videos from the
-Khan Academy platform. We applied our framework to the videos' transcripts, and
-to text of the quiz questions, to quantify the content of each moment of video
-and each quiz question. We used these embeddings, along with participants' quiz
-responses, to track how the learners' knowledge changed after watching each
-video. Our findings show how a limited set of quiz questions may be used to
-construct rich and meaningful representations of what each learner knows, and
-how their knowledge changes over time as they learn.
-
-\textbf{Keywords: education, learning, knowledge, concepts, natural language processing}
-
-\end{abstract}
-
-\section*{Main text}
 
@@
 
-Insert text here (Figs.~\ref{fig:demo}, \demo).
-
+\newpage
+\renewcommand{\refname}{Supplementary references}
 \bibliographystyle{apa}
 \bibliography{CDL-bibliography/cdl}
+
 \end{document}

### 2023-01-18 paper/main.tex
rough draft of introduction (still needs a bunch of references...)

@@
 
-\section*{Main text}
+\section*{Introduction}
+
+How do we acquire conceptual knowledge? Memorizing course lectures or textbook
+chapters by rote can lead to the superficial \textit{appearance} of
+understanding the underlying content, but achieving true conceptual
+understanding seems to require something deeper and richer. Does conceptual
+understanding entail connecting newly acquired information to the scaffolding
+of one's existing knowledge or experience? Or weaving a lecture's atomic
+elements (e.g., its component words) into a structured network that describes
+how those individual elements are related? Conceptual understanding could also
+involve building a mental model that transcends the meanings of those
+individual atomic elements by reflecting the deeper meaning underlying the
+gestalt whole.
+
+The difference between ``understanding'' and ``memorizing,'' as framed by the
+researchers in education, cognitive psychology, and cognitive
+neuroscience~\citep{Kato40, Gall10, ScotEtal13, HallGree08, Macl05} has
+profound analogs in the fields of natural language processing and natural
+language understanding. For example, considering the raw contents of a document
+(e.g., its constituent symbols, letters, and words) might provide some
+information about what the document is about, just as memorizing a passage
+might be used to answer simple questions about the passage~\citep[e.g., whether
+it might contain words related to furniture versus physics;][]{LandDuma97,
+BleiEtal03, BleiLaff06}. However, modern natural language processing
+models~\citep[e.g.,][]{MikoEtal13a, CerEtal18, BrowEtal20} also attempt to
+capture the deeper meaning \textit{underlying} those atomic elements. These
+models consider not only the co-occurrences of those elements within and across
+documents, but also patterns in how those elements appear across different
+scales (e.g., sentences, paragraphs, chapters, etc.), the temporal and
+grammatical properties of the elements, and other high-level characteristics of
+how they are used~\citep{Mann20, Mann21a}. According to these models, the deep
+conceptual meaning of a document may be captured by a feature vector in a
+high-dimensional representation space, where nearby vectors reflect
+conceptually related documents. A model that succeeds at capturing an analog of
+``understanding'' is able to assign nearby feature vectors to two conceptually
+related documents, \textit{even when the words contained in those documents
+have very little overlap}.
+
+What form might the representation of the sum total of a person's knowledge
+take? First, we might require a means of systematically describing or
+representing the nearly infinite set of possible things a person could know.
+Second, we might want to account for potential associations between different
+concepts. For example, the concepts of ``fish'' and ``water'' might be
+associated in the sense that fish live in water. Third, knowledge may have a
+critical dependency structure, such that knowing about a particular concept
+might require first knowing about a set of other concepts. For example,
+understanding the concept of a fish swimming in water first requires
+understanding what fish and water \textit{are}. Fourth, as we learn, our
+``current state of knowledge'' should change accordingly. Learning new concepts
+should both update our characterizations of ``what is known'' and should also
+unlock any now-satisfied dependencies of that newly learned concept so that
+they are ``tagged'' as available for future learning.
+
+Here we develop a framework for modelling how knowledge is acquired during
+learning. The central idea is to use text embedding models to define the
+coordinate systems of two maps: (a) a \textit{knowledge map} that describes the
+extent to which each concept is currently known and (b) a \textit{learning map}
+that describes the extent to which each concept could be learned. Each location
+on these maps represents a single concept, and the geometries are defined such
+that related concepts are located nearby in space. We use this framework to
+analyzing and interpreting behavioral data collected from an experiment that
+has participants watch and answer conceptual questions about a series of
+recorded course lectures.
+
+Our primary research goal is to advance our understanding of what it means to
+acquire deep real-world conceptual knowledge. Traditional laboratory approaches
+to studying learning and memory (e.g., list learning studies) often draw little
+distinction between memorization and understanding. Instead, these studies
+typically focus on whether information is effectively encoded or retrieved,
+rather than whether the information is \textit{understood}. Approaches to
+studying conceptual learning, such as category learning experiments, can start
+to investigate the distinction between memorization and understanding, often by
+training participants to distinguish arbitrary or random features in otherwise
+meaningless categorized stimuli. However the objective of real-world training,
+or learning from life experiences more generally, is often to develop new
+knowledge that may be applied in \textit{useful} ways in the future. In this
+sense, the gap between modern learning theories and modern pedagogical
+approaches and classroom learning strategies is enormous: most of our theories
+about \textit{how} people learn are inspired by experimental paradigms and
+models that have only peripheral relevance to the kinds of learning that
+students and teachers actually seek. To help bridge this gap, our study uses
+course materials from real online courses to inform, fit, and test models of
+real-world conceptual learning.
+
+\section*{Results}
 
@@
 
-Insert text here (Figs.~\ref{fig:demo}, \demo).
+\section*{Discussion}
+
+\section*{Materials and methods}
+
+\subsection*{Participants}
+
+\subsection*{Experiment}
+
+\subsection*{Analysis}
+
+\subsubsection*{Constructing text embeddings of multiple videos and questions}
+
+\subsubsection*{Estimating held-out conceptual knowledge}
+
+\subsubsection*{Creating knowledge and learning map visualizations}
 

### 2023-01-19 paper/main.tex
added more references to the introduction

@@
 
-\author{Paxton C. Fitzpatrick\textsuperscript{1} and Jeremy R.
-Manning\textsuperscript{*, 1}\\\textsuperscript{1}Dartmouth
+\author{Paxton C. Fitzpatrick and Jeremy R.
+Manning\textsuperscript{*}\\Dartmouth
 College\\\textsuperscript{*}Corresponding author:
@@
 understanding entail connecting newly acquired information to the scaffolding
-of one's existing knowledge or experience? Or weaving a lecture's atomic
+of one's existing knowledge or experience~\citep{BlayEtal06,CaraMaho03,
+ConsEtal16, DeacEtal04, SimoEtal04}? Or weaving a lecture's atomic
 elements (e.g., its component words) into a structured network that describes
@@
 individual atomic elements by reflecting the deeper meaning underlying the
-gestalt whole.
+gestalt whole~\citep{Kint70, Macl05, ScotEtal07}.
 
@@
 researchers in education, cognitive psychology, and cognitive
-neuroscience~\citep{Kato40, Gall10, ScotEtal13, HallGree08, Macl05} has
+neuroscience~\citep{Kato40, Gall00, ScotEtal07, HallGree08, Macl05} has
 profound analogs in the fields of natural language processing and natural
@@
 
-\begin{figure}[tp]
-\centering
-\includegraphics[width=0.8\textwidth]{figs/content-mastery}
-\caption{\textbf{Caption.} Placeholder text.}
-\label{fig:demo}
-\end{figure}
+% \begin{figure}[tp]
+% \centering
+% \includegraphics[width=0.8\textwidth]{figs/content-mastery}
+% \caption{\textbf{Caption.} Placeholder text.}
+% \label{fig:demo}
+% \end{figure}
 

### 2023-01-19 code/khan_helpers/khan_helpers/constants.py
standardize lecture/question colors for plots

@@ -21,3 +21,11 @@ STOP_WORDS = stopwords.words('english') + ['actual', 'actually', 'also', 'bit',
                                            'really', 'saw', 'see', 'seen',
                                            'thing', 'things', 'two', 'follow',
                                            'following']
+
+FORCES_LECTURE_COLOR = '#3f54a5'
+BOS_LECTURE_COLOR = '#0f8140'
+FORCES_QUESTION_COLOR = '#7d9ed2'
+BOS_QUESTION_COLOR = '#70c167'
+GENERAL_QUESTION_COLOR = '#b96bac'
+
+WORDLE_COLORS = ('#ffde17', '#ec008c', '#f26522')

### 2023-01-19 code/scripts/embedding/embedding_cruncher.py
removed old/unused code

@@ -1,66 +1,0 @@
-import sys
-import numpy as np
-from umap import UMAP
-from embedding_config import config
-from embedding_helpers import correlation_exp
-
-
-order, seed = int(sys.argv[1]), int(sys.argv[2])
-trajs_dir = config['datadir'].joinpath('trajectories')
-embeddings_dir = config['datadir'].joinpath('embeddings')
-models_dir = config['datadir'].joinpath('fit_reducers')
-
-ff_traj = np.load(trajs_dir.joinpath('forces_lecture.npy'))
-bos_traj = np.load(trajs_dir.joinpath('bos_lecture.npy'))
-questions = np.load(trajs_dir.joinpath('all_questions.npy'))
-
-ff_len = len(ff_traj)
-bos_len = len(bos_traj)
-
-if order == 1:
-    to_reduce = [ff_traj] + [bos_traj] + list(questions)
-elif order == 2:
-    to_reduce = [ff_traj] + list(questions) + [bos_traj]
-elif order == 3:
-    to_reduce = [bos_traj] + [ff_traj] + list(questions)
-elif order == 4:
-    to_reduce = [bos_traj] + list(questions) + [ff_traj]
-elif order == 5:
-    to_reduce = list(questions) + [ff_traj] + [bos_traj]
-else:
-    to_reduce = list(questions) + [bos_traj] + [ff_traj]
-
-split_inds = np.cumsum([np.atleast_2d(vec).shape[0] for vec in to_reduce])[:-1]
-stacked_vecs = np.log(np.vstack(to_reduce))
-
-for n_neighbors in range(5, 31, 5):
-    for min_dist in (.1, .2, .3, .4, .5, .6, .7, .8, .9):
-        for spread in range(1, 6):
-            fname = f"seed{seed}_nn{n_neighbors}_md{min_dist}_sp{spread}.npy"
-            embpath = embeddings_dir.joinpath(f'order{order}', fname)
-            modpath = models_dir.joinpath(f'order{order}', fname)
-            if embpath.is_file() and modpath.is_file():
-                continue
-
-            params = {
-                'n_components': 2,
-                'init': 'spectral',
-                'metric': correlation_exp,
-                'random_state': seed,
-                'n_neighbors': n_neighbors,
-                'min_dist': min_dist,
-                'spread': spread
-            }
-            np.random.seed(seed)
-            reducer = UMAP(**params).fit(stacked_vecs)
-
-            stacked_embeddings = reducer.embedding_
[…]

### 2023-01-19 code/scripts/embedding/embedding_helpers.py

@@ -1,88 +1,0 @@
-import numba
-import numpy as np
-from math import e
-
-
-@numba.njit
-def correlation_exp(x, y):
-    x = e ** x
-    y = e ** y
-    mu_x = 0.0
-    mu_y = 0.0
-    norm_x = 0.0
-    norm_y = 0.0
-    dot_product = 0.0
-
-    for i in range(x.shape[0]):
-        mu_x += x[i]
-        mu_y += y[i]
-
-    mu_x /= x.shape[0]
-    mu_y /= x.shape[0]
-
-    for i in range(x.shape[0]):
-        shifted_x = x[i] - mu_x
-        shifted_y = y[i] - mu_y
-        norm_x += shifted_x ** 2
-        norm_y += shifted_y ** 2
-        dot_product += shifted_x * shifted_y
-
-    if norm_x == 0.0 and norm_y == 0.0:
-        dist = 0.0
-        grad = np.zeros(x.shape)
-    elif dot_product == 0.0:
-        dist = 1.0
-        grad = np.zeros(x.shape)
-    else:
-        dist = 1.0 - (dot_product / np.sqrt(norm_x * norm_y))
-        grad = ((x - mu_x) / norm_x - (y - mu_y) / dot_product) * dist
-
-    return dist, grad
-
-
-# @numba.njit(fastmath=True)
-# def euclidean_exp(x, y):
-#     x = e ** x
-#     y = e ** y
-#     result = 0.0
-#     for i in range(x.shape[0]):
-#         result += (x[i] - y[i]) ** 2
-#     d = np.sqrt(result)
-#     grad = (x - y) / (1e-6 + d)
-#     return d, grad
-
-
-# @numba.njit(fastmath=True)
-# def symmetric_kl_exp(x, y, z=1e-11):
-#     x = e ** x
-#     y = e ** y
-#     n = x.shape[0]
-#     x_sum = 0.0
-#     y_sum = 0.0
-#     kl1 = 0.0
-#     kl2 = 0.0
-#
-#     for i in range(n):
-#         x[i] += z
-#         x_sum += x[i]
-#         y[i] += z
-#         y_sum += y[i]
-#
-#     for i in range(n):
-#         x[i] /= x_sum
-#         y[i] /= y_sum
-#
-#     for i in range(n):
-#         kl1 += x[i] * np.log(x[i] / y[i])
-#         kl2 += y[i] * np.log(y[i] / x[i])
-#
[…]

### 2023-01-19 code/scripts/embedding/run_job_cluster.sh

@@ -1,33 +1,0 @@
-#!/bin/bash -l
-
-# DO NOT MODIFY THIS FILE!
-
-# Portable Batch System (PBS) lines begin with "#PBS".  to-be-replaced text is sandwiched between angled brackets
-
-# declare a name for this job
-#PBS -N <config['jobname']>
-
-# specify the queue the job will be added to (if more than 600, use largeq)
-#PBS -q <config['q']>
-
-# specify the number of cores and nodes (estimate 4GB of RAM per core)
-#PBS -l nodes=<config['nnodes']>:ppn=<config['ppn']>
-
-# specify how long the job should run (wall time)
-#PBS -l walltime=<config['walltime']>
-
-# set the working directory *of the job* to the specified start directory
-cd <config['startdir']>
-
-echo ----
-
-echo ACTIVATING MEMORY DYNAMICS VIRTUAL ENVIRONMENT
-module load python
-source activate khan
-
-echo ----
-
-# run the job
-<config['cmd_wrapper']> <job_command> #note: job_command is reserved for the job command; it should not be specified in config.py
-
-conda deactivate

### 2023-01-19 docker/old/launch_notebooks.sh
remove old versions of docker setup files

@@ -1,462 +1,0 @@
-#!/usr/bin/env bash
-
-set -e
-
-# default arg values
-IMAGE_NAME="khan"                                        # name of image to build/use
-CONTAINER_NAME="Khan"                                    # name of container to create/start
-declare -i LAUNCH_BROWSER=1                              # true by default
-declare -i DETACH=0                                      # false by default
-
-# other configurables
-# NOTE: changing these has no effect after image is built & container is created
-declare -r DOCKERFILE_PATH="docker/Dockerfile-analyses"  # relative path from repository root to Dockerfile
-declare -r NOTEBOOKS_DIR="code/notebooks"                # relative path from repository root to notebooks folder
-declare -ir CONTAINER_PORT=8888                          # container port used to run notebook server and published to host
-declare -ir LOCAL_PORT=8888                              # host port bound to container port and used to run notebooks in browser
-
-
-# TODO: add extra configurable options for notebook-related --build-args (port, IP, etc.) and help to show_help()
-# TODO: check uname -m to set value passed to --platform=linux/<XXX>64. Will need to convert x86_64 to amd64
-########################################
-#         CLI PARSING FUNCTIONS        #
-########################################
-parse_args() {
-    while (( "$#" )); do
-        case "$1" in
-            -i | --image-name)
-                check_arg 1 "$@"
-                IMAGE_NAME=$2
-                shift 2
-                ;;
-            -c | --container-name)
-                check_arg 1 "$@"
-                CONTAINER_NAME=$2
-                shift 2
-                ;;
-            -b | --no-browser)
-                check_arg 0 "$@"
-                LAUNCH_BROWSER=0
-                shift
-                ;;
-            -d | --detach)
-                check_arg 0 "$@"
-                DETACH=1
-                shift
-                ;;
-            -h | --help)
-                show_help
-                exit 0
-                ;;
-            *)
-                { show_usage && echo "Error: unrecognized argument: $1"; } >&2
-                exit 1
-                ;;
-        esac
-    done
-
-    # readonly all values after updating defaults with args passed
-    readonly IMAGE_NAME
-    readonly CONTAINER_NAME
-    readonly LAUNCH_BROWSER
[…]

### 2023-01-20 paper/main.tex
added demographics survey responses, demographic survey notebook, and methods text reporting participant survey results

@@
 
+We enrolled a total of 50 Dartmouth undergraduate students in our study.
+Participants received course credit for enrolling. We asked each participant to
+fill out a demographic survey that included questions about their age, gender,
+native spoken language, ethnicity, race, hearing, color vision, sleep, coffee
+consumption, level of alertness, and several aspects of their educational
+background and prior coursework.
+
+Participants' ages ranged from 18 to 22 years (mean: 19.52 years;
+standard deviation: 1.09 years). A total of 15 participants reported
+their gender as male and 35 participants reported their gender as
+female. A total of 49 participants reported their native language as
+``English'' and 1 reported having another native language. A total of
+47 participants reported their ethnicity as ``Not Hispanic or Latino''
+and three reported their ethnicity as ``Hispanic or Latino.''
+Participants reported their races as White (32 participants), Asian
+(14 participants), Black or African American (5 participants),
+American Indian or Alaska Native (1 participant), and Native Hawaiian or
+Other Pacific Islander (1 participant). (Note that some participants
+selected multiple recial categories.)
+
+A total of 49 participants reporting having normal hearing and 1
+participant reported having some hearing impairment. A total of 49
+participants reported having normal color vision and 1 participant
+reported being color blind.  Participants reported having had, on the
+night prior to testing, 2 -- 4 hours of sleep (1 participant), 4 -- 6
+hours of sleep (9 participants), 6 -- 8 hours of sleep (35
+participants), or $8+$ hours of sleep (5 participants). They reported
+having consumed, on the same day and leading up to their testing
+session, 0 cups of coffee (38 participants), 1 cup of coffee (10
+participants), 3 cups of coffee (1 participant), or $4+$ cups of
+coffee (1 participant).
+
+No participants reported that their focus was currently impaired
+(e.g., by drugs or alcohol).  Participants reported their current
+level of alertness, and we converted their responses to numerical
+scores as follows: ``very sluggish'' (-2), ``a little sluggish'' (-1),
+``neutral'' (0), ``fairly alert'' (1), and ``very alert'' (2). Across
+all participants, a range of alertness levels were reported (range: -2
+-- 1; mean: -0.10; standard deviation: 0.84).
+
+Particpants reported their undergraduate major(s) as Social Sciences
+(28 participants), Natural sciences (16), Professional (e.g., pre-med
+or pre-law; 8 participants), Mathematics and engineering (7
+participants), Humanities (4 participants), or Undecided (3
+participants).  Note that some participants selected multiple
+categories for their undergraduate major.  We also asked participants
+about the courses they had taken.  In total, 46 participants reported
+having taken at least one Khan academy course in the past or being
+familiar with the Khan academy, and 4 reported not having taken any
+Khan academy courses.  Of the participants who reported having watched
+at least one Khan academy course, 1 participant declined to report the
+number of courses they had watched; 7 participants reported having
+watched 1--2 courses; 11 reported having watched 3--5 courses; 8
+reported having watched 5--10 courses; and 19 reported having watched
+10 or more courses.  We also asked participants about the specific
+courses they had watched, categorized under different subject areas.
+In the ``Mathematics'' area participants reported having watched
+videos on AP Calculus AB (21 participants), Precalculus (17
+participants), Algebra 2 (14 participants), AP Calculus BC (12
+participants), Trigonometry (11 participants), Algebra 1 (10
+participants), Geometry (8 participants), Pre-algebra (7
+participants), Multivariable Calculus (5 participants), Differential
+Equations (5 participants, Statistics and Probability (4
+participants), AP Statistics (2 participants), Linear Algebra (2
+participants), Early Math (1 participant), Arithmetic (1 participant),
+and other videos not listed in our survey (6 participants).  In the ``Science and engineering''
+area participants reported having watched videos on Chemistry, AP
+Chemistry, or Organic Chemstry (21
+participants); Physics, AP Physics I, or AP Physics II (15 participants); Biology, AP
+Biology; or High school Biology (15 participants); Health and Medicine
+(1 participant); or other videos not listed in our survey (20 participants).  We also asked
+participants if they had specifically seen the videos used in our
+experiment.  When we asked about the \textit{Four Fundamental Forces}
+video, 45 participants reported not having watched it before, 1
+participant reported that they were not sure if they had watched it
+before, and 4 participants declined to respond.  When we asked about
+the \textit{Birth of Stars} video, 46 participants reported not having
+watched it before and 4 participants declined to respond.  When we
+asked participants about non-Khan academy online courses, they
+reported having watched or taken courses on Mathematics (15
+participants), Science and engineering (11 participants), Test
+preparation (9 participants), Economics and finance (3 participants),
+Arts and humanities (2 participants), Computing (2 participants), and
+other categories not listed in our survey (18 participants).  Finally,
+we asked participants about in-person courses they had taken in
+different subject areas.  They reported taking courses in Mathematics
+(39 participants), Science and engineering (38 participants), Arts and
+humanities (35 participants), Test preparation (27 participants),
+Economics and finance (26 participants), Computing (15 participants),
+College and careers (7 participants), or other courses not listed in
+our survey (6 participants).
+
+% alertness + impairments
+
+% education
+
 \subsection*{Experiment}

### 2023-01-20 paper/main.tex
added experiment description and figure, supplemental table with question text

@@
 
-\newcommand{\demo}{S1}
+% supplemental tables
+\newcommand{\questions}{S1}
+
+% supplemental figures
 
@@
 
-% alertness + impairments
+\subsection*{Experiment}
 
-% education
+We hand-selected two roughly 10-minute course videos from the Khan Academy
+platform: \textit{The Four Fundamental Forces} (an introduction to gravity,
+electromagnetism, the weak nuclear force, and the strong nuclear force;
+duration: 10 minutes and 29 seconds) and \textit{Birth of Stars} (an
+introduction to how stars are formed; duration: 7 minutes and 57 seconds). We
+hand-wrote 30 multiple choice questions: 10 about the conceptual content of
+\textit{The Four Fundamental Forces}, another 10 about the conceptual content
+of \textit{Birth of Stars}, and 10 other questions that tested for general
+conceptual knowledge about basic physics (covering material that was not
+presented in either video). The full set of questions may be found in
+Table~\questions.
 
-\subsection*{Experiment}
+\begin{figure}[tp]
+\centering
+\includegraphics[width=\textwidth]{figs/experiment}
+
+\caption{\textbf{Experimental paradigm.} Participants alternate between
+answering 10-question multiple choice quizzes and watching two Khan academy
+videos. Each quiz contains a mix of 10 questions about each of: lecture 1,
+lecture 2, and general physics knowledge. The specific questions reflected on
+each quiz, and the orders of each quiz's questions, are randomized across
+participants.}
+
+\label{fig:experiment}
+\end{figure}
+
+Participants began the main experiment by answering a battery of 10 randomly
+selected questions (chosen from the full set of 30). Then they watched the
+\textit{The Four Fundamental Forces} video. Next, they answered a second set of
+10 questions (chosen at random from the remaining 20 questions). Fourth,
+participants watch the \textit{Birth of Stars} video, and finally they answered
+the remaining 10 questions. Our experimental procedure is diagramed in
+Figure~\ref{fig:experiment}. We used the experiment to develop and test our
+computational framework for estimating knowledge and learning maps.
 

### 2023-01-20 paper/supplement.tex
added experiment description and figure, supplemental table with question text

@@
 \usepackage{placeins}
+\usepackage{booktabs}
+\usepackage{longtable}
 
@@
 \renewcommand{\thefigure}{S\arabic{figure}}
+\renewcommand{\thetable}{S\arabic{table}}
 \renewcommand{\bibnumfmt}[1]{[S#1]}
@@
 
+\begin{titlepage}
 \maketitle
+\end{titlepage}
 
-\begin{figure}[tp]
-\centering
-\includegraphics[width=0.8\textwidth]{figs/content-mastery}
-\caption{\textbf{Caption.} Placeholder text.}
-\label{fig:demo}
-\end{figure}
+\begin{tiny}
+\renewcommand*{\arraystretch}{1.4}
+\begin{longtable}{r|p{0.375in}|p{1.275in}|p{0.75in}|p{0.75in}|p{0.75in}|p{0.75in}}
+
+    \textbf{ID} & \textbf{Question set} &                                                                                                                                                                                                                                                                         \textbf{Question} &                                                                                                                                     \textbf{Correct response} &                                                                                                     \textbf{Alternative 1} &                                                                                                                          \textbf{Alternative 2} &                                                                                                                                 \textbf{Alternative 3} \\\hline
+    1     &     FFF &                                                                                                                                                                                   Why is the gravitational attraction between you and your computer too small for you to notice?
+&                                           Neither you nor your computer has enough mass to cause a noticable gravitational attraction &                You and your computer are too close for the gravitational attraction to be significant &                                                                        Humans are too small to detect the force of gravity &  The gravitational attraction between you and your computer is disrupted by the larger gravitational field generated by the earth \\\hline
+    2     &     FFF &                                                                                                                                                                                                                    Which of the following is an example of the Weak Interaction?
+&                          A neutron in a radioactive Cesium atom is converted into a proton, leading to the release of a few particles &  Light from the sun collides with a satellite orbiting Earth and exerts a small push on the satellite &  Two protons bound together in a Helium nucleus resist separation despite a repulsive electromagnetic force acting on them &                                                   A distant galaxy exerts a small but detectable gravitational pull on the  Earth \\\hline
+    3     &     FFF &                                                                                                                                                                                                            Roughly how many times stronger is the Weak Interaction than gravity?
+&                                                                                                    10,\-000,\-000,\-000,\-000,\-000,\-000,\-000,\-000 &                                                                                                    10 &                                                                                                                  1,000,000 &                                                                                  The Weak Interaction is less strong than gravity \\\hline
+    4     &     FFF &                                                                                                                                                                              Why don't you and your computer experience any attraction or repulsion due to the Weak Interaction?
+&                                                                         The weak interaction only acts over extremely small distances &                The weak interaction between you and your computer is counteracted by the other forces &                                                                                   You and your computer have no net charge &                                            Neither you nor your computer has enough mass to induce a significant Weak Interaction \\\hline
+    5     &     FFF &                                                                                                                                                                                            Which of the following is a difference between gravity and the electromagnetic force?
+&                                            Gravity is only ever attractive while the electromagnetic force can both attract and repel &                                           Gravity is a much more powerful force than electromagnetism &           Gravity can only act over large distances while the electromagnetic force can act over large and small distances &                   The electromagnetic force can only act over small distances while gravity can act over small or large distances \\\hline
+    6     &     FFF &                                                                                                                                                                                                  Electricity and magnetism can be shown to be two cases of the same force if we: &                                                                                            View them in different frames of reference &                              Switch which charges we call positive and which charges we call negative &                                        Consider both the effects over small distances and the effects over large distances &                                                           Consider both the attractive and repulsive properties of the two forces \\\hline
+    7     &     FFF &                                                                                                                                  Which of the following are the primary two fundamental forces acting in opposition between the positively-charged protons in an atom's nucleus?
+&                                                                                        The Strong Force and the Electromagnetic Force &                                                                      Gravity and the Weak Interaction &                                                                                      Gravity and the Electromagnetic Force &                                                                                         The Strong Force and the Weak Interaction \\\hline
+    8     &     FFF &                                                                                                                                                                     Why does the universe have a very uneven distribution of mass but a relatively equal distribution of charge?
+&  Positive and negative charges cancel out and become a neutral charge when they combine while masses only grow larger as they combine &                                                    Masses tend to repel while charges tend to attract &                                                                         Masses tend to attract while charges tend to repel &       The gravitational interaction acting between masses is stronger than the electromagnetic interaction acting between charges \\\hline
+    9     &     FFF &  In your body, there are a tremendous amount of negatively-charged electrons.
+Your computer also contains a huge number of negatively-charged electrons.
+We know that like charges repel, but you and your computer are not repelled apart.
+Which of the following explains why?
+&                                    The electrons' negative charges are balanced by the positive charges of an equal number of protons &                                         An attractive gravitational force balances out this repulsion &                                                              The Electromagnetic force only acts over very small distances &                                                                     The Electromagnetic force only acts over very large distances \\\hline
+    10    &     FFF &                                                                                                                                                                                        Which of the following is a similarity between the Weak Interaction and the Strong Force?
+&                                                                                               Both act only over very small distances &                                                      Both are stronger than the Electromagnetic force &                                                                                               Both are weaker than Gravity &                                                                     Both are responsible for attractions between distant galaxies \\\hline
+    11    &     FFF &                                                                                                                                                                                                                          Which force is stronger than the Electromagnetic Force?
+&                                                                                                                          Strong Force &                                                                                               Gravity &                                                                                                           Weak Interaction &                                                                                            Electromagnetic Force is the strongest \\\hline
+    12    &     FFF &                                                                                                                                                                                                                Roughly how many times stronger is the Strong Force than gravity?
+&                                                                                                                                 10\textasciicircum 38 &                                                                                                   100 &                                                                                                                      10\textasciicircum 18 &                                                                                           The Strong Force is weaker than gravity \\\hline
+    13    &     FFF &                                                                                                                                                      Which of the following would have to be true for the Weak Interaction to cause repulsion or attraction between two objects?
+&                                                                            The objects would have to be extremely close to each other &                                                          The objects would have to have the same mass &                                                            The objects would have to be extremely far away from each other &                                                                                   The objects would have to have different masses \\\hline
+    14    &     FFF &                                                                                                                                                                                                                                  Which force keeps us from jumping off of Earth?
+&                                                                                                                               Gravity &                                                                                          Strong Force &                                                                                                           Weak Interaction &                                                                                                             Electromagnetic Force \\\hline
+    15    &     FFF &                                                                                                                                                                                                                                            What does the Coulomb Force refer to?
+&                                      The repulsion of objects with similar charge and the attraction of objects with different charge &          The repulsion of objects with similar mass and the attraction of objects with different mass &                 The repulsion of objects with similar temperature and the attraction of objects with different temperature &                                The repulsion of objects with similar density and the attraction of objects with different density \\\hline
+    16    &     BoS &                                                                                                                                                                                                      Which of the following describes the effect of gravity on a cloud of atoms?
+&                                                                                 The atoms move to the center of the mass of the atoms &                                          The atoms move away from the center of the mass of the atoms &                                                                  The atoms spin around the center of the mass of the atoms &                                                                                         Gravity has no effect on a cloud of atoms \\\hline
+    17    &     BoS &                                                                                                                                                                                                               Which of the following occurs as a cloud of atoms gets more dense?
+&                                                                                                                 Temperature increases &                                                                                 Temperature decreases &                                                                                                             Mass increases &                                                                                                                    Mass decreases \\\hline
+    18    &     BoS &                                                                                                                                                                   Which temperature does a cloud of hydrogen atoms approach as it gets denser in the process of becoming a star?
+&                                                                                                                     10 Million Kelvin &                                                                                              0 Kelvin &                                                                                                              10,000 Kelvin &                                                                                                                 10 Billion Kelvin \\\hline
+    19    &     BoS &                                                                                                                                                                                                                           Which of the following can overcome the Coulomb Force?
+&                                                                                                    High temperature and high pressure &                                                                     Low temperature and high pressure &                                                                                          High temperature and low pressure &                                                                                                  Low temperature and low pressure \\\hline
+    20    &     BoS &                                                                                                                                                                                                   Which of the following prevents a star from collapsing as a result of gravity?
+&                                                           Energy released from the fusion of hydrogen atoms provides outward pressure &                                    The fusion of hydrogen atoms decreases the temperature of the star &                                                                               The gravitational pull of other stars nearby &                                                                                                              The Weak Interaction \\\hline
+    21    &     BoS &                                                                                                                                                                                                                           How are supermassive stars different from other stars?
+&                                                                                                               Fusion occurs very fast &                                                                               Fusion occurs very slow &                                                                                         Fusion occurs in the reverse order &                                                                                                      Fusion does not occur at all \\\hline
+    22    &     BoS &                                                                                                                                                                                               Which of the following is the FIRST product of two hydrogen atoms fusing together?
+&                                                                                                                             Deuterium &                                                                                                Oxygen &                                                                                                                     Helium &                                                                                                                         Beryllium \\\hline
+    23    &     BoS &                                                                                                                                                                                       Once hydrogen atoms get close enough together, which of the following keeps them together?
+&                                                                                                                      The Strong Force &                                                                             The Electromagnetic Force &                                                                                                                    Gravity &                                                                                                              The Weak Interaction \\\hline
+    24    &     BoS &                                                                                                                                                    When two nuclei fuse together, how does the mass of the combined nucleus compare to the mass of each of the original nucleus?
+&                                                                                           The mass of the combined nucleus is smaller &                                                            The mass of the combined nucleus is larger &                                                                               The mass of the combined nucleus is the same &                                                                                It is not possible for two nuclei to fuse together \\\hline
+    25    &     BoS &                                                                                                                                                                                            If we say that our Sun is a main sequence star, what does that tell us about the Sun?
+&                                                                     Hydrogen atoms in the Sun are fusing together and becoming Helium &                                                                        The Sun is a supermassive star &                                     The Sun does not experience the force of Gravity but does experience the Coulomb Force &                                                                                 The Sun is comprised of 10 million Hydrogen atoms \\\hline
+    26    &     BoS &                                                                                                                                                                                                      Which force would cause a massive cloud of hydrogen atoms to move together?
+&                                                                                                                               Gravity &                                                                                          Strong Force &                                                                                                           Weak Interaction &                                                                                                             Electromagnetic Force \\\hline
+    27    &     BoS &                                                                                                                                                                                                                              Which of the following occurs as density increases?
+&                                                                                                                 Temperature increases &                                                                                      Volume increases &                                                                                                             Mass increases &                                                                                                                 None of the above \\\hline
+    28    &     BoS &                                                                                                                                                                                                                          Which of the following is a product of Hydrogen fusion?
+&                                                                                                                                Helium &                                                                                                Oxygen &                                                                                                                     Cesium &                                                                                                                            Carbon \\\hline
+    29    &     BoS &                                                                                                                                                                                                                       Which of the following terms accurately describes the Sun?
+&                                                                                                                    Main sequence star &                                                                                     Supermassive star &                                                                                                  Alternative sequence star &                                                                                                                 None of the above \\\hline
+    30    &     BoS &                                                                                                                                                                                                                   Which of the following terms best describes a fusion reaction?
+&                                                                                                                              Ignition &                                                                                            Combustion &                                                                                                              Decomposition &                                                                                                                      Displacement \\\hline
+    31    &      GK &                                                                                                                                                                                                   Which of the following lists of particles is ordered from smallest to largest?
+&                                                                                                       Electron, proton, nucleus, atom &                                                                       Atom, electron, proton, nucleus &                                                                                           Electron, nucleus, atom, neutron &                                                                                                  Neutron, nucleus, electrom, atom \\\hline
+    32    &      GK &                                                                                                                                                                                                                          Which of the following defines what element an atom is?
+&                                                                                                                 Its number of protons &                                                                                Its number of neutrons &                                                                                                    Its number of electrons &                                                                                                                          Its mass \\\hline
+    33    &      GK &                                                                                                                                                                    Suppose that in some atom, a proton is converted into a neutron.
+What changes as a result of this conversion?
+&                                                                                                                    The atom's element &                                                                The atom's mass (in atomic mass units) &                                                                                                        The atom's velocity &                                                                                                                The atom's density \\\hline
+    34    &      GK &                                                                                                                                                                                                                Which of the following lists is ordered from smallest to largest?
+&                                                                                                  Star, solar system, galaxy, universe &                                                             Galaxy, solar system, Milky Way, universe &                                                                                         Planet, galaxy, star, solar system &                                                                                             Earth, solar system, universe, galaxy \\\hline
+    35    &      GK &                                                                                                                                                                                                                    Which of the following are located in the nucleus of an atom?
+&                                                                                                                  Protons and neutrons &                                                                                          Only protons &                                                                                                             Only electrons &                                                                                                            Neutrons and electrons \\\hline
+    36    &      GK &                                                                                                                                                                                                                                       Which of the following has the least mass?
+&                                                                                                                           An electron &                                                                                              A proton &                                                                                                                  A neutron &                                                                                                                   A hydrogen atom \\\hline
+    37    &      GK &                                                                                                                                                                                                                         What percent of an atom's space does its nucleus occupy?
+&                                                                                                                          Less than 1\% &                                                                                                   10\% &                                                                                                                        50\% &                                                                                                                     More than 90\% \\\hline
+    38    &      GK &                                                                                                                                                                              In the famous equation attributed to Albert Einstein, E = mc\textasciicircum 2, what does the letter "m" represent?
+&                                                                                                                                  Mass &                                                                                              Momentum &                                                                                                          Moment of inertia &                                                                                                                             Moles \\\hline
+    39    &      GK &                                                                                                                                                                                                If I were to heat up an inflated balloon, which of the the following would occur?
+&                                                                                                              The balloon would expand &                                                                              The balloon would shrink &                                                                                          None of these answers are correct &                                        The balloon could expand or shrink depending on whether it's filled with air or helium gas \\
+
+    \caption{\textbf{Question pool.}  Each participant answered questions on three 30-question quizzes.
+Ten questions from each question set were included on each quiz: questions about the \textit{Four Fundamental Forces} lecture (FFF), questions about the \textit{Birth of Stars} lecture, and questions about general physics knowledge (GK).
+Each question appeared on at most one quiz (for each participant).}
+
+    \label{tab:questions}
+    \end{longtable}
+\end{tiny}
 

### 2023-01-20 paper/main.tex
fixed error in reported numbers of questions (thanks for the catch PF!)

@@
 introduction to how stars are formed; duration: 7 minutes and 57 seconds). We
-hand-wrote 30 multiple choice questions: 10 about the conceptual content of
-\textit{The Four Fundamental Forces}, another 10 about the conceptual content
-of \textit{Birth of Stars}, and 10 other questions that tested for general
+hand-wrote 39 multiple choice questions: 15 about the conceptual content of
+\textit{The Four Fundamental Forces}, another 15 about the conceptual content
+of \textit{Birth of Stars}, and 9 other questions that tested for general
 conceptual knowledge about basic physics (covering material that was not
@@
 \caption{\textbf{Experimental paradigm.} Participants alternate between
-answering 10-question multiple choice quizzes and watching two Khan academy
-videos. Each quiz contains a mix of 10 questions about each of: lecture 1,
-lecture 2, and general physics knowledge. The specific questions reflected on
-each quiz, and the orders of each quiz's questions, are randomized across
+answering 13-question multiple choice quizzes and watching two Khan academy
+videos. Each quiz contains a mix of 5 questions about lecture 1, 5 questions about lecture 2,
+and 3 general physics knowledge questions. The specific questions reflected on
+each quiz, and the orders of each quiz's questions, were randomized across
 participants.}

### 2023-01-20 paper/main.tex
oops-- another typo fix

@@
 
-Participants began the main experiment by answering a battery of 10 randomly
-selected questions (chosen from the full set of 30). Then they watched the
+Participants began the main experiment by answering a battery of 13 randomly
+selected questions (chosen from the full set of 39). Then they watched the
 \textit{The Four Fundamental Forces} video. Next, they answered a second set of
-10 questions (chosen at random from the remaining 20 questions). Fourth,
+13 questions (chosen at random from the remaining 20 questions). Fourth,
 participants watch the \textit{Birth of Stars} video, and finally they answered
-the remaining 10 questions. Our experimental procedure is diagramed in
+the remaining 13 questions. Our experimental procedure is diagramed in
 Figure~\ref{fig:experiment}. We used the experiment to develop and test our

### 2023-01-20 paper/main.tex
🤦
added sliding window figure

@@
 \textit{The Four Fundamental Forces} video. Next, they answered a second set of
-13 questions (chosen at random from the remaining 20 questions). Fourth,
+13 questions (chosen at random from the remaining 26 questions). Fourth,
 participants watch the \textit{Birth of Stars} video, and finally they answered
@@
 
+\begin{figure}[tp]
+\centering
+\includegraphics[width=\textwidth]{figs/sliding_windows}
+
+\caption{\textbf{Constructing video content \textit{trajectories}. \textbf{A.
+Building a document pool from sliding windows of text.} We decompose each
+video's transcript into a series of overlapping sliding windows. The set of
+transcript snippets (across all windows) may be treated as a set of
+``documents'' for training a text embedding model. After training a text
+embedding model using the two videos' sliding windows, along with the text from
+each question in our pool (Tab.~\questions), } we construct ``trajectories''
+through text embedding space by joining the embedding coordinates of successive
+sliding windows from each video. \textbf{B. Embedding multiple videos and
+questions.} Applying the same text embedding approach to each video, along with
+the text of each question, results in one trajectory per video and one
+embedding coordinate (dot) per question (blue: Four Fundamental Forces; green:
+Birth of Stars; pink: general physics knowledge).}
+
+\label{fig:sliding-windows}
+\end{figure}
+
+\subsubsection*{Estimating dynamic knowledge traces}
+
 \subsubsection*{Estimating held-out conceptual knowledge}

### 2023-01-20 paper/main.tex
added section on creating video trajectories and question embeddings, added table of top words from each topic to supplement

@@
 \newcommand{\questions}{S1}
+\newcommand{\topics}{S2}
 
@@
 
+We extended an approach developed by~\citep{HeusEtal21} to construct text
+embeddings for each moment of each lecture, and of each question in our pool.
+Briefly, our approach uses a topic model~\citep{BleiEtal03}, trained on a set
+of documents, to discover a set of $k$ ``topics'' or ``themes.'' Formally, each
+topic is defined as a set of weights over each word in the model's vocabulary
+(i.e., the union of all unique words, across all documents, excluding ``stop
+words.''). Conceptually, each topic is intended to give larger weights to set
+of words that appear conceptually related or that tend to co-occur in the same
+documents. After fitting a topic model, each document in the training set, or
+any \textit{new} document that contains at least some of the words in the
+model's vocabulary, may be represented as a $k$-dimensional vector describing
+how much the document (most probably) reflects each topic. (Unless, otherwise
+noted, we used $k = 15$ topics.)
+
 \begin{figure}[tp]
@@
 embedding coordinate (dot) per question (blue: Four Fundamental Forces; green:
-Birth of Stars; pink: general physics knowledge).}
+Birth of Stars; pink: general physics knowledge). Here we have projected the
+15-dimensional embeddings into a 3D space using Uniform Manifold Approximation
+and Projection~\citep[UMAP;][]{McInEtal18a}.}
 
@@
 \end{figure}
+
+As illustrated in Figure~\ref{fig:sliding-windows}A, we start by building up a
+corpus of documents using overlapping sliding windows that span each video's
+transcript. Khan Academy videos are hosted on the YouTube platform, and all
+YouTube videos are run through Google's speech-to-text API~\citep{HalpEtal16}
+to derive a timestamped transcript of any detected speech in the video. The
+resulting transcripts contain one timestamped row per line, and each line
+generally corresponds to a few seconds of spoken content from the video. We
+defined a sliding window length of (up to) $w = 30$ transcript lines, and we
+assigned each window a timestamp according to the midpoint between its first
+and last lines' timestamps. These sliding windows ramped up and down in length
+at the very beginning and end of the transcript, respectively. In other words,
+the first sliding window covered only the first line from the transcript; the
+second sliding window covered the first two lines; and so on. This ensured that
+each line of the transcript appeared in the same number ($w$) of sliding
+windows. We treated the text from each sliding window as a single ``document,''
+and we combined these documents across the two videos' windows to create a single
+training corpus for the topic model.  The top words from each of the 15 discovered
+topics may be found in Table~\topics.
+
+After fitting a topic model to each videos' transcripts, we could use the
+trained model to transform arbitrary (potentially new) documents into
+$k$-dimensional topic vectors. A convenient property of these topic vectors is
+that documents that reflect similar blends of topics (i.e., documents that
+reflect similar themes, according to the model) will yield similar (in terms of
+Euclidean distance, correlation, etc.) topic vectors. In general, the
+similarity between different documents' topic vectors may be used to
+characterize the similarity in content between the documents.
+
+We transformed each sliding window's text into a topic vector, and then used
+linear interpolation (independently for each topic dimension) to resample the
+resulting timeseries to once per second. This yielded a single topic vector for
+each second of each video. We also used the fitted model to obtain topic
+vectors for each question in our pool (Tab.~\questions). Taken together, we
+obtained a \textit{trajectory} for each video, describing its path through
+topic space, and a single coordinate for each question
+(Fig.~\ref{fig:sliding-windows}B). Embedding both videos and all of the
+questions using a common model enables us to compare the content from different
+moments of videos, compare the content across videos, and estimate potential
+associations between specific questions and specific moments of video.
 

### 2023-01-20 paper/supplement.tex
added section on creating video trajectories and question embeddings, added table of top words from each topic to supplement

@@
     31    &      GK &                                                                                                                                                                                                   Which of the following lists of particles is ordered from smallest to largest?
-&                                                                                                       Electron, proton, nucleus, atom &                                                                       Atom, electron, proton, nucleus &                                                                                           Electron, nucleus, atom, neutron &                                                                                                  Neutron, nucleus, electrom, atom \\\hline
+&                                                                                                       Electron, proton, nucleus, atom &                                                                       Atom, electron, proton, nucleus &                                                                                           Electron, nucleus, atom, neutron &                                                                                                  Neutron, nucleus, electron, atom \\\hline
     32    &      GK &                                                                                                                                                                                                                          Which of the following defines what element an atom is?
@@
 
-    \caption{\textbf{Question pool.}  Each participant answered questions on three 30-question quizzes.
-Ten questions from each question set were included on each quiz: questions about the \textit{Four Fundamental Forces} lecture (FFF), questions about the \textit{Birth of Stars} lecture, and questions about general physics knowledge (GK).
-Each question appeared on at most one quiz (for each participant).}
+    \caption{\textbf{Question pool.} Each participant answered questions on
+    three 30-question quizzes. Ten questions from each question set were
+    included on each quiz: questions about the \textit{Four Fundamental Forces}
+    lecture (FFF), questions about the \textit{Birth of Stars} lecture, and
+    questions about general physics knowledge (GK). Each question appeared on
+    at most one quiz (for each participant).}
 
@@
 \end{tiny}
+
+\newpage
+
+\begin{table}[tp]
+    \centering
+\begin{tiny}
+\begin{tabular}{r|l|l|l|l|l|l|l|l|l|l}
+
+    \textbf{Topic} &       \textbf{1}  &        \textbf{2}  &               \textbf{3}  &           \textbf{4}  &       \textbf{5}  &        \textbf{6}  &             \textbf{7}  &           \textbf{8}  &        \textbf{9}  &               \textbf{10} \\\hline
+    0     &     star &    helium &             main &         mass &   atomic &  sequence &            get &       energy &      fuse &         hydrogen \\\hline
+    1     &   charge &     force &             mass &      gravity &   strong &   attract &          large &     strength &  distance &  electromagnetic \\\hline
+    2     &     huge &     force &  electromagnetic &        macro &      way &     scale &  concentration &        apply &      kind &           charge \\\hline
+    3     &     atom &     dense &               go &     hydrogen &     slow &       get &           huge &     condense &      mass &            would \\\hline
+    4     &   fusion &       get &        threshold &         core &    occur &      mass &      something &        start &   several &          jupiter \\\hline
+    5     &   enough &  ignition &           proton &        force &      get &     close &        nucleus &      coulomb &    fusion &            would \\\hline
+    6     &   energy &  pressure &         ignition &         mass &   little &      keep &        provide &       fusion &       get &         hydrogen \\\hline
+    7     &   proton &      weak &          neutron &  interaction &      one &        go &        nucleon &       cesium &     extra &              get \\\hline
+    8     &      run &      kind &              say &           go &     want &     would &            get &         well &      give &         although \\\hline
+    9     &     huge &     cloud &            space &        float &  imagine &  hydrogen &           atom &          say &  distance &          combine \\\hline
+    10    &      one &  hydrogen &           helium &           go &   proton &   neutron &           keep &       atomic &    detail &             fuse \\\hline
+    11    &  gravity &     force &             weak &  interaction &    apply &  strength &       distance &          ten &  relative &             next \\\hline
+    12    &    force &        go &    electrostatic &         call &   charge &    magnet &           side &      coulomb &      know &        different \\\hline
+    13    &    force &      atom &          nucleus &     electron &     much &  hydrogen &            get &       around &   coulomb &           charge \\\hline
+    14    &    force &     scale &          gravity &        start &     weak &     orbit &           keep &  fundamental &    around &         surprise \\
+
+    \label{tab:topics}
+
+\end{tabular}
+\end{tiny}
+\caption{\textbf{Topics.} The table displays the 10 top-weighted word from
+    each of the 15 topics identified from sliding windows of two course video
+    transcripts (see \textit{Constructing text embeddings of multiple videos
+    and questions}).}
+\end{table}
 

### 2023-01-21 paper/main.tex
working on methods (knowledge traces and maps)

@@
 
-% \begin{figure}[tp]
-% \centering
-% \includegraphics[width=0.8\textwidth]{figs/content-mastery}
-% \caption{\textbf{Caption.} Placeholder text.}
-% \label{fig:demo}
-% \end{figure}
+\begin{figure}[tp]
+    \centering
+    \includegraphics[width=0.7\textwidth]{figs/content-mastery}
+
+    \caption{\textbf{Estimating moment-by-moment knowledge acquisition.}
+    \textbf{A. Moment-by-moment knowledge about the \textit{Four Fundamental
+    Forces}}. Each trace displays the weighted proportion of correctly answered
+    questions about the content reflected in each moment of the lecture (see
+    \textit{Estimating dynamic knowledge traces}), using responses from one
+    quiz (color). The traces are averaged across participants. \textbf{B.
+    Average estimated knowledge about the \textbf{Four Fundamental Forces}.}
+    Each bar displays the across-timepoint average knowledge, estimated using
+    the responses to one quiz's questions. \textbf{C. Moment-by-moment
+    knowledge about the \textit{Birth of Stars}}. The panel is in the same
+    format as Panel A, but here the knowledge estimates are for the
+    moment-by-moment content of the \textit{Birth of Stars} lecture. \textbf{D.
+    Average estimated knowledge about the \textit{Birth of Stars}.} The panel
+    is in the same format as Panel B, but here the knowledge estimates are for
+    the content of the \textit{Birth of Stars} lecture. All panels: error
+    ribbons and error bars denote 95\% confidence intervals, estimated across
+    participants.}
+
+    \label{fig:knowledge-timeseries}
+    \end{figure}
 
@@
 the first sliding window covered only the first line from the transcript; the
-second sliding window covered the first two lines; and so on. This ensured that
+second sliding window covered the first two lines; and so on. This insured that
 each line of the transcript appeared in the same number ($w$) of sliding
@@
 
+We used the following equation to estimate each participant's knowledge about
+timepoint $t$ of a given lecture, $\hat{k}(t)$:
+\begin{equation} 
+    \hat{k}(t) = \frac{\sum_{i \in \mathrm{correct}}\mathrm{ncorr}(t, i)}{\sum_{j = 1}^N \mathrm{ncorr}(t, j)},
+    \label{eqn:prop}
+\end{equation}
+where
+
+\begin{equation} 
+    \mathrm{ncorr}(x, y) = \frac{\mathrm{corr}(x, y) - \mathrm{mincorr}}{\mathrm{maxcorr} - \mathrm{mincorr}},
+\end{equation} 
+and where $\mathrm{mincorr}$ and $\mathrm{maxcorr}$ are the minimum and maximum
+correlations between any lecture timepoint and question, taken over all
+timepoints and questions across both lectures and all three question sets.
+
+Intuitively, $\mathrm{ncorr}(x, y)$ is the correlation between two topic
+vectors (e.g., the topic vector from one timepoint in a lecture, $x$, and the
+topic vector for one question, $y$), normalized by the minimum and maximum
+correlations (across all timepoints and questions) to range between 0 and 1,
+inclusive. Equation~\ref{eqn:prop} then computes the weighted average
+proportion of correctly answered questions about the content presented at
+timepoint $t$, where the weights are given by the normalized correlations
+between timepoint $t$'s topic vector and the topic vectors for each question.
+The normalization step (i.e., using $\mathrm{ncorr}$ instead of the raw
+correlations) insures that every question (except the least-relevant question)
+contributes some non-zero amount to the knowledge estimate.
+
 \subsubsection*{Estimating held-out conceptual knowledge}
@@
 
+\begin{equation}
+    \hat{k}(x) = \frac{\sum_{i \in \mathrm{correct}} \mathrm{RBF}(x, q_i, \lambda)}{\sum_{j = 1}^N \mathrm{RBF}(x, q_j, \lambda)},
+\end{equation}
+where
+\begin{equation}
+    \mathrm{RBF}(x, \mu, \lambda) = \exp\left\{-\frac{||x - \mu||^2}{\lambda}\right\}.
+\end{equation}
+
 \bibliographystyle{apa}

### 2023-01-22 paper/main.tex
added knowledge map figure, finished a complete draft of the methods section (excluding the "estimating held-out knowledge" section, which is waiting on our remaining analyses-- see slack discussion for more info)

@@
 % supplemental figures
+\newcommand{\individualKnowledgeMapsA}{S1}
+\newcommand{\individualKnowledgeMapsB}{S2}
+\newcommand{\individualKnowledgeMapsC}{S3}
+\newcommand{\individualLearningMapsA}{S4}
+\newcommand{\individualLearningMapsB}{S5}
 
@@
     \label{fig:knowledge-timeseries}
+    \end{figure}
+
+\begin{figure}[tp]
+    \centering
+    \includegraphics[width=\textwidth]{figs/knowledge_and_learning_maps}
+
+    \caption{\textbf{Mapping out the geometry of knowledge and learning.}
+    \textbf{A. Average ``knowledge maps'' estimated using each quiz.} Each map
+    displays a 2D projection of the estimated knowledge about the content
+    reflected by \textit{all} regions of topic space (see \textit{Creating
+    knowledge and learning map visualizations}). The topic trajectories of each
+    lecture and the coordinates of each question are indicated by dotted lines
+    and dots. Each map reflects an average across all participants. For
+    individual participants' maps, see
+    Figures~\individualKnowledgeMapsA,~\individualKnowledgeMapsB,
+    and~\individualKnowledgeMapsC. \textbf{B. Average ``learning maps''
+    estiamted between each successive pair of quizzes.} The learning maps are
+    in the same general format as the knowledge maps in Panel A, but each
+    coordinate in the learning maps indicates the \textit{difference} between
+    the corresponding coordinates in the indicated \textit{pair} of knowledge
+    maps-- i.e., how much the estimated knowledge ``changed'' across the two
+    quizzes. Each map reflects an average across all participants. For
+    individual participants' maps, see
+    Figures~\individualLearningMapsA~and~\individualLearningMapsB. \textbf{C.
+    Word clouds for sampled points in topic space.} Each word cloud displays
+    the relative weights of each word reflected by the blend of topics
+    represented at the locations of the stars in the maps. The words' colors
+    indicate how much each word is weighted on average across all timepoints'
+    topic vectors in the \textit{Four Fundamental Forces} (blue) and
+    \textit{Birth of Stars} (green) videos, respectively.}
+
+    \label{fig:knowledge-maps}
     \end{figure}
@@
 
-\begin{equation}
-    \hat{k}(x) = \frac{\sum_{i \in \mathrm{correct}} \mathrm{RBF}(x, q_i, \lambda)}{\sum_{j = 1}^N \mathrm{RBF}(x, q_j, \lambda)},
-\end{equation}
-where
+An important feature of our approach is that, given a trained text embedding
+model and participants' quiz performance on each question, we can estimate
+their knowledge about \textit{any} content expressable by the embedding model--
+not solely the content explicitly probed by the quiz questions. To visualize
+these estimates
+(Figs.~\ref{fig:knowledge-maps},~\individualKnowledgeMapsA,~\individualKnowledgeMapsB,~\individualKnowledgeMapsC,~\individualLearningMapsA,
+and~\individualLearningMapsB), we used UMAP~\citep{McInEtal18a} to define a 2D
+projection of the text embedding space. Sampling the original 100-dimensional
+space at high resolution to obtain an adequate set of topic vectors spanning
+the embedding space would be computationally intractable. However, sampling a
+2D grid is much more feasible. We defined a rectangle enclosing the 2D
+projections of the lectures' and quizzes' embeddings, and we sampled points
+from a regular $100 \times 100$ grid of coordinates that evenly tiled the
+enclosing rectangle. We sought to estimate participants' knoweldge (and
+learning-- i.e., changes in knowledge) at each of the resulting 10000
+coordinates.
+
+To generate our estimates, we placed a set of 39 radial basis functions (RBFs)
+throughout the embedding space, centered on the 2D projections for each
+question (i.e., we included one RBF for each question). At coordinate $x$, the
+value of an RBF centered on a question's coordinate $\mu$, is given by:
 \begin{equation}
     \mathrm{RBF}(x, \mu, \lambda) = \exp\left\{-\frac{||x - \mu||^2}{\lambda}\right\}.
+    \label{eqn:rbf}
 \end{equation}
+The $\lambda$ term in the RBF equation controls the ``smoothness'' of the
+function, where larger values of $\lambda$ result in smoother maps. In our
+implementation we used $\lambda = 50$.  Next, we estimated the ``knowledge''
+at each coordinate, $x$, using:
+\begin{equation}
+    \hat{k}(x) = \frac{\sum_{i \in \mathrm{correct}} \mathrm{RBF}(x, q_i, \lambda)}{\sum_{j = 1}^N \mathrm{RBF}(x, q_j, \lambda)}.
+    \label{eqn:rbf-knowledge}
+\end{equation}
+Intuitively, Equation~\ref{eqn:rbf-knowledge} computes the weighted proportion of
+correctly answered questions, where the weights are given by how nearby (in the 2D space)
+each question is to the $x$.  We also defined \textit{learning maps} as the coordinate-by-coordinate
+differences between any pair of knowledge maps.  Intuitively, learning maps reflect the \textit{change}
+in knowledge across two maps.
 

### 2023-01-23 paper/main.tex
working on results section

@@
 
-How do we acquire conceptual knowledge? Memorizing course lectures or textbook
-chapters by rote can lead to the superficial \textit{appearance} of
-understanding the underlying content, but achieving true conceptual
-understanding seems to require something deeper and richer. Does conceptual
-understanding entail connecting newly acquired information to the scaffolding
-of one's existing knowledge or experience~\citep{BlayEtal06,CaraMaho03,
-ConsEtal16, DeacEtal04, SimoEtal04}? Or weaving a lecture's atomic
-elements (e.g., its component words) into a structured network that describes
-how those individual elements are related? Conceptual understanding could also
-involve building a mental model that transcends the meanings of those
-individual atomic elements by reflecting the deeper meaning underlying the
-gestalt whole~\citep{Kint70, Macl05, ScotEtal07}.
+Suppose that a teacher had access to a complete ``map'' of everything a student
+knew. Defining what such a map might even look like, let alone how it might be
+constructed or filled in, is itself a non-trivial problem. But if a teacher
+\textit{were} to gain access to such a map, how might that change their ability
+to teach the student? Perhaps they might start by checking how well the student
+knew the to-be-learned information already, or how much they knew about related
+concepts. For some students, they could potentially optimize their teaching
+efforts to maximize efficiency by focusing primarily on not-yet-known content.
+For other students (or other content areas), it might be more effective to
+optimize for direct connections between already-known content and any new
+material. Observing how the student's knowledge was changing over time, in
+response to their training, could also help to guide the teacher.
+
+Designing and building procedures and tools for mapping out knowledge touches
+on deep questions about what it means to learn. For example, how do we acquire
+conceptual knowledge? Memorizing course lectures or textbook chapters by rote
+can lead to the superficial \textit{appearance} of understanding the underlying
+content, but achieving true conceptual understanding seems to require something
+deeper and richer. Does conceptual understanding entail connecting newly
+acquired information to the scaffolding of one's existing knowledge or
+experience~\citep{BlayEtal06,CaraMaho03, ConsEtal16, DeacEtal04, SimoEtal04}?
+Or weaving a lecture's atomic elements (e.g., its component words) into a
+structured network that describes how those individual elements are related?
+Conceptual understanding could also involve building a mental model that
+transcends the meanings of those individual atomic elements by reflecting the
+deeper meaning underlying the gestalt whole~\citep{Kint70, Macl05, ScotEtal07}.
 
@@
 
-What form might the representation of the sum total of a person's knowledge
-take? First, we might require a means of systematically describing or
-representing the nearly infinite set of possible things a person could know.
-Second, we might want to account for potential associations between different
-concepts. For example, the concepts of ``fish'' and ``water'' might be
-associated in the sense that fish live in water. Third, knowledge may have a
+Given these insights, what form might the representation of the sum total of a
+person's knowledge take? First, we might require a means of systematically
+describing or representing the nearly infinite set of possible things a person
+could know. Second, we might want to account for potential associations between
+different concepts. For example, the concepts of ``fish'' and ``water'' might
+be associated in the sense that fish live in water. Third, knowledge may have a
 critical dependency structure, such that knowing about a particular concept
@@
 that related concepts are located nearby in space. We use this framework to
-analyzing and interpreting behavioral data collected from an experiment that
-has participants watch and answer conceptual questions about a series of
-recorded course lectures.
+analyze and interpret behavioral data collected from an experiment that has
+participants watch and answer conceptual questions about a series of recorded
+course lectures.
 
@@
 course materials from real online courses to inform, fit, and test models of
-real-world conceptual learning.
+real-world conceptual learning. We also provide a ``proof of concept''
+demonstration of how our models might be used to construct ``maps'' of what
+students know, and how their knowledge changes with training. In addition to
+helping to visualize knowledge (and changes in knowledge), we hope that such
+maps might lead to real-world tools for improving how we educate.
 
 \section*{Results}
+
+At its core, our main modeling approach is based around a simple assumption
+that we sought to test empirically: all else being equal, knowledge about a
+given concept is predictive of knowledge about similar or related concepts.
+From a geometric perspective, this assumption implies that knowledge is
+fundamentally ``smooth.'' In other words, as one moves through a space
+representing someone's knowledge (where similar concepts occupy nearby
+coordinates), their ``level of knowledge'' should change relatively gradually
+throughout that space. To begin to test this smoothness assumption, we sought
+to track our participants' knowledge and how it changed over time in response
+to training.
+
+We asked our participants to answer questions from several multiple choice
+quizzes and watch two lecture videos from the \textit{Khan Academy} platform
+(Fig.~\ref{fig:experiment}). One lecture video, entitled \textit{Four
+Fundamental Forces}, was about the four fundamental forces in physics: gravity,
+strong and weak interactions, and electromagnetism. The second lecture video,
+entitled \textit{Birth of Stars}, provides an overview of our current
+understanding of how stars form. We selected both lessons to be (a) accessible
+to a broad audience, e.g., by minimizing prerequisite knowledge, (b) largely
+independent of each other, e.g., so that the two videos focused on different
+material and did not depend on each other, and (c) related to each other, e.g.,
+so that both videos contained at least \textit{some} similar or overlapping
+content. The two videos we selected are introductory, about different primary
+concepts, but also touch on ``physics'' and ``astronomy'' themes. We also wrote
+a set of multiple choice quiz questions that would enable us to test
+participants' knoweldge about each individual video and about related content
+not specifically presented in either video (Tab.~\questions). Participants
+answered questions randomly drawn from each content area (lecture 1, lecture 2,
+and general physics knowledge) across each of three quizzes. Quiz 1 was
+intended to assessed participants' knowledge before training; quiz 2 assessed
+knowledge after watching the Four Fundamental Forces video (i.e., lecture 1);
+and quiz 3 assessed knowledge after watching the Birth of Stars video (i.e.,
+lecture 2).
+
+\begin{figure}[tp]
+    \centering
+    \includegraphics[width=\textwidth]{figs/experiment}
+
+    \caption{\textbf{Experimental paradigm.} Participants alternate between
+    answering 13-question multiple choice quizzes and watching two Khan academy
+    videos. Each quiz contains a mix of 5 questions about lecture 1, 5
+    questions about lecture 2, and 3 general physics knowledge questions. The
+    specific questions reflected on each quiz, and the orders of each quiz's
+    questions, were randomized across participants.}
+
+    \label{fig:experiment}
+\end{figure}
+
+We trained a text embedding model using sliding windows of text from the two
+videos' transcripts (see \textit{Constructing text embeddings of multiple
+videos and questions}). We also used the same model (i.e., trained on the
+videos' transcripts) to embed the text of each question in our pool. This
+yielded, for each second of each video, and for each question, a single topic
+vector-- i.e., a coordinate in a text embedding space
+(Fig.~\ref{fig:sliding-windows}). Intuitively, each dimension of the embedding
+space corresponds to a ``theme'' or ``topic'' reflected in some part(s) of the
+videos (Tab.~\topics), and the coordinates in embedding space denote the blend
+of themes reflected by a particular excerpt of text (e.g., from part of a
+video's transcript, from a question, etc.).
+
+\begin{figure}[tp]
+    \centering
+    \includegraphics[width=\textwidth]{figs/lecture-question-similarity}
+
+    \caption{\textbf{Which parts of each lecture are captured by each
+    question?} Each panel displays timeseries plots showing how each question's
+    topic vector correlates with each video timepoint's topic vector. The left
+    panel displays these correlations for the \textit{Four Fundamental Forces}
+    lecture and associated questions, and the right panels displays these
+    correlations for the \textit{Birth of Stars} lecture and associated
+    questions. The colors denote question identities. The diamonds in each
+    panel denote the moment of peak correlation between the indicated
+    questions, in the indicated lectures. The associated questions' text, and
+    snippets of the lectures' transcripts in the best-matching sliding windows,
+    are displayed at the bottom of the figure.}
+
+    \label{fig:question-correlations}
+\end{figure}
+
+Although a single lecture may be organized a single broad theme at a coarse
+scale, at a finer scale each moment of a lecture typically covers a narrower
+range of content. We wondered whether a text embedding model trained on the
+lectures' transcripts might capture some of this finer scale content. For
+example, if a particular question asks about the content from one small part of
+a lecture, we wondered whether our text embedding model could be used to
+automatically identify the ``matching'' moment(s) in the lecture. When we
+correlated each question's topic vector with the topic vectors for each second
+of the lectures, we found some evidence that each question is temporally
+specific (Fig.~\ref{fig:question-correlations}). In particular, most questions'
+topic vectors were maximally correlated with a well-defined range of timepoints
+from their corresponding lectures, and the correlations fell off sharply
+outside of that range. We also examined the best-matching intervals for each
+question qualitatively by comparing the text of the question to the text of the
+most-correlated parts of the lectures. Despite that the questions were excluded
+from the text embedding model's training set, in general we found a close
+correspondence between the conceptual content that each question covered and
+the content covered by the best-matching moments of the lectures. Two
+representative examples are shown at the bottom of
+Fig.~\ref{fig:question-correlations}.
+
+The ability to quantify how much each question is ``asking about'' each moment
+of the lectures could enable high-resolution insights into participants'
+knowledge. Traditional approaches to estimating how much a student ``knows''
+about the content of a given lecture entail computing the proportion of
+correctly answered questions. But if two students receive identical scores on
+an exam, might our modeling framework help us to gain more naunced insights
+into the \textit{specific} content that each student has mastered (or failed to
+master)? For example, a student who misses three questions that were all about
+the same concept (e.g., concept $A$) will have gotten the same
+\textit{proportion} of questions correct as another student who missed three
+questions about three \textit{different} concepts (e.g., $A$, $B$, and $C$).
+But if we wanted to fill in the ``gaps'' in the two students' understandings,
+we might do well to focus on concept $A$ for the first student, but add in
+concepts $B$ and $C$ for the second student.
+
+\textbf{JRM STOPPED HERE...}
+
+As a sanity check, we anticipated that our knowledge estimates
+should show a content-specific ``boost'' in participants' knowledge after
+watching each video.
 
@@
 
-\begin{figure}[tp]
-\centering
-\includegraphics[width=\textwidth]{figs/experiment}
-
-\caption{\textbf{Experimental paradigm.} Participants alternate between
-answering 13-question multiple choice quizzes and watching two Khan academy
-videos. Each quiz contains a mix of 5 questions about lecture 1, 5 questions about lecture 2,
-and 3 general physics knowledge questions. The specific questions reflected on
-each quiz, and the orders of each quiz's questions, were randomized across
-participants.}
-
-\label{fig:experiment}
-\end{figure}
-
 Participants began the main experiment by answering a battery of 13 randomly

### 2023-01-23 paper/admin/cover_letter.tex

\title{cover letter}
%
% See http://texblog.org/2013/11/11/latexs-alternative-letter-class-newlfm/
% and http://www.ctan.org/tex-archive/macros/latex/contrib/newlfm
% for more information.
%
\documentclass[11pt,stdletter,orderfromtodate,sigleft]{newlfm}
\usepackage{blindtext, xfrac, animate, hyperref, pxfonts, geometry}

  \setlength{\voffset}{0in}

\newlfmP{dateskipbefore=0pt}
\newlfmP{sigsize=20pt}
\newlfmP{sigskipbefore=10pt}

\newlfmP{Headlinewd=0pt,Footlinewd=0pt}

\newcommand{\journal}{Journal Name}
\newcommand{\articletype}{Article Type}
\newcommand{\title}{Paper title}
\newcommand{\corresponding}{Corresponding Author Name}

\namefrom{\vspace{-0.3in}\corresponding}
\addrfrom{
  Corresponding Author Institution\\
  Corresponding Author Department\\
  Corresponding Author Address\\
  City, State, Zip code}
\addrto{}
\dateset{\today}

\greetto{To the editors of \textit{\journal}:}

\closeline{Sincerely,}
%\usepackage{setspace}
%\linespread{0.85}
% How will your work make others in the field think differently and move the field forward?
% How does your work relate to the current literature on the topic?
% Who do you consider to be the most relevant audience for this work?
% Have you made clear in the letter what the work has and has not achieved?

\begin{document}
\begin{newlfm}
  We have enclosed our manuscript entitled \textit{\title} to be
  considered for publication as an \textit{\articletype}.  The
  manuscript... (insert one sentence summary).

(insert 1--2 paragraph summary of most important findings and how they
fit into the broader literature)

We expect that this article will be of interest to... (briefly describe target audience).

Thank you for considering this manuscript, and I hope you will find it suitable for publication in \textit{\journal}.

\end{newlfm}
\end{document}

### 2023-01-25 code/khan_helpers/khan_helpers/constants.py
standardize colors for correctly and incorrectly answered questions

@@ -29,3 +29,6 @@ BOS_QUESTION_COLOR = '#70c167'
 GENERAL_QUESTION_COLOR = '#b96bac'
 
 WORDLE_COLORS = ('#ffde17', '#ec008c', '#f26522')
+
+CORRECT_ANSWER_COLOR = '#67c4ca'
+INCORRECT_ANSWER_COLOR = '#cb6d67'

### 2023-01-25 paper/main.tex
finished remaining methods section, added in (captionless) held-out-questions figure

@@
 
+\begin{figure}[tp]
+    \centering
+    \includegraphics[width=\textwidth]{figs/held-out-question-analyses}
+
+    \caption{\textbf{Estimating knowledge for held-out questions.}}
+
+    \label{fig:predictions}
+\end{figure}
+
 \section*{Discussion}
@@
 
-\subsubsection*{Estimating held-out conceptual knowledge}
-
 \subsubsection*{Creating knowledge and learning map visualizations}
@@
 
+\subsubsection*{Testing the ``smoothness'' of knowledge}
+
+A core assumption of our modeling framework is that knowledge is ``smooth''
+such that knowing about one concept implies knowledge about other related
+concepts (i.e., concepts that are nearby in text embedding space). Conversely,
+\textit{not} knowing about a given concept implies \textit{less} knowledge
+about other related concepts. We characterized how estimated knowledge (and
+lack of knowledge) fell off with distance in the text embedding space
+(Fig.~\ref{fig:predictions}, top panels).
+
+For each participant, for each quiz, for each of $c$ correctly answered
+question $q$ in turn, we sorted all of the other correctly answered questions
+in descending order of their topic vectors' correlations with $q$'s topic
+vector. We repeated this for all correctly answered questions to obtain a $c
+\times (c - 1)$ matrix of correlations, where the rows corresponded to held-out
+questions and the columns corresponded to the most similar (leftmost column),
+second most similar (second column), other correctly answered questions. Note
+that each correlation for each pair of questions ($a$ and $b$) appears exactly
+twice in this matrix: once when $a$ is the held-out question, and once when $b$
+is the held-out question. We applied the Fisher $z$-transformation to these
+correlations, averaged down the rows, and then applied the inverse Fisher
+$z$-transformation to obtain a $1 \times (c - 1)$ array of average correlations
+for the participant. We repeated this process across all $n$ participants,
+yielding an $n \times 14$ matrix (15 is the maximum number of questions that
+could have been answered correctly on any single 15-question quiz, so at most
+14 correctly answered questions could be compared to a held-out correctly
+answered question). Note that some of the entries, for some of the
+participants, were empty (e.g., if a given participant answered at least one
+question incorrectly, they would never have 14 other correctly answered
+questions to compare to a held-out correctly answered question). If a
+participant answered \textit{no} questions correctly on a given quiz, their
+entire row would be empty.
+
+The blue ribbon plots in the top panels of Figure~\ref{fig:predictions} display
+the mean (across participants) and bootstrap-estimated 95\% confidence
+intervals of these matrices (i.e., one per quiz, each plotted in a separate
+panel). We repeated the same process for \textit{incorrectly} answered
+questions (i.e., comparing held-out incorrectly answered questions to other
+incorrectly answered questions from the same quiz, for each participant in
+turn) to obtain the red ribbon plots in the top panels of
+Figure~\ref{fig:predictions}.
+
+\subsubsection*{Estimating held-out conceptual knowledge}
+
+If we are able to accurately estimate a participant's knowledge about the
+content tested by a given question, the estimated knowledge should have some
+predictive information about whether the participant is likely ot answer the
+question correctly or incorrectly. For each question in turn, for each
+participant, we used Equation~\ref{eqn:prop} to estimate (using all
+\textit{other} questions from the same quiz, from the same participant) the
+participant's knowledge at the held-out question's embedding coordinate. For
+each quiz, we aggregated these estimates into two distributions: one for the
+estimated knowledge at the coordinates of each \textit{correctly} answered
+question, and anotehr for the estimated knowledge at the coordinates of each
+\textit{incorrectly} answered question (Fig.~\ref{fig:predictions}, bottom
+panels). We then used independent samples $t$-tests to compare the means of
+these distributions of estimated knowledge.
+
 \bibliographystyle{apa}

### 2023-01-25 code/khan_helpers/khan_helpers/constants.py
update FIG_DIR to save figures to source/ folder

@@ -9,7 +9,7 @@ PARTICIPANTS_DIR = DATA_DIR.joinpath('participants')
 TRAJS_DIR = DATA_DIR.joinpath('trajectories')
 EMBS_DIR = DATA_DIR.joinpath('embeddings')
 MODELS_DIR = DATA_DIR.joinpath('models')
-FIG_DIR = Path('/mnt/paper/figs/')
+FIG_DIR = Path('/mnt/paper/figs/source/')
 
 # number of timestamped lines in lecture transcript sliding windows
 LECTURE_WSIZE = 30

### 2023-01-25 paper/main.tex
added paragraph with missing stats for knowledge timeseries figure and associated text

@@
 But if we wanted to fill in the ``gaps'' in the two students' understandings,
-we might do well to focus on concept $A$ for the first student, but add in
-concepts $B$ and $C$ for the second student.
+we might do well to focus on concept $A$ for the first student, but to also add
+in materials pertaining to concepts $B$ and $C$ for the second student.
 
-\textbf{JRM STOPPED HERE...}
-
-As a sanity check, we anticipated that our knowledge estimates
-should show a content-specific ``boost'' in participants' knowledge after
-watching each video.
+We developed a simple formula (Eqn.~\ref{eqn:prop}) for using a participant's
+responses to a small set of multiple choice questions to estimate how much the
+participant ``knows'' about the concept reflected by any arbitrary coordinate,
+$x$, in text embedding space (e.g., the content reflected by any moment in a
+lecture they had watched; see \textit{Estimating dynamic knowledge traces}).
+Essentially, the estimated knowledge at the coordinate is given by the weighted
+average proportion of quiz questions the participant answered correctly, where
+the weights reflect how much each question is ``about'' the content at $x$.
+When we apply this approach to estimate the participant's knowledge about the
+content presented in each moment of each lecture, we can obtain a detailed
+timecourse describing how much ``knowledge'' the participant has about any part
+of the lecture. As shown in Figures~\ref{fig:knowledge-timeseries}A and C), we
+can also apply this approach separately for the questions from each quiz the
+participants took throughout the experiment. From just 13 questions per quiz,
+we obtain a high-resolution snapshot (at the time each quiz was taken) of what
+the participants knew about any moment's content, from either of the two
+lectures they watched (comprising a total of 1106 samples across the two
+lectures).
 
@@
 \end{figure}
+
+Of course, even though the timecourses in
+Figure~\ref{fig:knowledge-timeseries}A and C provide detailed
+\textit{estimates} about participants' knowlege, those estimates are only
+\textit{useful} to the extent that they accurately reflect what participants
+actually know. As one sanity check, we anticipated that the knowledge estimates
+should show a content-specific ``boost'' in participants' knowledge after
+watching each lecture. In other words, if participants learn about each
+lecture's content when they watch each lecture, the knowledge estimates should
+reflect that. After watching the \textit{Four Fundamental Forces} lecture,
+participants should show more knowledge for the content of that lecture than
+they had before, and that knowledge should persist for the remainder of the
+experiment. Specifically, knowledge about that lecture's content should be
+relatively low when estimated using Quiz 1 responses, but should increase when
+estimated using Quiz 2 or 3 responses (Fig.~\ref{fig:knowledge-timeseries}B).
+Indeed, we found that participants' estimated knowledge about the content of
+the \textit{Four Fundamental Forces} was substantially higher on Quiz 2 versus
+Quiz 1 ($t(XX) = XX, p = XX$) and on Quiz 3 versus Quiz 1 ($t(XX) = XX, p =
+XX$). We found no reliable differences in estimated knowledge about that
+lecture's content on Quiz 2 versus 3 ($t(XX) = XX, p = XX$). Similarly, we
+hypothesized (and subsequently confirmed) that participants should show more
+estimated knowledge about the content of the \textit{Birth of Stars} lecture
+after (versus before) watching it (Fig.~\ref{fig:knowledge-timeseries}D).
+Specifically, since participants watched that lecture after taking Quiz 2 (but
+before Quiz 3), we hypothesized that their knowledge estimates should be
+relatively low on Quizzes 1 and 2, but should show a ``boost'' on Quiz 3.
+Consistent with this prediction, we found no reliable differences in estimated
+knowledge about the \textit{Birth of Stars} lecture content on Quizzes 1 versus
+2 ($t(XX) = XX, p = XX$), but the estimated knowledge was substantially higher
+on Quiz 3 versus 2 ($t(XX) = XX, p = XX$) and Quiz 3 versus 1 ($t(XX) = XX, p =
+XX$).
 
@@
 
-    \caption{\textbf{Estimating knowledge for held-out questions.}}
+    \caption{\textbf{Estimating knowledge at the embedding coordinates of
+    held-out questions.} \textbf{Top panels.} Separately for each quiz (panel
+    column), we plot the average correlations between the topic vectors of
+    held-out correctly (blue) and incorrectly (red) answered questions, and the
+    topic vectors for the $n$ closest remaining correctly or incorrectly
+    answered questions, respectively. For details, see \textit{Testing the
+    ``smoothness'' of knowledge}. \textbf{Bottom panels.} Separately for each
+    quiz (panel column), we plot the distributions of predicted knowledge at
+    the embedding coordinates of each held out correctly (blue) or incorrectly
+    (red) answered question. The $t$-tests reported in each panel are between
+    the distributions of estimated knowledge at the coordinates of correctly
+    versus incorrectly answered held-out questions. For details, see
+    \textit{Estimating held-out conceptual knowledge}.}
 

### 2023-01-25 paper/main.tex
backing up progress before stopping for a meeting...

@@
 
+A core assumption of our modeling framework is that knowledge is ``smooth''
+such that knowing about one concept implies knowledge about other related
+concepts (i.e., concepts that are nearby in text embedding space). Conversely,
+\textit{not} knowing about a given concept implies \textit{less} knowledge
+about other related concepts. We characterized how estimated knowledge (and
+lack of knowledge) fell off with distance in the text embedding space
+(Fig.~\ref{fig:predictions}, top panels).
+
+\begin{figure}[tp]
+    \centering
+    \includegraphics[width=\textwidth]{figs/held-out-question-analyses}
+
+    \caption{\textbf{Estimating knowledge at the embedding coordinates of
+    held-out questions.} \textbf{Top panels.} Separately for each quiz (panel
+    column), we plot the average correlations between the topic vectors of
+    held-out correctly (blue) and incorrectly (red) answered questions, and the
+    topic vectors for the $n$ closest remaining correctly or incorrectly
+    answered questions, respectively. For details, see \textit{Testing the
+    ``smoothness'' of knowledge}. \textbf{Bottom panels.} Separately for each
+    quiz (panel column), we plot the distributions of predicted knowledge at
+    the embedding coordinates of each held out correctly (blue) or incorrectly
+    (red) answered question. The $t$-tests reported in each panel are between
+    the distributions of estimated knowledge at the coordinates of correctly
+    versus incorrectly answered held-out questions. For details, see
+    \textit{Estimating held-out conceptual knowledge}.}
+
+    \label{fig:predictions}
+\end{figure}
+
+For each participant, for each quiz, for each of $c$ correctly answered
+question $q$ in turn, we sorted all of the other correctly answered questions
+in descending order of their topic vectors' correlations with $q$'s topic
+vector. We repeated this for all correctly answered questions to obtain a $c
+\times (c - 1)$ matrix of correlations, where the rows corresponded to held-out
+questions and the columns corresponded to the most similar (leftmost column),
+second most similar (second column), other correctly answered questions. Each
+correlation for each pair of questions ($a$ and $b$) appears exactly twice in
+this matrix: once when $a$ is the held-out question, and once when $b$ is the
+held-out question. We applied the Fisher $z$-transformation to these
+correlations, averaged down the rows, and then applied the inverse Fisher
+$z$-transformation to obtain a $1 \times (c - 1)$ array of average correlations
+for the participant. We repeated this process across all $n$ participants,
+yielding an $n \times 14$ matrix (15 is the maximum number of questions that
+could have been answered correctly on any single 15-question quiz, so at most
+14 correctly answered questions could be compared to a held-out correctly
+answered question). Note that some of the entries, for some of the
+participants, were empty (e.g., if a given participant answered at least one
+question incorrectly, they would never have 14 other correctly answered
+questions to compare to a held-out correctly answered question). If a
+participant answered \textit{no} questions correctly on a given quiz, their
+entire row would be empty.
+
+The blue ribbon plots in the top panels of Figure~\ref{fig:predictions} display
+the mean (across participants) and bootstrap-estimated 95\% confidence
+intervals of these matrices (i.e., one per quiz, each plotted in a separate
+panel). We repeated the same process for \textit{incorrectly} answered
+questions (i.e., comparing held-out incorrectly answered questions to other
+incorrectly answered questions from the same quiz, for each participant in
+turn) to obtain the red ribbon plots in the top panels of
+Figure~\ref{fig:predictions}.
+
+The correlation plots for both curves, in all three top panels of
+Figure~\ref{fig:predictions}, confirm one aspect of our ``smoothness''
+assumption. Specifically, given the topic vector of a correctly answered
+question, other correctly answered questions also tend to have similar topic
+vectors...
+
+\textbf{JRM NOTE 1: need to think about these results more; stopping here
+temporarily to back up progress...}
+
+\textbf{JRM NOTE 2: consider moving ``estimating held-out conceptual
+knowledge'' from methods to here.}
+
+Knowledge estimates need not be limited to the content of the lectures. As
+illustrated in Figure~\ref{fig:knowledge-maps}, our general approach to
+estimating knowledge from a small number of quiz questions may be applied to
+\textit{any} content, given its text embedding coordinate. To visualize how
+knowledge ``spreads'' through text embedding space to content beyond the
+lectures participants watched, we first fit a new topic model to the lectures'
+sliding windows with $k = 100$ topics. We hoped that increasing the number of
+topics from 15 to 100 might help us to generalize the knowledge predictions.
+(Aside from increasing the number of topics from 15 to 100, all other
+procedures and model parameters were carried over from the preceding analyses.)
+
 \begin{figure}[tp]
@@
     \label{fig:knowledge-maps}
-    \end{figure}
-
-\begin{figure}[tp]
-    \centering
-    \includegraphics[width=\textwidth]{figs/held-out-question-analyses}
-
-    \caption{\textbf{Estimating knowledge at the embedding coordinates of
-    held-out questions.} \textbf{Top panels.} Separately for each quiz (panel
-    column), we plot the average correlations between the topic vectors of
-    held-out correctly (blue) and incorrectly (red) answered questions, and the
-    topic vectors for the $n$ closest remaining correctly or incorrectly
-    answered questions, respectively. For details, see \textit{Testing the
-    ``smoothness'' of knowledge}. \textbf{Bottom panels.} Separately for each
-    quiz (panel column), we plot the distributions of predicted knowledge at
-    the embedding coordinates of each held out correctly (blue) or incorrectly
-    (red) answered question. The $t$-tests reported in each panel are between
-    the distributions of estimated knowledge at the coordinates of correctly
-    versus incorrectly answered held-out questions. For details, see
-    \textit{Estimating held-out conceptual knowledge}.}
-
-    \label{fig:predictions}
     \end{figure}
@@
 
-\subsubsection*{Testing the ``smoothness'' of knowledge}
-
-A core assumption of our modeling framework is that knowledge is ``smooth''
-such that knowing about one concept implies knowledge about other related
-concepts (i.e., concepts that are nearby in text embedding space). Conversely,
-\textit{not} knowing about a given concept implies \textit{less} knowledge
-about other related concepts. We characterized how estimated knowledge (and
-lack of knowledge) fell off with distance in the text embedding space
-(Fig.~\ref{fig:predictions}, top panels).
-
-For each participant, for each quiz, for each of $c$ correctly answered
-question $q$ in turn, we sorted all of the other correctly answered questions
-in descending order of their topic vectors' correlations with $q$'s topic
-vector. We repeated this for all correctly answered questions to obtain a $c
-\times (c - 1)$ matrix of correlations, where the rows corresponded to held-out
-questions and the columns corresponded to the most similar (leftmost column),
-second most similar (second column), other correctly answered questions. Note
-that each correlation for each pair of questions ($a$ and $b$) appears exactly
-twice in this matrix: once when $a$ is the held-out question, and once when $b$
-is the held-out question. We applied the Fisher $z$-transformation to these
-correlations, averaged down the rows, and then applied the inverse Fisher
-$z$-transformation to obtain a $1 \times (c - 1)$ array of average correlations
-for the participant. We repeated this process across all $n$ participants,
-yielding an $n \times 14$ matrix (15 is the maximum number of questions that
-could have been answered correctly on any single 15-question quiz, so at most
-14 correctly answered questions could be compared to a held-out correctly
-answered question). Note that some of the entries, for some of the
-participants, were empty (e.g., if a given participant answered at least one
-question incorrectly, they would never have 14 other correctly answered
-questions to compare to a held-out correctly answered question). If a
-participant answered \textit{no} questions correctly on a given quiz, their
-entire row would be empty.
-
-The blue ribbon plots in the top panels of Figure~\ref{fig:predictions} display
-the mean (across participants) and bootstrap-estimated 95\% confidence
-intervals of these matrices (i.e., one per quiz, each plotted in a separate
-panel). We repeated the same process for \textit{incorrectly} answered
-questions (i.e., comparing held-out incorrectly answered questions to other
-incorrectly answered questions from the same quiz, for each participant in
-turn) to obtain the red ribbon plots in the top panels of
-Figure~\ref{fig:predictions}.
-
 \subsubsection*{Estimating held-out conceptual knowledge}

### 2023-01-25 code/khan_helpers/khan_helpers/__init__.py
function to set plotting style on import

@@ -1,10 +1,10 @@
 from pathlib import Path
 
-import matplotlib as mpl
 from IPython.display import display, Markdown
 
 from .experiment import Experiment
 from .participant import Participant
+from .functions import set_figure_style
 
 
 version_info = (0, 0, 1)
@@ -29,5 +29,4 @@ try:
 except NameError:
     pass
 
-# embed text in PDFs for illustrator
-mpl.rcParams['pdf.fonttype'] = 42
+set_figure_style()

### 2023-01-25 code/khan_helpers/khan_helpers/constants.py

@@ -4,11 +4,13 @@ from nltk.corpus import stopwords
 
 
 DATA_DIR = Path('/mnt/data')
-RAW_DIR = DATA_DIR.joinpath('raw')
-PARTICIPANTS_DIR = DATA_DIR.joinpath('participants')
-TRAJS_DIR = DATA_DIR.joinpath('trajectories')
 EMBS_DIR = DATA_DIR.joinpath('embeddings')
+FONTS_DIR = DATA_DIR.joinpath('fonts')
 MODELS_DIR = DATA_DIR.joinpath('models')
+PARTICIPANTS_DIR = DATA_DIR.joinpath('participants')
+RAW_DIR = DATA_DIR.joinpath('raw')
+TRAJS_DIR = DATA_DIR.joinpath('trajectories')
+
 FIG_DIR = Path('/mnt/paper/figs/source/')
 
 # number of timestamped lines in lecture transcript sliding windows

### 2023-01-25 code/khan_helpers/khan_helpers/functions.py

@@ -14,13 +14,14 @@ import numpy as np
 import pandas as pd
 from IPython.display import display, HTML
 from IPython.core.oinspect import pylight
+from matplotlib import font_manager
 from nltk import pos_tag
 from nltk.corpus import wordnet
 from nltk.stem import WordNetLemmatizer
 from scipy.interpolate import interp1d
 from scipy.spatial.distance import cdist
 
-from .constants import LECTURE_WSIZE, STOP_WORDS
+from .constants import FONTS_DIR, LECTURE_WSIZE, STOP_WORDS
 
 
 def _ts_to_sec(ts):
@@ -637,6 +638,23 @@ def reconstruct_trace(lecture, questions, accuracy):
     b = wz[:, acc].sum(axis=1)
     # divide weight from correct answers by total possible weight
     return b / a
+
+
+def set_figure_style():
+    # embed text in PDFs for illustrator
+    plt.rcParams['pdf.fonttype'] = 42
+
+    # use Myriad Pro font, if available
+    if FONTS_DIR.is_dir() and next(FONTS_DIR.iterdir(), None) is not None:
+        myriad_pro_fonts = [f for f in font_manager.fontManager.ttflist
+                            if f.name == 'Myriad Pro']
+        if len(myriad_pro_fonts) == 0:
+            for font_file in font_manager.findSystemFonts(fontpaths=[FONTS_DIR]):
+                font_manager.fontManager.addfont(font_file)
+
+        plt.rcParams['font.family'] = 'sans-serif'
+        plt.rcParams['font.sans-serif'] = (['Myriad Pro']
+                                           + plt.rcParams['font.sans-serif'])
 
 
 def show_source(obj):

### 2023-01-26 paper/main.tex

@@
 
-A core assumption of our modeling framework is that knowledge is ``smooth''
-such that knowing about one concept implies knowledge about other related
-concepts (i.e., concepts that are nearby in text embedding space). Conversely,
-\textit{not} knowing about a given concept implies \textit{less} knowledge
-about other related concepts. We characterized how estimated knowledge (and
-lack of knowledge) fell off with distance in the text embedding space
-(Fig.~\ref{fig:predictions}, top panels).
+If we are able to accurately estimate a participant's knowledge about the
+content tested by a given question, the estimated knowledge should have some
+predictive information about whether the participant is likely ot answer the
+question correctly or incorrectly. For each question in turn, for each
+participant, we used Equation~\ref{eqn:prop} to estimate (using all
+\textit{other} questions from the same quiz, from the same participant) the
+participant's knowledge at the held-out question's embedding coordinate. For
+each quiz, we aggregated these estimates into two distributions: one for the
+estimated knowledge at the coordinates of each \textit{correctly} answered
+question, and another for the estimated knowledge at the coordinates of each
+\textit{incorrectly} answered question (Fig.~\ref{fig:predictions}). We then
+used independent samples $t$-tests to compare the means of these distributions
+of estimated knowledge.
 
@@
     \caption{\textbf{Estimating knowledge at the embedding coordinates of
-    held-out questions.} \textbf{Top panels.} Separately for each quiz (panel
-    column), we plot the average correlations between the topic vectors of
-    held-out correctly (blue) and incorrectly (red) answered questions, and the
-    topic vectors for the $n$ closest remaining correctly or incorrectly
-    answered questions, respectively. For details, see \textit{Testing the
-    ``smoothness'' of knowledge}. \textbf{Bottom panels.} Separately for each
-    quiz (panel column), we plot the distributions of predicted knowledge at
-    the embedding coordinates of each held out correctly (blue) or incorrectly
-    (red) answered question. The $t$-tests reported in each panel are between
-    the distributions of estimated knowledge at the coordinates of correctly
-    versus incorrectly answered held-out questions. For details, see
-    \textit{Estimating held-out conceptual knowledge}.}
+    held-out questions.} Separately for each quiz (panel), we plot the
+    distributions of predicted knowledge at the embedding coordinates of each
+    held out correctly (blue) or incorrectly (red) answered question. The
+    $t$-tests reported in each panel are between the distributions of estimated
+    knowledge at the coordinates of correctly versus incorrectly answered
+    held-out questions.}
 
@@
 
-For each participant, for each quiz, for each of $c$ correctly answered
-question $q$ in turn, we sorted all of the other correctly answered questions
-in descending order of their topic vectors' correlations with $q$'s topic
-vector. We repeated this for all correctly answered questions to obtain a $c
-\times (c - 1)$ matrix of correlations, where the rows corresponded to held-out
-questions and the columns corresponded to the most similar (leftmost column),
-second most similar (second column), other correctly answered questions. Each
-correlation for each pair of questions ($a$ and $b$) appears exactly twice in
-this matrix: once when $a$ is the held-out question, and once when $b$ is the
-held-out question. We applied the Fisher $z$-transformation to these
-correlations, averaged down the rows, and then applied the inverse Fisher
-$z$-transformation to obtain a $1 \times (c - 1)$ array of average correlations
-for the participant. We repeated this process across all $n$ participants,
-yielding an $n \times 14$ matrix (15 is the maximum number of questions that
-could have been answered correctly on any single 15-question quiz, so at most
-14 correctly answered questions could be compared to a held-out correctly
-answered question). Note that some of the entries, for some of the
-participants, were empty (e.g., if a given participant answered at least one
-question incorrectly, they would never have 14 other correctly answered
-questions to compare to a held-out correctly answered question). If a
-participant answered \textit{no} questions correctly on a given quiz, their
-entire row would be empty.
-
-The blue ribbon plots in the top panels of Figure~\ref{fig:predictions} display
-the mean (across participants) and bootstrap-estimated 95\% confidence
-intervals of these matrices (i.e., one per quiz, each plotted in a separate
-panel). We repeated the same process for \textit{incorrectly} answered
-questions (i.e., comparing held-out incorrectly answered questions to other
-incorrectly answered questions from the same quiz, for each participant in
-turn) to obtain the red ribbon plots in the top panels of
-Figure~\ref{fig:predictions}.
-
-The correlation plots for both curves, in all three top panels of
-Figure~\ref{fig:predictions}, confirm one aspect of our ``smoothness''
-assumption. Specifically, given the topic vector of a correctly answered
-question, other correctly answered questions also tend to have similar topic
-vectors...
-
-\textbf{JRM NOTE 1: need to think about these results more; stopping here
-temporarily to back up progress...}
-
-\textbf{JRM NOTE 2: consider moving ``estimating held-out conceptual
-knowledge'' from methods to here.}
+For the initial quizzes participants took (prior to watching either lecture),
+participants' estimated knowledge tended to be low overall, and relatively
+unstructured (Fig.~\ref{fig:predictions}, left panel). When we held out
+individual questions and estimated their knowledge at the held-out questions'
+embedding coordinates, we found no reliable differences in the estimates when
+the held-out question had been correctly versus incorrectly answered ($t(633) =
+0.577, p = 0.564$). After watching the first video, estimated knowledge for
+held-out correctly answered questions (from the second quiz;
+Fig.~\ref{fig:predictions}, middle panel) exhibited a positive shift relative
+to held-out incorrectly answered questions ($t(633) = 3.961, p < 0.001$). After
+watching the second video, estimated knowledge (from the third quiz;
+Fig.~\ref{fig:predictions}, right panel) for \textit{all} questions exhibited a
+positive shift. However, the increase in estimated knowledge for held-out
+correctly answered questions was larger than for held-out incorrectly answered
+questions ($t(628) = 2.045, p = 0.041$).
 
@@
 procedures and model parameters were carried over from the preceding analyses.)
+We resampled each lecture's topic trajectory to 1~Hz and also projected each
+question into the same 100-dimensional topic space.
 
@@
     \end{figure}
+
+We projected the resulting 100-dimensional topic vectors (for each second of
+video and for each question) into a shared 2-dimensional space (see
+\textit{Creating knowledge and learning map visualizations}). Next, we sampled
+points evenly from a $100 \times 100$ grid of coordinates that evenly tiled a
+rectangle enclosing the 2D projections of the video trajectories and questions.
+We used Equation~\ref{eqn:rbf-knowledge} to estimate participants' knowledge at
+each of these 10K sampled locations, and we averaged these estimates across
+participants to obtain an estimated average \textit{knowledge map}
+(Fig.~\ref{fig:knowledge-maps}). Intuitively, the knowledge map constructed
+from a given quiz's responses provides a visualization of how ``much''
+participants know about any content expressible by the fitted model.
+
+Several features of the resulting knowledge maps are worth noting. The average
+knowledge map estimated from Quiz 1 responses (Fig.~\ref{fig:knowledge-maps},
+leftmost map) shows that participants tended to have relatively little
+knowledge about any parts of the text embedding space (i.e., the shading is
+relatively dark everywhere). The knowledge map estimated from Quiz 2 responses
+shows a marked increase in knowledge on the left side of the map (around
+roughly the same range of coordinates covered by the \textit{Four Fundamental
+Forces} lecture, indicated by the dotted blue line). In other words,
+participants' estimated increase in knowledge is localized to conceptual
+content that is nearby (i.e., related to) the content from the lecture they
+watched prior to taking Quiz 2. This localization is non-trivial: the knowledge
+estimates are informed only by the embedded coordinates of the \textit{quiz
+questions}, not by the embeddings of either lecture. Finally, the knowledge map
+estimated from Quiz 3 responses shows a second increase in knowledge, localized
+to the region surrounding the embedding of the \textit{Birth of Stars} lecture
+participants watched prior to taken Quiz 3.
+
+Another way of visualizing these content-specific increases in knowledge
+(apparently driven by watching each lecture) is displayed in
+Figure~\ref{fig:knowledge-maps}B. Taking the point-by-point difference between
+the knowledge maps estimated from responses to a successive pair of quizzes
+yields a \textit{learning map} that describes the \textit{change} in knowledge
+estimates from one quiz to the next. These learning maps highlight that the
+estimated knowledge increases we observed across maps were specific to the
+regions around the embeddings of each lecture in turn.
+
+Because the 2D projection we used to construct the knowledge and learning maps
+is (partially) invertable, we may gain additional insights into the estimates
+by reconstructing the original high-dimensional topic vectors for any point(s)
+in the maps we are interested in. For example, this could serve as a useful
+tool for an instructor looking to better understand which content areas a
+student (or a group of students) knows well (or poorly). As a demonstration, we
+show the top-weighted words from the blends of topics reconstructed from three
+locations on the maps (Fig.~\ref{fig:knowledge-maps}C): one point near the
+\textit{Four Fundamental Forces} embedding (yellow); a second point near the
+\textit{Birth of Stars} embedding (orange), and a third point somewhere in
+between the two lectures' embeddings (pink). As shown in the word clouds in the
+Panel, the top-weighted words at the coordinate near the \textit{Four
+Fundamental Forces} embedding also tended to be weighted heavily by the topics
+expressed in that lecture. Similarly, the top-weighted words at the coordinate
+near the \textit{Birth of Stars} embedding tended to be weighted most heavily
+by the topics expressed in \textit{that} lecture. And the top-weighted words at
+the coordinate between the two lectures' embeddings show a roughly even mix of
+words most strongly associated with each lecture.
 
@@
 
-\subsubsection*{Estimating held-out conceptual knowledge}
-
-If we are able to accurately estimate a participant's knowledge about the
-content tested by a given question, the estimated knowledge should have some
-predictive information about whether the participant is likely ot answer the
-question correctly or incorrectly. For each question in turn, for each
-participant, we used Equation~\ref{eqn:prop} to estimate (using all
-\textit{other} questions from the same quiz, from the same participant) the
-participant's knowledge at the held-out question's embedding coordinate. For
-each quiz, we aggregated these estimates into two distributions: one for the
-estimated knowledge at the coordinates of each \textit{correctly} answered
-question, and anotehr for the estimated knowledge at the coordinates of each
-\textit{incorrectly} answered question (Fig.~\ref{fig:predictions}, bottom
-panels). We then used independent samples $t$-tests to compare the means of
-these distributions of estimated knowledge.
-
 \bibliographystyle{apa}

### 2023-01-26 paper/main.tex
added stats for knowledge estimates, recompiled

@@
 the \textit{Four Fundamental Forces} was substantially higher on Quiz 2 versus
-Quiz 1 ($t(XX) = XX, p = XX$) and on Quiz 3 versus Quiz 1 ($t(XX) = XX, p =
-XX$). We found no reliable differences in estimated knowledge about that
-lecture's content on Quiz 2 versus 3 ($t(XX) = XX, p = XX$). Similarly, we
+Quiz 1 ($t(49) = 8.764, p < 0.001$) and on Quiz 3 versus Quiz 1 ($t(49) = 10.519, p <
+0.001$). We found no reliable differences in estimated knowledge about that
+lecture's content on Quiz 2 versus 3 ($t(49) = 0.160, p = 0.874$). Similarly, we
 hypothesized (and subsequently confirmed) that participants should show more
@@
 knowledge about the \textit{Birth of Stars} lecture content on Quizzes 1 versus
-2 ($t(XX) = XX, p = XX$), but the estimated knowledge was substantially higher
-on Quiz 3 versus 2 ($t(XX) = XX, p = XX$) and Quiz 3 versus 1 ($t(XX) = XX, p =
-XX$).
+2 ($t(49) = 1.013, p = 0.316$), but the estimated knowledge was substantially higher
+on Quiz 3 versus 2 ($t(49) = 10.561, p < 0.001$) and Quiz 3 versus 1 ($t(49) = 8.969, p <
+0.001$).
 
@@
     \centering
-    \includegraphics[width=\textwidth]{figs/held-out-question-analyses}
+    \includegraphics[width=\textwidth]{figs/held-out-question-analysis}
 

### 2023-01-26 paper/main.tex
flattened transparency in Fig 1, lots of minor wording tweaks, added a topic comparison figure + associated text to the results section

@@
 
-\title{Geometric models reveal the hidden structure of conceptual knowledge}
+\title{Text embedding models reveal high resolution insights into conceptual
+knowledge from short multiple choice quizzes}
 
@@
 representation space, where nearby coordinates reflect similar or related
-concepts. We tested our approach using behavioral data collected from a group
-of college students. In the experiment, we asked the participants to answer
-sets of quiz questions interleaved between watching two course videos from the
-Khan Academy platform. We applied our framework to the videos' transcripts, and
-to text of the quiz questions, to quantify the content of each moment of video
-and each quiz question. We used these embeddings, along with participants' quiz
-responses, to track how the learners' knowledge changed after watching each
-video. Our findings show how a limited set of quiz questions may be used to
-construct rich and meaningful representations of what each learner knows, and
-how their knowledge changes over time as they learn.
+concepts. We test our approach using behavioral data collected from a group of
+college students. In the experiment, we ask the participants to answer small
+sets of multiple choice quiz questions interleaved between watching two course
+videos from the Khan Academy platform. We applied our framework to the videos'
+transcripts, and to text of the quiz questions, to quantify the content of each
+moment of video and each quiz question. We used these embeddings, along with
+participants' quiz responses, to track how the learners' knowledge changed
+after watching each video. Our findings show how a small set of quiz questions
+may be used to obtain rich and meaningful high resolution insights into what
+each learner knows, and how their knowledge changes over time as they learn.
 
@@
 
-Suppose that a teacher had access to a complete ``map'' of everything a student
-knew. Defining what such a map might even look like, let alone how it might be
-constructed or filled in, is itself a non-trivial problem. But if a teacher
-\textit{were} to gain access to such a map, how might that change their ability
-to teach the student? Perhaps they might start by checking how well the student
-knew the to-be-learned information already, or how much they knew about related
-concepts. For some students, they could potentially optimize their teaching
-efforts to maximize efficiency by focusing primarily on not-yet-known content.
-For other students (or other content areas), it might be more effective to
-optimize for direct connections between already-known content and any new
-material. Observing how the student's knowledge was changing over time, in
-response to their training, could also help to guide the teacher.
+Suppose that a teacher had access to a complete ``map'' of everything their
+student knew. Defining what such a map might even look like, let alone how it
+might be constructed or filled in, is itself a non-trivial problem. But if a
+teacher \textit{were} to gain access to such a map, how might that change their
+ability to teach the student? Perhaps they might start by checking how well the
+student knew the to-be-learned information already, or how much they knew about
+related concepts. For some students, they could potentially optimize their
+teaching efforts to maximize efficiency by focusing primarily on not-yet-known
+content. For other students (or other content areas), it might be more
+effective to optimize for direct connections between already-known content and
+any new material. Observing how the student's knowledge was changing over time,
+in response to their training, could also help to guide the teacher.
 
@@
 extent to which each concept is currently known and (b) a \textit{learning map}
-that describes the extent to which each concept could be learned. Each location
-on these maps represents a single concept, and the geometries are defined such
-that related concepts are located nearby in space. We use this framework to
-analyze and interpret behavioral data collected from an experiment that has
-participants watch and answer conceptual questions about a series of recorded
-course lectures.
+that describes changes in knowledge over time. Each location on these maps
+represents a single concept, and the maps' geometries are defined such that
+related concepts are located nearby in space. We use this framework to analyze
+and interpret behavioral data collected from an experiment that has
+participants watch and answer multiple choice questions about a series of
+recorded course lectures.
 
@@
 
-We asked our participants to answer questions from several multiple choice
-quizzes and watch two lecture videos from the \textit{Khan Academy} platform
-(Fig.~\ref{fig:experiment}). One lecture video, entitled \textit{Four
-Fundamental Forces}, was about the four fundamental forces in physics: gravity,
-strong and weak interactions, and electromagnetism. The second lecture video,
-entitled \textit{Birth of Stars}, provides an overview of our current
-understanding of how stars form. We selected both lessons to be (a) accessible
-to a broad audience, e.g., by minimizing prerequisite knowledge, (b) largely
-independent of each other, e.g., so that the two videos focused on different
-material and did not depend on each other, and (c) related to each other, e.g.,
-so that both videos contained at least \textit{some} similar or overlapping
-content. The two videos we selected are introductory, about different primary
-concepts, but also touch on ``physics'' and ``astronomy'' themes. We also wrote
-a set of multiple choice quiz questions that would enable us to test
-participants' knoweldge about each individual video and about related content
-not specifically presented in either video (Tab.~\questions). Participants
-answered questions randomly drawn from each content area (lecture 1, lecture 2,
-and general physics knowledge) across each of three quizzes. Quiz 1 was
-intended to assessed participants' knowledge before training; quiz 2 assessed
-knowledge after watching the Four Fundamental Forces video (i.e., lecture 1);
-and quiz 3 assessed knowledge after watching the Birth of Stars video (i.e.,
-lecture 2).
-
 \begin{figure}[tp]
@@
 
+We asked our participants to answer questions from several multiple choice
+quizzes and watch two lecture videos from the \textit{Khan Academy} platform
+(Fig.~\ref{fig:experiment}). One lecture video, entitled \textit{Four
+Fundamental Forces}, was about the four fundamental forces in physics: gravity,
+strong and weak interactions, and electromagnetism. The second lecture video,
+entitled \textit{Birth of Stars}, provides an overview of our current
+understanding of how stars form. We selected both lessons to be (a) accessible
+to a broad audience, e.g., by minimizing prerequisite knowledge, (b) largely
+independent of each other, e.g., so that the two videos focused on different
+material and did not depend on each other, and (c) related to each other, e.g.,
+so that both videos contained at least \textit{some} similar or overlapping
+content. The two videos we selected are introductory (i.e., minimizing specific
+prerequisite knowledge), and are about different primary concepts, but they
+both also touch on ``physics'' and ``astronomy'' themes. We also wrote a set of
+multiple choice quiz questions that would enable us to test participants'
+knoweldge about each individual video and about related content not
+specifically presented in either video (Tab.~\questions). Participants answered
+questions randomly drawn from each content area (lecture 1, lecture 2, and
+general physics knowledge) across each of three quizzes. Quiz 1 was intended to
+assessed participants' knowledge before training; quiz 2 assessed knowledge
+after watching the \textit{Four Fundamental Forces} video (i.e., lecture 1);
+and quiz 3 assessed knowledge after watching the \textit{Birth of Stars} video
+(i.e., lecture 2).
+
 We trained a text embedding model using sliding windows of text from the two
@@
 videos' transcripts) to embed the text of each question in our pool. This
-yielded, for each second of each video, and for each question, a single topic
-vector-- i.e., a coordinate in a text embedding space
+yielded, for each second of each video, and for each question, a single
+15-dimensional topic vector---i.e., a coordinate in a text embedding space
 (Fig.~\ref{fig:sliding-windows}). Intuitively, each dimension of the embedding
@@
     \centering
+    \includegraphics[width=0.6\textwidth]{figs/active-topics}
+
+\caption{\textbf{Lecture and question topic overlap.} The bar plots display the
+variability in topic weights across lecture timepoints (top panels) and
+questions (bottom panels); colors denote topics. The top-weighted words from
+the most ``expressive'' (i.e., variable across observations) topics from each
+lecture are displayed in the upper right (orange: topic 2; yellow-green: topic
+4). The top-weighted words from the full set of topics may be found in
+Table~\topics.}
+
+    \label{fig:topics}
+\end{figure}
+
+Given that we trained the text embedding model using the video transcripts, we
+wondered whether the questions that were (ostensibly, by design) ``about'' the
+content of each lecture would ``match up'' correctly with the lectures. In
+other words, we hoped that the text embeddings would capture something about
+the deeper conceptual content of the lectures, beyond surface details such as
+exact wording choices. If so, when we embed \textit{new} text outside of the
+model's training set, we should see a correspondance between the embeddings of
+the training data (i.e., snippets of text from the lectures' transcripts) and
+other text that reflects related concepts (e.g., questions \textit{about} each
+lecture). Further, although the content from any given moment from a lecture
+might stray from the average content (across all timepoints), we hoped that
+\textit{variability} in each topic's expression over timepoints within a
+lecture would match up with the variability in topic expressions for questions
+about that lecture. Intuitively, the variability in the expression of a given
+topic relates to how much ``information''~\citep{Fish22} the lecture (or
+questions) reflect about that topic. When we compared the variability in topic
+weights across each lecture's timepoints with the variability in topic weights
+across each question set, we found a strong correspondence
+(Fig.~|ref{fig:topics}). The most variable topics from the \textit{Four
+Fundamental Forces} lecture, and questions about that lecture, are 2, 3, 8, 12,
+13, 14, and 15. The most variable topics from the \textbf{Birth of Stars}
+lecture, and questions about that lecture, are 1, 4, 5, 6, and 7. This strong
+overlap between the lectures and questions specifically about each lecture
+indicates that the topic model captures some of the underlying conceptual
+content.
+
+\begin{figure}[tp]
+    \centering
     \includegraphics[width=\textwidth]{figs/lecture-question-similarity}
@@
     question?} Each panel displays timeseries plots showing how each question's
-    topic vector correlates with each video timepoint's topic vector. The left
-    panel displays these correlations for the \textit{Four Fundamental Forces}
-    lecture and associated questions, and the right panels displays these
-    correlations for the \textit{Birth of Stars} lecture and associated
-    questions. The colors denote question identities. The diamonds in each
-    panel denote the moment of peak correlation between the indicated
-    questions, in the indicated lectures. The associated questions' text, and
-    snippets of the lectures' transcripts in the best-matching sliding windows,
-    are displayed at the bottom of the figure.}
+    topic vector correlates with each video timepoint's topic vector (Panel
+    \textbf{A.}: correlations for the \textit{Four Fundamental Forces} lecture
+    and associated questions; Panel \textbf{B.}: correlations for the
+    \textit{Birth of Stars} lecture and associated questions). The colors denote
+    question identities. The diamonds in each panel denote the moment of peak
+    correlation between the indicated questions, in the indicated lectures. The
+    associated questions' text, and snippets of the lectures' transcripts in
+    the best-matching sliding windows, are displayed at the bottom of the
+    figure.}
 
@@
 
-Although a single lecture may be organized a single broad theme at a coarse
-scale, at a finer scale each moment of a lecture typically covers a narrower
-range of content. We wondered whether a text embedding model trained on the
-lectures' transcripts might capture some of this finer scale content. For
-example, if a particular question asks about the content from one small part of
-a lecture, we wondered whether our text embedding model could be used to
-automatically identify the ``matching'' moment(s) in the lecture. When we
+Although a single lecture may be organized around a single broad theme at a
+coarse scale, at a finer scale each moment of a lecture typically covers a
+narrower range of content. We wondered whether a text embedding model trained
+on the lectures' transcripts might capture some of this finer scale content.
+For example, if a particular question asks about the content from one small
+part of a lecture, we wondered whether our text embedding model could be used
+to automatically identify the ``matching'' moment(s) in the lecture. When we
 correlated each question's topic vector with the topic vectors for each second
@@
 specific (Fig.~\ref{fig:question-correlations}). In particular, most questions'
-topic vectors were maximally correlated with a well-defined range of timepoints
-from their corresponding lectures, and the correlations fell off sharply
-outside of that range. We also examined the best-matching intervals for each
-question qualitatively by comparing the text of the question to the text of the
-most-correlated parts of the lectures. Despite that the questions were excluded
-from the text embedding model's training set, in general we found a close
+topic vectors were maximally correlated with a well-defined (and relatively
+narrow) range of timepoints from their corresponding lectures, and the
+correlations fell off sharply outside of that range. We also examined the
+best-matching intervals for each question qualitatively by comparing the text
+of the question to the text of the most-correlated parts of the lectures.
+Despite that the questions were excluded from the text embedding model's
+training set, in general we found (through manual inspection) a close
 correspondence between the conceptual content that each question covered and
@@
 
-The ability to quantify how much each question is ``asking about'' each moment
-of the lectures could enable high-resolution insights into participants'
-knowledge. Traditional approaches to estimating how much a student ``knows''
-about the content of a given lecture entail computing the proportion of
-correctly answered questions. But if two students receive identical scores on
-an exam, might our modeling framework help us to gain more naunced insights
-into the \textit{specific} content that each student has mastered (or failed to
-master)? For example, a student who misses three questions that were all about
-the same concept (e.g., concept $A$) will have gotten the same
-\textit{proportion} of questions correct as another student who missed three
-questions about three \textit{different} concepts (e.g., $A$, $B$, and $C$).
-But if we wanted to fill in the ``gaps'' in the two students' understandings,
-we might do well to focus on concept $A$ for the first student, but to also add
-in materials pertaining to concepts $B$ and $C$ for the second student.
+The ability to quantify how much each question is ``asking about'' the content
+from each moment of the lectures could enable high-resolution insights into
+participants' knowledge. Traditional approaches to estimating how much a
+student ``knows'' about the content of a given lecture entail computing the
+proportion of correctly answered questions. But if two students receive
+identical scores on an exam, might our modeling framework help us to gain more
+naunced insights into the \textit{specific} content that each student has
+mastered (or failed to master)? For example, a student who misses three
+questions that were all about the same concept (e.g., concept $A$) will have
+gotten the same \textit{proportion} of questions correct as another student who
+missed three questions about three \textit{different} concepts (e.g., $A$, $B$,
+and $C$). But if we wanted to fill in the ``gaps'' in the two students'
+understandings, we might do well to focus on concept $A$ for the first student,
+but to also add in materials pertaining to concepts $B$ and $C$ for the second
+student.
 
@@
 timecourse describing how much ``knowledge'' the participant has about any part
-of the lecture. As shown in Figures~\ref{fig:knowledge-timeseries}A and C), we
-can also apply this approach separately for the questions from each quiz the
+of the lecture. As shown in Figure~\ref{fig:knowledge-timeseries}, we can also
+apply this approach separately for the questions from each quiz the
 participants took throughout the experiment. From just 13 questions per quiz,
@@
 content tested by a given question, the estimated knowledge should have some
-predictive information about whether the participant is likely ot answer the
+predictive information about whether the participant is likely to answer the
 question correctly or incorrectly. For each question in turn, for each
@@
 procedures and model parameters were carried over from the preceding analyses.)
-We resampled each lecture's topic trajectory to 1~Hz and also projected each
-question into the same 100-dimensional topic space.
+As in our other analyses, we resampled each lecture's topic trajectory to 1~Hz
+and also projected each question into a shared text embedding space.
 
@@
     the corresponding coordinates in the indicated \textit{pair} of knowledge
-    maps-- i.e., how much the estimated knowledge ``changed'' across the two
+    maps---i.e., how much the estimated knowledge ``changed'' across the two
     quizzes. Each map reflects an average across all participants. For
@@
 points evenly from a $100 \times 100$ grid of coordinates that evenly tiled a
-rectangle enclosing the 2D projections of the video trajectories and questions.
-We used Equation~\ref{eqn:rbf-knowledge} to estimate participants' knowledge at
-each of these 10K sampled locations, and we averaged these estimates across
+rectangle enclosing the 2D projections of the videos and questions. We used
+Equation~\ref{eqn:rbf-knowledge} to estimate participants' knowledge at each of
+these 10K sampled locations, and we averaged these estimates across
 participants to obtain an estimated average \textit{knowledge map}
@@
 from a given quiz's responses provides a visualization of how ``much''
-participants know about any content expressible by the fitted model.
+participants know about any content expressible by the fitted text embedding
+model.
 
@@
 estimates are informed only by the embedded coordinates of the \textit{quiz
-questions}, not by the embeddings of either lecture. Finally, the knowledge map
-estimated from Quiz 3 responses shows a second increase in knowledge, localized
-to the region surrounding the embedding of the \textit{Birth of Stars} lecture
-participants watched prior to taken Quiz 3.
+questions}, not by the embeddings of either lecture
+(Eqn.~\ref{eqn:rbf-knowledge}). Finally, the knowledge map estimated from Quiz
+3 responses shows a second increase in knowledge, localized to the region
+surrounding the embedding of the \textit{Birth of Stars} lecture participants
+watched prior to taking Quiz 3.
 
@@
 show the top-weighted words from the blends of topics reconstructed from three
-locations on the maps (Fig.~\ref{fig:knowledge-maps}C): one point near the
-\textit{Four Fundamental Forces} embedding (yellow); a second point near the
-\textit{Birth of Stars} embedding (orange), and a third point somewhere in
+example locations on the maps (Fig.~\ref{fig:knowledge-maps}C): one point near
+the \textit{Four Fundamental Forces} embedding (yellow); a second point near
+the \textit{Birth of Stars} embedding (orange), and a third point somewhere in
 between the two lectures' embeddings (pink). As shown in the word clouds in the
-Panel, the top-weighted words at the coordinate near the \textit{Four
+Panel, the top-weighted words at the example coordinate near the \textit{Four
 Fundamental Forces} embedding also tended to be weighted heavily by the topics
-expressed in that lecture. Similarly, the top-weighted words at the coordinate
-near the \textit{Birth of Stars} embedding tended to be weighted most heavily
-by the topics expressed in \textit{that} lecture. And the top-weighted words at
-the coordinate between the two lectures' embeddings show a roughly even mix of
-words most strongly associated with each lecture.
+expressed in that lecture. Similarly, the top-weighted words at the example
+coordinate near the \textit{Birth of Stars} embedding tended to be weighted
+most heavily by the topics expressed in \textit{that} lecture. And the
+top-weighted words at the example coordinate between the two lectures'
+embeddings show a roughly even mix of words most strongly associated with each
+lecture.
 
@@
 reported being color blind.  Participants reported having had, on the
-night prior to testing, 2 -- 4 hours of sleep (1 participant), 4 -- 6
-hours of sleep (9 participants), 6 -- 8 hours of sleep (35
+night prior to testing, 2--4 hours of sleep (1 participant), 4--6
+hours of sleep (9 participants), 6--8 hours of sleep (35
 participants), or $8+$ hours of sleep (5 participants). They reported
@@
 
-Particpants reported their undergraduate major(s) as Social Sciences
-(28 participants), Natural sciences (16), Professional (e.g., pre-med
-or pre-law; 8 participants), Mathematics and engineering (7
-participants), Humanities (4 participants), or Undecided (3
-participants).  Note that some participants selected multiple
-categories for their undergraduate major.  We also asked participants
-about the courses they had taken.  In total, 46 participants reported
-having taken at least one Khan academy course in the past or being
-familiar with the Khan academy, and 4 reported not having taken any
-Khan academy courses.  Of the participants who reported having watched
-at least one Khan academy course, 1 participant declined to report the
-number of courses they had watched; 7 participants reported having
-watched 1--2 courses; 11 reported having watched 3--5 courses; 8
-reported having watched 5--10 courses; and 19 reported having watched
-10 or more courses.  We also asked participants about the specific
-courses they had watched, categorized under different subject areas.
-In the ``Mathematics'' area participants reported having watched
-videos on AP Calculus AB (21 participants), Precalculus (17
-participants), Algebra 2 (14 participants), AP Calculus BC (12
-participants), Trigonometry (11 participants), Algebra 1 (10
-participants), Geometry (8 participants), Pre-algebra (7
-participants), Multivariable Calculus (5 participants), Differential
-Equations (5 participants, Statistics and Probability (4
-participants), AP Statistics (2 participants), Linear Algebra (2
-participants), Early Math (1 participant), Arithmetic (1 participant),
-and other videos not listed in our survey (6 participants).  In the ``Science and engineering''
-area participants reported having watched videos on Chemistry, AP
-Chemistry, or Organic Chemstry (21
-participants); Physics, AP Physics I, or AP Physics II (15 participants); Biology, AP
-Biology; or High school Biology (15 participants); Health and Medicine
-(1 participant); or other videos not listed in our survey (20 participants).  We also asked
-participants if they had specifically seen the videos used in our
-experiment.  When we asked about the \textit{Four Fundamental Forces}
-video, 45 participants reported not having watched it before, 1
-participant reported that they were not sure if they had watched it
-before, and 4 participants declined to respond.  When we asked about
-the \textit{Birth of Stars} video, 46 participants reported not having
-watched it before and 4 participants declined to respond.  When we
-asked participants about non-Khan academy online courses, they
-reported having watched or taken courses on Mathematics (15
-participants), Science and engineering (11 participants), Test
-preparation (9 participants), Economics and finance (3 participants),
-Arts and humanities (2 participants), Computing (2 participants), and
-other categories not listed in our survey (18 participants).  Finally,
-we asked participants about in-person courses they had taken in
-different subject areas.  They reported taking courses in Mathematics
-(39 participants), Science and engineering (38 participants), Arts and
-humanities (35 participants), Test preparation (27 participants),
-Economics and finance (26 participants), Computing (15 participants),
-College and careers (7 participants), or other courses not listed in
-our survey (6 participants).
+Particpants reported their undergraduate major(s) as Social Sciences (28
+participants), Natural sciences (16), Professional (e.g., pre-med or pre-law; 8
+participants), Mathematics and engineering (7 participants), Humanities (4
+participants), or Undecided (3 participants). Note that some participants
+selected multiple categories for their undergraduate major. We also asked
+participants about the courses they had taken. In total, 46 participants
+reported having taken at least one Khan academy course in the past or being
+familiar with the Khan academy, and 4 reported not having taken any Khan
+academy courses. Of the participants who reported having watched at least one
+Khan academy course, 1 participant declined to report the number of courses
+they had watched; 7 participants reported having watched 1--2 courses; 11
+reported having watched 3--5 courses; 8 reported having watched 5--10 courses;
+and 19 reported having watched 10 or more courses. We also asked participants
+about the specific courses they had watched, categorized under different
+subject areas. In the ``Mathematics'' area participants reported having watched
+videos on AP Calculus AB (21 participants), Precalculus (17 participants),
+Algebra 2 (14 participants), AP Calculus BC (12 participants), Trigonometry (11
+participants), Algebra 1 (10 participants), Geometry (8 participants),
+Pre-algebra (7 participants), Multivariable Calculus (5 participants),
+Differential Equations (5 participants), Statistics and Probability (4
+participants), AP Statistics (2 participants), Linear Algebra (2 participants),
+Early Math (1 participant), Arithmetic (1 participant), and other videos not
+listed in our survey (6 participants). In the ``Science and engineering'' area
+participants reported having watched videos on Chemistry, AP Chemistry, or
+Organic Chemstry (21 participants); Physics, AP Physics I, or AP Physics II (15
+participants); Biology, AP Biology; or High school Biology (15 participants);
+Health and Medicine (1 participant); or other videos not listed in our survey
+(20 participants). We also asked participants if they had specifically seen the
+videos used in our experiment. When we asked about the \textit{Four Fundamental
+Forces} video, 45 participants reported not having watched it before, 1
+participant reported that they were not sure if they had watched it before, and
+4 participants declined to respond. When we asked about the \textit{Birth of
+Stars} video, 46 participants reported not having watched it before and 4
+participants declined to respond. When we asked participants about non-Khan
+academy online courses, they reported having watched or taken courses on
+Mathematics (15 participants), Science and engineering (11 participants), Test
+preparation (9 participants), Economics and finance (3 participants), Arts and
+humanities (2 participants), Computing (2 participants), and other categories
+not listed in our survey (18 participants). Finally, we asked participants
+about in-person courses they had taken in different subject areas. They
+reported taking courses in Mathematics (39 participants), Science and
+engineering (38 participants), Arts and humanities (35 participants), Test
+preparation (27 participants), Economics and finance (26 participants),
+Computing (15 participants), College and careers (7 participants), or other
+courses not listed in our survey (6 participants).
 
@@
 
-We hand-selected two roughly 10-minute course videos from the Khan Academy
-platform: \textit{The Four Fundamental Forces} (an introduction to gravity,
-electromagnetism, the weak nuclear force, and the strong nuclear force;
-duration: 10 minutes and 29 seconds) and \textit{Birth of Stars} (an
-introduction to how stars are formed; duration: 7 minutes and 57 seconds). We
-hand-wrote 39 multiple choice questions: 15 about the conceptual content of
-\textit{The Four Fundamental Forces}, another 15 about the conceptual content
-of \textit{Birth of Stars}, and 9 other questions that tested for general
-conceptual knowledge about basic physics (covering material that was not
-presented in either video). The full set of questions may be found in
-Table~\questions.
+We hand-selected two course videos from the Khan Academy platform: \textit{Four
+Fundamental Forces} (an introduction to gravity, electromagnetism, the weak
+nuclear force, and the strong nuclear force; duration: 10 minutes and 29
+seconds) and \textit{Birth of Stars} (an introduction to how stars are formed;
+duration: 7 minutes and 57 seconds). We hand-wrote 39 multiple choice
+questions: 15 about the conceptual content of \textit{Four Fundamental Forces},
+another 15 about the conceptual content of \textit{Birth of Stars}, and 9 other
+questions that tested for general conceptual knowledge about basic physics
+(covering material that was not presented in either video). The full set of
+questions may be found in Table~\questions.
 
@@
 Figure~\ref{fig:experiment}. We used the experiment to develop and test our
-computational framework for estimating knowledge and learning maps.
+computational framework for estimating knowledge and learning.
 
@@
 (i.e., the union of all unique words, across all documents, excluding ``stop
-words.''). Conceptually, each topic is intended to give larger weights to set
-of words that appear conceptually related or that tend to co-occur in the same
-documents. After fitting a topic model, each document in the training set, or
-any \textit{new} document that contains at least some of the words in the
-model's vocabulary, may be represented as a $k$-dimensional vector describing
-how much the document (most probably) reflects each topic. (Unless, otherwise
-noted, we used $k = 15$ topics.)
+words.''). Conceptually, each topic is intended to give larger weights to words
+that are conceptually related or that tend to co-occur in the same documents.
+After fitting a topic model, each document in the training set, or any
+\textit{new} document that contains at least some of the words in the model's
+vocabulary, may be represented as a $k$-dimensional vector describing how much
+the document (most probably) reflects each topic. (Unless, otherwise noted, we
+used $k = 15$ topics.)
 
@@
 the text of each question, results in one trajectory per video and one
-embedding coordinate (dot) per question (blue: Four Fundamental Forces; green:
-Birth of Stars; pink: general physics knowledge). Here we have projected the
-15-dimensional embeddings into a 3D space using Uniform Manifold Approximation
-and Projection~\citep[UMAP;][]{McInEtal18a}.}
+embedding coordinate (dot) per question (blue: \textit{Four Fundamental
+Forces}; green: \textit{Birth of Stars}; pink: general physics knowledge). Here
+we have projected the 15-dimensional embeddings into a 3D space using Uniform
+Manifold Approximation and Projection~\citep[UMAP;][]{McInEtal18a}.}
 
@@
 similarity between different documents' topic vectors may be used to
-characterize the similarity in content between the documents.
+characterize the similarity in conceptual content between the documents.
 
@@
 \begin{equation} 
-    \hat{k}(t) = \frac{\sum_{i \in \mathrm{correct}}\mathrm{ncorr}(t, i)}{\sum_{j = 1}^N \mathrm{ncorr}(t, j)},
+    \hat{k}\left(f(t, L)\right) = \frac{\sum_{i \in \mathrm{correct}}\mathrm{ncorr}\left(f(t, L), f(i, Q)\right)}{\sum_{j = 1}^N \mathrm{ncorr}\left(f(t, L), f(j, Q)\right)},
     \label{eqn:prop}
@@
 correlations between any lecture timepoint and question, taken over all
-timepoints and questions across both lectures and all three question sets.
+timepoints and questions across both lectures and all three question sets. We
+also define $f(s, \Omega)$ as the $s$\textsuperscript{th} topic vector from the
+set of topic vectors $\Omega$. Here $t$ indexes the set of lecture topic
+vectors, $L$, and $i$ and $j$ index the topic vectors of questions in the
+quiz's question set, $Q$. Note that ``correct'' denotes the set of indices of
+the questions the participant answered correctly on the given quiz.
 
@@
 enclosing rectangle. We sought to estimate participants' knoweldge (and
-learning-- i.e., changes in knowledge) at each of the resulting 10000
+learning---i.e., changes in knowledge) at each of the resulting 10000
 coordinates.

### 2023-01-26 paper/supplement.tex
flattened transparency in Fig 1, lots of minor wording tweaks, added a topic comparison figure + associated text to the results section

@@
 
-\newcommand{\demo}{1}
+\newcommand{\knowledgeMaps}{5}
 
-\title{\textit{Supplementary materials for}: Geometric models reveal the hidden structure of conceptual knowledge}
+\title{\textit{Supplementary materials for}: Text embedding models reveal high
+resolution insights into conceptual knowledge from short multiple choice
+quizzes}
 
@@
 \newpage
+
+\begin{figure}[tp]
+    \centering
+    \includegraphics[height=0.9\textheight]{figs/individual-knowledge-maps-quiz1}
+
+    \caption{\textbf{Individual participants' knowledge maps estimated from
+    Quiz 1 responses.} Each panel is in the same format as the knowledge maps
+    displayed in the left panel of Figure~\knowledgeMaps A in the main text,
+    but here the maps have been computed separately for each participant.}
+
+    \label{fig:knowledge-maps-q1}
+\end{figure}
+
+\begin{figure}[tp]
+    \centering
+    \includegraphics[height=0.9\textheight]{figs/individual-knowledge-maps-quiz2}
+
+    \caption{\textbf{Individual participants' knowledge maps estimated from
+    Quiz 2 responses.} Each panel is in the same format as the knowledge maps
+    displayed in the middle panel of Figure~\knowledgeMaps A in the main text,
+    but here the maps have been computed separately for each participant.}
+
+    \label{fig:knowledge-maps-q2}
+\end{figure}
+
+\begin{figure}[tp]
+    \centering
+    \includegraphics[height=0.9\textheight]{figs/individual-knowledge-maps-quiz3}
+
+    \caption{\textbf{Individual participants' knowledge maps estimated from
+    Quiz 3 responses.} Each panel is in the same format as the knowledge maps
+    displayed in the right panel of Figure~\knowledgeMaps A in the main text,
+    but here the maps have been computed separately for each participant.}
+
+    \label{fig:knowledge-maps-q3}
+\end{figure}
+
+\begin{figure}[tp]
+    \centering
+    \includegraphics[height=0.9\textheight]{figs/individual-learnings-maps-quiz1-2}
+
+    \caption{\textbf{Individual participants' learning maps estimated from
+    Quiz 1 and 2 responses.} Each panel is in the same format as the learning map
+    displayed in the left panel of Figure~\knowledgeMaps B in the main text,
+    but here the maps have been computed separately for each participant.}
+
+    \label{fig:learning-maps-q1_2}
+\end{figure}
+
+\begin{figure}[tp]
+    \centering
+    \includegraphics[height=0.9\textheight]{figs/individual-learnings-maps-quiz2-3}
+
+    \caption{\textbf{Individual participants' learning maps estimated from
+    Quiz 2 and 3 responses.} Each panel is in the same format as the learning map
+    displayed in the right panel of Figure~\knowledgeMaps B in the main text,
+    but here the maps have been computed separately for each participant.}
+
+    \label{fig:learning-maps-q1_2}
+\end{figure}
+
 \renewcommand{\refname}{Supplementary references}

### 2023-01-26 paper/main.tex
added andy as a co-author (yay!)
checking in a messy and incomplete version of the discussion section...

@@
 
-\author{Paxton C. Fitzpatrick and Jeremy R.
-Manning\textsuperscript{*}\\Dartmouth
-College\\\textsuperscript{*}Corresponding author:
+\author{Paxton C. Fitzpatrick\textsuperscript{1},
+Andrew C. Heusser\textsuperscript{1, 2}, and Jeremy R.
+Manning\textsuperscript{1, *}\\\textsuperscript{1}Dartmouth
+College\\\textsuperscript{2}Akili Interactive\\\textsuperscript{*}Corresponding author:
 jeremy.r.manning@dartmouth.edu}
@@
 
+\textbf{JRM NOTE: add overview of our findings.  Also need (lots of) citations below...}
+
+Teaching, like effective writing and speaking, is fundamentally about empathy.
+Great teachers consider students' interests, backgrounds, and working memory
+capacities, and flexibly optimize their teaching strategies within those
+constraints. In the classroom, empathizing with students also means maintaining
+open lines of communication by fostering an environment in which all students
+feel comfortable speaking up if they have an exciting new idea, or if they are
+having trouble understanding something. In-person instruction also often
+entails dynamic student-teacher and student-student interactions. These
+in-person interactions can provide the instructor with valuable information
+about students' understanding of the course material, beyond what they can
+glean solely from exams or assignments. In turn, this can allow the instructor
+to adapt their teaching approaches on-the-fly according to students' questions
+and behaviors. But what does great teaching look like in asynchronous online
+courses, when the instructor typically prepares course lectures and materials
+without knowing who will ultimately be learning from them? Can the empathetic
+side of teaching be automated and scaled?
+
+The notion of empathy is tightly associated with ``theory of mind'' of other
+individuals. Considering others' unique perspectives, prior experiences,
+knowledge, goals, etc., can help us to more effectively interact and
+communicate. The knowledge and learning maps we estimate in our study
+(Fig.~\ref{fig:knowledge-maps}) hint at one potential form that an automated
+empathetic teacher might take. We imagine that automated content delivery
+systems that \textbf{JRM NOTE: CONTINUE....}
+
+Over the past several years, the global pandemic has forced many educators to
+teach remotely. This change in world circumstances is happening alongside (and
+perhaps accelerating) geometric growth in the availability of high quality
+online courses on platforms such as Khan Academy, Coursera, EdX, and others.
+Continued expansion of the global internet backbone and improvements in
+computing hardware have also facilitated improvements in video streaming,
+enabling videos to be easily downloaded and shared by large segments of the
+world's population. This exciting time for online course instruction provides
+an opportunity to re-evaluate how we, as a global community, educate ourselves
+and each other. For example, we can ask: what makes an effective course or
+training program? Which aspects of teaching might be optimized or automated?
+How and why do learning needs and goals vary across people? How might we lower
+barriers to achieving a high quality education?
+
+Alongside these questions, there is a growing desire to extend existing
+theories beyond the domain of lab testing rooms and into real classrooms. In
+part, this has led to a recent resurgence of ``naturalistic'' or
+``observational'' experimental paradigms that attempt to better reflect more
+ethologically valid phenomena that are more directly relevant to real-world
+situations and behaviors. In turn, this has brought new challenges in data
+analysis and interpretation. A key step towards solving these challenges will
+be to build explicit models of real-world scenarios and how people behave in
+them (e.g., models of how people learn conceptual content from real-world
+courses, as in our current study). A second key step will be to understand
+which sorts of signals derived from behaviors and/or other measurements (e.g.,
+neurophysiological data; \textbf{CITE Hassan/Norman lab stuff, Poeppel lab
+stuff, Para lab stuff, etc.}) might help to inform these models. A third major
+step will be to develop and employ reliable ways of evaluating the complex
+models and data that are a hallmark of naturalistic paradigms.
+
+Ultimately, our work suggests a new line of questions regarding the future of
+education: which aspects of teaching can be optimized and/or automated? The
+social benefits of face-to-face instruction, such as social interactions,
+friendships, and emotional support, cannot (and perhaps should not) be fully
+replaced by an automated computer-based system. Nor can modern computer systems
+experience emotional empathy in the human sense of the word. On the other hand,
+perhaps it is possible to separate out the social aspects of classroom
+instruction from the purely learning-related aspects. Our study shows that text
+embedding models can uncover detailed insights into students' knowledge and how
+it changes over time during learning.  We hope that these advances might help
+pave the way for new ways of teaching or delivering educational content
+that are tailored to individual students' learning needs and goals.
+
 \section*{Materials and methods}

### 2023-01-27 paper/main.tex
backing up progress on discussion section-- mostly added a bunch of references

@@
 
-\textbf{JRM NOTE: add overview of our findings.  Also need (lots of) citations below...}
-
-Teaching, like effective writing and speaking, is fundamentally about empathy.
-Great teachers consider students' interests, backgrounds, and working memory
-capacities, and flexibly optimize their teaching strategies within those
-constraints. In the classroom, empathizing with students also means maintaining
-open lines of communication by fostering an environment in which all students
-feel comfortable speaking up if they have an exciting new idea, or if they are
-having trouble understanding something. In-person instruction also often
+Teaching, like effective writing and speaking, is fundamentally about
+empathy~\citep{AldrEtal22, StojEtal12, MeyeEtal19}. Great teachers consider
+students' interests~\citep{SwarEtal12, Clar10}, backgrounds~\citep{MuijReyn10,
+Rose76, denBEtal10}, and working memory capacities~\citep{Allo12}, and flexibly
+optimize their teaching strategies within those constraints~\citep{GoodEtal07,
+AndeEtal21, John02}. In the classroom, empathizing with students also means
+maintaining open lines of communication~\citep{WulfWulf10} by fostering an
+environment in which all students feel comfortable speaking up if they have an
+exciting new idea, or if they are having trouble understanding
+something~\citep{TurnBrai15, GarrRasm14}. In-person instruction also often
 entails dynamic student-teacher and student-student interactions. These
@@
 about students' understanding of the course material, beyond what they can
-glean solely from exams or assignments. In turn, this can allow the instructor
-to adapt their teaching approaches on-the-fly according to students' questions
-and behaviors. But what does great teaching look like in asynchronous online
-courses, when the instructor typically prepares course lectures and materials
-without knowing who will ultimately be learning from them? Can the empathetic
-side of teaching be automated and scaled?
+glean solely from exams or assignments~\citep{Engl09, vandEtal10c, HallWals02}.
+In turn, this can allow the instructor to adapt their teaching approaches
+on-the-fly according to students' questions and behaviors. But what does great
+teaching look like in asynchronous online courses, when the instructor
+typically prepares course lectures and materials without knowing who will
+ultimately be learning from them? Can the empathetic side of teaching be
+automated and scaled?
 
-The notion of empathy is tightly associated with ``theory of mind'' of other
-individuals. Considering others' unique perspectives, prior experiences,
-knowledge, goals, etc., can help us to more effectively interact and
-communicate. The knowledge and learning maps we estimate in our study
+The notion of empathy also related to ``theory of mind'' of other
+individuals~\citep{GoldWinn12, KansEtal15, Melt11}. Considering others' unique
+perspectives, prior experiences, knowledge, goals, etc., can help us to more
+effectively interact and communicate~\citep{ShaoEtal18, StepBaer06, Ratk18}.
+The knowledge and learning maps we estimate in our study
 (Fig.~\ref{fig:knowledge-maps}) hint at one potential form that an automated
-empathetic teacher might take. We imagine that automated content delivery
-systems that \textbf{JRM NOTE: CONTINUE....}
+``empathetic'' teacher might take. We imagine that automated content delivery
+systems that adapt lessons on the fly according to continually updated
+estimates of what students know and how quickly they are learning different
+conceptual content~\citep[e.g., building on ideas such as ][and
+others]{AndeSkwa86, Half88, Kuma05, WolzEtal88}.
 
@@
 courses, as in our current study). A second key step will be to understand
-which sorts of signals derived from behaviors and/or other measurements (e.g.,
-neurophysiological data; \textbf{CITE Hassan/Norman lab stuff, Poeppel lab
-stuff, Para lab stuff, etc.}) might help to inform these models. A third major
-step will be to develop and employ reliable ways of evaluating the complex
-models and data that are a hallmark of naturalistic paradigms.
+which sorts of signals derived from behaviors and/or other
+measurements~\citep[e.g., neurophysiological data; ][]{NguyEtal22, MeshEtal20,
+PoulEtal17, BeviEtal19, DikkEtal17} might help to inform these models. A third
+major step will be to develop and employ reliable ways of evaluating the
+complex models and data that are a hallmark of naturalistic paradigms.
 

### 2023-01-27 paper/main.tex

@@
 Over the past several years, the global pandemic has forced many educators to
-teach remotely. This change in world circumstances is happening alongside (and
-perhaps accelerating) geometric growth in the availability of high quality
-online courses on platforms such as Khan Academy, Coursera, EdX, and others.
-Continued expansion of the global internet backbone and improvements in
-computing hardware have also facilitated improvements in video streaming,
-enabling videos to be easily downloaded and shared by large segments of the
-world's population. This exciting time for online course instruction provides
-an opportunity to re-evaluate how we, as a global community, educate ourselves
-and each other. For example, we can ask: what makes an effective course or
-training program? Which aspects of teaching might be optimized or automated?
-How and why do learning needs and goals vary across people? How might we lower
-barriers to achieving a high quality education?
+teach remotely~\citep{MoseEtal21, ShimLee20, KawaEtal21, Whal20}. This change
+in world circumstances is happening alongside (and perhaps accelerating)
+geometric growth in the availability of high quality online courses on
+platforms such as Khan Academy~\citep{Khan04}, Coursera~\citep{Youn12},
+EdX~\citep{Kolo13}, and others~\citep{RhoaEtal13}. Continued expansion of the
+global internet backbone and improvements in computing hardware have also
+facilitated improvements in video streaming, enabling videos to be easily
+downloaded and shared by large segments of the world's population. This
+exciting time for online course instruction provides an opportunity to
+re-evaluate how we, as a global community, educate ourselves and each other.
+For example, we can ask: what makes an effective course or training program?
+Which aspects of teaching might be optimized or automated? How and why do
+learning needs and goals vary across people? How might we lower barriers to
+achieving a high quality education?
 
 Alongside these questions, there is a growing desire to extend existing
-theories beyond the domain of lab testing rooms and into real classrooms. In
-part, this has led to a recent resurgence of ``naturalistic'' or
-``observational'' experimental paradigms that attempt to better reflect more
-ethologically valid phenomena that are more directly relevant to real-world
-situations and behaviors. In turn, this has brought new challenges in data
-analysis and interpretation. A key step towards solving these challenges will
-be to build explicit models of real-world scenarios and how people behave in
-them (e.g., models of how people learn conceptual content from real-world
-courses, as in our current study). A second key step will be to understand
-which sorts of signals derived from behaviors and/or other
-measurements~\citep[e.g., neurophysiological data; ][]{NguyEtal22, MeshEtal20,
-PoulEtal17, BeviEtal19, DikkEtal17} might help to inform these models. A third
-major step will be to develop and employ reliable ways of evaluating the
-complex models and data that are a hallmark of naturalistic paradigms.
+theories beyond the domain of lab testing rooms and into real
+classrooms~\citep{Kauf03}. In part, this has led to a recent resurgence of
+``naturalistic'' or ``observational'' experimental paradigms that attempt to
+better reflect more ethologically valid phenomena that are more directly
+relevant to real-world situations and behaviors~\citep{NastEtal20}. In turn,
+this has brought new challenges in data analysis and interpretation. A key step
+towards solving these challenges will be to build explicit models of real-world
+scenarios and how people behave in them (e.g., models of how people learn
+conceptual content from real-world courses, as in our current study). A second
+key step will be to understand which sorts of signals derived from behaviors
+and/or other measurements~\citep[e.g., neurophysiological data; ][]{NguyEtal22,
+MeshEtal20, PoulEtal17, BeviEtal19, DikkEtal17} might help to inform these
+models. A third major step will be to develop and employ reliable ways of
+evaluating the complex models and data that are a hallmark of naturalistic
+paradigms.
 

### 2023-01-27 paper/supplement.tex

@@
 
-\author{Paxton C. Fitzpatrick\textsuperscript{1} and Jeremy R.
-Manning\textsuperscript{*, 1}\\\textsuperscript{1}Dartmouth
-College\\\textsuperscript{*}Corresponding author:
+\author{Paxton C. Fitzpatrick\textsuperscript{1},
+Andrew C. Heusser\textsuperscript{1, 2}, and Jeremy R.
+Manning\textsuperscript{1, *}\\\textsuperscript{1}Dartmouth
+College\\\textsuperscript{2}Akili Interactive\\\textsuperscript{*}Corresponding author:
 jeremy.r.manning@dartmouth.edu}

### 2023-01-27 paper/supplement.tex
another round of edits

@@
     included on each quiz: questions about the \textit{Four Fundamental Forces}
-    lecture (FFF), questions about the \textit{Birth of Stars} lecture, and
-    questions about general physics knowledge (GK). Each question appeared on
-    at most one quiz (for each participant).}
+    lecture (FFF), questions about the \textit{Birth of Stars} lecture (BoS),
+    and questions about general physics knowledge (GK). Each question appeared
+    on at most one quiz (for each participant).}
 
@@
     \textbf{Topic} &       \textbf{1}  &        \textbf{2}  &               \textbf{3}  &           \textbf{4}  &       \textbf{5}  &        \textbf{6}  &             \textbf{7}  &           \textbf{8}  &        \textbf{9}  &               \textbf{10} \\\hline
-    0     &     star &    helium &             main &         mass &   atomic &  sequence &            get &       energy &      fuse &         hydrogen \\\hline
-    1     &   charge &     force &             mass &      gravity &   strong &   attract &          large &     strength &  distance &  electromagnetic \\\hline
-    2     &     huge &     force &  electromagnetic &        macro &      way &     scale &  concentration &        apply &      kind &           charge \\\hline
-    3     &     atom &     dense &               go &     hydrogen &     slow &       get &           huge &     condense &      mass &            would \\\hline
-    4     &   fusion &       get &        threshold &         core &    occur &      mass &      something &        start &   several &          jupiter \\\hline
-    5     &   enough &  ignition &           proton &        force &      get &     close &        nucleus &      coulomb &    fusion &            would \\\hline
-    6     &   energy &  pressure &         ignition &         mass &   little &      keep &        provide &       fusion &       get &         hydrogen \\\hline
-    7     &   proton &      weak &          neutron &  interaction &      one &        go &        nucleon &       cesium &     extra &              get \\\hline
-    8     &      run &      kind &              say &           go &     want &     would &            get &         well &      give &         although \\\hline
-    9     &     huge &     cloud &            space &        float &  imagine &  hydrogen &           atom &          say &  distance &          combine \\\hline
-    10    &      one &  hydrogen &           helium &           go &   proton &   neutron &           keep &       atomic &    detail &             fuse \\\hline
-    11    &  gravity &     force &             weak &  interaction &    apply &  strength &       distance &          ten &  relative &             next \\\hline
-    12    &    force &        go &    electrostatic &         call &   charge &    magnet &           side &      coulomb &      know &        different \\\hline
-    13    &    force &      atom &          nucleus &     electron &     much &  hydrogen &            get &       around &   coulomb &           charge \\\hline
-    14    &    force &     scale &          gravity &        start &     weak &     orbit &           keep &  fundamental &    around &         surprise \\
+    1     &     star &    helium &             main &         mass &   atomic &  sequence &            get &       energy &      fuse &         hydrogen \\\hline
+    2     &   charge &     force &             mass &      gravity &   strong &   attract &          large &     strength &  distance &  electromagnetic \\\hline
+    3     &     huge &     force &  electromagnetic &        macro &      way &     scale &  concentration &        apply &      kind &           charge \\\hline
+    4     &     atom &     dense &               go &     hydrogen &     slow &       get &           huge &     condense &      mass &            would \\\hline
+    5     &   fusion &       get &        threshold &         core &    occur &      mass &      something &        start &   several &          jupiter \\\hline
+    6     &   enough &  ignition &           proton &        force &      get &     close &        nucleus &      coulomb &    fusion &            would \\\hline
+    7     &   energy &  pressure &         ignition &         mass &   little &      keep &        provide &       fusion &       get &         hydrogen \\\hline
+    8     &   proton &      weak &          neutron &  interaction &      one &        go &        nucleon &       cesium &     extra &              get \\\hline
+    9     &      run &      kind &              say &           go &     want &     would &            get &         well &      give &         although \\\hline
+    10     &     huge &     cloud &            space &        float &  imagine &  hydrogen &           atom &          say &  distance &          combine \\\hline
+    11    &      one &  hydrogen &           helium &           go &   proton &   neutron &           keep &       atomic &    detail &             fuse \\\hline
+    12    &  gravity &     force &             weak &  interaction &    apply &  strength &       distance &          ten &  relative &             next \\\hline
+    13    &    force &        go &    electrostatic &         call &   charge &    magnet &           side &      coulomb &      know &        different \\\hline
+    14    &    force &      atom &          nucleus &     electron &     much &  hydrogen &            get &       around &   coulomb &           charge \\\hline
+    15    &    force &     scale &          gravity &        start &     weak &     orbit &           keep &  fundamental &    around &         surprise \\
 
@@
 
-\renewcommand{\refname}{Supplementary references}
-\bibliographystyle{apa}
-\bibliography{CDL-bibliography/cdl}
+% \renewcommand{\refname}{Supplementary references}
+% \bibliographystyle{apa}
+% \bibliography{CDL-bibliography/cdl}
 

### 2023-01-27 paper/main.tex

@@
 representation space, where nearby coordinates reflect similar or related
-concepts. We test our approach using behavioral data collected from a group of
-college students. In the experiment, we ask the participants to answer small
-sets of multiple choice quiz questions interleaved between watching two course
-videos from the Khan Academy platform. We applied our framework to the videos'
-transcripts, and to text of the quiz questions, to quantify the content of each
-moment of video and each quiz question. We used these embeddings, along with
-participants' quiz responses, to track how the learners' knowledge changed
-after watching each video. Our findings show how a small set of quiz questions
-may be used to obtain rich and meaningful high resolution insights into what
-each learner knows, and how their knowledge changes over time as they learn.
+concepts. We test our approach using behavioral data from participants who
+answered small sets of multiple choice quiz questions interleaved between
+watching two course videos from the Khan Academy platform. We applied our
+framework to the videos' transcripts, and to text of the quiz questions, to
+quantify the content of each moment of video and each quiz question. We used
+these embeddings, along with participants' quiz responses, to track how the
+learners' knowledge changed after watching each video. Our findings show how a
+small set of quiz questions may be used to obtain rich and meaningful high
+resolution insights into what each learner knows, and how their knowledge
+changes over time as they learn.
 
@@
 multiple choice quiz questions that would enable us to test participants'
-knoweldge about each individual video and about related content not
+knowledge about each individual video and about related content not
 specifically presented in either video (Tab.~\questions). Participants answered
@@
 across each question set, we found a strong correspondence
-(Fig.~|ref{fig:topics}). The most variable topics from the \textit{Four
+(Fig.~\ref{fig:topics}). The most variable topics from the \textit{Four
 Fundamental Forces} lecture, and questions about that lecture, are 2, 3, 8, 12,
-13, 14, and 15. The most variable topics from the \textbf{Birth of Stars}
+13, 14, and 15. The most variable topics from the \textit{Birth of Stars}
 lecture, and questions about that lecture, are 1, 4, 5, 6, and 7. This strong
@@
 representative examples are shown at the bottom of
-Fig.~\ref{fig:question-correlations}.
+Figure~\ref{fig:question-correlations}.
 
@@
 identical scores on an exam, might our modeling framework help us to gain more
-naunced insights into the \textit{specific} content that each student has
+nuanced insights into the \textit{specific} content that each student has
 mastered (or failed to master)? For example, a student who misses three
@@
 participant's knowledge at the held-out question's embedding coordinate. For
-each quiz, we aggregated these estimates into two distributions: one for the
+each quiz, we grouped these estimates into two distributions: one for the
 estimated knowledge at the coordinates of each \textit{correctly} answered
@@
     and~\individualKnowledgeMapsC. \textbf{B. Average ``learning maps''
-    estiamted between each successive pair of quizzes.} The learning maps are
+    estimated between each successive pair of quizzes.} The learning maps are
     in the same general format as the knowledge maps in Panel A, but each
@@
 Because the 2D projection we used to construct the knowledge and learning maps
-is (partially) invertable, we may gain additional insights into the estimates
+is (partially) invertible, we may gain additional insights into the estimates
 by reconstructing the original high-dimensional topic vectors for any point(s)
@@
 (Fig.~\ref{fig:knowledge-maps}) hint at one potential form that an automated
-``empathetic'' teacher might take. We imagine that automated content delivery
+``empathetic'' teacher might take. We imagine automated content delivery
 systems that adapt lessons on the fly according to continually updated
 estimates of what students know and how quickly they are learning different
-conceptual content~\citep[e.g., building on ideas such as ][and
+conceptual content~\citep[e.g., building on ideas such as][and
 others]{AndeSkwa86, Half88, Kuma05, WolzEtal88}.
@@
 Other Pacific Islander (1 participant). (Note that some participants
-selected multiple recial categories.)
+selected multiple racial categories.)
 
@@
 
-Particpants reported their undergraduate major(s) as Social Sciences (28
+Participants reported their undergraduate major(s) as Social Sciences (28
 participants), Natural sciences (16), Professional (e.g., pre-med or pre-law; 8
@@
 participants reported having watched videos on Chemistry, AP Chemistry, or
-Organic Chemstry (21 participants); Physics, AP Physics I, or AP Physics II (15
+Organic Chemistry (21 participants); Physics, AP Physics I, or AP Physics II (15
 participants); Biology, AP Biology; or High school Biology (15 participants);
@@
 model and participants' quiz performance on each question, we can estimate
-their knowledge about \textit{any} content expressable by the embedding model--
+their knowledge about \textit{any} content expressible by the embedding model--
 not solely the content explicitly probed by the quiz questions. To visualize
@@
 from a regular $100 \times 100$ grid of coordinates that evenly tiled the
-enclosing rectangle. We sought to estimate participants' knoweldge (and
+enclosing rectangle. We sought to estimate participants' knowledge (and
 learning---i.e., changes in knowledge) at each of the resulting 10000
@@
 
+\section*{Author contributions}
+
+Conceptualization: PCF, ACH, and JRM. Methodology: PCF, ACH, and JRM. Software:
+PCF. Validation: PCF. Formal analysis: PCF. Resources: PCF, ACH, and JRM. Data
+curation: PCF. Writing (original draft): JRM. Writing (review and editing):
+PCF, ACH, and JRM. Visualization: PCH and JRM. Supervision: JRM. Project
+administration: PCH. Funding acquisition: JRM.
+
+\section*{Data and code availability}
+
+All of the data analyzed in this manuscript, along with all of the code for
+running our experiment and carrying out the analyses may be found at
+https://github.com/Con\-text\-Lab/eff\-ic\-ient-learn\-ing-khan.
+
+\section*{Acknowledgements}
+
+We acknowledge useful discussions, assistance in setting up an earlier
+(unpublished) version of this study, and assistance with some of the data
+collection efforts from Will Baxley, Max Bluestone, Daniel Carstensen, Kunal
+Jha, Caroline Lee, Lucy Owen, Xinming Xu, and Kirsten Ziman. Our work was
+supported in part by NSF CAREER Award Number 2145172 to JRM. The content is
+solely the responsibility of the authors and does not necessarily represent the
+official views of our supporting organizations. The funders had no role in
+study design, data collection and analysis, decision to publish, or preparation
+of the manuscript.
+
 \bibliographystyle{apa}

### 2023-01-28 paper/main.tex
saving progress on edits

@@
 
+% simple command for inline comments
+\newcommand{\comment}[1]{}
+
 \doublespacing
@@
 
-\title{Text embedding models reveal high resolution insights into conceptual
-knowledge from short multiple choice quizzes}
+%\title{Text embedding models reveal high-resolution insights into conceptual
+%knowledge and learning from short multiple-choice quizzes}
+\title{A geometric framework for capturing high-resolution insights into
+conceptual knowledge and learning in classroom-like settings}
 
@@
 Andrew C. Heusser\textsuperscript{1, 2}, and Jeremy R.
-Manning\textsuperscript{1, *}\\\textsuperscript{1}Dartmouth
-College\\\textsuperscript{2}Akili Interactive\\\textsuperscript{*}Corresponding author:
-jeremy.r.manning@dartmouth.edu}
+Manning\textsuperscript{1, *}\\\small{\textsuperscript{1}Department of Psychological and Brain Sciences}\\\small{Dartmouth College, Hanover, NH 03755, USA}\\\small{\textsuperscript{2}Akili Interactive Labs}\\\small{Boston, MA 02110, USA}\\\small{\textsuperscript{*}Corresponding author:
+Jeremy.R.Manning@Dartmouth.edu}}
 
@@
 
-\begin{abstract} We develop a mathematical framework, based on natural language
+\begin{abstract}\noindent We develop a mathematical framework, based on natural language
 processing models, for tracking and characterizing the acquisition of
-conceptual knowledge. Our approach embeds each concept in a high dimensional
-representation space, where nearby coordinates reflect similar or related
+conceptual knowledge in real-world educational contexts. Our approach embeds
+course content in a high-dimensional
+conceptual space, where nearby coordinates reflect similar or related
 concepts. We test our approach using behavioral data from participants who
-answered small sets of multiple choice quiz questions interleaved between
-watching two course videos from the Khan Academy platform. We applied our
-framework to the videos' transcripts, and to text of the quiz questions, to
-quantify the content of each moment of video and each quiz question. We used
+watched two lecture videos from the Khan Academy platform, interleaved
+between three short multiple-choice quizzes. We applied our
+framework to the videos' transcripts and the text of the quiz questions to
+quantify the conceptual content presented in each moment of video and knowledge probed by each quiz question. We used
 these embeddings, along with participants' quiz responses, to track how the
-learners' knowledge changed after watching each video. Our findings show how a
-small set of quiz questions may be used to obtain rich and meaningful high
-resolution insights into what each learner knows, and how their knowledge
+learners' knowledge changed after watching each video. Our findings demonstrate how a
+small set of quiz questions may be used to obtain rich and meaningful 
+high-resolution insights into individual students' knowledge, and how it
 changes over time as they learn.
@@
 
-Suppose that a teacher had access to a complete ``map'' of everything their
+Suppose that a teacher had access to a complete ``map'' of everything a
 student knew. Defining what such a map might even look like, let alone how it
 might be constructed or filled in, is itself a non-trivial problem. But if a
-teacher \textit{were} to gain access to such a map, how might that change their
-ability to teach the student? Perhaps they might start by checking how well the
+teacher \textit{were} to gain access to such a map, how might it change their
+ability to teach that student? Perhaps they might start by checking how well the
 student knew the to-be-learned information already, or how much they knew about
@@
 content. For other students (or other content areas), it might be more
-effective to optimize for direct connections between already-known content and
-any new material. Observing how the student's knowledge was changing over time,
-in response to their training, could also help to guide the teacher.
+effective to optimize for direct connections between already known content and
+new material. Observing how the student's knowledge changed over time,
+in response to their teaching, could also help to guide the teacher towards
+the most effective strategy for that individual student.
 
@@
 
-The difference between ``understanding'' and ``memorizing,'' as framed by the
+The difference between ``understanding'' and ``memorizing,'' as framed by
 researchers in education, cognitive psychology, and cognitive
-neuroscience~\citep{Kato40, Gall00, ScotEtal07, HallGree08, Macl05} has
+neuroscience~\citep[e.g.,][]{Kato40, Gall00, ScotEtal07, HallGree08, Macl05} has
 profound analogs in the fields of natural language processing and natural
@@
 information about what the document is about, just as memorizing a passage
-might be used to answer simple questions about the passage~\citep[e.g., whether
+might provide some ability to answer simple questions about it~\citep[e.g., whether
 it might contain words related to furniture versus physics;][]{LandDuma97,
@@
 ``current state of knowledge'' should change accordingly. Learning new concepts
-should both update our characterizations of ``what is known'' and should also
-unlock any now-satisfied dependencies of that newly learned concept so that
+should both update our characterizations of ``what is known'' and also
+unlock any now-satisfied dependencies of those newly learned concepts so that
 they are ``tagged'' as available for future learning.
+% TODO: is the second half of this paragraph relevant to this paper??
 

### 2023-01-28 paper/main.tex
first pass of edits through end of intro

@@
 might provide some ability to answer simple questions about it~\citep[e.g., whether
-it might contain words related to furniture versus physics;][]{LandDuma97,
+it contains words related to furniture versus physics;][]{LandDuma97,
 BleiEtal03, BleiLaff06}. However, modern natural language processing
@@
 
-Here we develop a framework for modelling how knowledge is acquired during
+Here we develop a framework for modeling how knowledge is acquired during
 learning. The central idea is to use text embedding models to define the
@@
 related concepts are located nearby in space. We use this framework to analyze
-and interpret behavioral data collected from an experiment that has
+and interpret behavioral data collected from an experiment that had
 participants watch and answer multiple choice questions about a series of
@@
 models that have only peripheral relevance to the kinds of learning that
-students and teachers actually seek. To help bridge this gap, our study uses
+students and teachers actually seek \citep{Macl05}. To help bridge this gap, our study uses
 course materials from real online courses to inform, fit, and test models of
@@
 fundamentally ``smooth.'' In other words, as one moves through a space
-representing someone's knowledge (where similar concepts occupy nearby
+representing an individual's knowledge (where similar concepts occupy nearby
 coordinates), their ``level of knowledge'' should change relatively gradually

### 2023-01-29 paper/main.tex
initial edits to results and experiment methods

@@
 and interpret behavioral data collected from an experiment that had
-participants watch and answer multiple choice questions about a series of
+participants watch and answer multiple-choice questions about a series of
 recorded course lectures.
@@
 models that have only peripheral relevance to the kinds of learning that
-students and teachers actually seek \citep{Macl05}. To help bridge this gap, our study uses
+students and teachers actually seek \citep{Macl05, HallGree08}. To help bridge this gap, our study uses
 course materials from real online courses to inform, fit, and test models of
@@
     \caption{\textbf{Experimental paradigm.} Participants alternate between
-    answering 13-question multiple choice quizzes and watching two Khan academy
-    videos. Each quiz contains a mix of 5 questions about lecture 1, 5
-    questions about lecture 2, and 3 general physics knowledge questions. The
+    answering 13-question multiple-choice quizzes and watching two Khan Academy
+    lectures. Each quiz contains a mix of 5 questions about lecture 1, 5
+    questions about lecture 2, and 3 questions about general physics knowledge. The
     specific questions reflected on each quiz, and the orders of each quiz's
@@
 
-We asked our participants to answer questions from several multiple choice
-quizzes and watch two lecture videos from the \textit{Khan Academy} platform
-(Fig.~\ref{fig:experiment}). One lecture video, entitled \textit{Four
-Fundamental Forces}, was about the four fundamental forces in physics: gravity,
-strong and weak interactions, and electromagnetism. The second lecture video,
-entitled \textit{Birth of Stars}, provides an overview of our current
-understanding of how stars form. We selected both lessons to be (a) accessible
-to a broad audience, e.g., by minimizing prerequisite knowledge, (b) largely
-independent of each other, e.g., so that the two videos focused on different
-material and did not depend on each other, and (c) related to each other, e.g.,
-so that both videos contained at least \textit{some} similar or overlapping
-content. The two videos we selected are introductory (i.e., minimizing specific
-prerequisite knowledge), and are about different primary concepts, but they
-both also touch on ``physics'' and ``astronomy'' themes. We also wrote a set of
-multiple choice quiz questions that would enable us to test participants'
-knowledge about each individual video and about related content not
-specifically presented in either video (Tab.~\questions). Participants answered
+We asked participants in our study to answer questions from several multiple-choice
+quizzes and watch two lecture videos from the Khan Academy platform
+(Fig.~\ref{fig:experiment}). The first lecture video, entitled \textit{Four
+Fundamental Forces}, discussed the four fundamental forces in physics: gravity,
+strong and weak interactions, and electromagnetism. The second,
+entitled \textit{Birth of Stars}, provided an overview of our current
+understanding of how stars form. We selected these lessons to be (a) accessible
+to a broad audience, i.e., requiring minimal prerequisite knowledge to understand;
+(b) conceptually related to each other, i.e., covering at least \textit{some}
+similar or overlapping content; and (c) largely independent of each other, i.e., focused
+on sufficiently different material that understanding one did not require having seen
+the other. Thus, the two videos we selected are introductory, high-level lectures that both 
+belong to Khan Academy's ``Cosmology and Astronomy" course domain, but come from
+different lecture series (``Scale of the Universe" and ``Stars, Black Holes, and Galaxies" 
+for the first and second lectures, respectively).
+
+We also wrote a set of
+multiple-choice quiz questions that would enable us to test participants'
+knowledge about each individual lecture, as well as related content not
+specifically presented in either video ( see Tab.~\questions). Participants answered
 questions randomly drawn from each content area (lecture 1, lecture 2, and
 general physics knowledge) across each of three quizzes. Quiz 1 was intended to
-assessed participants' knowledge before training; quiz 2 assessed knowledge
-after watching the \textit{Four Fundamental Forces} video (i.e., lecture 1);
+assessed participants' ``baseline" knowledge before training, quiz 2 assessed knowledge
+after watching the \textit{Four Fundamental Forces} video (i.e., lecture 1),
 and quiz 3 assessed knowledge after watching the \textit{Birth of Stars} video
@@
 
-We trained a text embedding model using sliding windows of text from the two
-videos' transcripts (see \textit{Constructing text embeddings of multiple
-videos and questions}). We also used the same model (i.e., trained on the
+We trained a topic model \citep{BleiEtal03} using sliding windows of text from the two
+lectures' transcripts (see \hyperref[subsec:topic-modeling]{\textit{Constructing text embeddings of multiple
+lectures and questions}}). We also used the same model (i.e., trained on the
 videos' transcripts) to embed the text of each question in our pool. This
@@
     \centering
-    \includegraphics[width=0.6\textwidth]{figs/active-topics}
+    \includegraphics[width=0.7\textwidth]{figs/active-topics}
 
@@
 questions (bottom panels); colors denote topics. The top-weighted words from
-the most ``expressive'' (i.e., variable across observations) topics from each
+the most ``expressive'' (i.e., variable across observations) topic from each
 lecture are displayed in the upper right (orange: topic 2; yellow-green: topic
@@
 We developed a simple formula (Eqn.~\ref{eqn:prop}) for using a participant's
-responses to a small set of multiple choice questions to estimate how much the
+responses to a small set of multiple-choice questions to estimate how much the
 participant ``knows'' about the concept reflected by any arbitrary coordinate,
@@
 
-Participants reported their undergraduate major(s) as Social Sciences (28
-participants), Natural sciences (16), Professional (e.g., pre-med or pre-law; 8
-participants), Mathematics and engineering (7 participants), Humanities (4
-participants), or Undecided (3 participants). Note that some participants
+Participants reported their undergraduate major(s) as ``social sciences" (28
+participants), ``natural sciences" (16 participants), ``professional" (e.g., pre-med or pre-law; 8
+participants), ``mathematics and engineering" (7 participants), ``humanities" (4
+participants), or ``undecided" (3 participants). Note that some participants
 selected multiple categories for their undergraduate major. We also asked
-participants about the courses they had taken. In total, 46 participants
-reported having taken at least one Khan academy course in the past or being
-familiar with the Khan academy, and 4 reported not having taken any Khan
-academy courses. Of the participants who reported having watched at least one
-Khan academy course, 1 participant declined to report the number of courses
-they had watched; 7 participants reported having watched 1--2 courses; 11
-reported having watched 3--5 courses; 8 reported having watched 5--10 courses;
+participants about the courses they had taken. In total, 45 participants
+reported having taken at least one Khan Academy course in the past, 
+and 5 reported not having taken any Khan
+Academy courses. Of those who reported having watched at least one
+Khan Academy course, 7 participants reported having watched 1--2 courses, 11
+reported having watched 3--5 courses, 8 reported having watched 5--10 courses,
 and 19 reported having watched 10 or more courses. We also asked participants
 about the specific courses they had watched, categorized under different
-subject areas. In the ``Mathematics'' area participants reported having watched
+subject areas. In the ``Mathematics'' area, participants reported having watched
 videos on AP Calculus AB (21 participants), Precalculus (17 participants),
@@
 Early Math (1 participant), Arithmetic (1 participant), and other videos not
-listed in our survey (6 participants). In the ``Science and engineering'' area
+listed in our survey (5 participants). In the ``Science and engineering'' area,
 participants reported having watched videos on Chemistry, AP Chemistry, or
@@
 Health and Medicine (1 participant); or other videos not listed in our survey
-(20 participants). We also asked participants if they had specifically seen the
-videos used in our experiment. When we asked about the \textit{Four Fundamental
-Forces} video, 45 participants reported not having watched it before, 1
-participant reported that they were not sure if they had watched it before, and
-4 participants declined to respond. When we asked about the \textit{Birth of
-Stars} video, 46 participants reported not having watched it before and 4
-participants declined to respond. When we asked participants about non-Khan
-academy online courses, they reported having watched or taken courses on
+(19 participants). We also asked participants whether they had specifically seen the
+videos used in our experiment. Of the 45 participants who reported having having
+taken at least one Khan Academy course in the past, 44 participants reported that they had not watched the \textit{Four Fundamental Forces} video, and 1 participant reported that they were not sure whether they had watched it.
+All participants reported that they had not watched the \textit{Birth of Stars} video.
+When we asked participants about non-Khan
+Academy online courses, they reported having watched or taken courses on
 Mathematics (15 participants), Science and engineering (11 participants), Test
@@
 seconds) and \textit{Birth of Stars} (an introduction to how stars are formed;
-duration: 7 minutes and 57 seconds). We hand-wrote 39 multiple choice
+duration: 7 minutes and 57 seconds). We hand-wrote 39 multiple-choice
 questions: 15 about the conceptual content of \textit{Four Fundamental Forces},
-another 15 about the conceptual content of \textit{Birth of Stars}, and 9 other
+15 about the conceptual content of \textit{Birth of Stars}, and 9
 questions that tested for general conceptual knowledge about basic physics
 (covering material that was not presented in either video). The full set of
-questions may be found in Table~\questions.
+questions and answer options may be found in Table~\questions.
+
+%Over the course of the experiment, participants completed three multiple-choice quizzes
 
@@
 selected questions (chosen from the full set of 39). Then they watched the
-\textit{The Four Fundamental Forces} video. Next, they answered a second set of
+\textit{The Four Fundamental Forces} lecture video. Next, they answered a second set of
 13 questions (chosen at random from the remaining 26 questions). Fourth,
@@
 
-\subsubsection*{Constructing text embeddings of multiple videos and questions}
+\subsubsection*{Constructing text embeddings of multiple lectures and questions}\label{subsec:topic-modeling}
 

### 2023-01-29 paper/main.tex
move sliding window fig to results section, WIP updates to topic modeling description

@@
 \usepackage{lineno}
+
+\usepackage{xcolor}
 
@@
 Our primary research goal is to advance our understanding of what it means to
-acquire deep real-world conceptual knowledge. Traditional laboratory approaches
+acquire deep, real-world conceptual knowledge. Traditional laboratory approaches
 to studying learning and memory (e.g., list learning studies) often draw little
@@
 rather than whether the information is \textit{understood}. Approaches to
-studying conceptual learning, such as category learning experiments, can start
+studying conceptual learning, such as category learning experiments, can begin
 to investigate the distinction between memorization and understanding, often by
@@
 course materials from real online courses to inform, fit, and test models of
-real-world conceptual learning. We also provide a ``proof of concept''
-demonstration of how our models might be used to construct ``maps'' of what
+real-world conceptual learning. We also provide a
+demonstration of how our models can be used to construct ``maps'' of what
 students know, and how their knowledge changes with training. In addition to
@@
 throughout that space. To begin to test this smoothness assumption, we sought
-to track our participants' knowledge and how it changed over time in response
+to track participants' knowledge and how it changed over time in response
 to training.
@@
 
-We asked participants in our study to answer questions from several multiple-choice
-quizzes and watch two lecture videos from the Khan Academy platform
-(Fig.~\ref{fig:experiment}). The first lecture video, entitled \textit{Four
+We asked participants in our study to complete brief multiple-choice quizzes before, between, and after watching two lecture videos from the Khan Academy \citep{Khan04} platform (Fig.~\ref{fig:experiment}).
+The first lecture video, entitled \textit{Four
 Fundamental Forces}, discussed the four fundamental forces in physics: gravity,
@@
 entitled \textit{Birth of Stars}, provided an overview of our current
-understanding of how stars form. We selected these lessons to be (a) accessible
+understanding of how stars form.
+%(See \hyperref[subsec:experiment]{\textit{Experiment}} for more information on how these lectures were chosen.)
+%Each multiple-choice quiz consisted of 13 questions that would enable us to test participants'
+%knowledge about each individual lecture, as well as related content not
+%specifically presented in either video ( see Tab.~\questions).
+%
+%We selected these lessons to be accessible to a broad audience (i.e., requiring minimal prerequisite knowledge to understand) and largely independent of each other (i.e., focused on sufficiently different material that understanding one did not require having seen the other), but conceptually related to each other (covering at least \textit{some} similar or overlapping content).
+We selected these lessons to be (a) accessible
 to a broad audience, i.e., requiring minimal prerequisite knowledge to understand;
@@
 on sufficiently different material that understanding one did not require having seen
-the other. Thus, the two videos we selected are introductory, high-level lectures that both 
-belong to Khan Academy's ``Cosmology and Astronomy" course domain, but come from
-different lecture series (``Scale of the Universe" and ``Stars, Black Holes, and Galaxies" 
+the other. The two videos we selected are introductory lectures that both
+belong to Khan Academy's ``Cosmology and Astronomy'' course domain, but are taken from
+different lecture series (``Scale of the Universe'' and ``Stars, Black Holes, and Galaxies''
 for the first and second lectures, respectively).
 
-We also wrote a set of
+%We asked participants in our study to answer questions from several multiple-choice
+%quizzes and watch two lecture videos from the Khan Academy platform
+%(Fig.~\ref{fig:experiment}). The first lecture video, entitled \textit{Four
+%Fundamental Forces}, discussed the four fundamental forces in physics: gravity,
+%strong and weak interactions, and electromagnetism. The second,
+%entitled \textit{Birth of Stars}, provided an overview of our current
+%understanding of how stars form. We selected these lessons to be (a) accessible
+%to a broad audience, i.e., requiring minimal prerequisite knowledge to understand;
+%(b) conceptually related to each other, i.e., covering at least \textit{some}
+%similar or overlapping content; and (c) largely independent of each other, i.e., focused
+%on sufficiently different material that understanding one did not require having seen
+%the other. Thus, the two videos we selected are introductory, high-level lectures that both
+%belong to Khan Academy's ``Cosmology and Astronomy'' course domain, but come from
+%different lecture series (``Scale of the Universe'' and ``Stars, Black Holes, and Galaxies''
+%for the first and second lectures, respectively).
+
+We then created a pool of
 multiple-choice quiz questions that would enable us to test participants'
@@
 questions randomly drawn from each content area (lecture 1, lecture 2, and
-general physics knowledge) across each of three quizzes. Quiz 1 was intended to
-assessed participants' ``baseline" knowledge before training, quiz 2 assessed knowledge
+general physics knowledge) on each of the three quizzes. Quiz 1 was intended to
+assess participants' ``baseline'' knowledge before training, quiz 2 assessed knowledge
 after watching the \textit{Four Fundamental Forces} video (i.e., lecture 1),
@@
 (i.e., lecture 2).
+
+\begin{figure}[tp]
+\centering
+\includegraphics[width=\textwidth]{figs/sliding_windows}
+
+\caption{\textbf{Constructing video content \textit{trajectories}. \textbf{A}.
+Building a document pool from sliding windows of text.} We decompose each
+video's transcript into a series of overlapping sliding windows. The set of
+transcript snippets (across all windows) may be treated as a set of
+``documents'' for training a text embedding model. After training a text
+embedding model on the two videos' sliding windows, we construct ``trajectories''
+through text embedding space by joining the embedding coordinates of successive
+sliding windows from each video. \textbf{B. Embedding multiple videos and
+questions.} Applying the same text embedding approach to each video, along with
+the text of each question in our pool (Tab.~\questions), results in one trajectory per video and one
+embedding coordinate (dot) per question (blue: \textit{Four Fundamental
+Forces}; green: \textit{Birth of Stars}; purple: general physics knowledge). \color{red}{Here
+we have projected the 15-dimensional embeddings into a 3D space using Uniform
+Manifold Approximation and Projection~\citep[UMAP;][]{McInEtal18a}}.}
+
+\label{fig:sliding-windows}
+\end{figure}
+
+To study how participants' conceptual knowledge changed over the course of the experiment, 
+we first sought to characterize the abstract concepts presented to them in each of the two 
+lectures. We adapted an approach we developed in prior work \citep{HeusEtal21} to extract 
+the latent themes from the lectures' contents using a topic model \citep{BleiEtal03}. Briefly, 
+topic models take as input a collection of text documents and learn a set of ``topics'' (i.e., 
+latent themes) from their contents. Once fit, a topic model can be used to transform arbitrary 
+(potentially new) documents into sets of ``topic proportions,'' describing the weighted blend 
+of learned topics reflected in their texts. We parsed automatically generated transcripts of 
+the two lectures into overlapping sliding windows, and used these as documents to fit our 
+model (Fig.~\ref{fig:sliding-windows}A; see 
+\hyperref[subsec:topic-modeling]{\textit{Constructing text embeddings of multiple lectures 
+and questions}}). The ($k$=15) topics
+
+%To construct a corpus of text documents for the two lectures, we parsed their transcripts into overlapping sliding windows (Fig.~\ref{fig:sliding-windows}A; see \hyperref[subsec:topic-modeling]{\textit{Constructing text embeddings of multiple lectures and questions}})
 
@@
 
-Participants reported their undergraduate major(s) as ``social sciences" (28
-participants), ``natural sciences" (16 participants), ``professional" (e.g., pre-med or pre-law; 8
-participants), ``mathematics and engineering" (7 participants), ``humanities" (4
-participants), or ``undecided" (3 participants). Note that some participants
+Participants reported their undergraduate major(s) as ``social sciences'' (28
+participants), ``natural sciences'' (16 participants), ``professional'' (e.g., pre-med or pre-law; 8
+participants), ``mathematics and engineering'' (7 participants), ``humanities'' (4
+participants), or ``undecided'' (3 participants). Note that some participants
 selected multiple categories for their undergraduate major. We also asked
@@
 
-\subsection*{Experiment}
+\subsection*{Experiment}\label{subsec:experiment}
 
@@
 seconds) and \textit{Birth of Stars} (an introduction to how stars are formed;
-duration: 7 minutes and 57 seconds). We hand-wrote 39 multiple-choice
-questions: 15 about the conceptual content of \textit{Four Fundamental Forces},
-15 about the conceptual content of \textit{Birth of Stars}, and 9
+duration: 7 minutes and 57 seconds). We then hand-created 39 multiple-choice
+questions: 15 about the conceptual content of \textit{Four Fundamental Forces} (i.e., lecture 1),
+15 about the conceptual content of \textit{Birth of Stars} (i.e., lecture 2), and 9
 questions that tested for general conceptual knowledge about basic physics
 (covering material that was not presented in either video). The full set of
-questions and answer options may be found in Table~\questions.
+questions and answer choices may be found in Table~\questions.
 
-%Over the course of the experiment, participants completed three multiple-choice quizzes
-
-Participants began the main experiment by answering a battery of 13 randomly
-selected questions (chosen from the full set of 39). Then they watched the
-\textit{The Four Fundamental Forces} lecture video. Next, they answered a second set of
-13 questions (chosen at random from the remaining 26 questions). Fourth,
-participants watch the \textit{Birth of Stars} video, and finally they answered
-the remaining 13 questions. Our experimental procedure is diagramed in
-Figure~\ref{fig:experiment}. We used the experiment to develop and test our
-computational framework for estimating knowledge and learning.
+Over the course of the experiment, participants completed three 13-question 
+multiple-choice quizzes: the first before viewing lecture 1, the second between 
+lectures 1 and 2, and the third after viewing lecture 2 (Fig.~\ref{fig:experiment}). 
+The questions appearing on each quiz, for each participant, were randomly 
+chosen from the full set of 39, with the constraints that (a) each quiz contain 5
+questions about lecture 1, 5 questions about lecture 2, and 3 questions, and 
+(b) each question appear exactly once. The order of questions on each quiz,
+and the order of answer options for each question, were also randomized. Our
+experimental protocol was approved by the Committee for the Protection of 
+Human Subjects at Dartmouth College.  We used the experiment to develop 
+and test our computational framework for estimating knowledge and learning.
 
@@
 
-We extended an approach developed by~\citep{HeusEtal21} to construct text
-embeddings for each moment of each lecture, and of each question in our pool.
-Briefly, our approach uses a topic model~\citep{BleiEtal03}, trained on a set
+We adapted an approach we developed in prior work~\citep{HeusEtal21} to embed
+each moment of the two lectures and each question in our pool in a common representational space.
+Briefly, our approach uses a topic model~\citep[Latent Dirichlet Allocation;][]{BleiEtal03}, 
+fit to a corpus of documents to discover a set of $k$ ``topics'' or ``themes'' from their contents.
+Formally, each topic is defined as a set of weights over each word in the model's vocabulary
+(i.e., the union of all unique words, across all documents, excluding ``stop
+words.'').
+
+We adapted an approach we developed in prior work~\citep{HeusEtal21} to embed
+each moment of the two lectures and each question in our pool in a common representational space.
+Briefly, our approach uses a topic model~\citep[Latent Dirichlet Allocation;][]{BleiEtal03}, trained on a set
 of documents, to discover a set of $k$ ``topics'' or ``themes.'' Formally, each
@@
 
-\begin{figure}[tp]
-\centering
-\includegraphics[width=\textwidth]{figs/sliding_windows}
+%\begin{figure}[tp]
+%\centering
+%\includegraphics[width=\textwidth]{figs/sliding_windows}
+%
+%\caption{\textbf{Constructing video content \textit{trajectories}. \textbf{A}.
+%Building a document pool from sliding windows of text.} We decompose each
+%video's transcript into a series of overlapping sliding windows. The set of
+%transcript snippets (across all windows) may be treated as a set of
+%``documents'' for training a text embedding model. After training a text
+%embedding model on the two videos' sliding windows, we construct ``trajectories''
+%through text embedding space by joining the embedding coordinates of successive
+%sliding windows from each video. \textbf{B. Embedding multiple videos and
+%questions.} Applying the same text embedding approach to each video, along with
+%the text of each question in our pool (Tab.~\questions), results in one trajectory per video and one
+%embedding coordinate (dot) per question (blue: \textit{Four Fundamental
+%Forces}; green: \textit{Birth of Stars}; purple: general physics knowledge). \color{red}{Here
+%we have projected the 15-dimensional embeddings into a 3D space using Uniform
+%Manifold Approximation and Projection~\citep[UMAP;][]{McInEtal18a}}.}
+%
+%\label{fig:sliding-windows}
+%\end{figure}
 
-\caption{\textbf{Constructing video content \textit{trajectories}. \textbf{A.
-Building a document pool from sliding windows of text.} We decompose each
-video's transcript into a series of overlapping sliding windows. The set of
-transcript snippets (across all windows) may be treated as a set of
-``documents'' for training a text embedding model. After training a text
-embedding model using the two videos' sliding windows, along with the text from
-each question in our pool (Tab.~\questions), } we construct ``trajectories''
-through text embedding space by joining the embedding coordinates of successive
-sliding windows from each video. \textbf{B. Embedding multiple videos and
-questions.} Applying the same text embedding approach to each video, along with
-the text of each question, results in one trajectory per video and one
-embedding coordinate (dot) per question (blue: \textit{Four Fundamental
-Forces}; green: \textit{Birth of Stars}; pink: general physics knowledge). Here
-we have projected the 15-dimensional embeddings into a 3D space using Uniform
-Manifold Approximation and Projection~\citep[UMAP;][]{McInEtal18a}.}
-
-\label{fig:sliding-windows}
-\end{figure}
+As illustrated in Figure~\ref{fig:sliding-windows}A, we first
 
@@
 corpus of documents using overlapping sliding windows that span each video's
-transcript. Khan Academy videos are hosted on the YouTube platform, and all
+transcript.
+Khan Academy provides professionally created, manual transcriptions of all videos for closed captioning.
+However, such transcripts would not be readily available in all contexts to which our framework could potentially be applied.
+Khan Academy videos are hosted on the YouTube platform, which additionally provides automated transcripts
+
+Khan Academy videos are hosted on the YouTube platform, and all
 YouTube videos are run through Google's speech-to-text API~\citep{HalpEtal16}

### 2023-01-29 paper/main.tex
add labels and \namerefs for section references, replace \hyperref with \nameref

@@
 understanding of how stars form.
-%(See \hyperref[subsec:experiment]{\textit{Experiment}} for more information on how these lectures were chosen.)
+%(See \textit{\nameref{subsec:experiment}} for more information on how these lectures were chosen.)
 %Each multiple-choice quiz consisted of 13 questions that would enable us to test participants'
@@
 the two lectures into overlapping sliding windows, and used these as documents to fit our 
-model (Fig.~\ref{fig:sliding-windows}A; see 
-\hyperref[subsec:topic-modeling]{\textit{Constructing text embeddings of multiple lectures 
-and questions}}). The ($k$=15) topics
-
-%To construct a corpus of text documents for the two lectures, we parsed their transcripts into overlapping sliding windows (Fig.~\ref{fig:sliding-windows}A; see \hyperref[subsec:topic-modeling]{\textit{Constructing text embeddings of multiple lectures and questions}})
+model (Fig.~\ref{fig:sliding-windows}A; see \textit{\nameref{subsec:topic-modeling}}).
+The ($k$=15) topics
+
+%To construct a corpus of text documents for the two lectures, we parsed their transcripts into overlapping sliding windows (Fig.~\ref{fig:sliding-windows}A; see \textit{\nameref{subsec:topic-modeling}})
 
 We trained a topic model \citep{BleiEtal03} using sliding windows of text from the two
-lectures' transcripts (see \hyperref[subsec:topic-modeling]{\textit{Constructing text embeddings of multiple
-lectures and questions}}). We also used the same model (i.e., trained on the
+lectures' transcripts (see \textit{\nameref{subsec:topic-modeling}}). We also used the same model (i.e., trained on the
 videos' transcripts) to embed the text of each question in our pool. This
@@
 $x$, in text embedding space (e.g., the content reflected by any moment in a
-lecture they had watched; see \textit{Estimating dynamic knowledge traces}).
+lecture they had watched; see \textit{\nameref{subsec:traces}}).
 Essentially, the estimated knowledge at the coordinate is given by the weighted
@@
     questions about the content reflected in each moment of the lecture (see
-    \textit{Estimating dynamic knowledge traces}), using responses from one
+    \textit{\nameref{subsec:traces}}), using responses from one
     quiz (color). The traces are averaged across participants. \textbf{B.
@@
     displays a 2D projection of the estimated knowledge about the content
-    reflected by \textit{all} regions of topic space (see \textit{Creating
-    knowledge and learning map visualizations}). The topic trajectories of each
+    reflected by \textit{all} regions of topic space (see 
+    \textit{\nameref{subsec:knowledge-maps}}). The topic trajectories of each
     lecture and the coordinates of each question are indicated by dotted lines
@@
 video and for each question) into a shared 2-dimensional space (see
-\textit{Creating knowledge and learning map visualizations}). Next, we sampled
+\textit{\nameref{subsec:knowledge-maps}}). Next, we sampled
 points evenly from a $100 \times 100$ grid of coordinates that evenly tiled a
@@
 
-\subsubsection*{Estimating dynamic knowledge traces}
+\subsubsection*{Estimating dynamic knowledge traces}\label{subsec:traces}
 
@@
 
-\subsubsection*{Creating knowledge and learning map visualizations}
+\subsubsection*{Creating knowledge and learning map visualizations}\label{subsec:knowledge-maps}
 

### 2023-01-30 paper/main.tex
fixed initials in author contributions
rewrote topic modeling results paragraph

@@
 understanding of how stars form.
-%(See \textit{\nameref{subsec:experiment}} for more information on how these lectures were chosen.)
-%Each multiple-choice quiz consisted of 13 questions that would enable us to test participants'
-%knowledge about each individual lecture, as well as related content not
-%specifically presented in either video ( see Tab.~\questions).
-%
-%We selected these lessons to be accessible to a broad audience (i.e., requiring minimal prerequisite knowledge to understand) and largely independent of each other (i.e., focused on sufficiently different material that understanding one did not require having seen the other), but conceptually related to each other (covering at least \textit{some} similar or overlapping content).
 We selected these lessons to be (a) accessible
@@
 for the first and second lectures, respectively).
-
-%We asked participants in our study to answer questions from several multiple-choice
-%quizzes and watch two lecture videos from the Khan Academy platform
-%(Fig.~\ref{fig:experiment}). The first lecture video, entitled \textit{Four
-%Fundamental Forces}, discussed the four fundamental forces in physics: gravity,
-%strong and weak interactions, and electromagnetism. The second,
-%entitled \textit{Birth of Stars}, provided an overview of our current
-%understanding of how stars form. We selected these lessons to be (a) accessible
-%to a broad audience, i.e., requiring minimal prerequisite knowledge to understand;
-%(b) conceptually related to each other, i.e., covering at least \textit{some}
-%similar or overlapping content; and (c) largely independent of each other, i.e., focused
-%on sufficiently different material that understanding one did not require having seen
-%the other. Thus, the two videos we selected are introductory, high-level lectures that both
-%belong to Khan Academy's ``Cosmology and Astronomy'' course domain, but come from
-%different lecture series (``Scale of the Universe'' and ``Stars, Black Holes, and Galaxies''
-%for the first and second lectures, respectively).
 
@@
 
-To study how participants' conceptual knowledge changed over the course of the experiment, 
-we first sought to characterize the abstract concepts presented to them in each of the two 
-lectures. We adapted an approach we developed in prior work \citep{HeusEtal21} to extract 
-the latent themes from the lectures' contents using a topic model \citep{BleiEtal03}. Briefly, 
-topic models take as input a collection of text documents and learn a set of ``topics'' (i.e., 
-latent themes) from their contents. Once fit, a topic model can be used to transform arbitrary 
-(potentially new) documents into sets of ``topic proportions,'' describing the weighted blend 
-of learned topics reflected in their texts. We parsed automatically generated transcripts of 
-the two lectures into overlapping sliding windows, and used these as documents to fit our 
-model (Fig.~\ref{fig:sliding-windows}A; see \textit{\nameref{subsec:topic-modeling}}).
-The ($k$=15) topics
-
-%To construct a corpus of text documents for the two lectures, we parsed their transcripts into overlapping sliding windows (Fig.~\ref{fig:sliding-windows}A; see \textit{\nameref{subsec:topic-modeling}})
-
-We trained a topic model \citep{BleiEtal03} using sliding windows of text from the two
-lectures' transcripts (see \textit{\nameref{subsec:topic-modeling}}). We also used the same model (i.e., trained on the
-videos' transcripts) to embed the text of each question in our pool. This
-yielded, for each second of each video, and for each question, a single
-15-dimensional topic vector---i.e., a coordinate in a text embedding space
-(Fig.~\ref{fig:sliding-windows}). Intuitively, each dimension of the embedding
-space corresponds to a ``theme'' or ``topic'' reflected in some part(s) of the
-videos (Tab.~\topics), and the coordinates in embedding space denote the blend
-of themes reflected by a particular excerpt of text (e.g., from part of a
-video's transcript, from a question, etc.).
+To study how participants' conceptual knowledge changed over the course of the
+experiment, we first sought to characterize the abstract concepts presented to
+them in each of the two lectures. We adapted an approach we developed in prior
+work \citep{HeusEtal21} to extract the latent themes from the lectures' contents
+using a topic model \citep{BleiEtal03}. Briefly, topic models take as input a
+collection of text documents and learn a set of ``topics'' (i.e., latent
+themes) from their contents. Once fit, a topic model can be used to transform
+arbitrary (potentially new) documents into sets of ``topic proportions,''
+describing the weighted blend of learned topics reflected in their texts. We
+parsed automatically generated transcripts of the two lectures into
+overlapping sliding windows, which we treated as documents to fit our model
+(Fig.~\ref{fig:sliding-windows}A; see \textit{\nameref{subsec:topic-modeling}}).
+Transforming these windows with our model resulted in a number-of-windows by
+number-of-topics (15) topic-proportions matrix, denoting the unique mixture
+of broad themes from both lectures reflected in each window's content.
+Intuitively, each window's ``topic vector'' (i.e., column of the
+topic-proportions matrix) is analogous to a coordinate in a 15-dimensional
+space (whose axes are topics learned by the model). Within this space, each lecture's series of
+topic vectors (i.e., corresponding to sliding windows parsed from its
+transcript) forms a \textit{trajectory} that captures how its conceptual
+content unfolds over time (Fig.~\ref{fig:sliding-windows}A). We resampled
+these trajectories to a resolution of 1 topic vector for each second of video.
 
@@
 curation: PCF. Writing (original draft): JRM. Writing (review and editing):
-PCF, ACH, and JRM. Visualization: PCH and JRM. Supervision: JRM. Project
-administration: PCH. Funding acquisition: JRM.
+PCF, ACH, and JRM. Visualization: PCF and JRM. Supervision: JRM. Project
+administration: PCF. Funding acquisition: JRM.
 

### 2023-01-30 paper/main.tex
place \namerefs in \mbox to prevent bug when split across line or page breaks

@@
 \newcommand{\comment}[1]{}
+% italicize section names in \nameref and place in \mbox to prevent bug when 
+% text is split across lines or pages
+\NewCommandCopy{\oldnameref}{\nameref}
+\renewcommand{\nameref}[1]{\mbox{\textit{\oldnameref{#1}}}}
 
@@
 overlapping sliding windows, which we treated as documents to fit our model
-(Fig.~\ref{fig:sliding-windows}A; see \textit{\nameref{subsec:topic-modeling}}).
+(Fig.~\ref{fig:sliding-windows}A; see \nameref{subsec:topic-modeling}).
 Transforming these windows with our model resulted in a number-of-windows by
@@
 \end{figure}
+
+Next, wondered whether we could use this same model to capture the
 
@@
 $x$, in text embedding space (e.g., the content reflected by any moment in a
-lecture they had watched; see \textit{\nameref{subsec:traces}}).
+lecture they had watched; see \nameref{subsec:traces}).
 Essentially, the estimated knowledge at the coordinate is given by the weighted
@@
     questions about the content reflected in each moment of the lecture (see
-    \textit{\nameref{subsec:traces}}), using responses from one
+    \nameref{subsec:traces}), using responses from one
     quiz (color). The traces are averaged across participants. \textbf{B.
@@
     reflected by \textit{all} regions of topic space (see
-    \textit{\nameref{subsec:knowledge-maps}}). The topic trajectories of each
+    \nameref{subsec:knowledge-maps}). The topic trajectories of each
     lecture and the coordinates of each question are indicated by dotted lines
@@
 video and for each question) into a shared 2-dimensional space (see
-\textit{\nameref{subsec:knowledge-maps}}). Next, we sampled
+\nameref{subsec:knowledge-maps}). Next, we sampled
 points evenly from a $100 \times 100$ grid of coordinates that evenly tiled a
@@
 chosen from the full set of 39, with the constraints that (a) each quiz contain 5
-questions about lecture 1, 5 questions about lecture 2, and 3 questions, and
-(b) each question appear exactly once. The order of questions on each quiz,
+questions about lecture 1, 5 questions about lecture 2, and 3 questions about general physics knowledge, and
+(b) each question appear exactly once for each participant. The order of questions on each quiz,
 and the order of answer options for each question, were also randomized. Our
@@
 \subsubsection*{Constructing text embeddings of multiple lectures and questions}\label{subsec:topic-modeling}
+Following \citet{HeusEtal21}
 

### 2023-01-30 paper/main.tex
update sliding window fig caption to match new layout

@@
 
-\caption{\textbf{Constructing video content \textit{trajectories}. \textbf{A}.
+\caption{\textbf{Modeling course content.} \textbf{A.
 Building a document pool from sliding windows of text.} We decompose each
-video's transcript into a series of overlapping sliding windows. The set of
+lecture's transcript into a series of overlapping sliding windows. The set of
 transcript snippets (across all windows) may be treated as a set of
-``documents'' for training a text embedding model. After training a text
-embedding model on the two videos' sliding windows, we construct ``trajectories''
-through text embedding space by joining the embedding coordinates of successive
-sliding windows from each video. \textbf{B. Embedding multiple videos and
-questions.} Applying the same text embedding approach to each video, along with
-the text of each question in our pool (Tab.~\questions), results in one trajectory per video and one
-embedding coordinate (dot) per question (blue: \textit{Four Fundamental
-Forces}; green: \textit{Birth of Stars}; purple: general physics knowledge). \color{red}{Here
-we have projected the 15-dimensional embeddings into a 3D space using Uniform
-Manifold Approximation and Projection~\citep[UMAP;][]{McInEtal18a}}.}
-
+``documents'' for training a text embedding model.
+\textbf{B.
+Constructing lecture content \textit{trajectories}.}  After training our model on the sliding windows from both lectures, we transform each lecture into a ``trajectory'' through text embedding space by joining the embedding coordinates of successive
+sliding windows parsed from its transcript. \textbf{C. Embedding multiple lectures and
+questions in a shared space.} We apply the same model (trained on the two lectures' windows) to both lectures, along with the text of each question in our pool (Tab.~\questions), to project them into a shared text embedding space.
+This results in one trajectory per lecture and one coordinate for each question.
+Here we have projected the 15-dimensional embeddings onto their first 3 principal components for visualization.}
 \label{fig:sliding-windows}

### 2023-01-30 paper/main.tex
backing up progress, rewrote framing of question-based analyses/results

@@
 
-%\title{Text embedding models reveal high-resolution insights into conceptual
-%knowledge and learning from short multiple-choice quizzes}
-\title{A geometric framework for capturing high-resolution insights into
+\title{Text embedding models enable high-resolution insights into
 conceptual knowledge and learning in classroom-like settings}
@@
 concepts. We test our approach using behavioral data from participants who
-watched two lecture videos from the Khan Academy platform, interleaved
+viewed two lecture videos from the Khan Academy platform, interleaved
 between three short multiple-choice quizzes. We applied our
-framework to the videos' transcripts and the text of the quiz questions to
+framework to the lectures' transcripts and the text of the quiz questions to
 quantify the conceptual content presented in each moment of video and knowledge probed by each quiz question. We used
@@
 small set of quiz questions may be used to obtain rich and meaningful
-high-resolution insights into individual students' knowledge, and how it
+high-resolution insights into individuals' knowledge, and how it
 changes over time as they learn.
@@
 (Fig.~\ref{fig:sliding-windows}A; see \nameref{subsec:topic-modeling}).
-Transforming these windows with our model resulted in a number-of-windows by
+Transforming these windows with our model yielded a number-of-windows by
 number-of-topics (15) topic-proportions matrix, denoting the unique mixture
@@
 topic-proportions matrix) is analogous to a coordinate in a 15-dimensional
-space (whose axes are topics learned by the model). Within this space, each lecture's series of
+space (whose axes are topics discovered by the model). Within this space, each lecture's sequence of
 topic vectors (i.e., corresponding to sliding windows parsed from its
 transcript) forms a \textit{trajectory} that captures how its conceptual
-content unfolds over time (Fig.~\ref{fig:sliding-windows}A). We resampled
+content unfolds over time (Fig.~\ref{fig:sliding-windows}B). We resampled
 these trajectories to a resolution of 1 topic vector for each second of video.
@@
 
-Next, wondered whether we could use this same model to capture the
+Next, we sought to characterize what information participants' performance on each of the three quizzes could provide about their conceptual knowledge at that point in time.
+Traditional approaches to evaluating students' performance on short-form knowledge assessments such as those in our study entail computing the proportion of correctly answered questions to assign a simple numeric score.
+While this may provide some measure of the \textit{extent} of a learner's knowledge, such a score affords little information to either the teacher or the learner about the particular \textit{contents} of their knowledge---in other words, raw ``proportion-correct'' measures may capture \textit{how much} a student knows, but not \textit{what} they know.
+For instance, suppose a participant in our study was highly knowledgeable about fundamental physical forces (i.e., lecture 1 content) but unfamiliar with how stars are formed (i.e., lecture 2 content), while a second participant was unfamiliar with fundamental forces but had extensive prior knowledge about star formation.
+Since quiz 1 (completed before viewing either lecture) contained an equal number of questions about each lecture's content (see Fig.~\ref{fig:experiment}), these two participants could easily achieve the same proportion-correct score despite their conceptual knowledge differing substantially.
+How might we distinguish these individuals?
+
+We hypothesized that our text embedding model, which we had trained on transcripts of the two lectures to characterize their conceptual contents, should also allow us to capture the conceptual knowledge probed by each quiz question.
+Given that the questions were (ostensibly, by design) ``about'' the content of
+
+In other words, given that the questions were (ostensibly, by design) ``about'' one lecture or the other,
 

### 2023-01-30 paper/main.tex
WIP topic variance fig explanation

@@
 Next, we sought to characterize what information participants' performance on each of the three quizzes could provide about their conceptual knowledge at that point in time.
-Traditional approaches to evaluating students' performance on short-form knowledge assessments such as those in our study entail computing the proportion of correctly answered questions to assign a simple numeric score.
-While this may provide some measure of the \textit{extent} of a learner's knowledge, such a score affords little information to either the teacher or the learner about the particular \textit{contents} of their knowledge---in other words, raw ``proportion-correct'' measures may capture \textit{how much} a student knows, but not \textit{what} they know.
+Traditional approaches to evaluating students' performance on short-form knowledge assessments, such as those in our study, entail computing the proportion of correctly answered questions to assign a simple numeric score.
+While this may afford some measure of the \textit{extent} of a learner's knowledge, such a score provides little information to either the teacher or the learner about the particular \textit{contents} of their knowledge---in other words, raw ``proportion-correct'' measures may capture \textit{how much} a student knows, but not \textit{what} they know.
 For instance, suppose a participant in our study was highly knowledgeable about fundamental physical forces (i.e., lecture 1 content) but unfamiliar with how stars are formed (i.e., lecture 2 content), while a second participant was unfamiliar with fundamental forces but had extensive prior knowledge about star formation.
@@
 We hypothesized that our text embedding model, which we had trained on transcripts of the two lectures to characterize their conceptual contents, should also allow us to capture the conceptual knowledge probed by each quiz question.
-Given that the questions were (ostensibly, by design) ``about'' the content of
+If our model successfully represented information about the deeper conceptual content of the lectures (i.e., beyond surface-level details such as particular word choices) then we should be able to recover a correspondence between their embeddings and embeddings of other text that reflect related concepts (e.g., quiz questions that were ostensibly, by design, ``about'' one of the two lecture) despite differences in exact verbiage.
+Intuitively, while the content of each given lecture will naturally vary from moment to moment, the particular combination of dimensions along which its trajectory varies across moments correspond to the topics that encode meaningful ``information''~\citep{Fish22}  about that lecture's dynamic conceptual content.
+We therefore expected that quiz questions pertaining to those same concepts might express the same set of topics.
 
-In other words, given that the questions were (ostensibly, by design) ``about'' one lecture or the other,
-
-Given that we trained the text embedding model using the video transcripts, we
-wondered whether the questions that were (ostensibly, by design) ``about'' the
-content of each lecture would ``match up'' correctly with the lectures. In
-other words, we hoped that the text embeddings would capture something about
-the deeper conceptual content of the lectures, beyond surface details such as
-exact wording choices. If so, when we embed \textit{new} text outside of the
-model's training set, we should see a correspondance between the embeddings of
-the training data (i.e., snippets of text from the lectures' transcripts) and
-other text that reflects related concepts (e.g., questions \textit{about} each
-lecture). Further, although the content from any given moment from a lecture
-might stray from the average content (across all timepoints), we hoped that
-\textit{variability} in each topic's expression over timepoints within a
-lecture would match up with the variability in topic expressions for questions
-about that lecture. Intuitively, the variability in the expression of a given
-topic relates to how much ``information''~\citep{Fish22} the lecture (or
-questions) reflect about that topic. When we compared the variability in topic
+When we compared the variability in topic
 weights across each lecture's timepoints with the variability in topic weights

### 2023-01-30 paper/main.tex
progress on results, split softwraps to hardwraps for shared editing

@@
 models that have only peripheral relevance to the kinds of learning that
-students and teachers actually seek \citep{Macl05, HallGree08}. To help bridge this gap, our study uses
+students and teachers actually seek~\citep{Macl05, HallGree08}. To help bridge this gap, our study uses
 course materials from real online courses to inform, fit, and test models of
@@
 
-We asked participants in our study to complete brief multiple-choice quizzes before, between, and after watching two lecture videos from the Khan Academy \citep{Khan04} platform (Fig.~\ref{fig:experiment}).
+We asked participants in our study to complete brief multiple-choice quizzes before, between, and after watching two lecture videos from the Khan Academy~\citep{Khan04} platform (Fig.~\ref{fig:experiment}).
 The first lecture video, entitled \textit{Four
@@
 them in each of the two lectures. We adapted an approach we developed in prior
-work \citep{HeusEtal21} to extract the latent themes from the lectures' contents
-using a topic model \citep{BleiEtal03}. Briefly, topic models take as input a
+work~\citep{HeusEtal21} to extract the latent themes from the lectures' contents
+using a topic model~\citep{BleiEtal03}. Briefly, topic models take as input a
 collection of text documents and learn a set of ``topics'' (i.e., latent
@@
 
+Next, we sought to characterize what information participants' performance on
+each of the three quizzes could provide about their conceptual knowledge at
+that point in time. Traditional approaches to evaluating students'
+performance on short-form knowledge assessments, such as those in our study,
+entail computing the proportion of correctly answered questions to assign a
+simple numeric score. While this may afford some measure of the
+\textit{extent} of a learner's knowledge, such a score provides little
+information to either the teacher or the learner about the particular
+\textit{contents} of their knowledge---in other words, raw
+``proportion-correct'' measures may capture \textit{how much} a student
+knows, but not \textit{what} they know. For instance, suppose a participant
+in our study was highly knowledgeable about fundamental physical forces (i.e
+., lecture 1 content) but unfamiliar with how stars are formed (i.e., lecture
+2 content), while a second participant was unfamiliar with fundamental forces
+but had extensive prior knowledge about star formation. Since quiz 1
+(completed before viewing either lecture) contained an equal number of
+questions about each lecture's content (see Fig.~\ref{fig:experiment}), these
+two participants could easily achieve the same proportion-correct score
+despite their conceptual knowledge differing substantially. How might we
+distinguish these individuals?
+
 \begin{figure}[tp]
@@
 
-Next, we sought to characterize what information participants' performance on each of the three quizzes could provide about their conceptual knowledge at that point in time.
-Traditional approaches to evaluating students' performance on short-form knowledge assessments, such as those in our study, entail computing the proportion of correctly answered questions to assign a simple numeric score.
-While this may afford some measure of the \textit{extent} of a learner's knowledge, such a score provides little information to either the teacher or the learner about the particular \textit{contents} of their knowledge---in other words, raw ``proportion-correct'' measures may capture \textit{how much} a student knows, but not \textit{what} they know.
-For instance, suppose a participant in our study was highly knowledgeable about fundamental physical forces (i.e., lecture 1 content) but unfamiliar with how stars are formed (i.e., lecture 2 content), while a second participant was unfamiliar with fundamental forces but had extensive prior knowledge about star formation.
-Since quiz 1 (completed before viewing either lecture) contained an equal number of questions about each lecture's content (see Fig.~\ref{fig:experiment}), these two participants could easily achieve the same proportion-correct score despite their conceptual knowledge differing substantially.
-How might we distinguish these individuals?
-
-We hypothesized that our text embedding model, which we had trained on transcripts of the two lectures to characterize their conceptual contents, should also allow us to capture the conceptual knowledge probed by each quiz question.
-If our model successfully represented information about the deeper conceptual content of the lectures (i.e., beyond surface-level details such as particular word choices) then we should be able to recover a correspondence between their embeddings and embeddings of other text that reflect related concepts (e.g., quiz questions that were ostensibly, by design, ``about'' one of the two lecture) despite differences in exact verbiage.
-Intuitively, while the content of each given lecture will naturally vary from moment to moment, the particular combination of dimensions along which its trajectory varies across moments correspond to the topics that encode meaningful ``information''~\citep{Fish22}  about that lecture's dynamic conceptual content.
-We therefore expected that quiz questions pertaining to those same concepts might express the same set of topics.
-
-When we compared the variability in topic
-weights across each lecture's timepoints with the variability in topic weights
-across each question set, we found a strong correspondence
-(Fig.~\ref{fig:topics}). The most variable topics from the \textit{Four
-Fundamental Forces} lecture, and questions about that lecture, are 2, 3, 8, 12,
-13, 14, and 15. The most variable topics from the \textit{Birth of Stars}
-lecture, and questions about that lecture, are 1, 4, 5, 6, and 7. This strong
-overlap between the lectures and questions specifically about each lecture
-indicates that the topic model captures some of the underlying conceptual
-content.
+We hypothesized that our text embedding model, which we had trained on
+transcripts of the two lectures to characterize their conceptual contents,
+should also allow us to capture the conceptual knowledge probed by each quiz
+question. If our model successfully represented information about the deeper
+conceptual content of the lectures (i.e., beyond surface-level details such
+as particular word choices) then we should be able to recover a
+correspondence between their embeddings and embeddings of other text that
+reflect related concepts (e.g., quiz questions that were ostensibly, by
+design, ``about'' one of the two lecture) despite differences in exact
+verbiage. Intuitively, while the content of each given lecture will naturally
+vary from moment to moment, the particular combination of dimensions along
+which its trajectory varies across moments correspond to topics that encode
+meaningful ``information''~\citep{Fish22}  about that lecture's dynamic
+conceptual content. We therefore expected that quiz questions pertaining to
+those same concepts might express the same set of topics.
+
+%Figure~\ref{fig:topics} displays the variability in topic weights across timepoints in each lecture, and across questions in each category (i.e., lecture 1-related, lecture 2-related, and general physics knowledge).
+
+We used our model to transformed the text of each question in our pool into
+the same embedding space as the two lectures' trajectories (Fig
+.~\ref{fig:sliding-windows}C). This yielded a single 15-dimensional
+coordinate (i.e., topic vector) for each question. When we compared the
+variability in topic weights across each lecture's timepoints, and across
+questions from each category (i.e., lecture 1-related, lecture 2-related, and
+general physics knowledge), we found multiple interesting patterns. First,
+there is a strong correspondence between the sets of topics expressed by each
+lecture and its relevant questions. This indicates that our model is
+sensitive to the underlying conceptual content tested by different question,
+and should allow us to differentially assess participants' knowledge for the
+two lectures based on the \textit{specific} questions they answered correctly
+or incorrectly on each quiz. Second, the topics expressed by the general
+physics knowledge questions comprise a nonspecific mix of topics from the two
+lectures (4 from lecture 1; 5 from lecture 2), most of which are expressed to
+a relatively low degree. This indicates that our model should enable us to
+discriminate questions that are highly relevant to our assessment of
+participants' knowledge about concepts from the lectures from those that are
+not (or potentially less so). Third, the two lectures' trajectories vary
+along largely non-overlapping topic dimensions (e.g., variations in weight
+for topics 2, 3, 8, 12, 13, and 15 are specific to lecture 1; variations in
+weight for topics 1, 4, 5, 6, 7, and 10 are specific to lecture 2), but also
+share a small number of expressed topics in common (topics 11 and 14). This 
+indicates that our lecture is able to simultaneously capture
 
@@
 \subsubsection*{Constructing text embeddings of multiple lectures and questions}\label{subsec:topic-modeling}
-Following \citet{HeusEtal21}
+Following~\citet{HeusEtal21}
 

### 2023-01-31 paper/main.tex
finished fig 3 section

@@
 
-\begin{figure}[tp]
-    \centering
-    \includegraphics[width=0.7\textwidth]{figs/active-topics}
-
-\caption{\textbf{Lecture and question topic overlap.} The bar plots display the
-variability in topic weights across lecture timepoints (top panels) and
-questions (bottom panels); colors denote topics. The top-weighted words from
-the most ``expressive'' (i.e., variable across observations) topic from each
-lecture are displayed in the upper right (orange: topic 2; yellow-green: topic
-4). The top-weighted words from the full set of topics may be found in
-Table~\topics.}
-
-    \label{fig:topics}
-\end{figure}
-
 We hypothesized that our text embedding model, which we had trained on
@@
 correspondence between their embeddings and embeddings of other text that
-reflect related concepts (e.g., quiz questions that were ostensibly, by
+reflects related concepts (e.g., quiz questions that were ostensibly, by
 design, ``about'' one of the two lecture) despite differences in exact
@@
 
-%Figure~\ref{fig:topics} displays the variability in topic weights across timepoints in each lecture, and across questions in each category (i.e., lecture 1-related, lecture 2-related, and general physics knowledge).
-
-We used our model to transformed the text of each question in our pool into
-the same embedding space as the two lectures' trajectories (Fig
-.~\ref{fig:sliding-windows}C). This yielded a single 15-dimensional
-coordinate (i.e., topic vector) for each question. When we compared the
-variability in topic weights across each lecture's timepoints, and across
+\begin{figure}[tp]
+    \centering
+    \includegraphics[width=\textwidth]{figs/active-topics}
+
+\caption{\textbf{Lecture and question topic overlap.} \textbf{A. Topic 
+weight variability}. The bar plots display the variance of each topic's weight 
+across lecture timepoints (top row) and questions (bottom row); colors 
+denote topics. The top-weighted words from the most ``expressive'' (i.e., 
+variable across observations) topic from each lecture are displayed in the 
+upper right (orange: topic 2; yellow-green: topic 4). The top-weighted words 
+from the full set of topics may be found in Table~\topics.
+\textbf{B.
+Relationships between topic weight variability.} Pairwise correlations between the distributions of topic weight variance for each lecture and question category.
+Each row/column corresponds to a bar plot in panel A.}
+
+    \label{fig:topics}
+\end{figure}
+
+We used our model to transform the text of each question in our pool into
+the same embedding space as the two lectures' trajectories 
+(Fig.~\ref{fig:sliding-windows}C). This yielded a single 15-dimensional
+coordinate (i.e., topic vector) for each question. We then computed the variance
+of each topic's weight across timepoints of each lecture, and across 
 questions from each category (i.e., lecture 1-related, lecture 2-related, and
-general physics knowledge), we found multiple interesting patterns. First,
-there is a strong correspondence between the sets of topics expressed by each
-lecture and its relevant questions. This indicates that our model is
-sensitive to the underlying conceptual content tested by different question,
-and should allow us to differentially assess participants' knowledge for the
-two lectures based on the \textit{specific} questions they answered correctly
-or incorrectly on each quiz. Second, the topics expressed by the general
-physics knowledge questions comprise a nonspecific mix of topics from the two
-lectures (4 from lecture 1; 5 from lecture 2), most of which are expressed to
-a relatively low degree. This indicates that our model should enable us to
-discriminate questions that are highly relevant to our assessment of
-participants' knowledge about concepts from the lectures from those that are
-not (or potentially less so). Third, the two lectures' trajectories vary
-along largely non-overlapping topic dimensions (e.g., variations in weight
-for topics 2, 3, 8, 12, 13, and 15 are specific to lecture 1; variations in
-weight for topics 1, 4, 5, 6, 7, and 10 are specific to lecture 2), but also
-share a small number of expressed topics in common (topics 11 and 14). This 
-indicates that our lecture is able to simultaneously capture
+general physics knowledge; Fig.~\ref{fig:topics}A). Visual inspection of 
+Figure~\ref{fig:topics}A reveals a strong correspondence between the sets of 
+topics expressed by each lecture and its related questions, as well as limited 
+overlap in the topics expressed by non-matched lecture-question set pairs. 
+To quantify these apparent similarities and differences, we computed the correlation 
+between each pair of topic-weight variance distributions (Fig.~\ref{fig:topics}B). 
+We found that our model captured the contents of lecture-related questions 
+using a weighted blend of topic dimensions that was highly similar to that of 
+their reference lecture (\textit{Four Fundamental Forces} (\textit{FFF}) 
+questions vs.~lecture: Pearson's $r(13) = 
+0.824,~p<0.001,~95\%~\mathrm{confidence~interval~(CI)} = [0.696, 0.973]$; 
+\textit{Birth of Stars} (\textit{BoS}) questions vs.~lecture: $r(13) = 
+0.801,~p<0.001,~95\%~\mathrm{CI} = [0.539, 0.958]$) but diverged significantly 
+from that of the non-reference lecture (\textit{FFF} questions vs.~\textit{BoS} 
+lecture: $r(13) = -0.620,~p = 0.014,~95\%~\mathrm{CI} = [-0.871, -0.326]$; 
+\textit{BoS} questions vs.~\textit{FFF} lecture: $r(13) = -0.550,~p = 
+0.034,~95\%~\mathrm{CI} = [-0.803, -0.246]$). This indicated that our model 
+was sufficiently sensitive to the conceptual content tested by different quiz questions to differentiate between those relating to one lecture versus the other, and allow us to
+
+sensitive to the underlying conceptual 
+content tested by different question,and should allow us to differentially assess 
+participants' knowledge for the two lectures based on the \textit{specific}
+questions they answered correctly or incorrectly on each quiz.
+%When we compared the
+%variability in topic weights across each lecture's timepoints, and across
+%questions from each category (i.e., lecture 1-related, lecture 2-related, and
+%general physics knowledge), we found multiple interesting patterns (Fig.~\ref{fig:topics}). First,
+%there is a strong correspondence between the sets of topics expressed by each
+%lecture and its relevant questions. This indicates that our model is
+%sensitive to the underlying conceptual content tested by different question,
+%and should allow us to differentially assess participants' knowledge for the
+%two lectures based on the \textit{specific} questions they answered correctly
+%or incorrectly on each quiz. Second, the topics expressed by the general
+%physics knowledge questions comprise a nonspecific mix of topics from the two
+%lectures (4 from lecture 1; 5 from lecture 2), most of which are expressed to
+%a relatively low degree. This indicates that our model should enable us to
+%discriminate questions that are highly relevant to our assessment of
+%participants' knowledge about concepts from the lectures from those that are
+%not (or potentially less so). Third, the two lectures' trajectories vary
+%along largely non-overlapping topic dimensions (e.g., variations in weight
+%for topics 2, 3, 8, 12, 13, and 15 are specific to lecture 1; variations in
+%weight for topics 1, 4, 5, 6, 7, and 10 are specific to lecture 2), but also
+%share a small number of expressed topics in common (topics 11 and 14). This
+%indicates that our lecture is able to simultaneously capture
 
@@
     \includegraphics[width=\textwidth]{figs/lecture-question-similarity}
-
     \caption{\textbf{Which parts of each lecture are captured by each
@@
 
-Although a single lecture may be organized around a single broad theme at a
+Although an individual lecture may be organized around a single broad theme at a
 coarse scale, at a finer scale each moment of a lecture typically covers a

### 2023-01-31 paper/supplement.tex
quick fixes to supplement

@@
 &                                                                                                                              Ignition &                                                                                            Combustion &                                                                                                              Decomposition &                                                                                                                      Displacement \\\hline
-    31    &      GK &                                                                                                                                                                                                   Which of the following lists of particles is ordered from smallest to largest?
+    31    &      GPK &                                                                                                                                                                                                   Which of the following lists of particles is ordered from smallest to largest?
 &                                                                                                       Electron, proton, nucleus, atom &                                                                       Atom, electron, proton, nucleus &                                                                                           Electron, nucleus, atom, neutron &                                                                                                  Neutron, nucleus, electron, atom \\\hline
-    32    &      GK &                                                                                                                                                                                                                          Which of the following defines what element an atom is?
+    32    &      GPK &                                                                                                                                                                                                                          Which of the following defines what element an atom is?
 &                                                                                                                 Its number of protons &                                                                                Its number of neutrons &                                                                                                    Its number of electrons &                                                                                                                          Its mass \\\hline
-    33    &      GK &                                                                                                                                                                    Suppose that in some atom, a proton is converted into a neutron.
+    33    &      GPK &                                                                                                                                                                    Suppose that in some atom, a proton is converted into a neutron.
 What changes as a result of this conversion?
 &                                                                                                                    The atom's element &                                                                The atom's mass (in atomic mass units) &                                                                                                        The atom's velocity &                                                                                                                The atom's density \\\hline
-    34    &      GK &                                                                                                                                                                                                                Which of the following lists is ordered from smallest to largest?
+    34    &      GPK &                                                                                                                                                                                                                Which of the following lists is ordered from smallest to largest?
 &                                                                                                  Star, solar system, galaxy, universe &                                                             Galaxy, solar system, Milky Way, universe &                                                                                         Planet, galaxy, star, solar system &                                                                                             Earth, solar system, universe, galaxy \\\hline
-    35    &      GK &                                                                                                                                                                                                                    Which of the following are located in the nucleus of an atom?
+    35    &      GPK &                                                                                                                                                                                                                    Which of the following are located in the nucleus of an atom?
 &                                                                                                                  Protons and neutrons &                                                                                          Only protons &                                                                                                             Only electrons &                                                                                                            Neutrons and electrons \\\hline
-    36    &      GK &                                                                                                                                                                                                                                       Which of the following has the least mass?
+    36    &      GPK &                                                                                                                                                                                                                                       Which of the following has the least mass?
 &                                                                                                                           An electron &                                                                                              A proton &                                                                                                                  A neutron &                                                                                                                   A hydrogen atom \\\hline
-    37    &      GK &                                                                                                                                                                                                                         What percent of an atom's space does its nucleus occupy?
+    37    &      GPK &                                                                                                                                                                                                                         What percent of an atom's space does its nucleus occupy?
 &                                                                                                                          Less than 1\% &                                                                                                   10\% &                                                                                                                        50\% &                                                                                                                     More than 90\% \\\hline
-    38    &      GK &                                                                                                                                                                              In the famous equation attributed to Albert Einstein, E = mc\textasciicircum 2, what does the letter "m" represent?
+    38    &      GPK &                                                                                                                                                                              In the famous equation attributed to Albert Einstein, E = mc\textasciicircum 2, what does the letter "m" represent?
 &                                                                                                                                  Mass &                                                                                              Momentum &                                                                                                          Moment of inertia &                                                                                                                             Moles \\\hline
-    39    &      GK &                                                                                                                                                                                                If I were to heat up an inflated balloon, which of the the following would occur?
+    39    &      GPK &                                                                                                                                                                                                If I were to heat up an inflated balloon, which of the the following would occur?
 &                                                                                                              The balloon would expand &                                                                              The balloon would shrink &                                                                                          None of these answers are correct &                                        The balloon could expand or shrink depending on whether it's filled with air or helium gas \\
@@
     \caption{\textbf{Question pool.} Each participant answered questions on
-    three 30-question quizzes. Ten questions from each question set were
-    included on each quiz: questions about the \textit{Four Fundamental Forces}
-    lecture (FFF), questions about the \textit{Birth of Stars} lecture (BoS),
-    and questions about general physics knowledge (GK). Each question appeared
+    three 13-question quizzes. Each quiz included 5 questions about the \textit{Four Fundamental Forces}
+    lecture (FFF), 5 questions about the \textit{Birth of Stars} lecture (BoS),
+    and 3 questions about general physics knowledge (GPK). Each question appeared
     on at most one quiz (for each participant).}

### 2023-01-31 paper/main.tex

@@
 general physics knowledge; Fig.~\ref{fig:topics}A). Visual inspection of 
-Figure~\ref{fig:topics}A reveals a strong correspondence between the sets of 
-topics expressed by each lecture and its related questions, as well as limited 
+Figure~\ref{fig:topics}A suggests a strong correspondence between the sets of 
+topics expressed by each lecture and its related questions, with only limited 
 overlap in the topics expressed by non-matched lecture-question set pairs. 
@@
 between each pair of topic-weight variance distributions (Fig.~\ref{fig:topics}B). 
-We found that our model captured the contents of lecture-related questions 
-using a weighted blend of topic dimensions that was highly similar to that of 
+We found that our model represented the contents of lecture-related questions 
+using a combination of topic dimensions (and relative variation along those topic dimensions) that was highly similar to that of 
 their reference lecture (\textit{Four Fundamental Forces} (\textit{FFF}) 
@@
 0.034,~95\%~\mathrm{CI} = [-0.803, -0.246]$). This indicated that our model
-was sufficiently sensitive to the conceptual content tested by different quiz questions to differentiate between those relating to one lecture versus the other, and allow us to
-
-sensitive to the underlying conceptual 
-content tested by different question,and should allow us to differentially assess 
-participants' knowledge for the two lectures based on the \textit{specific}
-questions they answered correctly or incorrectly on each quiz.
+captured the conceptual contents of the lectures and quiz questions 
+sufficiently well to differentiate between questions relating to one lecture 
+versus the other.
+
+%This indicated that our model
+%captures the conceptual contents of the lectures and quiz questions 
+%sufficiently well to differentiate between questions relating to one lecture 
+%versus the other, and could potentially be used to assess participants' knowledge for each lecture
+
+% , and could be used to assess participants' knowledge about
+%each lecture independently, based on the \textit{specific} questions they
+%answered correctly or incorrectly on each quiz. 
+%providing a slightly more 
+%nuanced measure of what concepts they do and do not know than a simple 
+%proportion-correct score.
+
 %When we compared the
@@
 
+This could enable us to estimate participants' knowledge for each of the two lectures, separately, by
+
+This aspect of our model could enable us to assess participants' knowledge for each lecture separately, based on which \textit{specific} questions they answered right on wrong on each quiz, providing a slightly more refined estimate of the concepts they do and do not know than single proportion-correct score.
+However, while lectures are often organized around a single, broad theme at a coarse timescale, they typically cover...
+%While individual lectures may be organized around a single broad theme at a coarse scale,
+
+\textcolor{red}{\textbf{Paxton stopped here}}
+
 \begin{figure}[tp]
@@
     question identities. The diamonds in each panel denote the moment of peak
-    correlation between the indicated questions, in the indicated lectures. The
-    associated questions' text, and snippets of the lectures' transcripts in
-    the best-matching sliding windows, are displayed at the bottom of the
+    correlation between the indicated question and the lecture trajectory. The
+    associated questions' text and snippets of the lectures' transcripts from the surrounding 30 seconds, are displayed at the bottom of the
     figure.}
@@
     Word clouds for sampled points in topic space.} Each word cloud displays
-    the relative weights of each word reflected by the blend of topics
+    the relative weights of each word (via their relative sizes) reflected by the blend of topics
     represented at the locations of the stars in the maps. The words' colors
-    indicate how much each word is weighted on average across all timepoints'
+    indicate how much each word is weighted, on average, across all timepoints'
     topic vectors in the \textit{Four Fundamental Forces} (blue) and
@@
 Equation~\ref{eqn:rbf-knowledge} to estimate participants' knowledge at each of
-these 10K sampled locations, and we averaged these estimates across
+these 10,000 sampled locations, and we averaged these estimates across
 participants to obtain an estimated average \textit{knowledge map}
@@
 Because the 2D projection we used to construct the knowledge and learning maps
-is (partially) invertible, we may gain additional insights into the estimates
+is invertible, we may gain additional insights into the estimates
 by reconstructing the original high-dimensional topic vectors for any point(s)
@@
 For example, we can ask: what makes an effective course or training program?
-Which aspects of teaching might be optimized or automated? How and why do
+Which aspects of teaching might be optimized or automated? How can we provide  How and why do
 learning needs and goals vary across people? How might we lower barriers to
@@
 \subsubsection*{Constructing text embeddings of multiple lectures and questions}\label{subsec:topic-modeling}
-Following~\citet{HeusEtal21}
-
 We adapted an approach we developed in prior work~\citep{HeusEtal21} to embed
 each moment of the two lectures and each question in our pool in a common representational space.
-Briefly, our approach uses a topic model~\citep[Latent Dirichlet Allocation;][]{BleiEtal03},
-fit to a corpus of documents to discover a set of $k$ ``topics'' or ``themes'' from their contents.
-Formally, each topic is defined as a set of weights over each word in the model's vocabulary
-(i.e., the union of all unique words, across all documents, excluding ``stop
-words.'').
-
-We adapted an approach we developed in prior work~\citep{HeusEtal21} to embed
-each moment of the two lectures and each question in our pool in a common representational space.
-Briefly, our approach uses a topic model~\citep[Latent Dirichlet Allocation;][]{BleiEtal03}, trained on a set
+Briefly, our approach uses a topic model (Latent Dirichlet Allocation;~\citealp{BleiEtal03}), trained on a set
 of documents, to discover a set of $k$ ``topics'' or ``themes.'' Formally, each
@@
 
-%\begin{figure}[tp]
-%\centering
-%\includegraphics[width=\textwidth]{figs/sliding_windows}
-%
-%\caption{\textbf{Constructing video content \textit{trajectories}. \textbf{A}.
-%Building a document pool from sliding windows of text.} We decompose each
-%video's transcript into a series of overlapping sliding windows. The set of
-%transcript snippets (across all windows) may be treated as a set of
-%``documents'' for training a text embedding model. After training a text
-%embedding model on the two videos' sliding windows, we construct ``trajectories''
-%through text embedding space by joining the embedding coordinates of successive
-%sliding windows from each video. \textbf{B. Embedding multiple videos and
-%questions.} Applying the same text embedding approach to each video, along with
-%the text of each question in our pool (Tab.~\questions), results in one trajectory per video and one
-%embedding coordinate (dot) per question (blue: \textit{Four Fundamental
-%Forces}; green: \textit{Birth of Stars}; purple: general physics knowledge). \color{red}{Here
-%we have projected the 15-dimensional embeddings into a 3D space using Uniform
-%Manifold Approximation and Projection~\citep[UMAP;][]{McInEtal18a}}.}
-%
-%\label{fig:sliding-windows}
-%\end{figure}
-
-As illustrated in Figure~\ref{fig:sliding-windows}A, we first
-
 As illustrated in Figure~\ref{fig:sliding-windows}A, we start by building up a
 corpus of documents using overlapping sliding windows that span each video's
-transcript.
-Khan Academy provides professionally created, manual transcriptions of all videos for closed captioning.
-However, such transcripts would not be readily available in all contexts to which our framework could potentially be applied.
-Khan Academy videos are hosted on the YouTube platform, which additionally provides automated transcripts
-
-Khan Academy videos are hosted on the YouTube platform, and all
-YouTube videos are run through Google's speech-to-text API~\citep{HalpEtal16}
-to derive a timestamped transcript of any detected speech in the video. The
-resulting transcripts contain one timestamped row per line, and each line
-generally corresponds to a few seconds of spoken content from the video. We
-defined a sliding window length of (up to) $w = 30$ transcript lines, and we
-assigned each window a timestamp according to the midpoint between its first
+transcript. Khan Academy provides professionally created, manual 
+transcriptions of all videos for closed captioning. However, such transcripts 
+would not be readily available in all contexts to which our framework could 
+potentially be applied. Khan Academy videos are hosted on the YouTube 
+platform, which additionally provides automated captions. We opted to use 
+these automated transcripts (which, in prior work, we have found are 
+sufficiently near-human quality yield reliable data in behavioral studies; 
+\citealp{ZimaEtal18}) when developing our framework in order to make it 
+more easily extensible and adaptable by others in the future.
+
+We fetched these automated transcripts using the \texttt{youtube-transcript-api} 
+Python package (\textcolor{red}{\textbf{Jeremy can you add a citation for this?} 
+https://github.com/jdepoix/youtube-transcript-api}). The transcripts consisted of 
+one timestamped line of text for every few seconds (mean: 2.34s; standard 
+deviation: 0.83s) of spoken content in the video (i.e., corresponding to each 
+individual caption that would appear on-screen if viewing the lecture via YouTube, 
+and when those lines would appear). We
+defined a sliding window length of (up to) $w = 30$ transcript lines, and
+assigned each window a timestamp corresponding to the midpoint between its first
 and last lines' timestamps. These sliding windows ramped up and down in length
@@
 each line of the transcript appeared in the same number ($w$) of sliding
-windows. We treated the text from each sliding window as a single ``document,''
+windows. After performing various standard text preprocessing (e.g., normalizing case, 
+lemmatizing, removing punctuation and stop-words), we treated the text from each 
+sliding window as a single ``document,''
 and we combined these documents across the two videos' windows to create a single
@@
 reflect similar themes, according to the model) will yield similar (in terms of
-Euclidean distance, correlation, etc.) topic vectors. In general, the
+Euclidean \textcolor{red}{should we say something like cosine instead of euclidean?} distance, correlation, etc.) topic vectors. In general, the
 similarity between different documents' topic vectors may be used to
@@
 linear interpolation (independently for each topic dimension) to resample the
-resulting timeseries to once per second. This yielded a single topic vector for
-each second of each video. We also used the fitted model to obtain topic
+resulting timeseries to one vector per second. We also used the fitted model to obtain topic
 vectors for each question in our pool (Tab.~\questions). Taken together, we
@@
 topic space, and a single coordinate for each question
-(Fig.~\ref{fig:sliding-windows}B). Embedding both videos and all of the
+(Fig.~\ref{fig:sliding-windows}C). Embedding both videos and all of the
 questions using a common model enables us to compare the content from different
@@
 correlations between any lecture timepoint and question, taken over all
-timepoints and questions across both lectures and all three question sets. We
+timepoints and questions across both lectures and all five question used to estimate the knowledge trace \textcolor{red}{\textbf{Note: make sure this is correct in results section; not sure i caught all instances}}.
+We
 also define $f(s, \Omega)$ as the $s$\textsuperscript{th} topic vector from the
 set of topic vectors $\Omega$. Here $t$ indexes the set of lecture topic
-vectors, $L$, and $i$ and $j$ index the topic vectors of questions in the
-quiz's question set, $Q$. Note that ``correct'' denotes the set of indices of
+vectors, $L$, and $i$ and $j$ index the topic vectors of questions used to estimate the knowledge trace, $Q$. Note that ``correct'' denotes the set of indices of
 the questions the participant answered correctly on the given quiz.
@@
 topic vector for one question, $y$), normalized by the minimum and maximum
-correlations (across all timepoints and questions) to range between 0 and 1,
+correlations (across all timepoints $t$ and questions $Q$) to range between 0 and 1,
 inclusive. Equation~\ref{eqn:prop} then computes the weighted average
@@
 The normalization step (i.e., using $\mathrm{ncorr}$ instead of the raw
-correlations) insures that every question (except the least-relevant question)
+correlations) insures that every question
 contributes some non-zero amount to the knowledge estimate.
@@
 model and participants' quiz performance on each question, we can estimate
-their knowledge about \textit{any} content expressible by the embedding model--
-not solely the content explicitly probed by the quiz questions. To visualize
-these estimates
+their knowledge about \textit{any} content expressible by the embedding 
+model---not solely the content explicitly probed by the quiz questions or even 
+appearing in the lectures. To visualize these estimates
 (Figs.~\ref{fig:knowledge-maps},~\individualKnowledgeMapsA,~\individualKnowledgeMapsB,~\individualKnowledgeMapsC,~\individualLearningMapsA,
-and~\individualLearningMapsB), we used UMAP~\citep{McInEtal18a} to define a 2D
+and~\individualLearningMapsB), we used Uniform Manifold Approximation and Projection (UMAP; \citealp{McInEtal18a}) to construct a 2D
 projection of the text embedding space. Sampling the original 100-dimensional
@@
 enclosing rectangle. We sought to estimate participants' knowledge (and
-learning---i.e., changes in knowledge) at each of the resulting 10000
+learning, i.e., changes in knowledge) at each of the resulting 10,000
 coordinates.

### 2023-01-31 paper/main.tex
initial round of edits (incomplete)

@@
 
-\title{Text embedding models enable high-resolution insights into
-conceptual knowledge and learning in classroom-like settings}
+\title{Text embedding models reveal high resolution insights into conceptual
+knowledge from short multiple choice quizzes}
 
@@
 
-\begin{abstract}\noindent We develop a mathematical framework, based on natural language
-processing models, for tracking and characterizing the acquisition of
-conceptual knowledge in real-world educational contexts. Our approach embeds
-course content in a high-dimensional
-conceptual space, where nearby coordinates reflect similar or related
+\begin{abstract}\noindent We develop a mathematical framework, based on natural
+language processing models, for tracking and characterizing the acquisition of
+conceptual knowledge. Our approach embeds each concept in a high dimensional
+representation space, where nearby coordinates reflect similar or related
 concepts. We test our approach using behavioral data from participants who
-viewed two lecture videos from the Khan Academy platform, interleaved
-between three short multiple-choice quizzes. We applied our
-framework to the lectures' transcripts and the text of the quiz questions to
-quantify the conceptual content presented in each moment of video and knowledge probed by each quiz question. We used
+answered small sets of multiple choice quiz questions interleaved between
+watching two course videos from the Khan Academy platform. We applied our
+framework to the videos' transcripts, and to text of the quiz questions, to
+quantify the content of each moment of video and each quiz question. We used
 these embeddings, along with participants' quiz responses, to track how the
-learners' knowledge changed after watching each video. Our findings demonstrate how a
-small set of quiz questions may be used to obtain rich and meaningful
-high-resolution insights into individuals' knowledge, and how it
+learners' knowledge changed after watching each video. Our findings show how a
+small set of quiz questions may be used to obtain rich and meaningful high
+resolution insights into what each learner knows, and how their knowledge
 changes over time as they learn.
@@
 
-Suppose that a teacher had access to a complete ``map'' of everything a
-student knew. Defining what such a map might even look like, let alone how it
+Suppose that a teacher had access to a complete tangible ``map'' of everything
+a student knew. Defining what such a map might even look like, let alone how it
 might be constructed or filled in, is itself a non-trivial problem. But if a
 teacher \textit{were} to gain access to such a map, how might it change their
-ability to teach that student? Perhaps they might start by checking how well the
-student knew the to-be-learned information already, or how much they knew about
-related concepts. For some students, they could potentially optimize their
-teaching efforts to maximize efficiency by focusing primarily on not-yet-known
-content. For other students (or other content areas), it might be more
-effective to optimize for direct connections between already known content and
-new material. Observing how the student's knowledge changed over time,
-in response to their teaching, could also help to guide the teacher towards
-the most effective strategy for that individual student.
+ability to teach that student? Perhaps they might start by checking how well
+the student knew the to-be-learned information already, or how much they knew
+about related concepts. For some students, they could potentially optimize
+their teaching efforts to maximize efficiency by focusing primarily on
+not-yet-known content. For other students (or other content areas), it might be
+more effective to optimize for direct connections between already known content
+and new material. Observing how the student's knowledge changed over time, in
+response to their teaching, could also help to guide the teacher towards the
+most effective strategy for that individual student.
 
@@
 Our primary research goal is to advance our understanding of what it means to
-acquire deep, real-world conceptual knowledge. Traditional laboratory approaches
-to studying learning and memory (e.g., list learning studies) often draw little
-distinction between memorization and understanding. Instead, these studies
-typically focus on whether information is effectively encoded or retrieved,
-rather than whether the information is \textit{understood}. Approaches to
-studying conceptual learning, such as category learning experiments, can begin
-to investigate the distinction between memorization and understanding, often by
-training participants to distinguish arbitrary or random features in otherwise
-meaningless categorized stimuli. However the objective of real-world training,
-or learning from life experiences more generally, is often to develop new
-knowledge that may be applied in \textit{useful} ways in the future. In this
-sense, the gap between modern learning theories and modern pedagogical
-approaches and classroom learning strategies is enormous: most of our theories
-about \textit{how} people learn are inspired by experimental paradigms and
-models that have only peripheral relevance to the kinds of learning that
-students and teachers actually seek~\citep{Macl05, HallGree08}. To help bridge this gap, our study uses
-course materials from real online courses to inform, fit, and test models of
-real-world conceptual learning. We also provide a
-demonstration of how our models can be used to construct ``maps'' of what
-students know, and how their knowledge changes with training. In addition to
-helping to visualize knowledge (and changes in knowledge), we hope that such
-maps might lead to real-world tools for improving how we educate.
+acquire deep, real-world conceptual knowledge. Traditional laboratory
+approaches to studying learning and memory (e.g., list learning studies) often
+draw little distinction between memorization and understanding. Instead, these
+studies typically focus on whether information is effectively encoded or
+retrieved, rather than whether the information is \textit{understood}.
+Approaches to studying conceptual learning, such as category learning
+experiments, can begin to investigate the distinction between memorization and
+understanding, often by training participants to distinguish arbitrary or
+random features in otherwise meaningless categorized stimuli. However the
+objective of real-world training, or learning from life experiences more
+generally, is often to develop new knowledge that may be applied in
+\textit{useful} ways in the future. In this sense, the gap between modern
+learning theories and modern pedagogical approaches and classroom learning
+strategies is enormous: most of our theories about \textit{how} people learn
+are inspired by experimental paradigms and models that have only peripheral
+relevance to the kinds of learning that students and teachers actually
+seek~\citep{Macl05, HallGree08}. To help bridge this gap, our study uses course
+materials from real online courses to inform, fit, and test models of
+real-world conceptual learning. We also provide a demonstration of how our
+models can be used to construct ``maps'' of what students know, and how their
+knowledge changes with training. In addition to helping to visualize knowledge
+(and changes in knowledge), we hope that such maps might lead to real-world
+tools for improving how we educate.
 
@@
 
-We asked participants in our study to complete brief multiple-choice quizzes before, between, and after watching two lecture videos from the Khan Academy~\citep{Khan04} platform (Fig.~\ref{fig:experiment}).
-The first lecture video, entitled \textit{Four
-Fundamental Forces}, discussed the four fundamental forces in physics: gravity,
-strong and weak interactions, and electromagnetism. The second,
-entitled \textit{Birth of Stars}, provided an overview of our current
-understanding of how stars form.
-We selected these lessons to be (a) accessible
-to a broad audience, i.e., requiring minimal prerequisite knowledge to understand;
-(b) conceptually related to each other, i.e., covering at least \textit{some}
-similar or overlapping content; and (c) largely independent of each other, i.e., focused
-on sufficiently different material that understanding one did not require having seen
-the other. The two videos we selected are introductory lectures that both
-belong to Khan Academy's ``Cosmology and Astronomy'' course domain, but are taken from
-different lecture series (``Scale of the Universe'' and ``Stars, Black Holes, and Galaxies''
-for the first and second lectures, respectively).
-
-We then created a pool of
-multiple-choice quiz questions that would enable us to test participants'
-knowledge about each individual lecture, as well as related content not
-specifically presented in either video ( see Tab.~\questions). Participants answered
-questions randomly drawn from each content area (lecture 1, lecture 2, and
-general physics knowledge) on each of the three quizzes. Quiz 1 was intended to
-assess participants' ``baseline'' knowledge before training, quiz 2 assessed knowledge
-after watching the \textit{Four Fundamental Forces} video (i.e., lecture 1),
-and quiz 3 assessed knowledge after watching the \textit{Birth of Stars} video
-(i.e., lecture 2).
+We asked participants in our study to complete brief multiple-choice quizzes
+before, between, and after watching two lecture videos from the Khan
+Academy~\citep{Khan04} platform (Fig.~\ref{fig:experiment}). The first lecture
+video, entitled \textit{Four Fundamental Forces}, discussed the four
+fundamental forces in physics: gravity, strong and weak interactions, and
+electromagnetism. The second, entitled \textit{Birth of Stars}, provided an
+overview of our current understanding of how stars form. We selected these
+lessons to be (a) accessible to a broad audience, i.e., requiring minimal
+prerequisite knowledge to understand; (b) conceptually related to each other,
+i.e., covering at least \textit{some} similar or overlapping content; and (c)
+largely independent of each other, i.e., focused on sufficiently different
+material that understanding one did not require having seen the other. The two
+videos we selected are introductory lectures that both belong to Khan Academy's
+``Cosmology and Astronomy'' course domain, but are taken from different lecture
+series (``Scale of the Universe'' and ``Stars, Black Holes, and Galaxies'' for
+the first and second lectures, respectively).
+
+We created a pool of multiple-choice quiz questions that would enable us to
+evaluate participants' knowledge about each individual lecture along with
+related content not specifically presented in either video (see
+Tab.~\questions). Participants answered questions randomly drawn from each
+content area (lecture 1, lecture 2, and general physics knowledge) on each of
+the three quizzes. Quiz 1 was intended to assess participants' ``baseline''
+knowledge before training, quiz 2 assessed knowledge after watching the
+\textit{Four Fundamental Forces} video (i.e., lecture 1), and quiz 3 assessed
+knowledge after watching the \textit{Birth of Stars} video (i.e., lecture 2).
 
@@
 
-\caption{\textbf{Modeling course content.} \textbf{A.
-Building a document pool from sliding windows of text.} We decompose each
-lecture's transcript into a series of overlapping sliding windows. The set of
-transcript snippets (across all windows) may be treated as a set of
-``documents'' for training a text embedding model.
-\textbf{B.
-Constructing lecture content \textit{trajectories}.}  After training our model on the sliding windows from both lectures, we transform each lecture into a ``trajectory'' through text embedding space by joining the embedding coordinates of successive
-sliding windows parsed from its transcript. \textbf{C. Embedding multiple lectures and
-questions in a shared space.} We apply the same model (trained on the two lectures' windows) to both lectures, along with the text of each question in our pool (Tab.~\questions), to project them into a shared text embedding space.
-This results in one trajectory per lecture and one coordinate for each question.
-Here we have projected the 15-dimensional embeddings onto their first 3 principal components for visualization.}
+\caption{\textbf{Modeling course content.} \textbf{A. Building a document pool
+from sliding windows of text.} We decompose each lecture's transcript into a
+series of overlapping sliding windows. The set of transcript snippets (across
+all windows) may be treated as a set of ``documents'' for training a text
+embedding model. \textbf{B. Constructing lecture content
+\textit{trajectories}.} After training our model on the sliding windows from
+both lectures, we transform each lecture into a ``trajectory'' through text
+embedding space by joining the embedding coordinates of successive sliding
+windows parsed from its transcript. \textbf{C. Embedding multiple lectures and
+questions in a shared space.} We apply the same model (trained on the two
+lectures' windows) to both lectures, along with the text of each question in
+our pool (Tab.~\questions), to project them into a shared text embedding space.
+This results in one trajectory per lecture and one coordinate for each
+question. Here we have projected the 15-dimensional embeddings onto their first
+3 principal components for visualization.}
+
 \label{fig:sliding-windows}
@@
 them in each of the two lectures. We adapted an approach we developed in prior
-work~\citep{HeusEtal21} to extract the latent themes from the lectures' contents
-using a topic model~\citep{BleiEtal03}. Briefly, topic models take as input a
-collection of text documents and learn a set of ``topics'' (i.e., latent
-themes) from their contents. Once fit, a topic model can be used to transform
-arbitrary (potentially new) documents into sets of ``topic proportions,''
-describing the weighted blend of learned topics reflected in their texts. We
-parsed automatically generated transcripts of the two lectures into
-overlapping sliding windows, which we treated as documents to fit our model
+work~\citep{HeusEtal21} to extract the latent themes from the lectures'
+contents using a topic model~\citep{BleiEtal03}. Briefly, topic models take as
+input a collection of text documents and learn a set of ``topics'' (i.e.,
+latent themes) from their contents. Once fit, a topic model can be used to
+transform arbitrary (potentially new) documents into sets of ``topic
+proportions,'' describing the weighted blend of learned topics reflected in
+their texts. We parsed automatically generated transcripts of the two lectures
+into overlapping sliding windows, each containing the text of the lecture
+transcript from a particular time range. We treated the set of text (across all
+of these windows) as documents to fit our model
 (Fig.~\ref{fig:sliding-windows}A; see \nameref{subsec:topic-modeling}).
-Transforming these windows with our model yielded a number-of-windows by
-number-of-topics (15) topic-proportions matrix, denoting the unique mixture
-of broad themes from both lectures reflected in each window's content.
-Intuitively, each window's ``topic vector'' (i.e., column of the
-topic-proportions matrix) is analogous to a coordinate in a 15-dimensional
-space (whose axes are topics discovered by the model). Within this space, each lecture's sequence of
-topic vectors (i.e., corresponding to sliding windows parsed from its
-transcript) forms a \textit{trajectory} that captures how its conceptual
-content unfolds over time (Fig.~\ref{fig:sliding-windows}B). We resampled
-these trajectories to a resolution of 1 topic vector for each second of video.
+Transforming the text from every window with our model yielded a
+number-of-windows by number-of-topics (15) topic-proportions matrix that
+described the unique mixture of broad themes from both lectures reflected in
+each window's content. Intuitively, each window's ``topic vector'' (i.e.,
+column of the topic-proportions matrix) is analogous to a coordinate in a
+15-dimensional space whose axes are topics discovered by the model. Within this
+space, each lecture's sequence of topic vectors (i.e., corresponding to sliding
+windows parsed from its transcript) forms a \textit{trajectory} that captures
+how its conceptual content unfolds over time (Fig.~\ref{fig:sliding-windows}B).
+We resampled these trajectories to a resolution of one topic vector for each
+second of video (i.e., 1~Hz).
 
@@
 question. If our model successfully represented information about the deeper
-conceptual content of the lectures (i.e., beyond surface-level details such
-as particular word choices) then we should be able to recover a
-correspondence between their embeddings and embeddings of other text that
-reflects related concepts (e.g., quiz questions that were ostensibly, by
-design, ``about'' one of the two lecture) despite differences in exact
-verbiage. Intuitively, while the content of each given lecture will naturally
-vary from moment to moment, the particular combination of dimensions along
-which its trajectory varies across moments correspond to topics that encode
-meaningful ``information''~\citep{Fish22}  about that lecture's dynamic
-conceptual content. We therefore expected that quiz questions pertaining to
-those same concepts might express the same set of topics.
+conceptual content of the lectures (i.e., beyond surface-level details such as
+particular word choices) then we should be able to recover a correspondence
+between their embeddings and embeddings of other text that reflects related
+concepts (e.g., quiz questions that were ostensibly, by design, ``about'' one
+of the two lecture) despite differences in exact verbiage. Intuitively, while
+the content of each given lecture will naturally vary from moment to moment,
+the particular combination of dimensions along which its trajectory varies
+across moments correspond to topics that encode meaningful
+``information''~\citep{Fish22} about that lecture's dynamic conceptual content.
+We therefore expected that quiz questions pertaining to those same concepts
+might express the same set of topics.
 
@@
 
-\caption{\textbf{Lecture and question topic overlap.} \textbf{A. Topic 
-weight variability}. The bar plots display the variance of each topic's weight 
-across lecture timepoints (top row) and questions (bottom row); colors 
-denote topics. The top-weighted words from the most ``expressive'' (i.e., 
-variable across observations) topic from each lecture are displayed in the 
-upper right (orange: topic 2; yellow-green: topic 4). The top-weighted words 
-from the full set of topics may be found in Table~\topics.
-\textbf{B.
-Relationships between topic weight variability.} Pairwise correlations between the distributions of topic weight variance for each lecture and question category.
-Each row/column corresponds to a bar plot in panel A.}
+\caption{\textbf{Lecture and question topic overlap.} \textbf{A. Topic weight
+variability}. The bar plots display the variance of each topic's weight across
+lecture timepoints (top row) and questions (bottom row); colors denote topics.
+The top-weighted words from the most ``expressive'' (i.e., variable across
+observations) topic from each lecture are displayed in the upper right (orange:
+topic 2; yellow-green: topic 4). The top-weighted words from the full set of
+topics may be found in Table~\topics. \textbf{B. Relationships between topic
+weight variability.} Pairwise correlations between the distributions of topic
+weight variance for each lecture and question category. Each row and column
+corresponds to a bar plot in Panel A.}
 
@@
 
-We used our model to transform the text of each question in our pool into
-the same embedding space as the two lectures' trajectories 
+We used our model to transform the text of each question in our pool into the
+same embedding space as the two lectures' trajectories
 (Fig.~\ref{fig:sliding-windows}C). This yielded a single 15-dimensional
-coordinate (i.e., topic vector) for each question. We then computed the variance
-of each topic's weight across timepoints of each lecture, and across 
+coordinate (i.e., topic vector) for each question. We then computed the
+variance of each topic's weight across timepoints of each lecture, and across
 questions from each category (i.e., lecture 1-related, lecture 2-related, and
@@
 topics expressed by each lecture and its related questions, with only limited
-overlap in the topics expressed by non-matched lecture-question set pairs. 
-To quantify these apparent similarities and differences, we computed the correlation 
-between each pair of topic-weight variance distributions (Fig.~\ref{fig:topics}B). 
-We found that our model represented the contents of lecture-related questions 
-using a combination of topic dimensions (and relative variation along those topic dimensions) that was highly similar to that of 
+overlap in the topics expressed by non-matched lecture-question set pairs. To
+quantify these apparent similarities and differences, we computed the
+correlation between each pair of topic-weight variance distributions
+(Fig.~\ref{fig:topics}B). We found that our model represented the contents of
+lecture-related questions using a combination of topic dimensions (and relative
+variation along those topic dimensions) that was highly similar to that of
 their reference lecture (\textit{Four Fundamental Forces} (\textit{FFF})
@@
 
-%This indicated that our model
-%captures the conceptual contents of the lectures and quiz questions 
-%sufficiently well to differentiate between questions relating to one lecture 
-%versus the other, and could potentially be used to assess participants' knowledge for each lecture
-
-% , and could be used to assess participants' knowledge about
-%each lecture independently, based on the \textit{specific} questions they
-%answered correctly or incorrectly on each quiz. 
-%providing a slightly more 
-%nuanced measure of what concepts they do and do not know than a simple 
-%proportion-correct score.
-
-%When we compared the
-%variability in topic weights across each lecture's timepoints, and across
-%questions from each category (i.e., lecture 1-related, lecture 2-related, and
-%general physics knowledge), we found multiple interesting patterns (Fig.~\ref{fig:topics}). First,
-%there is a strong correspondence between the sets of topics expressed by each
-%lecture and its relevant questions. This indicates that our model is
-%sensitive to the underlying conceptual content tested by different question,
-%and should allow us to differentially assess participants' knowledge for the
-%two lectures based on the \textit{specific} questions they answered correctly
-%or incorrectly on each quiz. Second, the topics expressed by the general
-%physics knowledge questions comprise a nonspecific mix of topics from the two
-%lectures (4 from lecture 1; 5 from lecture 2), most of which are expressed to
-%a relatively low degree. This indicates that our model should enable us to
-%discriminate questions that are highly relevant to our assessment of
-%participants' knowledge about concepts from the lectures from those that are
-%not (or potentially less so). Third, the two lectures' trajectories vary
-%along largely non-overlapping topic dimensions (e.g., variations in weight
-%for topics 2, 3, 8, 12, 13, and 15 are specific to lecture 1; variations in
-%weight for topics 1, 4, 5, 6, 7, and 10 are specific to lecture 2), but also
-%share a small number of expressed topics in common (topics 11 and 14). This
-%indicates that our lecture is able to simultaneously capture
-
-This could enable us to estimate participants' knowledge for each of the two lectures, separately, by
-
-This aspect of our model could enable us to assess participants' knowledge for each lecture separately, based on which \textit{specific} questions they answered right on wrong on each quiz, providing a slightly more refined estimate of the concepts they do and do not know than single proportion-correct score.
-However, while lectures are often organized around a single, broad theme at a coarse timescale, they typically cover...
-%While individual lectures may be organized around a single broad theme at a coarse scale,
-
-\textcolor{red}{\textbf{Paxton stopped here}}
-
-\begin{figure}[tp]
-    \centering
-    \includegraphics[width=\textwidth]{figs/lecture-question-similarity}
-    \caption{\textbf{Which parts of each lecture are captured by each
-    question?} Each panel displays timeseries plots showing how each question's
-    topic vector correlates with each video timepoint's topic vector (Panel
-    \textbf{A.}: correlations for the \textit{Four Fundamental Forces} lecture
-    and associated questions; Panel \textbf{B.}: correlations for the
-    \textit{Birth of Stars} lecture and associated questions). The colors denote
-    question identities. The diamonds in each panel denote the moment of peak
-    correlation between the indicated question and the lecture trajectory. The
-    associated questions' text and snippets of the lectures' transcripts from the surrounding 30 seconds, are displayed at the bottom of the
-    figure.}
-
-    \label{fig:question-correlations}
-\end{figure}
-
-Although an individual lecture may be organized around a single broad theme at a
+Although a single lecture may be organized around a single broad theme at a
 coarse scale, at a finer scale each moment of a lecture typically covers a
@@
 
+\begin{figure}[tp] \centering
+\includegraphics[width=\textwidth]{figs/lecture-question-similarity}
+
+\caption{\textbf{Which parts of each lecture are captured by each question?}
+Each panel displays timeseries plots showing how each question's topic vector
+correlates with each video timepoint's topic vector (Panel \textbf{A.}:
+correlations for the \textit{Four Fundamental Forces} lecture and associated
+questions; Panel \textbf{B.}: correlations for the \textit{Birth of Stars}
+lecture and associated questions). The colors denote question identities. The
+diamonds in each panel denote the moment of peak correlation between the
+indicated question and the lecture trajectory. The associated questions' text
+and snippets of the lectures' transcripts from the surrounding 30 seconds, are
+displayed at the bottom of the figure.}
+
+    \label{fig:question-correlations}
+\end{figure}
+
 The ability to quantify how much each question is ``asking about'' the content
@@
 $x$, in text embedding space (e.g., the content reflected by any moment in a
-lecture they had watched; see \nameref{subsec:traces}).
-Essentially, the estimated knowledge at the coordinate is given by the weighted
-average proportion of quiz questions the participant answered correctly, where
-the weights reflect how much each question is ``about'' the content at $x$.
-When we apply this approach to estimate the participant's knowledge about the
-content presented in each moment of each lecture, we can obtain a detailed
-timecourse describing how much ``knowledge'' the participant has about any part
-of the lecture. As shown in Figure~\ref{fig:knowledge-timeseries}, we can also
-apply this approach separately for the questions from each quiz the
-participants took throughout the experiment. From just 13 questions per quiz,
-we obtain a high-resolution snapshot (at the time each quiz was taken) of what
-the participants knew about any moment's content, from either of the two
-lectures they watched (comprising a total of 1106 samples across the two
-lectures).
+lecture they had watched; see \nameref{subsec:traces}). Essentially, the
+estimated knowledge at the coordinate is given by the weighted average
+proportion of quiz questions the participant answered correctly, where the
+weights reflect how much each question is ``about'' the content at $x$. When we
+apply this approach to estimate the participant's knowledge about the content
+presented in each moment of each lecture, we can obtain a detailed timecourse
+describing how much ``knowledge'' the participant has about any part of the
+lecture. As shown in Figure~\ref{fig:knowledge-timeseries}, we can also apply
+this approach separately for the questions from each quiz the participants took
+throughout the experiment. From just 13 questions per quiz, we obtain a
+high-resolution snapshot (at the time each quiz was taken) of what the
+participants knew about any moment's content, from either of the two lectures
+they watched (comprising a total of 1106 samples across the two lectures).
 
@@
 that documents that reflect similar blends of topics (i.e., documents that
-reflect similar themes, according to the model) will yield similar (in terms of
-Euclidean \textcolor{red}{should we say something like cosine instead of euclidean?} distance, correlation, etc.) topic vectors. In general, the
-similarity between different documents' topic vectors may be used to
-characterize the similarity in conceptual content between the documents.
+reflect similar themes, according to the model) will yield similar coordinates
+(in terms of Euclidean distance, correlation, or other geometric measures). In
+general, the similarity between different documents' topic vectors may be used
+to characterize the similarity in conceptual content between the documents.
 
@@
 linear interpolation (independently for each topic dimension) to resample the
-resulting timeseries to one vector per second. We also used the fitted model to obtain topic
-vectors for each question in our pool (Tab.~\questions). Taken together, we
-obtained a \textit{trajectory} for each video, describing its path through
-topic space, and a single coordinate for each question
+resulting timeseries to one vector per second. We also used the fitted model to
+obtain topic vectors for each question in our pool (Tab.~\questions). Taken
+together, we obtained a \textit{trajectory} for each video, describing its path
+through topic space, and a single coordinate for each question
 (Fig.~\ref{fig:sliding-windows}C). Embedding both videos and all of the
@@
 \end{equation}
+
 and where $\mathrm{mincorr}$ and $\mathrm{maxcorr}$ are the minimum and maximum
 correlations between any lecture timepoint and question, taken over all
-timepoints and questions across both lectures and all five question used to estimate the knowledge trace \textcolor{red}{\textbf{Note: make sure this is correct in results section; not sure i caught all instances}}.
-We
-also define $f(s, \Omega)$ as the $s$\textsuperscript{th} topic vector from the
-set of topic vectors $\Omega$. Here $t$ indexes the set of lecture topic
-vectors, $L$, and $i$ and $j$ index the topic vectors of questions used to estimate the knowledge trace, $Q$. Note that ``correct'' denotes the set of indices of
-the questions the participant answered correctly on the given quiz.
+timepoints and questions across both lectures and all five question used to
+estimate the knowledge trace \textcolor{red}{\textbf{Note: make sure this is
+correct in results section; not sure i caught all instances}}. We also define
+$f(s, \Omega)$ as the $s$\textsuperscript{th} topic vector from the set of
+topic vectors $\Omega$. Here $t$ indexes the set of lecture topic vectors, $L$,
+and $i$ and $j$ index the topic vectors of questions used to estimate the
+knowledge trace, $Q$. Note that ``correct'' denotes the set of indices of the
+questions the participant answered correctly on the given quiz.
 
@@
 (Figs.~\ref{fig:knowledge-maps},~\individualKnowledgeMapsA,~\individualKnowledgeMapsB,~\individualKnowledgeMapsC,~\individualLearningMapsA,
-and~\individualLearningMapsB), we used Uniform Manifold Approximation and Projection (UMAP; \citealp{McInEtal18a}) to construct a 2D
-projection of the text embedding space. Sampling the original 100-dimensional
-space at high resolution to obtain an adequate set of topic vectors spanning
-the embedding space would be computationally intractable. However, sampling a
-2D grid is much more feasible. We defined a rectangle enclosing the 2D
-projections of the lectures' and quizzes' embeddings, and we sampled points
-from a regular $100 \times 100$ grid of coordinates that evenly tiled the
-enclosing rectangle. We sought to estimate participants' knowledge (and
-learning, i.e., changes in knowledge) at each of the resulting 10,000
-coordinates.
+and~\individualLearningMapsB), we used Uniform Manifold Approximation and
+Projection (UMAP; \citealp{McInEtal18a}) to construct a 2D projection of the
+text embedding space. Sampling the original 100-dimensional space at high
+resolution to obtain an adequate set of topic vectors spanning the embedding
+space would be computationally intractable. However, sampling a 2D grid is much
+more feasible. We defined a rectangle enclosing the 2D projections of the
+lectures' and quizzes' embeddings, and we sampled points from a regular $100
+\times 100$ grid of coordinates that evenly tiled the enclosing rectangle. We
+sought to estimate participants' knowledge (and learning, i.e., changes in
+knowledge) at each of the resulting 10,000 coordinates.
 

### 2023-01-31 paper/main.tex
checking in changes before i go to a talk (everything is a mess!!!)

@@
 % supplemental figures
-\newcommand{\individualKnowledgeMapsA}{S1}
-\newcommand{\individualKnowledgeMapsB}{S2}
-\newcommand{\individualKnowledgeMapsC}{S3}
-\newcommand{\individualLearningMapsA}{S4}
-\newcommand{\individualLearningMapsB}{S5}
+\newcommand{\topicWeights}{S1} 
+\newcommand{\individualKnowledgeMapsA}{S2}
+\newcommand{\individualKnowledgeMapsB}{S3}
+\newcommand{\individualKnowledgeMapsC}{S4}
+\newcommand{\individualLearningMapsA}{S5}
+\newcommand{\individualLearningMapsB}{S6}
 
@@
 
-\title{Text embedding models reveal high resolution insights into conceptual
+\title{Text embedding models yield high resolution insights into conceptual
 knowledge from short multiple choice quizzes}
@@
 researchers in education, cognitive psychology, and cognitive
-neuroscience~\citep[e.g.,][]{Kato40, Gall00, ScotEtal07, HallGree08, Macl05} has
-profound analogs in the fields of natural language processing and natural
+neuroscience~\citep[e.g.,][]{Kato40, Gall00, ScotEtal07, HallGree08, Macl05}
+has profound analogs in the fields of natural language processing and natural
 language understanding. For example, considering the raw contents of a document
@@
 information about what the document is about, just as memorizing a passage
-might provide some ability to answer simple questions about it~\citep[e.g., whether
-it contains words related to furniture versus physics;][]{LandDuma97,
-BleiEtal03, BleiLaff06}. However, modern natural language processing
-models~\citep[e.g.,][]{MikoEtal13a, CerEtal18, BrowEtal20} also attempt to
-capture the deeper meaning \textit{underlying} those atomic elements. These
-models consider not only the co-occurrences of those elements within and across
-documents, but also patterns in how those elements appear across different
-scales (e.g., sentences, paragraphs, chapters, etc.), the temporal and
-grammatical properties of the elements, and other high-level characteristics of
-how they are used~\citep{Mann20, Mann21a}. According to these models, the deep
-conceptual meaning of a document may be captured by a feature vector in a
-high-dimensional representation space, where nearby vectors reflect
-conceptually related documents. A model that succeeds at capturing an analog of
-``understanding'' is able to assign nearby feature vectors to two conceptually
-related documents, \textit{even when the words contained in those documents
-have very little overlap}.
+might provide some ability to answer simple questions about it. However, text
+embedding models~\citep[e.g.,][]{LandDuma97, DeerEtal90, BleiEtal03,
+BleiLaff06, MikoEtal13a, CerEtal18, BrowEtal20} also attempt to capture the
+deeper meaning \textit{underlying} those atomic elements. These models consider
+not only the co-occurrences of those elements within and across documents, but
+also patterns in how those elements appear across different scales (e.g.,
+sentences, paragraphs, chapters, etc.), the temporal and grammatical properties
+of the elements, and other high-level characteristics of how they are
+used~\citep{Mann20, Mann21a}. According to these models, the deep conceptual
+meaning of a document may be captured by a feature vector in a high-dimensional
+representation space, where nearby vectors reflect conceptually related
+documents. A model that succeeds at capturing an analog of ``understanding'' is
+able to assign nearby feature vectors to two conceptually related documents,
+\textit{even when the words contained in those documents have very little
+overlap}.
 
@@
 throughout that space. To begin to test this smoothness assumption, we sought
-to track participants' knowledge and how it changed over time in response
-to training.
+to track participants' knowledge and how it changed over time in response to
+training. Two overarching goals guide our approach. First, we want to gain
+detailed insights into what learners know, at different points in their
+training. For example, rather than simply reporting on the proportions of
+questions participants answer correctly (i.e., their overall performance), we
+seek estimates of their knowledge about a variety of specific concepts.
+Second, we want our approach to be potentially scalable to large numbers of
+concepts, courses, and students. This requires the conceptual content of
+interest to be discovered \textit{automatically}, rather than relying on
+manually produced ratings or labels.
 
@@
 overview of our current understanding of how stars form. We selected these
-lessons to be (a) accessible to a broad audience, i.e., requiring minimal
-prerequisite knowledge to understand; (b) conceptually related to each other,
-i.e., covering at least \textit{some} similar or overlapping content; and (c)
-largely independent of each other, i.e., focused on sufficiently different
-material that understanding one did not require having seen the other. The two
-videos we selected are introductory lectures that both belong to Khan Academy's
-``Cosmology and Astronomy'' course domain, but are taken from different lecture
-series (``Scale of the Universe'' and ``Stars, Black Holes, and Galaxies'' for
-the first and second lectures, respectively).
-
-We created a pool of multiple-choice quiz questions that would enable us to
-evaluate participants' knowledge about each individual lecture along with
-related content not specifically presented in either video (see
-Tab.~\questions). Participants answered questions randomly drawn from each
-content area (lecture 1, lecture 2, and general physics knowledge) on each of
-the three quizzes. Quiz 1 was intended to assess participants' ``baseline''
-knowledge before training, quiz 2 assessed knowledge after watching the
-\textit{Four Fundamental Forces} video (i.e., lecture 1), and quiz 3 assessed
-knowledge after watching the \textit{Birth of Stars} video (i.e., lecture 2).
+particular lectures to satisfy three general criteria. First, we wanted both
+lectures to be accessible to a broad audience (i.e., with minimal prerequisite
+knowledge) so as to limit the impact of prior training on our participants'
+abilities to learn from the lectures. To this end, we selected two introductory
+videos that were intended to be viewed at the start of students' training in
+their respective content areas. Second, we wanted both lectures to have some
+related content, so that we could test our approach's ability to distinguish
+similar conceptual content. To this end, we chose two videos from the same (per
+instructor annotations) Khan Academy course domain, ``Cosmology and
+Astronomy.'' Third, we sought to minimize dependencies and specific overalp
+between the videos. For example, we did not want participants' abilities to
+understand one video to (directly) influence their abilities to understand the
+other. To satisfy this last criterion, we chose videos from two different
+lecture series (lectures 1 and 2 were from the ``Scale of the Universe'' and
+``Stars, Black Holes, and Galaxies'' series, respectively).
+
+We also wrote a set of multiple-choice quiz questions that we hoped would
+enable us to evaluate participants' knowledge about each individual lecture,
+along with related knowledge about physics not specifically presented in either
+video (see Tab.~\questions~for the full list of questions in our stimulus
+pool). Participants answered questions randomly drawn from each content area
+(lecture 1, lecture 2, and general physics knowledge) on each of the three
+quizzes. Quiz 1 was intended to assess participants' ``baseline'' knowledge
+before training, quiz 2 assessed knowledge after watching the \textit{Four
+Fundamental Forces} video (i.e., lecture 1), and quiz 3 assessed knowledge
+after watching the \textit{Birth of Stars} video (i.e., lecture 2).
 
@@
 
-To study how participants' conceptual knowledge changed over the course of the
-experiment, we first sought to characterize the abstract concepts presented to
-them in each of the two lectures. We adapted an approach we developed in prior
-work~\citep{HeusEtal21} to extract the latent themes from the lectures'
-contents using a topic model~\citep{BleiEtal03}. Briefly, topic models take as
-input a collection of text documents and learn a set of ``topics'' (i.e.,
-latent themes) from their contents. Once fit, a topic model can be used to
-transform arbitrary (potentially new) documents into sets of ``topic
-proportions,'' describing the weighted blend of learned topics reflected in
-their texts. We parsed automatically generated transcripts of the two lectures
-into overlapping sliding windows, each containing the text of the lecture
-transcript from a particular time range. We treated the set of text (across all
-of these windows) as documents to fit our model
+To study in detail how participants' conceptual knowledge changed over the
+course of the experiment, we first sought to model the conceptual content
+presented to them at each moment throughout each of the two lectures. We
+adapted an approach we developed in prior work~\citep{HeusEtal21} to identify
+the latent themes in the lectures using a topic model~\citep{BleiEtal03}.
+Briefly, topic models take as input a collection of text documents and learn a
+set of ``topics'' (i.e., latent themes) from their contents. Once fit, a topic
+model can be used to transform arbitrary (potentially new) documents into sets
+of ``topic proportions,'' describing the weighted blend of learned topics
+reflected in their texts. We parsed automatically generated transcripts of the
+two lectures into overlapping sliding windows, where each window contained the
+text of the lecture transcript from a particular time range. We treated the set
+of text snippets (across all of these windows) as documents to fit our model
 (Fig.~\ref{fig:sliding-windows}A; see \nameref{subsec:topic-modeling}).
-Transforming the text from every window with our model yielded a
+Transforming the text from every sliding window with our model yielded a
 number-of-windows by number-of-topics (15) topic-proportions matrix that
 described the unique mixture of broad themes from both lectures reflected in
-each window's content. Intuitively, each window's ``topic vector'' (i.e.,
-column of the topic-proportions matrix) is analogous to a coordinate in a
-15-dimensional space whose axes are topics discovered by the model. Within this
-space, each lecture's sequence of topic vectors (i.e., corresponding to sliding
-windows parsed from its transcript) forms a \textit{trajectory} that captures
-how its conceptual content unfolds over time (Fig.~\ref{fig:sliding-windows}B).
-We resampled these trajectories to a resolution of one topic vector for each
+each window's content. Each window's ``topic vector'' (i.e., column of the
+topic-proportions matrix) is a coordinate in a 15-dimensional space whose axes
+are topics discovered by the model. Within this space, each lecture's sequence
+of topic vectors (i.e., corresponding to its transcript's overlapping text
+snippets across sliding windows) forms a \textit{trajectory} that captures how
+its conceptual content unfolds over time (Fig.~\ref{fig:sliding-windows}B). We
+resampled these trajectories to a resolution of one topic vector for each
 second of video (i.e., 1~Hz).
 
-Next, we sought to characterize what information participants' performance on
-each of the three quizzes could provide about their conceptual knowledge at
-that point in time. Traditional approaches to evaluating students'
-performance on short-form knowledge assessments, such as those in our study,
-entail computing the proportion of correctly answered questions to assign a
-simple numeric score. While this may afford some measure of the
-\textit{extent} of a learner's knowledge, such a score provides little
-information to either the teacher or the learner about the particular
-\textit{contents} of their knowledge---in other words, raw
-``proportion-correct'' measures may capture \textit{how much} a student
-knows, but not \textit{what} they know. For instance, suppose a participant
-in our study was highly knowledgeable about fundamental physical forces (i.e
-., lecture 1 content) but unfamiliar with how stars are formed (i.e., lecture
-2 content), while a second participant was unfamiliar with fundamental forces
-but had extensive prior knowledge about star formation. Since quiz 1
-(completed before viewing either lecture) contained an equal number of
-questions about each lecture's content (see Fig.~\ref{fig:experiment}), these
-two participants could easily achieve the same proportion-correct score
-despite their conceptual knowledge differing substantially. How might we
-distinguish these individuals?
-
-We hypothesized that our text embedding model, which we had trained on
-transcripts of the two lectures to characterize their conceptual contents,
-should also allow us to capture the conceptual knowledge probed by each quiz
-question. If our model successfully represented information about the deeper
-conceptual content of the lectures (i.e., beyond surface-level details such as
-particular word choices) then we should be able to recover a correspondence
-between their embeddings and embeddings of other text that reflects related
-concepts (e.g., quiz questions that were ostensibly, by design, ``about'' one
-of the two lecture) despite differences in exact verbiage. Intuitively, while
-the content of each given lecture will naturally vary from moment to moment,
-the particular combination of dimensions along which its trajectory varies
-across moments correspond to topics that encode meaningful
-``information''~\citep{Fish22} about that lecture's dynamic conceptual content.
-We therefore expected that quiz questions pertaining to those same concepts
-might express the same set of topics.
+We hypothesized that a topic model trained on transcripts of the two lectures,
+should also capture the conceptual knowledge probed by each quiz question. If
+indeed the topic model could capture information about the deeper conceptual
+content of the lectures (i.e., beyond surface-level details such as particular
+word choices) then we should be able to recover a correspondence between each
+lecture and questions \textit{about} each lecture. Importantly, such a
+correspondence could not solely arise from superficial text matching between
+lecture transcripts and questions, since the lectures and questions used
+different words. Simply comparing the average topic weights from each lecture
+and question sets (averaging across time and questions, respectively) reveals a
+striking correspondence (Fig.~\topicWeights). Specifically, the average topic
+weights from lecture 1 are strongly correlated with the average topic weights
+from lecture 1 questions ($r(13) = XX, p = XX$, 95\% confidence interval
+(CI)~$= XX$), and the average topic weights from lecture 2 are strongly
+correlated with the average topic weights from lecture 2 questions ($r(13) =
+XX, p = XX, CI = XX$). At the same time, the average topics from two lectures
+are \textit{negatively} correlated ($r(13) = XX, p = XX, CI = XX$). The full
+set of pairwise comparisons between topic vectors for the lectures and each
+question set is reported in Figure~\topicWeights.
 
@@
 
-We used our model to transform the text of each question in our pool into the
-same embedding space as the two lectures' trajectories
+Another, more sensitive, way of summarizing the conceptual content of the
+lectures and questions is to look at \textit{variability} in how topics are
+weighted over time and across different questions (Fig.~\ref{fig:topics}).
+Intuitively, the variability in the expression of a given topic relates to how
+much ``information''~\citep{Fish22} the lecture (or questions) reflect about
+that topic. For example, suppose a given topic is weighted on heavily
+throughout a lecture. That topic might be characteristic of some aspect or
+property of the lecture \textit{overall} (conceptual or otherwise), but unless
+the topic's weights changed in meaningful ways over time, the topic would be a
+poor indicator of any \textit{specific} conceptual content in the lecture. We
+therefore also compared the variance in topic weights (across time or
+questions) between the lectures and questions.  [ADD BACK CORRELATION RESULTS]
+
+\textbf{JRM STOPPED HERE...}
+
+We used the fitted topic model to transform the text of each question in our
+stimulus pool into the same embedding space as the two lectures' trajectories
 (Fig.~\ref{fig:sliding-windows}C). This yielded a single 15-dimensional
@@
 variance of each topic's weight across timepoints of each lecture, and across
-questions from each category (i.e., lecture 1-related, lecture 2-related, and
+questions from each category (i.e., questions about lecture 1, lecture 2, and
 general physics knowledge; Fig.~\ref{fig:topics}A). Visual inspection of
@@
 quantify these apparent similarities and differences, we computed the
-correlation between each pair of topic-weight variance distributions
-(Fig.~\ref{fig:topics}B). We found that our model represented the contents of
+correlations between each pair of topic-weight variance vectors (i.e., vectors
+containing the variance across timepoints or questions, for each topic;
+Fig.~\ref{fig:topics}B).
+
+We found that our model represented the contents of
 lecture-related questions using a combination of topic dimensions (and relative

### 2023-01-31 paper/supplement.tex
checking in changes before i go to a talk (everything is a mess!!!)

@@
 
-\title{\textit{Supplementary materials for}: Text embedding models reveal high
+\title{\textit{Supplementary materials for}: Text embedding models yield high
 resolution insights into conceptual knowledge from short multiple choice
@@
 \renewcommand{\citenumfont}[1]{S#1}
+
+\newcommand{\topics}{3}
 
@@
 
-    \label{tab:topics}
-
 \end{tabular}
 \end{tiny}
+
 \caption{\textbf{Topics.} The table displays the 10 top-weighted word from
@@
     and questions}).}
+    \label{tab:topics}
 \end{table}
+
+\newpage
+
+\begin{figure}[tp]
+    \centering
+    \includegraphics[width=\textwidth]{figs/topic-weights}
+
+\caption{\textbf{Averarge topic weights for each lecture and question type}.
+The bar plots display the variance of each topic's weight across lecture
+timepoints (top row) and questions (bottom row); colors denote topics. The
+top-weighted words from the most heavily weighted topics are displayed in the
+upper right (orange: topic 2; yellow-green: topic 4). The top-weighted words
+from the full set of topics may be found in Table~S2. Also see
+Figure~\topics A in the main text.}
+
+    \label{fig:topics}
+\end{figure}
 

### 2023-01-31 paper/main.tex
checking in edits to intro + results

@@
 therefore also compared the variance in topic weights (across time or
-questions) between the lectures and questions.  [ADD BACK CORRELATION RESULTS]
-
-\textbf{JRM STOPPED HERE...}
-
-We used the fitted topic model to transform the text of each question in our
-stimulus pool into the same embedding space as the two lectures' trajectories
-(Fig.~\ref{fig:sliding-windows}C). This yielded a single 15-dimensional
-coordinate (i.e., topic vector) for each question. We then computed the
-variance of each topic's weight across timepoints of each lecture, and across
-questions from each category (i.e., questions about lecture 1, lecture 2, and
-general physics knowledge; Fig.~\ref{fig:topics}A). Visual inspection of
-Figure~\ref{fig:topics}A suggests a strong correspondence between the sets of
-topics expressed by each lecture and its related questions, with only limited
-overlap in the topics expressed by non-matched lecture-question set pairs. To
-quantify these apparent similarities and differences, we computed the
-correlations between each pair of topic-weight variance vectors (i.e., vectors
-containing the variance across timepoints or questions, for each topic;
-Fig.~\ref{fig:topics}B).
-
-We found that our model represented the contents of
-lecture-related questions using a combination of topic dimensions (and relative
-variation along those topic dimensions) that was highly similar to that of
-their reference lecture (\textit{Four Fundamental Forces} (\textit{FFF})
-questions vs.~lecture: Pearson's $r(13) =
-0.824,~p<0.001,~95\%~\mathrm{confidence~interval~(CI)} = [0.696, 0.973]$;
-\textit{Birth of Stars} (\textit{BoS}) questions vs.~lecture: $r(13) =
-0.801,~p<0.001,~95\%~\mathrm{CI} = [0.539, 0.958]$) but diverged significantly
-from that of the non-reference lecture (\textit{FFF} questions vs.~\textit{BoS}
-lecture: $r(13) = -0.620,~p = 0.014,~95\%~\mathrm{CI} = [-0.871, -0.326]$;
-\textit{BoS} questions vs.~\textit{FFF} lecture: $r(13) = -0.550,~p =
-0.034,~95\%~\mathrm{CI} = [-0.803, -0.246]$). This indicated that our model
-captured the conceptual contents of the lectures and quiz questions
-sufficiently well to differentiate between questions relating to one lecture
-versus the other.
+questions) between the lectures and questions. The variability in topic
+expression (over time and across questions) was similar for the lecture 1 video
+and questions ($r(13) = 0.824,~p<0.001, CI = [0.696, 0.973]$) and the lecture 2
+video and questions ($r(13) = 0.801,~p<0.001,~95\%~\mathrm{CI} = [0.539,
+0.958]$). However, as reported in Figure~\ref{fig:topics}B, the variability in
+topic expressions across \textit{different} videos and lecture-specific
+questions (i.e., lecture 1 video versus lecture 2 questions; lecture 2 video
+versus lecture 1 questions) were \textit{negatively} correlated, and neither
+video's topic variability was reliably correlated with the topic variability
+across general physics knowledge questions. Taken together, the analyses
+reported in Figures~\ref{fig:topics} and~\topicWeights~indicate that a topic
+model fit to the videos' transcripts can also reveal correspondances (at a
+coarse scale) between the lectures and (held-out) questions.
 
@@
 but to also add in materials pertaining to concepts $B$ and $C$ for the second
-student.
+student. In other words, raw ``proportion-correct'' measures may capture
+\textit{how much} a student knows, but not \textit{what} they know. We wondered
+whether our modeling framework might enable us to (formally and automatically)
+infer participants' knowledge at the scale of individual concepts (e.g., as
+captured by a single question).
 
@@
 the \textit{Four Fundamental Forces} was substantially higher on Quiz 2 versus
-Quiz 1 ($t(49) = 8.764, p < 0.001$) and on Quiz 3 versus Quiz 1 ($t(49) = 10.519, p <
-0.001$). We found no reliable differences in estimated knowledge about that
-lecture's content on Quiz 2 versus 3 ($t(49) = 0.160, p = 0.874$). Similarly, we
-hypothesized (and subsequently confirmed) that participants should show more
-estimated knowledge about the content of the \textit{Birth of Stars} lecture
-after (versus before) watching it (Fig.~\ref{fig:knowledge-timeseries}D).
-Specifically, since participants watched that lecture after taking Quiz 2 (but
-before Quiz 3), we hypothesized that their knowledge estimates should be
-relatively low on Quizzes 1 and 2, but should show a ``boost'' on Quiz 3.
-Consistent with this prediction, we found no reliable differences in estimated
-knowledge about the \textit{Birth of Stars} lecture content on Quizzes 1 versus
-2 ($t(49) = 1.013, p = 0.316$), but the estimated knowledge was substantially higher
-on Quiz 3 versus 2 ($t(49) = 10.561, p < 0.001$) and Quiz 3 versus 1 ($t(49) = 8.969, p <
-0.001$).
+Quiz 1 ($t(49) = 8.764, p < 0.001$) and on Quiz 3 versus Quiz 1 ($t(49) =
+10.519, p < 0.001$). We found no reliable differences in estimated knowledge
+about that lecture's content on Quiz 2 versus 3 ($t(49) = 0.160, p = 0.874$).
+Similarly, we hypothesized (and subsequently confirmed) that participants
+should show more estimated knowledge about the content of the \textit{Birth of
+Stars} lecture after (versus before) watching it
+(Fig.~\ref{fig:knowledge-timeseries}D). Specifically, since participants
+watched that lecture after taking Quiz 2 (but before Quiz 3), we hypothesized
+that their knowledge estimates should be relatively low on Quizzes 1 and 2, but
+should show a ``boost'' on Quiz 3. Consistent with this prediction, we found no
+reliable differences in estimated knowledge about the \textit{Birth of Stars}
+lecture content on Quizzes 1 versus 2 ($t(49) = 1.013, p = 0.316$), but the
+estimated knowledge was substantially higher on Quiz 3 versus 2 ($t(49) =
+10.561, p < 0.001$) and Quiz 3 versus 1 ($t(49) = 8.969, p < 0.001$).
 

### 2023-02-01 paper/main.tex

@@
 
-We fetched these automated transcripts using the \texttt{youtube-transcript-api} 
-Python package (\textcolor{red}{\textbf{Jeremy can you add a citation for this?} 
-https://github.com/jdepoix/youtube-transcript-api}). The transcripts consisted of 
-one timestamped line of text for every few seconds (mean: 2.34s; standard 
-deviation: 0.83s) of spoken content in the video (i.e., corresponding to each 
-individual caption that would appear on-screen if viewing the lecture via YouTube, 
-and when those lines would appear). We
-defined a sliding window length of (up to) $w = 30$ transcript lines, and
-assigned each window a timestamp corresponding to the midpoint between its first
-and last lines' timestamps. These sliding windows ramped up and down in length
-at the very beginning and end of the transcript, respectively. In other words,
-the first sliding window covered only the first line from the transcript; the
-second sliding window covered the first two lines; and so on. This insured that
-each line of the transcript appeared in the same number ($w$) of sliding
-windows. After performing various standard text preprocessing (e.g., normalizing case, 
-lemmatizing, removing punctuation and stop-words), we treated the text from each 
-sliding window as a single ``document,''
-and we combined these documents across the two videos' windows to create a single
-training corpus for the topic model.  The top words from each of the 15 discovered
-topics may be found in Table~\topics.
+We fetched these automated transcripts using the
+\texttt{youtube-transcript-api} Python package~\citep{Depo19}. The transcripts
+consisted of one timestamped line of text for every few seconds (mean: 2.34~s;
+standard deviation: 0.83~s) of spoken content in the video (i.e., corresponding
+to each individual caption that would appear on-screen if viewing the lecture
+via YouTube, and when those lines would appear). We defined a sliding window
+length of (up to) $w = 30$ transcript lines, and assigned each window a
+timestamp corresponding to the midpoint between its first and last lines'
+timestamps. These sliding windows ramped up and down in length at the very
+beginning and end of the transcript, respectively. In other words, the first
+sliding window covered only the first line from the transcript; the second
+sliding window covered the first two lines; and so on. This insured that each
+line of the transcript appeared in the same number ($w$) of sliding windows.
+After performing various standard text preprocessing (e.g., normalizing case,
+lemmatizing, removing punctuation and stop-words), we treated the text from
+each sliding window as a single ``document,'' and we combined these documents
+across the two videos' windows to create a single training corpus for the topic
+model. The top words from each of the 15 discovered topics may be found in
+Table~\topics.
 
@@
 \end{equation}
-
 and where $\mathrm{mincorr}$ and $\mathrm{maxcorr}$ are the minimum and maximum
@@
 timepoints and questions across both lectures and all five question used to
-estimate the knowledge trace \textcolor{red}{\textbf{Note: make sure this is
-correct in results section; not sure i caught all instances}}. We also define
-$f(s, \Omega)$ as the $s$\textsuperscript{th} topic vector from the set of
-topic vectors $\Omega$. Here $t$ indexes the set of lecture topic vectors, $L$,
-and $i$ and $j$ index the topic vectors of questions used to estimate the
-knowledge trace, $Q$. Note that ``correct'' denotes the set of indices of the
-questions the participant answered correctly on the given quiz.
+estimate the knowledge trace. We also define $f(s, \Omega)$ as the
+$s$\textsuperscript{th} topic vector from the set of topic vectors $\Omega$.
+Here $t$ indexes the set of lecture topic vectors, $L$, and $i$ and $j$ index
+the topic vectors of questions used to estimate the knowledge trace, $Q$. Note
+that ``correct'' denotes the set of indices of the questions the participant
+answered correctly on the given quiz.
 

### 2023-02-01 paper/main.tex
finished (i think! 🤞) addressing PCF's comments in slack and in the latex notes.

@@
 \subsubsection*{Constructing text embeddings of multiple lectures and questions}\label{subsec:topic-modeling}
+
 We adapted an approach we developed in prior work~\citep{HeusEtal21} to embed
-each moment of the two lectures and each question in our pool in a common representational space.
-Briefly, our approach uses a topic model (Latent Dirichlet Allocation;~\citealp{BleiEtal03}), trained on a set
-of documents, to discover a set of $k$ ``topics'' or ``themes.'' Formally, each
-topic is defined as a set of weights over each word in the model's vocabulary
-(i.e., the union of all unique words, across all documents, excluding ``stop
-words.''). Conceptually, each topic is intended to give larger weights to words
-that are conceptually related or that tend to co-occur in the same documents.
-After fitting a topic model, each document in the training set, or any
-\textit{new} document that contains at least some of the words in the model's
-vocabulary, may be represented as a $k$-dimensional vector describing how much
-the document (most probably) reflects each topic. (Unless, otherwise noted, we
-used $k = 15$ topics.)
+each moment of the two lectures and each question in our pool in a common
+representational space. Briefly, our approach uses a topic model (Latent
+Dirichlet Allocation;~\citealp{BleiEtal03}), trained on a set of documents, to
+discover a set of $k$ ``topics'' or ``themes.'' Formally, each topic is defined
+as a set of weights over each word in the model's vocabulary (i.e., the union
+of all unique words, across all documents, excluding ``stop words.'').
+Conceptually, each topic is intended to give larger weights to words that are
+conceptually related or that tend to co-occur in the same documents. After
+fitting a topic model, each document in the training set, or any \textit{new}
+document that contains at least some of the words in the model's vocabulary,
+may be represented as a $k$-dimensional vector describing how much the document
+(most probably) reflects each topic. (Unless, otherwise noted, we used $k = 15$
+topics.)
 
@@
 resolution to obtain an adequate set of topic vectors spanning the embedding
-space would be computationally intractable. However, sampling a 2D grid is much
-more feasible. We defined a rectangle enclosing the 2D projections of the
-lectures' and quizzes' embeddings, and we sampled points from a regular $100
-\times 100$ grid of coordinates that evenly tiled the enclosing rectangle. We
+space would be computationally intractable. However, sampling a 2D grid is
+trivial.
+
+At a high level, the UMAP algorithm obtains low-dimensional embeddings by
+minimizing the cross entropy between the pairwise (clustered) distances between
+the observations in their original (e.g., 100-dimensional) space and the
+pairwise (clustered) distances in the low-dimensional embedding space (in our
+approach, the embedding space is 2D). In our implementation, pairwise distances
+in the original high-dimensional space were defined as 1 minus the correlation
+between the pair of coordinates, and pairwise distances in the low-dimensional
+embedding space were defiend as the Euclidean distance between the pair of
+coordinates.
+
+Although UMAP is not fully invertible, due to its clustering step, it is
+possible to approximately invert the embedded low-dimensional points. In our
+application, we sought to embed topic vectors, whose elements are always
+non-negative. Because the inversion step is inexact, sometimes it results in
+negative-valued vectors (even if the original observations were all
+non-negative), which are incompatable with the topic modeling framework. To
+protect against this issue, we log-transformed the topic vectors prior to
+embedding them in the 2D space. When we inverted the embedded vectors (e.g., to
+estimate topic vectors or word clouds, as in Fig.~\ref{fig:knowledge-maps}C),
+we passed to inverted (log-transformed) values through the exponential function
+to obtain a vector of non-negative values.
+
+After embedding both lectures' topic trajectories and the topic vectors of
+every question, we defined a rectangle enclosing the 2D projections of the
+lectures' and quizzes' embeddings. We then sampled points from a regular $100
+\times 100$ grid of coordinates that evenly tiled this enclosing rectangle. We
 sought to estimate participants' knowledge (and learning, i.e., changes in
-knowledge) at each of the resulting 10,000 coordinates.
+knowledge) at each of the resulting 10K coordinates.
 

### 2023-02-01 paper/main.tex
addressed (some of) ACH's comments

@@
 most effective strategy for that individual student.
+
+A common approach to assessing students' learning is to compile a set of quiz
+questions, tally up the proportion of correctly answered questions, and provide
+the student with feedback in the form of a letter grade. Although a numerical
+or letter grades give \textit{some} indication about whether the student has
+mastered the to-be-learned material, any single measure of performance on a
+complex task is at risk of conflating underlying factors, losing relevant
+information, and so on. For example, consider the relative utility of the
+imaginary map described above that characterizes in detail a student's
+knowledge, versus a single annotation saying that the student answered 85\% of
+their quiz questions correctly, or that they received a `B'. Here, we show that
+the same quiz data required to compute proportion correct scores or letter
+grades can be used to instead obtain much more detailed insights into what the
+student knows at the time they took the quiz.
 
@@
 Participants reported their undergraduate major(s) as ``social sciences'' (28
-participants), ``natural sciences'' (16 participants), ``professional'' (e.g., pre-med or pre-law; 8
-participants), ``mathematics and engineering'' (7 participants), ``humanities'' (4
-participants), or ``undecided'' (3 participants). Note that some participants
-selected multiple categories for their undergraduate major. We also asked
-participants about the courses they had taken. In total, 45 participants
-reported having taken at least one Khan Academy course in the past,
-and 5 reported not having taken any Khan
-Academy courses. Of those who reported having watched at least one
-Khan Academy course, 7 participants reported having watched 1--2 courses, 11
-reported having watched 3--5 courses, 8 reported having watched 5--10 courses,
-and 19 reported having watched 10 or more courses. We also asked participants
-about the specific courses they had watched, categorized under different
-subject areas. In the ``Mathematics'' area, participants reported having watched
-videos on AP Calculus AB (21 participants), Precalculus (17 participants),
-Algebra 2 (14 participants), AP Calculus BC (12 participants), Trigonometry (11
+participants), ``natural sciences'' (16 participants), ``professional'' (e.g.,
+pre-med or pre-law; 8 participants), ``mathematics and engineering'' (7
+participants), ``humanities'' (4 participants), or ``undecided'' (3
+participants). Note that some participants selected multiple categories for
+their undergraduate major. We also asked participants about the courses they
+had taken. In total, 45 participants reported having taken at least one Khan
+Academy course in the past, and 5 reported not having taken any Khan Academy
+courses. Of those who reported having watched at least one Khan Academy course,
+7 participants reported having watched 1--2 courses, 11 reported having watched
+3--5 courses, 8 reported having watched 5--10 courses, and 19 reported having
+watched 10 or more courses. We also asked participants about the specific
+courses they had watched, categorized under different subject areas. In the
+``Mathematics'' area, participants reported having watched videos on AP
+Calculus AB (21 participants), Precalculus (17 participants), Algebra 2 (14
+participants), AP Calculus BC (12 participants), Trigonometry (11
 participants), Algebra 1 (10 participants), Geometry (8 participants),
@@
 participants reported having watched videos on Chemistry, AP Chemistry, or
-Organic Chemistry (21 participants); Physics, AP Physics I, or AP Physics II (15
-participants); Biology, AP Biology; or High school Biology (15 participants);
-Health and Medicine (1 participant); or other videos not listed in our survey
-(19 participants). We also asked participants whether they had specifically seen the
-videos used in our experiment. Of the 45 participants who reported having having
-taken at least one Khan Academy course in the past, 44 participants reported that they had not watched the \textit{Four Fundamental Forces} video, and 1 participant reported that they were not sure whether they had watched it.
-All participants reported that they had not watched the \textit{Birth of Stars} video.
-When we asked participants about non-Khan
+Organic Chemistry (21 participants); Physics, AP Physics I, or AP Physics II
+(15 participants); Biology, AP Biology; or High school Biology (15
+participants); Health and Medicine (1 participant); or other videos not listed
+in our survey (19 participants). We also asked participants whether they had
+specifically seen the videos used in our experiment. Of the 45 participants who
+reported having having taken at least one Khan Academy course in the past, 44
+participants reported that they had not watched the \textit{Four Fundamental
+Forces} video, and 1 participant reported that they were not sure whether they
+had watched it. All participants reported that they had not watched the
+\textit{Birth of Stars} video. When we asked participants about non-Khan
 Academy online courses, they reported having watched or taken courses on

### 2023-02-01 paper/main.tex
overhauled discussion section

@@
 
-Teaching, like effective writing and speaking, is fundamentally about
-empathy~\citep{AldrEtal22, StojEtal12, MeyeEtal19}. Great teachers consider
-students' interests~\citep{SwarEtal12, Clar10}, backgrounds~\citep{MuijReyn10,
-Rose76, denBEtal10}, and working memory capacities~\citep{Allo12}, and flexibly
-optimize their teaching strategies within those constraints~\citep{GoodEtal07,
-AndeEtal21, John02}. In the classroom, empathizing with students also means
-maintaining open lines of communication~\citep{WulfWulf10} by fostering an
-environment in which all students feel comfortable speaking up if they have an
-exciting new idea, or if they are having trouble understanding
-something~\citep{TurnBrai15, GarrRasm14}. In-person instruction also often
-entails dynamic student-teacher and student-student interactions. These
-in-person interactions can provide the instructor with valuable information
-about students' understanding of the course material, beyond what they can
-glean solely from exams or assignments~\citep{Engl09, vandEtal10c, HallWals02}.
-In turn, this can allow the instructor to adapt their teaching approaches
-on-the-fly according to students' questions and behaviors. But what does great
-teaching look like in asynchronous online courses, when the instructor
-typically prepares course lectures and materials without knowing who will
-ultimately be learning from them? Can the empathetic side of teaching be
-automated and scaled?
-
-The notion of empathy also related to ``theory of mind'' of other
-individuals~\citep{GoldWinn12, KansEtal15, Melt11}. Considering others' unique
-perspectives, prior experiences, knowledge, goals, etc., can help us to more
-effectively interact and communicate~\citep{ShaoEtal18, StepBaer06, Ratk18}.
-The knowledge and learning maps we estimate in our study
-(Fig.~\ref{fig:knowledge-maps}) hint at one potential form that an automated
-``empathetic'' teacher might take. We imagine automated content delivery
-systems that adapt lessons on the fly according to continually updated
-estimates of what students know and how quickly they are learning different
-conceptual content~\citep[e.g., building on ideas such as][and
-others]{AndeSkwa86, Half88, Kuma05, WolzEtal88}.
+We developed a computational framework that uses short multiple choice quizzes
+to provide nuanced insights into what learners know and how their knowledge
+changes with training. First, we show that our approach can automatically match
+up the conceptual content of individual questions with the corresponding
+moments in lecture videos where those concepts were presented
+(Fig.~\ref{fig:question-correlations}). Next, we demonstrate how we can
+estimate moment-by-moment ``knowledge traces'' that reflect how much knowledge
+participants have before and after watching each lecture video
+(Fig.~\ref{fig:knowledge-timeseries}). We also show that these knowledge
+estimates can generalize to held-out questions (Fig.~\ref{fig:predictions}).
+Finally, we use our framework to construct visual maps that provide snapshot
+estimates of how much participants know about any concept within the scope of
+our text embedding model, and how much their knowledge changes with training
+(Fig.~\ref{fig:knowledge-maps}).
 
@@
 For example, we can ask: what makes an effective course or training program?
-Which aspects of teaching might be optimized or automated? How can we provide  How and why do
-learning needs and goals vary across people? How might we lower barriers to
-achieving a high quality education?
+Which aspects of teaching might be optimized or automated? How can we provide
+How and why do learning needs and goals vary across people? How might we lower
+barriers to achieving a high quality education?
 
@@
 
-Ultimately, our work suggests a new line of questions regarding the future of
-education: which aspects of teaching can be optimized and/or automated? The
-social benefits of face-to-face instruction, such as social interactions,
-friendships, and emotional support, cannot (and perhaps should not) be fully
-replaced by an automated computer-based system. Nor can modern computer systems
-experience emotional empathy in the human sense of the word. On the other hand,
-perhaps it is possible to separate out the social aspects of classroom
-instruction from the purely learning-related aspects. Our study shows that text
-embedding models can uncover detailed insights into students' knowledge and how
-it changes over time during learning.  We hope that these advances might help
-pave the way for new ways of teaching or delivering educational content
-that are tailored to individual students' learning needs and goals.
+Beyond specifically predicting what people \textit{know}, the fundamental ideas
+we develop here also relate to the notion of ``theory of mind'' of other
+individuals~\citep{GoldWinn12, KansEtal15, Melt11}. Considering others' unique
+perspectives, prior experiences, knowledge, goals, etc., can help us to more
+effectively interact and communicate~\citep{ShaoEtal18, StepBaer06, Ratk18}.
+One could imagine future extensions of our work (e.g., analogous to the
+knowledge and learning maps shown in Fig.~\ref{fig:knowledge-maps}), that
+attempt to characterize how well-aligned different people's knowledge bases or
+backgrounds are. In turn, this might be used to model how knowledge flow not
+just between teachers and students, but between friends having a conversation,
+individuals out on a first date, participants at a business meeting, doctors
+and patients, experts and non-experts, political allies and adversaries, and
+more. For example, the extent to which two people's knowledge maps ``match'' in
+a given region of text embedding space might serve as a predictor of how
+effectively the people will communicate about the corresponding conceptual
+content.
+
+Ultimately, our work suggests a rich new line of questions about the ``form''
+of knowledge, how knowledge changes over time, and how we might map out the
+full space of what an individual knows. Our finding that detailed estimates
+about knowledge may be obtained from short quizzes shows one way that
+traditional approaches to evaluation in education might be extended. We hope
+that these advances might help pave the way for new ways of teaching or
+delivering educational content that are tailored to individual students'
+learning needs and goals.
 

### 2023-02-01 paper/main.tex
backing up

@@
 weights from lecture 1 are strongly correlated with the average topic weights
-from lecture 1 questions ($r(13) = XX, p = XX$, 95\% confidence interval
-(CI)~$= XX$), and the average topic weights from lecture 2 are strongly
-correlated with the average topic weights from lecture 2 questions ($r(13) =
-XX, p = XX, CI = XX$). At the same time, the average topics from two lectures
-are \textit{negatively} correlated ($r(13) = XX, p = XX, CI = XX$). The full
-set of pairwise comparisons between topic vectors for the lectures and each
-question set is reported in Figure~\topicWeights.
+from lecture 1 questions ($r(13) = 0.809, p < 0.001$, 95\% confidence interval
+(CI)~$= [0.633, 0.962]$), and the average topic weights from lecture 2 are
+strongly correlated with the average topic weights from lecture 2 questions
+($r(13) = 0.728, p = 0.002, CI = [0.456, 0.920]$). At the same time, the
+average topics from two lectures are \textit{negatively} correlated ($r(13) =
+-0.634, p = 0.011, CI = [-0.924, -0.237]$), indicating that the topic model
+also exhibits some degree of specificity. The full set of pairwise comparisons
+between topic vectors for the lectures and each question set is reported in
+Figure~\topicWeights.
 

### 2023-02-01 paper/main.tex
minor polish/edits

@@
 questions, tally up the proportion of correctly answered questions, and provide
-the student with feedback in the form of a letter grade. Although a numerical
-or letter grades give \textit{some} indication about whether the student has
-mastered the to-be-learned material, any single measure of performance on a
+the student with feedback in the form of a letter grade. Although numerical or
+letter grades give \textit{some} indication about whether the student has
+mastered the to-be-learned material, any univariate measure of performance on a
 complex task is at risk of conflating underlying factors, losing relevant
@@
 instructor annotations) Khan Academy course domain, ``Cosmology and
-Astronomy.'' Third, we sought to minimize dependencies and specific overalp
+Astronomy.'' Third, we sought to minimize dependencies and specific overlap
 between the videos. For example, we did not want participants' abilities to
@@
 described the unique mixture of broad themes from both lectures reflected in
-each window's content. Each window's ``topic vector'' (i.e., column of the
+each window's text. Each window's ``topic vector'' (i.e., column of the
 topic-proportions matrix) is a coordinate in a 15-dimensional space whose axes
@@
 
-We hypothesized that a topic model trained on transcripts of the two lectures,
+We hypothesized that a topic model trained on transcripts of the two lectures
 should also capture the conceptual knowledge probed by each quiz question. If
@@
 poor indicator of any \textit{specific} conceptual content in the lecture. We
-therefore also compared the variance in topic weights (across time or
+therefore also compared the variances in topic weights (across time or
 questions) between the lectures and questions. The variability in topic
@@
 questions (i.e., lecture 1 video versus lecture 2 questions; lecture 2 video
-versus lecture 1 questions) were \textit{negatively} correlated, and neither
+versus lecture 1 questions) were negatively correlated, and neither
 video's topic variability was reliably correlated with the topic variability
@@
 For example, if a particular question asks about the content from one small
-part of a lecture, we wondered whether our text embedding model could be used
-to automatically identify the ``matching'' moment(s) in the lecture. When we
-correlated each question's topic vector with the topic vectors for each second
+part of a lecture, we wondered whether the text embeddings could be used to
+automatically identify the ``matching'' moment(s) in the lecture. When we
+correlated each question's topic vector with the topic vectors from each second
 of the lectures, we found some evidence that each question is temporally
@@
 video and for each question) into a shared 2-dimensional space (see
-\nameref{subsec:knowledge-maps}). Next, we sampled
-points evenly from a $100 \times 100$ grid of coordinates that evenly tiled a
-rectangle enclosing the 2D projections of the videos and questions. We used
+\nameref{subsec:knowledge-maps}). Next, we sampled points from a $100 \times
+100$ grid of coordinates that evenly tiled a rectangle enclosing the 2D
+projections of the videos and questions. We used
 Equation~\ref{eqn:rbf-knowledge} to estimate participants' knowledge at each of
@@
 up the conceptual content of individual questions with the corresponding
-moments in lecture videos where those concepts were presented
+moments in lecture videos when those concepts were presented
 (Fig.~\ref{fig:question-correlations}). Next, we demonstrate how we can
 estimate moment-by-moment ``knowledge traces'' that reflect how much knowledge
-participants have before and after watching each lecture video
-(Fig.~\ref{fig:knowledge-timeseries}). We also show that these knowledge
-estimates can generalize to held-out questions (Fig.~\ref{fig:predictions}).
-Finally, we use our framework to construct visual maps that provide snapshot
-estimates of how much participants know about any concept within the scope of
-our text embedding model, and how much their knowledge changes with training
-(Fig.~\ref{fig:knowledge-maps}).
+participants have about each video's content before and after watching each
+lecture video (Fig.~\ref{fig:knowledge-timeseries}). We also show that these
+knowledge estimates can generalize to held-out questions
+(Fig.~\ref{fig:predictions}). Finally, we use our framework to construct visual
+maps that provide snapshot estimates of how much participants know about any
+concept within the scope of our text embedding model, and how much their
+knowledge changes with training (Fig.~\ref{fig:knowledge-maps}).
 
@@
 For example, we can ask: what makes an effective course or training program?
-Which aspects of teaching might be optimized or automated? How can we provide
-How and why do learning needs and goals vary across people? How might we lower
-barriers to achieving a high quality education?
+Which aspects of teaching might be optimized or automated? How and why do
+learning needs and goals vary across people? How might we lower barriers to
+achieving a high quality education?
 
@@
 attempt to characterize how well-aligned different people's knowledge bases or
-backgrounds are. In turn, this might be used to model how knowledge flow not
-just between teachers and students, but between friends having a conversation,
-individuals out on a first date, participants at a business meeting, doctors
-and patients, experts and non-experts, political allies and adversaries, and
-more. For example, the extent to which two people's knowledge maps ``match'' in
-a given region of text embedding space might serve as a predictor of how
-effectively the people will communicate about the corresponding conceptual
-content.
-
-Ultimately, our work suggests a rich new line of questions about the ``form''
-of knowledge, how knowledge changes over time, and how we might map out the
-full space of what an individual knows. Our finding that detailed estimates
-about knowledge may be obtained from short quizzes shows one way that
+backgrounds are. In turn, this might be used to model how knowledge (or other
+forms of communicable information) flows not just between teachers and
+students, but between friends having a conversation, individuals out on a first
+date, participants at a business meeting, doctors and patients, experts and
+non-experts, political allies or adversaries, and more. For example, the extent
+to which two people's knowledge maps ``match'' or ``align'' in a given region
+of text embedding space might serve as a predictor of how effectively the
+people will communicate about the corresponding conceptual content.
+
+Ultimately, our work suggests a rich new line of questions about the geometric
+``form'' of knowledge, how knowledge changes over time, and how we might map
+out the full space of what an individual knows. Our finding that detailed
+estimates about knowledge may be obtained from short quizzes shows one way that
 traditional approaches to evaluation in education might be extended. We hope
@@
 multiple-choice quizzes: the first before viewing lecture 1, the second between
-lectures 1 and 2, and the third after viewing lecture 2 (Fig.~\ref{fig:experiment}).
-The questions appearing on each quiz, for each participant, were randomly
-chosen from the full set of 39, with the constraints that (a) each quiz contain 5
-questions about lecture 1, 5 questions about lecture 2, and 3 questions about general physics knowledge, and
-(b) each question appear exactly once for each participant. The order of questions on each quiz,
-and the order of answer options for each question, were also randomized. Our
-experimental protocol was approved by the Committee for the Protection of
-Human Subjects at Dartmouth College.  We used the experiment to develop
-and test our computational framework for estimating knowledge and learning.
+lectures 1 and 2, and the third after viewing lecture 2
+(Fig.~\ref{fig:experiment}). The questions appearing on each quiz, for each
+participant, were randomly chosen from the full set of 39, with the constraints
+that (a) each quiz contain 5 questions about lecture 1, 5 questions about
+lecture 2, and 3 questions about general physics knowledge, and (b) each
+question appear exactly once for each participant. The orders of questions on
+each quiz, and the orders of answer options for each question, were also
+randomized. Our experimental protocol was approved by the Committee for the
+Protection of Human Subjects at Dartmouth College. We used the experiment to
+develop and test our computational framework for estimating knowledge and
+learning.
 
@@
 Conceptually, each topic is intended to give larger weights to words that are
-conceptually related or that tend to co-occur in the same documents. After
+semantically related or that tend to co-occur in the same documents. After
 fitting a topic model, each document in the training set, or any \textit{new}
@@
 corpus of documents using overlapping sliding windows that span each video's
-transcript. Khan Academy provides professionally created, manual 
-transcriptions of all videos for closed captioning. However, such transcripts 
-would not be readily available in all contexts to which our framework could 
-potentially be applied. Khan Academy videos are hosted on the YouTube 
-platform, which additionally provides automated captions. We opted to use 
-these automated transcripts (which, in prior work, we have found are 
-sufficiently near-human quality yield reliable data in behavioral studies; 
-\citealp{ZimaEtal18}) when developing our framework in order to make it 
-more easily extensible and adaptable by others in the future.
+transcript. Khan Academy provides professionally created, manual transcriptions
+of all videos for closed captioning. However, such transcripts would not be
+readily available in all contexts to which our framework could potentially be
+applied. Khan Academy videos are hosted on the YouTube platform, which
+additionally provides automated captions. We opted to use these automated
+transcripts (which, in prior work, we have found are sufficiently near-human
+quality yield reliable data in behavioral studies; \citealp{ZimaEtal18}) when
+developing our framework in order to make it more directly extensible and
+adaptable by others in the future.
 
@@
 
-Although UMAP is not fully invertible, due to its clustering step, it is
-possible to approximately invert the embedded low-dimensional points. In our
-application, we sought to embed topic vectors, whose elements are always
-non-negative. Because the inversion step is inexact, sometimes it results in
-negative-valued vectors (even if the original observations were all
-non-negative), which are incompatable with the topic modeling framework. To
-protect against this issue, we log-transformed the topic vectors prior to
-embedding them in the 2D space. When we inverted the embedded vectors (e.g., to
-estimate topic vectors or word clouds, as in Fig.~\ref{fig:knowledge-maps}C),
-we passed to inverted (log-transformed) values through the exponential function
-to obtain a vector of non-negative values.
+In our application, all of the coordinates we embedded were topic vectors,
+whose elements are always non-negative. Although UMAP is an invertible
+transformation at the embedding locations of the original data, other locations
+in the embedding space will not necessarily follow the same implicit ``rules''
+as the original high-dimensional data. For example, inverting an arbitrary
+coordinate in the embedding space might result in negative-valued vectors,
+which are incompatable with the topic modeling framework. To protect against
+this issue, we log-transformed the topic vectors prior to embedding them in the
+2D space. When we inverted the embedded vectors (e.g., to estimate topic
+vectors or word clouds, as in Fig.~\ref{fig:knowledge-maps}C), we passed the
+inverted (log-transformed) values through the exponential function to obtain a
+vector of non-negative values.
 
@@
 sought to estimate participants' knowledge (and learning, i.e., changes in
-knowledge) at each of the resulting 10K coordinates.
+knowledge) at each of the resulting 10,000 coordinates.
 

### 2023-02-01 paper/supplement.tex

@@
 \begin{figure}[tp]
-    \centering
     \includegraphics[width=\textwidth]{figs/topic-weights}
 
-\caption{\textbf{Averarge topic weights for each lecture and question type}.
-The bar plots display the variance of each topic's weight across lecture
-timepoints (top row) and questions (bottom row); colors denote topics. The
-top-weighted words from the most heavily weighted topics are displayed in the
-upper right (orange: topic 2; yellow-green: topic 4). The top-weighted words
-from the full set of topics may be found in Table~S2. Also see
-Figure~\topics A in the main text.}
+\caption{\textbf{Topic weights. A. Average topic weights for each lecture and
+question type}. The bar plots display each topic's average weight across
+lecture timepoints (top row) and questions (bottom row); colors denote topics.
+The top-weighted words from the highest-weighted topic from each lecture are
+displayed in the upper right (orange: topic 2; yellow-green: topic 4). The
+top-weighted words from the full set of topics may be found in
+Table~\ref{tab:topics}. \textbf{B. Relationships between average topic
+weights.} Pairwise correlations between the distributions of average topic
+weights for each lecture and question category. Each row and column corresponds
+to a bar plot in Panel A. Also see Figure~\topics A in the main text.}
 

### 2023-02-01 paper/main.tex
final pass through intro

@@
 
-\title{Text embedding models yield high resolution insights into conceptual
-knowledge from short multiple choice quizzes}
+\title{Text embedding models yield high-resolution insights into conceptual
+knowledge from short multiple-choice quizzes}
 
@@
 concepts. We test our approach using behavioral data from participants who
-answered small sets of multiple choice quiz questions interleaved between
+answered small sets of multiple-choice quiz questions interleaved between
 watching two course videos from the Khan Academy platform. We applied our
-framework to the videos' transcripts, and to text of the quiz questions, to
+framework to the videos' transcripts and the text of the quiz questions to
 quantify the content of each moment of video and each quiz question. We used
@@
 learners' knowledge changed after watching each video. Our findings show how a
-small set of quiz questions may be used to obtain rich and meaningful high
-resolution insights into what each learner knows, and how their knowledge
+small set of quiz questions may be used to obtain rich and meaningful, high-resolution
+insights into what each learner knows, and how their knowledge
 changes over time as they learn.
@@
 
-Suppose that a teacher had access to a complete tangible ``map'' of everything
+Suppose that a teacher had access to a complete, tangible ``map'' of everything
 a student knew. Defining what such a map might even look like, let alone how it
@@
 
-A common approach to assessing students' learning is to compile a set of quiz
-questions, tally up the proportion of correctly answered questions, and provide
-the student with feedback in the form of a letter grade. Although numerical or
-letter grades give \textit{some} indication about whether the student has
+A common approach to assessing a student's knowledge is to present them with a set of quiz
+questions, calculate the proportion they answer correctly, and provide
+them with feedback in the form of a simple numeric or letter grade. While such a
+grade can provide \textit{some} indication of whether the student has
 mastered the to-be-learned material, any univariate measure of performance on a
-complex task is at risk of conflating underlying factors, losing relevant
-information, and so on. For example, consider the relative utility of the
-imaginary map described above that characterizes in detail a student's
-knowledge, versus a single annotation saying that the student answered 85\% of
+complex task sacrifices certain relevant information, risks conflating underlying
+factors, and so on. For example, consider the relative utility of the
+imaginary map described above that characterizes a student's knowledge
+in detail, versus a single annotation saying that the student answered 85\% of
 their quiz questions correctly, or that they received a `B'. Here, we show that
-the same quiz data required to compute proportion correct scores or letter
-grades can be used to instead obtain much more detailed insights into what the
+the same quiz data required to compute proportion-correct scores or letter
+grades can instead be used to obtain much more detailed insights into what the
 student knows at the time they took the quiz.
@@
 researchers in education, cognitive psychology, and cognitive
-neuroscience~\citep[e.g.,][]{Kato40, Gall00, ScotEtal07, HallGree08, Macl05}
+neuroscience (e.g.,~\citealp{Kato40, Gall00, ScotEtal07, HallGree08, Macl05})
 has profound analogs in the fields of natural language processing and natural
@@
 might provide some ability to answer simple questions about it. However, text
-embedding models~\citep[e.g.,][]{LandDuma97, DeerEtal90, BleiEtal03,
-BleiLaff06, MikoEtal13a, CerEtal18, BrowEtal20} also attempt to capture the
+embedding models (e.g.,~\citealp{LandDuma97, DeerEtal90, BleiEtal03,
+BleiLaff06, MikoEtal13a, CerEtal18, BrowEtal20}) also attempt to capture the
 deeper meaning \textit{underlying} those atomic elements. These models consider
@@
 able to assign nearby feature vectors to two conceptually related documents,
-\textit{even when the words contained in those documents have very little
+\textit{even when the specific words contained in those documents have very little
 overlap}.
@@
 
-Here we develop a framework for modeling how knowledge is acquired during
-learning. The central idea is to use text embedding models to define the
+Here we develop a framework for modeling how conceptual knowledge is acquired during
+learning. The central idea behind our framework is to use text embedding models to define the
 coordinate systems of two maps: (a) a \textit{knowledge map} that describes the
@@
 and interpret behavioral data collected from an experiment that had
-participants watch and answer multiple-choice questions about a series of
+participants answer sets multiple-choice questions about a series of
 recorded course lectures.
@@
 acquire deep, real-world conceptual knowledge. Traditional laboratory
-approaches to studying learning and memory (e.g., list learning studies) often
+approaches to studying learning and memory (e.g., list-learning studies) often
 draw little distinction between memorization and understanding. Instead, these
@@
 \textit{useful} ways in the future. In this sense, the gap between modern
-learning theories and modern pedagogical approaches and classroom learning
+learning theories and modern pedagogical approaches that inform classroom learning
 strategies is enormous: most of our theories about \textit{how} people learn
@@
     \caption{\textbf{Experimental paradigm.} Participants alternate between
-    answering 13-question multiple-choice quizzes and watching two Khan Academy
+    completing three 13-question multiple-choice quizzes and watching two Khan Academy
     lectures. Each quiz contains a mix of 5 questions about lecture 1, 5

### 2023-02-01 paper/main.tex

@@
 Or weaving a lecture's atomic elements (e.g., its component words) into a
-structured network that describes how those individual elements are related?
-Conceptual understanding could also involve building a mental model that
-transcends the meanings of those individual atomic elements by reflecting the
-deeper meaning underlying the gestalt whole~\citep{Kint70, Macl05, ScotEtal07}.
+structured network that describes how those individual elements are
+related~\citep{LeeChen22}? Conceptual understanding could also involve building
+a mental model that transcends the meanings of those individual atomic elements
+by reflecting the deeper meaning underlying the gestalt whole~\citep{Kint70,
+Macl05, ScotEtal07}.
 
@@
 
-Here we develop a framework for modeling how conceptual knowledge is acquired during
-learning. The central idea behind our framework is to use text embedding models to define the
-coordinate systems of two maps: (a) a \textit{knowledge map} that describes the
-extent to which each concept is currently known and (b) a \textit{learning map}
-that describes changes in knowledge over time. Each location on these maps
-represents a single concept, and the maps' geometries are defined such that
-related concepts are located nearby in space. We use this framework to analyze
-and interpret behavioral data collected from an experiment that had
-participants answer sets multiple-choice questions about a series of
+Here we develop a framework for modeling how conceptual knowledge is acquired
+during learning. The central idea behind our framework is to use text embedding
+models to define the coordinate systems of two maps: (a) a \textit{knowledge
+map} that describes the extent to which each concept is currently known and (b)
+a \textit{learning map} that describes changes in knowledge over time. Each
+location on these maps represents a single concept, and the maps' geometries
+are defined such that related concepts are located nearby in space. We use this
+framework to analyze and interpret behavioral data collected from an experiment
+that had participants answer sets multiple-choice questions about a series of
 recorded course lectures.
@@
 \textit{useful} ways in the future. In this sense, the gap between modern
-learning theories and modern pedagogical approaches that inform classroom learning
-strategies is enormous: most of our theories about \textit{how} people learn
-are inspired by experimental paradigms and models that have only peripheral
-relevance to the kinds of learning that students and teachers actually
-seek~\citep{Macl05, HallGree08}. To help bridge this gap, our study uses course
-materials from real online courses to inform, fit, and test models of
-real-world conceptual learning. We also provide a demonstration of how our
+learning theories and modern pedagogical approaches that inform classroom
+learning strategies is enormous: most of our theories about \textit{how} people
+learn are inspired by experimental paradigms and models that have only
+peripheral relevance to the kinds of learning that students and teachers
+actually seek~\citep{Macl05, HallGree08}. To help bridge this gap, our study
+uses course materials from real online courses to inform, fit, and test models
+of real-world conceptual learning. We also provide a demonstration of how our
 models can be used to construct ``maps'' of what students know, and how their
@@
 (and changes in knowledge), we hope that such maps might lead to real-world
-tools for improving how we educate.
+tools for improving how we educate. Taken together, our work shows that
+existing course materials and evaluative tools like short multiple-choice
+quizzes may be leveraged to gain highly detailed insights into what students
+know and how they learn.
 

### 2023-02-01 paper/main.tex
final edits through end of results

@@
 language processing models, for tracking and characterizing the acquisition of
-conceptual knowledge. Our approach embeds each concept in a high dimensional
+conceptual knowledge. Our approach embeds each concept in a high-dimensional
 representation space, where nearby coordinates reflect similar or related
 concepts. We test our approach using behavioral data from participants who
-answered small sets of multiple-choice quiz questions interleaved between
-watching two course videos from the Khan Academy platform. We applied our
+answered small sets of multiple-choice quiz questions, interleaved between
+watching two course videos from the Khan Academy platform. We apply our
 framework to the videos' transcripts and the text of the quiz questions to
-quantify the content of each moment of video and each quiz question. We used
+quantify the content of each moment of video and each quiz question. We use
 these embeddings, along with participants' quiz responses, to track how the
@@
 (e.g., its constituent symbols, letters, and words) might provide some
-information about what the document is about, just as memorizing a passage
+clues as to what the document is about, just as memorizing a passage
 might provide some ability to answer simple questions about it. However, text
@@
 meaning of a document may be captured by a feature vector in a high-dimensional
-representation space, where nearby vectors reflect conceptually related
-documents. A model that succeeds at capturing an analog of ``understanding'' is
+representation space, wherein nearby vectors reflect conceptually related
+documents. A model that succeeds at capturing an analogue of ``understanding'' is
 able to assign nearby feature vectors to two conceptually related documents,
@@
 
-Given these insights, what form might the representation of the sum total of a
+Given these insights, what form might a representation of the sum total of a
 person's knowledge take? First, we might require a means of systematically
@@
 during learning. The central idea behind our framework is to use text embedding
-models to define the coordinate systems of two maps: (a) a \textit{knowledge
-map} that describes the extent to which each concept is currently known and (b)
+models to define the coordinate systems of two maps: a \textit{knowledge
+map} that describes the extent to which each concept is currently known, and
 a \textit{learning map} that describes changes in knowledge over time. Each
@@
 Second, we want our approach to be potentially scalable to large numbers of
-concepts, courses, and students. This requires the conceptual content of
-interest to be discovered \textit{automatically}, rather than relying on
+concepts, courses, and students. This requires that the conceptual content of
+interest be discovered \textit{automatically}, rather than relying on
 manually produced ratings or labels.
@@
 quizzes. Quiz 1 was intended to assess participants' ``baseline'' knowledge
-before training, quiz 2 assessed knowledge after watching the \textit{Four
-Fundamental Forces} video (i.e., lecture 1), and quiz 3 assessed knowledge
+before training, Quiz 2 assessed knowledge after watching the \textit{Four
+Fundamental Forces} video (i.e., lecture 1), and Quiz 3 assessed knowledge
 after watching the \textit{Birth of Stars} video (i.e., lecture 2).
@@
 from sliding windows of text.} We decompose each lecture's transcript into a
-series of overlapping sliding windows. The set of transcript snippets (across
+series of overlapping sliding windows. The full set of transcript snippets (across
 all windows) may be treated as a set of ``documents'' for training a text
@@
 This results in one trajectory per lecture and one coordinate for each
-question. Here we have projected the 15-dimensional embeddings onto their first
+question. Here, we have projected the 15-dimensional embeddings onto their first
 3 principal components for visualization.}
@@
 the latent themes in the lectures using a topic model~\citep{BleiEtal03}.
-Briefly, topic models take as input a collection of text documents and learn a
+Briefly, topic models take as input a collection of text documents, and learn a
 set of ``topics'' (i.e., latent themes) from their contents. Once fit, a topic
@@
 two lectures into overlapping sliding windows, where each window contained the
-text of the lecture transcript from a particular time range. We treated the set
+text of the lecture transcript from a particular time span. We treated the set
 of text snippets (across all of these windows) as documents to fit our model
@@
 each window's text. Each window's ``topic vector'' (i.e., column of the
-topic-proportions matrix) is a coordinate in a 15-dimensional space whose axes
+topic-proportions matrix) is analogous to a coordinate in a 15-dimensional space whose axes
 are topics discovered by the model. Within this space, each lecture's sequence
@@
 content of the lectures (i.e., beyond surface-level details such as particular
-word choices) then we should be able to recover a correspondence between each
+word choices), then we should be able to recover a correspondence between each
 lecture and questions \textit{about} each lecture. Importantly, such a
@@
 different words. Simply comparing the average topic weights from each lecture
-and question sets (averaging across time and questions, respectively) reveals a
+and question set (averaging across time and questions, respectively) reveals a
 striking correspondence (Fig.~\topicWeights). Specifically, the average topic
 weights from lecture 1 are strongly correlated with the average topic weights
-from lecture 1 questions ($r(13) = 0.809, p < 0.001$, 95\% confidence interval
-(CI)~$= [0.633, 0.962]$), and the average topic weights from lecture 2 are
+from lecture 1 questions ($r(13) = 0.809,~p < 0.001$, 95\% confidence interval
+(CI)~$= [0.633,~0.962]$), and the average topic weights from lecture 2 are
 strongly correlated with the average topic weights from lecture 2 questions
-($r(13) = 0.728, p = 0.002, CI = [0.456, 0.920]$). At the same time, the
-average topics from two lectures are \textit{negatively} correlated ($r(13) =
--0.634, p = 0.011, CI = [-0.924, -0.237]$), indicating that the topic model
+($r(13) = 0.728,~p = 0.002$, 95\% CI~$= [0.456,~0.920]$). At the same time, the
+average topic weights from the two lectures are \textit{negatively} correlated with 
+their non-matching question sets (lecture 1 video vs.~lecture 2 questions: $r(13) = 
+-0.547,~p = 0.035$, 95\% CI~$= [-0.812, ~-0.231]$; lecture 2 video vs.~lecture 1 questions: $r(13) 
+= -0.612,~p = 0.015$, 95\% CI~$= [-0.874,~-0.281]$), indicating that the topic model
 also exhibits some degree of specificity. The full set of pairwise comparisons
-between topic vectors for the lectures and each question set is reported in
+between average topic weights for the lectures and question sets is reported in
 Figure~\topicWeights.
@@
 weight variability.} Pairwise correlations between the distributions of topic
-weight variance for each lecture and question category. Each row and column
+weight variance for each lecture and question set. Each row and column
 corresponds to a bar plot in Panel A.}
@@
 Intuitively, the variability in the expression of a given topic relates to how
-much ``information''~\citep{Fish22} the lecture (or questions) reflect about
+much ``information''~\citep{Fish22} the lecture (or question set) reflects about
 that topic. For example, suppose a given topic is weighted on heavily
@@
 expression (over time and across questions) was similar for the lecture 1 video
-and questions ($r(13) = 0.824,~p<0.001, CI = [0.696, 0.973]$) and the lecture 2
-video and questions ($r(13) = 0.801,~p<0.001,~95\%~\mathrm{CI} = [0.539,
-0.958]$). However, as reported in Figure~\ref{fig:topics}B, the variability in
+and questions ($r(13) = 0.824,~p<0.001$, 95\% CI~$= [0.696,~0.973]$) and the lecture 2
+video and questions ($r(13) = 0.801,~p<0.001$, 95\% CI~$= [0.539,~0.958]$). 
+However, as reported in Figure~\ref{fig:topics}B, the variability in
 topic expressions across \textit{different} videos and lecture-specific
-questions (i.e., lecture 1 video versus lecture 2 questions; lecture 2 video
-versus lecture 1 questions) were negatively correlated, and neither
+questions (i.e., lecture 1 video vs.~lecture 2 questions; lecture 2 video
+vs.~lecture 1 questions) were negatively correlated, and neither
 video's topic variability was reliably correlated with the topic variability
@@
 reported in Figures~\ref{fig:topics} and~\topicWeights~indicate that a topic
-model fit to the videos' transcripts can also reveal correspondances (at a
-coarse scale) between the lectures and (held-out) questions.
+model fit to the videos' transcripts can also reveal correspondences (at a
+coarse scale) between the lectures and questions.
 
@@
 specific (Fig.~\ref{fig:question-correlations}). In particular, most questions'
-topic vectors were maximally correlated with a well-defined (and relatively
+topic vectors were maximally correlated with a well defined (and relatively
 narrow) range of timepoints from their corresponding lectures, and the
-correlations fell off sharply outside of that range. We also examined the
-best-matching intervals for each question qualitatively by comparing the text
+correlations fell off sharply outside of that range. We also qualitatively examined the
+best-matching intervals for each question by comparing the text
 of the question to the text of the most-correlated parts of the lectures.
@@
 training set, in general we found (through manual inspection) a close
-correspondence between the conceptual content that each question covered and
+correspondence between the conceptual content that each question probed and
 the content covered by the best-matching moments of the lectures. Two
@@
 infer participants' knowledge at the scale of individual concepts (e.g., as
-captured by a single question).
+captured by a single moment of a lecture).
 
@@
 this approach separately for the questions from each quiz the participants took
-throughout the experiment. From just 13 questions per quiz, we obtain a
+throughout the experiment. From just a few questions per quiz, we obtain a
 high-resolution snapshot (at the time each quiz was taken) of what the
 participants knew about any moment's content, from either of the two lectures
-they watched (comprising a total of 1106 samples across the two lectures).
+they watched (comprising a total of 1,100 samples across the two lectures).
 
@@
 the \textit{Four Fundamental Forces} was substantially higher on Quiz 2 versus
-Quiz 1 ($t(49) = 8.764, p < 0.001$) and on Quiz 3 versus Quiz 1 ($t(49) =
-10.519, p < 0.001$). We found no reliable differences in estimated knowledge
-about that lecture's content on Quiz 2 versus 3 ($t(49) = 0.160, p = 0.874$).
+Quiz 1 ($t(49) = 8.764,~p < 0.001$) and on Quiz 3 versus Quiz 1 ($t(49) =
+10.519,~p < 0.001$). We found no reliable differences in estimated knowledge
+about that lecture's content on Quiz 2 versus 3 ($t(49) = 0.160,~p = 0.874$).
 Similarly, we hypothesized (and subsequently confirmed) that participants
@@
 reliable differences in estimated knowledge about the \textit{Birth of Stars}
-lecture content on Quizzes 1 versus 2 ($t(49) = 1.013, p = 0.316$), but the
+lecture content on Quizzes 1 versus 2 ($t(49) = 1.013,~p = 0.316$), but the
 estimated knowledge was substantially higher on Quiz 3 versus 2 ($t(49) =
-10.561, p < 0.001$) and Quiz 3 versus 1 ($t(49) = 8.969, p < 0.001$).
+10.561,~p < 0.001$) and Quiz 3 versus 1 ($t(49) = 8.969,~p < 0.001$).
 
 If we are able to accurately estimate a participant's knowledge about the
-content tested by a given question, the estimated knowledge should have some
+content tested by a given question, our estimates of their knowledge should carry some
 predictive information about whether the participant is likely to answer the
-question correctly or incorrectly. For each question in turn, for each
+question correctly or incorrectly. We developed a statistical approach to test this claim. 
+For each question in turn, for each
 participant, we used Equation~\ref{eqn:prop} to estimate (using all
@@
     distributions of predicted knowledge at the embedding coordinates of each
-    held out correctly (blue) or incorrectly (red) answered question. The
+    held-out correctly (blue) or incorrectly (red) answered question. The
     $t$-tests reported in each panel are between the distributions of estimated
@@
 the held-out question had been correctly versus incorrectly answered ($t(633) =
-0.577, p = 0.564$). After watching the first video, estimated knowledge for
+0.577,~p = 0.564$). After watching the first video, estimated knowledge for
 held-out correctly answered questions (from the second quiz;
 Fig.~\ref{fig:predictions}, middle panel) exhibited a positive shift relative
-to held-out incorrectly answered questions ($t(633) = 3.961, p < 0.001$). After
+to held-out incorrectly answered questions ($t(633) = 3.961,~p < 0.001$). After
 watching the second video, estimated knowledge (from the third quiz;
@@
 correctly answered questions was larger than for held-out incorrectly answered
-questions ($t(628) = 2.045, p = 0.041$).
+questions (estimated knowledge for correctly versus incorrectly answered 
+Quiz 3 questions: $t(628) = 2.045,~p = 0.041$).
 
@@
     \nameref{subsec:knowledge-maps}). The topic trajectories of each
-    lecture and the coordinates of each question are indicated by dotted lines
-    and dots. Each map reflects an average across all participants. For
+    lecture are indicated by dotted lines, and the coordinates of each question are indicated by
+    dots. Each map reflects an average across all participants. For
     individual participants' maps, see
@@
     and~\individualKnowledgeMapsC. \textbf{B. Average ``learning maps''
-    estimated between each successive pair of quizzes.} The learning maps are
-    in the same general format as the knowledge maps in Panel A, but each
-    coordinate in the learning maps indicates the \textit{difference} between
+    estimated between each successive pair of quizzes.} The learning maps follow
+    the same general format as the knowledge maps in Panel A, but here the shading at each
+    coordinate indicates the \textit{difference} between
     the corresponding coordinates in the indicated \textit{pair} of knowledge
-    maps---i.e., how much the estimated knowledge ``changed'' across the two
+    maps---i.e., how much the estimated knowledge ``changed'' between the two
     quizzes. Each map reflects an average across all participants. For
@@
     the relative weights of each word (via their relative sizes) reflected by the blend of topics
-    represented at the locations of the stars in the maps. The words' colors
+    represented at the locations of the stars on the maps. The words' colors
     indicate how much each word is weighted, on average, across all timepoints'
@@
 We projected the resulting 100-dimensional topic vectors (for each second of
-video and for each question) into a shared 2-dimensional space (see
+video and for each question) onto a shared 2-dimensional plane (see
 \nameref{subsec:knowledge-maps}). Next, we sampled points from a $100 \times
@@
 Equation~\ref{eqn:rbf-knowledge} to estimate participants' knowledge at each of
-these 10,000 sampled locations, and we averaged these estimates across
+these 10,000 sampled locations, and averaged these estimates across
 participants to obtain an estimated average \textit{knowledge map}
-(Fig.~\ref{fig:knowledge-maps}). Intuitively, the knowledge map constructed
+(Fig.~\ref{fig:knowledge-maps}A). Intuitively, the knowledge map constructed
 from a given quiz's responses provides a visualization of how ``much''
@@
 Several features of the resulting knowledge maps are worth noting. The average
-knowledge map estimated from Quiz 1 responses (Fig.~\ref{fig:knowledge-maps},
+knowledge map estimated from Quiz 1 responses (Fig.~\ref{fig:knowledge-maps}A,
 leftmost map) shows that participants tended to have relatively little
@@
 shows a marked increase in knowledge on the left side of the map (around
-roughly the same range of coordinates covered by the \textit{Four Fundamental
+roughly the same range of coordinates traversed by the \textit{Four Fundamental
 Forces} lecture, indicated by the dotted blue line). In other words,
@@
 content that is nearby (i.e., related to) the content from the lecture they
-watched prior to taking Quiz 2. This localization is non-trivial: the knowledge
+watched prior to taking Quiz~2. This localization is non-trivial: the knowledge
 estimates are informed only by the embedded coordinates of the \textit{quiz
 questions}, not by the embeddings of either lecture
-(Eqn.~\ref{eqn:rbf-knowledge}). Finally, the knowledge map estimated from Quiz
+(see Eqn.~\ref{eqn:rbf-knowledge}). Finally, the knowledge map estimated from Quiz
 3 responses shows a second increase in knowledge, localized to the region
 surrounding the embedding of the \textit{Birth of Stars} lecture participants
-watched prior to taking Quiz 3.
+watched immediately prior to taking Quiz 3.
 
 Another way of visualizing these content-specific increases in knowledge
-(apparently driven by watching each lecture) is displayed in
+after participants viewed each lecture is displayed in
 Figure~\ref{fig:knowledge-maps}B. Taking the point-by-point difference between
@@
 Because the 2D projection we used to construct the knowledge and learning maps
-is invertible, we may gain additional insights into the estimates
-by reconstructing the original high-dimensional topic vectors for any point(s)
-in the maps we are interested in. For example, this could serve as a useful
+is invertible, we may gain additional insights into these maps' meaning
+by reconstructing the original high-dimensional topic vector for any location
+on the map we are interested in. For example, this could serve as a useful
 tool for an instructor looking to better understand which content areas a
@@
 the \textit{Four Fundamental Forces} embedding (yellow); a second point near
-the \textit{Birth of Stars} embedding (orange), and a third point somewhere in
+the \textit{Birth of Stars} embedding (orange), and a third point
 between the two lectures' embeddings (pink). As shown in the word clouds in the

### 2023-02-01 paper/main.tex
edits through discussion

@@
 specific (Fig.~\ref{fig:question-correlations}). In particular, most questions'
-topic vectors were maximally correlated with a well defined (and relatively
+topic vectors were maximally correlated with a well-defined (and relatively
 narrow) range of timepoints from their corresponding lectures, and the
@@
 
-We developed a computational framework that uses short multiple choice quizzes
-to provide nuanced insights into what learners know and how their knowledge
+We developed a computational framework that uses short multiple-choice quizzes
+to gain nuanced insights into what learners know and how their knowledge
 changes with training. First, we show that our approach can automatically match
-up the conceptual content of individual questions with the corresponding
+the conceptual knowledge probed by individual quiz questions to the corresponding
 moments in lecture videos when those concepts were presented
 (Fig.~\ref{fig:question-correlations}). Next, we demonstrate how we can
-estimate moment-by-moment ``knowledge traces'' that reflect how much knowledge
-participants have about each video's content before and after watching each
-lecture video (Fig.~\ref{fig:knowledge-timeseries}). We also show that these
-knowledge estimates can generalize to held-out questions
+estimate moment-by-moment ``knowledge traces'' that reflect the degree of knowledge
+participants have about each video's time-varying content, and capture temporally 
+specific increases in knowledge after viewing each lecture (Fig.~\ref{fig:knowledge-timeseries}).
+ We also show that these knowledge estimates can generalize to held-out questions
 (Fig.~\ref{fig:predictions}). Finally, we use our framework to construct visual
@@
 
-Over the past several years, the global pandemic has forced many educators to
+Over the past several years, the global pandemic has forced numerous educators to
 teach remotely~\citep{MoseEtal21, ShimLee20, KawaEtal21, Whal20}. This change
@@
 facilitated improvements in video streaming, enabling videos to be easily
-downloaded and shared by large segments of the world's population. This
+shared and viewed by large segments of the world's population. This
 exciting time for online course instruction provides an opportunity to
@@
 For example, we can ask: what makes an effective course or training program?
-Which aspects of teaching might be optimized or automated? How and why do
+Which aspects of teaching might be optimized and/or augmented by automated tools? How and why do
 learning needs and goals vary across people? How might we lower barriers to
-achieving a high quality education?
+achieving a high-quality education?
 
@@
 key step will be to understand which sorts of signals derived from behaviors
-and/or other measurements~\citep[e.g., neurophysiological data; ][]{NguyEtal22,
-MeshEtal20, PoulEtal17, BeviEtal19, DikkEtal17} might help to inform these
+and/or other measurements (e.g., neurophysiological data;~\citealp{NguyEtal22,
+MeshEtal20, PoulEtal17, BeviEtal19, DikkEtal17}) might help to inform these
 models. A third major step will be to develop and employ reliable ways of
@@
 forms of communicable information) flows not just between teachers and
-students, but between friends having a conversation, individuals out on a first
+students, but between friends having a conversation, individuals on a first
 date, participants at a business meeting, doctors and patients, experts and
@@
 to which two people's knowledge maps ``match'' or ``align'' in a given region
-of text embedding space might serve as a predictor of how effectively the
-people will communicate about the corresponding conceptual content.
+of text embedding space might serve as a predictor of how effectively they 
+will be able to communicate about the corresponding conceptual content.
 
@@
 estimates about knowledge may be obtained from short quizzes shows one way that
-traditional approaches to evaluation in education might be extended. We hope
-that these advances might help pave the way for new ways of teaching or
+traditional approaches to evaluation in education may be extended. We hope
+that these advances might help pave the way for new approaches to teaching or
 delivering educational content that are tailored to individual students'

### 2023-02-01 paper/main.tex
final edits to paper

@@
 
-Over the past several years, the global pandemic has forced numerous educators to
+Over the past several years, the global pandemic has forced many educators to
 teach remotely~\citep{MoseEtal21, ShimLee20, KawaEtal21, Whal20}. This change
@@
 Participants received course credit for enrolling. We asked each participant to
-fill out a demographic survey that included questions about their age, gender,
+complete a demographic survey that included questions about their age, gender,
 native spoken language, ethnicity, race, hearing, color vision, sleep, coffee
@@
 Conceptually, each topic is intended to give larger weights to words that are
-semantically related or that tend to co-occur in the same documents. After
+semantically related or tend to co-occur in the same documents. After
 fitting a topic model, each document in the training set, or any \textit{new}
@@
 additionally provides automated captions. We opted to use these automated
-transcripts (which, in prior work, we have found are sufficiently near-human
+transcripts (which, in prior work, we have found are of sufficiently near-human
 quality yield reliable data in behavioral studies; \citealp{ZimaEtal18}) when
@@
 lemmatizing, removing punctuation and stop-words), we treated the text from
-each sliding window as a single ``document,'' and we combined these documents
+each sliding window as a single ``document,'' and combined these documents
 across the two videos' windows to create a single training corpus for the topic
@@
 
-After fitting a topic model to each videos' transcripts, we could use the
+After fitting a topic model to the two videos' transcripts, we could use the
 trained model to transform arbitrary (potentially new) documents into
@@
 correlations between any lecture timepoint and question, taken over all
-timepoints and questions across both lectures and all five question used to
-estimate the knowledge trace. We also define $f(s, \Omega)$ as the
+timepoints in the given lecture, and all five questions \textbf{about} that lecture appearing on the given quiz. 
+We also define $f(s, \Omega)$ as the
 $s$\textsuperscript{th} topic vector from the set of topic vectors $\Omega$.
@@
 At a high level, the UMAP algorithm obtains low-dimensional embeddings by
-minimizing the cross entropy between the pairwise (clustered) distances between
+minimizing the cross-entropy between the pairwise (clustered) distances between
 the observations in their original (e.g., 100-dimensional) space and the
@@
 We acknowledge useful discussions, assistance in setting up an earlier
-(unpublished) version of this study, and assistance with some of the data
+(unpublished) version of this study, and assistance with data
 collection efforts from Will Baxley, Max Bluestone, Daniel Carstensen, Kunal

### 2023-02-01 code/khan_helpers/khan_helpers/experiment.py
cleanup and documentation for khan_helpers package

@@ -16,8 +16,20 @@ from .functions import _ts_to_sec
 
 
 class LazyLoader:
-    # Descriptor class that handles deferred loading and caching of data
+    """
+    Descriptor class that handles deferred loading and caching of data
+    """
     def __init__(self, loader, *loader_args, **loader_kwargs):
+        """
+        Parameters
+        ----------
+        loader : str
+            The name of the instance method with which to load the data.
+        *loader_args : tuple, optional
+            Positional arguments to pass to `loader`.
+        **loader_kwargs : dict, optional
+            Keyword arguments to pass to `loader`.
+        """
         self.loader = loader
         self.loader_args = loader_args
         self.loader_kwargs = loader_kwargs
@@ -31,6 +43,10 @@ class LazyLoader:
 
 
 class Experiment:
+    """
+    Class used to simplify accessing and managing data from the
+    experiment and analyses.
+    """
     participants = LazyLoader('_load_participants')
     avg_participant = LazyLoader('_load_avg_participant')
 
@@ -75,11 +91,16 @@ class Experiment:
         elif lecture in ('bos', 2):
             return self.bos_traj
         else:
-            raise ValueError('`lecture` should be either 1, "forces", 2, or "bos"')
+            raise ValueError(
+                '`lecture` should be either 1, "forces", 2, or "bos"'
+            )
 
     def get_question_vecs(self, qids=None, lectures=None):
         # get question topic vectors by question ID(s) or lecture(s)
-        if (qids is lectures is None) or (qids is not None and lectures is not None):
+        if (
+                (qids is lectures is None) or
+                (qids is not None and lectures is not None)
+        ):
             raise ValueError("must pass either `qids` or `lecture` (not both)")
         if lectures is not None:
             qids = []
@@ -153,7 +174,13 @@ class Experiment:
         path = RAW_DIR.joinpath('questions.tsv')
         return pd.read_csv(path,
                            sep='\t',
-                           names=['index', 'lecture', 'question', 'A', 'B', 'C', 'D'],
+                           names=['index',
+                                  'lecture',
+                                  'question',
+                                  'A',
+                                  'B',
+                                  'C',
+                                  'D'],
                            index_col='index')
 
     def _load_windows(self, lecture):
@@ -180,7 +207,8 @@ class Experiment:
[…]

### 2023-02-01 code/khan_helpers/khan_helpers/functions.py

@@ -1,3 +1,4 @@
+import logging
 import math
 import re
 import warnings
@@ -25,7 +26,21 @@ from .constants import FONTS_DIR, LECTURE_WSIZE, STOP_WORDS
 
 
 def _ts_to_sec(ts):
-    # converts timestamp of elapsed time from "MM:SS" format to scalar
+    """
+    Converts a timestamp denoting elapsed time from "MM:SS[.ss]" format
+    to a scalar
+
+    Parameters
+    ----------
+    ts : str
+        A timestamp consisting of minutes and seconds, separated by a
+        colon, where seconds may be a whole number or a decimal.
+
+    Returns
+    -------
+    float
+        The total number of seconds represented by the timestamp.
+    """
     mins, secs = ts.split(':')
     return timedelta(minutes=int(mins), seconds=float(secs)).total_seconds()
 
@@ -149,27 +164,48 @@ def corr_mean(rs, axis=None, fix_inf=False, **kwargs):
     Parameters
     ----------
     rs : array_like
-        Array of *r*-values.  May be any type accepted by `numpy.nanmean`
+        Array of *r*-values.  May be any type accepted by
+        `numpy.nanmean()`.
     axis : None or int or tuple of ints, optional
-        Axis or axes along which the means are computed. If None
+        Axis or axes along which the means are computed. If `None`
         (default), the mean of the flattened array is computed.
-    kwargs : various types, optional
+    fix_inf : bool, optional
+        See `z2r()` docstring for details. Default: False.
+    **kwargs : various types, optional
         Additional keyword arguments passed to `numpy.nanmean` (see
         https://numpy.org/doc/stable/reference/generated/numpy.nanmean.html
         for details).
 
     Returns
     -------
-    cm : float or numpy.ndarray
-        The average correlation coefficient
+    float or numpy.ndarray
+        The mean correlation coefficient
 
     """
-    return z2r(np.nanmean(r2z(np.asanyarray(rs), fix_inf=fix_inf), axis=axis, **kwargs))
+    zs = r2z(np.asanyarray(rs), fix_inf=fix_inf)
+    zmean = np.nanmean(zs, axis=axis, **kwargs)
+    return z2r(zmean)
 
 
 @numba.njit
 def correlation_exp(x, y):
-    # TODO: add docstring
+    """
+    Computes the correlation distance between two n-dimensional
+    vectors, exponentiating each element first. Returns the result and
+    the gradient of the distance function with respect to `x`.
+
[…]

### 2023-02-01 code/khan_helpers/khan_helpers/participant.py

@@ -9,6 +9,7 @@ from .constants import PARTICIPANTS_DIR, RAW_DIR
 
 
 class Participant:
+    """Class to manage data for individual participants"""
     def __init__(self, subid, data=None, raw_data=None, date_collected=None):
         self.subID = subid
         self.data = data
@@ -77,7 +78,8 @@ class Participant:
                 qid = q_info.index[0]
                 lec = q_info.loc[qid, 'video']
                 # get answer
-                ans_text = unescape(answer_block[f'Q{q_num}']).replace(chr(8217), "'")
+                ans_text = unescape(answer_block[f'Q{q_num}'])
+                ans_text = ans_text.replace(chr(8217), "'")
                 # error on failure to match question or unexpected letter
                 try:
                     ans_let = q_info.squeeze()[q_info.squeeze() == ans_text].index[0]
@@ -90,7 +92,11 @@ class Participant:
                 # set accuracy for response
                 acc = 1 if ans_let == 'A' else 0
                 data.append([qid, acc, ans_let, set_num, lec])
-        return pd.DataFrame(data, columns=['qID', 'accuracy', 'response', 'quiz', 'lecture'])
+        return pd.DataFrame(data, columns=['qID',
+                                           'accuracy',
+                                           'response',
+                                           'quiz',
+                                           'lecture'])
 
     def _repr_html_(self):
         # for displaying in Jupyter (IPython) notebooks
@@ -140,8 +146,9 @@ class Participant:
             return self.knowledge_maps[kmap_key]
         except KeyError as e:
             raise KeyError(
-                f'No knowledge map stored for {self} under "{kmap_key}". Stored '
-                f"knowledge maps are: {', '.join(self.knowledge_maps.keys())}"
+                f'No knowledge map stored for {self} under "{kmap_key}". '
+                "Stored knowledge maps are: "
+                f"{', '.join(self.knowledge_maps.keys())}"
             ) from e
 
     def get_trace(self, trace_key):

### 2023-02-01 paper/main.tex

@@
 correlations between any lecture timepoint and question, taken over all
-timepoints in the given lecture, and all five questions \textbf{about} that lecture appearing on the given quiz. 
+timepoints in the given lecture, and all five questions \textit{about} that lecture appearing on the given quiz. 
 We also define $f(s, \Omega)$ as the

### 2023-02-01 paper/supplement.tex

@@
 
-\newcommand{\knowledgeMaps}{5}
+\newcommand{\topics}{3}
+\newcommand{\knowledgeMaps}{7}
 
-\title{\textit{Supplementary materials for}: Text embedding models yield high
-resolution insights into conceptual knowledge from short multiple choice
+\title{\textit{Supplementary materials for}: Text embedding models yield 
+high-resolution insights into conceptual knowledge from short multiple-choice
 quizzes}
@@
 \renewcommand{\citenumfont}[1]{S#1}
-
-\newcommand{\topics}{3}
 
@@
 
-\caption{\textbf{Topics.} The table displays the 10 top-weighted word from
-    each of the 15 topics identified from sliding windows of two course video
-    transcripts (see \textit{Constructing text embeddings of multiple videos
+\caption{\textbf{Topics.} The table displays the 10 top-weighted words (columns) from
+    each of the 15 topics (rows) identified from sliding windows of the two course video
+    transcripts (see \textit{Constructing text embeddings of multiple lectures
     and questions}).}
@@
 \caption{\textbf{Topic weights. A. Average topic weights for each lecture and
-question type}. The bar plots display each topic's average weight across
+question set}. The bar plots display each topic's average weight across
 lecture timepoints (top row) and questions (bottom row); colors denote topics.
@@
 weights.} Pairwise correlations between the distributions of average topic
-weights for each lecture and question category. Each row and column corresponds
-to a bar plot in Panel A. Also see Figure~\topics A in the main text.}
+weights for each lecture and question set. Each row and column corresponds
+to a bar plot in Panel A. Also see Figure~\topics~in the main text.}
 
@@
     \caption{\textbf{Individual participants' knowledge maps estimated from
-    Quiz 1 responses.} Each panel is in the same format as the knowledge maps
+    Quiz 1 responses.} Each panel is in the same format as the knowledge map
     displayed in the left panel of Figure~\knowledgeMaps A in the main text,
-    but here the maps have been computed separately for each participant.}
+    but here the maps are shown separately for each participant.}
 
@@
     \caption{\textbf{Individual participants' knowledge maps estimated from
-    Quiz 2 responses.} Each panel is in the same format as the knowledge maps
+    Quiz 2 responses.} Each panel is in the same format as the knowledge map
     displayed in the middle panel of Figure~\knowledgeMaps A in the main text,
-    but here the maps have been computed separately for each participant.}
+    but here the maps are shown separately for each participant.}
 
@@
     \caption{\textbf{Individual participants' knowledge maps estimated from
-    Quiz 3 responses.} Each panel is in the same format as the knowledge maps
+    Quiz 3 responses.} Each panel is in the same format as the knowledge map
     displayed in the right panel of Figure~\knowledgeMaps A in the main text,
-    but here the maps have been computed separately for each participant.}
+    but here the maps are shown separately for each participant.}
 
@@
     displayed in the left panel of Figure~\knowledgeMaps B in the main text,
-    but here the maps have been computed separately for each participant.}
+    but here the maps are shown separately for each participant.}
 

### 2023-02-08 paper/admin/cover_letter.tex
added a cover letter draft

@@
 
-\newcommand{\journal}{Journal Name}
-\newcommand{\articletype}{Article Type}
-\newcommand{\title}{Paper title}
-\newcommand{\corresponding}{Corresponding Author Name}
+\newcommand{\journal}{Nature Human Behavior}
+\newcommand{\articletype}{Article}
+\newcommand{\myTitle}{Text embedding models yield high-resolution insights into conceptual knowledge from short multiple-choice quizzes}
+\newcommand{\corresponding}{Jeremy R. Manning}
 
@@
 \addrfrom{
-  Corresponding Author Institution\\
-  Corresponding Author Department\\
-  Corresponding Author Address\\
-  City, State, Zip code}
+  Dartmouth College\\
+  Department of Psychological and Brain Sciences\\
+  HB 6207 Moore Hall\\
+  Hanover, NH, 03755}
 \addrto{}
@@
 \begin{newlfm}
-  We have enclosed our manuscript entitled \textit{\title} to be
-  considered for publication as an \textit{\articletype}.  The
-  manuscript... (insert one sentence summary).
 
-(insert 1--2 paragraph summary of most important findings and how they
-fit into the broader literature)
+  We have enclosed our manuscript entitled \textit{\myTitle} to be considered for
+  publication as an \textit{\articletype}. In our manuscript, we develop and
+  test a mathematical framework, based on natural language processing models,
+  for tracking and characterizing the acquisition of real-world conceptual
+  knowledge.
 
-We expect that this article will be of interest to... (briefly describe target audience).
+  We asked our participants to watch two lecture videos from the Khan Academy
+  platform and to take short multiple-choice quizzes before and after each
+  lecture. We used a natural language processing model to capture the
+  conceptual content of each moment of the lectures, and of each question. This
+  model represents each lecture as a ``trajectory'' through a high-dimensional
+  embedding space, and each question as a point in the same space. We designed
+  the embedding space to map conceptually related content onto nearby
+  coordinates. We used these embeddings, along with participants' automatically
+  graded responses to the quiz questions, to characterize nuances in
+  participants' knowledge. Essentially, our approach models ``knowledge'' about
+  a given concept as the weighted proportion of questions a participant answers
+  correctly, where the weights reflect how much each question is ``about'' the
+  given concept (according to the natural language processing model). Whereas
+  the raw proportion of correctly answered questions can characterize
+  content-nonspecific knowledge (e.g., something akin to ``how \textit{much}
+  the participant knows''), these weighted proportions provide estimates about
+  \textit{what} the participant knows.
 
-Thank you for considering this manuscript, and I hope you will find it suitable for publication in \textit{\journal}.
+  Our manuscript makes several important contributions. First, we define our
+  framework and show how we can jointly model the content of multiple
+  real-world course lectures and questions. We designed our framework to be
+  scalable to a very broad range of content areas. Second, we use participants'
+  behavioral data to evaluate the knowledge estimates produced by our
+  framework. We show that the knowledge estimates can reliably differentiate
+  whether participants will answer individual held-out quiz questions correctly
+  versus incorrectly. Third, we use our framework to construct detailed
+  ``maps'' of what participants know (based on their responses from a single
+  quiz) and how their knowledge changes over time (based on differences between
+  the knowledge maps estimated from successive quizzes). These maps demonstrate
+  how knowledge (and changes in knowledge) about \textit{any} conceptual
+  content expressible by the text embedding model may be estimated from the
+  same small set of multiple-choice questions.
+
+In addition to showing how detailed insights into what people know may be
+gleaned from a small number of questions, our work also lays the foundation for
+several exciting future applications and research areas. For example, the
+knowledge maps produced by our framework could be used by educators to help
+guide their lessons and better understand their students. The maps could also
+be used as a core component of a new generation of automated tutors that adapt
+to-be-presented content according to the latest estimate of what a student
+knows. More broadly, we also see potential overlap with other research domains
+that consider how information ``flows'' between people. In our manuscript we
+focus on information flow from teachers (i.e., the course lectures) to
+students. But we see analogous approaches being used to characterize other
+social domains as well, such as between friends having a conversation,
+doctor-patient interactions, romantic partnerships, business meetings, and
+more. We suggest that the degree of overlap between two individuals' knowledge
+maps, in a particular region of content space, may serve as a predictive signal
+for how effectively those individuals will be able to communicate about content
+in that region of content space. We expect that this article will be of
+interest to a broad audience including educators, cognitive psychologists,
+social psychologists, natural language processing researchers, and others.
+
+Thank you for considering this manuscript, and we hope you will find it suitable
+for publication in \textit{\journal}.
 

### 2023-02-15 paper/main.tex
starting to address pinned items in slack channel

@@
     completing three 13-question multiple-choice quizzes and watching two Khan Academy
-    lectures. Each quiz contains a mix of 5 questions about lecture 1, 5
-    questions about lecture 2, and 3 questions about general physics knowledge. The
+    lectures. Each quiz contains a mix of 5 questions about lecture~1, 5
+    questions about lecture~2, and 3 questions about general physics knowledge. The
     specific questions reflected on each quiz, and the orders of each quiz's
@@
 pool). Participants answered questions randomly drawn from each content area
-(lecture 1, lecture 2, and general physics knowledge) on each of the three
-quizzes. Quiz 1 was intended to assess participants' ``baseline'' knowledge
-before training, Quiz 2 assessed knowledge after watching the \textit{Four
-Fundamental Forces} video (i.e., lecture 1), and Quiz 3 assessed knowledge
-after watching the \textit{Birth of Stars} video (i.e., lecture 2).
+(lecture~1, lecture~2, and general physics knowledge) on each of the three
+quizzes. Quiz~1 was intended to assess participants' ``baseline'' knowledge
+before training, Quiz~2 assessed knowledge after watching the \textit{Four
+Fundamental Forces} video (i.e., lecture~1), and Quiz~3 assessed knowledge
+after watching the \textit{Birth of Stars} video (i.e., lecture~2).
 
@@
 striking correspondence (Fig.~\topicWeights). Specifically, the average topic
-weights from lecture 1 are strongly correlated with the average topic weights
-from lecture 1 questions ($r(13) = 0.809,~p < 0.001$, 95\% confidence interval
-(CI)~$= [0.633,~0.962]$), and the average topic weights from lecture 2 are
-strongly correlated with the average topic weights from lecture 2 questions
+weights from lecture~1 are strongly correlated with the average topic weights
+from lecture~1 questions ($r(13) = 0.809,~p < 0.001$, 95\% confidence interval
+(CI)~$= [0.633,~0.962]$), and the average topic weights from lecture~2 are
+strongly correlated with the average topic weights from lecture~2 questions
 ($r(13) = 0.728,~p = 0.002$, 95\% CI~$= [0.456,~0.920]$). At the same time, the
 average topic weights from the two lectures are \textit{negatively} correlated with 
-their non-matching question sets (lecture 1 video vs.~lecture 2 questions: $r(13) = 
--0.547,~p = 0.035$, 95\% CI~$= [-0.812, ~-0.231]$; lecture 2 video vs.~lecture 1 questions: $r(13) 
+their non-matching question sets (lecture~1 video vs.~lecture~2 questions: $r(13) = 
+-0.547,~p = 0.035$, 95\% CI~$= [-0.812, ~-0.231]$; lecture~2 video vs.~lecture~1 questions: $r(13) 
 = -0.612,~p = 0.015$, 95\% CI~$= [-0.874,~-0.281]$), indicating that the topic model
@@
 questions) between the lectures and questions. The variability in topic
-expression (over time and across questions) was similar for the lecture 1 video
-and questions ($r(13) = 0.824,~p<0.001$, 95\% CI~$= [0.696,~0.973]$) and the lecture 2
+expression (over time and across questions) was similar for the lecture~1 video
+and questions ($r(13) = 0.824,~p<0.001$, 95\% CI~$= [0.696,~0.973]$) and the lecture~2
 video and questions ($r(13) = 0.801,~p<0.001$, 95\% CI~$= [0.539,~0.958]$). 
@@
 topic expressions across \textit{different} videos and lecture-specific
-questions (i.e., lecture 1 video vs.~lecture 2 questions; lecture 2 video
-vs.~lecture 1 questions) were negatively correlated, and neither
+questions (i.e., lecture~1 video vs.~lecture~2 questions; lecture~2 video
+vs.~lecture~1 questions) were negatively correlated, and neither
 video's topic variability was reliably correlated with the topic variability
@@
 experiment. Specifically, knowledge about that lecture's content should be
-relatively low when estimated using Quiz 1 responses, but should increase when
-estimated using Quiz 2 or 3 responses (Fig.~\ref{fig:knowledge-timeseries}B).
+relatively low when estimated using Quiz~1 responses, but should increase when
+estimated using Quiz~2 or~3 responses (Fig.~\ref{fig:knowledge-timeseries}B).
 Indeed, we found that participants' estimated knowledge about the content of
-the \textit{Four Fundamental Forces} was substantially higher on Quiz 2 versus
-Quiz 1 ($t(49) = 8.764,~p < 0.001$) and on Quiz 3 versus Quiz 1 ($t(49) =
+the \textit{Four Fundamental Forces} was substantially higher on Quiz~2 versus
+Quiz~1 ($t(49) = 8.764,~p < 0.001$) and on Quiz~3 versus Quiz~1 ($t(49) =
 10.519,~p < 0.001$). We found no reliable differences in estimated knowledge
-about that lecture's content on Quiz 2 versus 3 ($t(49) = 0.160,~p = 0.874$).
+about that lecture's content on Quiz~2 versus~3 ($t(49) = 0.160,~p = 0.874$).
 Similarly, we hypothesized (and subsequently confirmed) that participants
@@
 (Fig.~\ref{fig:knowledge-timeseries}D). Specifically, since participants
-watched that lecture after taking Quiz 2 (but before Quiz 3), we hypothesized
+watched that lecture after taking Quiz~2 (but before Quiz~3), we hypothesized
 that their knowledge estimates should be relatively low on Quizzes 1 and 2, but
-should show a ``boost'' on Quiz 3. Consistent with this prediction, we found no
+should show a ``boost'' on Quiz~3. Consistent with this prediction, we found no
 reliable differences in estimated knowledge about the \textit{Birth of Stars}
 lecture content on Quizzes 1 versus 2 ($t(49) = 1.013,~p = 0.316$), but the
-estimated knowledge was substantially higher on Quiz 3 versus 2 ($t(49) =
-10.561,~p < 0.001$) and Quiz 3 versus 1 ($t(49) = 8.969,~p < 0.001$).
+estimated knowledge was substantially higher on Quiz~3 versus~2 ($t(49) =
+10.561,~p < 0.001$) and Quiz~3 versus 1 ($t(49) = 8.969,~p < 0.001$).
 
@@
 questions (estimated knowledge for correctly versus incorrectly answered 
-Quiz 3 questions: $t(628) = 2.045,~p = 0.041$).
+Quiz~3 questions: $t(628) = 2.045,~p = 0.041$).
 
@@
     indicate how much each word is weighted, on average, across all timepoints'
-    topic vectors in the \textit{Four Fundamental Forces} (blue) and
-    \textit{Birth of Stars} (green) videos, respectively.}
+    topic vectors in the \textit{Four Fundamental Forces} (bluer coloring) and
+    \textit{Birth of Stars} (greener coloring) videos, respectively.}
 
@@
 Several features of the resulting knowledge maps are worth noting. The average
-knowledge map estimated from Quiz 1 responses (Fig.~\ref{fig:knowledge-maps}A,
+knowledge map estimated from Quiz~1 responses (Fig.~\ref{fig:knowledge-maps}A,
 leftmost map) shows that participants tended to have relatively little
 knowledge about any parts of the text embedding space (i.e., the shading is
-relatively dark everywhere). The knowledge map estimated from Quiz 2 responses
+relatively dark everywhere). The knowledge map estimated from Quiz~2 responses
 shows a marked increase in knowledge on the left side of the map (around
@@
 surrounding the embedding of the \textit{Birth of Stars} lecture participants
-watched immediately prior to taking Quiz 3.
+watched immediately prior to taking Quiz~3.
 
@@
 duration: 7 minutes and 57 seconds). We then hand-created 39 multiple-choice
-questions: 15 about the conceptual content of \textit{Four Fundamental Forces} (i.e., lecture 1),
-15 about the conceptual content of \textit{Birth of Stars} (i.e., lecture 2), and 9
+questions: 15 about the conceptual content of \textit{Four Fundamental Forces} (i.e., lecture~1),
+15 about the conceptual content of \textit{Birth of Stars} (i.e., lecture~2), and 9
 questions that tested for general conceptual knowledge about basic physics
@@
 Over the course of the experiment, participants completed three 13-question
-multiple-choice quizzes: the first before viewing lecture 1, the second between
-lectures 1 and 2, and the third after viewing lecture 2
+multiple-choice quizzes: the first before viewing lecture~1, the second between
+lectures 1 and 2, and the third after viewing lecture~2
 (Fig.~\ref{fig:experiment}). The questions appearing on each quiz, for each
 participant, were randomly chosen from the full set of 39, with the constraints
-that (a) each quiz contain 5 questions about lecture 1, 5 questions about
-lecture 2, and 3 questions about general physics knowledge, and (b) each
+that (a) each quiz contain 5 questions about lecture~1, 5 questions about
+lecture~2, and 3 questions about general physics knowledge, and (b) each
 question appear exactly once for each participant. The orders of questions on
@@
 reflect similar themes, according to the model) will yield similar coordinates
-(in terms of Euclidean distance, correlation, or other geometric measures). In
-general, the similarity between different documents' topic vectors may be used
-to characterize the similarity in conceptual content between the documents.
+(in terms of correlation, cosine similarity, Kullback-Leibler divergence,
+Euclidean distance, or other geometric measures). In general, the similarity
+between different documents' topic vectors may be used to characterize the
+similarity in conceptual content between the documents.
 

### 2023-02-15 launch_notebooks.sh
re-add launch_notebooks script

@@ -1,0 +1,462 @@
+#!/usr/bin/env bash
+
+set -e
+
+# default arg values
+IMAGE_NAME="khan"                                        # name of image to build/use
+CONTAINER_NAME="Khan"                                    # name of container to create/start
+declare -i LAUNCH_BROWSER=1                              # true by default
+declare -i DETACH=0                                      # false by default
+
+# other configurables
+# NOTE: changing these has no effect after image is built & container is created
+declare -r DOCKERFILE_PATH="docker/Dockerfile-analyses"  # relative path from repository root to Dockerfile
+declare -r NOTEBOOKS_DIR="code/notebooks"                # relative path from repository root to notebooks folder
+declare -ir CONTAINER_PORT=8888                          # container port used to run notebook server and published to host
+declare -ir LOCAL_PORT=8888                              # host port bound to container port and used to run notebooks in browser
+
+
+# TODO: add extra configurable options for notebook-related --build-args (port, IP, etc.) and help to show_help()
+# TODO: check uname -m to set value passed to --platform=linux/<XXX>64. Will need to convert x86_64 to amd64
+########################################
+#         CLI PARSING FUNCTIONS        #
+########################################
+parse_args() {
+    while (( "$#" )); do
+        case "$1" in
+            -i | --image-name)
+                check_arg 1 "$@"
+                IMAGE_NAME=$2
+                shift 2
+                ;;
+            -c | --container-name)
+                check_arg 1 "$@"
+                CONTAINER_NAME=$2
+                shift 2
+                ;;
+            -b | --no-browser)
+                check_arg 0 "$@"
+                LAUNCH_BROWSER=0
+                shift
+                ;;
+            -d | --detach)
+                check_arg 0 "$@"
+                DETACH=1
+                shift
+                ;;
+            -h | --help)
+                show_help
+                exit 0
+                ;;
+            *)
+                { show_usage && echo "Error: unrecognized argument: $1"; } >&2
+                exit 1
+                ;;
+        esac
+    done
+
+    # readonly all values after updating defaults with args passed
+    readonly IMAGE_NAME
+    readonly CONTAINER_NAME
+    readonly LAUNCH_BROWSER
[…]

### 2023-02-16 paper/main.tex
forgot to check in some saved edits

@@
 this approach separately for the questions from each quiz the participants took
-throughout the experiment. From just a few questions per quiz, we obtain a
-high-resolution snapshot (at the time each quiz was taken) of what the
-participants knew about any moment's content, from either of the two lectures
-they watched (comprising a total of 1,100 samples across the two lectures).
+throughout the experiment. From just a few questions per quiz (see
+Sec.~\ref{subsec:traces}), we obtain a high-resolution snapshot (at the time
+each quiz was taken) of what the participants knew about any moment's content,
+from either of the two lectures they watched (comprising a total of 1,100
+samples across the two lectures).
 

### 2023-02-16 launch_notebooks.sh
change notebook server url from 0.0.0.0 to 127.0.0.1 to bypass ssl popup in chrome

@@ -382,6 +382,7 @@ get_nbserver_url() {
     local url_dir_info="${running_nbserver#Currently running servers:}"
     nbserver_url="${url_dir_info%% *}"
     nbserver_url="${nbserver_url//$'\n'}"
+    nbserver_url="${nbserver_url/0.0.0.0/127.0.0.1}"
 }
 
 

### 2023-02-16 docker/jupyter_notebook_config.py
fix bug in delete_to_trash config option

@@ -15,4 +15,4 @@ c.NotebookApp.notebook_dir = getenv("NOTEBOOK_DIR")
 c.NotebookApp.open_browser = False
 c.NotebookApp.allow_root = True
 # https://github.com/jupyter/notebook/issues/3130
-c.NotebookApp.delete_to_trash = False
+c.FileContentsManager.delete_to_trash = False

### 2023-02-17 launch_notebooks.sh
silence docker scan message after build

@@ -335,7 +335,7 @@ local_image_exists() {
 
 build_local_image() {
     fancy_echo "building image: $IMAGE_NAME"
-    docker build \
+    DOCKER_SCAN_SUGGEST=false docker build \
         --rm \
         --force-rm \
         --build-arg WORKDIR="/mnt/$NOTEBOOKS_DIR" \

### 2023-02-20 paper/main.tex
add non-breaking spaces between 'lecture'/'quiz' and number so line doesn't start with digit

--- 2023-02-15 paper/main.tex
@@
 other. To satisfy this last criterion, we chose videos from two different
-lecture series (lectures 1 and 2 were from the ``Scale of the Universe'' and
+lecture series (lectures~1 and 2 were from the ``Scale of the Universe'' and
 ``Stars, Black Holes, and Galaxies'' series, respectively).
@@
 relatively low when estimated using Quiz~1 responses, but should increase when
-estimated using Quiz~2 or~3 responses (Fig.~\ref{fig:knowledge-timeseries}B).
+estimated using Quiz~2 or 3 responses (Fig.~\ref{fig:knowledge-timeseries}B).
 Indeed, we found that participants' estimated knowledge about the content of
@@
 10.519,~p < 0.001$). We found no reliable differences in estimated knowledge
-about that lecture's content on Quiz~2 versus~3 ($t(49) = 0.160,~p = 0.874$).
+about that lecture's content on Quiz~2 versus 3 ($t(49) = 0.160,~p = 0.874$).
 Similarly, we hypothesized (and subsequently confirmed) that participants
@@
 watched that lecture after taking Quiz~2 (but before Quiz~3), we hypothesized
-that their knowledge estimates should be relatively low on Quizzes 1 and 2, but
+that their knowledge estimates should be relatively low on Quizzes~1 and 2, but
 should show a ``boost'' on Quiz~3. Consistent with this prediction, we found no
 reliable differences in estimated knowledge about the \textit{Birth of Stars}
-lecture content on Quizzes 1 versus 2 ($t(49) = 1.013,~p = 0.316$), but the
-estimated knowledge was substantially higher on Quiz~3 versus~2 ($t(49) =
+lecture content on Quizzes~1 versus 2 ($t(49) = 1.013,~p = 0.316$), but the
+estimated knowledge was substantially higher on Quiz~3 versus 2 ($t(49) =
 10.561,~p < 0.001$) and Quiz~3 versus 1 ($t(49) = 8.969,~p < 0.001$).
@@
     indicate how much each word is weighted, on average, across all timepoints'
-    topic vectors in the \textit{Four Fundamental Forces} (bluer coloring) and
-    \textit{Birth of Stars} (greener coloring) videos, respectively.}
+    topic vectors in the \textit{Four Fundamental Forces} (blue) and
+    \textit{Birth of Stars} (green) videos, respectively.}
 
@@
 multiple-choice quizzes: the first before viewing lecture~1, the second between
-lectures 1 and 2, and the third after viewing lecture~2
+lectures~1 and 2, and the third after viewing lecture~2
 (Fig.~\ref{fig:experiment}). The questions appearing on each quiz, for each
@@
 reflect similar themes, according to the model) will yield similar coordinates
-(in terms of correlation, cosine similarity, Kullback-Leibler divergence,
-Euclidean distance, or other geometric measures). In general, the similarity
-between different documents' topic vectors may be used to characterize the
-similarity in conceptual content between the documents.
+(in terms of Euclidean distance, correlation, or other geometric measures). In
+general, the similarity between different documents' topic vectors may be used
+to characterize the similarity in conceptual content between the documents.
 

### 2023-02-20 paper/main.tex
udpate counts in demographics

@@
 ``neutral'' (0), ``fairly alert'' (1), and ``very alert'' (2). Across
-all participants, a range of alertness levels were reported (range: -2
--- 1; mean: -0.10; standard deviation: 0.84).
+all participants, a range of alertness levels were reported (range: 
+-2--1; mean: -0.10; standard deviation: 0.84).
 
@@
 participants). Note that some participants selected multiple categories for
-their undergraduate major. We also asked participants about the courses they
+their undergraduate major(s). We also asked participants about the courses they
 had taken. In total, 45 participants reported having taken at least one Khan
@@
 Organic Chemistry (21 participants); Physics, AP Physics I, or AP Physics II
-(15 participants); Biology, AP Biology; or High school Biology (15
+(18 participants); Biology, AP Biology; or High school Biology (15
 participants); Health and Medicine (1 participant); or other videos not listed
-in our survey (19 participants). We also asked participants whether they had
+in our survey (5 participants). We also asked participants whether they had
 specifically seen the videos used in our experiment. Of the 45 participants who
@@
 humanities (2 participants), Computing (2 participants), and other categories
-not listed in our survey (18 participants). Finally, we asked participants
+not listed in our survey (17 participants). Finally, we asked participants
 about in-person courses they had taken in different subject areas. They
-reported taking courses in Mathematics (39 participants), Science and
-engineering (38 participants), Arts and humanities (35 participants), Test
+reported taking courses in Mathematics (38 participants), Science and
+engineering (37 participants), Arts and humanities (34 participants), Test
 preparation (27 participants), Economics and finance (26 participants),
-Computing (15 participants), College and careers (7 participants), or other
+Computing (14 participants), College and careers (7 participants), or other
 courses not listed in our survey (6 participants).

### 2023-02-20 exp/static/js/demographics.js
major experiment code cleanup

@@ -1,14 +1,14 @@
 var runDemographics = function(options) {
-    window.onload = function() {
-      $("body").append("<div id='googleform'><iframe src='https://docs.google.com/forms/d/e/1FAIpQLSfBL9Q7UNQg9q8lbO-TkKJpdaCS4thMr3x-MjpC_q0xOfA77w/viewform?embedded=true' width='" +
-          $(window).width() + "' height='" +
-          $(window).height() + "' frameborder='0' marginheight='0' marginwidth='0'>Loading...</iframe></div>")
+  window.onload = function() {
+    $("body").append("<div id='googleform'><iframe src='https://docs.google.com/forms/d/e/1FAIpQLSfBL9Q7UNQg9q8lbO-TkKJpdaCS4thMr3x-MjpC_q0xOfA77w/viewform?embedded=true' width='" +
+        $(window).width() + "' height='" +
+        $(window).height() + "' frameborder='0' marginheight='0' marginwidth='0'>Loading...</iframe></div>")
 
-      $("body").append("<button class='btn btn-success' id='nextBtn' style='position: fixed; bottom: 0px; right: 0px;' id='fixedbutton'>Done</button>")
+    $("body").append("<button class='btn btn-success' id='nextBtn' style='position: fixed; bottom: 0px; right: 0px;' id='fixedbutton'>Done</button>")
 
-      $('#nextBtn').click(function() {
-        $("body").remove();
-        runExperiment(options);
-      });
-    };
+    $('#nextBtn').click(function() {
+      $("body").remove();
+      runExperiment(options);
+    });
   };
+};

### 2023-02-20 exp/static/js/experiment.js

@@ -291,23 +291,23 @@ var runExperiment = function(options) {
     message: '<p>We’d like you to really focus on this HIT so that we can collect clean data. Please turn off any music (but keep your volume turned on), close any additional open tabs in your browser (or any other open programs), remove any distractions around you (e.g. phone), and make yourself comfortable. When you are ready, please press the following button to switch your browser to fullscreen mode. (Your browser will remain in fullscreen for the duration of the HIT.  If you need to exit the HIT early, you may press ESCAPE (esc) to exit fullscreen mode and return your browser back to normal.</p>',
     button_label: 'Enter fullscreen mode',
     fullscreen_mode: true
-   };
-   experimentTimeline.push(fscreen)
+  };
+  experimentTimeline.push(fscreen)
 
-   var soundcheck_movie = {
-      type: "instructions",
-      pages: ["<h2>Speaker adjustment</h2><p>Click the button to play the following sound clip:</p>" +
-      "<audio id='soundTest' src='static/files/furelise.mp3' preload='auto'></audio>" +
-      "<button style='background-color:white; outline:none' class='btn btn-large' onclick='document.getElementById(" + '"soundTest"' + ").play();'><i class='fa fa-play-circle-o fa-5x'></i></button>" +
-      "<p>Take this time to adjust your speaker or headphone volume to a comfortable level. Press the spacebar to continue to the next screen once you are ready.</p>"],
-      key_forward: 32
-    }
+  var soundcheck_movie = {
+    type: "instructions",
+    pages: ["<h2>Speaker adjustment</h2><p>Click the button to play the following sound clip:</p>" +
+            "<audio id='soundTest' src='static/files/furelise.mp3' preload='auto'></audio>" +
+            "<button style='background-color:white; outline:none' class='btn btn-large' onclick='document.getElementById(" + '"soundTest"' + ").play();'><i class='fa fa-play-circle-o fa-5x'></i></button>" +
+            "<p>Take this time to adjust your speaker or headphone volume to a comfortable level. Press the spacebar to continue to the next screen once you are ready.</p>"],
+    key_forward: 32
+  }
   experimentTimeline.push(soundcheck_movie);
 
   // opening instructions
   var open_instructions = {
-      type: "instructions",
-      pages: ["<div class='instructions'> <p style='font-weight:bold'> PLEASE READ THESE INSTRUCTIONS CAREFULLY</p>" +
+    type: "instructions",
[…]

### 2023-02-20 exp/static/js/postquestionnaire.js

@@ -1,11 +1,0 @@
-var runPostQuestionnaire = function(options) {
-  $("body").append("<div id='googleform'><iframe src='https://docs.google.com/forms/d/e/1FAIpQLSdj6IV19P50l3Ee4fjTUWDyTEuOcwaVIVDOMlCRoQ6aKbtfjw/viewform?embedded=true' width='" +
-      $(window).width() + "' height='" +
-      $(window).height() + "' frameborder='0' marginheight='0' marginwidth='0'>Loading...</iframe></div>")
-
-  $("body").append("<button class='btn btn-success' id='finishedBtn' style='position: fixed; bottom: 0px; right: 0px;' id='fixedbutton'>Finished!</button>")
-
-  $('#finishedBtn').click(function() {
-      psiTurk.completeHIT();
-  });
-};

### 2023-02-20 exp/static/js/warnings.js

@@ -1,92 +1,0 @@
-var runWarnings = function(options, cb) {
-    if (options.show) {
-
-        warningsTimeline = [];
-
-        // instructions for microphone test
-        var warnings1 = {
-            type: 'text',
-            text: "<div class='instructions'>" +
-                "<p>For this experiment, we will be recording your voice while you recall lists of words, so you'll need to turn on your microphone. Please click <i>allow</i> when prompted. If your microphone is not working, you <b> will not be able to do this experiment.</b></p>" +
-                "<p>Press any key to allow microphone access.</p></div>",
-            is_html: true
-        }
-        warningsTimeline.push(warnings1);
-
-        // create the mic test
-        var micInit = {
-            type: 'call-function',
-            func: accessMic,
-            timing_post_trial: 5000,
-        };
-        warningsTimeline.push(micInit);
-
-        var warnings2 = {
-            type: "text",
-            text: "<div class= 'instructions'>" +
-                "<p> For the duration of the experiment, you will need to remain in <strong>fullscreen mode</strong>. If this is not possible, please exit the experiment now.</p>" +
-                "<p> Otherwise, please press a key to continue.</p></div>",
-            html: true
-        };
-        warningsTimeline.push(warnings2);
-
-        var warnings3 = {
-            type: "text",
-            text: "<div class= 'instructions'>" +
-                "<p> Before we start, please make sure that your computer is connected to a <strong>power source</strong>.</p>" +
-                "<p> Please do this now and then press any key to continue.</p></div>",
-            html: true
-        };
-        warningsTimeline.push(warnings3);
-
-        jsPsych.init({
-            timeline: warningsTimeline,
-            on_finish: function() {
-                cb();
-                psiTurk.saveData({
-                    success: function() {
-                        console.log("Warnings Shown!");
-                    }
-                });
-            },
-            on_data_update: function(data) {
-                psiTurk.recordTrialData(data);
-            }
-        });
-    } else {
-        cb();
-    };
-};
-
-var accessMic = function() {
-
-    $spinner = "<div class='instructions'><p>Please click <strong>allow</strong>.</p></div>";
-    $(".jspsych-display-element").append($spinner);
-
-    //Wrap the getUserMedia function from the different browsers
-    navigator.getUserMedia = navigator.getUserMedia ||
-        navigator.webkitGetUserMedia ||
-        navigator.mozGetUserMedia;
-
[…]

### 2023-02-20 exp/static/js/demographics.js
lock google form, fill consent form & debriefing with template text

@@ -1,6 +1,6 @@
 var runDemographics = function(options) {
   window.onload = function() {
-    $("body").append("<div id='googleform'><iframe src='https://docs.google.com/forms/d/e/1FAIpQLSfBL9Q7UNQg9q8lbO-TkKJpdaCS4thMr3x-MjpC_q0xOfA77w/viewform?embedded=true' width='" +
+    $("body").append("<div id='googleform'><iframe src='https://docs.google.com/forms/d/e/1FAIpQLSfsAsQ1NlKa26G3Q2EwI6gq_kW599LhMkwCa7Q9XCJLB7Ow2A/viewform?embedded=true' width='" +
         $(window).width() + "' height='" +
         $(window).height() + "' frameborder='0' marginheight='0' marginwidth='0'>Loading...</iframe></div>")
 

### 2023-02-20 exp/static/js/experiment.js

@@ -429,11 +429,11 @@ var runExperiment = function(options) {
   // finished message
   var finished_message = {
     type: "instructions",
-    pages: ["<h2>Debriefing</h2>" +
-            "<p>Thank you for contributing to research in The Contextual Dynamics Laboratory (http://www.context-lab.com/) at Dartmouth College!</p>" +
-            "<p>You will receive a base payment of $5/hour for your participation in the task in addition to a performance bonus upon submission of this HIT.</p>" +
-            "<p>Our lab is interested in developing technology to predicit future learning and test performance on information learned from short videos from past test performance. We will use your responses during this experiment to help develop models that will track participant learning while viewing short online videos and predict participant performance on future tests. We hope that this technology can help to improve learning from online courses.</p>" +
-            "<p>We've taken great care to design this task appropriately for Amazon Mechanical Turk and your enjoyment as a Worker, and securely store your data on our servers without any personally-identifiable information. If for any reason you would like to contact us to ask further questions or comment on this experiment, please call the research director for this study: Dr. Jeremy Manning, at (603) 646-2777 during normal business hours (9 — 5 PM, Monday — Friday), or send an email to contextualdynamics@gmail.com with the title 'AMT Experiment Inquiry'. If you have questions, concerns, complaints, or suggestions about human research at Dartmouth College, you may call the Office of the Committee for the Protection of Human Subjects at Dartmouth College (603) 646-6482 during normal business hours. Otherwise, thank you for your contributions to scientific research and enjoy your day! </p>",
+    pages: ["<h2>Your <b>Debriefing</b> goes here</h2>" +
+            "<p>Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.</p>" +
+            "<p>Amet venenatis urna cursus eget nunc scelerisque. In massa tempor nec feugiat nisl pretium fusce id.</p>" +
[…]

### 2023-02-21 code/khan_helpers/khan_helpers/functions.py
final code cleanup

@@ -78,7 +78,7 @@ def bootstrap_ci_plot(
     ignore_nan : bool, optional
         If True (default: False), ignore NaNs in all calculations
         (handle them with numpy NaN-aware functions and suppress common
-        NaN-related warnigns).
+        NaN-related warnings).
     color : str or tuple of float, optional
         Any color specification accepted by Matplotlib. See
         https://matplotlib.org/3.5.1/tutorials/colors/colors.html for a
@@ -105,7 +105,7 @@ def bootstrap_ci_plot(
 
     Returns
     -------
-    returns : matplotlib.axes.Axes or list of objects
+    returns : matplotlib.axes.Axes or tuple of objects
         Return value depends on the value passed to `return_bounds`. If
         False (default), the Axes object alone is returned. If True, a
         3-tuple is returned, where the first item is the Axes object and

### 2023-02-21 launch_notebooks.sh

@@ -16,8 +16,6 @@ declare -ir CONTAINER_PORT=8888                          # container port used t
 declare -ir LOCAL_PORT=8888                              # host port bound to container port and used to run notebooks in browser
 
 
-# TODO: add extra configurable options for notebook-related --build-args (port, IP, etc.) and help to show_help()
-# TODO: check uname -m to set value passed to --platform=linux/<XXX>64. Will need to convert x86_64 to amd64
 ########################################
 #         CLI PARSING FUNCTIONS        #
 ########################################
@@ -85,7 +83,7 @@ check_arg() {
 
 
 show_usage() {
-    echo "launch_notebooks.sh [-h] [-d] [-b] [-i NAME] [-c NAME]"
+    echo "./launch_notebooks.sh [-h] [-d] [-b] [-i NAME] [-c NAME]"
 }
 
 
@@ -120,6 +118,7 @@ show_help() {
 
     local -i description_newline_indent=$(( option_indent + max_option_len + description_offset ))
 
+    echo
     show_usage
     echo
     echo_block -c $max_cols "$long_description"
@@ -313,7 +312,7 @@ attempt_start_daemon() {
             exit 254
         else
             printf "."
-            sleep 1
+            sleep 2
         fi
     done
     # adds a newline after dynamic printf'd output

### 2023-02-21 paper/admin/cover_letter.tex
editing pass through cover letter

@@
 \documentclass[11pt,stdletter,orderfromtodate,sigleft]{newlfm}
+\let\geometry\relax
 \usepackage{blindtext, xfrac, animate, hyperref, pxfonts, geometry}
@@
 
-\newcommand{\journal}{Nature Human Behavior}
+\newcommand{\journal}{Nature Human Behaviour}
 \newcommand{\articletype}{Article}
@@
 
-  We asked our participants to watch two lecture videos from the Khan Academy
-  platform and to take short multiple-choice quizzes before and after each
+  We asked participants in our study to watch two lecture videos from the Khan Academy
+  platform and complete short multiple-choice quizzes before and after each
   lecture. We used a natural language processing model to capture the
-  conceptual content of each moment of the lectures, and of each question. This
+  conceptual content presented in each moment of the lectures, and probed by each quiz question. This
   model represents each lecture as a ``trajectory'' through a high-dimensional
-  embedding space, and each question as a point in the same space. We designed
+  embedding space, and each question as a point in this same space. We designed
   the embedding space to map conceptually related content onto nearby
@@
   graded responses to the quiz questions, to characterize nuances in
-  participants' knowledge. Essentially, our approach models ``knowledge'' about
+  participants' knowledge and how it changed with exposure to each lecture's content. Essentially, our approach models ``knowledge'' about
   a given concept as the weighted proportion of questions a participant answers
@@
   content-nonspecific knowledge (e.g., something akin to ``how \textit{much}
-  the participant knows''), these weighted proportions provide estimates about
-  \textit{what} the participant knows.
+  an individual knows''), these weighted proportions provide estimates about
+  \textit{what} an individual knows.
 
@@
   behavioral data to evaluate the knowledge estimates produced by our
-  framework. We show that the knowledge estimates can reliably differentiate
+  framework. We show that these knowledge estimates can reliably differentiate
   whether participants will answer individual held-out quiz questions correctly
@@
 knowledge maps produced by our framework could be used by educators to help
-guide their lessons and better understand their students. The maps could also
+guide their lessons and better understand their students. These maps could also
 be used as a core component of a new generation of automated tutors that adapt
@@
 knows. More broadly, we also see potential overlap with other research domains
-that consider how information ``flows'' between people. In our manuscript we
+that consider how information ``flows'' between people. In our manuscript, we
 focus on information flow from teachers (i.e., the course lectures) to
@@
 for how effectively those individuals will be able to communicate about content
-in that region of content space. We expect that this article will be of
+in that region of space. We expect that this article will be of
 interest to a broad audience including educators, cognitive psychologists,

### 2023-02-21 paper/main.tex

@@
     completing three 13-question multiple-choice quizzes and watching two Khan Academy
-    lectures. Each quiz contains a mix of 5 questions about lecture~1, 5
-    questions about lecture~2, and 3 questions about general physics knowledge. The
+    lectures. Each quiz contains a mix of 5 questions about Lecture~1, 5
+    questions about Lecture~2, and 3 questions about general physics knowledge. The
     specific questions reflected on each quiz, and the orders of each quiz's
@@
 other. To satisfy this last criterion, we chose videos from two different
-lecture series (lectures~1 and 2 were from the ``Scale of the Universe'' and
+lecture series (Lectures~1 and 2 were from the ``Scale of the Universe'' and
 ``Stars, Black Holes, and Galaxies'' series, respectively).
@@
 pool). Participants answered questions randomly drawn from each content area
-(lecture~1, lecture~2, and general physics knowledge) on each of the three
+(Lecture~1, Lecture~2, and general physics knowledge) on each of the three
 quizzes. Quiz~1 was intended to assess participants' ``baseline'' knowledge
 before training, Quiz~2 assessed knowledge after watching the \textit{Four
-Fundamental Forces} video (i.e., lecture~1), and Quiz~3 assessed knowledge
-after watching the \textit{Birth of Stars} video (i.e., lecture~2).
+Fundamental Forces} video (i.e., Lecture~1), and Quiz~3 assessed knowledge
+after watching the \textit{Birth of Stars} video (i.e., Lecture~2).
 
@@
 striking correspondence (Fig.~\topicWeights). Specifically, the average topic
-weights from lecture~1 are strongly correlated with the average topic weights
-from lecture~1 questions ($r(13) = 0.809,~p < 0.001$, 95\% confidence interval
-(CI)~$= [0.633,~0.962]$), and the average topic weights from lecture~2 are
-strongly correlated with the average topic weights from lecture~2 questions
+weights from Lecture~1 are strongly correlated with the average topic weights
+from Lecture~1 questions ($r(13) = 0.809,~p < 0.001$, 95\% confidence interval
+(CI)~$= [0.633,~0.962]$), and the average topic weights from Lecture~2 are
+strongly correlated with the average topic weights from Lecture~2 questions
 ($r(13) = 0.728,~p = 0.002$, 95\% CI~$= [0.456,~0.920]$). At the same time, the
 average topic weights from the two lectures are \textit{negatively} correlated with 
-their non-matching question sets (lecture~1 video vs.~lecture~2 questions: $r(13) = 
--0.547,~p = 0.035$, 95\% CI~$= [-0.812, ~-0.231]$; lecture~2 video vs.~lecture~1 questions: $r(13) 
+their non-matching question sets (Lecture~1 video vs.~Lecture~2 questions: $r(13) = 
+-0.547,~p = 0.035$, 95\% CI~$= [-0.812, ~-0.231]$; Lecture~2 video vs.~Lecture~1 questions: $r(13) 
 = -0.612,~p = 0.015$, 95\% CI~$= [-0.874,~-0.281]$), indicating that the topic model
@@
 questions) between the lectures and questions. The variability in topic
-expression (over time and across questions) was similar for the lecture~1 video
-and questions ($r(13) = 0.824,~p<0.001$, 95\% CI~$= [0.696,~0.973]$) and the lecture~2
+expression (over time and across questions) was similar for the Lecture~1 video
+and questions ($r(13) = 0.824,~p<0.001$, 95\% CI~$= [0.696,~0.973]$) and the Lecture~2
 video and questions ($r(13) = 0.801,~p<0.001$, 95\% CI~$= [0.539,~0.958]$). 
@@
 topic expressions across \textit{different} videos and lecture-specific
-questions (i.e., lecture~1 video vs.~lecture~2 questions; lecture~2 video
-vs.~lecture~1 questions) were negatively correlated, and neither
+questions (i.e., Lecture~1 video vs.~Lecture~2 questions; Lecture~2 video
+vs.~Lecture~1 questions) were negatively correlated, and neither
 video's topic variability was reliably correlated with the topic variability
@@
 duration: 7 minutes and 57 seconds). We then hand-created 39 multiple-choice
-questions: 15 about the conceptual content of \textit{Four Fundamental Forces} (i.e., lecture~1),
-15 about the conceptual content of \textit{Birth of Stars} (i.e., lecture~2), and 9
+questions: 15 about the conceptual content of \textit{Four Fundamental Forces} (i.e., Lecture~1),
+15 about the conceptual content of \textit{Birth of Stars} (i.e., Lecture~2), and 9
 questions that tested for general conceptual knowledge about basic physics
@@
 Over the course of the experiment, participants completed three 13-question
-multiple-choice quizzes: the first before viewing lecture~1, the second between
-lectures~1 and 2, and the third after viewing lecture~2
+multiple-choice quizzes: the first before viewing Lecture~1, the second between
+Lectures~1 and 2, and the third after viewing Lecture~2
 (Fig.~\ref{fig:experiment}). The questions appearing on each quiz, for each
 participant, were randomly chosen from the full set of 39, with the constraints
-that (a) each quiz contain 5 questions about lecture~1, 5 questions about
-lecture~2, and 3 questions about general physics knowledge, and (b) each
+that (a) each quiz contain 5 questions about Lecture~1, 5 questions about
+Lecture~2, and 3 questions about general physics knowledge, and (b) each
 question appear exactly once for each participant. The orders of questions on

### 2023-02-21 paper/main.tex

@@
 this approach separately for the questions from each quiz the participants took
-throughout the experiment. From just a few questions per quiz, we obtain a
+throughout the experiment. From just a few questions per quiz (see Sec.~\ref{subsec:traces}), we obtain a
 high-resolution snapshot (at the time each quiz was taken) of what the
@@
 reflect similar themes, according to the model) will yield similar coordinates
-(in terms of Euclidean distance, correlation, or other geometric measures). In
+(in terms of correlation, cosine similarity, Kullback-Leibler divergence, Euclidean distance, or other geometric measures). In
 general, the similarity between different documents' topic vectors may be used

### 2023-02-22 paper/main.tex
minor edits through intro

@@
 concepts. We test our approach using behavioral data from participants who
-answered small sets of multiple-choice quiz questions, interleaved between
+answered small sets of multiple-choice quiz questions interleaved between
 watching two course videos from the Khan Academy platform. We apply our
@@
 Suppose that a teacher had access to a complete, tangible ``map'' of everything
-a student knew. Defining what such a map might even look like, let alone how it
+a student knows. Defining what such a map might even look like, let alone how it
 might be constructed or filled in, is itself a non-trivial problem. But if a
@@
 ability to teach that student? Perhaps they might start by checking how well
-the student knew the to-be-learned information already, or how much they knew
+the student knows the to-be-learned information already, or how much they know
 about related concepts. For some students, they could potentially optimize
@@
 the same quiz data required to compute proportion-correct scores or letter
-grades can instead be used to obtain much more detailed insights into what the
-student knows at the time they took the quiz.
+grades can instead be used to obtain far more detailed insights into what a
+student knew at the time they took the quiz.
 
@@
 researchers in education, cognitive psychology, and cognitive
-neuroscience (e.g.,~\citealp{Kato40, Gall00, ScotEtal07, HallGree08, Macl05})
+neuroscience (e.g.,~\citealp{Kato40, Gall00, ScotEtal07, HallGree08, Macl05}),
 has profound analogs in the fields of natural language processing and natural
@@
 framework to analyze and interpret behavioral data collected from an experiment
-that had participants answer sets multiple-choice questions about a series of
+that had participants answer sets of multiple-choice questions about a series of
 recorded course lectures.
@@
 models can be used to construct ``maps'' of what students know, and how their
-knowledge changes with training. In addition to helping to visualize knowledge
+knowledge changes with training. In addition to helping to visually capture knowledge
 (and changes in knowledge), we hope that such maps might lead to real-world

### 2023-02-22 paper/main.tex
fixed supplementary figure names and references in main text

@@
 % supplemental tables
-\newcommand{\questions}{S1}
-\newcommand{\topics}{S2}
+\newcommand{\questions}{1}
+\newcommand{\topics}{2}
 
 % supplemental figures
-\newcommand{\topicWeights}{S1} 
-\newcommand{\individualKnowledgeMapsA}{S2}
-\newcommand{\individualKnowledgeMapsB}{S3}
-\newcommand{\individualKnowledgeMapsC}{S4}
-\newcommand{\individualLearningMapsA}{S5}
-\newcommand{\individualLearningMapsB}{S6}
+\newcommand{\topicWeights}{1} 
+\newcommand{\individualKnowledgeMapsA}{2}
+\newcommand{\individualKnowledgeMapsB}{3}
+\newcommand{\individualKnowledgeMapsC}{4}
+\newcommand{\individualLearningMapsA}{5}
+\newcommand{\individualLearningMapsB}{6}
 
@@
 representing an individual's knowledge (where similar concepts occupy nearby
-coordinates), their ``level of knowledge'' should change relatively gradually
-throughout that space. To begin to test this smoothness assumption, we sought
+coordinates), their ``level of knowledge'' should change relatively gradually. 
+To begin to test this smoothness assumption, we sought
 to track participants' knowledge and how it changed over time in response to
 training. Two overarching goals guide our approach. First, we want to gain
-detailed insights into what learners know, at different points in their
+detailed insights into what learners know at different points in their
 training. For example, rather than simply reporting on the proportions of
@@
 Second, we want our approach to be potentially scalable to large numbers of
-concepts, courses, and students. This requires that the conceptual content of
+diverse concepts, courses, and students. This requires that the conceptual content of
 interest be discovered \textit{automatically}, rather than relying on
@@
 videos that were intended to be viewed at the start of students' training in
-their respective content areas. Second, we wanted both lectures to have some
+their respective content areas. Second, we wanted the two lectures to have some
 related content, so that we could test our approach's ability to distinguish
@@
 along with related knowledge about physics not specifically presented in either
-video (see Tab.~\questions~for the full list of questions in our stimulus
+video (see Supplementary Tab.~\questions~for the full list of questions in our stimulus
 pool). Participants answered questions randomly drawn from each content area
@@
 lectures' windows) to both lectures, along with the text of each question in
-our pool (Tab.~\questions), to project them into a shared text embedding space.
+our pool (Supplementary Tab.~\questions), to project them into a shared text embedding space.
 This results in one trajectory per lecture and one coordinate for each
@@
 and question set (averaging across time and questions, respectively) reveals a
-striking correspondence (Fig.~\topicWeights). Specifically, the average topic
+striking correspondence (Supplementary Fig.~\topicWeights). Specifically, the average topic
 weights from Lecture~1 are strongly correlated with the average topic weights
@@
 between average topic weights for the lectures and question sets is reported in
-Figure~\topicWeights.
+Supplementary Figure~\topicWeights.
 
@@
 topic 2; yellow-green: topic 4). The top-weighted words from the full set of
-topics may be found in Table~\topics. \textbf{B. Relationships between topic
+topics may be found in Supplementary Table~\topics. \textbf{B. Relationships between topic
 weight variability.} Pairwise correlations between the distributions of topic
@@
 across general physics knowledge questions. Taken together, the analyses
-reported in Figures~\ref{fig:topics} and~\topicWeights~indicate that a topic
+reported in Figure~\ref{fig:topics} and Supplementary Figure~\topicWeights~indicate that a topic
 model fit to the videos' transcripts can also reveal correspondences (at a
@@
     individual participants' maps, see
-    Figures~\individualKnowledgeMapsA,~\individualKnowledgeMapsB,
+    Supplementary Figures~\individualKnowledgeMapsA,~\individualKnowledgeMapsB,
     and~\individualKnowledgeMapsC. \textbf{B. Average ``learning maps''
@@
     quizzes. Each map reflects an average across all participants. For
-    individual participants' maps, see
+    individual participants' maps, see Supplementary
     Figures~\individualLearningMapsA~and~\individualLearningMapsB. \textbf{C.
@@
 (covering material that was not presented in either video). The full set of
-questions and answer choices may be found in Table~\questions.
+questions and answer choices may be found in Supplementary Table~\questions.
 
@@
 model. The top words from each of the 15 discovered topics may be found in
-Table~\topics.
+Supplementary Table~\topics.
 
@@
 resulting timeseries to one vector per second. We also used the fitted model to
-obtain topic vectors for each question in our pool (Tab.~\questions). Taken
+obtain topic vectors for each question in our pool (Supplementary Tab.~\questions). Taken
 together, we obtained a \textit{trajectory} for each video, describing its path
@@
 appearing in the lectures. To visualize these estimates
-(Figs.~\ref{fig:knowledge-maps},~\individualKnowledgeMapsA,~\individualKnowledgeMapsB,~\individualKnowledgeMapsC,~\individualLearningMapsA,
+(Fig.~\ref{fig:knowledge-maps}, Supplementary Figs.~\individualKnowledgeMapsA,~\individualKnowledgeMapsB,~\individualKnowledgeMapsC,~\individualLearningMapsA,
 and~\individualLearningMapsB), we used Uniform Manifold Approximation and

### 2023-02-23 paper/main.tex
edits up through pg 14

@@
 factors, and so on. For example, consider the relative utility of the
-imaginary map described above that characterizes a student's knowledge
+theoretical map described above that characterizes a student's knowledge
 in detail, versus a single annotation saying that the student answered 85\% of
@@
 understanding, often by training participants to distinguish arbitrary or
-random features in otherwise meaningless categorized stimuli. However the
+random features in otherwise meaningless categorized stimuli~\citep{ReilEtal82, Este86a, Este86b, GlucEtal02, AshbMadd05, HulbNorm15}. However the
 objective of real-world training, or learning from life experiences more
@@
 lectures to be accessible to a broad audience (i.e., with minimal prerequisite
-knowledge) so as to limit the impact of prior training on our participants'
+knowledge) so as to limit the impact of prior training on participants'
 abilities to learn from the lectures. To this end, we selected two introductory
@@
 related content, so that we could test our approach's ability to distinguish
-similar conceptual content. To this end, we chose two videos from the same (per
-instructor annotations) Khan Academy course domain, ``Cosmology and
+similar conceptual content. To this end, we chose two videos from the same
+Khan Academy course domain, ``Cosmology and
 Astronomy.'' Third, we sought to minimize dependencies and specific overlap
@@
 enable us to evaluate participants' knowledge about each individual lecture,
-along with related knowledge about physics not specifically presented in either
+along with related knowledge about physics concepts not specifically presented in either
 video (see Supplementary Tab.~\questions~for the full list of questions in our stimulus
@@
 Transforming the text from every sliding window with our model yielded a
-number-of-windows by number-of-topics (15) topic-proportions matrix that
-described the unique mixture of broad themes from both lectures reflected in
+number-of-windows by number-of-topics (15) topic-proportions matrix
+describing the unique mixture of broad themes from both lectures reflected in
 each window's text. Each window's ``topic vector'' (i.e., column of the
@@
 video and questions ($r(13) = 0.801,~p<0.001$, 95\% CI~$= [0.539,~0.958]$). 
-However, as reported in Figure~\ref{fig:topics}B, the variability in
-topic expressions across \textit{different} videos and lecture-specific
+Simultaneously, as reported in Figure~\ref{fig:topics}B, the variability in
+topic expression across \textit{different} videos and lecture-specific
 questions (i.e., Lecture~1 video vs.~Lecture~2 questions; Lecture~2 video
@@
 
-Although a single lecture may be organized around a single broad theme at a
-coarse scale, at a finer scale each moment of a lecture typically covers a
-narrower range of content. We wondered whether a text embedding model trained
-on the lectures' transcripts might capture some of this finer scale content.
+While an individual lecture may be organized around a single broad theme at a
+coarse scale, at a finer scale, each moment of a lecture typically covers a
+narrower range of content. Given the correspondence we found between the variability
+in topic expression across moments of each lecture and questions from its
+corresponding set (Fig.~\ref{fig:topics}), we wondered whether the text embedding model
+might additionally capture these conceptual relationships at a finer scale.
 For example, if a particular question asks about the content from one small
 part of a lecture, we wondered whether the text embeddings could be used to
-automatically identify the ``matching'' moment(s) in the lecture. When we
-correlated each question's topic vector with the topic vectors from each second
-of the lectures, we found some evidence that each question is temporally
-specific (Fig.~\ref{fig:question-correlations}). In particular, most questions'
+automatically identify the ``matching'' moment(s) in the lecture. To explore this,
+we computed the correlation between each question's topic weights and the topic weights
+for each second of its corresponding lecture, and found that each question appeared to be
+temporally specific (Fig.~\ref{fig:question-correlations}). In particular, most questions'
 topic vectors were maximally correlated with a well-defined (and relatively
@@
 correlations fell off sharply outside of that range. We also qualitatively examined the
-best-matching intervals for each question by comparing the text
-of the question to the text of the most-correlated parts of the lectures.
+best-matching intervals for each question by comparing the question's text
+to the text of the most-correlated parts of the lectures.
 Despite that the questions were excluded from the text embedding model's
@@
 
-\begin{figure}[tp] \centering
+\begin{figure}[t] 
+    \centering
     \includegraphics[width=\textwidth]{figs/lecture-question-similarity}
@@
 missed three questions about three \textit{different} concepts (e.g., $A$, $B$,
-and $C$). But if we wanted to fill in the ``gaps'' in the two students'
-understandings, we might do well to focus on concept $A$ for the first student,
+and $C$). But if we wanted to help these two students fill in the ``gaps'' in their
+understandings, we might do well to focus specifically on concept $A$ for the first student,
 but to also add in materials pertaining to concepts $B$ and $C$ for the second
@@
 lecture they had watched; see \nameref{subsec:traces}). Essentially, the
-estimated knowledge at the coordinate is given by the weighted average
+estimated knowledge at coordinate $x$ is given by the weighted average
 proportion of quiz questions the participant answered correctly, where the
@@
 describing how much ``knowledge'' the participant has about any part of the
-lecture. As shown in Figure~\ref{fig:knowledge-timeseries}, we can also apply
-this approach separately for the questions from each quiz the participants took
-throughout the experiment. From just a few questions per quiz (see Sec.~\ref{subsec:traces}), we obtain a
+lecture. As shown in Figure~\ref{fig:knowledge-timeseries}A and C, we can apply
+this approach separately for the questions from each quiz participants took
+throughout the experiment. From just a few questions per quiz (see~\nameref{subsec:traces}), we obtain a
 high-resolution snapshot (at the time each quiz was taken) of what the
@@
     questions about the content reflected in each moment of the lecture (see
-    \nameref{subsec:traces}), using responses from one
+    \nameref{subsec:traces}), using responses from a single
     quiz (color). The traces are averaged across participants. \textbf{B.
@@
 
-Of course, even though the timecourses in
+While the timecourses in
 Figure~\ref{fig:knowledge-timeseries}A and C provide detailed
-\textit{estimates} about participants' knowlege, those estimates are only
+\textit{estimates} about participants' knowlege, these estimates are of course only
 \textit{useful} to the extent that they accurately reflect what participants
 actually know. As one sanity check, we anticipated that the knowledge estimates
-should show a content-specific ``boost'' in participants' knowledge after
+should reflect a content-specific ``boost'' in participants' knowledge after
 watching each lecture. In other words, if participants learn about each
 lecture's content when they watch each lecture, the knowledge estimates should
-reflect that. After watching the \textit{Four Fundamental Forces} lecture,
-participants should show more knowledge for the content of that lecture than
+capture that. After watching the \textit{Four Fundamental Forces} lecture,
+participants should exhibit more knowledge for the content of that lecture than
 they had before, and that knowledge should persist for the remainder of the
@@
 Similarly, we hypothesized (and subsequently confirmed) that participants
-should show more estimated knowledge about the content of the \textit{Birth of
+should show greater estimated knowledge about the content of the \textit{Birth of
 Stars} lecture after (versus before) watching it
@@
 
-If we are able to accurately estimate a participant's knowledge about the
+Additionally, if we are able to accurately estimate a participant's knowledge about the
 content tested by a given question, our estimates of their knowledge should carry some
-predictive information about whether the participant is likely to answer the
-question correctly or incorrectly. We developed a statistical approach to test this claim. 
-For each question in turn, for each
-participant, we used Equation~\ref{eqn:prop} to estimate (using all
-\textit{other} questions from the same quiz, from the same participant) the
-participant's knowledge at the held-out question's embedding coordinate. For
+predictive information about whether the participant is likely to answer that
+question correctly or incorrectly. To further validate our knowledge estimates, we developed a statistical approach to test this claim. 
+For each question in turn, we used equation~\ref{eqn:prop} to estimate each 
+participant's knowledge at the given question's embedding space coordinate, 
+using all \textit{other} questions that participant answered on the same quiz.
+%For each question in turn, for each
+%participant, we used Equation~\ref{eqn:prop} to estimate (using all
+%\textit{other} questions from the same quiz, from the same participant) the
+%participant's knowledge at the held-out question's embedding coordinate. 
+For
 each quiz, we grouped these estimates into two distributions: one for the
-estimated knowledge at the coordinates of each \textit{correctly} answered
-question, and another for the estimated knowledge at the coordinates of each
-\textit{incorrectly} answered question (Fig.~\ref{fig:predictions}). We then
+estimated knowledge at the coordinates of \textit{correctly} answered
+questions, and another for the estimated knowledge at the coordinates of
+\textit{incorrectly} answered questions (Fig.~\ref{fig:predictions}). We then
 used independent samples $t$-tests to compare the means of these distributions
@@
 As in our other analyses, we resampled each lecture's topic trajectory to 1~Hz
-and also projected each question into a shared text embedding space.
+and projected each question into a shared text embedding space.
 

### 2023-02-25 paper/supplement.tex
fixed supplementary figure names and references in main text
new topic-word distributions supp fig & caption

@@
 \renewcommand{\figurename}{Supplementary Figure}
+\renewcommand{\tablename}{Supplementary Table}
 
@@
 \makeatletter
-\renewcommand{\theequation}{S\arabic{equation}}
-\renewcommand{\thefigure}{S\arabic{figure}}
-\renewcommand{\thetable}{S\arabic{table}}
-\renewcommand{\bibnumfmt}[1]{[S#1]}
-\renewcommand{\citenumfont}[1]{S#1}
+%\renewcommand{\theequation}{S\arabic{equation}}
+%\renewcommand{\thefigure}{S\arabic{figure}}
+%\renewcommand{\thetable}{S\arabic{table}}
+%\renewcommand{\bibnumfmt}[1]{[S#1]}
+%\renewcommand{\citenumfont}[1]{S#1}
 
@@
 
-\newpage
-
 \begin{table}[tp]
@@
 \begin{figure}[tp]
+    \includegraphics[width=\textwidth]{figs/topic-word-distributions}
+
+    \caption{\textbf{Topic-word distributions}. Each topic is defined by a distribution 
+    of weights over words in the topic model's vocabulary (i.e., the union of all unique 
+    words from the two lectures' transcripts, excluding stop-words, after 
+    preprocessing). Each plot above displays the weights for the (up to) 50 words 
+    weighted most heavily by an individual topic extracted from the lectures' contents (see 
+    \textit{Constructing text embeddings of multiple lectures and questions}).}
+
+    \label{fig:topic-word-distributions}
+\end{figure}
+
+\begin{figure}[tp]
     \includegraphics[width=\textwidth]{figs/topic-weights}
@@
 displayed in the upper right (orange: topic 2; yellow-green: topic 4). The
-top-weighted words from the full set of topics may be found in
+top-weighted words from the full set of topics may be found in Supplementary
 Table~\ref{tab:topics}. \textbf{B. Relationships between average topic

### 2023-02-26 paper/supplement.tex
remove zero-weighted words from supp table 2, update caption

@@
 
-\newcommand{\topics}{3}
+\newcommand{\topicVariability}{3}
 \newcommand{\knowledgeMaps}{7}
+\newcommand{\topicModelMethods}{\textit{Constructing text embeddings of multiple lectures and questions}}
 
@@
                  8 &     proton &       weak &         neutron & interaction &        one &         go &       nucleon &      cesium &      extra &             get \\\hline
-    9     &      run &      kind &              say &           go &     want &     would &            get &         well &      give &         although \\\hline
-    10     &     huge &     cloud &            space &        float &  imagine &  hydrogen &           atom &          say &  distance &          combine \\\hline
+                 9 &            &            &                 &             &            &            &               &             &            &                 \\\hline
+                10 &       huge &      cloud &           space &       float &    imagine &   hydrogen &          atom &             &            &                 \\\hline
                 11 &        one &   hydrogen &          helium &          go &     proton &    neutron &          keep &      atomic &     detail &            fuse \\\hline
@@
 
-\caption{\textbf{Topics.} The table displays the 10 top-weighted words (columns) from
-    each of the 15 topics (rows) identified from sliding windows of the two course video
-    transcripts (see \textit{Constructing text embeddings of multiple lectures
-    and questions}).}
+    \caption{\textbf{Topics.} We fit a topic model with (up to) $k = 15$ topics to sliding 
+    windows parsed from the two course video transcripts (see~\topicModelMethods),
+    and identified 14 topics with non-zero weights. The table displays the (up to) 10 
+    top-weighted words (columns) from each of the topics (rows) discovered by the 
+    model. The weights of these words are shown in Supplementary Figure~\ref{fig:topic-word-distributions}.}
     \label{tab:topics}
@@
     preprocessing). Each plot above displays the weights for the (up to) 50 words 
-    weighted most heavily by an individual topic extracted from the lectures' contents (see 
-    \textit{Constructing text embeddings of multiple lectures and questions}).}
+    weighted most heavily by an individual topic extracted from the lectures' contents 
+    (see~\topicModelMethods).}
 
@@
 weights for each lecture and question set. Each row and column corresponds
-to a bar plot in Panel A. Also see Figure~\topics~in the main text.}
+to a bar plot in Panel A. Also see Figure~\topicVariability~in the main text.}
 

### 2023-02-28 paper/supplement.tex
final pass through supplement
revert changes to top words table

@@
 \makeatletter
-%\renewcommand{\theequation}{S\arabic{equation}}
-%\renewcommand{\thefigure}{S\arabic{figure}}
-%\renewcommand{\thetable}{S\arabic{table}}
-%\renewcommand{\bibnumfmt}[1]{[S#1]}
-%\renewcommand{\citenumfont}[1]{S#1}
-
-% \newcommand{\demo}{1}
 
@@
 
-    \caption{\textbf{Question pool.} Each participant answered questions on
-    three 13-question quizzes. Each quiz included 5 questions about the \textit{Four Fundamental Forces}
-    lecture (FFF), 5 questions about the \textit{Birth of Stars} lecture (BoS),
-    and 3 questions about general physics knowledge (GPK). Each question appeared
-    on at most one quiz (for each participant).}
+    \caption{\textbf{Question pool.} Each participant completed three quizzes consisting 
+    of 13 multiple-choice questions randomly selected from the question pool. Each 
+    quiz included 5 questions about the \textit{Four Fundamental Forces} lecture 
+    (FFF), 5 questions about the \textit{Birth of Stars} lecture (BoS), and 3 questions 
+    about general physics knowledge (GPK). Each question appeared on at most 
+    one quiz (for each participant).}
 
@@
     \begin{tabular}{r|l|l|l|l|l|l|l|l|l|l}
-
     \textbf{Topic} & \textbf{1} & \textbf{2} &      \textbf{3} &  \textbf{4} & \textbf{5} & \textbf{6} &    \textbf{7} &  \textbf{8} & \textbf{9} &     \textbf{10} \\\hline
@@
              8 &     proton &       weak &         neutron & interaction &        one &         go &       nucleon &      cesium &      extra &             get \\\hline
-                 9 &            &            &                 &             &            &            &               &             &            &                 \\\hline
-                10 &       huge &      cloud &           space &       float &    imagine &   hydrogen &          atom &             &            &                 \\\hline
+            10 &       huge &      cloud &           space &       float &    imagine &   hydrogen &          atom &         say &   distance &         combine \\\hline
             11 &        one &   hydrogen &          helium &          go &     proton &    neutron &          keep &      atomic &     detail &            fuse \\\hline
@@
             14 &      force &       atom &         nucleus &    electron &       much &   hydrogen &           get &      around &    coulomb &          charge \\\hline
-                15 &      force &      scale &         gravity &       start &       weak &      orbit &          keep & fundamental &     around &        surprise \\
-
+            15 &      force &      scale &         gravity &       start &       weak &      orbit &          keep & fundamental &     around &        surprise \\\hline
     \end{tabular}    
@@
     windows parsed from the two course video transcripts (see~\topicModelMethods),
-    and identified 14 topics with non-zero weights. The table displays the (up to) 10 
+    and identified 14 topics with non-zero weights. The table displays the 10 
     top-weighted words (columns) from each of the topics (rows) discovered by the 
@@
 
-    \label{fig:learning-maps-q1_2}
+    \label{fig:learning-maps-q2_3}
 \end{figure}

### 2023-02-28 paper/main.tex
added info about choosing number of topics and refs to new supp fig

@@
 may be represented as a $k$-dimensional vector describing how much the document
-(most probably) reflects each topic. (Unless, otherwise noted, we used $k = 15$
-topics.)
+(most probably) reflects each topic.
+To select an appropriate $k$ for our model, we identified the minimum number of
+topics that yielded at least one ``unused'' topic (i.e., in which all words in the vocabulary
+were assigned zero weight) after training. This indicated that the number of topics was
+sufficient to capture the set of latent themes present in the two lectures (from which we
+constructed our document corpus, as described below). We found this value to be $k = 15$
+topics. The distribution of weights over words in the vocabulary for each discovered topic is
+shown in Supplementary Figure~\topicWordWeights, and each topic's top-weighted
+words may be found in Supplementary Table~\topics.
 

### 2023-02-28 paper/main.tex
clearer justification for k = 100 topics for embeddings

@@
 lectures participants watched, we first fit a new topic model to the lectures'
-sliding windows with $k = 100$ topics. We hoped that increasing the number of
-topics from 15 to 100 might help us to generalize the knowledge predictions.
-(Aside from increasing the number of topics from 15 to 100, all other
-procedures and model parameters were carried over from the preceding analyses.)
+sliding windows with (up to)~$k = 100$~topics.
+Conceptually, increasing the number of topics used by the model functions to
+increase the ``resolution'' of the embedding space, providing a greater ability to
+estimate knowledge for content that is highly similar to (but not precisely the same as)
+that contained in the lectures.
+Aside from increasing the number of topics from 15 to 100, all other
+procedures and model parameters were carried over from the preceding analyses.
 As in our other analyses, we resampled each lecture's topic trajectory to 1~Hz

### 2023-02-28 paper/main.tex
refined discussion of fig 6 results

@@
 the held-out question had been correctly versus incorrectly answered ($t(633) =
-0.577,~p = 0.564$). After watching the first video, estimated knowledge for
+0.577,~p = 0.564$). This reflects a floor effect: when knowledge is low
+everywhere, there is little signal to differentiate between what is known
+versus unknown. After watching the first lecture, estimated knowledge for
 held-out correctly answered questions (from the second quiz;
 Fig.~\ref{fig:predictions}, middle panel) exhibited a positive shift relative
-to held-out incorrectly answered questions ($t(633) = 3.961,~p < 0.001$). After
-watching the second video, estimated knowledge (from the third quiz;
-Fig.~\ref{fig:predictions}, right panel) for \textit{all} questions exhibited a
-positive shift. However, the increase in estimated knowledge for held-out
-correctly answered questions was larger than for held-out incorrectly answered
-questions (estimated knowledge for correctly versus incorrectly answered
-Quiz~3 questions: $t(628) = 2.045,~p = 0.041$).
+to held-out incorrectly answered questions ($t(633) = 3.961,~p < 0.001$). This
+second quiz provides the maximally sensitive test for our knowledge
+predictions, since (if knowledge is estimated accurately) participants' Quiz~2
+responses should demonstrate specific knowledge about Lecture~1 content, but
+knowledge about Lecture~2 and general physics concepts should be roughly
+unchanged from before they watched Lecture~1. After watching the second lecture,
+estimated knowledge (from the third quiz; Fig.~\ref{fig:predictions}, right
+panel) for \textit{all} questions exhibited a positive shift. However, the
+estimated knowledge for held-out correctly answered questions remained
+greater than that for held-out incorrectly answered questions ($t(628) = 2.045,~p
+= 0.041$). This third contrast reflects a ceiling effect: when knowledge is
+relatively high everywhere, the signal differentiating what is known versus
+unknown is relatively weak. Taken together, this set of analyses demonstrates
+that our knowledge prediction framework is most informative when participants
+exhibit variability in their knowledge of the content captured by the text
+embedding model.
 

### 2023-03-01 paper/main.tex
edits up through end of results

@@
 % supplemental figures
-\newcommand{\topicWeights}{1}
-\newcommand{\individualKnowledgeMapsA}{2}
-\newcommand{\individualKnowledgeMapsB}{3}
-\newcommand{\individualKnowledgeMapsC}{4}
-\newcommand{\individualLearningMapsA}{5}
-\newcommand{\individualLearningMapsB}{6}
+\newcommand{\topicWordWeights}{1}
+\newcommand{\topicWeights}{2}
+\newcommand{\individualKnowledgeMapsA}{3}
+\newcommand{\individualKnowledgeMapsB}{4}
+\newcommand{\individualKnowledgeMapsC}{5}
+\newcommand{\individualLearningMapsA}{6}
+\newcommand{\individualLearningMapsB}{7}
 
@@
     embedding model. \textbf{B. Constructing lecture content
-    \textit{trajectories}.} After training our model on the sliding windows from
+    \textit{trajectories}.} After training the model on the sliding windows from
     both lectures, we transform each lecture into a ``trajectory'' through text
@@
 text of the lecture transcript from a particular time span. We treated the set
-of text snippets (across all of these windows) as documents to fit our model
-(Fig.~\ref{fig:sliding-windows}A; see \nameref{subsec:topic-modeling}).
-Transforming the text from every sliding window with our model yielded a
+of text snippets (across all of these windows) as documents to fit the model
+(Fig.~\ref{fig:sliding-windows}A; see~\nameref{subsec:topic-modeling}).
+Transforming the text from every sliding window with the model yielded a
 number-of-windows by number-of-topics (15) topic-proportions matrix
@@
 
-Additionally, if we are able to accurately estimate a participant's knowledge about the
+If we are able to accurately estimate a participant's knowledge about the
 content tested by a given question, our estimates of their knowledge should carry some
 predictive information about whether the participant is likely to answer that
-question correctly or incorrectly. To further validate our knowledge estimates, we developed a statistical approach to test this claim.
+question correctly or incorrectly. We developed a statistical approach to test this claim.
 For each question in turn, we used equation~\ref{eqn:prop} to estimate each
@@
 illustrated in Figure~\ref{fig:knowledge-maps}, our general approach to
-estimating knowledge from a small number of quiz questions may be applied to
+estimating knowledge from a small number of quiz questions may be extended to
 \textit{any} content, given its text embedding coordinate. To visualize how
@@
 estimate knowledge for content that is highly similar to (but not precisely the same as)
-that contained in the lectures.
+that contained in the two lectures.
 Aside from increasing the number of topics from 15 to 100, all other
@@
     reflected by \textit{all} regions of topic space (see
-    \nameref{subsec:knowledge-maps}). The topic trajectories of each
-    lecture are indicated by dotted lines, and the coordinates of each question are indicated by
-    dots. Each map reflects an average across all participants. For
-    individual participants' maps, see
-    Supplementary Figures~\individualKnowledgeMapsA,~\individualKnowledgeMapsB,
+    \nameref{subsec:knowledge-maps}). The topic trajectories of the two
+    lectures are indicated by dotted lines (blue: Lecture 1; green: Lecture 2),
+    and the coordinates of each question are indicated by dots (light blue:
+    Lecture 1-related; light green: Lecture 2-related; purple: general physics
+    knowledge). Each map reflects an average across all participants. For
+    individual participants' maps, see Supplementary
+    Figures~\individualKnowledgeMapsA,~\individualKnowledgeMapsB,
     and~\individualKnowledgeMapsC. \textbf{B. Average ``learning maps''
     estimated between each successive pair of quizzes.} The learning maps follow
-    the same general format as the knowledge maps in Panel A, but here the shading at each
-    coordinate indicates the \textit{difference} between
-    the corresponding coordinates in the indicated \textit{pair} of knowledge
+    the same general format as the knowledge maps in Panel A, but here the
+    shading at each coordinate indicates the \textit{difference} between the
+    corresponding coordinates in the indicated \textit{pair} of knowledge
     maps---i.e., how much the estimated knowledge ``changed'' between the two
@@
     Figures~\individualLearningMapsA~and~\individualLearningMapsB. \textbf{C.
-    Word clouds for sampled points in topic space.} Each word cloud displays
-    the relative weights of each word (via their relative sizes) reflected by the blend of topics
-    represented at the locations of the stars on the maps. The words' colors
-    indicate how much each word is weighted, on average, across all timepoints'
-    topic vectors in the \textit{Four Fundamental Forces} (blue) and
-    \textit{Birth of Stars} (green) videos, respectively.}
+    Word clouds for sampled points in topic space.} Each word cloud displays the
+    weighted blend of words underlying the topic proportions represented at the
+    corresponding colored star's location on the maps. In each word cloud, the
+    words' relative sizes correspond to their relative weights at the starred
+    location, and their colors indicate their relative weights in the
+    \textit{Four Fundamental Forces} (blue) versus \textit{Birth of Stars}
+    (green) lectures, on average, across all timepoints' topic vectors.}
 
@@
 We projected the resulting 100-dimensional topic vectors (for each second of
-video and for each question) onto a shared 2-dimensional plane (see
+video and each quiz question) onto a shared 2-dimensional plane (see
 \nameref{subsec:knowledge-maps}). Next, we sampled points from a $100 \times
@@
 from a given quiz's responses provides a visualization of how ``much''
-participants know about any content expressible by the fitted text embedding
-model.
+participants knew about any content expressible by the fitted text embedding
+model at the point in time when they completed that quiz.
 
@@
 content that is nearby (i.e., related to) the content from the lecture they
-watched prior to taking Quiz~2. This localization is non-trivial: the knowledge
+watched prior to taking Quiz~2. This localization is non-trivial: these knowledge
 estimates are informed only by the embedded coordinates of the \textit{quiz
@@
 estimated knowledge increases we observed across maps were specific to the
-regions around the embeddings of each lecture in turn.
+regions around the embeddings of each lecture, in turn.
 
@@
 example locations on the maps (Fig.~\ref{fig:knowledge-maps}C): one point near
-the \textit{Four Fundamental Forces} embedding (yellow); a second point near
+the \textit{Four Fundamental Forces} embedding (yellow), a second point near
 the \textit{Birth of Stars} embedding (orange), and a third point
 between the two lectures' embeddings (pink). As shown in the word clouds in the
-Panel, the top-weighted words at the example coordinate near the \textit{Four
-Fundamental Forces} embedding also tended to be weighted heavily by the topics
+panel, the top-weighted words at the example coordinate near the \textit{Four
+Fundamental Forces} embedding tended to be weighted more heavily by the topics
 expressed in that lecture. Similarly, the top-weighted words at the example
 coordinate near the \textit{Birth of Stars} embedding tended to be weighted
-most heavily by the topics expressed in \textit{that} lecture. And the
+more heavily by the topics expressed in \textit{that} lecture. And the
 top-weighted words at the example coordinate between the two lectures'

### 2023-03-01 paper/main.tex
edits through end of discussion

@@
 concept within the scope of our text embedding model, and how much their
-knowledge changes with training (Fig.~\ref{fig:knowledge-maps}).
+knowledge of those concepts changes with training (Fig.~\ref{fig:knowledge-maps}).
 
 Over the past several years, the global pandemic has forced many educators to
-teach remotely~\citep{MoseEtal21, ShimLee20, KawaEtal21, Whal20}. This change
+suddenly adapt to teaching remotely~\citep{MoseEtal21, ShimLee20, KawaEtal21, Whal20}. This change
 in world circumstances is happening alongside (and perhaps accelerating)
-geometric growth in the availability of high quality online courses on
+geometric growth in the availability of high-quality online courses from
 platforms such as Khan Academy~\citep{Khan04}, Coursera~\citep{Youn12},
@@
 facilitated improvements in video streaming, enabling videos to be easily
-shared and viewed by large segments of the world's population. This
+shared and viewed by increasingly large segments of the world's population. This
 exciting time for online course instruction provides an opportunity to
 re-evaluate how we, as a global community, educate ourselves and each other.
-For example, we can ask: what makes an effective course or training program?
+For example, we can ask: what defines an effective course or training program?
 Which aspects of teaching might be optimized and/or augmented by automated tools? How and why do
-learning needs and goals vary across people? How might we lower barriers to
-achieving a high-quality education?
+learning needs and goals vary across people? How might we lower barriers of access
+to a high-quality education?
 

### 2023-03-01 paper/main.tex
final edits to methods and ending sections of paper

@@
 We enrolled a total of 50 Dartmouth undergraduate students in our study.
-Participants received course credit for enrolling. We asked each participant to
+Participants received optional course credit for enrolling. We asked each participant to
 complete a demographic survey that included questions about their age, gender,
@@
 Lectures~1 and 2, and the third after viewing Lecture~2
-(Fig.~\ref{fig:experiment}). The questions appearing on each quiz, for each
+(see Fig.~\ref{fig:experiment}). The questions appearing on each quiz, for each
 participant, were randomly chosen from the full set of 39, with the constraints
-that (a) each quiz contain 5 questions about Lecture~1, 5 questions about
+that (a) each quiz contain exactly 5 questions about Lecture~1, 5 questions about
 Lecture~2, and 3 questions about general physics knowledge, and (b) each
@@
 randomized. Our experimental protocol was approved by the Committee for the
-Protection of Human Subjects at Dartmouth College. We used the experiment to
+Protection of Human Subjects at Dartmouth College. We used this experiment to
 develop and test our computational framework for estimating knowledge and
@@
 Dirichlet Allocation;~\citealp{BleiEtal03}), trained on a set of documents, to
-discover a set of $k$ ``topics'' or ``themes.'' Formally, each topic is defined
-as a set of weights over each word in the model's vocabulary (i.e., the union
+discover a set of (up to) $k$ ``topics'' or ``themes.'' Formally, each topic is defined
+as a distribution of weights over each word in the model's vocabulary (i.e., the union
 of all unique words, across all documents, excluding ``stop words.'').
@@
 topics that yielded at least one ``unused'' topic (i.e., in which all words in the vocabulary
-were assigned zero weight) after training. This indicated that the number of topics was
+were assigned uniform weights) after training. This indicated that the number of topics was
 sufficient to capture the set of latent themes present in the two lectures (from which we
@@
 additionally provides automated captions. We opted to use these automated
-transcripts (which, in prior work, we have found are of sufficiently near-human
-quality yield reliable data in behavioral studies; \citealp{ZimaEtal18}) when
+transcripts (which, in prior work, we have found to be of sufficiently near-human
+quality to yield reliable data in behavioral studies;~\citealp{ZimaEtal18}) when
 developing our framework in order to make it more directly extensible and
@@
 We fetched these automated transcripts using the
-\texttt{youtube-transcript-api} Python package~\citep{Depo19}. The transcripts
+\texttt{youtube-transcript-api} Python package~\citep{Depo18}. The transcripts
 consisted of one timestamped line of text for every few seconds (mean: 2.34~s;
@@
 length of (up to) $w = 30$ transcript lines, and assigned each window a
-timestamp corresponding to the midpoint between its first and last lines'
-timestamps. These sliding windows ramped up and down in length at the very
-beginning and end of the transcript, respectively. In other words, the first
-sliding window covered only the first line from the transcript; the second
-sliding window covered the first two lines; and so on. This insured that each
-line of the transcript appeared in the same number ($w$) of sliding windows.
+timestamp corresponding to the midpoint between the timestamps for its first and last lines.
+These sliding windows ramped up and down in length at the
+beginning and end of each transcript, respectively. In other words, each transcript's first
+sliding window covered only its first line, the second
+sliding window covered the first two lines, and so on. This ensured that each
+line from the transcripts appeared in the same number ($w$) of sliding windows.
+%and was equally represented in the topic model's training corpus.
 After performing various standard text preprocessing (e.g., normalizing case,
@@
 each sliding window as a single ``document,'' and combined these documents
-across the two videos' windows to create a single training corpus for the topic
-model. The top words from each of the 15 discovered topics may be found in
-Supplementary Table~\topics.
+across the two videos' windows to create a single training corpus for the topic model.
+%To select an appropriate number of topics for the model, we identified the
+%minimum $k$ that yielded at least one ``unused'' topic (i.e., in which all words
+%in the vocabulary were assigned zero weight) after training. This indicated that the
+%number of topics was sufficient to capture the set of latent themes present in the two
+%lectures. We found this value to be $k = 15$ topics.
+%Supplementary Figure~\topicWordWeights~displays the distribution of weights over words
+%in the vocabulary for each discovered topic, and each topic's top-weighted words may be found
+%in Supplementary Table~\topics.
 
@@
 resulting timeseries to one vector per second. We also used the fitted model to
-obtain topic vectors for each question in our pool (Supplementary Tab.~\questions). Taken
+obtain topic vectors for each question in our pool (see Supplementary Tab.~\questions). Taken
 together, we obtained a \textit{trajectory} for each video, describing its path
@@
 their knowledge about \textit{any} content expressible by the embedding
-model---not solely the content explicitly probed by the quiz questions or even
+model---not solely the content explicitly probed by the quiz questions, or even
 appearing in the lectures. To visualize these estimates
@@
 and~\individualLearningMapsB), we used Uniform Manifold Approximation and
-Projection (UMAP; \citealp{McInEtal18a}) to construct a 2D projection of the
+Projection (UMAP; \citealp{McInEtal18a, McInEtal18b}) to construct a 2D projection of the
 text embedding space. Sampling the original 100-dimensional space at high
@@
 in the original high-dimensional space were defined as 1 minus the correlation
-between the pair of coordinates, and pairwise distances in the low-dimensional
-embedding space were defiend as the Euclidean distance between the pair of
+between each pair of coordinates, and pairwise distances in the low-dimensional
+embedding space were defined as the Euclidean distance between each pair of
 coordinates.
@@
 In our application, all of the coordinates we embedded were topic vectors,
-whose elements are always non-negative. Although UMAP is an invertible
+whose elements are always non-negative and sum to one. Although UMAP is an invertible
 transformation at the embedding locations of the original data, other locations
@@
 coordinate in the embedding space might result in negative-valued vectors,
-which are incompatable with the topic modeling framework. To protect against
+which are incompatible with the topic modeling framework. To protect against
 this issue, we log-transformed the topic vectors prior to embedding them in the
@@
 inverted (log-transformed) values through the exponential function to obtain a
-vector of non-negative values.
+vector of non-negative values, and normalized them to sum to one.
 

### 2023-03-01 paper/supplement.tex

@@
     words from the two lectures' transcripts, excluding stop-words, after 
-    preprocessing). Each plot above displays the weights for the (up to) 50 words 
+    preprocessing). Each plot above displays the weights for the 50 words 
     weighted most heavily by an individual topic extracted from the lectures' contents 

### 2023-03-01 paper/main.tex
JRM final pass through

@@
 learners' knowledge changed after watching each video. Our findings show how a
-small set of quiz questions may be used to obtain rich and meaningful, high-resolution
-insights into what each learner knows, and how their knowledge
+small set of quiz questions may be used to obtain rich and meaningful
+high-resolution insights into what each learner knows, and how their knowledge
 changes over time as they learn.
@@
 along with related knowledge about physics concepts not specifically presented in either
-video (see Supplementary Tab.~\questions~for the full list of questions in our stimulus
+video (see Supp. Tab.~\questions~for the full list of questions in our stimulus
 pool). Participants answered questions randomly drawn from each content area
@@
     lectures' windows) to both lectures, along with the text of each question in
-    our pool (Supplementary Tab.~\questions), to project them into a shared text embedding space.
+    our pool (Supp. Tab.~\questions), to project them into a shared text embedding space.
     This results in one trajectory per lecture and one coordinate for each
@@
 and question set (averaging across time and questions, respectively) reveals a
-striking correspondence (Supplementary Fig.~\topicWeights). Specifically, the average topic
+striking correspondence (Supp. Fig.~\topicWeights). Specifically, the average topic
 weights from Lecture~1 are strongly correlated with the average topic weights
@@
 question correctly or incorrectly. We developed a statistical approach to test this claim.
-For each question in turn, we used equation~\ref{eqn:prop} to estimate each
+For each question in turn, we used Equation~\ref{eqn:prop} to estimate each
 participant's knowledge at the given question's embedding space coordinate,
@@
 resulting timeseries to one vector per second. We also used the fitted model to
-obtain topic vectors for each question in our pool (see Supplementary Tab.~\questions). Taken
+obtain topic vectors for each question in our pool (see Supp. Tab.~\questions). Taken
 together, we obtained a \textit{trajectory} for each video, describing its path
@@
 correlations) insures that every question
-contributes some non-zero amount to the knowledge estimate.
+contributes some non-negative amount to the knowledge estimate.
 
@@
 appearing in the lectures. To visualize these estimates
-(Fig.~\ref{fig:knowledge-maps}, Supplementary Figs.~\individualKnowledgeMapsA,~\individualKnowledgeMapsB,~\individualKnowledgeMapsC,~\individualLearningMapsA,
+(Fig.~\ref{fig:knowledge-maps}, Supp. Figs.~\individualKnowledgeMapsA,~\individualKnowledgeMapsB,~\individualKnowledgeMapsC,~\individualLearningMapsA,
 and~\individualLearningMapsB), we used Uniform Manifold Approximation and

### 2023-10-10 code/khan_helpers/khan_helpers/functions.py
fixed a couple docstring inconsistencies

@@ -806,14 +806,14 @@ def reconstruct_trace(lecture, questions, accuracy):
 
     Parameters
     ----------
-    lecture: numpy.ndarray
+    lecture : numpy.ndarray
         `(n_coordinates, n_features)` matrix of coordinates for which to
         estimate knowledge.
-    questions: numpy.ndarray
+    questions : numpy.ndarray
         `(n_observations, n_features)` matrix of coordinates for the
         quiz questions used to estimate knowledge for each of the
         `n_coordinates` locations.
-    accuracy: array_like
+    accuracy : array_like
         `(n_observations,)` binary array denoting whether each question
         was answered correctly (`True`|`1`) or incorrectly
         (`False`/`0`).
@@ -963,3 +963,5 @@ def z2r(z):
         Correlation value(s).
     """
     return (np.exp(2 * z) - 1) / (np.exp(2 * z) + 1)
+
+

### 2023-10-11 paper/main.tex
Reworded sentence

@@
 they are ``tagged'' as available for future learning.
-% TODO: is the second half of this paragraph relevant to this paper??
 
@@
 lecture. As shown in Figure~\ref{fig:knowledge-timeseries}A and C, we can apply
-this approach separately for the questions from each quiz participants took
-throughout the experiment. From just a few questions per quiz (see~\nameref{subsec:traces}), we obtain a
+this approach to the questions from each quiz taken throughout the experiment, separately.
+
+From just a few questions per quiz (see~\nameref{subsec:traces}), we obtain a
 high-resolution snapshot (at the time each quiz was taken) of what the
@@
 question correctly or incorrectly. We developed a statistical approach to test this claim.
-For each question in turn, we used Equation~\ref{eqn:prop} to estimate each
+For each question, in turn, we used Equation~\ref{eqn:prop} to estimate each
 participant's knowledge at the given question's embedding space coordinate,
 using all \textit{other} questions that participant answered on the same quiz.
-%For each question in turn, for each
-%participant, we used Equation~\ref{eqn:prop} to estimate (using all
-%\textit{other} questions from the same quiz, from the same participant) the
-%participant's knowledge at the held-out question's embedding coordinate.
-For
-each quiz, we grouped these estimates into two distributions: one for the
+For each quiz, we grouped these estimates into two distributions: one for the
 estimated knowledge at the coordinates of \textit{correctly} answered
@@
 line from the transcripts appeared in the same number ($w$) of sliding windows.
-%and was equally represented in the topic model's training corpus.
 After performing various standard text preprocessing (e.g., normalizing case,
@@
 across the two videos' windows to create a single training corpus for the topic model.
-%To select an appropriate number of topics for the model, we identified the
-%minimum $k$ that yielded at least one ``unused'' topic (i.e., in which all words
-%in the vocabulary were assigned zero weight) after training. This indicated that the
-%number of topics was sufficient to capture the set of latent themes present in the two
-%lectures. We found this value to be $k = 15$ topics.
-%Supplementary Figure~\topicWordWeights~displays the distribution of weights over words
-%in the vocabulary for each discovered topic, and each topic's top-weighted words may be found
-%in Supplementary Table~\topics.
 

### 2023-10-19 code/khan_helpers/khan_helpers/functions.py
fixed a few typos in docstrings

@@ -170,7 +170,7 @@ def corr_mean(rs, axis=None, fix_inf=False, **kwargs):
         Axis or axes along which the means are computed. If `None`
         (default), the mean of the flattened array is computed.
     fix_inf : bool, optional
-        See `z2r()` docstring for details. Default: False.
+        See `r2z()` docstring for details. Default: False.
     **kwargs : various types, optional
         Additional keyword arguments passed to `numpy.nanmean` (see
         https://numpy.org/doc/stable/reference/generated/numpy.nanmean.html
@@ -622,7 +622,7 @@ def preprocess_text(textlist, correction_counter=None):
     POS tagging, and lemmatization.
 
     Occasionally, the Treebank POS tagger mis-tags a word, which causes
-    WordNet's "Morphy" to apply the morphologocal transformations and
+    WordNet's "Morphy" to apply the morphological transformations and
     detachment rules for the wrong syntactic category, and fail to
     lemmatize the word.  The function attempts to handle these
     instances and can optionally record corrections made this way for
@@ -683,7 +683,7 @@ def preprocess_text(textlist, correction_counter=None):
     # to original chunk
     chunk_delimiter = 'chunkdelimiter'
     processed_chunks = [[] for _ in textlist]
-    # clean spacing, normalize case, strip puncutation
+    # clean spacing, normalize case, strip punctuation
     # (temporarily leave punctuation useful for POS tagging)
     full_text = f' {chunk_delimiter} '.join(textlist).lower()
     punc_stripped = re.sub("[^a-zA-Z\s']+", '', full_text.replace('-', ' '))
@@ -783,7 +783,7 @@ def rbf_sum(obs_coords, pred_coords, width, metric='euclidean'):
     width : scalar
         The Width of the Gaussian kernel.
     metric : str or callable, optional
-        The metric used to compute the pairwise distance between
+        The metric used to compute the pairwise distances between
         coordinates (default: `'euclidean'`, Euclidean distance). May be
         any named metric accepted by `scipy.spatial.distance.cdist` or a
         callable that takes two `array_like` arguments.

### 2023-10-20 paper/main.tex
delete extra space
cleaned up new figures, added new fig 7, recompiled pdf with new versions

@@
 lecture. As shown in Figure~\ref{fig:knowledge-timeseries}A and C, we can apply
-this approach to the questions from each quiz taken throughout the experiment, separately.
-
-From just a few questions per quiz (see~\nameref{subsec:traces}), we obtain a
+this approach separately for the questions from each quiz participants took
+throughout the experiment. From just a few questions per quiz (see~\nameref{subsec:traces}), we obtain a
 high-resolution snapshot (at the time each quiz was taken) of what the
@@
     \centering
-    \includegraphics[width=\textwidth]{figs/held-out-question-analysis}
+    \includegraphics[width=0.7\textwidth]{figs/predict-knowledge-questions}
 
@@
 embedding model.
+
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=\textwidth]{figs/knowledge-smoothness}
+
+    \caption{\textbf{Caption title.} Caption content.}
+
+    \label{fig:smoothness}
+\end{figure}
 

### 2023-10-22 paper/supplement.tex
JRM final pass through
fixed non-LaTeX quotes in supp table 1
add new supplementary table with question/lecture matched text

@@
 \renewcommand*{\arraystretch}{1.4}
-\begin{longtable}{r|p{0.375in}|p{1.275in}|p{0.75in}|p{0.75in}|p{0.75in}|p{0.75in}}
-
+\begin{longtable}{|r|p{0.375in}|p{1.275in}|p{0.75in}|p{0.75in}|p{0.75in}|p{0.75in}|}
+\hline
     \textbf{ID} & \textbf{Question set} &                                                                                                                                                                                                                                                                         \textbf{Question} &                                                                                                                                     \textbf{Correct response} &                                                                                                     \textbf{Alternative 1} &                                                                                                                          \textbf{Alternative 2} &                                                                                                                                 \textbf{Alternative 3} \\\hline
@@
 &                                                                                                                          Less than 1\% &                                                                                                   10\% &                                                                                                                        50\% &                                                                                                                     More than 90\% \\\hline
-    38    &      GPK &                                                                                                                                                                              In the famous equation attributed to Albert Einstein, E = mc\textasciicircum 2, what does the letter "m" represent?
+    38    &      GPK &                                                                                                                                                                              In the famous equation attributed to Albert Einstein, E = mc\textasciicircum 2, what does the letter ``m'' represent?
 &                                                                                                                                  Mass &                                                                                              Momentum &                                                                                                          Moment of inertia &                                                                                                                             Moles \\\hline
     39    &      GPK &                                                                                                                                                                                                If I were to heat up an inflated balloon, which of the the following would occur?
-&                                                                                                              The balloon would expand &                                                                              The balloon would shrink &                                                                                          None of these answers are correct &                                        The balloon could expand or shrink depending on whether it's filled with air or helium gas \\
+&                                                                                                              The balloon would expand &                                                                              The balloon would shrink &                                                                                          None of these answers are correct &                                        The balloon could expand or shrink depending on whether it's filled with air or helium gas \\\hline
 
@@
     \begin{tiny}
-    \begin{tabular}{r|l|l|l|l|l|l|l|l|l|l}
+    \begin{tabular}{|r|l|l|l|l|l|l|l|l|l|l|}
+    \hline
     \textbf{Topic} & \textbf{1} & \textbf{2} &      \textbf{3} &  \textbf{4} & \textbf{5} & \textbf{6} &    \textbf{7} &  \textbf{8} & \textbf{9} &     \textbf{10} \\\hline
@@
 
-    \caption{\textbf{Topics.} We fit a topic model with (up to) $k = 15$ topics to sliding 
-    windows parsed from the two course video transcripts (see~\topicModelMethods),
-    and identified 14 topics with non-zero weights. The table displays the 10 
-    top-weighted words (columns) from each of the topics (rows) discovered by the 
-    model. The weights of these words are shown in Supplementary Figure~\ref{fig:topic-word-distributions}.}
+    \caption{\textbf{Topics.} We fit a topic model with (up to) $k = 15$ topics
+    to sliding windows parsed from the two course video transcripts
+    (see~\topicModelMethods), and identified 14 topics with non-zero weights.
+    The table displays the 10 top-weighted words (columns) from each of the
+    topics (rows) discovered by the model. The weights of these words are shown
+    in Supplementary Figure~\ref{fig:topic-word-distributions}.}
+
     \label{tab:topics}
@@
 \newpage
+
+\begin{tiny}
+    \renewcommand*{\arraystretch}{1.4}
+    \begin{longtable}{|r|p{0.375in}|p{1.275in}|p{3.5in}|}
+        \hline
+        \textbf{ID} & \textbf{Question set} & \textbf{Question} & \textbf{Matched lecture transcript text} \\\hline
+        1  &          FFF &                                                                                                                                                                                   Why is the gravitational attraction between you and your computer too small for you to notice?
+&                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                              \textbf{[00:00.03--01:33.509]} what I want to do in this video is give a very high-level overview of the four fundamental forces four fundamental forces of the universe and I'm going to start with gravity I'm going to start with gravity and it might surprise some of you that gravity is actually the weakest of the four fundamental forces that's surprising because you say wow that's what keeps us glued not glued but it keeps us from jumping off the planet it's what keeps the moon in orbit around the earth the earth in orbit around the Sun the Sun in orbit around the the center of the Milky Way galaxy so it's it's a little bit surprising that it's actually the weakest of the forces and and that starts to make sense when you actually think about things on maybe more of a human scale or a molecular scale or even an atomic scale even on a human scale your computer monitor and you have some type of gravitational attraction but you don't notice it or your cell phone and your wallet there's gravitational attraction but you don't see them being drawn to each other the way you might see two magnets drawn to each other or repelled from each other and if you've got even a smaller scale you'll see that it matters even less we never even talk about gravity and chemistry although the gravity is there but at those scales the other forces really really really start to dominate so gravity's are weakest so if we move up a little bit from that we get and this is maybe the the hardest force for us to visualize or at least the hardest the least intuitive force for me is actually the weak force the weak sometimes called the weak interaction...
+\\\hline
+2  &          FFF &                                                                                                                                                                                                                    Which of the following is an example of the Weak Interaction?
+&                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                              \textbf{[01:22.439--03:05.1]} ...this is maybe the the hardest force for us to visualize or at least the hardest the least intuitive force for me is actually the weak force the weak sometimes called the weak interaction and it's what's responsible for radioactive decay in particular beta minus and beta plus decay and just to give you an example of the actual weak interaction if I had some cesium 137 137 means it has 137 nucleons a nucleon is either a proton or a neutron you add up the protons and neutrons of cesium you get 137 and it is cesium because it has exactly 55 protons now the weak interaction is what's responsible for one of the neutrons essentially one of its corks flipping and turning into a proton and I'm not going to go into detail of what a cork is and all of that and the math can get pretty hairy but I just want to give you an example of what the weak interaction does so if one of these one of these neutrons turns into a proton then we're going to have one extra proton but we have the same number of nucleons instead of a extra Neutron here you now have an extra proton here and so now this is a different atom it is now barium and in that flipping it will actually emit it'll actually emit an electron and an anti-electron neutrino and I'm not going to go into the details of what an anti-electron neutrino is these are fundamental particles but this is just what that weak interaction is it's not something that's completely obvious to us it's not kind of this traditional things pulling or pushing away from each other like we would like we associate...
+\\\hline
+3  &          FFF &                                                                                                                                                                                                            Roughly how many times stronger is the Weak Interaction than gravity?
+&                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  \textbf{[02:52.38--04:43.73]} ...anti-electron neutrino is these are fundamental particles but this is just what that weak interaction is it's not something that's completely obvious to us it's not kind of this traditional things pulling or pushing away from each other like we would like we associate with the other the other forces now the next strongest force and just to give a sense of how weak gravity is even relative to the weak interaction the weak interaction is 10 to the 25th times the strength of gravity times the strength of gravity and you might anything if this is so strong how come this doesn't operate on planets or us relative to the earth or the reason you know why doesn't this apply to intergalactic distances the way gravity does and the reason is the weak interaction really applies to very small distances very very small distances so it can be much stronger than gravity but only over very very and it really only applies on the sub atomic scale you go anything beyond that it kind of disappears as an actual force as an actual interaction now the next the next force up the hierarchy which is one that we are more familiar with it is something it's what actually dominates most of the chemistry that we deal with and electromagnetism that we deal with and that's the electro magnetic force we write it in magenta electro magnetic magnetic force and just to give a sense this is this is 10 to the 36 times the strength of gravity 10 to 36 times the strength of gravity so it kind of puts the weak force in its place it's 10 to the 12 times stronger than the weak force so these are huge numbers that we're talking about either this...
+\\\hline
+4  &          FFF &                                                                                                                                                                              Why don't you and your computer experience any attraction or repulsion due to the Weak Interaction?
+&                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                    \textbf{[00:00.03--02:42.9]} what I want to do in this video is give a very high-level overview of the four fundamental forces four fundamental forces of the universe and I'm going to start with gravity I'm going to start with gravity and it might surprise some of you that gravity is actually the weakest of the four fundamental forces that's surprising because you say wow that's what keeps us glued not glued but it keeps us from jumping off the planet it's what keeps the moon in orbit around the earth the earth in orbit around the Sun the Sun in orbit around the the center of the Milky Way galaxy so it's it's a little bit surprising that it's actually the weakest of the forces and and that starts to make sense when you actually think about things on maybe more of a human scale or a molecular scale or even an atomic scale even on a human scale your computer monitor and you have some type of gravitational attraction but you don't notice it or your cell phone and your wallet there's gravitational attraction but you don't see them being drawn to each other the way you might see two magnets drawn to each other or repelled from each other and if you've got even a smaller scale you'll see that it matters even less we never even talk about gravity and chemistry although the gravity is there but at those scales the other forces really really really start to dominate so gravity's are weakest so if we move up a little bit from that we get and this is maybe the the hardest force for us to visualize or at least the hardest the least intuitive force for me is actually the weak force the weak sometimes called the weak interaction and it's what's responsible for radioactive decay in particular beta minus and beta plus decay and just to give you an example of the actual weak interaction if I had some cesium 137 137 means it has 137 nucleons a nucleon is either a proton or a neutron you add up the protons and neutrons of cesium you get 137 and it is cesium because it has exactly 55 protons now the weak interaction is what's responsible for one of the neutrons essentially one of its corks flipping and turning into a proton and I'm not going to go into detail of what a cork is and all of that and the math can get pretty hairy but I just want to give you an example of what the weak interaction does so if one of these one of these neutrons turns into a proton then we're going to have one extra proton but we have the same number of nucleons instead of a extra Neutron here you now have an extra proton here and so now this is a different atom it is now barium and in that flipping it will actually emit it'll actually emit an electron and an...
+\\\hline
+5  &          FFF &                                                                                                                                                                                            Which of the following is a difference between gravity and the electromagnetic force?
+&                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  \textbf{[04:34.28--05:52.61]} ...times the strength of gravity 10 to 36 times the strength of gravity so it kind of puts the weak force in its place it's 10 to the 12 times stronger than the weak force so these are huge numbers that we're talking about either this relative that or even this relative to gravity and so you might be saying well you know the electromagnetic force that's unbelievably strong why doesn't that apply over over over these these kind of macro scales like gravity let me write there macro scales macro scales why doesn't it apply to macro scales and actually there's nothing about the electromagnetic force why it can't it or it actually does apply over large distances the reality though is you don't have these huge concentrations of either electric Ullom charges or magnetism the way you do mass so the mass that you have such huge concentrations it can operate over huge huge distances even though it's way way way weaker than the electromagnetic force the electromagnetic force what happens is because it's both attractive and repulsive it tends to kind of sort itself out so you don't have these huge huge huge concentrations of charge now the other thing you might be wondering about is you know why is it called the electromagnetic force in our everyday life there's things like there's things like the Coulomb force that or the electrostatic force which we're familiar...
+\\\hline
+6  &          FFF &                                                                                                                                                                                                  Electricity and magnetism can be shown to be two cases of the same force if we: &                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                          \textbf{[04:34.28--05:52.61]} ...times the strength of gravity 10 to 36 times the strength of gravity so it kind of puts the weak force in its place it's 10 to the 12 times stronger than the weak force so these are huge numbers that we're talking about either this relative that or even this relative to gravity and so you might be saying well you know the electromagnetic force that's unbelievably strong why doesn't that apply over over over these these kind of macro scales like gravity let me write there macro scales macro scales why doesn't it apply to macro scales and actually there's nothing about the electromagnetic force why it can't it or it actually does apply over large distances the reality though is you don't have these huge concentrations of either electric Ullom charges or magnetism the way you do mass so the mass that you have such huge concentrations it can operate over huge huge distances even though it's way way way weaker than the electromagnetic force the electromagnetic force what happens is because it's both attractive and repulsive it tends to kind of sort itself out so you don't have these huge huge huge concentrations of charge now the other thing you might be wondering about is you know why is it called the electromagnetic force in our everyday life there's things like there's things like the Coulomb force that or the electrostatic force which we're familiar\newline\textbf{[06:37.31--07:28.1]} ...that the cool force the electrostatic force and the magnetic force are actually the same thing viewed in different frames of references so I won't go into a lot of detail but just keep that in the back of your mind that they are connected in a future video I'll go more into the intuition of how they are connected and it deals with when what it's more apparent when they're moving when the charges are moving at relativistic frames and you have well I will go to a lot of detail there but just keep in mind that they really are the same force just viewed from different frames of reference now the strongest of the force is probably the best name of them all and that's the strong force that is the strong force the strong force and although you probably haven't seen this yet in our in chemistry classes it actually applies very strongly in...
+\\\hline
+7  &          FFF &                                                                                                                                  Which of the following are the primary two fundamental forces acting in opposition between the positively-charged protons in an atom's nucleus?
+&                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                              \textbf{[00:00.03--01:33.509]} what I want to do in this video is give a very high-level overview of the four fundamental forces four fundamental forces of the universe and I'm going to start with gravity I'm going to start with gravity and it might surprise some of you that gravity is actually the weakest of the four fundamental forces that's surprising because you say wow that's what keeps us glued not glued but it keeps us from jumping off the planet it's what keeps the moon in orbit around the earth the earth in orbit around the Sun the Sun in orbit around the the center of the Milky Way galaxy so it's it's a little bit surprising that it's actually the weakest of the forces and and that starts to make sense when you actually think about things on maybe more of a human scale or a molecular scale or even an atomic scale even on a human scale your computer monitor and you have some type of gravitational attraction but you don't notice it or your cell phone and your wallet there's gravitational attraction but you don't see them being drawn to each other the way you might see two magnets drawn to each other or repelled from each other and if you've got even a smaller scale you'll see that it matters even less we never even talk about gravity and chemistry although the gravity is there but at those scales the other forces really really really start to dominate so gravity's are weakest so if we move up a little bit from that we get and this is maybe the the hardest force for us to visualize or at least the hardest the least intuitive force for me is actually the weak force the weak sometimes called the weak interaction\newline\textbf{[07:10.13--08:35.24]} ...reference now the strongest of the force is probably the best name of them all and that's the strong force that is the strong force the strong force and although you probably haven't seen this yet in our in chemistry classes it actually applies very strongly in chemistry because from the get-go when you first learn when you first learn about atoms let me draw a helium atom a helium atom has two protons and it's nucleus two protons in its nucleus and it has two neutrons and then it also has two electrons circulating around so it has an electron and I can draw the electrons is much smaller than well I won't I won't try to do anything in relative size but it has two electrons floating around and one question that may or may not have jumped into your mind when you first saw this model of an atom is like well I see why the electrons are attracted to the nucleus it has a negative Coulomb charge the nucleus has a net positive Coulomb charge but what's not so obvious and that what tends not to sometimes be explained in chemistry class is these two positive charges are sitting right next to each other if the electromagnetic force was the only force in play if the Coulomb force was the only thing happening these guys would just run away from each other they would repel each other and so the only reason why they're able to stick to each other is that there's an even stronger force than the electromagnetic force operating at these very very very small distances...
+\\\hline
+8  &          FFF &                                                                                                                                                                     Why does the universe have a very uneven distribution of mass but a relatively equal distribution of charge?
+&                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                             \textbf{[08:24.11--10:26.27]} ...just run away from each other they would repel each other and so the only reason why they're able to stick to each other is that there's an even stronger force than the electromagnetic force operating at these very very very small distances so if you get two of these protons close enough together and the strong force only applies over very very very small distances subatomic I should even say sub nucleic distances then the strong interaction comes into play so then you have the strong interaction actually keeping these charges together and once again just to keep it in in in mind relative to gravity it is 10 to the 38th 10 38 times the strength times the strength of gravity or it's about a hundred times stronger than the electromagnetic force so once again the reason why you don't see the strong force which is the strongest of all of the forces or the weak interaction applying over huge scales is that they really only they only their strength dies off super super fast even when you start going to large radius nucleuses of atoms they strength starts to die off especially for the strong force the reason why you don't see the electromagnetic force operating over large distances even though in theory it can like gravity is that you don't see the type of charge concentrations the way you see mass concentrations in the universe because the charge concentrations tend to sort them out they start to equalize if I have if I have some if I have some positive a huge positive charge there and a huge negative charge there they will attract each other and then become essentially a big lump of neutral charge and once they're a big lump of neutral charge they won't they won't interact with anything else in gravity if you have one mass and another mass and they attract each other then you have another mass that's even better to attracting each other at other masses and so it'll keep attracting things to it so it kind of snowballs the process and that's why gravity can operates on these really really large large objects in our universe in the universe as a whole \\\hline
+9  &          FFF &  In your body, there are a tremendous amount of negatively-charged electrons.
+Your computer also contains a huge number of negatively-charged electrons.
+We know that like charges repel, but you and your computer are not repelled apart.
+Which of the following explains why?
+&  \textbf{[00:00.03--01:33.509]} what I want to do in this video is give a very high-level overview of the four fundamental forces four fundamental forces of the universe and I'm going to start with gravity I'm going to start with gravity and it might surprise some of you that gravity is actually the weakest of the four fundamental forces that's surprising because you say wow that's what keeps us glued not glued but it keeps us from jumping off the planet it's what keeps the moon in orbit around the earth the earth in orbit around the Sun the Sun in orbit around the the center of the Milky Way galaxy so it's it's a little bit surprising that it's actually the weakest of the forces and and that starts to make sense when you actually think about things on maybe more of a human scale or a molecular scale or even an atomic scale even on a human scale your computer monitor and you have some type of gravitational attraction but you don't notice it or your cell phone and your wallet there's gravitational attraction but you don't see them being drawn to each other the way you might see two magnets drawn to each other or repelled from each other and if you've got even a smaller scale you'll see that it matters even less we never even talk about gravity and chemistry although the gravity is there but at those scales the other forces really really really start to dominate so gravity's are weakest so if we move up a little bit from that we get and this is maybe the the hardest force for us to visualize or at least the hardest the least intuitive force for me is actually the weak force the weak sometimes called the weak interaction\newline\textbf{[05:32.6--08:33.14]} ...force the electromagnetic force what happens is because it's both attractive and repulsive it tends to kind of sort itself out so you don't have these huge huge huge concentrations of charge now the other thing you might be wondering about is you know why is it called the electromagnetic force in our everyday life there's things like there's things like the Coulomb force that or the electrostatic force which we're familiar with positive charges or like charges want to repel if both of these were negative the same thing would be happening and different charges like to attract we've seen this multiple times this is the Coulomb force or the electrostatic force electro static and then on the other side of the word yes you have the magnetic part and magnets you know you have you've played with magnets on your fridge they what's what you know if they're the same side of the magnet they're going to repel each other if they're the opposite sides opposite poles they're going to attract each other so why is it called one force and it's called one force and once again I'm not going to go into detail here it's called one force because it turns out that the cool force the electrostatic force and the magnetic force are actually the same thing viewed in different frames of references so I won't go into a lot of detail but just keep that in the back of your mind that they are connected in a future video I'll go more into the intuition of how they are connected and it deals with when what it's more apparent when they're moving when the charges are moving at relativistic frames and you have well I will go to a lot of detail there but just keep in mind that they really are the same force just viewed from different frames of reference now the strongest of the force is probably the best name of them all and that's the strong force that is the strong force the strong force and although you probably haven't seen this yet in our in chemistry classes it actually applies very strongly in chemistry because from the get-go when you first learn when you first learn about atoms let me draw a helium atom a helium atom has two protons and it's nucleus two protons in its nucleus and it has two neutrons and then it also has two electrons circulating around so it has an electron and I can draw the electrons is much smaller than well I won't I won't try to do anything in relative size but it has two electrons floating around and one question that may or may not have jumped into your mind when you first saw this model of an atom is like well I see why the electrons are attracted to the nucleus it has a negative Coulomb charge the nucleus has a net positive Coulomb charge but what's not so obvious and that what tends not to sometimes be explained in chemistry class is these two positive charges are sitting right next to each other if the electromagnetic force was the only force in play if the Coulomb force was the only thing happening these guys would just run away from each other they would repel each other and so the only reason why they're able to stick to each other is that there's an even stronger force than the electromagnetic force operating...
+\\\hline
+10 &          FFF &                                                                                                                                                                                        Which of the following is a similarity between the Weak Interaction and the Strong Force?
+&                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  \textbf{[02:52.38--04:43.73]} ...anti-electron neutrino is these are fundamental particles but this is just what that weak interaction is it's not something that's completely obvious to us it's not kind of this traditional things pulling or pushing away from each other like we would like we associate with the other the other forces now the next strongest force and just to give a sense of how weak gravity is even relative to the weak interaction the weak interaction is 10 to the 25th times the strength of gravity times the strength of gravity and you might anything if this is so strong how come this doesn't operate on planets or us relative to the earth or the reason you know why doesn't this apply to intergalactic distances the way gravity does and the reason is the weak interaction really applies to very small distances very very small distances so it can be much stronger than gravity but only over very very and it really only applies on the sub atomic scale you go anything beyond that it kind of disappears as an actual force as an actual interaction now the next the next force up the hierarchy which is one that we are more familiar with it is something it's what actually dominates most of the chemistry that we deal with and electromagnetism that we deal with and that's the electro magnetic force we write it in magenta electro magnetic magnetic force and just to give a sense this is this is 10 to the 36 times the strength of gravity 10 to 36 times the strength of gravity so it kind of puts the weak force in its place it's 10 to the 12 times stronger than the weak force so these are huge numbers that we're talking about either this...
+\\\hline
+11 &          FFF &                                                                                                                                                                                                                          Which force is stronger than the Electromagnetic Force?
+&                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  \textbf{[04:34.28--05:52.61]} ...times the strength of gravity 10 to 36 times the strength of gravity so it kind of puts the weak force in its place it's 10 to the 12 times stronger than the weak force so these are huge numbers that we're talking about either this relative that or even this relative to gravity and so you might be saying well you know the electromagnetic force that's unbelievably strong why doesn't that apply over over over these these kind of macro scales like gravity let me write there macro scales macro scales why doesn't it apply to macro scales and actually there's nothing about the electromagnetic force why it can't it or it actually does apply over large distances the reality though is you don't have these huge concentrations of either electric Ullom charges or magnetism the way you do mass so the mass that you have such huge concentrations it can operate over huge huge distances even though it's way way way weaker than the electromagnetic force the electromagnetic force what happens is because it's both attractive and repulsive it tends to kind of sort itself out so you don't have these huge huge huge concentrations of charge now the other thing you might be wondering about is you know why is it called the electromagnetic force in our everyday life there's things like there's things like the Coulomb force that or the electrostatic force which we're familiar...
+\\\hline
+12 &          FFF &                                                                                                                                                                                                                Roughly how many times stronger is the Strong Force than gravity?
+&                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  \textbf{[02:52.38--04:43.73]} ...anti-electron neutrino is these are fundamental particles but this is just what that weak interaction is it's not something that's completely obvious to us it's not kind of this traditional things pulling or pushing away from each other like we would like we associate with the other the other forces now the next strongest force and just to give a sense of how weak gravity is even relative to the weak interaction the weak interaction is 10 to the 25th times the strength of gravity times the strength of gravity and you might anything if this is so strong how come this doesn't operate on planets or us relative to the earth or the reason you know why doesn't this apply to intergalactic distances the way gravity does and the reason is the weak interaction really applies to very small distances very very small distances so it can be much stronger than gravity but only over very very and it really only applies on the sub atomic scale you go anything beyond that it kind of disappears as an actual force as an actual interaction now the next the next force up the hierarchy which is one that we are more familiar with it is something it's what actually dominates most of the chemistry that we deal with and electromagnetism that we deal with and that's the electro magnetic force we write it in magenta electro magnetic magnetic force and just to give a sense this is this is 10 to the 36 times the strength of gravity 10 to 36 times the strength of gravity so it kind of puts the weak force in its place it's 10 to the 12 times stronger than the weak force so these are huge numbers that we're talking about either this...
+\\\hline
+13 &          FFF &                                                                                                                                                      Which of the following would have to be true for the Weak Interaction to cause repulsion or attraction between two objects?
+&                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                 \textbf{[00:00.03--03:02.79]} what I want to do in this video is give a very high-level overview of the four fundamental forces four fundamental forces of the universe and I'm going to start with gravity I'm going to start with gravity and it might surprise some of you that gravity is actually the weakest of the four fundamental forces that's surprising because you say wow that's what keeps us glued not glued but it keeps us from jumping off the planet it's what keeps the moon in orbit around the earth the earth in orbit around the Sun the Sun in orbit around the the center of the Milky Way galaxy so it's it's a little bit surprising that it's actually the weakest of the forces and and that starts to make sense when you actually think about things on maybe more of a human scale or a molecular scale or even an atomic scale even on a human scale your computer monitor and you have some type of gravitational attraction but you don't notice it or your cell phone and your wallet there's gravitational attraction but you don't see them being drawn to each other the way you might see two magnets drawn to each other or repelled from each other and if you've got even a smaller scale you'll see that it matters even less we never even talk about gravity and chemistry although the gravity is there but at those scales the other forces really really really start to dominate so gravity's are weakest so if we move up a little bit from that we get and this is maybe the the hardest force for us to visualize or at least the hardest the least intuitive force for me is actually the weak force the weak sometimes called the weak interaction and it's what's responsible for radioactive decay in particular beta minus and beta plus decay and just to give you an example of the actual weak interaction if I had some cesium 137 137 means it has 137 nucleons a nucleon is either a proton or a neutron you add up the protons and neutrons of cesium you get 137 and it is cesium because it has exactly 55 protons now the weak interaction is what's responsible for one of the neutrons essentially one of its corks flipping and turning into a proton and I'm not going to go into detail of what a cork is and all of that and the math can get pretty hairy but I just want to give you an example of what the weak interaction does so if one of these one of these neutrons turns into a proton then we're going to have one extra proton but we have the same number of nucleons instead of a extra Neutron here you now have an extra proton here and so now this is a different atom it is now barium and in that flipping it will actually emit it'll actually emit an electron and an anti-electron neutrino and I'm not going to go into the details of what an anti-electron neutrino is these are fundamental particles but this is just what that weak interaction is it's not something that's completely obvious to us it's not kind of this traditional things pulling or pushing away from each...
+\\\hline
+14 &          FFF &                                                                                                                                                                                                                                  Which force keeps us from jumping off of Earth?
+&                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                              \textbf{[00:00.03--01:33.509]} what I want to do in this video is give a very high-level overview of the four fundamental forces four fundamental forces of the universe and I'm going to start with gravity I'm going to start with gravity and it might surprise some of you that gravity is actually the weakest of the four fundamental forces that's surprising because you say wow that's what keeps us glued not glued but it keeps us from jumping off the planet it's what keeps the moon in orbit around the earth the earth in orbit around the Sun the Sun in orbit around the the center of the Milky Way galaxy so it's it's a little bit surprising that it's actually the weakest of the forces and and that starts to make sense when you actually think about things on maybe more of a human scale or a molecular scale or even an atomic scale even on a human scale your computer monitor and you have some type of gravitational attraction but you don't notice it or your cell phone and your wallet there's gravitational attraction but you don't see them being drawn to each other the way you might see two magnets drawn to each other or repelled from each other and if you've got even a smaller scale you'll see that it matters even less we never even talk about gravity and chemistry although the gravity is there but at those scales the other forces really really really start to dominate so gravity's are weakest so if we move up a little bit from that we get and this is maybe the the hardest force for us to visualize or at least the hardest the least intuitive force for me is actually the weak force the weak sometimes called the weak interaction...
+\\\hline
+15 &          FFF &                                                                                                                                                                                                                                            What does the Coulomb Force refer to?
+&                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                     \textbf{[05:38.66--06:59.96]} ...itself out so you don't have these huge huge huge concentrations of charge now the other thing you might be wondering about is you know why is it called the electromagnetic force in our everyday life there's things like there's things like the Coulomb force that or the electrostatic force which we're familiar with positive charges or like charges want to repel if both of these were negative the same thing would be happening and different charges like to attract we've seen this multiple times this is the Coulomb force or the electrostatic force electro static and then on the other side of the word yes you have the magnetic part and magnets you know you have you've played with magnets on your fridge they what's what you know if they're the same side of the magnet they're going to repel each other if they're the opposite sides opposite poles they're going to attract each other so why is it called one force and it's called one force and once again I'm not going to go into detail here it's called one force because it turns out that the cool force the electrostatic force and the magnetic force are actually the same thing viewed in different frames of references so I won't go into a lot of detail but just keep that in the back of your mind that they are connected in a future video I'll go more into the intuition of how they are connected and it deals with when what it's more apparent when they're moving when the charges are moving at relativistic...
+\\\hline
+16 &          BoS &                                                                                                                                                                                                      Which of the following describes the effect of gravity on a cloud of atoms?
+&                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                        \textbf{[00:05.67--01:36.71]} ...and I say huge cloud huge both in distance and in mass if you were to combine all of the hydrogen atoms it would just be this really really massive thing so you have this huge cloud well we know that gravity would make the atoms actually attracted to each other instantly we normally don't think about the gravity of atoms but it would slowly affect these atoms and they'd slowly draw close to each other it would slowly condense they'd slowly they slowly move towards the center of mass of all of the atoms they'd slowly move in and so if we fast forward if we fast forward this cloud is going to get denser and denser it's going to get denser and denser and the hydrogen atoms are going to start bumping into each other and rubbing up against each other and interacting with each other and so it's going to get denser and denser and denser and remember was a huge mass of hydrogen atoms so the temperature is going up the temperature is going up and it'll they'll keep condensing they'll just keep condensing and condensing until something really interesting happens so let's imagine that they've gotten really dense here in the center they've gotten really dense here in the center and there's a bunch of hydrogen atoms all over it's really dense I could never draw the actual number of atoms here this is really give you an idea there's a huge amount of inward pressure from gravity from everything that wants to get to that center of mass of our entire cloud the temperature here the temperature here is approaching 10 million Kelvin and at that point...
+\\\hline
+17 &          BoS &                                                                                                                                                                                                               Which of the following occurs as a cloud of atoms gets more dense?
+&                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                             \textbf{[00:05.67--01:36.71]} ...and I say huge cloud huge both in distance and in mass if you were to combine all of the hydrogen atoms it would just be this really really massive thing so you have this huge cloud well we know that gravity would make the atoms actually attracted to each other instantly we normally don't think about the gravity of atoms but it would slowly affect these atoms and they'd slowly draw close to each other it would slowly condense they'd slowly they slowly move towards the center of mass of all of the atoms they'd slowly move in and so if we fast forward if we fast forward this cloud is going to get denser and denser it's going to get denser and denser and the hydrogen atoms are going to start bumping into each other and rubbing up against each other and interacting with each other and so it's going to get denser and denser and denser and remember was a huge mass of hydrogen atoms so the temperature is going up the temperature is going up and it'll they'll keep condensing they'll just keep condensing and condensing until something really interesting happens so let's imagine that they've gotten really dense here in the center they've gotten really dense here in the center and there's a bunch of hydrogen atoms all over it's really dense I could never draw the actual number of atoms here this is really give you an idea there's a huge amount of inward pressure from gravity from everything that wants to get to that center of mass of our entire cloud the temperature here the temperature here is approaching 10 million Kelvin and at that point\newline\textbf{[06:50.68--07:52.81]} ...there's there's questions of well what if what if there just wasn't enough mass to get to this level over here and there actually are things that never get to that quite that threshold to fuse all the way into helium there are a few things that don't quite make the threshold of stars that only fuse to this level so they are generating some of their eat or there are even smaller objects that just get to the point there's a huge temperature and pressure but fusion is not actually occurring inside of the core and something like Jupiter would be an example and you can go several several masses above Jupiter where you get something like that so you have to reach a certain threshold or the mass where the pressure and the temperature due to the heavy mass gets so large that you start this fusion at but the smaller you have above that threshold this the slower the fusion will occur but if you're supermassive the fusion will occur really really fast so that's a general idea of just how stars get formed and why they don't collapse on themselves and why they are these kind of little balls of fusion reactions existing in the universe and the next few videos we'll talk about what happens once that hydrogen fuel and the cure in the core starts to run out...
+\\\hline
+18 &          BoS &                                                                                                                                                                   Which temperature does a cloud of hydrogen atoms approach as it gets denser in the process of becoming a star?
+&                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                            \textbf{[00:05.67--01:47.82]} ...and I say huge cloud huge both in distance and in mass if you were to combine all of the hydrogen atoms it would just be this really really massive thing so you have this huge cloud well we know that gravity would make the atoms actually attracted to each other instantly we normally don't think about the gravity of atoms but it would slowly affect these atoms and they'd slowly draw close to each other it would slowly condense they'd slowly they slowly move towards the center of mass of all of the atoms they'd slowly move in and so if we fast forward if we fast forward this cloud is going to get denser and denser it's going to get denser and denser and the hydrogen atoms are going to start bumping into each other and rubbing up against each other and interacting with each other and so it's going to get denser and denser and denser and remember was a huge mass of hydrogen atoms so the temperature is going up the temperature is going up and it'll they'll keep condensing they'll just keep condensing and condensing until something really interesting happens so let's imagine that they've gotten really dense here in the center they've gotten really dense here in the center and there's a bunch of hydrogen atoms all over it's really dense I could never draw the actual number of atoms here this is really give you an idea there's a huge amount of inward pressure from gravity from everything that wants to get to that center of mass of our entire cloud the temperature here the temperature here is approaching 10 million Kelvin and at that point something neat happens it to kind of realize the neat thing that's happening let's remember what a hydrogen atom looks like a hydrogen and even more I'm just going to focus on the hydrogen\newline\textbf{[05:50.32--07:00.25]} ...helium and by definition helium has two protons and two neutrons so it has or we're talking about helium four in particular that isotope of helium it has an atomic mass of four and the whole this process releases a ton of energy because the atomic mass of the helium that gets produced is slightly lower than four of its of the atomic four times the atomic mass of each of the Constituent hydrogen's so all of this energy all of this energy from the fusion but it needs super high pressure super high temperatures to happen keeps keeps the star from collapsing and once the star is in in this stage once it is once it is using hydrogen it is fusing hydrogen in its core where the pressure and the temperatures of most to form helium it is now in its main sequence this is now a main sequence star main main sequence star and that's actually where the Sun is right now now there's there's questions of well what if what if there just wasn't enough mass to get to this level over here and there actually are things that never get to that quite that threshold to fuse all the way into helium there are a few...
+\\\hline
+19 &          BoS &                                                                                                                                                                                                                           Which of the following can overcome the Coulomb Force?
+&                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                   \textbf{[02:24.67--03:53.08]} ...learned about the four force is that if they did get close enough to each other that if they did get if somehow they're under huge temperatures and huge pressures you were able to get these two protons close enough to each other then all of a sudden the strong force will overtake it's much stronger than the Coulomb force and that these two hydrogen's will actually these this these nucleuses would actually fuse or that nuclei well anyway they would actually fuse together and so that is what actually happens once this gets hot and dense enough you now have enough pressure enough temperature to overcome the Coulomb force and bring these protons close enough to each other for fusion to occur for fusion fusion ignition ignition and the reason why is and I want to be very careful it's not ignition it's not combustion in the traditional sense it's not like you're burning a carbon molecule with out in the presence of oxygen it's not combustion it's ignition and the reason why it's called ignition is because when two of these protons or two of the nucleus is fuse the resulting the resulting nucleus has a slightly smaller mass and so in the first stage of this you actually have you actually have two protons two protons under enough pressure obviously this would not happen with just the Coulomb forces at with enough pressure to get close enough and then the strong interaction actually actually keeps them together one of these guys degrades in a neutron degrades into a neutron and the...
+\\\hline
+20 &          BoS &                                                                                                                                                                                                   Which of the following prevents a star from collapsing as a result of gravity?
+&                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                        \textbf{[03:36.34--05:04.75]} ...you actually have you actually have two protons two protons under enough pressure obviously this would not happen with just the Coulomb forces at with enough pressure to get close enough and then the strong interaction actually actually keeps them together one of these guys degrades in a neutron degrades into a neutron and the resulting mass of the combined protons is lower than the mass of each of the original by a little bit but that a little bit of mass results in a lot of energy plus plus energy and this energy is why we call it ignition and so what this energy does is it provides a little bit of outward pressure so that this thing doesn't keep keep collapsing so once you get pressure enough the fusion occurs and then that energy provides outward pressure to what is now a star what is now a star so now we are at where we actually have the ignition at the center we have and we still have all of the other molecules trying to get in providing the pressure for this fusion ignition now what is the hydrogen being fused into well on the first step of the first step of the reaction and I'm just kind of doing the most basic type of fusion that exhibit ours the hydrogen gets fused into deuterium deuterium of trouble spelling which is another way of calling heavy hydrogen this is still hydrogen because it has one proton and one Neutron now it is not...
+\\\hline
+21 &          BoS &                                                                                                                                                                                                                           How are supermassive stars different from other stars?
+&                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                        \textbf{[06:48.19--07:52.81]} ...actually where the Sun is right now now there's there's questions of well what if what if there just wasn't enough mass to get to this level over here and there actually are things that never get to that quite that threshold to fuse all the way into helium there are a few things that don't quite make the threshold of stars that only fuse to this level so they are generating some of their eat or there are even smaller objects that just get to the point there's a huge temperature and pressure but fusion is not actually occurring inside of the core and something like Jupiter would be an example and you can go several several masses above Jupiter where you get something like that so you have to reach a certain threshold or the mass where the pressure and the temperature due to the heavy mass gets so large that you start this fusion at but the smaller you have above that threshold this the slower the fusion will occur but if you're supermassive the fusion will occur really really fast so that's a general idea of just how stars get formed and why they don't collapse on themselves and why they are these kind of little balls of fusion reactions existing in the universe and the next few videos we'll talk about what happens once that hydrogen fuel and the cure in the core starts to run out...
+\\\hline
+22 &          BoS &                                                                                                                                                                                               Which of the following is the FIRST product of two hydrogen atoms fusing together?
+&                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                \textbf{[00:05.67--01:36.71]} ...and I say huge cloud huge both in distance and in mass if you were to combine all of the hydrogen atoms it would just be this really really massive thing so you have this huge cloud well we know that gravity would make the atoms actually attracted to each other instantly we normally don't think about the gravity of atoms but it would slowly affect these atoms and they'd slowly draw close to each other it would slowly condense they'd slowly they slowly move towards the center of mass of all of the atoms they'd slowly move in and so if we fast forward if we fast forward this cloud is going to get denser and denser it's going to get denser and denser and the hydrogen atoms are going to start bumping into each other and rubbing up against each other and interacting with each other and so it's going to get denser and denser and denser and remember was a huge mass of hydrogen atoms so the temperature is going up the temperature is going up and it'll they'll keep condensing they'll just keep condensing and condensing until something really interesting happens so let's imagine that they've gotten really dense here in the center they've gotten really dense here in the center and there's a bunch of hydrogen atoms all over it's really dense I could never draw the actual number of atoms here this is really give you an idea there's a huge amount of inward pressure from gravity from everything that wants to get to that center of mass of our entire cloud the temperature here the temperature here is approaching 10 million Kelvin and at that point\newline\textbf{[02:24.67--03:53.08]} ...learned about the four force is that if they did get close enough to each other that if they did get if somehow they're under huge temperatures and huge pressures you were able to get these two protons close enough to each other then all of a sudden the strong force will overtake it's much stronger than the Coulomb force and that these two hydrogen's will actually these this these nucleuses would actually fuse or that nuclei well anyway they would actually fuse together and so that is what actually happens once this gets hot and dense enough you now have enough pressure enough temperature to overcome the Coulomb force and bring these protons close enough to each other for fusion to occur for fusion fusion ignition ignition and the reason why is and I want to be very careful it's not ignition it's not combustion in the traditional sense it's not like you're burning a carbon molecule with out in the presence of oxygen it's not combustion it's ignition and the reason why it's called ignition is because when two of these protons or two of the nucleus is fuse the resulting the resulting nucleus has a slightly smaller mass and so in the first stage of this you actually have you actually have two protons two protons under enough pressure obviously this would not happen with just the Coulomb forces at with enough pressure to get close enough and then the strong interaction actually actually keeps them together one of these guys degrades in a neutron degrades into a neutron and the...
+\\\hline
+23 &          BoS &                                                                                                                                                                                       Once hydrogen atoms get close enough together, which of the following keeps them together?
+&                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                \textbf{[00:05.67--01:36.71]} ...and I say huge cloud huge both in distance and in mass if you were to combine all of the hydrogen atoms it would just be this really really massive thing so you have this huge cloud well we know that gravity would make the atoms actually attracted to each other instantly we normally don't think about the gravity of atoms but it would slowly affect these atoms and they'd slowly draw close to each other it would slowly condense they'd slowly they slowly move towards the center of mass of all of the atoms they'd slowly move in and so if we fast forward if we fast forward this cloud is going to get denser and denser it's going to get denser and denser and the hydrogen atoms are going to start bumping into each other and rubbing up against each other and interacting with each other and so it's going to get denser and denser and denser and remember was a huge mass of hydrogen atoms so the temperature is going up the temperature is going up and it'll they'll keep condensing they'll just keep condensing and condensing until something really interesting happens so let's imagine that they've gotten really dense here in the center they've gotten really dense here in the center and there's a bunch of hydrogen atoms all over it's really dense I could never draw the actual number of atoms here this is really give you an idea there's a huge amount of inward pressure from gravity from everything that wants to get to that center of mass of our entire cloud the temperature here the temperature here is approaching 10 million Kelvin and at that point\newline\textbf{[02:24.67--03:53.08]} ...learned about the four force is that if they did get close enough to each other that if they did get if somehow they're under huge temperatures and huge pressures you were able to get these two protons close enough to each other then all of a sudden the strong force will overtake it's much stronger than the Coulomb force and that these two hydrogen's will actually these this these nucleuses would actually fuse or that nuclei well anyway they would actually fuse together and so that is what actually happens once this gets hot and dense enough you now have enough pressure enough temperature to overcome the Coulomb force and bring these protons close enough to each other for fusion to occur for fusion fusion ignition ignition and the reason why is and I want to be very careful it's not ignition it's not combustion in the traditional sense it's not like you're burning a carbon molecule with out in the presence of oxygen it's not combustion it's ignition and the reason why it's called ignition is because when two of these protons or two of the nucleus is fuse the resulting the resulting nucleus has a slightly smaller mass and so in the first stage of this you actually have you actually have two protons two protons under enough pressure obviously this would not happen with just the Coulomb forces at with enough pressure to get close enough and then the strong interaction actually actually keeps them together one of these guys degrades in a neutron degrades into a neutron and the...
+\\\hline
+24 &          BoS &                                                                                                                                                    When two nuclei fuse together, how does the mass of the combined nucleus compare to the mass of each of the original nucleus?
+&                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                              \textbf{[02:26.05--04:49.15]} ...they did get close enough to each other that if they did get if somehow they're under huge temperatures and huge pressures you were able to get these two protons close enough to each other then all of a sudden the strong force will overtake it's much stronger than the Coulomb force and that these two hydrogen's will actually these this these nucleuses would actually fuse or that nuclei well anyway they would actually fuse together and so that is what actually happens once this gets hot and dense enough you now have enough pressure enough temperature to overcome the Coulomb force and bring these protons close enough to each other for fusion to occur for fusion fusion ignition ignition and the reason why is and I want to be very careful it's not ignition it's not combustion in the traditional sense it's not like you're burning a carbon molecule with out in the presence of oxygen it's not combustion it's ignition and the reason why it's called ignition is because when two of these protons or two of the nucleus is fuse the resulting the resulting nucleus has a slightly smaller mass and so in the first stage of this you actually have you actually have two protons two protons under enough pressure obviously this would not happen with just the Coulomb forces at with enough pressure to get close enough and then the strong interaction actually actually keeps them together one of these guys degrades in a neutron degrades into a neutron and the resulting mass of the combined protons is lower than the mass of each of the original by a little bit but that a little bit of mass results in a lot of energy plus plus energy and this energy is why we call it ignition and so what this energy does is it provides a little bit of outward pressure so that this thing doesn't keep keep collapsing so once you get pressure enough the fusion occurs and then that energy provides outward pressure to what is now a star what is now a star so now we are at where we actually have the ignition at the center we have and we still have all of the other molecules trying to get in providing the pressure for this fusion ignition now what is the hydrogen being fused into well on the first step of the first step of the reaction and I'm just kind of doing the...
+\\\hline
+25 &          BoS &                                                                                                                                                                                            If we say that our Sun is a main sequence star, what does that tell us about the Sun?
+&                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                \textbf{[05:47.08--07:01.75]} ...eventually gets fused and I'm not going to the detail of the reaction into helium and by definition helium has two protons and two neutrons so it has or we're talking about helium four in particular that isotope of helium it has an atomic mass of four and the whole this process releases a ton of energy because the atomic mass of the helium that gets produced is slightly lower than four of its of the atomic four times the atomic mass of each of the Constituent hydrogen's so all of this energy all of this energy from the fusion but it needs super high pressure super high temperatures to happen keeps keeps the star from collapsing and once the star is in in this stage once it is once it is using hydrogen it is fusing hydrogen in its core where the pressure and the temperatures of most to form helium it is now in its main sequence this is now a main sequence star main main sequence star and that's actually where the Sun is right now now there's there's questions of well what if what if there just wasn't enough mass to get to this level over here and there actually are things that never get to that quite that threshold to fuse all the way into helium there are a few things that don't quite make the...
+\\\hline
+26 &          BoS &                                                                                                                                                                                                      Which force would cause a massive cloud of hydrogen atoms to move together?
+&                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                        \textbf{[00:05.67--01:36.71]} ...and I say huge cloud huge both in distance and in mass if you were to combine all of the hydrogen atoms it would just be this really really massive thing so you have this huge cloud well we know that gravity would make the atoms actually attracted to each other instantly we normally don't think about the gravity of atoms but it would slowly affect these atoms and they'd slowly draw close to each other it would slowly condense they'd slowly they slowly move towards the center of mass of all of the atoms they'd slowly move in and so if we fast forward if we fast forward this cloud is going to get denser and denser it's going to get denser and denser and the hydrogen atoms are going to start bumping into each other and rubbing up against each other and interacting with each other and so it's going to get denser and denser and denser and remember was a huge mass of hydrogen atoms so the temperature is going up the temperature is going up and it'll they'll keep condensing they'll just keep condensing and condensing until something really interesting happens so let's imagine that they've gotten really dense here in the center they've gotten really dense here in the center and there's a bunch of hydrogen atoms all over it's really dense I could never draw the actual number of atoms here this is really give you an idea there's a huge amount of inward pressure from gravity from everything that wants to get to that center of mass of our entire cloud the temperature here the temperature here is approaching 10 million Kelvin and at that point\newline\textbf{[02:26.05--03:51.37]} ...they did get close enough to each other that if they did get if somehow they're under huge temperatures and huge pressures you were able to get these two protons close enough to each other then all of a sudden the strong force will overtake it's much stronger than the Coulomb force and that these two hydrogen's will actually these this these nucleuses would actually fuse or that nuclei well anyway they would actually fuse together and so that is what actually happens once this gets hot and dense enough you now have enough pressure enough temperature to overcome the Coulomb force and bring these protons close enough to each other for fusion to occur for fusion fusion ignition ignition and the reason why is and I want to be very careful it's not ignition it's not combustion in the traditional sense it's not like you're burning a carbon molecule with out in the presence of oxygen it's not combustion it's ignition and the reason why it's called ignition is because when two of these protons or two of the nucleus is fuse the resulting the resulting nucleus has a slightly smaller mass and so in the first stage of this you actually have you actually have two protons two protons under enough pressure obviously this would not happen with just the Coulomb forces at with enough pressure to get close enough and then the strong interaction actually actually keeps them together one of these guys degrades in a neutron...
+\\\hline
+27 &          BoS &                                                                                                                                                                                                                              Which of the following occurs as density increases?
+&                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                        \textbf{[06:48.19--07:52.81]} ...actually where the Sun is right now now there's there's questions of well what if what if there just wasn't enough mass to get to this level over here and there actually are things that never get to that quite that threshold to fuse all the way into helium there are a few things that don't quite make the threshold of stars that only fuse to this level so they are generating some of their eat or there are even smaller objects that just get to the point there's a huge temperature and pressure but fusion is not actually occurring inside of the core and something like Jupiter would be an example and you can go several several masses above Jupiter where you get something like that so you have to reach a certain threshold or the mass where the pressure and the temperature due to the heavy mass gets so large that you start this fusion at but the smaller you have above that threshold this the slower the fusion will occur but if you're supermassive the fusion will occur really really fast so that's a general idea of just how stars get formed and why they don't collapse on themselves and why they are these kind of little balls of fusion reactions existing in the universe and the next few videos we'll talk about what happens once that hydrogen fuel and the cure in the core starts to run out...
+\\\hline
+28 &          BoS &                                                                                                                                                                                                                          Which of the following is a product of Hydrogen fusion?
+&                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                        \textbf{[06:48.19--07:52.81]} ...actually where the Sun is right now now there's there's questions of well what if what if there just wasn't enough mass to get to this level over here and there actually are things that never get to that quite that threshold to fuse all the way into helium there are a few things that don't quite make the threshold of stars that only fuse to this level so they are generating some of their eat or there are even smaller objects that just get to the point there's a huge temperature and pressure but fusion is not actually occurring inside of the core and something like Jupiter would be an example and you can go several several masses above Jupiter where you get something like that so you have to reach a certain threshold or the mass where the pressure and the temperature due to the heavy mass gets so large that you start this fusion at but the smaller you have above that threshold this the slower the fusion will occur but if you're supermassive the fusion will occur really really fast so that's a general idea of just how stars get formed and why they don't collapse on themselves and why they are these kind of little balls of fusion reactions existing in the universe and the next few videos we'll talk about what happens once that hydrogen fuel and the cure in the core starts to run out...
+\\\hline
+29 &          BoS &                                                                                                                                                                                                                       Which of the following terms accurately describes the Sun?
+&                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                    \\\hline
+30 &          BoS &                                                                                                                                                                                                                   Which of the following terms best describes a fusion reaction?
+&                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                    \textbf{[04:51.639--06:05.83]} ...most basic type of fusion that exhibit ours the hydrogen gets fused into deuterium deuterium of trouble spelling which is another way of calling heavy hydrogen this is still hydrogen because it has one proton and one Neutron now it is not helium yet it does not have two it does not have two protons but then the deuterium keeps fusing and then we eventually end up with and then we end up with helium and we can even see that on the periodic table I lost my periodic table well I'll show you in the next video but we know hydrogen hydrogen hydrogen in its atomic state has an atomic number of one and it also has a mass of one it only has one nucleon and it's nucleus but it's being fused it goes to hydrogen too which is deuterium which is one Neutron one proton in its nucleus two nucleons and then that eventually gets fused and I'm not going to the detail of the reaction into helium and by definition helium has two protons and two neutrons so it has or we're talking about helium four in particular that isotope of helium it has an atomic mass of four and the whole this process releases a ton of energy because the atomic mass of the helium\newline\textbf{[06:50.68--07:52.81]} ...there's there's questions of well what if what if there just wasn't enough mass to get to this level over here and there actually are things that never get to that quite that threshold to fuse all the way into helium there are a few things that don't quite make the threshold of stars that only fuse to this level so they are generating some of their eat or there are even smaller objects that just get to the point there's a huge temperature and pressure but fusion is not actually occurring inside of the core and something like Jupiter would be an example and you can go several several masses above Jupiter where you get something like that so you have to reach a certain threshold or the mass where the pressure and the temperature due to the heavy mass gets so large that you start this fusion at but the smaller you have above that threshold this the slower the fusion will occur but if you're supermassive the fusion will occur really really fast so that's a general idea of just how stars get formed and why they don't collapse on themselves and why they are these kind of little balls of fusion reactions existing in the universe and the next few videos we'll talk about what happens once that hydrogen fuel and the cure in the core starts to run out...
+\\\hline
+
+    \caption{\textbf{Table title.} Caption content caption content caption content caption content caption content caption content caption content caption content caption content caption content.}
+    \end{longtable}
+\end{tiny}
 
@@
 
-% \renewcommand{\refname}{Supplementary references}
-% \bibliographystyle{apa}
-% \bibliography{CDL-bibliography/cdl}
-
 \end{document}

### 2023-10-22 paper/main.tex
text reflow

@@
 
-A common approach to assessing a student's knowledge is to present them with a set of quiz
-questions, calculate the proportion they answer correctly, and provide
-them with feedback in the form of a simple numeric or letter grade. While such a
-grade can provide \textit{some} indication of whether the student has
-mastered the to-be-learned material, any univariate measure of performance on a
-complex task sacrifices certain relevant information, risks conflating underlying
-factors, and so on. For example, consider the relative utility of the
-theoretical map described above that characterizes a student's knowledge
-in detail, versus a single annotation saying that the student answered 85\% of
+A common approach to assessing a student's knowledge is to present them with a
+set of quiz questions, calculate the proportion they answer correctly, and
+provide them with feedback in the form of a simple numeric or letter grade.
+While such a grade can provide \textit{some} indication of whether the student
+has mastered the to-be-learned material, any univariate measure of performance
+on a complex task sacrifices certain relevant information, risks conflating
+underlying factors, and so on. For example, consider the relative utility of
+the theoretical map described above that characterizes a student's knowledge in
+detail, versus a single annotation saying that the student answered 85\% of
 their quiz questions correctly, or that they received a `B'. Here, we show that
@@
 understanding, often by training participants to distinguish arbitrary or
-random features in otherwise meaningless categorized stimuli~\citep{ReilEtal82, Este86a, Este86b, GlucEtal02, AshbMadd05, HulbNorm15}. However the
-objective of real-world training, or learning from life experiences more
-generally, is often to develop new knowledge that may be applied in
-\textit{useful} ways in the future. In this sense, the gap between modern
-learning theories and modern pedagogical approaches that inform classroom
-learning strategies is enormous: most of our theories about \textit{how} people
-learn are inspired by experimental paradigms and models that have only
-peripheral relevance to the kinds of learning that students and teachers
-actually seek~\citep{Macl05, HallGree08}. To help bridge this gap, our study
-uses course materials from real online courses to inform, fit, and test models
-of real-world conceptual learning. We also provide a demonstration of how our
-models can be used to construct ``maps'' of what students know, and how their
-knowledge changes with training. In addition to helping to visually capture knowledge
-(and changes in knowledge), we hope that such maps might lead to real-world
-tools for improving how we educate. Taken together, our work shows that
-existing course materials and evaluative tools like short multiple-choice
-quizzes may be leveraged to gain highly detailed insights into what students
-know and how they learn.
+random features in otherwise meaningless categorized stimuli~\citep{ReilEtal82,
+Este86a, Este86b, GlucEtal02, AshbMadd05, HulbNorm15}. However the objective of
+real-world training, or learning from life experiences more generally, is often
+to develop new knowledge that may be applied in \textit{useful} ways in the
+future. In this sense, the gap between modern learning theories and modern
+pedagogical approaches that inform classroom learning strategies is enormous:
+most of our theories about \textit{how} people learn are inspired by
+experimental paradigms and models that have only peripheral relevance to the
+kinds of learning that students and teachers actually seek~\citep{Macl05,
+HallGree08}. To help bridge this gap, our study uses course materials from real
+online courses to inform, fit, and test models of real-world conceptual
+learning. We also provide a demonstration of how our models can be used to
+construct ``maps'' of what students know, and how their knowledge changes with
+training. In addition to helping to visually capture knowledge (and changes in
+knowledge), we hope that such maps might lead to real-world tools for improving
+how we educate. Taken together, our work shows that existing course materials
+and evaluative tools like short multiple-choice quizzes may be leveraged to
+gain highly detailed insights into what students know and how they learn.
 
@@
 coordinates), their ``level of knowledge'' should change relatively gradually.
-To begin to test this smoothness assumption, we sought
-to track participants' knowledge and how it changed over time in response to
-training. Two overarching goals guide our approach. First, we want to gain
-detailed insights into what learners know at different points in their
-training. For example, rather than simply reporting on the proportions of
-questions participants answer correctly (i.e., their overall performance), we
-seek estimates of their knowledge about a variety of specific concepts.
-Second, we want our approach to be potentially scalable to large numbers of
-diverse concepts, courses, and students. This requires that the conceptual content of
-interest be discovered \textit{automatically}, rather than relying on
-manually produced ratings or labels.
+To begin to test this smoothness assumption, we sought to track participants'
+knowledge and how it changed over time in response to training. Two overarching
+goals guide our approach. First, we want to gain detailed insights into what
+learners know at different points in their training. For example, rather than
+simply reporting on the proportions of questions participants answer correctly
+(i.e., their overall performance), we seek estimates of their knowledge about a
+variety of specific concepts. Second, we want our approach to be potentially
+scalable to large numbers of diverse concepts, courses, and students. This
+requires that the conceptual content of interest be discovered
+\textit{automatically}, rather than relying on manually produced ratings or
+labels.
 
@@
     \caption{\textbf{Experimental paradigm.} Participants alternate between
-    completing three 13-question multiple-choice quizzes and watching two Khan Academy
-    lectures. Each quiz contains a mix of 5 questions about Lecture~1, 5
-    questions about Lecture~2, and 3 questions about general physics knowledge. The
-    specific questions reflected on each quiz, and the orders of each quiz's
-    questions, were randomized across participants.}
+    completing three 13-question multiple-choice quizzes and watching two Khan
+    Academy lectures. Each quiz contains a mix of 5 questions about Lecture~1,
+    5 questions about Lecture~2, and 3 questions about general physics
+    knowledge. The specific questions reflected on each quiz, and the orders of
+    each quiz's questions, were randomized across participants.}
 
@@
 related content, so that we could test our approach's ability to distinguish
-similar conceptual content. To this end, we chose two videos from the same
-Khan Academy course domain, ``Cosmology and
-Astronomy.'' Third, we sought to minimize dependencies and specific overlap
-between the videos. For example, we did not want participants' abilities to
-understand one video to (directly) influence their abilities to understand the
-other. To satisfy this last criterion, we chose videos from two different
-lecture series (Lectures~1 and 2 were from the ``Scale of the Universe'' and
-``Stars, Black Holes, and Galaxies'' series, respectively).
+similar conceptual content. To this end, we chose two videos from the same Khan
+Academy course domain, ``Cosmology and Astronomy.'' Third, we sought to
+minimize dependencies and specific overlap between the videos. For example, we
+did not want participants' abilities to understand one video to (directly)
+influence their abilities to understand the other. To satisfy this last
+criterion, we chose videos from two different lecture series (Lectures~1 and 2
+were from the ``Scale of the Universe'' and ``Stars, Black Holes, and
+Galaxies'' series, respectively).
 
@@
 enable us to evaluate participants' knowledge about each individual lecture,
-along with related knowledge about physics concepts not specifically presented in either
-video (see Supp. Tab.~\questions~for the full list of questions in our stimulus
-pool). Participants answered questions randomly drawn from each content area
-(Lecture~1, Lecture~2, and general physics knowledge) on each of the three
-quizzes. Quiz~1 was intended to assess participants' ``baseline'' knowledge
-before training, Quiz~2 assessed knowledge after watching the \textit{Four
-Fundamental Forces} video (i.e., Lecture~1), and Quiz~3 assessed knowledge
-after watching the \textit{Birth of Stars} video (i.e., Lecture~2).
+along with related knowledge about physics concepts not specifically presented
+in either video (see Supp. Tab.~\questions~for the full list of questions in
+our stimulus pool). Participants answered questions randomly drawn from each
+content area (Lecture~1, Lecture~2, and general physics knowledge) on each of
+the three quizzes. Quiz~1 was intended to assess participants' ``baseline''
+knowledge before training, Quiz~2 assessed knowledge after watching the
+\textit{Four Fundamental Forces} video (i.e., Lecture~1), and Quiz~3 assessed
+knowledge after watching the \textit{Birth of Stars} video (i.e., Lecture~2).
 
@@
 
-    \caption{\textbf{Modeling course content.} \textbf{A. Building a document pool
-    from sliding windows of text.} We decompose each lecture's transcript into a
-    series of overlapping sliding windows. The full set of transcript snippets (across
-    all windows) may be treated as a set of ``documents'' for training a text
-    embedding model. \textbf{B. Constructing lecture content
-    \textit{trajectories}.} After training the model on the sliding windows from
-    both lectures, we transform each lecture into a ``trajectory'' through text
-    embedding space by joining the embedding coordinates of successive sliding
-    windows parsed from its transcript. \textbf{C. Embedding multiple lectures and
-    questions in a shared space.} We apply the same model (trained on the two
-    lectures' windows) to both lectures, along with the text of each question in
-    our pool (Supp. Tab.~\questions), to project them into a shared text embedding space.
-    This results in one trajectory per lecture and one coordinate for each
-    question. Here, we have projected the 15-dimensional embeddings onto their first
-    3 principal components for visualization.}
+    \caption{\textbf{Modeling course content.} \textbf{A. Building a document
+    pool from sliding windows of text.} We decompose each lecture's transcript
+    into a series of overlapping sliding windows. The full set of transcript
+    snippets (across all windows) may be treated as a set of ``documents'' for
+    training a text embedding model. \textbf{B. Constructing lecture content
+    \textit{trajectories}.} After training the model on the sliding windows
+    from both lectures, we transform each lecture into a ``trajectory'' through
+    text embedding space by joining the embedding coordinates of successive
+    sliding windows parsed from its transcript. \textbf{C. Embedding multiple
+    lectures and questions in a shared space.} We apply the same model (trained
+    on the two lectures' windows) to both lectures, along with the text of each
+    question in our pool (Supp. Tab.~\questions), to project them into a shared
+    text embedding space. This results in one trajectory per lecture and one
+    coordinate for each question. Here, we have projected the 15-dimensional
+    embeddings onto their first 3 principal components for visualization.}
 
@@
 Transforming the text from every sliding window with the model yielded a
-number-of-windows by number-of-topics (15) topic-proportions matrix
-describing the unique mixture of broad themes from both lectures reflected in
-each window's text. Each window's ``topic vector'' (i.e., column of the
-topic-proportions matrix) is analogous to a coordinate in a 15-dimensional space whose axes
-are topics discovered by the model. Within this space, each lecture's sequence
-of topic vectors (i.e., corresponding to its transcript's overlapping text
-snippets across sliding windows) forms a \textit{trajectory} that captures how
-its conceptual content unfolds over time (Fig.~\ref{fig:sliding-windows}B). We
-resampled these trajectories to a resolution of one topic vector for each
-second of video (i.e., 1~Hz).
+number-of-windows by number-of-topics (15) topic-proportions matrix describing
+the unique mixture of broad themes from both lectures reflected in each
+window's text. Each window's ``topic vector'' (i.e., column of the
+topic-proportions matrix) is analogous to a coordinate in a 15-dimensional
+space whose axes are topics discovered by the model. Within this space, each
+lecture's sequence of topic vectors (i.e., corresponding to its transcript's
+overlapping text snippets across sliding windows) forms a \textit{trajectory}
+that captures how its conceptual content unfolds over time
+(Fig.~\ref{fig:sliding-windows}B). We resampled these trajectories to a
+resolution of one topic vector for each second of video (i.e., 1~Hz).
 
@@
 and question set (averaging across time and questions, respectively) reveals a
-striking correspondence (Supp. Fig.~\topicWeights). Specifically, the average topic
-weights from Lecture~1 are strongly correlated with the average topic weights
-from Lecture~1 questions ($r(13) = 0.809,~p < 0.001$, 95\% confidence interval
-(CI)~$= [0.633,~0.962]$), and the average topic weights from Lecture~2 are
-strongly correlated with the average topic weights from Lecture~2 questions
+striking correspondence (Supp. Fig.~\topicWeights). Specifically, the average
+topic weights from Lecture~1 are strongly correlated with the average topic
+weights from Lecture~1 questions ($r(13) = 0.809,~p < 0.001$, 95\% confidence
+interval (CI)~$= [0.633,~0.962]$), and the average topic weights from Lecture~2
+are strongly correlated with the average topic weights from Lecture~2 questions
 ($r(13) = 0.728,~p = 0.002$, 95\% CI~$= [0.456,~0.920]$). At the same time, the
-average topic weights from the two lectures are \textit{negatively} correlated with
-their non-matching question sets (Lecture~1 video vs.~Lecture~2 questions: $r(13) =
--0.547,~p = 0.035$, 95\% CI~$= [-0.812, ~-0.231]$; Lecture~2 video vs.~Lecture~1 questions: $r(13)
-= -0.612,~p = 0.015$, 95\% CI~$= [-0.874,~-0.281]$), indicating that the topic model
-also exhibits some degree of specificity. The full set of pairwise comparisons
-between average topic weights for the lectures and question sets is reported in
-Supplementary Figure~\topicWeights.
+average topic weights from the two lectures are \textit{negatively} correlated
+with their non-matching question sets (Lecture~1 video vs.~Lecture~2 questions:
+$r(13) = -0.547,~p = 0.035$, 95\% CI~$= [-0.812, ~-0.231]$; Lecture~2 video
+vs.~Lecture~1 questions: $r(13) = -0.612,~p = 0.015$, 95\% CI~$=
+[-0.874,~-0.281]$), indicating that the topic model also exhibits some degree
+of specificity. The full set of pairwise comparisons between average topic
+weights for the lectures and question sets is reported in Supplementary
+Figure~\topicWeights.
 
@@
 
-    \caption{\textbf{Lecture and question topic overlap.} \textbf{A. Topic weight
-    variability}. The bar plots display the variance of each topic's weight across
-    lecture timepoints (top row) and questions (bottom row); colors denote topics.
-    The top-weighted words from the most ``expressive'' (i.e., variable across
-    observations) topic from each lecture are displayed in the upper right (orange:
-    topic 2; yellow-green: topic 4). The top-weighted words from the full set of
-    topics may be found in Supplementary Table~\topics. \textbf{B. Relationships between topic
-    weight variability.} Pairwise correlations between the distributions of topic
+    \caption{\textbf{Lecture and question topic overlap.} \textbf{A. Topic
+    weight variability}. The bar plots display the variance of each topic's
+    weight across lecture timepoints (top row) and questions (bottom row);
+    colors denote topics. The top-weighted words from the most ``expressive''
+    (i.e., variable across observations) topic from each lecture are displayed
+    in the upper right (orange: topic 2; yellow-green: topic 4). The
+    top-weighted words from the full set of topics may be found in
+    Supplementary Table~\topics. \textbf{B. Relationships between topic weight
+    variability.} Pairwise correlations between the distributions of topic
     weight variance for each lecture and question set. Each row and column
@@
 Intuitively, the variability in the expression of a given topic relates to how
-much ``information''~\citep{Fish22} the lecture (or question set) reflects about
-that topic. For example, suppose a given topic is weighted on heavily
+much ``information''~\citep{Fish22} the lecture (or question set) reflects
+about that topic. For example, suppose a given topic is weighted on heavily
 throughout a lecture. That topic might be characteristic of some aspect or
@@
 expression (over time and across questions) was similar for the Lecture~1 video
-and questions ($r(13) = 0.824,~p<0.001$, 95\% CI~$= [0.696,~0.973]$) and the Lecture~2
-video and questions ($r(13) = 0.801,~p<0.001$, 95\% CI~$= [0.539,~0.958]$).
-Simultaneously, as reported in Figure~\ref{fig:topics}B, the variability in
-topic expression across \textit{different} videos and lecture-specific
-questions (i.e., Lecture~1 video vs.~Lecture~2 questions; Lecture~2 video
-vs.~Lecture~1 questions) were negatively correlated, and neither
-video's topic variability was reliably correlated with the topic variability
-across general physics knowledge questions. Taken together, the analyses
-reported in Figure~\ref{fig:topics} and Supplementary Figure~\topicWeights~indicate that a topic
-model fit to the videos' transcripts can also reveal correspondences (at a
-coarse scale) between the lectures and questions.
+and questions ($r(13) = 0.824,~p<0.001$, 95\% CI~$= [0.696,~0.973]$) and the
+Lecture~2 video and questions ($r(13) = 0.801,~p<0.001$, 95\% CI~$=
+[0.539,~0.958]$). Simultaneously, as reported in Figure~\ref{fig:topics}B, the
+variability in topic expression across \textit{different} videos and
+lecture-specific questions (i.e., Lecture~1 video vs.~Lecture~2 questions;
+Lecture~2 video vs.~Lecture~1 questions) were negatively correlated, and
+neither video's topic variability was reliably correlated with the topic
+variability across general physics knowledge questions. Taken together, the
+analyses reported in Figure~\ref{fig:topics} and Supplementary
+Figure~\topicWeights~indicate that a topic model fit to the videos' transcripts
+can also reveal correspondences (at a coarse scale) between the lectures and
+questions.
 
@@
 coarse scale, at a finer scale, each moment of a lecture typically covers a
-narrower range of content. Given the correspondence we found between the variability
-in topic expression across moments of each lecture and questions from its
-corresponding set (Fig.~\ref{fig:topics}), we wondered whether the text embedding model
-might additionally capture these conceptual relationships at a finer scale.
-For example, if a particular question asks about the content from one small
-part of a lecture, we wondered whether the text embeddings could be used to
-automatically identify the ``matching'' moment(s) in the lecture. To explore this,
-we computed the correlation between each question's topic weights and the topic weights
-for each second of its corresponding lecture, and found that each question appeared to be
-temporally specific (Fig.~\ref{fig:question-correlations}). In particular, most questions'
-topic vectors were maximally correlated with a well-defined (and relatively
-narrow) range of timepoints from their corresponding lectures, and the
-correlations fell off sharply outside of that range. We also qualitatively examined the
-best-matching intervals for each question by comparing the question's text
-to the text of the most-correlated parts of the lectures.
-Despite that the questions were excluded from the text embedding model's
-training set, in general we found (through manual inspection) a close
-correspondence between the conceptual content that each question probed and
-the content covered by the best-matching moments of the lectures. Two
-representative examples are shown at the bottom of
-Figure~\ref{fig:question-correlations}.
+narrower range of content. Given the correspondence we found between the
+variability in topic expression across moments of each lecture and questions
+from its corresponding set (Fig.~\ref{fig:topics}), we wondered whether the
+text embedding model might additionally capture these conceptual relationships
+at a finer scale. For example, if a particular question asks about the content
+from one small part of a lecture, we wondered whether the text embeddings could
+be used to automatically identify the ``matching'' moment(s) in the lecture. To
+explore this, we computed the correlation between each question's topic weights
+and the topic weights for each second of its corresponding lecture, and found
+that each question appeared to be temporally specific
+(Fig.~\ref{fig:question-correlations}). In particular, most questions' topic
+vectors were maximally correlated with a well-defined (and relatively narrow)
+range of timepoints from their corresponding lectures, and the correlations
+fell off sharply outside of that range. We also qualitatively examined the
+best-matching intervals for each question by comparing the question's text to
+the text of the most-correlated parts of the lectures. Despite that the
+questions were excluded from the text embedding model's training set, in
+general we found (through manual inspection) a close correspondence between the
+conceptual content that each question probed and the content covered by the
+best-matching moments of the lectures. Two representative examples are shown at
+the bottom of Figure~\ref{fig:question-correlations}.
 
@@
 
-    \caption{\textbf{Which parts of each lecture are captured by each question?}
-    Each panel displays timeseries plots showing how each question's topic vector
-    correlates with each video timepoint's topic vector (Panel \textbf{A.}:
-    correlations for the \textit{Four Fundamental Forces} lecture and associated
-    questions; Panel \textbf{B.}: correlations for the \textit{Birth of Stars}
-    lecture and associated questions). The colors denote question identities. The
-    diamonds in each panel denote the moment of peak correlation between the
-    indicated question and the lecture trajectory. The associated questions' text
-    and snippets of the lectures' transcripts from the surrounding 30 seconds, are
-    displayed at the bottom of the figure.}
+    \caption{\textbf{Which parts of each lecture are captured by each
+    question?} Each panel displays timeseries plots showing how each question's
+    topic vector correlates with each video timepoint's topic vector (Panel
+    \textbf{A.}: correlations for the \textit{Four Fundamental Forces} lecture
+    and associated questions; Panel \textbf{B.}: correlations for the
+    \textit{Birth of Stars} lecture and associated questions). The colors
+    denote question identities. The diamonds in each panel denote the moment of
+    peak correlation between the indicated question and the lecture trajectory.
+    The associated questions' text and snippets of the lectures' transcripts
+    from the surrounding 30 seconds, are displayed at the bottom of the
+    figure.}
 
@@
 missed three questions about three \textit{different} concepts (e.g., $A$, $B$,
-and $C$). But if we wanted to help these two students fill in the ``gaps'' in their
-understandings, we might do well to focus specifically on concept $A$ for the first student,
-but to also add in materials pertaining to concepts $B$ and $C$ for the second
-student. In other words, raw ``proportion-correct'' measures may capture
-\textit{how much} a student knows, but not \textit{what} they know. We wondered
-whether our modeling framework might enable us to (formally and automatically)
-infer participants' knowledge at the scale of individual concepts (e.g., as
-captured by a single moment of a lecture).
+and $C$). But if we wanted to help these two students fill in the ``gaps'' in
+their understandings, we might do well to focus specifically on concept $A$ for
+the first student, but to also add in materials pertaining to concepts $B$ and
+$C$ for the second student. In other words, raw ``proportion-correct'' measures
+may capture \textit{how much} a student knows, but not \textit{what} they know.
+We wondered whether our modeling framework might enable us to (formally and
+automatically) infer participants' knowledge at the scale of individual
+concepts (e.g., as captured by a single moment of a lecture).
 
@@
 this approach separately for the questions from each quiz participants took
-throughout the experiment. From just a few questions per quiz (see~\nameref{subsec:traces}), we obtain a
-high-resolution snapshot (at the time each quiz was taken) of what the
-participants knew about any moment's content, from either of the two lectures
-they watched (comprising a total of 1,100 samples across the two lectures).
+throughout the experiment. From just a few questions per quiz
+(see~\nameref{subsec:traces}), we obtain a high-resolution snapshot (at the
+time each quiz was taken) of what the participants knew about any moment's
+content, from either of the two lectures they watched (comprising a total of
+1,100 samples across the two lectures).
 
@@
     questions about the content reflected in each moment of the lecture (see
-    \nameref{subsec:traces}), using responses from a single
-    quiz (color). The traces are averaged across participants. \textbf{B.
-    Average estimated knowledge about the \textbf{Four Fundamental Forces}.}
-    Each bar displays the across-timepoint average knowledge, estimated using
-    the responses to one quiz's questions. \textbf{C. Moment-by-moment
-    knowledge about the \textit{Birth of Stars}}. The panel is in the same
-    format as Panel A, but here the knowledge estimates are for the
-    moment-by-moment content of the \textit{Birth of Stars} lecture. \textbf{D.
-    Average estimated knowledge about the \textit{Birth of Stars}.} The panel
-    is in the same format as Panel B, but here the knowledge estimates are for
-    the content of the \textit{Birth of Stars} lecture. All panels: error
-    ribbons and error bars denote 95\% confidence intervals, estimated across
-    participants.}
+    \nameref{subsec:traces}), using responses from a single quiz (color). The
+    traces are averaged across participants. \textbf{B. Average estimated
+    knowledge about the \textbf{Four Fundamental Forces}.} Each bar displays
+    the across-timepoint average knowledge, estimated using the responses to
+    one quiz's questions. \textbf{C. Moment-by-moment knowledge about the
+    \textit{Birth of Stars}}. The panel is in the same format as Panel A, but
+    here the knowledge estimates are for the moment-by-moment content of the
+    \textit{Birth of Stars} lecture. \textbf{D. Average estimated knowledge
+    about the \textit{Birth of Stars}.} The panel is in the same format as
+    Panel B, but here the knowledge estimates are for the content of the
+    \textit{Birth of Stars} lecture. All panels: error ribbons and error bars
+    denote 95\% confidence intervals, estimated across participants.}
 
@@
 
-While the timecourses in
-Figure~\ref{fig:knowledge-timeseries}A and C provide detailed
-\textit{estimates} about participants' knowlege, these estimates are of course only
-\textit{useful} to the extent that they accurately reflect what participants
-actually know. As one sanity check, we anticipated that the knowledge estimates
-should reflect a content-specific ``boost'' in participants' knowledge after
-watching each lecture. In other words, if participants learn about each
-lecture's content when they watch each lecture, the knowledge estimates should
-capture that. After watching the \textit{Four Fundamental Forces} lecture,
-participants should exhibit more knowledge for the content of that lecture than
-they had before, and that knowledge should persist for the remainder of the
-experiment. Specifically, knowledge about that lecture's content should be
-relatively low when estimated using Quiz~1 responses, but should increase when
-estimated using Quiz~2 or 3 responses (Fig.~\ref{fig:knowledge-timeseries}B).
-Indeed, we found that participants' estimated knowledge about the content of
-the \textit{Four Fundamental Forces} was substantially higher on Quiz~2 versus
-Quiz~1 ($t(49) = 8.764,~p < 0.001$) and on Quiz~3 versus Quiz~1 ($t(49) =
-10.519,~p < 0.001$). We found no reliable differences in estimated knowledge
-about that lecture's content on Quiz~2 versus 3 ($t(49) = 0.160,~p = 0.874$).
-Similarly, we hypothesized (and subsequently confirmed) that participants
-should show greater estimated knowledge about the content of the \textit{Birth of
-Stars} lecture after (versus before) watching it
-(Fig.~\ref{fig:knowledge-timeseries}D). Specifically, since participants
-watched that lecture after taking Quiz~2 (but before Quiz~3), we hypothesized
-that their knowledge estimates should be relatively low on Quizzes~1 and 2, but
-should show a ``boost'' on Quiz~3. Consistent with this prediction, we found no
-reliable differences in estimated knowledge about the \textit{Birth of Stars}
-lecture content on Quizzes~1 versus 2 ($t(49) = 1.013,~p = 0.316$), but the
-estimated knowledge was substantially higher on Quiz~3 versus 2 ($t(49) =
-10.561,~p < 0.001$) and Quiz~3 versus 1 ($t(49) = 8.969,~p < 0.001$).
+While the timecourses in Figure~\ref{fig:knowledge-timeseries}A and C provide
+detailed \textit{estimates} about participants' knowlege, these estimates are
+of course only \textit{useful} to the extent that they accurately reflect what
+participants actually know. As one sanity check, we anticipated that the
+knowledge estimates should reflect a content-specific ``boost'' in
+participants' knowledge after watching each lecture. In other words, if
+participants learn about each lecture's content when they watch each lecture,
+the knowledge estimates should capture that. After watching the \textit{Four
+Fundamental Forces} lecture, participants should exhibit more knowledge for the
+content of that lecture than they had before, and that knowledge should persist
+for the remainder of the experiment. Specifically, knowledge about that
+lecture's content should be relatively low when estimated using Quiz~1
+responses, but should increase when estimated using Quiz~2 or 3 responses
+(Fig.~\ref{fig:knowledge-timeseries}B). Indeed, we found that participants'
+estimated knowledge about the content of the \textit{Four Fundamental Forces}
+was substantially higher on Quiz~2 versus Quiz~1 ($t(49) = 8.764,~p < 0.001$)
+and on Quiz~3 versus Quiz~1 ($t(49) = 10.519,~p < 0.001$). We found no reliable
+differences in estimated knowledge about that lecture's content on Quiz~2
+versus 3 ($t(49) = 0.160,~p = 0.874$). Similarly, we hypothesized (and
+subsequently confirmed) that participants should show greater estimated
+knowledge about the content of the \textit{Birth of Stars} lecture after
+(versus before) watching it (Fig.~\ref{fig:knowledge-timeseries}D).
+Specifically, since participants watched that lecture after taking Quiz~2 (but
+before Quiz~3), we hypothesized that their knowledge estimates should be
+relatively low on Quizzes~1 and 2, but should show a ``boost'' on Quiz~3.
+Consistent with this prediction, we found no reliable differences in estimated
+knowledge about the \textit{Birth of Stars} lecture content on Quizzes~1 versus
+2 ($t(49) = 1.013,~p = 0.316$), but the estimated knowledge was substantially
+higher on Quiz~3 versus 2 ($t(49) = 10.561,~p < 0.001$) and Quiz~3 versus 1
+($t(49) = 8.969,~p < 0.001$).
 
 If we are able to accurately estimate a participant's knowledge about the
-content tested by a given question, our estimates of their knowledge should carry some
-predictive information about whether the participant is likely to answer that
-question correctly or incorrectly. We developed a statistical approach to test this claim.
-For each question, in turn, we used Equation~\ref{eqn:prop} to estimate each
-participant's knowledge at the given question's embedding space coordinate,
-using all \textit{other} questions that participant answered on the same quiz.
-For each quiz, we grouped these estimates into two distributions: one for the
-estimated knowledge at the coordinates of \textit{correctly} answered
-questions, and another for the estimated knowledge at the coordinates of
-\textit{incorrectly} answered questions (Fig.~\ref{fig:predictions}). We then
-used independent samples $t$-tests to compare the means of these distributions
-of estimated knowledge.
+content tested by a given question, our estimates of their knowledge should
+carry some predictive information about whether the participant is likely to
+answer that question correctly or incorrectly. We developed a statistical
+approach to test this claim. For each question, in turn, we used
+Equation~\ref{eqn:prop} to estimate each participant's knowledge at the given
+question's embedding space coordinate, using all \textit{other} questions that
+participant answered on the same quiz. For each quiz, we grouped these
+estimates into two distributions: one for the estimated knowledge at the
+coordinates of \textit{correctly} answered questions, and another for the
+estimated knowledge at the coordinates of \textit{incorrectly} answered
+questions (Fig.~\ref{fig:predictions}). We then used independent samples
+$t$-tests to compare the means of these distributions of estimated knowledge.
 
@@
 knowledge about Lecture~2 and general physics concepts should be roughly
-unchanged from before they watched Lecture~1. After watching the second lecture,
-estimated knowledge (from the third quiz; Fig.~\ref{fig:predictions}, right
-panel) for \textit{all} questions exhibited a positive shift. However, the
-estimated knowledge for held-out correctly answered questions remained
-greater than that for held-out incorrectly answered questions ($t(628) = 2.045,~p
-= 0.041$). This third contrast reflects a ceiling effect: when knowledge is
-relatively high everywhere, the signal differentiating what is known versus
-unknown is relatively weak. Taken together, this set of analyses demonstrates
-that our knowledge prediction framework is most informative when participants
-exhibit variability in their knowledge of the content captured by the text
-embedding model.
+unchanged from before they watched Lecture~1. After watching the second
+lecture, estimated knowledge (from the third quiz; Fig.~\ref{fig:predictions},
+right panel) for \textit{all} questions exhibited a positive shift. However,
+the estimated knowledge for held-out correctly answered questions remained
+greater than that for held-out incorrectly answered questions ($t(628) =
+2.045,~p = 0.041$). This third contrast reflects a ceiling effect: when
+knowledge is relatively high everywhere, the signal differentiating what is
+known versus unknown is relatively weak. Taken together, this set of analyses
+demonstrates that our knowledge prediction framework is most informative when
+participants exhibit variability in their knowledge of the content captured by
+the text embedding model.
 
@@
 lectures participants watched, we first fit a new topic model to the lectures'
-sliding windows with (up to)~$k = 100$~topics.
-Conceptually, increasing the number of topics used by the model functions to
-increase the ``resolution'' of the embedding space, providing a greater ability to
-estimate knowledge for content that is highly similar to (but not precisely the same as)
-that contained in the two lectures.
-Aside from increasing the number of topics from 15 to 100, all other
-procedures and model parameters were carried over from the preceding analyses.
-As in our other analyses, we resampled each lecture's topic trajectory to 1~Hz
-and projected each question into a shared text embedding space.
+sliding windows with (up to)~$k = 100$~topics. Conceptually, increasing the
+number of topics used by the model functions to increase the ``resolution'' of
+the embedding space, providing a greater ability to estimate knowledge for
+content that is highly similar to (but not precisely the same as) that
+contained in the two lectures. Aside from increasing the number of topics from
+15 to 100, all other procedures and model parameters were carried over from the
+preceding analyses. As in our other analyses, we resampled each lecture's topic
+trajectory to 1~Hz and projected each question into a shared text embedding
+space.
 
@@
     and~\individualKnowledgeMapsC. \textbf{B. Average ``learning maps''
-    estimated between each successive pair of quizzes.} The learning maps follow
-    the same general format as the knowledge maps in Panel A, but here the
-    shading at each coordinate indicates the \textit{difference} between the
-    corresponding coordinates in the indicated \textit{pair} of knowledge
+    estimated between each successive pair of quizzes.} The learning maps
+    follow the same general format as the knowledge maps in Panel A, but here
+    the shading at each coordinate indicates the \textit{difference} between
+    the corresponding coordinates in the indicated \textit{pair} of knowledge
     maps---i.e., how much the estimated knowledge ``changed'' between the two
@@
     Figures~\individualLearningMapsA~and~\individualLearningMapsB. \textbf{C.
-    Word clouds for sampled points in topic space.} Each word cloud displays the
-    weighted blend of words underlying the topic proportions represented at the
-    corresponding colored star's location on the maps. In each word cloud, the
-    words' relative sizes correspond to their relative weights at the starred
-    location, and their colors indicate their relative weights in the
+    Word clouds for sampled points in topic space.} Each word cloud displays
+    the weighted blend of words underlying the topic proportions represented at
+    the corresponding colored star's location on the maps. In each word cloud,
+    the words' relative sizes correspond to their relative weights at the
+    starred location, and their colors indicate their relative weights in the
     \textit{Four Fundamental Forces} (blue) versus \textit{Birth of Stars}
@@
 content that is nearby (i.e., related to) the content from the lecture they
-watched prior to taking Quiz~2. This localization is non-trivial: these knowledge
-estimates are informed only by the embedded coordinates of the \textit{quiz
-questions}, not by the embeddings of either lecture
-(see Eqn.~\ref{eqn:rbf-knowledge}). Finally, the knowledge map estimated from Quiz
-3 responses shows a second increase in knowledge, localized to the region
+watched prior to taking Quiz~2. This localization is non-trivial: these
+knowledge estimates are informed only by the embedded coordinates of the
+\textit{quiz questions}, not by the embeddings of either lecture (see
+Eqn.~\ref{eqn:rbf-knowledge}). Finally, the knowledge map estimated from Quiz 3
+responses shows a second increase in knowledge, localized to the region
 surrounding the embedding of the \textit{Birth of Stars} lecture participants
@@
 
-Another way of visualizing these content-specific increases in knowledge
-after participants viewed each lecture is displayed in
+Another way of visualizing these content-specific increases in knowledge after
+participants viewed each lecture is displayed in
 Figure~\ref{fig:knowledge-maps}B. Taking the point-by-point difference between
@@
 Because the 2D projection we used to construct the knowledge and learning maps
-is invertible, we may gain additional insights into these maps' meaning
-by reconstructing the original high-dimensional topic vector for any location
-on the map we are interested in. For example, this could serve as a useful
-tool for an instructor looking to better understand which content areas a
-student (or a group of students) knows well (or poorly). As a demonstration, we
-show the top-weighted words from the blends of topics reconstructed from three
+is invertible, we may gain additional insights into these maps' meaning by
+reconstructing the original high-dimensional topic vector for any location on
+the map we are interested in. For example, this could serve as a useful tool
+for an instructor looking to better understand which content areas a student
+(or a group of students) knows well (or poorly). As a demonstration, we show
+the top-weighted words from the blends of topics reconstructed from three
 example locations on the maps (Fig.~\ref{fig:knowledge-maps}C): one point near
 the \textit{Four Fundamental Forces} embedding (yellow), a second point near
-the \textit{Birth of Stars} embedding (orange), and a third point
-between the two lectures' embeddings (pink). As shown in the word clouds in the
-panel, the top-weighted words at the example coordinate near the \textit{Four
-Fundamental Forces} embedding tended to be weighted more heavily by the topics
-expressed in that lecture. Similarly, the top-weighted words at the example
-coordinate near the \textit{Birth of Stars} embedding tended to be weighted
-more heavily by the topics expressed in \textit{that} lecture. And the
-top-weighted words at the example coordinate between the two lectures'
-embeddings show a roughly even mix of words most strongly associated with each
-lecture.
+the \textit{Birth of Stars} embedding (orange), and a third point between the
+two lectures' embeddings (pink). As shown in the word clouds in the panel, the
+top-weighted words at the example coordinate near the \textit{Four Fundamental
+Forces} embedding tended to be weighted more heavily by the topics expressed in
+that lecture. Similarly, the top-weighted words at the example coordinate near
+the \textit{Birth of Stars} embedding tended to be weighted more heavily by the
+topics expressed in \textit{that} lecture. And the top-weighted words at the
+example coordinate between the two lectures' embeddings show a roughly even mix
+of words most strongly associated with each lecture.
 
@@
 changes with training. First, we show that our approach can automatically match
-the conceptual knowledge probed by individual quiz questions to the corresponding
-moments in lecture videos when those concepts were presented
+the conceptual knowledge probed by individual quiz questions to the
+corresponding moments in lecture videos when those concepts were presented
 (Fig.~\ref{fig:question-correlations}). Next, we demonstrate how we can
-estimate moment-by-moment ``knowledge traces'' that reflect the degree of knowledge
-participants have about each video's time-varying content, and capture temporally
-specific increases in knowledge after viewing each lecture (Fig.~\ref{fig:knowledge-timeseries}).
- We also show that these knowledge estimates can generalize to held-out questions
-(Fig.~\ref{fig:predictions}). Finally, we use our framework to construct visual
-maps that provide snapshot estimates of how much participants know about any
-concept within the scope of our text embedding model, and how much their
-knowledge of those concepts changes with training (Fig.~\ref{fig:knowledge-maps}).
+estimate moment-by-moment ``knowledge traces'' that reflect the degree of
+knowledge participants have about each video's time-varying content, and
+capture temporally specific increases in knowledge after viewing each lecture
+(Fig.~\ref{fig:knowledge-timeseries}). We also show that these knowledge
+estimates can generalize to held-out questions (Fig.~\ref{fig:predictions}).
+Finally, we use our framework to construct visual maps that provide snapshot
+estimates of how much participants know about any concept within the scope of
+our text embedding model, and how much their knowledge of those concepts
+changes with training (Fig.~\ref{fig:knowledge-maps}).
 
 Over the past several years, the global pandemic has forced many educators to
-suddenly adapt to teaching remotely~\citep{MoseEtal21, ShimLee20, KawaEtal21, Whal20}. This change
-in world circumstances is happening alongside (and perhaps accelerating)
-geometric growth in the availability of high-quality online courses from
-platforms such as Khan Academy~\citep{Khan04}, Coursera~\citep{Youn12},
-EdX~\citep{Kolo13}, and others~\citep{RhoaEtal13}. Continued expansion of the
-global internet backbone and improvements in computing hardware have also
-facilitated improvements in video streaming, enabling videos to be easily
-shared and viewed by increasingly large segments of the world's population. This
-exciting time for online course instruction provides an opportunity to
-re-evaluate how we, as a global community, educate ourselves and each other.
-For example, we can ask: what defines an effective course or training program?
-Which aspects of teaching might be optimized and/or augmented by automated tools? How and why do
-learning needs and goals vary across people? How might we lower barriers of access
-to a high-quality education?
+suddenly adapt to teaching remotely~\citep{MoseEtal21, ShimLee20, KawaEtal21,
+Whal20}. This change in world circumstances is happening alongside (and perhaps
+accelerating) geometric growth in the availability of high-quality online
+courses from platforms such as Khan Academy~\citep{Khan04},
+Coursera~\citep{Youn12}, EdX~\citep{Kolo13}, and others~\citep{RhoaEtal13}.
+Continued expansion of the global internet backbone and improvements in
+computing hardware have also facilitated improvements in video streaming,
+enabling videos to be easily shared and viewed by increasingly large segments
+of the world's population. This exciting time for online course instruction
+provides an opportunity to re-evaluate how we, as a global community, educate
+ourselves and each other. For example, we can ask: what defines an effective
+course or training program? Which aspects of teaching might be optimized and/or
+augmented by automated tools? How and why do learning needs and goals vary
+across people? How might we lower barriers of access to a high-quality
+education?
 
@@
 to which two people's knowledge maps ``match'' or ``align'' in a given region
-of text embedding space might serve as a predictor of how effectively they
-will be able to communicate about the corresponding conceptual content.
+of text embedding space might serve as a predictor of how effectively they will
+be able to communicate about the corresponding conceptual content.
 
@@
 estimates about knowledge may be obtained from short quizzes shows one way that
-traditional approaches to evaluation in education may be extended. We hope
-that these advances might help pave the way for new approaches to teaching or
+traditional approaches to evaluation in education may be extended. We hope that
+these advances might help pave the way for new approaches to teaching or
 delivering educational content that are tailored to individual students'
@@
 We enrolled a total of 50 Dartmouth undergraduate students in our study.
-Participants received optional course credit for enrolling. We asked each participant to
-complete a demographic survey that included questions about their age, gender,
-native spoken language, ethnicity, race, hearing, color vision, sleep, coffee
-consumption, level of alertness, and several aspects of their educational
-background and prior coursework.
-
-Participants' ages ranged from 18 to 22 years (mean: 19.52 years;
-standard deviation: 1.09 years). A total of 15 participants reported
-their gender as male and 35 participants reported their gender as
-female. A total of 49 participants reported their native language as
-``English'' and 1 reported having another native language. A total of
-47 participants reported their ethnicity as ``Not Hispanic or Latino''
-and three reported their ethnicity as ``Hispanic or Latino.''
-Participants reported their races as White (32 participants), Asian
-(14 participants), Black or African American (5 participants),
-American Indian or Alaska Native (1 participant), and Native Hawaiian or
-Other Pacific Islander (1 participant). (Note that some participants
-selected multiple racial categories.)
-
-A total of 49 participants reporting having normal hearing and 1
-participant reported having some hearing impairment. A total of 49
-participants reported having normal color vision and 1 participant
-reported being color blind.  Participants reported having had, on the
-night prior to testing, 2--4 hours of sleep (1 participant), 4--6
-hours of sleep (9 participants), 6--8 hours of sleep (35
-participants), or $8+$ hours of sleep (5 participants). They reported
-having consumed, on the same day and leading up to their testing
-session, 0 cups of coffee (38 participants), 1 cup of coffee (10
-participants), 3 cups of coffee (1 participant), or $4+$ cups of
-coffee (1 participant).
-
-No participants reported that their focus was currently impaired
-(e.g., by drugs or alcohol).  Participants reported their current
-level of alertness, and we converted their responses to numerical
-scores as follows: ``very sluggish'' (-2), ``a little sluggish'' (-1),
-``neutral'' (0), ``fairly alert'' (1), and ``very alert'' (2). Across
-all participants, a range of alertness levels were reported (range:
--2--1; mean: -0.10; standard deviation: 0.84).
+Participants received optional course credit for enrolling. We asked each
+participant to complete a demographic survey that included questions about
+their age, gender, native spoken language, ethnicity, race, hearing, color
+vision, sleep, coffee consumption, level of alertness, and several aspects of
+their educational background and prior coursework.
+
+Participants' ages ranged from 18 to 22 years (mean: 19.52 years; standard
+deviation: 1.09 years). A total of 15 participants reported their gender as
+male and 35 participants reported their gender as female. A total of 49
+participants reported their native language as ``English'' and 1 reported
+having another native language. A total of 47 participants reported their
+ethnicity as ``Not Hispanic or Latino'' and three reported their ethnicity as
+``Hispanic or Latino.'' Participants reported their races as White (32
+participants), Asian (14 participants), Black or African American (5
+participants), American Indian or Alaska Native (1 participant), and Native
+Hawaiian or Other Pacific Islander (1 participant). (Note that some
+participants selected multiple racial categories.)
+
+A total of 49 participants reporting having normal hearing and 1 participant
+reported having some hearing impairment. A total of 49 participants reported
+having normal color vision and 1 participant reported being color blind.
+Participants reported having had, on the night prior to testing, 2--4 hours of
+sleep (1 participant), 4--6 hours of sleep (9 participants), 6--8 hours of
+sleep (35 participants), or $8+$ hours of sleep (5 participants). They reported
+having consumed, on the same day and leading up to their testing session, 0
+cups of coffee (38 participants), 1 cup of coffee (10 participants), 3 cups of
+coffee (1 participant), or $4+$ cups of coffee (1 participant).
+
+No participants reported that their focus was currently impaired (e.g., by
+drugs or alcohol). Participants reported their current level of alertness, and
+we converted their responses to numerical scores as follows: ``very sluggish''
+(-2), ``a little sluggish'' (-1), ``neutral'' (0), ``fairly alert'' (1), and
+``very alert'' (2). Across all participants, a range of alertness levels were
+reported (range: -2--1; mean: -0.10; standard deviation: 0.84).
 
@@
 duration: 7 minutes and 57 seconds). We then hand-created 39 multiple-choice
-questions: 15 about the conceptual content of \textit{Four Fundamental Forces} (i.e., Lecture~1),
-15 about the conceptual content of \textit{Birth of Stars} (i.e., Lecture~2), and 9
-questions that tested for general conceptual knowledge about basic physics
-(covering material that was not presented in either video). The full set of
-questions and answer choices may be found in Supplementary Table~\questions.
+questions: 15 about the conceptual content of \textit{Four Fundamental Forces}
+(i.e., Lecture~1), 15 about the conceptual content of \textit{Birth of Stars}
+(i.e., Lecture~2), and 9 questions that tested for general conceptual knowledge
+about basic physics (covering material that was not presented in either video).
+The full set of questions and answer choices may be found in Supplementary
+Table~\questions.
 
@@
 multiple-choice quizzes: the first before viewing Lecture~1, the second between
-Lectures~1 and 2, and the third after viewing Lecture~2
-(see Fig.~\ref{fig:experiment}). The questions appearing on each quiz, for each
+Lectures~1 and 2, and the third after viewing Lecture~2 (see
+Fig.~\ref{fig:experiment}). The questions appearing on each quiz, for each
 participant, were randomly chosen from the full set of 39, with the constraints
-that (a) each quiz contain exactly 5 questions about Lecture~1, 5 questions about
-Lecture~2, and 3 questions about general physics knowledge, and (b) each
+that (a) each quiz contain exactly 5 questions about Lecture~1, 5 questions
+about Lecture~2, and 3 questions about general physics knowledge, and (b) each
 question appear exactly once for each participant. The orders of questions on
@@
 Dirichlet Allocation;~\citealp{BleiEtal03}), trained on a set of documents, to
-discover a set of (up to) $k$ ``topics'' or ``themes.'' Formally, each topic is defined
-as a distribution of weights over each word in the model's vocabulary (i.e., the union
-of all unique words, across all documents, excluding ``stop words.'').
-Conceptually, each topic is intended to give larger weights to words that are
-semantically related or tend to co-occur in the same documents. After
+discover a set of (up to) $k$ ``topics'' or ``themes.'' Formally, each topic is
+defined as a distribution of weights over each word in the model's vocabulary
+(i.e., the union of all unique words, across all documents, excluding ``stop
+words.''). Conceptually, each topic is intended to give larger weights to words
+that are semantically related or tend to co-occur in the same documents. After
 fitting a topic model, each document in the training set, or any \textit{new}
@@
 may be represented as a $k$-dimensional vector describing how much the document
-(most probably) reflects each topic.
-To select an appropriate $k$ for our model, we identified the minimum number of
-topics that yielded at least one ``unused'' topic (i.e., in which all words in the vocabulary
-were assigned uniform weights) after training. This indicated that the number of topics was
-sufficient to capture the set of latent themes present in the two lectures (from which we
-constructed our document corpus, as described below). We found this value to be $k = 15$
-topics. The distribution of weights over words in the vocabulary for each discovered topic is
-shown in Supplementary Figure~\topicWordWeights, and each topic's top-weighted
-words may be found in Supplementary Table~\topics.
+(most probably) reflects each topic. To select an appropriate $k$ for our
+model, we identified the minimum number of topics that yielded at least one
+``unused'' topic (i.e., in which all words in the vocabulary were assigned
+uniform weights) after training. This indicated that the number of topics was
+sufficient to capture the set of latent themes present in the two lectures
+(from which we constructed our document corpus, as described below). We found
+this value to be $k = 15$ topics. The distribution of weights over words in the
+vocabulary for each discovered topic is shown in Supplementary
+Figure~\topicWordWeights, and each topic's top-weighted words may be found in
+Supplementary Table~\topics.
 
@@
 additionally provides automated captions. We opted to use these automated
-transcripts (which, in prior work, we have found to be of sufficiently near-human
-quality to yield reliable data in behavioral studies;~\citealp{ZimaEtal18}) when
-developing our framework in order to make it more directly extensible and
-adaptable by others in the future.
+transcripts (which, in prior work, we have found to be of sufficiently
+near-human quality to yield reliable data in behavioral
+studies;~\citealp{ZimaEtal18}) when developing our framework in order to make
+it more directly extensible and adaptable by others in the future.
 
@@
 length of (up to) $w = 30$ transcript lines, and assigned each window a
-timestamp corresponding to the midpoint between the timestamps for its first and last lines.
-These sliding windows ramped up and down in length at the
-beginning and end of each transcript, respectively. In other words, each transcript's first
-sliding window covered only its first line, the second
+timestamp corresponding to the midpoint between the timestamps for its first
+and last lines. These sliding windows ramped up and down in length at the
+beginning and end of each transcript, respectively. In other words, each
+transcript's first sliding window covered only its first line, the second
 sliding window covered the first two lines, and so on. This ensured that each
@@
 each sliding window as a single ``document,'' and combined these documents
-across the two videos' windows to create a single training corpus for the topic model.
+across the two videos' windows to create a single training corpus for the topic
+model.
 
@@
 reflect similar themes, according to the model) will yield similar coordinates
-(in terms of correlation, cosine similarity, Kullback-Leibler divergence, Euclidean distance, or other geometric measures). In
-general, the similarity between different documents' topic vectors may be used
-to characterize the similarity in conceptual content between the documents.
+(in terms of correlation, cosine similarity, Kullback-Leibler divergence,
+Euclidean distance, or other geometric measures). In general, the similarity
+between different documents' topic vectors may be used to characterize the
+similarity in conceptual content between the documents.
 
@@
 resulting timeseries to one vector per second. We also used the fitted model to
-obtain topic vectors for each question in our pool (see Supp. Tab.~\questions). Taken
-together, we obtained a \textit{trajectory} for each video, describing its path
-through topic space, and a single coordinate for each question
+obtain topic vectors for each question in our pool (see Supp. Tab.~\questions).
+Taken together, we obtained a \textit{trajectory} for each video, describing
+its path through topic space, and a single coordinate for each question
 (Fig.~\ref{fig:sliding-windows}C). Embedding both videos and all of the
@@
 topic vector for one question, $y$), normalized by the minimum and maximum
-correlations (across all timepoints $t$ and questions $Q$) to range between 0 and 1,
-inclusive. Equation~\ref{eqn:prop} then computes the weighted average
+correlations (across all timepoints $t$ and questions $Q$) to range between 0
+and 1, inclusive. Equation~\ref{eqn:prop} then computes the weighted average
 proportion of correctly answered questions about the content presented at
@@
 The normalization step (i.e., using $\mathrm{ncorr}$ instead of the raw
-correlations) insures that every question
-contributes some non-negative amount to the knowledge estimate.
+correlations) insures that every question contributes some non-negative amount
+to the knowledge estimate.
 
@@
 appearing in the lectures. To visualize these estimates
-(Fig.~\ref{fig:knowledge-maps}, Supp. Figs.~\individualKnowledgeMapsA,~\individualKnowledgeMapsB,~\individualKnowledgeMapsC,~\individualLearningMapsA,
+(Fig.~\ref{fig:knowledge-maps}, Supp.
+Figs.~\individualKnowledgeMapsA,~\individualKnowledgeMapsB,~\individualKnowledgeMapsC,~\individualLearningMapsA,
 and~\individualLearningMapsB), we used Uniform Manifold Approximation and
-Projection (UMAP; \citealp{McInEtal18a, McInEtal18b}) to construct a 2D projection of the
-text embedding space. Sampling the original 100-dimensional space at high
-resolution to obtain an adequate set of topic vectors spanning the embedding
-space would be computationally intractable. However, sampling a 2D grid is
-trivial.
+Projection (UMAP; \citealp{McInEtal18a, McInEtal18b}) to construct a 2D
+projection of the text embedding space. Sampling the original 100-dimensional
+space at high resolution to obtain an adequate set of topic vectors spanning
+the embedding space would be computationally intractable. However, sampling a
+2D grid is trivial.
 
@@
 In our application, all of the coordinates we embedded were topic vectors,
-whose elements are always non-negative and sum to one. Although UMAP is an invertible
-transformation at the embedding locations of the original data, other locations
-in the embedding space will not necessarily follow the same implicit ``rules''
-as the original high-dimensional data. For example, inverting an arbitrary
-coordinate in the embedding space might result in negative-valued vectors,
-which are incompatible with the topic modeling framework. To protect against
-this issue, we log-transformed the topic vectors prior to embedding them in the
-2D space. When we inverted the embedded vectors (e.g., to estimate topic
-vectors or word clouds, as in Fig.~\ref{fig:knowledge-maps}C), we passed the
-inverted (log-transformed) values through the exponential function to obtain a
-vector of non-negative values, and normalized them to sum to one.
+whose elements are always non-negative and sum to one. Although UMAP is an
+invertible transformation at the embedding locations of the original data,
+other locations in the embedding space will not necessarily follow the same
+implicit ``rules'' as the original high-dimensional data. For example,
+inverting an arbitrary coordinate in the embedding space might result in
+negative-valued vectors, which are incompatible with the topic modeling
+framework. To protect against this issue, we log-transformed the topic vectors
+prior to embedding them in the 2D space. When we inverted the embedded vectors
+(e.g., to estimate topic vectors or word clouds, as in
+Fig.~\ref{fig:knowledge-maps}C), we passed the inverted (log-transformed)
+values through the exponential function to obtain a vector of non-negative
+values, and normalized them to sum to one.
 
@@
 We acknowledge useful discussions, assistance in setting up an earlier
-(unpublished) version of this study, and assistance with data
-collection efforts from Will Baxley, Max Bluestone, Daniel Carstensen, Kunal
-Jha, Caroline Lee, Lucy Owen, Xinming Xu, and Kirsten Ziman. Our work was
-supported in part by NSF CAREER Award Number 2145172 to JRM. The content is
-solely the responsibility of the authors and does not necessarily represent the
-official views of our supporting organizations. The funders had no role in
-study design, data collection and analysis, decision to publish, or preparation
-of the manuscript.
+(unpublished) version of this study, and assistance with data collection
+efforts from Will Baxley, Max Bluestone, Daniel Carstensen, Kunal Jha, Caroline
+Lee, Lucy Owen, Xinming Xu, and Kirsten Ziman. Our work was supported in part
+by NSF CAREER Award Number 2145172 to JRM. The content is solely the
+responsibility of the authors and does not necessarily represent the official
+views of our supporting organizations. The funders had no role in study design,
+data collection and analysis, decision to publish, or preparation of the
+manuscript.
 

### 2023-10-22 paper/main.tex

@@
 The difference between ``understanding'' and ``memorizing,'' as framed by
-researchers in education, cognitive psychology, and cognitive
-neuroscience (e.g.,~\citealp{Kato40, Gall00, ScotEtal07, HallGree08, Macl05}),
-has profound analogs in the fields of natural language processing and natural
-language understanding. For example, considering the raw contents of a document
-(e.g., its constituent symbols, letters, and words) might provide some
-clues as to what the document is about, just as memorizing a passage
-might provide some ability to answer simple questions about it. However, text
-embedding models (e.g.,~\citealp{LandDuma97, DeerEtal90, BleiEtal03,
-BleiLaff06, MikoEtal13a, CerEtal18, BrowEtal20}) also attempt to capture the
-deeper meaning \textit{underlying} those atomic elements. These models consider
-not only the co-occurrences of those elements within and across documents, but
-also patterns in how those elements appear across different scales (e.g.,
-sentences, paragraphs, chapters, etc.), the temporal and grammatical properties
-of the elements, and other high-level characteristics of how they are
-used~\citep{Mann20, Mann21a}. According to these models, the deep conceptual
-meaning of a document may be captured by a feature vector in a high-dimensional
-representation space, wherein nearby vectors reflect conceptually related
-documents. A model that succeeds at capturing an analogue of ``understanding'' is
-able to assign nearby feature vectors to two conceptually related documents,
-\textit{even when the specific words contained in those documents have very little
-overlap}.
+researchers in education, cognitive psychology, and cognitive neuroscience
+(e.g.,~\citealp{Kato40, Gall00, ScotEtal07, HallGree08, Macl05}), has profound
+analogs in the fields of natural language processing and natural language
+understanding. For example, considering the raw contents of a document (e.g.,
+its constituent symbols, letters, and words) might provide some clues as to
+what the document is about, just as memorizing a passage might provide some
+ability to answer simple questions about it. However, text embedding models
+(e.g.,~\citealp{LandDuma97, DeerEtal90, BleiEtal03, BleiLaff06, MikoEtal13a,
+CerEtal18, BrowEtal20}) also attempt to capture the deeper meaning
+\textit{underlying} those atomic elements. These models consider not only the
+co-occurrences of those elements within and across documents, but (in many
+cases) also patterns in how those elements appear across different scales
+(e.g., sentences, paragraphs, chapters, etc.), the temporal and grammatical
+properties of the elements, and other high-level characteristics of how they
+are used~\citep{Mann20, Mann21a}. According to these models, the deep
+conceptual meaning of a document may be captured by a feature vector in a
+high-dimensional representation space, wherein nearby vectors reflect
+conceptually related documents. A model that succeeds at capturing an analogue
+of ``understanding'' is able to assign nearby feature vectors to two
+conceptually related documents, \textit{even when the specific words contained
+in those documents have very little overlap}.
 
 Given these insights, what form might a representation of the sum total of a
-person's knowledge take? First, we might require a means of systematically
-describing or representing the nearly infinite set of possible things a person
-could know. Second, we might want to account for potential associations between
-different concepts. For example, the concepts of ``fish'' and ``water'' might
-be associated in the sense that fish live in water. Third, knowledge may have a
-critical dependency structure, such that knowing about a particular concept
-might require first knowing about a set of other concepts. For example,
-understanding the concept of a fish swimming in water first requires
-understanding what fish and water \textit{are}. Fourth, as we learn, our
-``current state of knowledge'' should change accordingly. Learning new concepts
-should both update our characterizations of ``what is known'' and also
+person's knowledge take (speculatively)? First, we might require a means of
+systematically describing or representing the nearly infinite set of possible
+things a person could know. Second, we might want to account for potential
+associations between different concepts. For example, the concepts of ``fish''
+and ``water'' might be associated in the sense that fish live in water. Third,
+knowledge may have a critical dependency structure, such that knowing about a
+particular concept might require first knowing about a set of other concepts.
+For example, understanding the concept of a fish swimming in water first
+requires understanding what fish and water \textit{are}. Fourth, as we learn,
+our ``current state of knowledge'' should change accordingly. Learning new
+concepts should both update our characterizations of ``what is known'' and also
 unlock any now-satisfied dependencies of those newly learned concepts so that
@@
 \end{figure}
+
+It is important to clarify that although we use topic model-derived embeddings
+to \textit{characterize} the conceptual content of the lectures and questions,
+we do not claim that the topic model itself \textit{understands} the conceptual
+content of the lectures or questions. Rather, we view the topic model as a tool
+for capturing the \textit{structure} of the conceptual content of the lectures
+and questions in a way that enables us to capture, quantify, and track and
+predict participants' knowledge.
 
@@
 changes with training (Fig.~\ref{fig:knowledge-maps}).
+
+We view our work as making several contributions to the study of how people
+acquire conceptual knowledge. First, from a methodological standpoint, our
+modeling framework provides a systematic means of mapping out and
+characterizing knowledge in maps that have infinite (arbitrarily many) numbers
+of coordinates, and of ``filling out'' those maps using relatively small
+numbers of multiple choice quiz questions. Our experimental finding that we can
+use these maps to predict responses to held-out questions
+(Fig.~\ref{fig:predictions}) also has important psychological implications. One
+such psychological implication is that concepts that are assigned to nearby
+coordinates by the text embedding model also appear to be ``known to a similar
+extent'' (as reflected by participants' responses to held-out questions). This
+suggests that participants also \textit{conceptualize} similarly the content
+reflected by nearby embedding coordinates. A second psychological implication
+is that something about how participants' knowledge ``spreads'' across concepts
+is being captured by the knowledge maps we are inferring from their quiz
+responses (e.g., Fig.~\ref{fig:smoothness}). In other words, our study shows
+that knowledge about a given concept implies knowledge about related concepts.
 
@@
 about basic physics (covering material that was not presented in either video).
-The full set of questions and answer choices may be found in Supplementary
-Table~\questions.
+We note that estimating the specific ``amount'' of conceptual understanding
+that each question ``requires'' to answer is somewhat subjective, and might
+even come down to the ``strategy'' a given participant uses to answer the
+question at that particular moment. The full set of questions and answer
+choices may be found in Supplementary Table~\questions.
 

### 2023-10-23 paper/supplement.tex
added BERT comparison figure to supplement
new supplementary figs 3 & 4
caught some missing ellipses in supp tab 3

--- 2023-10-22 paper/supplement.tex
@@
 \\\hline
-6  &          FFF &                                                                                                                                                                                                  Electricity and magnetism can be shown to be two cases of the same force if we: &                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                          \textbf{[04:34.28--05:52.61]} ...times the strength of gravity 10 to 36 times the strength of gravity so it kind of puts the weak force in its place it's 10 to the 12 times stronger than the weak force so these are huge numbers that we're talking about either this relative that or even this relative to gravity and so you might be saying well you know the electromagnetic force that's unbelievably strong why doesn't that apply over over over these these kind of macro scales like gravity let me write there macro scales macro scales why doesn't it apply to macro scales and actually there's nothing about the electromagnetic force why it can't it or it actually does apply over large distances the reality though is you don't have these huge concentrations of either electric Ullom charges or magnetism the way you do mass so the mass that you have such huge concentrations it can operate over huge huge distances even though it's way way way weaker than the electromagnetic force the electromagnetic force what happens is because it's both attractive and repulsive it tends to kind of sort itself out so you don't have these huge huge huge concentrations of charge now the other thing you might be wondering about is you know why is it called the electromagnetic force in our everyday life there's things like there's things like the Coulomb force that or the electrostatic force which we're familiar\newline\textbf{[06:37.31--07:28.1]} ...that the cool force the electrostatic force and the magnetic force are actually the same thing viewed in different frames of references so I won't go into a lot of detail but just keep that in the back of your mind that they are connected in a future video I'll go more into the intuition of how they are connected and it deals with when what it's more apparent when they're moving when the charges are moving at relativistic frames and you have well I will go to a lot of detail there but just keep in mind that they really are the same force just viewed from different frames of reference now the strongest of the force is probably the best name of them all and that's the strong force that is the strong force the strong force and although you probably haven't seen this yet in our in chemistry classes it actually applies very strongly in...
+6  &          FFF &                                                                                                                                                                                                  Electricity and magnetism can be shown to be two cases of the same force if we: &                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                          \textbf{[04:34.28--05:52.61]} ...times the strength of gravity 10 to 36 times the strength of gravity so it kind of puts the weak force in its place it's 10 to the 12 times stronger than the weak force so these are huge numbers that we're talking about either this relative that or even this relative to gravity and so you might be saying well you know the electromagnetic force that's unbelievably strong why doesn't that apply over over over these these kind of macro scales like gravity let me write there macro scales macro scales why doesn't it apply to macro scales and actually there's nothing about the electromagnetic force why it can't it or it actually does apply over large distances the reality though is you don't have these huge concentrations of either electric Ullom charges or magnetism the way you do mass so the mass that you have such huge concentrations it can operate over huge huge distances even though it's way way way weaker than the electromagnetic force the electromagnetic force what happens is because it's both attractive and repulsive it tends to kind of sort itself out so you don't have these huge huge huge concentrations of charge now the other thing you might be wondering about is you know why is it called the electromagnetic force in our everyday life there's things like there's things like the Coulomb force that or the electrostatic force which we're familiar...\newline\textbf{[06:37.31--07:28.1]} ...that the cool force the electrostatic force and the magnetic force are actually the same thing viewed in different frames of references so I won't go into a lot of detail but just keep that in the back of your mind that they are connected in a future video I'll go more into the intuition of how they are connected and it deals with when what it's more apparent when they're moving when the charges are moving at relativistic frames and you have well I will go to a lot of detail there but just keep in mind that they really are the same force just viewed from different frames of reference now the strongest of the force is probably the best name of them all and that's the strong force that is the strong force the strong force and although you probably haven't seen this yet in our in chemistry classes it actually applies very strongly in...
 \\\hline
 7  &          FFF &                                                                                                                                  Which of the following are the primary two fundamental forces acting in opposition between the positively-charged protons in an atom's nucleus?
-&                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                              \textbf{[00:00.03--01:33.509]} what I want to do in this video is give a very high-level overview of the four fundamental forces four fundamental forces of the universe and I'm going to start with gravity I'm going to start with gravity and it might surprise some of you that gravity is actually the weakest of the four fundamental forces that's surprising because you say wow that's what keeps us glued not glued but it keeps us from jumping off the planet it's what keeps the moon in orbit around the earth the earth in orbit around the Sun the Sun in orbit around the the center of the Milky Way galaxy so it's it's a little bit surprising that it's actually the weakest of the forces and and that starts to make sense when you actually think about things on maybe more of a human scale or a molecular scale or even an atomic scale even on a human scale your computer monitor and you have some type of gravitational attraction but you don't notice it or your cell phone and your wallet there's gravitational attraction but you don't see them being drawn to each other the way you might see two magnets drawn to each other or repelled from each other and if you've got even a smaller scale you'll see that it matters even less we never even talk about gravity and chemistry although the gravity is there but at those scales the other forces really really really start to dominate so gravity's are weakest so if we move up a little bit from that we get and this is maybe the the hardest force for us to visualize or at least the hardest the least intuitive force for me is actually the weak force the weak sometimes called the weak interaction\newline\textbf{[07:10.13--08:35.24]} ...reference now the strongest of the force is probably the best name of them all and that's the strong force that is the strong force the strong force and although you probably haven't seen this yet in our in chemistry classes it actually applies very strongly in chemistry because from the get-go when you first learn when you first learn about atoms let me draw a helium atom a helium atom has two protons and it's nucleus two protons in its nucleus and it has two neutrons and then it also has two electrons circulating around so it has an electron and I can draw the electrons is much smaller than well I won't I won't try to do anything in relative size but it has two electrons floating around and one question that may or may not have jumped into your mind when you first saw this model of an atom is like well I see why the electrons are attracted to the nucleus it has a negative Coulomb charge the nucleus has a net positive Coulomb charge but what's not so obvious and that what tends not to sometimes be explained in chemistry class is these two positive charges are sitting right next to each other if the electromagnetic force was the only force in play if the Coulomb force was the only thing happening these guys would just run away from each other they would repel each other and so the only reason why they're able to stick to each other is that there's an even stronger force than the electromagnetic force operating at these very very very small distances...
+&                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                              \textbf{[00:00.03--01:33.509]} what I want to do in this video is give a very high-level overview of the four fundamental forces four fundamental forces of the universe and I'm going to start with gravity I'm going to start with gravity and it might surprise some of you that gravity is actually the weakest of the four fundamental forces that's surprising because you say wow that's what keeps us glued not glued but it keeps us from jumping off the planet it's what keeps the moon in orbit around the earth the earth in orbit around the Sun the Sun in orbit around the the center of the Milky Way galaxy so it's it's a little bit surprising that it's actually the weakest of the forces and and that starts to make sense when you actually think about things on maybe more of a human scale or a molecular scale or even an atomic scale even on a human scale your computer monitor and you have some type of gravitational attraction but you don't notice it or your cell phone and your wallet there's gravitational attraction but you don't see them being drawn to each other the way you might see two magnets drawn to each other or repelled from each other and if you've got even a smaller scale you'll see that it matters even less we never even talk about gravity and chemistry although the gravity is there but at those scales the other forces really really really start to dominate so gravity's are weakest so if we move up a little bit from that we get and this is maybe the the hardest force for us to visualize or at least the hardest the least intuitive force for me is actually the weak force the weak sometimes called the weak interaction...\newline\textbf{[07:10.13--08:35.24]} ...reference now the strongest of the force is probably the best name of them all and that's the strong force that is the strong force the strong force and although you probably haven't seen this yet in our in chemistry classes it actually applies very strongly in chemistry because from the get-go when you first learn when you first learn about atoms let me draw a helium atom a helium atom has two protons and it's nucleus two protons in its nucleus and it has two neutrons and then it also has two electrons circulating around so it has an electron and I can draw the electrons is much smaller than well I won't I won't try to do anything in relative size but it has two electrons floating around and one question that may or may not have jumped into your mind when you first saw this model of an atom is like well I see why the electrons are attracted to the nucleus it has a negative Coulomb charge the nucleus has a net positive Coulomb charge but what's not so obvious and that what tends not to sometimes be explained in chemistry class is these two positive charges are sitting right next to each other if the electromagnetic force was the only force in play if the Coulomb force was the only thing happening these guys would just run away from each other they would repel each other and so the only reason why they're able to stick to each other is that there's an even stronger force than the electromagnetic force operating at these very very very small distances...
 \\\hline
@@
 Which of the following explains why?
-&  \textbf{[00:00.03--01:33.509]} what I want to do in this video is give a very high-level overview of the four fundamental forces four fundamental forces of the universe and I'm going to start with gravity I'm going to start with gravity and it might surprise some of you that gravity is actually the weakest of the four fundamental forces that's surprising because you say wow that's what keeps us glued not glued but it keeps us from jumping off the planet it's what keeps the moon in orbit around the earth the earth in orbit around the Sun the Sun in orbit around the the center of the Milky Way galaxy so it's it's a little bit surprising that it's actually the weakest of the forces and and that starts to make sense when you actually think about things on maybe more of a human scale or a molecular scale or even an atomic scale even on a human scale your computer monitor and you have some type of gravitational attraction but you don't notice it or your cell phone and your wallet there's gravitational attraction but you don't see them being drawn to each other the way you might see two magnets drawn to each other or repelled from each other and if you've got even a smaller scale you'll see that it matters even less we never even talk about gravity and chemistry although the gravity is there but at those scales the other forces really really really start to dominate so gravity's are weakest so if we move up a little bit from that we get and this is maybe the the hardest force for us to visualize or at least the hardest the least intuitive force for me is actually the weak force the weak sometimes called the weak interaction\newline\textbf{[05:32.6--08:33.14]} ...force the electromagnetic force what happens is because it's both attractive and repulsive it tends to kind of sort itself out so you don't have these huge huge huge concentrations of charge now the other thing you might be wondering about is you know why is it called the electromagnetic force in our everyday life there's things like there's things like the Coulomb force that or the electrostatic force which we're familiar with positive charges or like charges want to repel if both of these were negative the same thing would be happening and different charges like to attract we've seen this multiple times this is the Coulomb force or the electrostatic force electro static and then on the other side of the word yes you have the magnetic part and magnets you know you have you've played with magnets on your fridge they what's what you know if they're the same side of the magnet they're going to repel each other if they're the opposite sides opposite poles they're going to attract each other so why is it called one force and it's called one force and once again I'm not going to go into detail here it's called one force because it turns out that the cool force the electrostatic force and the magnetic force are actually the same thing viewed in different frames of references so I won't go into a lot of detail but just keep that in the back of your mind that they are connected in a future video I'll go more into the intuition of how they are connected and it deals with when what it's more apparent when they're moving when the charges are moving at relativistic frames and you have well I will go to a lot of detail there but just keep in mind that they really are the same force just viewed from different frames of reference now the strongest of the force is probably the best name of them all and that's the strong force that is the strong force the strong force and although you probably haven't seen this yet in our in chemistry classes it actually applies very strongly in chemistry because from the get-go when you first learn when you first learn about atoms let me draw a helium atom a helium atom has two protons and it's nucleus two protons in its nucleus and it has two neutrons and then it also has two electrons circulating around so it has an electron and I can draw the electrons is much smaller than well I won't I won't try to do anything in relative size but it has two electrons floating around and one question that may or may not have jumped into your mind when you first saw this model of an atom is like well I see why the electrons are attracted to the nucleus it has a negative Coulomb charge the nucleus has a net positive Coulomb charge but what's not so obvious and that what tends not to sometimes be explained in chemistry class is these two positive charges are sitting right next to each other if the electromagnetic force was the only force in play if the Coulomb force was the only thing happening these guys would just run away from each other they would repel each other and so the only reason why they're able to stick to each other is that there's an even stronger force than the electromagnetic force operating...
+&  \textbf{[00:00.03--01:33.509]} what I want to do in this video is give a very high-level overview of the four fundamental forces four fundamental forces of the universe and I'm going to start with gravity I'm going to start with gravity and it might surprise some of you that gravity is actually the weakest of the four fundamental forces that's surprising because you say wow that's what keeps us glued not glued but it keeps us from jumping off the planet it's what keeps the moon in orbit around the earth the earth in orbit around the Sun the Sun in orbit around the the center of the Milky Way galaxy so it's it's a little bit surprising that it's actually the weakest of the forces and and that starts to make sense when you actually think about things on maybe more of a human scale or a molecular scale or even an atomic scale even on a human scale your computer monitor and you have some type of gravitational attraction but you don't notice it or your cell phone and your wallet there's gravitational attraction but you don't see them being drawn to each other the way you might see two magnets drawn to each other or repelled from each other and if you've got even a smaller scale you'll see that it matters even less we never even talk about gravity and chemistry although the gravity is there but at those scales the other forces really really really start to dominate so gravity's are weakest so if we move up a little bit from that we get and this is maybe the the hardest force for us to visualize or at least the hardest the least intuitive force for me is actually the weak force the weak sometimes called the weak interaction...\newline\textbf{[05:32.6--08:33.14]} ...force the electromagnetic force what happens is because it's both attractive and repulsive it tends to kind of sort itself out so you don't have these huge huge huge concentrations of charge now the other thing you might be wondering about is you know why is it called the electromagnetic force in our everyday life there's things like there's things like the Coulomb force that or the electrostatic force which we're familiar with positive charges or like charges want to repel if both of these were negative the same thing would be happening and different charges like to attract we've seen this multiple times this is the Coulomb force or the electrostatic force electro static and then on the other side of the word yes you have the magnetic part and magnets you know you have you've played with magnets on your fridge they what's what you know if they're the same side of the magnet they're going to repel each other if they're the opposite sides opposite poles they're going to attract each other so why is it called one force and it's called one force and once again I'm not going to go into detail here it's called one force because it turns out that the cool force the electrostatic force and the magnetic force are actually the same thing viewed in different frames of references so I won't go into a lot of detail but just keep that in the back of your mind that they are connected in a future video I'll go more into the intuition of how they are connected and it deals with when what it's more apparent when they're moving when the charges are moving at relativistic frames and you have well I will go to a lot of detail there but just keep in mind that they really are the same force just viewed from different frames of reference now the strongest of the force is probably the best name of them all and that's the strong force that is the strong force the strong force and although you probably haven't seen this yet in our in chemistry classes it actually applies very strongly in chemistry because from the get-go when you first learn when you first learn about atoms let me draw a helium atom a helium atom has two protons and it's nucleus two protons in its nucleus and it has two neutrons and then it also has two electrons circulating around so it has an electron and I can draw the electrons is much smaller than well I won't I won't try to do anything in relative size but it has two electrons floating around and one question that may or may not have jumped into your mind when you first saw this model of an atom is like well I see why the electrons are attracted to the nucleus it has a negative Coulomb charge the nucleus has a net positive Coulomb charge but what's not so obvious and that what tends not to sometimes be explained in chemistry class is these two positive charges are sitting right next to each other if the electromagnetic force was the only force in play if the Coulomb force was the only thing happening these guys would just run away from each other they would repel each other and so the only reason why they're able to stick to each other is that there's an even stronger force than the electromagnetic force operating...
 \\\hline
@@
 17 &          BoS &                                                                                                                                                                                                               Which of the following occurs as a cloud of atoms gets more dense?
-&                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                             \textbf{[00:05.67--01:36.71]} ...and I say huge cloud huge both in distance and in mass if you were to combine all of the hydrogen atoms it would just be this really really massive thing so you have this huge cloud well we know that gravity would make the atoms actually attracted to each other instantly we normally don't think about the gravity of atoms but it would slowly affect these atoms and they'd slowly draw close to each other it would slowly condense they'd slowly they slowly move towards the center of mass of all of the atoms they'd slowly move in and so if we fast forward if we fast forward this cloud is going to get denser and denser it's going to get denser and denser and the hydrogen atoms are going to start bumping into each other and rubbing up against each other and interacting with each other and so it's going to get denser and denser and denser and remember was a huge mass of hydrogen atoms so the temperature is going up the temperature is going up and it'll they'll keep condensing they'll just keep condensing and condensing until something really interesting happens so let's imagine that they've gotten really dense here in the center they've gotten really dense here in the center and there's a bunch of hydrogen atoms all over it's really dense I could never draw the actual number of atoms here this is really give you an idea there's a huge amount of inward pressure from gravity from everything that wants to get to that center of mass of our entire cloud the temperature here the temperature here is approaching 10 million Kelvin and at that point\newline\textbf{[06:50.68--07:52.81]} ...there's there's questions of well what if what if there just wasn't enough mass to get to this level over here and there actually are things that never get to that quite that threshold to fuse all the way into helium there are a few things that don't quite make the threshold of stars that only fuse to this level so they are generating some of their eat or there are even smaller objects that just get to the point there's a huge temperature and pressure but fusion is not actually occurring inside of the core and something like Jupiter would be an example and you can go several several masses above Jupiter where you get something like that so you have to reach a certain threshold or the mass where the pressure and the temperature due to the heavy mass gets so large that you start this fusion at but the smaller you have above that threshold this the slower the fusion will occur but if you're supermassive the fusion will occur really really fast so that's a general idea of just how stars get formed and why they don't collapse on themselves and why they are these kind of little balls of fusion reactions existing in the universe and the next few videos we'll talk about what happens once that hydrogen fuel and the cure in the core starts to run out...
+&                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                             \textbf{[00:05.67--01:36.71]} ...and I say huge cloud huge both in distance and in mass if you were to combine all of the hydrogen atoms it would just be this really really massive thing so you have this huge cloud well we know that gravity would make the atoms actually attracted to each other instantly we normally don't think about the gravity of atoms but it would slowly affect these atoms and they'd slowly draw close to each other it would slowly condense they'd slowly they slowly move towards the center of mass of all of the atoms they'd slowly move in and so if we fast forward if we fast forward this cloud is going to get denser and denser it's going to get denser and denser and the hydrogen atoms are going to start bumping into each other and rubbing up against each other and interacting with each other and so it's going to get denser and denser and denser and remember was a huge mass of hydrogen atoms so the temperature is going up the temperature is going up and it'll they'll keep condensing they'll just keep condensing and condensing until something really interesting happens so let's imagine that they've gotten really dense here in the center they've gotten really dense here in the center and there's a bunch of hydrogen atoms all over it's really dense I could never draw the actual number of atoms here this is really give you an idea there's a huge amount of inward pressure from gravity from everything that wants to get to that center of mass of our entire cloud the temperature here the temperature here is approaching 10 million Kelvin and at that point...\newline\textbf{[06:50.68--07:52.81]} ...there's there's questions of well what if what if there just wasn't enough mass to get to this level over here and there actually are things that never get to that quite that threshold to fuse all the way into helium there are a few things that don't quite make the threshold of stars that only fuse to this level so they are generating some of their eat or there are even smaller objects that just get to the point there's a huge temperature and pressure but fusion is not actually occurring inside of the core and something like Jupiter would be an example and you can go several several masses above Jupiter where you get something like that so you have to reach a certain threshold or the mass where the pressure and the temperature due to the heavy mass gets so large that you start this fusion at but the smaller you have above that threshold this the slower the fusion will occur but if you're supermassive the fusion will occur really really fast so that's a general idea of just how stars get formed and why they don't collapse on themselves and why they are these kind of little balls of fusion reactions existing in the universe and the next few videos we'll talk about what happens once that hydrogen fuel and the cure in the core starts to run out...
 \\\hline
 18 &          BoS &                                                                                                                                                                   Which temperature does a cloud of hydrogen atoms approach as it gets denser in the process of becoming a star?
-&                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                            \textbf{[00:05.67--01:47.82]} ...and I say huge cloud huge both in distance and in mass if you were to combine all of the hydrogen atoms it would just be this really really massive thing so you have this huge cloud well we know that gravity would make the atoms actually attracted to each other instantly we normally don't think about the gravity of atoms but it would slowly affect these atoms and they'd slowly draw close to each other it would slowly condense they'd slowly they slowly move towards the center of mass of all of the atoms they'd slowly move in and so if we fast forward if we fast forward this cloud is going to get denser and denser it's going to get denser and denser and the hydrogen atoms are going to start bumping into each other and rubbing up against each other and interacting with each other and so it's going to get denser and denser and denser and remember was a huge mass of hydrogen atoms so the temperature is going up the temperature is going up and it'll they'll keep condensing they'll just keep condensing and condensing until something really interesting happens so let's imagine that they've gotten really dense here in the center they've gotten really dense here in the center and there's a bunch of hydrogen atoms all over it's really dense I could never draw the actual number of atoms here this is really give you an idea there's a huge amount of inward pressure from gravity from everything that wants to get to that center of mass of our entire cloud the temperature here the temperature here is approaching 10 million Kelvin and at that point something neat happens it to kind of realize the neat thing that's happening let's remember what a hydrogen atom looks like a hydrogen and even more I'm just going to focus on the hydrogen\newline\textbf{[05:50.32--07:00.25]} ...helium and by definition helium has two protons and two neutrons so it has or we're talking about helium four in particular that isotope of helium it has an atomic mass of four and the whole this process releases a ton of energy because the atomic mass of the helium that gets produced is slightly lower than four of its of the atomic four times the atomic mass of each of the Constituent hydrogen's so all of this energy all of this energy from the fusion but it needs super high pressure super high temperatures to happen keeps keeps the star from collapsing and once the star is in in this stage once it is once it is using hydrogen it is fusing hydrogen in its core where the pressure and the temperatures of most to form helium it is now in its main sequence this is now a main sequence star main main sequence star and that's actually where the Sun is right now now there's there's questions of well what if what if there just wasn't enough mass to get to this level over here and there actually are things that never get to that quite that threshold to fuse all the way into helium there are a few...
+&                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                            \textbf{[00:05.67--01:47.82]} ...and I say huge cloud huge both in distance and in mass if you were to combine all of the hydrogen atoms it would just be this really really massive thing so you have this huge cloud well we know that gravity would make the atoms actually attracted to each other instantly we normally don't think about the gravity of atoms but it would slowly affect these atoms and they'd slowly draw close to each other it would slowly condense they'd slowly they slowly move towards the center of mass of all of the atoms they'd slowly move in and so if we fast forward if we fast forward this cloud is going to get denser and denser it's going to get denser and denser and the hydrogen atoms are going to start bumping into each other and rubbing up against each other and interacting with each other and so it's going to get denser and denser and denser and remember was a huge mass of hydrogen atoms so the temperature is going up the temperature is going up and it'll they'll keep condensing they'll just keep condensing and condensing until something really interesting happens so let's imagine that they've gotten really dense here in the center they've gotten really dense here in the center and there's a bunch of hydrogen atoms all over it's really dense I could never draw the actual number of atoms here this is really give you an idea there's a huge amount of inward pressure from gravity from everything that wants to get to that center of mass of our entire cloud the temperature here the temperature here is approaching 10 million Kelvin and at that point something neat happens it to kind of realize the neat thing that's happening let's remember what a hydrogen atom looks like a hydrogen and even more I'm just going to focus on the hydrogen...\newline\textbf{[05:50.32--07:00.25]} ...helium and by definition helium has two protons and two neutrons so it has or we're talking about helium four in particular that isotope of helium it has an atomic mass of four and the whole this process releases a ton of energy because the atomic mass of the helium that gets produced is slightly lower than four of its of the atomic four times the atomic mass of each of the Constituent hydrogen's so all of this energy all of this energy from the fusion but it needs super high pressure super high temperatures to happen keeps keeps the star from collapsing and once the star is in in this stage once it is once it is using hydrogen it is fusing hydrogen in its core where the pressure and the temperatures of most to form helium it is now in its main sequence this is now a main sequence star main main sequence star and that's actually where the Sun is right now now there's there's questions of well what if what if there just wasn't enough mass to get to this level over here and there actually are things that never get to that quite that threshold to fuse all the way into helium there are a few...
 \\\hline
@@
 22 &          BoS &                                                                                                                                                                                               Which of the following is the FIRST product of two hydrogen atoms fusing together?
-&                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                \textbf{[00:05.67--01:36.71]} ...and I say huge cloud huge both in distance and in mass if you were to combine all of the hydrogen atoms it would just be this really really massive thing so you have this huge cloud well we know that gravity would make the atoms actually attracted to each other instantly we normally don't think about the gravity of atoms but it would slowly affect these atoms and they'd slowly draw close to each other it would slowly condense they'd slowly they slowly move towards the center of mass of all of the atoms they'd slowly move in and so if we fast forward if we fast forward this cloud is going to get denser and denser it's going to get denser and denser and the hydrogen atoms are going to start bumping into each other and rubbing up against each other and interacting with each other and so it's going to get denser and denser and denser and remember was a huge mass of hydrogen atoms so the temperature is going up the temperature is going up and it'll they'll keep condensing they'll just keep condensing and condensing until something really interesting happens so let's imagine that they've gotten really dense here in the center they've gotten really dense here in the center and there's a bunch of hydrogen atoms all over it's really dense I could never draw the actual number of atoms here this is really give you an idea there's a huge amount of inward pressure from gravity from everything that wants to get to that center of mass of our entire cloud the temperature here the temperature here is approaching 10 million Kelvin and at that point\newline\textbf{[02:24.67--03:53.08]} ...learned about the four force is that if they did get close enough to each other that if they did get if somehow they're under huge temperatures and huge pressures you were able to get these two protons close enough to each other then all of a sudden the strong force will overtake it's much stronger than the Coulomb force and that these two hydrogen's will actually these this these nucleuses would actually fuse or that nuclei well anyway they would actually fuse together and so that is what actually happens once this gets hot and dense enough you now have enough pressure enough temperature to overcome the Coulomb force and bring these protons close enough to each other for fusion to occur for fusion fusion ignition ignition and the reason why is and I want to be very careful it's not ignition it's not combustion in the traditional sense it's not like you're burning a carbon molecule with out in the presence of oxygen it's not combustion it's ignition and the reason why it's called ignition is because when two of these protons or two of the nucleus is fuse the resulting the resulting nucleus has a slightly smaller mass and so in the first stage of this you actually have you actually have two protons two protons under enough pressure obviously this would not happen with just the Coulomb forces at with enough pressure to get close enough and then the strong interaction actually actually keeps them together one of these guys degrades in a neutron degrades into a neutron and the...
+&                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                \textbf{[00:05.67--01:36.71]} ...and I say huge cloud huge both in distance and in mass if you were to combine all of the hydrogen atoms it would just be this really really massive thing so you have this huge cloud well we know that gravity would make the atoms actually attracted to each other instantly we normally don't think about the gravity of atoms but it would slowly affect these atoms and they'd slowly draw close to each other it would slowly condense they'd slowly they slowly move towards the center of mass of all of the atoms they'd slowly move in and so if we fast forward if we fast forward this cloud is going to get denser and denser it's going to get denser and denser and the hydrogen atoms are going to start bumping into each other and rubbing up against each other and interacting with each other and so it's going to get denser and denser and denser and remember was a huge mass of hydrogen atoms so the temperature is going up the temperature is going up and it'll they'll keep condensing they'll just keep condensing and condensing until something really interesting happens so let's imagine that they've gotten really dense here in the center they've gotten really dense here in the center and there's a bunch of hydrogen atoms all over it's really dense I could never draw the actual number of atoms here this is really give you an idea there's a huge amount of inward pressure from gravity from everything that wants to get to that center of mass of our entire cloud the temperature here the temperature here is approaching 10 million Kelvin and at that point...\newline\textbf{[02:24.67--03:53.08]} ...learned about the four force is that if they did get close enough to each other that if they did get if somehow they're under huge temperatures and huge pressures you were able to get these two protons close enough to each other then all of a sudden the strong force will overtake it's much stronger than the Coulomb force and that these two hydrogen's will actually these this these nucleuses would actually fuse or that nuclei well anyway they would actually fuse together and so that is what actually happens once this gets hot and dense enough you now have enough pressure enough temperature to overcome the Coulomb force and bring these protons close enough to each other for fusion to occur for fusion fusion ignition ignition and the reason why is and I want to be very careful it's not ignition it's not combustion in the traditional sense it's not like you're burning a carbon molecule with out in the presence of oxygen it's not combustion it's ignition and the reason why it's called ignition is because when two of these protons or two of the nucleus is fuse the resulting the resulting nucleus has a slightly smaller mass and so in the first stage of this you actually have you actually have two protons two protons under enough pressure obviously this would not happen with just the Coulomb forces at with enough pressure to get close enough and then the strong interaction actually actually keeps them together one of these guys degrades in a neutron degrades into a neutron and the...
 \\\hline
 23 &          BoS &                                                                                                                                                                                       Once hydrogen atoms get close enough together, which of the following keeps them together?
-&                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                \textbf{[00:05.67--01:36.71]} ...and I say huge cloud huge both in distance and in mass if you were to combine all of the hydrogen atoms it would just be this really really massive thing so you have this huge cloud well we know that gravity would make the atoms actually attracted to each other instantly we normally don't think about the gravity of atoms but it would slowly affect these atoms and they'd slowly draw close to each other it would slowly condense they'd slowly they slowly move towards the center of mass of all of the atoms they'd slowly move in and so if we fast forward if we fast forward this cloud is going to get denser and denser it's going to get denser and denser and the hydrogen atoms are going to start bumping into each other and rubbing up against each other and interacting with each other and so it's going to get denser and denser and denser and remember was a huge mass of hydrogen atoms so the temperature is going up the temperature is going up and it'll they'll keep condensing they'll just keep condensing and condensing until something really interesting happens so let's imagine that they've gotten really dense here in the center they've gotten really dense here in the center and there's a bunch of hydrogen atoms all over it's really dense I could never draw the actual number of atoms here this is really give you an idea there's a huge amount of inward pressure from gravity from everything that wants to get to that center of mass of our entire cloud the temperature here the temperature here is approaching 10 million Kelvin and at that point\newline\textbf{[02:24.67--03:53.08]} ...learned about the four force is that if they did get close enough to each other that if they did get if somehow they're under huge temperatures and huge pressures you were able to get these two protons close enough to each other then all of a sudden the strong force will overtake it's much stronger than the Coulomb force and that these two hydrogen's will actually these this these nucleuses would actually fuse or that nuclei well anyway they would actually fuse together and so that is what actually happens once this gets hot and dense enough you now have enough pressure enough temperature to overcome the Coulomb force and bring these protons close enough to each other for fusion to occur for fusion fusion ignition ignition and the reason why is and I want to be very careful it's not ignition it's not combustion in the traditional sense it's not like you're burning a carbon molecule with out in the presence of oxygen it's not combustion it's ignition and the reason why it's called ignition is because when two of these protons or two of the nucleus is fuse the resulting the resulting nucleus has a slightly smaller mass and so in the first stage of this you actually have you actually have two protons two protons under enough pressure obviously this would not happen with just the Coulomb forces at with enough pressure to get close enough and then the strong interaction actually actually keeps them together one of these guys degrades in a neutron degrades into a neutron and the...
+&                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                \textbf{[00:05.67--01:36.71]} ...and I say huge cloud huge both in distance and in mass if you were to combine all of the hydrogen atoms it would just be this really really massive thing so you have this huge cloud well we know that gravity would make the atoms actually attracted to each other instantly we normally don't think about the gravity of atoms but it would slowly affect these atoms and they'd slowly draw close to each other it would slowly condense they'd slowly they slowly move towards the center of mass of all of the atoms they'd slowly move in and so if we fast forward if we fast forward this cloud is going to get denser and denser it's going to get denser and denser and the hydrogen atoms are going to start bumping into each other and rubbing up against each other and interacting with each other and so it's going to get denser and denser and denser and remember was a huge mass of hydrogen atoms so the temperature is going up the temperature is going up and it'll they'll keep condensing they'll just keep condensing and condensing until something really interesting happens so let's imagine that they've gotten really dense here in the center they've gotten really dense here in the center and there's a bunch of hydrogen atoms all over it's really dense I could never draw the actual number of atoms here this is really give you an idea there's a huge amount of inward pressure from gravity from everything that wants to get to that center of mass of our entire cloud the temperature here the temperature here is approaching 10 million Kelvin and at that point...\newline\textbf{[02:24.67--03:53.08]} ...learned about the four force is that if they did get close enough to each other that if they did get if somehow they're under huge temperatures and huge pressures you were able to get these two protons close enough to each other then all of a sudden the strong force will overtake it's much stronger than the Coulomb force and that these two hydrogen's will actually these this these nucleuses would actually fuse or that nuclei well anyway they would actually fuse together and so that is what actually happens once this gets hot and dense enough you now have enough pressure enough temperature to overcome the Coulomb force and bring these protons close enough to each other for fusion to occur for fusion fusion ignition ignition and the reason why is and I want to be very careful it's not ignition it's not combustion in the traditional sense it's not like you're burning a carbon molecule with out in the presence of oxygen it's not combustion it's ignition and the reason why it's called ignition is because when two of these protons or two of the nucleus is fuse the resulting the resulting nucleus has a slightly smaller mass and so in the first stage of this you actually have you actually have two protons two protons under enough pressure obviously this would not happen with just the Coulomb forces at with enough pressure to get close enough and then the strong interaction actually actually keeps them together one of these guys degrades in a neutron degrades into a neutron and the...
 \\\hline
@@
 26 &          BoS &                                                                                                                                                                                                      Which force would cause a massive cloud of hydrogen atoms to move together?
-&                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                        \textbf{[00:05.67--01:36.71]} ...and I say huge cloud huge both in distance and in mass if you were to combine all of the hydrogen atoms it would just be this really really massive thing so you have this huge cloud well we know that gravity would make the atoms actually attracted to each other instantly we normally don't think about the gravity of atoms but it would slowly affect these atoms and they'd slowly draw close to each other it would slowly condense they'd slowly they slowly move towards the center of mass of all of the atoms they'd slowly move in and so if we fast forward if we fast forward this cloud is going to get denser and denser it's going to get denser and denser and the hydrogen atoms are going to start bumping into each other and rubbing up against each other and interacting with each other and so it's going to get denser and denser and denser and remember was a huge mass of hydrogen atoms so the temperature is going up the temperature is going up and it'll they'll keep condensing they'll just keep condensing and condensing until something really interesting happens so let's imagine that they've gotten really dense here in the center they've gotten really dense here in the center and there's a bunch of hydrogen atoms all over it's really dense I could never draw the actual number of atoms here this is really give you an idea there's a huge amount of inward pressure from gravity from everything that wants to get to that center of mass of our entire cloud the temperature here the temperature here is approaching 10 million Kelvin and at that point\newline\textbf{[02:26.05--03:51.37]} ...they did get close enough to each other that if they did get if somehow they're under huge temperatures and huge pressures you were able to get these two protons close enough to each other then all of a sudden the strong force will overtake it's much stronger than the Coulomb force and that these two hydrogen's will actually these this these nucleuses would actually fuse or that nuclei well anyway they would actually fuse together and so that is what actually happens once this gets hot and dense enough you now have enough pressure enough temperature to overcome the Coulomb force and bring these protons close enough to each other for fusion to occur for fusion fusion ignition ignition and the reason why is and I want to be very careful it's not ignition it's not combustion in the traditional sense it's not like you're burning a carbon molecule with out in the presence of oxygen it's not combustion it's ignition and the reason why it's called ignition is because when two of these protons or two of the nucleus is fuse the resulting the resulting nucleus has a slightly smaller mass and so in the first stage of this you actually have you actually have two protons two protons under enough pressure obviously this would not happen with just the Coulomb forces at with enough pressure to get close enough and then the strong interaction actually actually keeps them together one of these guys degrades in a neutron...
+&                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                        \textbf{[00:05.67--01:36.71]} ...and I say huge cloud huge both in distance and in mass if you were to combine all of the hydrogen atoms it would just be this really really massive thing so you have this huge cloud well we know that gravity would make the atoms actually attracted to each other instantly we normally don't think about the gravity of atoms but it would slowly affect these atoms and they'd slowly draw close to each other it would slowly condense they'd slowly they slowly move towards the center of mass of all of the atoms they'd slowly move in and so if we fast forward if we fast forward this cloud is going to get denser and denser it's going to get denser and denser and the hydrogen atoms are going to start bumping into each other and rubbing up against each other and interacting with each other and so it's going to get denser and denser and denser and remember was a huge mass of hydrogen atoms so the temperature is going up the temperature is going up and it'll they'll keep condensing they'll just keep condensing and condensing until something really interesting happens so let's imagine that they've gotten really dense here in the center they've gotten really dense here in the center and there's a bunch of hydrogen atoms all over it's really dense I could never draw the actual number of atoms here this is really give you an idea there's a huge amount of inward pressure from gravity from everything that wants to get to that center of mass of our entire cloud the temperature here the temperature here is approaching 10 million Kelvin and at that point...\newline\textbf{[02:26.05--03:51.37]} ...they did get close enough to each other that if they did get if somehow they're under huge temperatures and huge pressures you were able to get these two protons close enough to each other then all of a sudden the strong force will overtake it's much stronger than the Coulomb force and that these two hydrogen's will actually these this these nucleuses would actually fuse or that nuclei well anyway they would actually fuse together and so that is what actually happens once this gets hot and dense enough you now have enough pressure enough temperature to overcome the Coulomb force and bring these protons close enough to each other for fusion to occur for fusion fusion ignition ignition and the reason why is and I want to be very careful it's not ignition it's not combustion in the traditional sense it's not like you're burning a carbon molecule with out in the presence of oxygen it's not combustion it's ignition and the reason why it's called ignition is because when two of these protons or two of the nucleus is fuse the resulting the resulting nucleus has a slightly smaller mass and so in the first stage of this you actually have you actually have two protons two protons under enough pressure obviously this would not happen with just the Coulomb forces at with enough pressure to get close enough and then the strong interaction actually actually keeps them together one of these guys degrades in a neutron...
 \\\hline
@@
 30 &          BoS &                                                                                                                                                                                                                   Which of the following terms best describes a fusion reaction?
-&                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                    \textbf{[04:51.639--06:05.83]} ...most basic type of fusion that exhibit ours the hydrogen gets fused into deuterium deuterium of trouble spelling which is another way of calling heavy hydrogen this is still hydrogen because it has one proton and one Neutron now it is not helium yet it does not have two it does not have two protons but then the deuterium keeps fusing and then we eventually end up with and then we end up with helium and we can even see that on the periodic table I lost my periodic table well I'll show you in the next video but we know hydrogen hydrogen hydrogen in its atomic state has an atomic number of one and it also has a mass of one it only has one nucleon and it's nucleus but it's being fused it goes to hydrogen too which is deuterium which is one Neutron one proton in its nucleus two nucleons and then that eventually gets fused and I'm not going to the detail of the reaction into helium and by definition helium has two protons and two neutrons so it has or we're talking about helium four in particular that isotope of helium it has an atomic mass of four and the whole this process releases a ton of energy because the atomic mass of the helium\newline\textbf{[06:50.68--07:52.81]} ...there's there's questions of well what if what if there just wasn't enough mass to get to this level over here and there actually are things that never get to that quite that threshold to fuse all the way into helium there are a few things that don't quite make the threshold of stars that only fuse to this level so they are generating some of their eat or there are even smaller objects that just get to the point there's a huge temperature and pressure but fusion is not actually occurring inside of the core and something like Jupiter would be an example and you can go several several masses above Jupiter where you get something like that so you have to reach a certain threshold or the mass where the pressure and the temperature due to the heavy mass gets so large that you start this fusion at but the smaller you have above that threshold this the slower the fusion will occur but if you're supermassive the fusion will occur really really fast so that's a general idea of just how stars get formed and why they don't collapse on themselves and why they are these kind of little balls of fusion reactions existing in the universe and the next few videos we'll talk about what happens once that hydrogen fuel and the cure in the core starts to run out...
+&                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                    \textbf{[04:51.639--06:05.83]} ...most basic type of fusion that exhibit ours the hydrogen gets fused into deuterium deuterium of trouble spelling which is another way of calling heavy hydrogen this is still hydrogen because it has one proton and one Neutron now it is not helium yet it does not have two it does not have two protons but then the deuterium keeps fusing and then we eventually end up with and then we end up with helium and we can even see that on the periodic table I lost my periodic table well I'll show you in the next video but we know hydrogen hydrogen hydrogen in its atomic state has an atomic number of one and it also has a mass of one it only has one nucleon and it's nucleus but it's being fused it goes to hydrogen too which is deuterium which is one Neutron one proton in its nucleus two nucleons and then that eventually gets fused and I'm not going to the detail of the reaction into helium and by definition helium has two protons and two neutrons so it has or we're talking about helium four in particular that isotope of helium it has an atomic mass of four and the whole this process releases a ton of energy because the atomic mass of the helium...\newline\textbf{[06:50.68--07:52.81]} ...there's there's questions of well what if what if there just wasn't enough mass to get to this level over here and there actually are things that never get to that quite that threshold to fuse all the way into helium there are a few things that don't quite make the threshold of stars that only fuse to this level so they are generating some of their eat or there are even smaller objects that just get to the point there's a huge temperature and pressure but fusion is not actually occurring inside of the core and something like Jupiter would be an example and you can go several several masses above Jupiter where you get something like that so you have to reach a certain threshold or the mass where the pressure and the temperature due to the heavy mass gets so large that you start this fusion at but the smaller you have above that threshold this the slower the fusion will occur but if you're supermassive the fusion will occur really really fast so that's a general idea of just how stars get formed and why they don't collapse on themselves and why they are these kind of little balls of fusion reactions existing in the universe and the next few videos we'll talk about what happens once that hydrogen fuel and the cure in the core starts to run out...
 \\\hline
@@
     \label{fig:topics}
+\end{figure}
+
+\begin{figure}[tp]
+    \centering
+    \includegraphics[width=\textwidth]{figs/forces-qcorrs-peaks}
+
+    \caption{\textbf{Figure title}.
+Figure caption figure caption figure caption figure caption figure caption figure caption figure caption figure caption figure caption figure caption figure caption figure.}
+
+    \label{fig:forces-peaks}
+\end{figure}
+
+\begin{figure}[tp]
+    \centering
+    \includegraphics[width=\textwidth]{figs/bos-qcorrs-peaks}
+
+    \caption{\textbf{Figure title}.
+Figure caption figure caption figure caption figure caption figure caption figure caption figure caption figure caption figure caption figure caption figure caption figure.}
+
+    \label{fig:bos-peaks}
+\end{figure}
+
+%\begin{figure}[tp]
+%    \centering
+%    \includegraphics[width=\textwidth]{figs/word-overlap-comparison-v2}
+%
+%    \caption{\textbf{Figure title}.
+Figure caption figure caption figure caption figure caption figure caption figure caption figure caption figure caption figure caption figure caption figure caption figure.}
+%
+%    \label{fig:compare-wordcount}
+%\end{figure}
+
+\begin{figure}[tp]
+    \centering
+    \includegraphics[width=0.8\textwidth]{figs/model-comparison}
+
+    \caption{\textbf{Figure title}.
+Figure caption figure caption figure caption figure caption figure caption figure caption figure caption figure caption figure caption figure caption figure caption figure.}
+
+    \label{fig:compare-bert}
 \end{figure}

### 2023-10-23 paper/main.tex
backing up changes:
- finished addressing R1 comments
- addressed some of R2's comments

@@
 \newcommand{\topics}{2}
+\newcommand{\matchTab}{3}
 
@@
 \newcommand{\individualLearningMapsB}{7}
+\newcommand{\ldaVsBERT}{8}
+\newcommand{\jaccard}{9}   % word match figure
 
@@
 content that is highly similar to (but not precisely the same as) that
-contained in the two lectures. Aside from increasing the number of topics from
-15 to 100, all other procedures and model parameters were carried over from the
-preceding analyses. As in our other analyses, we resampled each lecture's topic
-trajectory to 1~Hz and projected each question into a shared text embedding
-space.
+contained in the two lectures. This change in the number of topics overcame an
+undesireable behavior in the UMAP embedding procedure~\citep{McInEtal18},
+whereby embedding coordinates for the 15-topic model tended to be ``clumped''
+into separated clusters, rather than forming a smooth trajectory through the 2D
+space. When we increased the number of topics to 100, the embedding coordinates
+in the 2D space formed a smooth trajectory through the space, with
+substantially less clumping (Fig.~\ref{fig:knowledge-maps}). We note that we
+used these 2D maps solely for visualization; all relevant comparisons, distance
+computations, and statistical tests we report above were carried out in the
+original 15-dimensional space, using the 15-topic model. Aside from increasing
+the number of topics from 15 to 100, all other procedures and model parameters
+were carried over from the preceding analyses. As in our other analyses, we
+resampled each lecture's topic trajectory to 1~Hz and projected each question
+into a shared text embedding space.
 
@@
 is being captured by the knowledge maps we are inferring from their quiz
-responses (e.g., Fig.~\ref{fig:smoothness}). In other words, our study shows
-that knowledge about a given concept implies knowledge about related concepts.
+responses (e.g., Figs.~\ref{fig:smoothness},~\ref{fig:knowledge-maps}). In
+other words, our study shows that knowledge about a given concept implies
+knowledge about related concepts.
+
+In our study, we characterize the ``coordinates'' of participants' knowledge
+using a relatively simple ``bag of words'' text embedding model~\citep[LDA;
+]{BleiEtal03}. More sophisticated text embedding models, such as
+transformer-based models~\citep{ViswEtal17, DevlEtal18, ChatGPT, TouvEtal23}
+can learn complex grammatical and semantic relationships between words,
+higher-order syntactic structures, sylistic features, and more. We considered
+using transformer-based models in our study, but we were surprised to find that
+the text embeddings derived from these models were surprisingly uninformative
+with respect to differentiating or otherwise characterizing the conceptual
+content of the lectures and questions we used. We suspect that this reflects a
+broader challenge in constructing models that are high-resolution within a
+given domain (e.g., the domain of physics lectures and questions) \textit{and}
+sufficiently broad so as to enable them to cover a wide range of domains. For
+example, we found that the embeddings derived even from much larger and more
+modern models like BERT~\citep{DevlEtal18}, GPT~\citep{ViswEtal17},
+LLaMa~\citep{TouvEtal23}, and others that are trained on enormous text corpora,
+end up yielding poor resolution within the content space spanned by indiviudal
+course videos (Supp. Fig.~\ldaVsBERT). Whereas the LDA embeddings of the
+lectures and questions are ``near'' each other (i.e., the convex hull enclosing
+the two lectures' trajectories is highly overlapping with the convex hull
+enclosing the questions' embeddings), the BERT embeddings of the lectures and
+questions are instead largely distinct (top row of Supp. Fig.~\ldaVsBERT). The
+LDA embeddings of the questions for each lecture and the corresponding
+lecture's trajectory are also similar. For example, as shown in
+Fig.~\ref{fig:sliding-windows}C, the LDA embeddings for \textit{Four
+Fundamental Forces} questions (blue dots) appear closer to the \textit{Four
+Fundamental Forces} lecture trajectory (blue line), whereas the LDA embeddings
+for \textit{Birth of Stars} questions (green dots) appear closer to the
+\textit{Birth of Stars} lecture trajectory (green line). The BERT embeddings of
+the lectures and questions do not show this property (Supp. Fig.~\ldaVsBERT).
+We also examined per-question ``content matches'' between individual questions
+and individual moments of each lecture
+(Figs.~\ref{fig:question-correlations},~\ldaVsBERT). The timeseries plot of
+individual questions' correlations are different from each other when computed
+using LDA (e.g., the traces can be clearly visually separated), whereas the
+correlations computed from BERT embeddings of different questions all look very
+similar. This tells us that LDA is capturing some differences in content
+between the questions, whereas BERT is not. The timeseries plots of individual
+questions' correlations have clear ``peaks'' when computed using LDA, but not
+when computed using BERT. This tells us that LDA is capturing a ``match''
+between the content of each question and a relatively well-defined time window
+of the corresponding lectures. The BERT embeddings appear to blur together the
+content of the questions versus specific moments of each lecture. Finally, we
+also compared the pairwise correlations between embeddings of questions within
+versus across content areas (i.e., content covered by the individual lectures,
+lecture-specific questions, and by the ``general physics knowledge''
+questions). The LDA embeddings show a strong contrast between same-content
+embeddings versus across-content embeddings. In other words, the embeddings of
+questions about the \textit{Four Fundamental Forces} material are highly
+correlated with the embeddings of the \textit{Four Fundamental Forces} lecture,
+but not with the embeddings of \textit{Birth of Stars}, questions about
+\textit{Birth of Stars}, or general physics knowledge questions. We see a
+similar pattern with the LDA embeddings of the \textit{Birth of Stars}
+questions (Fig.~\ref{fig:topics}, Supp. Fig.~\topicWeights). In contrast, the
+BERT embeddings are all highly correlated with each other (Supp.
+Fig.~\ldaVsBERT). Taken together, these comparisons illustrate how LDA (trained
+on the specific content in question) provides both coverage of the requisite
+material and specificity at the level of the content covered by individual
+questions. BERT, on the other hand, essentially assigns both lectures and all
+of the questions (which are all broadly about ``physics'') into a tiny region
+of its embedding space, thereby blurring out meaningful distinctions between
+different specific concepts covered by the lectures and questions. We note that
+these are not criticisms of BERT (or other large language models trained on
+large and diverse corpora). Rather, our point is that simple fine-tuned models
+trained on a relatively small but specialized corpus can outperform much more
+complicated models trained on much larger corpora, when we are specifically
+interested in capturing subtle conceptual differences at the level of a single
+course lecture or question. Of course if our goal had been to find a model that
+generalized to many different content areas, we would expect our approach to
+perform comparatively poorly relative to BERT or other much larger models. We
+suggest that bridging the tradeoff between high resolution within each content
+area versus the ability to generalize to many different content areas will be
+an important challenge for future work in this domain.
+
+At the opposite end of the spectrum from large language models, one could also
+imagine \textit{simplifying} some aspects of our LDA-based approach by
+computing simple word overlap metrics. For example, the Jaccard similarity
+between text $A$ and $B$ is computed as the number of unique words in the
+intersection of words from $A$ and $B$ divided by the number of unique words in
+the union of words from $A$ and $B$. In a supplemental analysis (Supp.
+Fig.~\jaccard), we compared the LDA-based question-lecture matches we reported
+in Figure~\ref{fig:question-correlations} with the Jaccard similarities between
+each question and each sliding window of text from the corresponding lecture.
+As shown in Supplementary Figure~\jaccard, this simple word-matching approach
+does not appear to capture the same level of specificity as the LDA-based
+approach. For example, whereas the LDA-based approach often yields a clear peak
+in the timeseries of correlations between each question and the corresponding
+lecture, the Jaccard similarity-based approach does not. Furthermore, these
+LDA-based matches appear to capture conceptual overlaps between the questions
+and lectures (Supp. Tab.~\matchTab), whereas simple word matching does not. For
+example, one of the example questions examined in Supplementary Figure~\jaccard
+asks ``Which of the following occurs as a cloud of atoms gets more dense?''.
+The LDA-based matches identify lecture timepoints where the releveant
+\textit{topics} are discussed (e.g., when words like ``cloud,'' ``atom,''
+``dense,'' etc., are mentioned \textit{together}). The Jaccard similarity-based
+matches, on the other hand, are strong when \textit{any} of these words are
+mentioned, even if they do not occur together.
 
@@
 seconds) and \textit{Birth of Stars} (an introduction to how stars are formed;
-duration: 7 minutes and 57 seconds). We then hand-created 39 multiple-choice
+duration: 7 minutes and 57 seconds). All participants viewed the videos in the
+same order (i.e., \textit{Four Fundamental Forces} followed by \textit{Birth of
+Stars}). While we are not aware of any specific confounds of viewing order, nor
+have are we aware of how or why viewing order might influence our main
+findings, we acknowledge that we did not control for potential order effects in
+our study.
+
+We then hand-created 39 multiple-choice
 questions: 15 about the conceptual content of \textit{Four Fundamental Forces}
@@
 about basic physics (covering material that was not presented in either video).
+One of our group's undergraduate research assistants worked alongside a
+rotating Masters student to develop this set of questions (these researchers
+are acknowledged in our paper for their contribution, although they did not
+meet the criteria for authorship discussed with all team members at the start
+of the project, as determined by J.R.M.) The senior author (J.R.M.) tasked the
+pair of researchers with coming up with ``15 conceptual questions about each
+lecture, along with 9 additional questions about general physics knowledge.'' To
+help broaden the set of lecture-specific questions, the researchers were
+further instructed to work through each lecture in small segments, identify
+what each segment was ``about'' conceptually, and then write a question about
+that concept. The general physics questions were drawn from the researchers'
+coursework along with internet searches and brainstorming with the project team
+and other members of J.R.M.'s lab. The final set of questions (and response
+options) was reviewed and approved by J.R.M.
+
 We note that estimating the specific ``amount'' of conceptual understanding
@@
 to each individual caption that would appear on-screen if viewing the lecture
-via YouTube, and when those lines would appear). We defined a sliding window
-length of (up to) $w = 30$ transcript lines, and assigned each window a
-timestamp corresponding to the midpoint between the timestamps for its first
-and last lines. These sliding windows ramped up and down in length at the
-beginning and end of each transcript, respectively. In other words, each
-transcript's first sliding window covered only its first line, the second
-sliding window covered the first two lines, and so on. This ensured that each
-line from the transcripts appeared in the same number ($w$) of sliding windows.
-After performing various standard text preprocessing (e.g., normalizing case,
-lemmatizing, removing punctuation and stop-words), we treated the text from
-each sliding window as a single ``document,'' and combined these documents
-across the two videos' windows to create a single training corpus for the topic
-model.
+via YouTube, and when those lines would appear). After scraping the
+transcripts, we carried out several standard preprocessing steps. First, we
+removed all punctuation, replaced numbers with their word equivalents (e.g.,
+``1'' with ``one''), and converted all text to lowercase. Next, we removed all
+stop words, as defined by the Natural Language Toolkit~\citep[NLTK;
+]{BirdEtal09} English stop word list, augmented with the following additional
+words that we hand-identified as frequently occuring and non-diagnostic:
+``actual,'' ``actually,'' ``also,'' ``bit,'' ``could,'' ``e,'' ``even,''
+``first,'' ``follow,'' ``following,'' ``four,'' ``let,'' ``like,'' ``mc,''
+``really,'', ``saw,'' ``see,'' ``seen,'' ``thing,'' and ``two.'' We defined a
+sliding window length of (up to) $w = 30$ transcript lines, and assigned each
+window a timestamp corresponding to the midpoint between the timestamps for its
+first and last lines. This $w$ parameter was chosen to match the same number of
+words per sliding window (rounded to the nearest whole word, and after
+preprocessing) as the sliding windows we defined in our prior
+work~\citep{HeusEtal21}. The sliding windows contained an average of 73.8 words
+and lasted for an average of 62.22 seconds.
+
+These sliding windows ramped up and down in length at the beginning and end of
+each transcript, respectively. In other words, each transcript's first sliding
+window covered only its first line, the second sliding window covered the first
+two lines, and so on. This ensured that each line from the transcripts appeared
+in the same number ($w$) of sliding windows. After performing various standard
+text preprocessing (e.g., normalizing case, lemmatizing, removing punctuation
+and stop-words), we treated the text from each sliding window as a single
+``document,'' and combined these documents across the two videos' windows to
+create a single training corpus for the topic model.
 
@@
 The normalization step (i.e., using $\mathrm{ncorr}$ instead of the raw
-correlations) insures that every question contributes some non-negative amount
+correlations) ensures that every question contributes some non-negative amount
 to the knowledge estimate.

### 2023-10-23 paper/main.tex
backing up progress (working on addressing R2 comments)

@@
 
-We then hand-created 39 multiple-choice
-questions: 15 about the conceptual content of \textit{Four Fundamental Forces}
-(i.e., Lecture~1), 15 about the conceptual content of \textit{Birth of Stars}
-(i.e., Lecture~2), and 9 questions that tested for general conceptual knowledge
-about basic physics (covering material that was not presented in either video).
-One of our group's undergraduate research assistants worked alongside a
-rotating Masters student to develop this set of questions (these researchers
-are acknowledged in our paper for their contribution, although they did not
-meet the criteria for authorship discussed with all team members at the start
-of the project, as determined by J.R.M.) The senior author (J.R.M.) tasked the
-pair of researchers with coming up with ``15 conceptual questions about each
-lecture, along with 9 additional questions about general physics knowledge.'' To
-help broaden the set of lecture-specific questions, the researchers were
-further instructed to work through each lecture in small segments, identify
-what each segment was ``about'' conceptually, and then write a question about
-that concept. The general physics questions were drawn from the researchers'
-coursework along with internet searches and brainstorming with the project team
-and other members of J.R.M.'s lab. The final set of questions (and response
-options) was reviewed and approved by J.R.M.
+We then hand-created 39 multiple-choice questions: 15 about the conceptual
+content of \textit{Four Fundamental Forces} (i.e., Lecture~1), 15 about the
+conceptual content of \textit{Birth of Stars} (i.e., Lecture~2), and 9
+questions that tested for general conceptual knowledge about basic physics
+(covering material that was not presented in either video). One of our group's
+undergraduate research assistants worked alongside a rotating Masters student
+to develop this set of questions (these researchers are acknowledged in our
+paper for their contribution, although they did not meet the criteria for
+authorship discussed with all team members at the start of the project, as
+determined by J.R.M.) The senior author (J.R.M.) tasked the pair of researchers
+with coming up with ``15 conceptual questions about each lecture, along with 9
+additional questions about general physics knowledge.'' To help broaden the set
+of lecture-specific questions, the researchers were further instructed to work
+through each lecture in small segments, identify what each segment was
+``about'' conceptually, and then write a question about that concept. The
+general physics questions were drawn from the researchers' coursework along
+with internet searches and brainstorming with the project team and other
+members of J.R.M.'s lab. The final set of questions (and response options) was
+reviewed and approved by J.R.M.
 
@@
 words.''). Conceptually, each topic is intended to give larger weights to words
-that are semantically related or tend to co-occur in the same documents. After
+that are semantically related, as implied by their co-occurring in the same documents. After
 fitting a topic model, each document in the training set, or any \textit{new}
@@
 to each individual caption that would appear on-screen if viewing the lecture
-via YouTube, and when those lines would appear). After scraping the
-transcripts, we carried out several standard preprocessing steps. First, we
-removed all punctuation, replaced numbers with their word equivalents (e.g.,
-``1'' with ``one''), and converted all text to lowercase. Next, we removed all
-stop words, as defined by the Natural Language Toolkit~\citep[NLTK;
-]{BirdEtal09} English stop word list, augmented with the following additional
-words that we hand-identified as frequently occuring and non-diagnostic:
-``actual,'' ``actually,'' ``also,'' ``bit,'' ``could,'' ``e,'' ``even,''
-``first,'' ``follow,'' ``following,'' ``four,'' ``let,'' ``like,'' ``mc,''
-``really,'', ``saw,'' ``see,'' ``seen,'' ``thing,'' and ``two.'' We defined a
-sliding window length of (up to) $w = 30$ transcript lines, and assigned each
-window a timestamp corresponding to the midpoint between the timestamps for its
-first and last lines. This $w$ parameter was chosen to match the same number of
-words per sliding window (rounded to the nearest whole word, and after
-preprocessing) as the sliding windows we defined in our prior
-work~\citep{HeusEtal21}. The sliding windows contained an average of 73.8 words
-and lasted for an average of 62.22 seconds.
+via YouTube, and when those lines would appear). We defined a sliding window
+length of (up to) $w = 30$ transcript lines, and assigned each window a
+timestamp corresponding to the midpoint between the timestamps for its first
+and last lines. This $w$ parameter was chosen to match the same number of words
+per sliding window (rounded to the nearest whole word, and after preprocessing)
+as the sliding windows we defined in our prior work~\citep{HeusEtal21}. The
+sliding windows contained an average of 73.8 words and lasted for an average of
+62.22 seconds. After splitting the transcripts into sliding windows, we carried
+out several standard preprocessing steps. First, we removed all punctuation,
+replaced numbers with their word equivalents (e.g., ``1'' with ``one''), and
+converted all text to lowercase. Next, we removed all stop words, as defined by
+the Natural Language Toolkit~\citep[NLTK; ]{BirdEtal09} English stop word list,
+augmented with additional words following~\citep{BoydMimn14}: ``actual,''
+``actually,'' ``also,'' ``bit,'' ``could,'' ``e,'' ``even,'' ``first,''
+``follow,'' ``following,'' ``four,'' ``let,'' ``like,'' ``mc,'' ``really,'',
+``saw,'' ``see,'' ``seen,'' ``thing,'' and ``two.''
 

### 2023-10-24 paper/main.tex
complete draft of responses to all reviewer comments!

@@
 acquired information to the scaffolding of one's existing knowledge or
-experience~\citep{BlayEtal06,CaraMaho03, ConsEtal16, DeacEtal04, SimoEtal04}?
-Or weaving a lecture's atomic elements (e.g., its component words) into a
-structured network that describes how those individual elements are
-related~\citep{LeeChen22}? Conceptual understanding could also involve building
-a mental model that transcends the meanings of those individual atomic elements
-by reflecting the deeper meaning underlying the gestalt whole~\citep{Kint70,
-Macl05, ScotEtal07}.
+experience~\citep{BlayEtal06,CaraMaho03, ConsEtal16, DeacEtal04, SimoEtal04,
+HuebWill18}? Or weaving a lecture's atomic elements (e.g., its component words)
+into a structured network that describes how those individual elements are
+related~\citep{LeeChen22, vanPEtal21}? Conceptual understanding could also
+involve building a mental model that transcends the meanings of those
+individual atomic elements by reflecting the deeper meaning underlying the
+gestalt whole~\citep{Kint70, Macl05, ScotEtal07, TulcEtal23}.
 
@@
 (e.g.,~\citealp{LandDuma97, DeerEtal90, BleiEtal03, BleiLaff06, MikoEtal13a,
-CerEtal18, BrowEtal20}) also attempt to capture the deeper meaning
+CerEtal18, BrowEtal20, ViswEtal17}) also attempt to capture the deeper meaning
 \textit{underlying} those atomic elements. These models consider not only the
@@
 conceptually related documents, \textit{even when the specific words contained
-in those documents have very little overlap}.
+in those documents have very little overlap}. In this way, ``concepts'' are
+defined implicitly by the model's geometry~\citep[e.g., how the embedding coordinate
+of a given word or document relates to the coordinates of other text
+embeddings;][]{PianHill22}.
 
@@
 
-    \caption{\textbf{Estimating moment-by-moment knowledge acquisition.}
-    \textbf{A. Moment-by-moment knowledge about the \textit{Four Fundamental
-    Forces}}. Each trace displays the weighted proportion of correctly answered
-    questions about the content reflected in each moment of the lecture (see
-    \nameref{subsec:traces}), using responses from a single quiz (color). The
-    traces are averaged across participants. \textbf{B. Average estimated
-    knowledge about the \textbf{Four Fundamental Forces}.} Each bar displays
-    the across-timepoint average knowledge, estimated using the responses to
-    one quiz's questions. \textbf{C. Moment-by-moment knowledge about the
-    \textit{Birth of Stars}}. The panel is in the same format as Panel A, but
-    here the knowledge estimates are for the moment-by-moment content of the
-    \textit{Birth of Stars} lecture. \textbf{D. Average estimated knowledge
-    about the \textit{Birth of Stars}.} The panel is in the same format as
-    Panel B, but here the knowledge estimates are for the content of the
-    \textit{Birth of Stars} lecture. All panels: error ribbons and error bars
-    denote 95\% confidence intervals, estimated across participants.}
+    \caption{\textbf{Estimating knowledge about the content presented at each
+    moment of each lecture.} \textbf{A. Knowledge about the time-varying
+    content of \textit{Four Fundamental Forces}}. Each trace displays the
+    weighted proportion of correctly answered questions about the content
+    reflected in each moment of the lecture (see \nameref{subsec:traces}),
+    using responses from a single quiz (color). The traces are averaged across
+    participants. \textbf{B. Average estimated knowledge about \textbf{Four
+    Fundamental Forces}.} Each bar displays the across-timepoint average
+    knowledge, estimated using the responses to one quiz's questions.
+    \textbf{C. Knowledge about the time-varying content of \textit{Birth of
+    Stars}}. The panel is in the same format as Panel A, but here the knowledge
+    estimates are for the moment-by-moment content of the \textit{Birth of
+    Stars} lecture. \textbf{D. Average estimated knowledge about \textit{Birth
+    of Stars}.} The panel is in the same format as Panel B, but here the
+    knowledge estimates are for the content of the \textit{Birth of Stars}
+    lecture. All panels: error ribbons and error bars denote 95\% confidence
+    intervals, estimated across participants.}
 
@@
 estimated knowledge at the coordinates of \textit{incorrectly} answered
-questions (Fig.~\ref{fig:predictions}). We then used independent samples
-$t$-tests to compare the means of these distributions of estimated knowledge.
+questions (Fig.~\ref{fig:predictions}). We then used Mann-Whitney $U$-tests to
+compare the means of these distributions of estimated knowledge.
 
@@
     held-out correctly (blue) or incorrectly (red) answered question. The
-    $t$-tests reported in each panel are between the distributions of estimated
-    knowledge at the coordinates of correctly versus incorrectly answered
-    held-out questions.}
+    Mann-Whitney $U$-tests reported in each panel are between the distributions
+    of estimated knowledge at the coordinates of correctly versus incorrectly
+    answered held-out questions. In the top row (``All questions''), we used
+    all quiz questions (from each quiz, for each participant) except one to
+    estimate knowledge at the held-out question's embedding coordinate. In the
+    middle rows (``Across-lecture''), we used all questions about one lecture
+    to estimate knowledge at the embedding coordinate of a held-out question
+    about the \textit{other} lecture. In the bottom row (``Within-lecture''),
+    we used all but one question about one lecture to estimate knowledge at the
+    embedding coordinate of a held-out question about the \textit{same}
+    lecture. We repeated each of these analyses using all possible held-out
+    questions for each quiz and participant.}
 
@@
 participants' estimated knowledge tended to be low overall, and relatively
-unstructured (Fig.~\ref{fig:predictions}, left panel). When we held out
+unstructured (Fig.~\ref{fig:predictions}, left column). When we held out
 individual questions and estimated their knowledge at the held-out questions'
 embedding coordinates, we found no reliable differences in the estimates when
-the held-out question had been correctly versus incorrectly answered ($t(633) =
-0.577,~p = 0.564$). This reflects a floor effect: when knowledge is low
-everywhere, there is little signal to differentiate between what is known
-versus unknown. After watching the first lecture, estimated knowledge for
+the held-out question had been correctly versus incorrectly answered. This
+``null'' effect persisted when we used \textit{all} of the Quiz 1 questions
+from a given participant to predict a held-out question (``All questions''; $U
+= 50587, p = 0.723$), when we used questions from one lecture to predict
+knowledge at the embedding coordinate of a held-out question about the
+\textit{other} lecture (``Across-lecture''; predicting knowledge for held-out
+\textit{Four Fundamental Forces Questions} using \textit{Birth of Stars}
+questions: $U = 8244, p = 0.184$; predicting knowledge for held-out
+\textit{Birth of Stars} questions: $U = 8202.5, p = 0.161$), and when we used
+questions from one lecture to predict knowledge at the embedding coordinate of
+a held-out question about the \textit{same} lecture (``Within-lecture'';
+\textit{Four Fundamental Forces}: $U = 7681.5, p = 0.746$; \textit{Birth of
+Stars}: $U = 8125, p = 0.204$). We believe that this reflects a floor effect:
+when knowledge is low everywhere, there is little signal to differentiate
+between what is known versus unknown.
+
+After watching \textit{Four Fundamental Forces}, estimated knowledge for
 held-out correctly answered questions (from the second quiz;
-Fig.~\ref{fig:predictions}, middle panel) exhibited a positive shift relative
-to held-out incorrectly answered questions ($t(633) = 3.961,~p < 0.001$). This
-second quiz provides the maximally sensitive test for our knowledge
-predictions, since (if knowledge is estimated accurately) participants' Quiz~2
-responses should demonstrate specific knowledge about Lecture~1 content, but
-knowledge about Lecture~2 and general physics concepts should be roughly
-unchanged from before they watched Lecture~1. After watching the second
-lecture, estimated knowledge (from the third quiz; Fig.~\ref{fig:predictions},
-right panel) for \textit{all} questions exhibited a positive shift. However,
-the estimated knowledge for held-out correctly answered questions remained
-greater than that for held-out incorrectly answered questions ($t(628) =
-2.045,~p = 0.041$). This third contrast reflects a ceiling effect: when
-knowledge is relatively high everywhere, the signal differentiating what is
-known versus unknown is relatively weak. Taken together, this set of analyses
-demonstrates that our knowledge prediction framework is most informative when
-participants exhibit variability in their knowledge of the content captured by
-the text embedding model.
+Fig.~\ref{fig:predictions}, middle column) exhibited a positive shift relative
+to held-out incorrectly answered questions. This held when we included all
+questions in the analysis ($U = 58332, p < 0.001$), when we predicted knowledge
+across-lectures (\textit{Four Fundamental Forces}: $U = 6749.5, p = 0.014$;
+\textit{Birth of Stars}: $U = 8480, p = 0.016$), and when we predicted
+knowledge at the embedding coordinates of held-out \textit{Four Fundamental
+Forces} questions using other \textit{Four Fundamental Forces} questions from
+the same quiz and participant ($U = 7224, p < 0.001$). This difference did
+\textit{not} hold for within-lecture predictions of \textit{Birth of Stars}
+knowledge ($U = 7419, p = 0.739$). Again, we suggest that this might reflect a
+floor effect whereby knowledge about the content of the \textit{Birth of Stars}
+material is relatively low everywhere in that region of text embedding space.
+
+Finally, after watching \textit{Birth of Stars}, estimated knowledge for
+held-out correctly answered questions (from the third quiz;
+Fig.~\ref{fig:predictions}, right column) was higher for held-out correctly
+answered questions than for held-out incorrectly answered questions. This held
+when we included all questions in the analysis ($U = 38279, p = 0.022$), when
+we carried out across-lecture predictions (\textit{Four Fundamental Forces}: $U
+= 6684.5, p = 0.032$; \textit{Birth of Stars}: $U = 6414.5, p = 0.002$), and
+and when we carried out within-lecture predictions of held-out \textit{Birth of
+Stars} questions using other \textit{Birth of Stars} questions from the same
+quiz and participant ($U = 6126, p = 0.006$). However, we found the
+\textit{opposite} effect when we carried out within-lecture predictions of
+held-out \textit{Four Fundamental Forces} questions using other \textit{Four
+Fundamental Forces} questions from the same quiz and participant ($U = 6734, p
+= 0.027$). Specifically, held-out correctly answered Quiz 3 questions about
+\textit{Four Fundamental Forces} had reliably \textit{lower} estimated
+knowledge than held-out incorrectly answered questions. Speculatively, we
+suggest that this may reflect participants forgetting some of the \textit{Four
+Fundamental Forces} content. If this forgetting happens in a relatively
+``random'' way (with respect to spatial distance within the text embedding
+space), then it could explain why some held-out questions about \textit{Four
+Fundamental Forces} were answered incorrectly, even if questions at nearby
+coordinates (i.e., about similar content) were answered correctly. This might
+lead our approach to over-estimate knowledge for held-out questions about
+``forgotten'' knowledge that particpants answered incorrectly.
+
+That the knowledge estimates derived from the text embedding space reliably
+distinguish between held-out correctly versus incorrectly answered questions
+(Fig.~\ref{fig:predictions}) suggests that the text embedding space bears at
+least some relationship to participants' knowledge. But what does that
+relationship look like as we move through the embedding space? For example,
+suppose we know that a participant answers a question (at embedding coordinate
+$X$) correctly. As we move away from $X$ in the embedding space, how does quiz
+performance ``fall off'' with distance? Or, suppose the participant instead
+answered that same question \textit{in}correctly. Again, as we move away from
+$X$ in the embedding space, how does our confidence that the participant does
+\textit{not} know about the content change with distance? We reasoned that,
+assuming our space is capturing something about how participants actually
+organize their knowledge, conceptual knowledge right around $X$ should be similar
+to the participant's knowledge of the content at $X$. And at another extreme, at
+some distance (after moving sufficiently far away from $X$), our guesses about
+what participants know (based on their response to the question at location $X$)
+should be no better than guessing based on their overall proportion of
+correctly answered questions—i.e., if $Y$ is very far away from $X$, all we can do
+with the participant's response to $X$ is guess that ``their performance on quiz
+questions about $Y$ is about equal to their average performance on quiz questions
+about any material.''
 
@@
     \centering
-    \includegraphics[width=\textwidth]{figs/knowledge-smoothness}
-
-    \caption{\textbf{Caption title.} Caption content.}
+    \includegraphics[width=0.8\textwidth]{figs/knowledge-smoothness}
+
+    \caption{\textbf{Quiz performance falls off gradually in text embedding
+    space.} \textbf{A. Performance versus distance.} For each participant, for
+    each correctly answered question (blue) or incorrectly answered question
+    (red), we computed the proportion of correctly answered questions within a
+    given distance of that question's embedding coordinate. We repeated this
+    analysis for all questions and participants, and separately for each quiz
+    (column). The black lines denote the average proportion correct across
+    \textit{all} questions included in the analysis at the given distance.
+    \textbf{B. Maximum distance for which performance is reliably different
+    from the average.} We used a bootstrap procedure
+    (see~\nameref{subsec:smoothness}) to estimate the point at which the blue
+    and red lines in Panel A reliably diverged from the black line. We repeated
+    this analysis separately for correctly and incorrectly answered questions
+    from each quiz. \textbf{All panels.} Error ribbons denote
+    bootstrap-estimated 95\% confidence intervals.}
 
@@
 \end{figure}
+
+With these ideas in mind, we asked: conditioned on answering a question
+correctly, what proportion of all questions (within some radius, $r$, of that
+question's embedding coordinate) were answered correctly? We plotted this
+proportion as a function of $r$. Similarly, we could ask, conditioned on
+answering a question incorrectly, how the proportion of correct responses
+changed with $r$. As shown in Figure~\ref{fig:smoothness}, we found that quiz
+performance falls off smoothly with distance, and the ``rate'' of the falloff
+does not appear to change across the different quizzes, as measured by the
+distance at which performance becomes statistically indistinguishable from a
+simple proportion correct score (see~\nameref{subsec:smoothness}). This
+suggests that, at least within the region of text embedding space covered by
+the questions our participants answered (and as characterized using our topic
+model), the rate at which knowledge changes with distance is relatively
+constant, even as participants' overall level of knowledge varies across
+quizzes or regions of the embedding space.
 
@@
 
+Another application for large language models that does \textit{not} require
+explicitly modeling the content of individual lectures or questions is to
+leverage the models' ability to generate text. For example, generative text
+models like ChatGPT~\citep{ChatGPT} and LLaMa~\citep{TouvEtal23} are already
+being used to build a new generation of interactive tutoring
+systems~\citep[e.g.,][]{MannEtal23b}.  Unlike the approach we have taken here,
+these systems do not explicitly model what learners know, or how their knowledge 
+changes over time with training.  One could imagine building a hybrid system
+that combines the best of both worlds: a large language model that can
+\textit{generate} text, combined with a smaller model that can \textit{infer}
+what learners know and how their knowledge changes over time.  Such a hybrid
+system could potentially be used to build a new generation of interactive
+tutoring systems that are able to adapt to learners' needs in real time, and
+that are able to provide more nuanced feedback about what learners know and
+what they do not know.
+
 At the opposite end of the spectrum from large language models, one could also
@@
 mentioned, even if they do not occur together.
+
+We view our approach as occupying a sort of ``sweet spot,'' between much larger
+language models and simple word matching-based approaches, that enables us to
+capture the relevant conceptual content of course materials at an appropriate
+semantic scale. Our approach enables us to accurately and consistently identify
+each question's content in a way that also matches up with what is presented in
+the lectures. In turn, this enables us to construct accurate predictions about
+participants' knowledge of the conceptual content tested by held-out questions
+(Fig.~\ref{fig:predictions}).
+
+One limitation of our approach is that topic models contain no explicit
+internal representations of more complex aspects of ``knowledge,'' like
+knowledge graphs, dependencies or associations between concepts, causality, and
+so on. These representations might (in principle) be added as extensions to our
+approach to more accurately and precisely capture, characterize, and track
+learners' knowledge. However, modeling these aspects of knowledge will likely
+require substantial additional research effort.
 
@@
 members of J.R.M.'s lab. The final set of questions (and response options) was
-reviewed and approved by J.R.M.
+reviewed and approved by J.R.M. before we collected or analyzed the text or
+experimental data.
 
@@
 and last lines. This $w$ parameter was chosen to match the same number of words
-per sliding window (rounded to the nearest whole word, and after preprocessing)
-as the sliding windows we defined in our prior work~\citep{HeusEtal21}. The
-sliding windows contained an average of 73.8 words and lasted for an average of
-62.22 seconds. After splitting the transcripts into sliding windows, we carried
-out several standard preprocessing steps. First, we removed all punctuation,
-replaced numbers with their word equivalents (e.g., ``1'' with ``one''), and
-converted all text to lowercase. Next, we removed all stop words, as defined by
-the Natural Language Toolkit~\citep[NLTK; ]{BirdEtal09} English stop word list,
-augmented with additional words following~\citep{BoydMimn14}: ``actual,''
-``actually,'' ``also,'' ``bit,'' ``could,'' ``e,'' ``even,'' ``first,''
-``follow,'' ``following,'' ``four,'' ``let,'' ``like,'' ``mc,'' ``really,'',
-``saw,'' ``see,'' ``seen,'' ``thing,'' and ``two.''
+per sliding window (rounded to the nearest whole word, and before
+preprocessing) as the sliding windows we defined in our prior
+work~\citep{HeusEtal21} (i.e., 185 words per sliding window).
 
@@
 two lines, and so on. This ensured that each line from the transcripts appeared
-in the same number ($w$) of sliding windows. After performing various standard
-text preprocessing (e.g., normalizing case, lemmatizing, removing punctuation
-and stop-words), we treated the text from each sliding window as a single
-``document,'' and combined these documents across the two videos' windows to
-create a single training corpus for the topic model.
+in the same number ($w$) of sliding windows. We next performed a series of
+standard text preprocessing steps: normalizing case, lemmatizing, removing
+punctuation and removing stop-words. We constructed our corpus of stop words by
+augmenting the Natural Language Toolkit~\citep[NLTK; ]{BirdEtal09} English stop
+word list with the following additional words, selected using the stop word
+approach suggested by~\citep{BoydMimn14}: ``actual,'' ``actually,'' ``also,''
+``bit,'' ``could,'' ``e,'' ``even,'' ``first,'' ``follow,'' ``following,''
+``four,'' ``let,'' ``like,'' ``mc,'' ``really,'', ``saw,'' ``see,'' ``seen,''
+``thing,'' and ``two.'' This yielded sliding windows with an average of 73.8
+remaining words, and lasting for an average of 62.22~seconds. We treated the
+text from each sliding window as a single ``document,'' and combined these
+documents across the two videos' windows to create a single training corpus for
+the topic model.
 
@@
 to the knowledge estimate.
+
+\subsubsection*{Estimating the ``smoothness'' of knowledge}\label{subsec:smoothness}
+
+In the analysis reported in Figure~\ref{fig:smoothness}A, we show how
+participants' quiz performance changes as a function of distance to a given
+correctly or incorrectly answered reference question. We used a bootstrap-based
+approach to estimate the maximum distances over which these proportions
+of correctly answered questions could be reliably distinguished from participants'
+overall average proportion of correctly answered questions.
+
+In our bootstrap procedure, we ran 10,000 iterations to estimate the
+relationship between participants' performance and the distance to a given
+reference question. For each of these iterations, for every individual quiz
+($q$), we first determined the across-participants average ``simple''
+proportion correct and its 95\% confidence interval. This interval was
+established by repeatedly (1,000 times) subsampling participants with
+replacement, computing the mean ``simple'' proportion correct for each
+subsample, and then deriving the 2.5\textsuperscript{th} and
+97.5\textsuperscript{th} percentiles from the distribution of these subsample
+means. We used this interval as our benchmark for determining whether the
+proportion of correctly answered questions for a given subset of questions was
+reliably different (at the $p < 0.05$ significance level) from the average
+proportion correct across all questions.
+
+Next, for each participant, we examined all 15 questions they answered on quiz
+$q$. We treated each question as the ``reference question'' in turn. Around
+this reference, we constructed a series of 15-dimensional spheres (starting
+with a radius of 0), where each successive circle had a radius of 0.01
+(correlation distance) greater than its predecessor. Within each of these
+spheres, we calculated the proportion of questions answered correctly by the
+participant. The per-radius proportion correct values were then averaged across
+both categories of ``reference questions'': those answered correctly and those
+answered incorrectly. This yielded two distinct proportion-correct values for
+each binned distance (radius) for a specific participant and quiz. From these,
+we established the average proportion correct within each radius for both
+categories of reference questions. Finally, we identified the minimum binned
+distance from the correctly answered reference questions for which the average
+proportion correct intersected the 95\% confidence interval of the simple
+average proportion correct computed earlier. (A parallel analysis was conducted
+for the incorrectly answered reference questions.) We display the resulting
+distance estimates, for each quiz and reference question status, in
+Figure~\ref{fig:smoothness}B.
 

### 2023-10-24 paper/supplement.tex
filled in supplemental materials captions, updated word overlap comparison figure highlights.  also re-regenerated and compiled the track-changes pdf and updated old.tex using the prior submission of our paper.

@@
 
-    \caption{\textbf{Table title.} Caption content caption content caption content caption content caption content caption content caption content caption content caption content caption content.}
+\caption{\textbf{Lecture-specific questions and lecture excerpts.} We used the
+text embeddings of each question about \textit{Four Fundamental Forces} (FFF)
+and \textit{Birth of Stars} to identify corresponding matching intervals of the
+lectures. The text of the questions and the best-matching time intervals of the
+lecture transcripts are displayed (lecture times are noted in square brackets).
+Timecourses of topic correlations for each question may be found in
+Supplemntary Figures~\ref{fig:forces-peaks} and~\ref{fig:bos-peaks}. Note that
+no matching lecture interval was found for Question 29.} 
+\label{tab:matches}
 \end{longtable}
@@
 
-    \caption{\textbf{Figure title}.
-Figure caption figure caption figure caption figure caption figure caption figure caption figure caption figure caption figure caption figure caption figure caption figure.}
-
+    \caption{\textbf{Topic correlation timeseries plots for individual
+    \textit{Four Fundamental Forces} questions}. Each panel displays a
+    timeseries plot showing how the question's topic vector correlates with the
+    topic vectors for each timepoint of \textit{Four Fundamental Forces}. The
+    shaded regions in each curve denote the full width at half maximum (FWHM)
+    of the peak(s) in the curve. These FWHM intervals were used to identify the
+    corresponding lecture intervals displayed in Supplementary
+    Table~\ref{tab:matches}. The diamonds denote the peak correlation values
+    (local maxima) within each shaded region.}
     \label{fig:forces-peaks}
@@
 
-    \caption{\textbf{Figure title}.
-Figure caption figure caption figure caption figure caption figure caption figure caption figure caption figure caption figure caption figure caption figure caption figure.}
+    \caption{\textbf{Topic correlation timeseries plots for individual
+    \textit{Birth of Stars} questions}. Each panel displays a
+    timeseries plot showing how the question's topic vector correlates with the
+    topic vectors for each timepoint of \textit{Birth of Stars}. The
+    shaded regions in each curve denote the full width at half maximum (FWHM)
+    of the peak(s) in the curve. These FWHM intervals were used to identify the
+    corresponding lecture intervals displayed in Supplementary
+    Table~\ref{tab:matches}. The diamonds denote the peak correlation values
+    (local maxima) within each shaded region.}
 
@@
 
-%\begin{figure}[tp]
-%    \centering
-%    \includegraphics[width=\textwidth]{figs/word-overlap-comparison-v2}
-%
-%    \caption{\textbf{Figure title}.
-Figure caption figure caption figure caption figure caption figure caption figure caption figure caption figure caption figure caption figure caption figure caption figure.}
-%
-%    \label{fig:compare-wordcount}
-%\end{figure}
+\begin{figure}[tp]
+    \centering
+    \includegraphics[width=0.57\textwidth]{figs/word-overlap-comparison}
+
+    \caption{\textbf{Topic correlations versus word overlap}. \textbf{A.
+    Single-timepoint comparisons for \textit{Four Fundamental Forces}.} Each
+    question about \textit{Four Fundamental Forces} was compared to each
+    timepoint of the lecture (dots). The blue dots denote the correlations
+    between the topic vectors, and the orange dots denote Jaccard similarities
+    (defined as the number of unique words in common between the question and
+    corresponding window of the lecture, divided by the total number of unique
+    words in both). \textbf{B. Single-timepoint comparisons for \textit{Birth
+    of Stars}. Same format as Panel A. \textbf{C. Topic correlation timeseries
+    plots.} This panel is in the same format as Figure 4A from the main text,
+    but here the example question highlighted in purple in Panel A has been
+    emphasized for the \textit{Four Fundamental Forces} traces on the left, and
+    the example question highlighted in green in Panel B has been emphasized
+    for the \textbf{Birth of Stars} traces on the right. \textbf{D. Jaccard
+    similarity timeseries plots.} These panels are in the same format as Panel
+    C, but they display the Jaccard similarity timeseries for the same
+    questions. \textbf{E. Question and lecture text.} The text for the example
+    purple (left) and green (right) questions is shown on top, and the text
+    from the best-matching intervals of the lectures (computed using topic
+    correlations; see Supp. Tab.~\ref{tab:matches}) are shown on the bottom.}}
+
+    \label{fig:compare-wordcount}
+\end{figure}
 
@@
     \centering
-    \includegraphics[width=0.8\textwidth]{figs/model-comparison}
+    \includegraphics[width=0.7\textwidth]{figs/model-comparison}
 
-    \caption{\textbf{Figure title}.
-Figure caption figure caption figure caption figure caption figure caption figure caption figure caption figure caption figure caption figure caption figure caption figure.}
+    \caption{\textbf{Comparing LDA vs. BERT embeddings}. The rows of the
+    display the equivalents of Figures 2C (top row), 4A and B (middle two
+    rows), and 3B (bottom row) computed using LDA (left) and BERT (right).}
 

### 2023-10-24 paper/old.tex

--- 2023-10-23 paper/main.tex
@@
 \newcommand{\topics}{2}
-\newcommand{\matchTab}{3}
 
@@
 \newcommand{\individualLearningMapsB}{7}
-\newcommand{\ldaVsBERT}{8}
-\newcommand{\jaccard}{9}   % word match figure
 
@@
 
-A common approach to assessing a student's knowledge is to present them with a
-set of quiz questions, calculate the proportion they answer correctly, and
-provide them with feedback in the form of a simple numeric or letter grade.
-While such a grade can provide \textit{some} indication of whether the student
-has mastered the to-be-learned material, any univariate measure of performance
-on a complex task sacrifices certain relevant information, risks conflating
-underlying factors, and so on. For example, consider the relative utility of
-the theoretical map described above that characterizes a student's knowledge in
-detail, versus a single annotation saying that the student answered 85\% of
+A common approach to assessing a student's knowledge is to present them with a set of quiz
+questions, calculate the proportion they answer correctly, and provide
+them with feedback in the form of a simple numeric or letter grade. While such a
+grade can provide \textit{some} indication of whether the student has
+mastered the to-be-learned material, any univariate measure of performance on a
+complex task sacrifices certain relevant information, risks conflating underlying
+factors, and so on. For example, consider the relative utility of the
+theoretical map described above that characterizes a student's knowledge
+in detail, versus a single annotation saying that the student answered 85\% of
 their quiz questions correctly, or that they received a `B'. Here, we show that
@@
 The difference between ``understanding'' and ``memorizing,'' as framed by
-researchers in education, cognitive psychology, and cognitive neuroscience
-(e.g.,~\citealp{Kato40, Gall00, ScotEtal07, HallGree08, Macl05}), has profound
-analogs in the fields of natural language processing and natural language
-understanding. For example, considering the raw contents of a document (e.g.,
-its constituent symbols, letters, and words) might provide some clues as to
-what the document is about, just as memorizing a passage might provide some
-ability to answer simple questions about it. However, text embedding models
-(e.g.,~\citealp{LandDuma97, DeerEtal90, BleiEtal03, BleiLaff06, MikoEtal13a,
-CerEtal18, BrowEtal20}) also attempt to capture the deeper meaning
-\textit{underlying} those atomic elements. These models consider not only the
-co-occurrences of those elements within and across documents, but (in many
-cases) also patterns in how those elements appear across different scales
-(e.g., sentences, paragraphs, chapters, etc.), the temporal and grammatical
-properties of the elements, and other high-level characteristics of how they
-are used~\citep{Mann20, Mann21a}. According to these models, the deep
-conceptual meaning of a document may be captured by a feature vector in a
-high-dimensional representation space, wherein nearby vectors reflect
-conceptually related documents. A model that succeeds at capturing an analogue
-of ``understanding'' is able to assign nearby feature vectors to two
-conceptually related documents, \textit{even when the specific words contained
-in those documents have very little overlap}.
+researchers in education, cognitive psychology, and cognitive
+neuroscience (e.g.,~\citealp{Kato40, Gall00, ScotEtal07, HallGree08, Macl05}),
+has profound analogs in the fields of natural language processing and natural
+language understanding. For example, considering the raw contents of a document
+(e.g., its constituent symbols, letters, and words) might provide some
+clues as to what the document is about, just as memorizing a passage
+might provide some ability to answer simple questions about it. However, text
+embedding models (e.g.,~\citealp{LandDuma97, DeerEtal90, BleiEtal03,
+BleiLaff06, MikoEtal13a, CerEtal18, BrowEtal20}) also attempt to capture the
+deeper meaning \textit{underlying} those atomic elements. These models consider
+not only the co-occurrences of those elements within and across documents, but
+also patterns in how those elements appear across different scales (e.g.,
+sentences, paragraphs, chapters, etc.), the temporal and grammatical properties
+of the elements, and other high-level characteristics of how they are
+used~\citep{Mann20, Mann21a}. According to these models, the deep conceptual
+meaning of a document may be captured by a feature vector in a high-dimensional
+representation space, wherein nearby vectors reflect conceptually related
+documents. A model that succeeds at capturing an analogue of ``understanding'' is
+able to assign nearby feature vectors to two conceptually related documents,
+\textit{even when the specific words contained in those documents have very little
+overlap}.
 
 Given these insights, what form might a representation of the sum total of a
-person's knowledge take (speculatively)? First, we might require a means of
-systematically describing or representing the nearly infinite set of possible
-things a person could know. Second, we might want to account for potential
-associations between different concepts. For example, the concepts of ``fish''
-and ``water'' might be associated in the sense that fish live in water. Third,
-knowledge may have a critical dependency structure, such that knowing about a
-particular concept might require first knowing about a set of other concepts.
-For example, understanding the concept of a fish swimming in water first
-requires understanding what fish and water \textit{are}. Fourth, as we learn,
-our ``current state of knowledge'' should change accordingly. Learning new
-concepts should both update our characterizations of ``what is known'' and also
+person's knowledge take? First, we might require a means of systematically
+describing or representing the nearly infinite set of possible things a person
+could know. Second, we might want to account for potential associations between
+different concepts. For example, the concepts of ``fish'' and ``water'' might
+be associated in the sense that fish live in water. Third, knowledge may have a
+critical dependency structure, such that knowing about a particular concept
+might require first knowing about a set of other concepts. For example,
+understanding the concept of a fish swimming in water first requires
+understanding what fish and water \textit{are}. Fourth, as we learn, our
+``current state of knowledge'' should change accordingly. Learning new concepts
+should both update our characterizations of ``what is known'' and also
 unlock any now-satisfied dependencies of those newly learned concepts so that
@@
 understanding, often by training participants to distinguish arbitrary or
-random features in otherwise meaningless categorized stimuli~\citep{ReilEtal82,
-Este86a, Este86b, GlucEtal02, AshbMadd05, HulbNorm15}. However the objective of
-real-world training, or learning from life experiences more generally, is often
-to develop new knowledge that may be applied in \textit{useful} ways in the
-future. In this sense, the gap between modern learning theories and modern
-pedagogical approaches that inform classroom learning strategies is enormous:
-most of our theories about \textit{how} people learn are inspired by
-experimental paradigms and models that have only peripheral relevance to the
-kinds of learning that students and teachers actually seek~\citep{Macl05,
-HallGree08}. To help bridge this gap, our study uses course materials from real
-online courses to inform, fit, and test models of real-world conceptual
-learning. We also provide a demonstration of how our models can be used to
-construct ``maps'' of what students know, and how their knowledge changes with
-training. In addition to helping to visually capture knowledge (and changes in
-knowledge), we hope that such maps might lead to real-world tools for improving
-how we educate. Taken together, our work shows that existing course materials
-and evaluative tools like short multiple-choice quizzes may be leveraged to
-gain highly detailed insights into what students know and how they learn.
+random features in otherwise meaningless categorized stimuli~\citep{ReilEtal82, Este86a, Este86b, GlucEtal02, AshbMadd05, HulbNorm15}. However the
+objective of real-world training, or learning from life experiences more
+generally, is often to develop new knowledge that may be applied in
+\textit{useful} ways in the future. In this sense, the gap between modern
+learning theories and modern pedagogical approaches that inform classroom
+learning strategies is enormous: most of our theories about \textit{how} people
+learn are inspired by experimental paradigms and models that have only
+peripheral relevance to the kinds of learning that students and teachers
+actually seek~\citep{Macl05, HallGree08}. To help bridge this gap, our study
+uses course materials from real online courses to inform, fit, and test models
+of real-world conceptual learning. We also provide a demonstration of how our
+models can be used to construct ``maps'' of what students know, and how their
+knowledge changes with training. In addition to helping to visually capture knowledge
+(and changes in knowledge), we hope that such maps might lead to real-world
+tools for improving how we educate. Taken together, our work shows that
+existing course materials and evaluative tools like short multiple-choice
+quizzes may be leveraged to gain highly detailed insights into what students
+know and how they learn.
 
@@
 coordinates), their ``level of knowledge'' should change relatively gradually.
-To begin to test this smoothness assumption, we sought to track participants'
-knowledge and how it changed over time in response to training. Two overarching
-goals guide our approach. First, we want to gain detailed insights into what
-learners know at different points in their training. For example, rather than
-simply reporting on the proportions of questions participants answer correctly
-(i.e., their overall performance), we seek estimates of their knowledge about a
-variety of specific concepts. Second, we want our approach to be potentially
-scalable to large numbers of diverse concepts, courses, and students. This
-requires that the conceptual content of interest be discovered
-\textit{automatically}, rather than relying on manually produced ratings or
-labels.
+To begin to test this smoothness assumption, we sought
+to track participants' knowledge and how it changed over time in response to
+training. Two overarching goals guide our approach. First, we want to gain
+detailed insights into what learners know at different points in their
+training. For example, rather than simply reporting on the proportions of
+questions participants answer correctly (i.e., their overall performance), we
+seek estimates of their knowledge about a variety of specific concepts.
+Second, we want our approach to be potentially scalable to large numbers of
+diverse concepts, courses, and students. This requires that the conceptual content of
+interest be discovered \textit{automatically}, rather than relying on
+manually produced ratings or labels.
 
@@
     \caption{\textbf{Experimental paradigm.} Participants alternate between
-    completing three 13-question multiple-choice quizzes and watching two Khan
-    Academy lectures. Each quiz contains a mix of 5 questions about Lecture~1,
-    5 questions about Lecture~2, and 3 questions about general physics
-    knowledge. The specific questions reflected on each quiz, and the orders of
-    each quiz's questions, were randomized across participants.}
+    completing three 13-question multiple-choice quizzes and watching two Khan Academy
+    lectures. Each quiz contains a mix of 5 questions about Lecture~1, 5
+    questions about Lecture~2, and 3 questions about general physics knowledge. The
+    specific questions reflected on each quiz, and the orders of each quiz's
+    questions, were randomized across participants.}
 
@@
 related content, so that we could test our approach's ability to distinguish
-similar conceptual content. To this end, we chose two videos from the same Khan
-Academy course domain, ``Cosmology and Astronomy.'' Third, we sought to
-minimize dependencies and specific overlap between the videos. For example, we
-did not want participants' abilities to understand one video to (directly)
-influence their abilities to understand the other. To satisfy this last
-criterion, we chose videos from two different lecture series (Lectures~1 and 2
-were from the ``Scale of the Universe'' and ``Stars, Black Holes, and
-Galaxies'' series, respectively).
+similar conceptual content. To this end, we chose two videos from the same
+Khan Academy course domain, ``Cosmology and
+Astronomy.'' Third, we sought to minimize dependencies and specific overlap
+between the videos. For example, we did not want participants' abilities to
+understand one video to (directly) influence their abilities to understand the
+other. To satisfy this last criterion, we chose videos from two different
+lecture series (Lectures~1 and 2 were from the ``Scale of the Universe'' and
+``Stars, Black Holes, and Galaxies'' series, respectively).
 
@@
 enable us to evaluate participants' knowledge about each individual lecture,
-along with related knowledge about physics concepts not specifically presented
-in either video (see Supp. Tab.~\questions~for the full list of questions in
-our stimulus pool). Participants answered questions randomly drawn from each
-content area (Lecture~1, Lecture~2, and general physics knowledge) on each of
-the three quizzes. Quiz~1 was intended to assess participants' ``baseline''
-knowledge before training, Quiz~2 assessed knowledge after watching the
-\textit{Four Fundamental Forces} video (i.e., Lecture~1), and Quiz~3 assessed
-knowledge after watching the \textit{Birth of Stars} video (i.e., Lecture~2).
+along with related knowledge about physics concepts not specifically presented in either
+video (see Supp. Tab.~\questions~for the full list of questions in our stimulus
+pool). Participants answered questions randomly drawn from each content area
+(Lecture~1, Lecture~2, and general physics knowledge) on each of the three
+quizzes. Quiz~1 was intended to assess participants' ``baseline'' knowledge
+before training, Quiz~2 assessed knowledge after watching the \textit{Four
+Fundamental Forces} video (i.e., Lecture~1), and Quiz~3 assessed knowledge
+after watching the \textit{Birth of Stars} video (i.e., Lecture~2).
 
@@
 
-    \caption{\textbf{Modeling course content.} \textbf{A. Building a document
-    pool from sliding windows of text.} We decompose each lecture's transcript
-    into a series of overlapping sliding windows. The full set of transcript
-    snippets (across all windows) may be treated as a set of ``documents'' for
-    training a text embedding model. \textbf{B. Constructing lecture content
-    \textit{trajectories}.} After training the model on the sliding windows
-    from both lectures, we transform each lecture into a ``trajectory'' through
-    text embedding space by joining the embedding coordinates of successive
-    sliding windows parsed from its transcript. \textbf{C. Embedding multiple
-    lectures and questions in a shared space.} We apply the same model (trained
-    on the two lectures' windows) to both lectures, along with the text of each
-    question in our pool (Supp. Tab.~\questions), to project them into a shared
-    text embedding space. This results in one trajectory per lecture and one
-    coordinate for each question. Here, we have projected the 15-dimensional
-    embeddings onto their first 3 principal components for visualization.}
+    \caption{\textbf{Modeling course content.} \textbf{A. Building a document pool
+    from sliding windows of text.} We decompose each lecture's transcript into a
+    series of overlapping sliding windows. The full set of transcript snippets (across
+    all windows) may be treated as a set of ``documents'' for training a text
+    embedding model. \textbf{B. Constructing lecture content
+    \textit{trajectories}.} After training the model on the sliding windows from
+    both lectures, we transform each lecture into a ``trajectory'' through text
+    embedding space by joining the embedding coordinates of successive sliding
+    windows parsed from its transcript. \textbf{C. Embedding multiple lectures and
+    questions in a shared space.} We apply the same model (trained on the two
+    lectures' windows) to both lectures, along with the text of each question in
+    our pool (Supp. Tab.~\questions), to project them into a shared text embedding space.
+    This results in one trajectory per lecture and one coordinate for each
+    question. Here, we have projected the 15-dimensional embeddings onto their first
+    3 principal components for visualization.}
 
@@
 Transforming the text from every sliding window with the model yielded a
-number-of-windows by number-of-topics (15) topic-proportions matrix describing
-the unique mixture of broad themes from both lectures reflected in each
-window's text. Each window's ``topic vector'' (i.e., column of the
-topic-proportions matrix) is analogous to a coordinate in a 15-dimensional
-space whose axes are topics discovered by the model. Within this space, each
-lecture's sequence of topic vectors (i.e., corresponding to its transcript's
-overlapping text snippets across sliding windows) forms a \textit{trajectory}
-that captures how its conceptual content unfolds over time
-(Fig.~\ref{fig:sliding-windows}B). We resampled these trajectories to a
-resolution of one topic vector for each second of video (i.e., 1~Hz).
+number-of-windows by number-of-topics (15) topic-proportions matrix
+describing the unique mixture of broad themes from both lectures reflected in
+each window's text. Each window's ``topic vector'' (i.e., column of the
+topic-proportions matrix) is analogous to a coordinate in a 15-dimensional space whose axes
+are topics discovered by the model. Within this space, each lecture's sequence
+of topic vectors (i.e., corresponding to its transcript's overlapping text
+snippets across sliding windows) forms a \textit{trajectory} that captures how
+its conceptual content unfolds over time (Fig.~\ref{fig:sliding-windows}B). We
+resampled these trajectories to a resolution of one topic vector for each
+second of video (i.e., 1~Hz).
 
@@
 and question set (averaging across time and questions, respectively) reveals a
-striking correspondence (Supp. Fig.~\topicWeights). Specifically, the average
-topic weights from Lecture~1 are strongly correlated with the average topic
-weights from Lecture~1 questions ($r(13) = 0.809,~p < 0.001$, 95\% confidence
-interval (CI)~$= [0.633,~0.962]$), and the average topic weights from Lecture~2
-are strongly correlated with the average topic weights from Lecture~2 questions
+striking correspondence (Supp. Fig.~\topicWeights). Specifically, the average topic
+weights from Lecture~1 are strongly correlated with the average topic weights
+from Lecture~1 questions ($r(13) = 0.809,~p < 0.001$, 95\% confidence interval
+(CI)~$= [0.633,~0.962]$), and the average topic weights from Lecture~2 are
+strongly correlated with the average topic weights from Lecture~2 questions
 ($r(13) = 0.728,~p = 0.002$, 95\% CI~$= [0.456,~0.920]$). At the same time, the
-average topic weights from the two lectures are \textit{negatively} correlated
-with their non-matching question sets (Lecture~1 video vs.~Lecture~2 questions:
-$r(13) = -0.547,~p = 0.035$, 95\% CI~$= [-0.812, ~-0.231]$; Lecture~2 video
-vs.~Lecture~1 questions: $r(13) = -0.612,~p = 0.015$, 95\% CI~$=
-[-0.874,~-0.281]$), indicating that the topic model also exhibits some degree
-of specificity. The full set of pairwise comparisons between average topic
-weights for the lectures and question sets is reported in Supplementary
-Figure~\topicWeights.
+average topic weights from the two lectures are \textit{negatively} correlated with
+their non-matching question sets (Lecture~1 video vs.~Lecture~2 questions: $r(13) =
+-0.547,~p = 0.035$, 95\% CI~$= [-0.812, ~-0.231]$; Lecture~2 video vs.~Lecture~1 questions: $r(13)
+= -0.612,~p = 0.015$, 95\% CI~$= [-0.874,~-0.281]$), indicating that the topic model
+also exhibits some degree of specificity. The full set of pairwise comparisons
+between average topic weights for the lectures and question sets is reported in
+Supplementary Figure~\topicWeights.
 
@@
 
-    \caption{\textbf{Lecture and question topic overlap.} \textbf{A. Topic
-    weight variability}. The bar plots display the variance of each topic's
-    weight across lecture timepoints (top row) and questions (bottom row);
-    colors denote topics. The top-weighted words from the most ``expressive''
-    (i.e., variable across observations) topic from each lecture are displayed
-    in the upper right (orange: topic 2; yellow-green: topic 4). The
-    top-weighted words from the full set of topics may be found in
-    Supplementary Table~\topics. \textbf{B. Relationships between topic weight
-    variability.} Pairwise correlations between the distributions of topic
+    \caption{\textbf{Lecture and question topic overlap.} \textbf{A. Topic weight
+    variability}. The bar plots display the variance of each topic's weight across
+    lecture timepoints (top row) and questions (bottom row); colors denote topics.
+    The top-weighted words from the most ``expressive'' (i.e., variable across
+    observations) topic from each lecture are displayed in the upper right (orange:
+    topic 2; yellow-green: topic 4). The top-weighted words from the full set of
+    topics may be found in Supplementary Table~\topics. \textbf{B. Relationships between topic
+    weight variability.} Pairwise correlations between the distributions of topic
     weight variance for each lecture and question set. Each row and column
@@
 \end{figure}
-
-It is important to clarify that although we use topic model-derived embeddings
-to \textit{characterize} the conceptual content of the lectures and questions,
-we do not claim that the topic model itself \textit{understands} the conceptual
-content of the lectures or questions. Rather, we view the topic model as a tool
-for capturing the \textit{structure} of the conceptual content of the lectures
-and questions in a way that enables us to capture, quantify, and track and
-predict participants' knowledge.
 
@@
 Intuitively, the variability in the expression of a given topic relates to how
-much ``information''~\citep{Fish22} the lecture (or question set) reflects
-about that topic. For example, suppose a given topic is weighted on heavily
+much ``information''~\citep{Fish22} the lecture (or question set) reflects about
+that topic. For example, suppose a given topic is weighted on heavily
 throughout a lecture. That topic might be characteristic of some aspect or
@@
 expression (over time and across questions) was similar for the Lecture~1 video
-and questions ($r(13) = 0.824,~p<0.001$, 95\% CI~$= [0.696,~0.973]$) and the
-Lecture~2 video and questions ($r(13) = 0.801,~p<0.001$, 95\% CI~$=
-[0.539,~0.958]$). Simultaneously, as reported in Figure~\ref{fig:topics}B, the
-variability in topic expression across \textit{different} videos and
-lecture-specific questions (i.e., Lecture~1 video vs.~Lecture~2 questions;
-Lecture~2 video vs.~Lecture~1 questions) were negatively correlated, and
-neither video's topic variability was reliably correlated with the topic
-variability across general physics knowledge questions. Taken together, the
-analyses reported in Figure~\ref{fig:topics} and Supplementary
-Figure~\topicWeights~indicate that a topic model fit to the videos' transcripts
-can also reveal correspondences (at a coarse scale) between the lectures and
-questions.
+and questions ($r(13) = 0.824,~p<0.001$, 95\% CI~$= [0.696,~0.973]$) and the Lecture~2
+video and questions ($r(13) = 0.801,~p<0.001$, 95\% CI~$= [0.539,~0.958]$).
+Simultaneously, as reported in Figure~\ref{fig:topics}B, the variability in
+topic expression across \textit{different} videos and lecture-specific
+questions (i.e., Lecture~1 video vs.~Lecture~2 questions; Lecture~2 video
+vs.~Lecture~1 questions) were negatively correlated, and neither
+video's topic variability was reliably correlated with the topic variability
+across general physics knowledge questions. Taken together, the analyses
+reported in Figure~\ref{fig:topics} and Supplementary Figure~\topicWeights~indicate that a topic
+model fit to the videos' transcripts can also reveal correspondences (at a
+coarse scale) between the lectures and questions.
 
@@
 coarse scale, at a finer scale, each moment of a lecture typically covers a
-narrower range of content. Given the correspondence we found between the
-variability in topic expression across moments of each lecture and questions
-from its corresponding set (Fig.~\ref{fig:topics}), we wondered whether the
-text embedding model might additionally capture these conceptual relationships
-at a finer scale. For example, if a particular question asks about the content
-from one small part of a lecture, we wondered whether the text embeddings could
-be used to automatically identify the ``matching'' moment(s) in the lecture. To
-explore this, we computed the correlation between each question's topic weights
-and the topic weights for each second of its corresponding lecture, and found
-that each question appeared to be temporally specific
-(Fig.~\ref{fig:question-correlations}). In particular, most questions' topic
-vectors were maximally correlated with a well-defined (and relatively narrow)
-range of timepoints from their corresponding lectures, and the correlations
-fell off sharply outside of that range. We also qualitatively examined the
-best-matching intervals for each question by comparing the question's text to
-the text of the most-correlated parts of the lectures. Despite that the
-questions were excluded from the text embedding model's training set, in
-general we found (through manual inspection) a close correspondence between the
-conceptual content that each question probed and the content covered by the
-best-matching moments of the lectures. Two representative examples are shown at
-the bottom of Figure~\ref{fig:question-correlations}.
+narrower range of content. Given the correspondence we found between the variability
+in topic expression across moments of each lecture and questions from its
+corresponding set (Fig.~\ref{fig:topics}), we wondered whether the text embedding model
+might additionally capture these conceptual relationships at a finer scale.
+For example, if a particular question asks about the content from one small
+part of a lecture, we wondered whether the text embeddings could be used to
+automatically identify the ``matching'' moment(s) in the lecture. To explore this,
+we computed the correlation between each question's topic weights and the topic weights
+for each second of its corresponding lecture, and found that each question appeared to be
+temporally specific (Fig.~\ref{fig:question-correlations}). In particular, most questions'
+topic vectors were maximally correlated with a well-defined (and relatively
+narrow) range of timepoints from their corresponding lectures, and the
+correlations fell off sharply outside of that range. We also qualitatively examined the
+best-matching intervals for each question by comparing the question's text
+to the text of the most-correlated parts of the lectures.
+Despite that the questions were excluded from the text embedding model's
+training set, in general we found (through manual inspection) a close
+correspondence between the conceptual content that each question probed and
+the content covered by the best-matching moments of the lectures. Two
+representative examples are shown at the bottom of
+Figure~\ref{fig:question-correlations}.
 
@@
 
-    \caption{\textbf{Which parts of each lecture are captured by each
-    question?} Each panel displays timeseries plots showing how each question's
-    topic vector correlates with each video timepoint's topic vector (Panel
-    \textbf{A.}: correlations for the \textit{Four Fundamental Forces} lecture
-    and associated questions; Panel \textbf{B.}: correlations for the
-    \textit{Birth of Stars} lecture and associated questions). The colors
-    denote question identities. The diamonds in each panel denote the moment of
-    peak correlation between the indicated question and the lecture trajectory.
-    The associated questions' text and snippets of the lectures' transcripts
-    from the surrounding 30 seconds, are displayed at the bottom of the
-    figure.}
+    \caption{\textbf{Which parts of each lecture are captured by each question?}
+    Each panel displays timeseries plots showing how each question's topic vector
+    correlates with each video timepoint's topic vector (Panel \textbf{A.}:
+    correlations for the \textit{Four Fundamental Forces} lecture and associated
+    questions; Panel \textbf{B.}: correlations for the \textit{Birth of Stars}
+    lecture and associated questions). The colors denote question identities. The
+    diamonds in each panel denote the moment of peak correlation between the
+    indicated question and the lecture trajectory. The associated questions' text
+    and snippets of the lectures' transcripts from the surrounding 30 seconds, are
+    displayed at the bottom of the figure.}
 
@@
 missed three questions about three \textit{different} concepts (e.g., $A$, $B$,
-and $C$). But if we wanted to help these two students fill in the ``gaps'' in
-their understandings, we might do well to focus specifically on concept $A$ for
-the first student, but to also add in materials pertaining to concepts $B$ and
-$C$ for the second student. In other words, raw ``proportion-correct'' measures
-may capture \textit{how much} a student knows, but not \textit{what} they know.
-We wondered whether our modeling framework might enable us to (formally and
-automatically) infer participants' knowledge at the scale of individual
-concepts (e.g., as captured by a single moment of a lecture).
+and $C$). But if we wanted to help these two students fill in the ``gaps'' in their
+understandings, we might do well to focus specifically on concept $A$ for the first student,
+but to also add in materials pertaining to concepts $B$ and $C$ for the second
+student. In other words, raw ``proportion-correct'' measures may capture
+\textit{how much} a student knows, but not \textit{what} they know. We wondered
+whether our modeling framework might enable us to (formally and automatically)
+infer participants' knowledge at the scale of individual concepts (e.g., as
+captured by a single moment of a lecture).
 
@@
 this approach separately for the questions from each quiz participants took
-throughout the experiment. From just a few questions per quiz
-(see~\nameref{subsec:traces}), we obtain a high-resolution snapshot (at the
-time each quiz was taken) of what the participants knew about any moment's
-content, from either of the two lectures they watched (comprising a total of
-1,100 samples across the two lectures).
+throughout the experiment. From just a few questions per quiz (see~\nameref{subsec:traces}), we obtain a
+high-resolution snapshot (at the time each quiz was taken) of what the
+participants knew about any moment's content, from either of the two lectures
+they watched (comprising a total of 1,100 samples across the two lectures).
 
@@
     questions about the content reflected in each moment of the lecture (see
-    \nameref{subsec:traces}), using responses from a single quiz (color). The
-    traces are averaged across participants. \textbf{B. Average estimated
-    knowledge about the \textbf{Four Fundamental Forces}.} Each bar displays
-    the across-timepoint average knowledge, estimated using the responses to
-    one quiz's questions. \textbf{C. Moment-by-moment knowledge about the
-    \textit{Birth of Stars}}. The panel is in the same format as Panel A, but
-    here the knowledge estimates are for the moment-by-moment content of the
-    \textit{Birth of Stars} lecture. \textbf{D. Average estimated knowledge
-    about the \textit{Birth of Stars}.} The panel is in the same format as
-    Panel B, but here the knowledge estimates are for the content of the
-    \textit{Birth of Stars} lecture. All panels: error ribbons and error bars
-    denote 95\% confidence intervals, estimated across participants.}
+    \nameref{subsec:traces}), using responses from a single
+    quiz (color). The traces are averaged across participants. \textbf{B.
+    Average estimated knowledge about the \textbf{Four Fundamental Forces}.}
+    Each bar displays the across-timepoint average knowledge, estimated using
+    the responses to one quiz's questions. \textbf{C. Moment-by-moment
+    knowledge about the \textit{Birth of Stars}}. The panel is in the same
+    format as Panel A, but here the knowledge estimates are for the
+    moment-by-moment content of the \textit{Birth of Stars} lecture. \textbf{D.
+    Average estimated knowledge about the \textit{Birth of Stars}.} The panel
+    is in the same format as Panel B, but here the knowledge estimates are for
+    the content of the \textit{Birth of Stars} lecture. All panels: error
+    ribbons and error bars denote 95\% confidence intervals, estimated across
+    participants.}
 
@@
 
-While the timecourses in Figure~\ref{fig:knowledge-timeseries}A and C provide
-detailed \textit{estimates} about participants' knowlege, these estimates are
-of course only \textit{useful} to the extent that they accurately reflect what
-participants actually know. As one sanity check, we anticipated that the
-knowledge estimates should reflect a content-specific ``boost'' in
-participants' knowledge after watching each lecture. In other words, if
-participants learn about each lecture's content when they watch each lecture,
-the knowledge estimates should capture that. After watching the \textit{Four
-Fundamental Forces} lecture, participants should exhibit more knowledge for the
-content of that lecture than they had before, and that knowledge should persist
-for the remainder of the experiment. Specifically, knowledge about that
-lecture's content should be relatively low when estimated using Quiz~1
-responses, but should increase when estimated using Quiz~2 or 3 responses
-(Fig.~\ref{fig:knowledge-timeseries}B). Indeed, we found that participants'
-estimated knowledge about the content of the \textit{Four Fundamental Forces}
-was substantially higher on Quiz~2 versus Quiz~1 ($t(49) = 8.764,~p < 0.001$)
-and on Quiz~3 versus Quiz~1 ($t(49) = 10.519,~p < 0.001$). We found no reliable
-differences in estimated knowledge about that lecture's content on Quiz~2
-versus 3 ($t(49) = 0.160,~p = 0.874$). Similarly, we hypothesized (and
-subsequently confirmed) that participants should show greater estimated
-knowledge about the content of the \textit{Birth of Stars} lecture after
-(versus before) watching it (Fig.~\ref{fig:knowledge-timeseries}D).
-Specifically, since participants watched that lecture after taking Quiz~2 (but
-before Quiz~3), we hypothesized that their knowledge estimates should be
-relatively low on Quizzes~1 and 2, but should show a ``boost'' on Quiz~3.
-Consistent with this prediction, we found no reliable differences in estimated
-knowledge about the \textit{Birth of Stars} lecture content on Quizzes~1 versus
-2 ($t(49) = 1.013,~p = 0.316$), but the estimated knowledge was substantially
-higher on Quiz~3 versus 2 ($t(49) = 10.561,~p < 0.001$) and Quiz~3 versus 1
-($t(49) = 8.969,~p < 0.001$).
+While the timecourses in
+Figure~\ref{fig:knowledge-timeseries}A and C provide detailed
+\textit{estimates} about participants' knowlege, these estimates are of course only
+\textit{useful} to the extent that they accurately reflect what participants
+actually know. As one sanity check, we anticipated that the knowledge estimates
+should reflect a content-specific ``boost'' in participants' knowledge after
+watching each lecture. In other words, if participants learn about each
+lecture's content when they watch each lecture, the knowledge estimates should
+capture that. After watching the \textit{Four Fundamental Forces} lecture,
+participants should exhibit more knowledge for the content of that lecture than
+they had before, and that knowledge should persist for the remainder of the
+experiment. Specifically, knowledge about that lecture's content should be
+relatively low when estimated using Quiz~1 responses, but should increase when
+estimated using Quiz~2 or 3 responses (Fig.~\ref{fig:knowledge-timeseries}B).
+Indeed, we found that participants' estimated knowledge about the content of
+the \textit{Four Fundamental Forces} was substantially higher on Quiz~2 versus
+Quiz~1 ($t(49) = 8.764,~p < 0.001$) and on Quiz~3 versus Quiz~1 ($t(49) =
+10.519,~p < 0.001$). We found no reliable differences in estimated knowledge
+about that lecture's content on Quiz~2 versus 3 ($t(49) = 0.160,~p = 0.874$).
+Similarly, we hypothesized (and subsequently confirmed) that participants
+should show greater estimated knowledge about the content of the \textit{Birth of
+Stars} lecture after (versus before) watching it
+(Fig.~\ref{fig:knowledge-timeseries}D). Specifically, since participants
+watched that lecture after taking Quiz~2 (but before Quiz~3), we hypothesized
+that their knowledge estimates should be relatively low on Quizzes~1 and 2, but
+should show a ``boost'' on Quiz~3. Consistent with this prediction, we found no
+reliable differences in estimated knowledge about the \textit{Birth of Stars}
+lecture content on Quizzes~1 versus 2 ($t(49) = 1.013,~p = 0.316$), but the
+estimated knowledge was substantially higher on Quiz~3 versus 2 ($t(49) =
+10.561,~p < 0.001$) and Quiz~3 versus 1 ($t(49) = 8.969,~p < 0.001$).
 
 If we are able to accurately estimate a participant's knowledge about the
-content tested by a given question, our estimates of their knowledge should
-carry some predictive information about whether the participant is likely to
-answer that question correctly or incorrectly. We developed a statistical
-approach to test this claim. For each question, in turn, we used
-Equation~\ref{eqn:prop} to estimate each participant's knowledge at the given
-question's embedding space coordinate, using all \textit{other} questions that
-participant answered on the same quiz. For each quiz, we grouped these
-estimates into two distributions: one for the estimated knowledge at the
-coordinates of \textit{correctly} answered questions, and another for the
-estimated knowledge at the coordinates of \textit{incorrectly} answered
-questions (Fig.~\ref{fig:predictions}). We then used independent samples
-$t$-tests to compare the means of these distributions of estimated knowledge.
+content tested by a given question, our estimates of their knowledge should carry some
+predictive information about whether the participant is likely to answer that
+question correctly or incorrectly. We developed a statistical approach to test this claim.
+For each question, in turn, we used Equation~\ref{eqn:prop} to estimate each
+participant's knowledge at the given question's embedding space coordinate,
+using all \textit{other} questions that participant answered on the same quiz.
+For each quiz, we grouped these estimates into two distributions: one for the
+estimated knowledge at the coordinates of \textit{correctly} answered
+questions, and another for the estimated knowledge at the coordinates of
+\textit{incorrectly} answered questions (Fig.~\ref{fig:predictions}). We then
+used independent samples $t$-tests to compare the means of these distributions
+of estimated knowledge.
 
@@
     \centering
-    \includegraphics[width=0.7\textwidth]{figs/predict-knowledge-questions}
+    \includegraphics[width=\textwidth]{figs/held-out-question-analysis}
 
@@
 knowledge about Lecture~2 and general physics concepts should be roughly
-unchanged from before they watched Lecture~1. After watching the second
-lecture, estimated knowledge (from the third quiz; Fig.~\ref{fig:predictions},
-right panel) for \textit{all} questions exhibited a positive shift. However,
-the estimated knowledge for held-out correctly answered questions remained
-greater than that for held-out incorrectly answered questions ($t(628) =
-2.045,~p = 0.041$). This third contrast reflects a ceiling effect: when
-knowledge is relatively high everywhere, the signal differentiating what is
-known versus unknown is relatively weak. Taken together, this set of analyses
-demonstrates that our knowledge prediction framework is most informative when
-participants exhibit variability in their knowledge of the content captured by
-the text embedding model.
-
-\begin{figure}[t]
-    \centering
-    \includegraphics[width=\textwidth]{figs/knowledge-smoothness}
-
-    \caption{\textbf{Caption title.} Caption content.}
-
-    \label{fig:smoothness}
-\end{figure}
+unchanged from before they watched Lecture~1. After watching the second lecture,
+estimated knowledge (from the third quiz; Fig.~\ref{fig:predictions}, right
+panel) for \textit{all} questions exhibited a positive shift. However, the
+estimated knowledge for held-out correctly answered questions remained
+greater than that for held-out incorrectly answered questions ($t(628) = 2.045,~p
+= 0.041$). This third contrast reflects a ceiling effect: when knowledge is
+relatively high everywhere, the signal differentiating what is known versus
+unknown is relatively weak. Taken together, this set of analyses demonstrates
+that our knowledge prediction framework is most informative when participants
+exhibit variability in their knowledge of the content captured by the text
+embedding model.
 
@@
 lectures participants watched, we first fit a new topic model to the lectures'
-sliding windows with (up to)~$k = 100$~topics. Conceptually, increasing the
-number of topics used by the model functions to increase the ``resolution'' of
-the embedding space, providing a greater ability to estimate knowledge for
-content that is highly similar to (but not precisely the same as) that
-contained in the two lectures. This change in the number of topics overcame an
-undesireable behavior in the UMAP embedding procedure~\citep{McInEtal18},
-whereby embedding coordinates for the 15-topic model tended to be ``clumped''
-into separated clusters, rather than forming a smooth trajectory through the 2D
-space. When we increased the number of topics to 100, the embedding coordinates
-in the 2D space formed a smooth trajectory through the space, with
-substantially less clumping (Fig.~\ref{fig:knowledge-maps}). We note that we
-used these 2D maps solely for visualization; all relevant comparisons, distance
-computations, and statistical tests we report above were carried out in the
-original 15-dimensional space, using the 15-topic model. Aside from increasing
-the number of topics from 15 to 100, all other procedures and model parameters
-were carried over from the preceding analyses. As in our other analyses, we
-resampled each lecture's topic trajectory to 1~Hz and projected each question
-into a shared text embedding space.
+sliding windows with (up to)~$k = 100$~topics.
+Conceptually, increasing the number of topics used by the model functions to
+increase the ``resolution'' of the embedding space, providing a greater ability to
+estimate knowledge for content that is highly similar to (but not precisely the same as)
+that contained in the two lectures.
+Aside from increasing the number of topics from 15 to 100, all other
+procedures and model parameters were carried over from the preceding analyses.
+As in our other analyses, we resampled each lecture's topic trajectory to 1~Hz
+and projected each question into a shared text embedding space.
 
@@
     and~\individualKnowledgeMapsC. \textbf{B. Average ``learning maps''
-    estimated between each successive pair of quizzes.} The learning maps
-    follow the same general format as the knowledge maps in Panel A, but here
-    the shading at each coordinate indicates the \textit{difference} between
-    the corresponding coordinates in the indicated \textit{pair} of knowledge
+    estimated between each successive pair of quizzes.} The learning maps follow
+    the same general format as the knowledge maps in Panel A, but here the
+    shading at each coordinate indicates the \textit{difference} between the
+    corresponding coordinates in the indicated \textit{pair} of knowledge
     maps---i.e., how much the estimated knowledge ``changed'' between the two
@@
     Figures~\individualLearningMapsA~and~\individualLearningMapsB. \textbf{C.
-    Word clouds for sampled points in topic space.} Each word cloud displays
-    the weighted blend of words underlying the topic proportions represented at
-    the corresponding colored star's location on the maps. In each word cloud,
-    the words' relative sizes correspond to their relative weights at the
-    starred location, and their colors indicate their relative weights in the
+    Word clouds for sampled points in topic space.} Each word cloud displays the
+    weighted blend of words underlying the topic proportions represented at the
+    corresponding colored star's location on the maps. In each word cloud, the
+    words' relative sizes correspond to their relative weights at the starred
+    location, and their colors indicate their relative weights in the
     \textit{Four Fundamental Forces} (blue) versus \textit{Birth of Stars}
@@
 content that is nearby (i.e., related to) the content from the lecture they
-watched prior to taking Quiz~2. This localization is non-trivial: these
-knowledge estimates are informed only by the embedded coordinates of the
-\textit{quiz questions}, not by the embeddings of either lecture (see
-Eqn.~\ref{eqn:rbf-knowledge}). Finally, the knowledge map estimated from Quiz 3
-responses shows a second increase in knowledge, localized to the region
+watched prior to taking Quiz~2. This localization is non-trivial: these knowledge
+estimates are informed only by the embedded coordinates of the \textit{quiz
+questions}, not by the embeddings of either lecture
+(see Eqn.~\ref{eqn:rbf-knowledge}). Finally, the knowledge map estimated from Quiz
+3 responses shows a second increase in knowledge, localized to the region
 surrounding the embedding of the \textit{Birth of Stars} lecture participants
@@
 
-Another way of visualizing these content-specific increases in knowledge after
-participants viewed each lecture is displayed in
+Another way of visualizing these content-specific increases in knowledge
+after participants viewed each lecture is displayed in
 Figure~\ref{fig:knowledge-maps}B. Taking the point-by-point difference between
@@
 Because the 2D projection we used to construct the knowledge and learning maps
-is invertible, we may gain additional insights into these maps' meaning by
-reconstructing the original high-dimensional topic vector for any location on
-the map we are interested in. For example, this could serve as a useful tool
-for an instructor looking to better understand which content areas a student
-(or a group of students) knows well (or poorly). As a demonstration, we show
-the top-weighted words from the blends of topics reconstructed from three
+is invertible, we may gain additional insights into these maps' meaning
+by reconstructing the original high-dimensional topic vector for any location
+on the map we are interested in. For example, this could serve as a useful
+tool for an instructor looking to better understand which content areas a
+student (or a group of students) knows well (or poorly). As a demonstration, we
+show the top-weighted words from the blends of topics reconstructed from three
 example locations on the maps (Fig.~\ref{fig:knowledge-maps}C): one point near
 the \textit{Four Fundamental Forces} embedding (yellow), a second point near
-the \textit{Birth of Stars} embedding (orange), and a third point between the
-two lectures' embeddings (pink). As shown in the word clouds in the panel, the
-top-weighted words at the example coordinate near the \textit{Four Fundamental
-Forces} embedding tended to be weighted more heavily by the topics expressed in
-that lecture. Similarly, the top-weighted words at the example coordinate near
-the \textit{Birth of Stars} embedding tended to be weighted more heavily by the
-topics expressed in \textit{that} lecture. And the top-weighted words at the
-example coordinate between the two lectures' embeddings show a roughly even mix
-of words most strongly associated with each lecture.
+the \textit{Birth of Stars} embedding (orange), and a third point
+between the two lectures' embeddings (pink). As shown in the word clouds in the
+panel, the top-weighted words at the example coordinate near the \textit{Four
+Fundamental Forces} embedding tended to be weighted more heavily by the topics
+expressed in that lecture. Similarly, the top-weighted words at the example
+coordinate near the \textit{Birth of Stars} embedding tended to be weighted
+more heavily by the topics expressed in \textit{that} lecture. And the
+top-weighted words at the example coordinate between the two lectures'
+embeddings show a roughly even mix of words most strongly associated with each
+lecture.
 
@@
 changes with training. First, we show that our approach can automatically match
-the conceptual knowledge probed by individual quiz questions to the
-corresponding moments in lecture videos when those concepts were presented
+the conceptual knowledge probed by individual quiz questions to the corresponding
+moments in lecture videos when those concepts were presented
 (Fig.~\ref{fig:question-correlations}). Next, we demonstrate how we can
-estimate moment-by-moment ``knowledge traces'' that reflect the degree of
-knowledge participants have about each video's time-varying content, and
-capture temporally specific increases in knowledge after viewing each lecture
-(Fig.~\ref{fig:knowledge-timeseries}). We also show that these knowledge
-estimates can generalize to held-out questions (Fig.~\ref{fig:predictions}).
-Finally, we use our framework to construct visual maps that provide snapshot
-estimates of how much participants know about any concept within the scope of
-our text embedding model, and how much their knowledge of those concepts
-changes with training (Fig.~\ref{fig:knowledge-maps}).
-
-We view our work as making several contributions to the study of how people
-acquire conceptual knowledge. First, from a methodological standpoint, our
-modeling framework provides a systematic means of mapping out and
-characterizing knowledge in maps that have infinite (arbitrarily many) numbers
-of coordinates, and of ``filling out'' those maps using relatively small
-numbers of multiple choice quiz questions. Our experimental finding that we can
-use these maps to predict responses to held-out questions
-(Fig.~\ref{fig:predictions}) also has important psychological implications. One
-such psychological implication is that concepts that are assigned to nearby
-coordinates by the text embedding model also appear to be ``known to a similar
-extent'' (as reflected by participants' responses to held-out questions). This
-suggests that participants also \textit{conceptualize} similarly the content
-reflected by nearby embedding coordinates. A second psychological implication
-is that something about how participants' knowledge ``spreads'' across concepts
-is being captured by the knowledge maps we are inferring from their quiz
-responses (e.g., Figs.~\ref{fig:smoothness},~\ref{fig:knowledge-maps}). In
-other words, our study shows that knowledge about a given concept implies
-knowledge about related concepts.
-
-In our study, we characterize the ``coordinates'' of participants' knowledge
-using a relatively simple ``bag of words'' text embedding model~\citep[LDA;
-]{BleiEtal03}. More sophisticated text embedding models, such as
-transformer-based models~\citep{ViswEtal17, DevlEtal18, ChatGPT, TouvEtal23}
-can learn complex grammatical and semantic relationships between words,
-higher-order syntactic structures, sylistic features, and more. We considered
-using transformer-based models in our study, but we were surprised to find that
-the text embeddings derived from these models were surprisingly uninformative
-with respect to differentiating or otherwise characterizing the conceptual
-content of the lectures and questions we used. We suspect that this reflects a
-broader challenge in constructing models that are high-resolution within a
-given domain (e.g., the domain of physics lectures and questions) \textit{and}
-sufficiently broad so as to enable them to cover a wide range of domains. For
-example, we found that the embeddings derived even from much larger and more
-modern models like BERT~\citep{DevlEtal18}, GPT~\citep{ViswEtal17},
-LLaMa~\citep{TouvEtal23}, and others that are trained on enormous text corpora,
-end up yielding poor resolution within the content space spanned by indiviudal
-course videos (Supp. Fig.~\ldaVsBERT). Whereas the LDA embeddings of the
-lectures and questions are ``near'' each other (i.e., the convex hull enclosing
-the two lectures' trajectories is highly overlapping with the convex hull
-enclosing the questions' embeddings), the BERT embeddings of the lectures and
-questions are instead largely distinct (top row of Supp. Fig.~\ldaVsBERT). The
-LDA embeddings of the questions for each lecture and the corresponding
-lecture's trajectory are also similar. For example, as shown in
-Fig.~\ref{fig:sliding-windows}C, the LDA embeddings for \textit{Four
-Fundamental Forces} questions (blue dots) appear closer to the \textit{Four
-Fundamental Forces} lecture trajectory (blue line), whereas the LDA embeddings
-for \textit{Birth of Stars} questions (green dots) appear closer to the
-\textit{Birth of Stars} lecture trajectory (green line). The BERT embeddings of
-the lectures and questions do not show this property (Supp. Fig.~\ldaVsBERT).
-We also examined per-question ``content matches'' between individual questions
-and individual moments of each lecture
-(Figs.~\ref{fig:question-correlations},~\ldaVsBERT). The timeseries plot of
-individual questions' correlations are different from each other when computed
-using LDA (e.g., the traces can be clearly visually separated), whereas the
-correlations computed from BERT embeddings of different questions all look very
-similar. This tells us that LDA is capturing some differences in content
-between the questions, whereas BERT is not. The timeseries plots of individual
-questions' correlations have clear ``peaks'' when computed using LDA, but not
-when computed using BERT. This tells us that LDA is capturing a ``match''
-between the content of each question and a relatively well-defined time window
-of the corresponding lectures. The BERT embeddings appear to blur together the
-content of the questions versus specific moments of each lecture. Finally, we
-also compared the pairwise correlations between embeddings of questions within
-versus across content areas (i.e., content covered by the individual lectures,
-lecture-specific questions, and by the ``general physics knowledge''
-questions). The LDA embeddings show a strong contrast between same-content
-embeddings versus across-content embeddings. In other words, the embeddings of
-questions about the \textit{Four Fundamental Forces} material are highly
-correlated with the embeddings of the \textit{Four Fundamental Forces} lecture,
-but not with the embeddings of \textit{Birth of Stars}, questions about
-\textit{Birth of Stars}, or general physics knowledge questions. We see a
-similar pattern with the LDA embeddings of the \textit{Birth of Stars}
-questions (Fig.~\ref{fig:topics}, Supp. Fig.~\topicWeights). In contrast, the
-BERT embeddings are all highly correlated with each other (Supp.
-Fig.~\ldaVsBERT). Taken together, these comparisons illustrate how LDA (trained
-on the specific content in question) provides both coverage of the requisite
-material and specificity at the level of the content covered by individual
-questions. BERT, on the other hand, essentially assigns both lectures and all
-of the questions (which are all broadly about ``physics'') into a tiny region
-of its embedding space, thereby blurring out meaningful distinctions between
-different specific concepts covered by the lectures and questions. We note that
-these are not criticisms of BERT (or other large language models trained on
-large and diverse corpora). Rather, our point is that simple fine-tuned models
-trained on a relatively small but specialized corpus can outperform much more
-complicated models trained on much larger corpora, when we are specifically
-interested in capturing subtle conceptual differences at the level of a single
-course lecture or question. Of course if our goal had been to find a model that
-generalized to many different content areas, we would expect our approach to
-perform comparatively poorly relative to BERT or other much larger models. We
-suggest that bridging the tradeoff between high resolution within each content
-area versus the ability to generalize to many different content areas will be
-an important challenge for future work in this domain.
-
-At the opposite end of the spectrum from large language models, one could also
-imagine \textit{simplifying} some aspects of our LDA-based approach by
-computing simple word overlap metrics. For example, the Jaccard similarity
-between text $A$ and $B$ is computed as the number of unique words in the
-intersection of words from $A$ and $B$ divided by the number of unique words in
-the union of words from $A$ and $B$. In a supplemental analysis (Supp.
-Fig.~\jaccard), we compared the LDA-based question-lecture matches we reported
-in Figure~\ref{fig:question-correlations} with the Jaccard similarities between
-each question and each sliding window of text from the corresponding lecture.
-As shown in Supplementary Figure~\jaccard, this simple word-matching approach
-does not appear to capture the same level of specificity as the LDA-based
-approach. For example, whereas the LDA-based approach often yields a clear peak
-in the timeseries of correlations between each question and the corresponding
-lecture, the Jaccard similarity-based approach does not. Furthermore, these
-LDA-based matches appear to capture conceptual overlaps between the questions
-and lectures (Supp. Tab.~\matchTab), whereas simple word matching does not. For
-example, one of the example questions examined in Supplementary Figure~\jaccard
-asks ``Which of the following occurs as a cloud of atoms gets more dense?''.
-The LDA-based matches identify lecture timepoints where the releveant
-\textit{topics} are discussed (e.g., when words like ``cloud,'' ``atom,''
-``dense,'' etc., are mentioned \textit{together}). The Jaccard similarity-based
-matches, on the other hand, are strong when \textit{any} of these words are
-mentioned, even if they do not occur together.
+estimate moment-by-moment ``knowledge traces'' that reflect the degree of knowledge
+participants have about each video's time-varying content, and capture temporally
+specific increases in knowledge after viewing each lecture (Fig.~\ref{fig:knowledge-timeseries}).
+ We also show that these knowledge estimates can generalize to held-out questions
+(Fig.~\ref{fig:predictions}). Finally, we use our framework to construct visual
+maps that provide snapshot estimates of how much participants know about any
+concept within the scope of our text embedding model, and how much their
+knowledge of those concepts changes with training (Fig.~\ref{fig:knowledge-maps}).
 
 Over the past several years, the global pandemic has forced many educators to
-suddenly adapt to teaching remotely~\citep{MoseEtal21, ShimLee20, KawaEtal21,
-Whal20}. This change in world circumstances is happening alongside (and perhaps
-accelerating) geometric growth in the availability of high-quality online
-courses from platforms such as Khan Academy~\citep{Khan04},
-Coursera~\citep{Youn12}, EdX~\citep{Kolo13}, and others~\citep{RhoaEtal13}.
-Continued expansion of the global internet backbone and improvements in
-computing hardware have also facilitated improvements in video streaming,
-enabling videos to be easily shared and viewed by increasingly large segments
-of the world's population. This exciting time for online course instruction
-provides an opportunity to re-evaluate how we, as a global community, educate
-ourselves and each other. For example, we can ask: what defines an effective
-course or training program? Which aspects of teaching might be optimized and/or
-augmented by automated tools? How and why do learning needs and goals vary
-across people? How might we lower barriers of access to a high-quality
-education?
+suddenly adapt to teaching remotely~\citep{MoseEtal21, ShimLee20, KawaEtal21, Whal20}. This change
+in world circumstances is happening alongside (and perhaps accelerating)
+geometric growth in the availability of high-quality online courses from
+platforms such as Khan Academy~\citep{Khan04}, Coursera~\citep{Youn12},
+EdX~\citep{Kolo13}, and others~\citep{RhoaEtal13}. Continued expansion of the
+global internet backbone and improvements in computing hardware have also
+facilitated improvements in video streaming, enabling videos to be easily
+shared and viewed by increasingly large segments of the world's population. This
+exciting time for online course instruction provides an opportunity to
+re-evaluate how we, as a global community, educate ourselves and each other.
+For example, we can ask: what defines an effective course or training program?
+Which aspects of teaching might be optimized and/or augmented by automated tools? How and why do
+learning needs and goals vary across people? How might we lower barriers of access
+to a high-quality education?
 
@@
 to which two people's knowledge maps ``match'' or ``align'' in a given region
-of text embedding space might serve as a predictor of how effectively they will
-be able to communicate about the corresponding conceptual content.
+of text embedding space might serve as a predictor of how effectively they
+will be able to communicate about the corresponding conceptual content.
 
@@
 estimates about knowledge may be obtained from short quizzes shows one way that
-traditional approaches to evaluation in education may be extended. We hope that
-these advances might help pave the way for new approaches to teaching or
+traditional approaches to evaluation in education may be extended. We hope
+that these advances might help pave the way for new approaches to teaching or
 delivering educational content that are tailored to individual students'
@@
 We enrolled a total of 50 Dartmouth undergraduate students in our study.
-Participants received optional course credit for enrolling. We asked each
-participant to complete a demographic survey that included questions about
-their age, gender, native spoken language, ethnicity, race, hearing, color
-vision, sleep, coffee consumption, level of alertness, and several aspects of
-their educational background and prior coursework.
-
-Participants' ages ranged from 18 to 22 years (mean: 19.52 years; standard
-deviation: 1.09 years). A total of 15 participants reported their gender as
-male and 35 participants reported their gender as female. A total of 49
-participants reported their native language as ``English'' and 1 reported
-having another native language. A total of 47 participants reported their
-ethnicity as ``Not Hispanic or Latino'' and three reported their ethnicity as
-``Hispanic or Latino.'' Participants reported their races as White (32
-participants), Asian (14 participants), Black or African American (5
-participants), American Indian or Alaska Native (1 participant), and Native
-Hawaiian or Other Pacific Islander (1 participant). (Note that some
-participants selected multiple racial categories.)
-
-A total of 49 participants reporting having normal hearing and 1 participant
-reported having some hearing impairment. A total of 49 participants reported
-having normal color vision and 1 participant reported being color blind.
-Participants reported having had, on the night prior to testing, 2--4 hours of
-sleep (1 participant), 4--6 hours of sleep (9 participants), 6--8 hours of
-sleep (35 participants), or $8+$ hours of sleep (5 participants). They reported
-having consumed, on the same day and leading up to their testing session, 0
-cups of coffee (38 participants), 1 cup of coffee (10 participants), 3 cups of
-coffee (1 participant), or $4+$ cups of coffee (1 participant).
-
-No participants reported that their focus was currently impaired (e.g., by
-drugs or alcohol). Participants reported their current level of alertness, and
-we converted their responses to numerical scores as follows: ``very sluggish''
-(-2), ``a little sluggish'' (-1), ``neutral'' (0), ``fairly alert'' (1), and
-``very alert'' (2). Across all participants, a range of alertness levels were
-reported (range: -2--1; mean: -0.10; standard deviation: 0.84).
+Participants received optional course credit for enrolling. We asked each participant to
+complete a demographic survey that included questions about their age, gender,
+native spoken language, ethnicity, race, hearing, color vision, sleep, coffee
+consumption, level of alertness, and several aspects of their educational
+background and prior coursework.
+
+Participants' ages ranged from 18 to 22 years (mean: 19.52 years;
+standard deviation: 1.09 years). A total of 15 participants reported
+their gender as male and 35 participants reported their gender as
+female. A total of 49 participants reported their native language as
+``English'' and 1 reported having another native language. A total of
+47 participants reported their ethnicity as ``Not Hispanic or Latino''
+and three reported their ethnicity as ``Hispanic or Latino.''
+Participants reported their races as White (32 participants), Asian
+(14 participants), Black or African American (5 participants),
+American Indian or Alaska Native (1 participant), and Native Hawaiian or
+Other Pacific Islander (1 participant). (Note that some participants
+selected multiple racial categories.)
+
+A total of 49 participants reporting having normal hearing and 1
+participant reported having some hearing impairment. A total of 49
+participants reported having normal color vision and 1 participant
+reported being color blind.  Participants reported having had, on the
+night prior to testing, 2--4 hours of sleep (1 participant), 4--6
+hours of sleep (9 participants), 6--8 hours of sleep (35
+participants), or $8+$ hours of sleep (5 participants). They reported
+having consumed, on the same day and leading up to their testing
+session, 0 cups of coffee (38 participants), 1 cup of coffee (10
+participants), 3 cups of coffee (1 participant), or $4+$ cups of
+coffee (1 participant).
+
+No participants reported that their focus was currently impaired
+(e.g., by drugs or alcohol).  Participants reported their current
+level of alertness, and we converted their responses to numerical
+scores as follows: ``very sluggish'' (-2), ``a little sluggish'' (-1),
+``neutral'' (0), ``fairly alert'' (1), and ``very alert'' (2). Across
+all participants, a range of alertness levels were reported (range:
+-2--1; mean: -0.10; standard deviation: 0.84).
 
@@
 seconds) and \textit{Birth of Stars} (an introduction to how stars are formed;
-duration: 7 minutes and 57 seconds). All participants viewed the videos in the
-same order (i.e., \textit{Four Fundamental Forces} followed by \textit{Birth of
-Stars}). While we are not aware of any specific confounds of viewing order, nor
-have are we aware of how or why viewing order might influence our main
-findings, we acknowledge that we did not control for potential order effects in
-our study.
-
-We then hand-created 39 multiple-choice questions: 15 about the conceptual
-content of \textit{Four Fundamental Forces} (i.e., Lecture~1), 15 about the
-conceptual content of \textit{Birth of Stars} (i.e., Lecture~2), and 9
+duration: 7 minutes and 57 seconds). We then hand-created 39 multiple-choice
+questions: 15 about the conceptual content of \textit{Four Fundamental Forces} (i.e., Lecture~1),
+15 about the conceptual content of \textit{Birth of Stars} (i.e., Lecture~2), and 9
 questions that tested for general conceptual knowledge about basic physics
-(covering material that was not presented in either video). One of our group's
-undergraduate research assistants worked alongside a rotating Masters student
-to develop this set of questions (these researchers are acknowledged in our
-paper for their contribution, although they did not meet the criteria for
-authorship discussed with all team members at the start of the project, as
-determined by J.R.M.) The senior author (J.R.M.) tasked the pair of researchers
-with coming up with ``15 conceptual questions about each lecture, along with 9
-additional questions about general physics knowledge.'' To help broaden the set
-of lecture-specific questions, the researchers were further instructed to work
-through each lecture in small segments, identify what each segment was
-``about'' conceptually, and then write a question about that concept. The
-general physics questions were drawn from the researchers' coursework along
-with internet searches and brainstorming with the project team and other
-members of J.R.M.'s lab. The final set of questions (and response options) was
-reviewed and approved by J.R.M.
-
-We note that estimating the specific ``amount'' of conceptual understanding
-that each question ``requires'' to answer is somewhat subjective, and might
-even come down to the ``strategy'' a given participant uses to answer the
-question at that particular moment. The full set of questions and answer
-choices may be found in Supplementary Table~\questions.
+(covering material that was not presented in either video). The full set of
+questions and answer choices may be found in Supplementary Table~\questions.
 
@@
 multiple-choice quizzes: the first before viewing Lecture~1, the second between
-Lectures~1 and 2, and the third after viewing Lecture~2 (see
-Fig.~\ref{fig:experiment}). The questions appearing on each quiz, for each
+Lectures~1 and 2, and the third after viewing Lecture~2
+(see Fig.~\ref{fig:experiment}). The questions appearing on each quiz, for each
 participant, were randomly chosen from the full set of 39, with the constraints
-that (a) each quiz contain exactly 5 questions about Lecture~1, 5 questions
-about Lecture~2, and 3 questions about general physics knowledge, and (b) each
+that (a) each quiz contain exactly 5 questions about Lecture~1, 5 questions about
+Lecture~2, and 3 questions about general physics knowledge, and (b) each
 question appear exactly once for each participant. The orders of questions on
@@
 Dirichlet Allocation;~\citealp{BleiEtal03}), trained on a set of documents, to
-discover a set of (up to) $k$ ``topics'' or ``themes.'' Formally, each topic is
-defined as a distribution of weights over each word in the model's vocabulary
-(i.e., the union of all unique words, across all documents, excluding ``stop
-words.''). Conceptually, each topic is intended to give larger weights to words
-that are semantically related, as implied by their co-occurring in the same documents. After
+discover a set of (up to) $k$ ``topics'' or ``themes.'' Formally, each topic is defined
+as a distribution of weights over each word in the model's vocabulary (i.e., the union
+of all unique words, across all documents, excluding ``stop words.'').
+Conceptually, each topic is intended to give larger weights to words that are
+semantically related or tend to co-occur in the same documents. After
 fitting a topic model, each document in the training set, or any \textit{new}
@@
 may be represented as a $k$-dimensional vector describing how much the document
-(most probably) reflects each topic. To select an appropriate $k$ for our
-model, we identified the minimum number of topics that yielded at least one
-``unused'' topic (i.e., in which all words in the vocabulary were assigned
-uniform weights) after training. This indicated that the number of topics was
-sufficient to capture the set of latent themes present in the two lectures
-(from which we constructed our document corpus, as described below). We found
-this value to be $k = 15$ topics. The distribution of weights over words in the
-vocabulary for each discovered topic is shown in Supplementary
-Figure~\topicWordWeights, and each topic's top-weighted words may be found in
-Supplementary Table~\topics.
+(most probably) reflects each topic.
+To select an appropriate $k$ for our model, we identified the minimum number of
+topics that yielded at least one ``unused'' topic (i.e., in which all words in the vocabulary
+were assigned uniform weights) after training. This indicated that the number of topics was
+sufficient to capture the set of latent themes present in the two lectures (from which we
+constructed our document corpus, as described below). We found this value to be $k = 15$
+topics. The distribution of weights over words in the vocabulary for each discovered topic is
+shown in Supplementary Figure~\topicWordWeights, and each topic's top-weighted
+words may be found in Supplementary Table~\topics.
 
@@
 additionally provides automated captions. We opted to use these automated
-transcripts (which, in prior work, we have found to be of sufficiently
-near-human quality to yield reliable data in behavioral
-studies;~\citealp{ZimaEtal18}) when developing our framework in order to make
-it more directly extensible and adaptable by others in the future.
+transcripts (which, in prior work, we have found to be of sufficiently near-human
+quality to yield reliable data in behavioral studies;~\citealp{ZimaEtal18}) when
+developing our framework in order to make it more directly extensible and
+adaptable by others in the future.
 
@@
 length of (up to) $w = 30$ transcript lines, and assigned each window a
-timestamp corresponding to the midpoint between the timestamps for its first
-and last lines. This $w$ parameter was chosen to match the same number of words
-per sliding window (rounded to the nearest whole word, and after preprocessing)
-as the sliding windows we defined in our prior work~\citep{HeusEtal21}. The
-sliding windows contained an average of 73.8 words and lasted for an average of
-62.22 seconds. After splitting the transcripts into sliding windows, we carried
-out several standard preprocessing steps. First, we removed all punctuation,
-replaced numbers with their word equivalents (e.g., ``1'' with ``one''), and
-converted all text to lowercase. Next, we removed all stop words, as defined by
-the Natural Language Toolkit~\citep[NLTK; ]{BirdEtal09} English stop word list,
-augmented with additional words following~\citep{BoydMimn14}: ``actual,''
-``actually,'' ``also,'' ``bit,'' ``could,'' ``e,'' ``even,'' ``first,''
-``follow,'' ``following,'' ``four,'' ``let,'' ``like,'' ``mc,'' ``really,'',
-``saw,'' ``see,'' ``seen,'' ``thing,'' and ``two.''
-
-These sliding windows ramped up and down in length at the beginning and end of
-each transcript, respectively. In other words, each transcript's first sliding
-window covered only its first line, the second sliding window covered the first
-two lines, and so on. This ensured that each line from the transcripts appeared
-in the same number ($w$) of sliding windows. After performing various standard
-text preprocessing (e.g., normalizing case, lemmatizing, removing punctuation
-and stop-words), we treated the text from each sliding window as a single
-``document,'' and combined these documents across the two videos' windows to
-create a single training corpus for the topic model.
+timestamp corresponding to the midpoint between the timestamps for its first and last lines.
+These sliding windows ramped up and down in length at the
+beginning and end of each transcript, respectively. In other words, each transcript's first
+sliding window covered only its first line, the second
+sliding window covered the first two lines, and so on. This ensured that each
+line from the transcripts appeared in the same number ($w$) of sliding windows.
+After performing various standard text preprocessing (e.g., normalizing case,
+lemmatizing, removing punctuation and stop-words), we treated the text from
+each sliding window as a single ``document,'' and combined these documents
+across the two videos' windows to create a single training corpus for the topic model.
 
@@
 reflect similar themes, according to the model) will yield similar coordinates
-(in terms of correlation, cosine similarity, Kullback-Leibler divergence,
-Euclidean distance, or other geometric measures). In general, the similarity
-between different documents' topic vectors may be used to characterize the
-similarity in conceptual content between the documents.
+(in terms of correlation, cosine similarity, Kullback-Leibler divergence, Euclidean distance, or other geometric measures). In
+general, the similarity between different documents' topic vectors may be used
+to characterize the similarity in conceptual content between the documents.
 
@@
 resulting timeseries to one vector per second. We also used the fitted model to
-obtain topic vectors for each question in our pool (see Supp. Tab.~\questions).
-Taken together, we obtained a \textit{trajectory} for each video, describing
-its path through topic space, and a single coordinate for each question
+obtain topic vectors for each question in our pool (see Supp. Tab.~\questions). Taken
+together, we obtained a \textit{trajectory} for each video, describing its path
+through topic space, and a single coordinate for each question
 (Fig.~\ref{fig:sliding-windows}C). Embedding both videos and all of the
@@
 topic vector for one question, $y$), normalized by the minimum and maximum
-correlations (across all timepoints $t$ and questions $Q$) to range between 0
-and 1, inclusive. Equation~\ref{eqn:prop} then computes the weighted average
+correlations (across all timepoints $t$ and questions $Q$) to range between 0 and 1,
+inclusive. Equation~\ref{eqn:prop} then computes the weighted average
 proportion of correctly answered questions about the content presented at
@@
 The normalization step (i.e., using $\mathrm{ncorr}$ instead of the raw
-correlations) ensures that every question contributes some non-negative amount
-to the knowledge estimate.
+correlations) insures that every question
+contributes some non-negative amount to the knowledge estimate.
 
@@
 appearing in the lectures. To visualize these estimates
-(Fig.~\ref{fig:knowledge-maps}, Supp.
-Figs.~\individualKnowledgeMapsA,~\individualKnowledgeMapsB,~\individualKnowledgeMapsC,~\individualLearningMapsA,
+(Fig.~\ref{fig:knowledge-maps}, Supp. Figs.~\individualKnowledgeMapsA,~\individualKnowledgeMapsB,~\individualKnowledgeMapsC,~\individualLearningMapsA,
 and~\individualLearningMapsB), we used Uniform Manifold Approximation and
-Projection (UMAP; \citealp{McInEtal18a, McInEtal18b}) to construct a 2D
-projection of the text embedding space. Sampling the original 100-dimensional
-space at high resolution to obtain an adequate set of topic vectors spanning
-the embedding space would be computationally intractable. However, sampling a
-2D grid is trivial.
+Projection (UMAP; \citealp{McInEtal18a, McInEtal18b}) to construct a 2D projection of the
+text embedding space. Sampling the original 100-dimensional space at high
+resolution to obtain an adequate set of topic vectors spanning the embedding
+space would be computationally intractable. However, sampling a 2D grid is
+trivial.
 
@@
 In our application, all of the coordinates we embedded were topic vectors,
-whose elements are always non-negative and sum to one. Although UMAP is an
-invertible transformation at the embedding locations of the original data,
-other locations in the embedding space will not necessarily follow the same
-implicit ``rules'' as the original high-dimensional data. For example,
-inverting an arbitrary coordinate in the embedding space might result in
-negative-valued vectors, which are incompatible with the topic modeling
-framework. To protect against this issue, we log-transformed the topic vectors
-prior to embedding them in the 2D space. When we inverted the embedded vectors
-(e.g., to estimate topic vectors or word clouds, as in
-Fig.~\ref{fig:knowledge-maps}C), we passed the inverted (log-transformed)
-values through the exponential function to obtain a vector of non-negative
-values, and normalized them to sum to one.
+whose elements are always non-negative and sum to one. Although UMAP is an invertible
+transformation at the embedding locations of the original data, other locations
+in the embedding space will not necessarily follow the same implicit ``rules''
+as the original high-dimensional data. For example, inverting an arbitrary
+coordinate in the embedding space might result in negative-valued vectors,
+which are incompatible with the topic modeling framework. To protect against
+this issue, we log-transformed the topic vectors prior to embedding them in the
+2D space. When we inverted the embedded vectors (e.g., to estimate topic
+vectors or word clouds, as in Fig.~\ref{fig:knowledge-maps}C), we passed the
+inverted (log-transformed) values through the exponential function to obtain a
+vector of non-negative values, and normalized them to sum to one.
 
@@
 We acknowledge useful discussions, assistance in setting up an earlier
-(unpublished) version of this study, and assistance with data collection
-efforts from Will Baxley, Max Bluestone, Daniel Carstensen, Kunal Jha, Caroline
-Lee, Lucy Owen, Xinming Xu, and Kirsten Ziman. Our work was supported in part
-by NSF CAREER Award Number 2145172 to JRM. The content is solely the
-responsibility of the authors and does not necessarily represent the official
-views of our supporting organizations. The funders had no role in study design,
-data collection and analysis, decision to publish, or preparation of the
-manuscript.
+(unpublished) version of this study, and assistance with data
+collection efforts from Will Baxley, Max Bluestone, Daniel Carstensen, Kunal
+Jha, Caroline Lee, Lucy Owen, Xinming Xu, and Kirsten Ziman. Our work was
+supported in part by NSF CAREER Award Number 2145172 to JRM. The content is
+solely the responsibility of the authors and does not necessarily represent the
+official views of our supporting organizations. The funders had no role in
+study design, data collection and analysis, decision to publish, or preparation
+of the manuscript.
 

### 2023-10-24 paper/main.tex
another round of JRM edits + spell checking, formatting edits, etc.

@@
 \newcommand{\topicWeights}{2}
-\newcommand{\individualKnowledgeMapsA}{3}
-\newcommand{\individualKnowledgeMapsB}{4}
-\newcommand{\individualKnowledgeMapsC}{5}
-\newcommand{\individualLearningMapsA}{6}
-\newcommand{\individualLearningMapsB}{7}
-\newcommand{\ldaVsBERT}{8}
-\newcommand{\jaccard}{9}   % word match figure
+\newcommand{\forcesCorrs}{3}
+\newcommand{\bosCorrs}{4}
+\newcommand{\jaccard}{5}
+\newcommand{\ldaVsBERT}{6}
+\newcommand{\individualKnowledgeMapsA}{7}
+\newcommand{\individualKnowledgeMapsB}{8}
+\newcommand{\individualKnowledgeMapsC}{9}
+\newcommand{\individualLearningMapsA}{10}
+\newcommand{\individualLearningMapsB}{11}
 
@@
 
-The difference between ``understanding'' and ``memorizing,'' as framed by
-researchers in education, cognitive psychology, and cognitive neuroscience
-(e.g.,~\citealp{Kato40, Gall00, ScotEtal07, HallGree08, Macl05}), has profound
-analogs in the fields of natural language processing and natural language
-understanding. For example, considering the raw contents of a document (e.g.,
-its constituent symbols, letters, and words) might provide some clues as to
-what the document is about, just as memorizing a passage might provide some
-ability to answer simple questions about it. However, text embedding models
-(e.g.,~\citealp{LandDuma97, DeerEtal90, BleiEtal03, BleiLaff06, MikoEtal13a,
-CerEtal18, BrowEtal20, ViswEtal17}) also attempt to capture the deeper meaning
-\textit{underlying} those atomic elements. These models consider not only the
-co-occurrences of those elements within and across documents, but (in many
-cases) also patterns in how those elements appear across different scales
-(e.g., sentences, paragraphs, chapters, etc.), the temporal and grammatical
-properties of the elements, and other high-level characteristics of how they
-are used~\citep{Mann20, Mann21a}. According to these models, the deep
-conceptual meaning of a document may be captured by a feature vector in a
-high-dimensional representation space, wherein nearby vectors reflect
-conceptually related documents. A model that succeeds at capturing an analogue
-of ``understanding'' is able to assign nearby feature vectors to two
-conceptually related documents, \textit{even when the specific words contained
-in those documents have very little overlap}. In this way, ``concepts'' are
-defined implicitly by the model's geometry~\citep[e.g., how the embedding coordinate
-of a given word or document relates to the coordinates of other text
-embeddings;][]{PianHill22}.
+The difference between ``understanding'' and ``memorizing,'' as framed
+by researchers in education, cognitive psychology, and cognitive
+neuroscience~\citep[e.g.,][]{Kato40, Gall00, ScotEtal07, HallGree08,
+  Macl05}, has profound analogs in the fields of natural language
+processing and natural language understanding. For example,
+considering the raw contents of a document (e.g., its constituent
+symbols, letters, and words) might provide some clues as to what the
+document is about, just as memorizing a passage might provide some
+ability to answer simple questions about it. However, text embedding
+models~\citep[e.g., ][]{LandDuma97, DeerEtal90, BleiEtal03,
+  BleiLaff06, MikoEtal13a, CerEtal18, BrowEtal20, ViswEtal17} also
+attempt to capture the deeper meaning \textit{underlying} those atomic
+elements. These models consider not only the co-occurrences of those
+elements within and across documents, but (in many cases) also
+patterns in how those elements appear across different scales (e.g.,
+sentences, paragraphs, chapters, etc.), the temporal and grammatical
+properties of the elements, and other high-level characteristics of
+how they are used~\citep{Mann20, Mann21a}. According to these models,
+the deep conceptual meaning of a document may be captured by a feature
+vector in a high-dimensional representation space, wherein nearby
+vectors reflect conceptually related documents. A model that succeeds
+at capturing an analogue of ``understanding'' is able to assign nearby
+feature vectors to two conceptually related documents, \textit{even
+  when the specific words contained in those documents do not fully
+  overlap}. In this way, ``concepts'' are defined implicitly by the
+model's geometry~\citep[e.g., how the embedding coordinate of a given
+word or document relates to the coordinates of other text
+embeddings; ][]{PianHill22}.
 
@@
 along with related knowledge about physics concepts not specifically presented
-in either video (see Supp. Tab.~\questions~for the full list of questions in
+in either video (see Supp.~Tab.~\questions~for the full list of questions in
 our stimulus pool). Participants answered questions randomly drawn from each
@@
     on the two lectures' windows) to both lectures, along with the text of each
-    question in our pool (Supp. Tab.~\questions), to project them into a shared
+    question in our pool (Supp.~Tab.~\questions), to project them into a shared
     text embedding space. This results in one trajectory per lecture and one
@@
 correspondence could not solely arise from superficial text matching between
-lecture transcripts and questions, since the lectures and questions used
-different words. Simply comparing the average topic weights from each lecture
-and question set (averaging across time and questions, respectively) reveals a
-striking correspondence (Supp. Fig.~\topicWeights). Specifically, the average
-topic weights from Lecture~1 are strongly correlated with the average topic
-weights from Lecture~1 questions ($r(13) = 0.809,~p < 0.001$, 95\% confidence
-interval (CI)~$= [0.633,~0.962]$), and the average topic weights from Lecture~2
-are strongly correlated with the average topic weights from Lecture~2 questions
-($r(13) = 0.728,~p = 0.002$, 95\% CI~$= [0.456,~0.920]$). At the same time, the
-average topic weights from the two lectures are \textit{negatively} correlated
-with their non-matching question sets (Lecture~1 video vs.~Lecture~2 questions:
-$r(13) = -0.547,~p = 0.035$, 95\% CI~$= [-0.812, ~-0.231]$; Lecture~2 video
-vs.~Lecture~1 questions: $r(13) = -0.612,~p = 0.015$, 95\% CI~$=
-[-0.874,~-0.281]$), indicating that the topic model also exhibits some degree
-of specificity. The full set of pairwise comparisons between average topic
-weights for the lectures and question sets is reported in Supplementary
-Figure~\topicWeights.
+lecture transcripts and questions, since the lectures and questions often used
+different words (Supp.~Fig.~\jaccard) and phrasings. Simply comparing the
+average topic weights from each lecture and question set (averaging across time
+and questions, respectively) reveals a striking correspondence (Supp.
+Fig.~\topicWeights). Specifically, the average topic weights from Lecture~1 are
+strongly correlated with the average topic weights from Lecture~1 questions
+($r(13) = 0.809,~p < 0.001$, 95\% confidence interval (CI)~$= [0.633,~0.962]$),
+and the average topic weights from Lecture~2 are strongly correlated with the
+average topic weights from Lecture~2 questions ($r(13) = 0.728,~p = 0.002$,
+95\% CI~$= [0.456,~0.920]$). At the same time, the average topic weights from
+the two lectures are \textit{negatively} correlated with their non-matching
+question sets (Lecture~1 video vs.~Lecture~2 questions: $r(13) = -0.547,~p =
+0.035$, 95\% CI~$= [-0.812, ~-0.231]$; Lecture~2 video vs.~Lecture~1 questions:
+$r(13) = -0.612,~p = 0.015$, 95\% CI~$= [-0.874,~-0.281]$), indicating that the
+topic model also exhibits some degree of specificity. The full set of pairwise
+comparisons between average topic weights for the lectures and question sets is
+reported in Supplementary Figure~\topicWeights.
 
@@
 range of timepoints from their corresponding lectures, and the correlations
-fell off sharply outside of that range. We also qualitatively examined the
-best-matching intervals for each question by comparing the question's text to
-the text of the most-correlated parts of the lectures. Despite that the
-questions were excluded from the text embedding model's training set, in
-general we found (through manual inspection) a close correspondence between the
-conceptual content that each question probed and the content covered by the
-best-matching moments of the lectures. Two representative examples are shown at
-the bottom of Figure~\ref{fig:question-correlations}.
+fell off sharply outside of that range (Supp.~Figs.~\forcesCorrs,~\bosCorrs).
+We also qualitatively examined the best-matching intervals for each question by
+comparing the question's text to the text of the most-correlated parts of the
+lectures (Supp.~Tab.~\matchTab). Despite that the questions were excluded from
+the text embedding model's training set, in general we found (through manual
+inspection) a close correspondence between the conceptual content that each
+question probed and the content covered by the best-matching moments of the
+lectures. Two representative examples are shown at the bottom of
+Figure~\ref{fig:question-correlations}.
 
@@
 apply this approach to estimate the participant's knowledge about the content
-presented in each moment of each lecture, we can obtain a detailed timecourse
-describing how much ``knowledge'' the participant has about any part of the
-lecture. As shown in Figure~\ref{fig:knowledge-timeseries}A and C, we can apply
-this approach separately for the questions from each quiz participants took
-throughout the experiment. From just a few questions per quiz
-(see~\nameref{subsec:traces}), we obtain a high-resolution snapshot (at the
-time each quiz was taken) of what the participants knew about any moment's
-content, from either of the two lectures they watched (comprising a total of
-1,100 samples across the two lectures).
+presented in each moment of each lecture, we can obtain a detailed time course
+describing how much ``knowledge'' the participant has about the content
+presented at any part of the lecture. As shown in
+Figure~\ref{fig:knowledge-timeseries}A and C, we can apply this approach
+separately for the questions from each quiz participants took throughout the
+experiment. From just a few questions per quiz (see~\nameref{subsec:traces}),
+we obtain a high-resolution snapshot (at the time each quiz was taken) of what
+the participants knew about any moment's content, from either of the two
+lectures they watched (comprising a total of 1,100 samples across the two
+lectures).
 
@@
 
-While the timecourses in Figure~\ref{fig:knowledge-timeseries}A and C provide
+While the time courses in Figure~\ref{fig:knowledge-timeseries}A and C provide
 detailed \textit{estimates} about participants' knowlege, these estimates are
@@
 lead our approach to over-estimate knowledge for held-out questions about
-``forgotten'' knowledge that particpants answered incorrectly.
+``forgotten'' knowledge that participants answered incorrectly.
 
@@
 answered that same question \textit{in}correctly. Again, as we move away from
-$X$ in the embedding space, how does our confidence that the participant does
+$X$ in the embedding space, how do the chances that the participant does
 \textit{not} know about the content change with distance? We reasoned that,
 assuming our space is capturing something about how participants actually
-organize their knowledge, conceptual knowledge right around $X$ should be similar
-to the participant's knowledge of the content at $X$. And at another extreme, at
-some distance (after moving sufficiently far away from $X$), our guesses about
-what participants know (based on their response to the question at location $X$)
-should be no better than guessing based on their overall proportion of
-correctly answered questions—i.e., if $Y$ is very far away from $X$, all we can do
-with the participant's response to $X$ is guess that ``their performance on quiz
-questions about $Y$ is about equal to their average performance on quiz questions
-about any material.''
+organize their knowledge, conceptual knowledge right around $X$ should be
+similar to the participant's knowledge of the content at $X$. And at another
+extreme, at some distance (after moving sufficiently far away from $X$), our
+guesses about what participants know (based on their response to the question
+at location $X$) should be no better than guessing based on their overall
+proportion of correctly answered questions—i.e., if $Y$ is very far away from
+$X$, all we can do with the participant's response to $X$ is guess that ``their
+performance on quiz questions about $Y$ is about equal to their average
+performance on quiz questions about any material.''
 
@@
 contained in the two lectures. This change in the number of topics overcame an
-undesireable behavior in the UMAP embedding procedure~\citep{McInEtal18},
+undesirable behavior in the UMAP embedding procedure~\citep{McInEtal18a},
 whereby embedding coordinates for the 15-topic model tended to be ``clumped''
@@
 Because the 2D projection we used to construct the knowledge and learning maps
-is invertible, we may gain additional insights into these maps' meaning by
+is invertible, we may gain additional insights into these maps' meanings by
 reconstructing the original high-dimensional topic vector for any location on
@@
 numbers of multiple choice quiz questions. Our experimental finding that we can
-use these maps to predict responses to held-out questions
-(Fig.~\ref{fig:predictions}) also has important psychological implications. One
-such psychological implication is that concepts that are assigned to nearby
-coordinates by the text embedding model also appear to be ``known to a similar
-extent'' (as reflected by participants' responses to held-out questions). This
-suggests that participants also \textit{conceptualize} similarly the content
-reflected by nearby embedding coordinates. A second psychological implication
-is that something about how participants' knowledge ``spreads'' across concepts
-is being captured by the knowledge maps we are inferring from their quiz
-responses (e.g., Figs.~\ref{fig:smoothness},~\ref{fig:knowledge-maps}). In
-other words, our study shows that knowledge about a given concept implies
-knowledge about related concepts.
+use these maps to predict responses to held-out questions has several
+psychological implications as well. For example, concepts that are assigned to
+nearby coordinates by the text embedding model also appear to be ``known to a
+similar extent'' (as reflected by participants' responses to held-out
+questions; Fig.~\ref{fig:predictions}). This suggests that participants also
+\textit{conceptualize} similarly the content reflected by nearby embedding
+coordinates. The ``spatial smoothness'' of participants' knowledge (as
+estimated using quiz performance) is being captured by the knowledge maps we
+are inferring from their quiz responses (e.g.,
+Figs.~\ref{fig:smoothness},~\ref{fig:knowledge-maps}). In other words, our
+study shows that knowledge about a given concept implies knowledge about
+related concepts, and we also show how estimated knowledge falls off with
+distance in text embedding space.
 
@@
 using a relatively simple ``bag of words'' text embedding model~\citep[LDA;
-]{BleiEtal03}. More sophisticated text embedding models, such as
+][]{BleiEtal03}. More sophisticated text embedding models, such as
 transformer-based models~\citep{ViswEtal17, DevlEtal18, ChatGPT, TouvEtal23}
 can learn complex grammatical and semantic relationships between words,
-higher-order syntactic structures, sylistic features, and more. We considered
-using transformer-based models in our study, but we were surprised to find that
-the text embeddings derived from these models were surprisingly uninformative
-with respect to differentiating or otherwise characterizing the conceptual
-content of the lectures and questions we used. We suspect that this reflects a
-broader challenge in constructing models that are high-resolution within a
-given domain (e.g., the domain of physics lectures and questions) \textit{and}
-sufficiently broad so as to enable them to cover a wide range of domains. For
-example, we found that the embeddings derived even from much larger and more
-modern models like BERT~\citep{DevlEtal18}, GPT~\citep{ViswEtal17},
-LLaMa~\citep{TouvEtal23}, and others that are trained on enormous text corpora,
-end up yielding poor resolution within the content space spanned by indiviudal
-course videos (Supp. Fig.~\ldaVsBERT). Whereas the LDA embeddings of the
-lectures and questions are ``near'' each other (i.e., the convex hull enclosing
-the two lectures' trajectories is highly overlapping with the convex hull
-enclosing the questions' embeddings), the BERT embeddings of the lectures and
-questions are instead largely distinct (top row of Supp. Fig.~\ldaVsBERT). The
-LDA embeddings of the questions for each lecture and the corresponding
-lecture's trajectory are also similar. For example, as shown in
-Fig.~\ref{fig:sliding-windows}C, the LDA embeddings for \textit{Four
-Fundamental Forces} questions (blue dots) appear closer to the \textit{Four
-Fundamental Forces} lecture trajectory (blue line), whereas the LDA embeddings
-for \textit{Birth of Stars} questions (green dots) appear closer to the
-\textit{Birth of Stars} lecture trajectory (green line). The BERT embeddings of
-the lectures and questions do not show this property (Supp. Fig.~\ldaVsBERT).
-We also examined per-question ``content matches'' between individual questions
-and individual moments of each lecture
+higher-order syntactic structures, stylistic features, and more. We considered
+using transformer-based models in our study, but we found that the text
+embeddings derived from these models were surprisingly uninformative with
+respect to differentiating or otherwise characterizing the conceptual content
+of the lectures and questions we used. We suspect that this reflects a broader
+challenge in constructing models that are high-resolution within a given domain
+(e.g., the domain of physics lectures and questions) \textit{and} sufficiently
+broad so as to enable them to cover a wide range of domains. For example, we
+found that the embeddings derived even from much larger and more modern models
+like BERT~\citep{DevlEtal18}, GPT~\citep{ViswEtal17}, LLaMa~\citep{TouvEtal23},
+and others that are trained on enormous text corpora, end up yielding poor
+resolution within the content space spanned by individual course videos
+(Supp.~Fig.~\ldaVsBERT). Whereas the LDA embeddings of the lectures and
+questions are ``near'' each other (i.e., the convex hull enclosing the two
+lectures' trajectories is highly overlapping with the convex hull enclosing the
+questions' embeddings), the BERT embeddings of the lectures and questions are
+instead largely distinct (top row of Supp.~Fig.~\ldaVsBERT). The LDA embeddings
+of the questions for each lecture and the corresponding lecture's trajectory
+are also similar. For example, as shown in Fig.~\ref{fig:sliding-windows}C, the
+LDA embeddings for \textit{Four Fundamental Forces} questions (blue dots)
+appear closer to the \textit{Four Fundamental Forces} lecture trajectory (blue
+line), whereas the LDA embeddings for \textit{Birth of Stars} questions (green
+dots) appear closer to the \textit{Birth of Stars} lecture trajectory (green
+line). The BERT embeddings of the lectures and questions do not show this
+property (Supp.~Fig.~\ldaVsBERT). We also examined per-question ``content
+matches'' between individual questions and individual moments of each lecture
 (Figs.~\ref{fig:question-correlations},~\ldaVsBERT). The timeseries plot of
@@
 similar pattern with the LDA embeddings of the \textit{Birth of Stars}
-questions (Fig.~\ref{fig:topics}, Supp. Fig.~\topicWeights). In contrast, the
+questions (Fig.~\ref{fig:topics}, Supp.~Fig.~\topicWeights). In contrast, the
 BERT embeddings are all highly correlated with each other (Supp.
@@
 systems~\citep[e.g.,][]{MannEtal23b}. Unlike the approach we have taken here,
-these systems do not explicitly model what learners know, or how their knowledge 
-changes over time with training.  One could imagine building a hybrid system
-that combines the best of both worlds: a large language model that can
-\textit{generate} text, combined with a smaller model that can \textit{infer}
-what learners know and how their knowledge changes over time.  Such a hybrid
-system could potentially be used to build a new generation of interactive
-tutoring systems that are able to adapt to learners' needs in real time, and
-that are able to provide more nuanced feedback about what learners know and
-what they do not know.
+these generative text model-based systems do not explicitly model what learners
+know, or how their knowledge changes over time with training. One could imagine
+building a hybrid system that combines the best of both worlds: a large
+language model that can \textit{generate} text, combined with a smaller model
+that can \textit{infer} what learners know and how their knowledge changes over
+time. Such a hybrid system could potentially be used to build the next
+generation of interactive tutoring systems that are able to adapt to learners'
+needs in real time, and that are able to provide more nuanced feedback about
+what learners know and what they do not know.
 
@@
 does not appear to capture the same level of specificity as the LDA-based
-approach. For example, whereas the LDA-based approach often yields a clear peak
-in the timeseries of correlations between each question and the corresponding
-lecture, the Jaccard similarity-based approach does not. Furthermore, these
-LDA-based matches appear to capture conceptual overlaps between the questions
-and lectures (Supp. Tab.~\matchTab), whereas simple word matching does not. For
-example, one of the example questions examined in Supplementary Figure~\jaccard
-asks ``Which of the following occurs as a cloud of atoms gets more dense?''.
-The LDA-based matches identify lecture timepoints where the releveant
-\textit{topics} are discussed (e.g., when words like ``cloud,'' ``atom,''
-``dense,'' etc., are mentioned \textit{together}). The Jaccard similarity-based
-matches, on the other hand, are strong when \textit{any} of these words are
-mentioned, even if they do not occur together.
+approach. Whereas the LDA-based approach often yields a clear peak in the
+timeseries of correlations between each question and the corresponding lecture,
+the Jaccard similarity-based approach does not. Furthermore, these LDA-based
+matches appear to capture conceptual overlaps between the questions and
+lectures (Supp.~Tab.~\matchTab), whereas simple word matching does not. For
+example, one of the example questions examined in Supplementary
+Figure~\jaccard~asks ``Which of the following occurs as a cloud of atoms gets
+more dense?''. The LDA-based matches identify lecture timepoints where the
+relevant \textit{topics} are discussed (e.g., when words like ``cloud,''
+``atom,'' ``dense,'' etc., are mentioned \textit{together}). The Jaccard
+similarity-based matches, on the other hand, are strong when \textit{any} of
+these words are mentioned, even if they do not occur together.
 
@@
 
-Over the past several years, the global pandemic has forced many educators to
+Within the past several years, the global pandemic forced many educators to
 suddenly adapt to teaching remotely~\citep{MoseEtal21, ShimLee20, KawaEtal21,
@@
 key step will be to understand which sorts of signals derived from behaviors
-and/or other measurements (e.g., neurophysiological data;~\citealp{NguyEtal22,
-MeshEtal20, PoulEtal17, BeviEtal19, DikkEtal17}) might help to inform these
+and/or other measurements~\citep[e.g., neurophysiological data; ][]{NguyEtal22,
+MeshEtal20, PoulEtal17, BeviEtal19, DikkEtal17} might help to inform these
 models. A third major step will be to develop and employ reliable ways of
@@
 participant, were randomly chosen from the full set of 39, with the constraints
-that (a) each quiz contain exactly 5 questions about Lecture~1, 5 questions
+that (a) each quiz contained exactly 5 questions about Lecture~1, 5 questions
 about Lecture~2, and 3 questions about general physics knowledge, and (b) each
@@
 each moment of the two lectures and each question in our pool in a common
-representational space. Briefly, our approach uses a topic model (Latent
-Dirichlet Allocation;~\citealp{BleiEtal03}), trained on a set of documents, to
+representational space. Briefly, our approach uses a topic model~\citep[Latent
+Dirichlet Allocation; ][]{BleiEtal03} trained on a set of documents, to
 discover a set of (up to) $k$ ``topics'' or ``themes.'' Formally, each topic is
-defined as a distribution of weights over each word in the model's vocabulary
+defined as a distribution of weights over words in the model's vocabulary
 (i.e., the union of all unique words, across all documents, excluding ``stop
 words.''). Conceptually, each topic is intended to give larger weights to words
-that are semantically related, as implied by their co-occurring in the same documents. After
-fitting a topic model, each document in the training set, or any \textit{new}
-document that contains at least some of the words in the model's vocabulary,
-may be represented as a $k$-dimensional vector describing how much the document
-(most probably) reflects each topic. To select an appropriate $k$ for our
-model, we identified the minimum number of topics that yielded at least one
-``unused'' topic (i.e., in which all words in the vocabulary were assigned
-uniform weights) after training. This indicated that the number of topics was
-sufficient to capture the set of latent themes present in the two lectures
-(from which we constructed our document corpus, as described below). We found
-this value to be $k = 15$ topics. The distribution of weights over words in the
-vocabulary for each discovered topic is shown in Supplementary
-Figure~\topicWordWeights, and each topic's top-weighted words may be found in
-Supplementary Table~\topics.
+that are semantically related, as implied by their co-occurring in the same
+documents. After fitting a topic model, each document in the training set, or
+any \textit{new} document that contains at least some of the words in the
+model's vocabulary, may be represented as a $k$-dimensional vector describing
+how much the document (most probably) reflects each topic. To select an
+appropriate $k$ for our model, we identified the minimum number of topics that
+yielded at least one ``unused'' topic (i.e., in which all words in the
+vocabulary were assigned uniform weights) after training. This indicated that
+the number of topics was sufficient to capture the set of latent themes present
+in the two lectures (from which we constructed our document corpus, as
+described below). We found this value to be $k = 15$ topics. The distribution
+of weights over words in the vocabulary for each discovered topic is shown in
+Supplementary Figure~\topicWordWeights, and each topic's top-weighted words may
+be found in Supplementary Table~\topics.
 
@@
 additionally provides automated captions. We opted to use these automated
-transcripts (which, in prior work, we have found to be of sufficiently
+transcripts~\citep[which, in prior work, we have found to be of sufficiently
 near-human quality to yield reliable data in behavioral
-studies;~\citealp{ZimaEtal18}) when developing our framework in order to make
+studies; ][]{ZimaEtal18} when developing our framework in order to make
 it more directly extensible and adaptable by others in the future.
@@
 punctuation and removing stop-words. We constructed our corpus of stop words by
-augmenting the Natural Language Toolkit~\citep[NLTK; ]{BirdEtal09} English stop
-word list with the following additional words, selected using the stop word
-approach suggested by~\citep{BoydMimn14}: ``actual,'' ``actually,'' ``also,''
-``bit,'' ``could,'' ``e,'' ``even,'' ``first,'' ``follow,'' ``following,''
-``four,'' ``let,'' ``like,'' ``mc,'' ``really,'', ``saw,'' ``see,'' ``seen,''
-``thing,'' and ``two.'' This yielded sliding windows with an average of 73.8
-remaining words, and lasting for an average of 62.22~seconds. We treated the
-text from each sliding window as a single ``document,'' and combined these
-documents across the two videos' windows to create a single training corpus for
-the topic model.
+augmenting the Natural Language Toolkit~\citep[NLTK; ][]{BirdEtal09} English
+stop word list with the following additional words, selected using the approach
+suggested by~\citep{BoydMimn14}: ``actual,'' ``actually,'' ``also,'' ``bit,''
+``could,'' ``e,'' ``even,'' ``first,'' ``follow,'' ``following,'' ``four,''
+``let,'' ``like,'' ``mc,'' ``really,'', ``saw,'' ``see,'' ``seen,'' ``thing,''
+and ``two.'' This yielded sliding windows with an average of 73.8 remaining
+words, and lasting for an average of 62.22~seconds. We treated the text from
+each sliding window as a single ``document,'' and combined these documents
+across the two videos' windows to create a single training corpus for the topic
+model.
 
@@
 resulting timeseries to one vector per second. We also used the fitted model to
-obtain topic vectors for each question in our pool (see Supp. Tab.~\questions).
+obtain topic vectors for each question in our pool (see Supp.~Tab.~\questions).
 Taken together, we obtained a \textit{trajectory} for each video, describing
@@
 this reference, we constructed a series of 15-dimensional spheres (starting
-with a radius of 0), where each successive circle had a radius of 0.01
+with a radius of 0), where each successive sphere had a radius of 0.01
 (correlation distance) greater than its predecessor. Within each of these
 spheres, we calculated the proportion of questions answered correctly by the
-participant. The per-radius proportion correct values were then averaged across
-both categories of ``reference questions'': those answered correctly and those
-answered incorrectly. This yielded two distinct proportion-correct values for
-each binned distance (radius) for a specific participant and quiz. From these,
-we established the average proportion correct within each radius for both
+participant. This yielded two distinct sets of proportion-correct values for
+each binned distance (radius) for a specific participant and quiz: one set of
+values where the reference questions had been answered correctly, and another
+set where the reference questions had been answered incorrectly. From these, we
+established the average proportion correct within each radius for both
 categories of reference questions. Finally, we identified the minimum binned
@@
 proportion correct intersected the 95\% confidence interval of the simple
-average proportion correct computed earlier. (A parallel analysis was conducted
-for the incorrectly answered reference questions.) We display the resulting
-distance estimates, for each quiz and reference question status, in
+average proportion correct computed earlier. We display the resulting distance
+estimates, for each quiz and reference question status, in
 Figure~\ref{fig:smoothness}B.
@@
 and~\individualLearningMapsB), we used Uniform Manifold Approximation and
-Projection (UMAP; \citealp{McInEtal18a, McInEtal18b}) to construct a 2D
+Projection~\citep[UMAP; ][]{McInEtal18a, McInEtal18b} to construct a 2D
 projection of the text embedding space. Sampling the original 100-dimensional
@@
 Lee, Lucy Owen, Xinming Xu, and Kirsten Ziman. Our work was supported in part
-by NSF CAREER Award Number 2145172 to JRM. The content is solely the
+by NSF CAREER Award Number 2145172 to J.R.M. The content is solely the
 responsibility of the authors and does not necessarily represent the official

### 2023-10-24 paper/main.tex

@@
 how much the document (most probably) reflects each topic. To select an
-appropriate $k$ for our model, we identified the minimum number of topics that
-yielded at least one ``unused'' topic (i.e., in which all words in the
-vocabulary were assigned uniform weights) after training. This indicated that
-the number of topics was sufficient to capture the set of latent themes present
-in the two lectures (from which we constructed our document corpus, as
-described below). We found this value to be $k = 15$ topics. The distribution
-of weights over words in the vocabulary for each discovered topic is shown in
+appropriate $k$ for our model, as a starting point, we identified the minimum
+number of topics that yielded at least one ``unused'' topic (i.e., in which all
+words in the vocabulary were assigned uniform weights) after training. This
+indicated that the number of topics was sufficient to capture the set of latent
+themes present in the two lectures (from which we constructed our document
+corpus, as described below). We found this value to be $k = 15$ topics. We
+found that with a limited number of additional adjustments
+following~\citep{BoydMimn14}, such as removing corpus-specific stop-words, the
+model yielded (subjectively) sensible and coherent topics. The distribution of
+weights over words in the vocabulary for each discovered topic is shown in
 Supplementary Figure~\topicWordWeights, and each topic's top-weighted words may

### 2023-10-24 paper/supplement.tex
finished a round of edits to the supplement

@@
     1     &     FFF &                                                                                                                                                                                   Why is the gravitational attraction between you and your computer too small for you to notice?
-&                                           Neither you nor your computer has enough mass to cause a noticable gravitational attraction &                You and your computer are too close for the gravitational attraction to be significant &                                                                        Humans are too small to detect the force of gravity &  The gravitational attraction between you and your computer is disrupted by the larger gravitational field generated by the earth \\\hline
+&                                           Neither you nor your computer has enough mass to cause a noticeable gravitational attraction &                You and your computer are too close for the gravitational attraction to be significant &                                                                        Humans are too small to detect the force of gravity &  The gravitational attraction between you and your computer is disrupted by the larger gravitational field generated by the earth \\\hline
     2     &     FFF &                                                                                                                                                                                                                    Which of the following is an example of the Weak Interaction?
@@
 5  &          FFF &                                                                                                                                                                                            Which of the following is a difference between gravity and the electromagnetic force?
-&                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  \textbf{[04:34.28--05:52.61]} ...times the strength of gravity 10 to 36 times the strength of gravity so it kind of puts the weak force in its place it's 10 to the 12 times stronger than the weak force so these are huge numbers that we're talking about either this relative that or even this relative to gravity and so you might be saying well you know the electromagnetic force that's unbelievably strong why doesn't that apply over over over these these kind of macro scales like gravity let me write there macro scales macro scales why doesn't it apply to macro scales and actually there's nothing about the electromagnetic force why it can't it or it actually does apply over large distances the reality though is you don't have these huge concentrations of either electric Ullom charges or magnetism the way you do mass so the mass that you have such huge concentrations it can operate over huge huge distances even though it's way way way weaker than the electromagnetic force the electromagnetic force what happens is because it's both attractive and repulsive it tends to kind of sort itself out so you don't have these huge huge huge concentrations of charge now the other thing you might be wondering about is you know why is it called the electromagnetic force in our everyday life there's things like there's things like the Coulomb force that or the electrostatic force which we're familiar...
+&                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  \textbf{[04:34.28--05:52.61]} ...times the strength of gravity 10 to 36 times the strength of gravity so it kind of puts the weak force in its place it's 10 to the 12 times stronger than the weak force so these are huge numbers that we're talking about either this relative that or even this relative to gravity and so you might be saying well you know the electromagnetic force that's unbelievably strong why doesn't that apply over over over these these kind of macro scales like gravity let me write there macro scales macro scales why doesn't it apply to macro scales and actually there's nothing about the electromagnetic force why it can't it or it actually does apply over large distances the reality though is you don't have these huge concentrations of either electric Coulomb charges or magnetism the way you do mass so the mass that you have such huge concentrations it can operate over huge huge distances even though it's way way way weaker than the electromagnetic force the electromagnetic force what happens is because it's both attractive and repulsive it tends to kind of sort itself out so you don't have these huge huge huge concentrations of charge now the other thing you might be wondering about is you know why is it called the electromagnetic force in our everyday life there's things like there's things like the Coulomb force that or the electrostatic force which we're familiar...
 \\\hline
-6  &          FFF &                                                                                                                                                                                                  Electricity and magnetism can be shown to be two cases of the same force if we: &                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                          \textbf{[04:34.28--05:52.61]} ...times the strength of gravity 10 to 36 times the strength of gravity so it kind of puts the weak force in its place it's 10 to the 12 times stronger than the weak force so these are huge numbers that we're talking about either this relative that or even this relative to gravity and so you might be saying well you know the electromagnetic force that's unbelievably strong why doesn't that apply over over over these these kind of macro scales like gravity let me write there macro scales macro scales why doesn't it apply to macro scales and actually there's nothing about the electromagnetic force why it can't it or it actually does apply over large distances the reality though is you don't have these huge concentrations of either electric Ullom charges or magnetism the way you do mass so the mass that you have such huge concentrations it can operate over huge huge distances even though it's way way way weaker than the electromagnetic force the electromagnetic force what happens is because it's both attractive and repulsive it tends to kind of sort itself out so you don't have these huge huge huge concentrations of charge now the other thing you might be wondering about is you know why is it called the electromagnetic force in our everyday life there's things like there's things like the Coulomb force that or the electrostatic force which we're familiar...\newline\textbf{[06:37.31--07:28.1]} ...that the cool force the electrostatic force and the magnetic force are actually the same thing viewed in different frames of references so I won't go into a lot of detail but just keep that in the back of your mind that they are connected in a future video I'll go more into the intuition of how they are connected and it deals with when what it's more apparent when they're moving when the charges are moving at relativistic frames and you have well I will go to a lot of detail there but just keep in mind that they really are the same force just viewed from different frames of reference now the strongest of the force is probably the best name of them all and that's the strong force that is the strong force the strong force and although you probably haven't seen this yet in our in chemistry classes it actually applies very strongly in...
+6  &          FFF &                                                                                                                                                                                                  Electricity and magnetism can be shown to be two cases of the same force if we: &                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                          \textbf{[04:34.28--05:52.61]} ...times the strength of gravity 10 to 36 times the strength of gravity so it kind of puts the weak force in its place it's 10 to the 12 times stronger than the weak force so these are huge numbers that we're talking about either this relative that or even this relative to gravity and so you might be saying well you know the electromagnetic force that's unbelievably strong why doesn't that apply over over over these these kind of macro scales like gravity let me write there macro scales macro scales why doesn't it apply to macro scales and actually there's nothing about the electromagnetic force why it can't it or it actually does apply over large distances the reality though is you don't have these huge concentrations of either electric Coulomb charges or magnetism the way you do mass so the mass that you have such huge concentrations it can operate over huge huge distances even though it's way way way weaker than the electromagnetic force the electromagnetic force what happens is because it's both attractive and repulsive it tends to kind of sort itself out so you don't have these huge huge huge concentrations of charge now the other thing you might be wondering about is you know why is it called the electromagnetic force in our everyday life there's things like there's things like the Coulomb force that or the electrostatic force which we're familiar...\newline\textbf{[06:37.31--07:28.1]} ...that the cool force the electrostatic force and the magnetic force are actually the same thing viewed in different frames of references so I won't go into a lot of detail but just keep that in the back of your mind that they are connected in a future video I'll go more into the intuition of how they are connected and it deals with when what it's more apparent when they're moving when the charges are moving at relativistic frames and you have well I will go to a lot of detail there but just keep in mind that they really are the same force just viewed from different frames of reference now the strongest of the force is probably the best name of them all and that's the strong force that is the strong force the strong force and although you probably haven't seen this yet in our in chemistry classes it actually applies very strongly in...
 \\\hline
@@
 11 &          FFF &                                                                                                                                                                                                                          Which force is stronger than the Electromagnetic Force?
-&                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  \textbf{[04:34.28--05:52.61]} ...times the strength of gravity 10 to 36 times the strength of gravity so it kind of puts the weak force in its place it's 10 to the 12 times stronger than the weak force so these are huge numbers that we're talking about either this relative that or even this relative to gravity and so you might be saying well you know the electromagnetic force that's unbelievably strong why doesn't that apply over over over these these kind of macro scales like gravity let me write there macro scales macro scales why doesn't it apply to macro scales and actually there's nothing about the electromagnetic force why it can't it or it actually does apply over large distances the reality though is you don't have these huge concentrations of either electric Ullom charges or magnetism the way you do mass so the mass that you have such huge concentrations it can operate over huge huge distances even though it's way way way weaker than the electromagnetic force the electromagnetic force what happens is because it's both attractive and repulsive it tends to kind of sort itself out so you don't have these huge huge huge concentrations of charge now the other thing you might be wondering about is you know why is it called the electromagnetic force in our everyday life there's things like there's things like the Coulomb force that or the electrostatic force which we're familiar...
+&                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  \textbf{[04:34.28--05:52.61]} ...times the strength of gravity 10 to 36 times the strength of gravity so it kind of puts the weak force in its place it's 10 to the 12 times stronger than the weak force so these are huge numbers that we're talking about either this relative that or even this relative to gravity and so you might be saying well you know the electromagnetic force that's unbelievably strong why doesn't that apply over over over these these kind of macro scales like gravity let me write there macro scales macro scales why doesn't it apply to macro scales and actually there's nothing about the electromagnetic force why it can't it or it actually does apply over large distances the reality though is you don't have these huge concentrations of either electric Coulomb charges or magnetism the way you do mass so the mass that you have such huge concentrations it can operate over huge huge distances even though it's way way way weaker than the electromagnetic force the electromagnetic force what happens is because it's both attractive and repulsive it tends to kind of sort itself out so you don't have these huge huge huge concentrations of charge now the other thing you might be wondering about is you know why is it called the electromagnetic force in our everyday life there's things like there's things like the Coulomb force that or the electrostatic force which we're familiar...
 \\\hline
@@
 lecture transcripts are displayed (lecture times are noted in square brackets).
-Timecourses of topic correlations for each question may be found in
+Time courses of topic correlations for each question may be found in
 Supplemntary Figures~\ref{fig:forces-peaks} and~\ref{fig:bos-peaks}. Note that
@@
 
-    \caption{\textbf{Topic correlation timeseries plots for individual
+    \caption{\textbf{Topic correlation time series plots for individual
     \textit{Four Fundamental Forces} questions}. Each panel displays a
-    timeseries plot showing how the question's topic vector correlates with the
+    time series plot showing how the question's topic vector correlates with the
     topic vectors for each timepoint of \textit{Four Fundamental Forces}. The
-    shaded regions in each curve denote the full width at half maximum (FWHM)
+    shaded regions in each curve denote the full width at half maxima (FWHM)
     of the peak(s) in the curve. These FWHM intervals were used to identify the
@@
 
-    \caption{\textbf{Topic correlation timeseries plots for individual
+    \caption{\textbf{Topic correlation time series plots for individual
     \textit{Birth of Stars} questions}. Each panel displays a
-    timeseries plot showing how the question's topic vector correlates with the
+    time series plot showing how the question's topic vector correlates with the
     topic vectors for each timepoint of \textit{Birth of Stars}. The
-    shaded regions in each curve denote the full width at half maximum (FWHM)
+    shaded regions in each curve denote the full width at half maxima (FWHM)
     of the peak(s) in the curve. These FWHM intervals were used to identify the
@@
     words in both). \textbf{B. Single-timepoint comparisons for \textit{Birth
-    of Stars}. Same format as Panel A. \textbf{C. Topic correlation timeseries
+    of Stars}}. Same format as Panel A. \textbf{C. Topic correlation time series
     plots.} This panel is in the same format as Figure 4A from the main text,
@@
     the example question highlighted in green in Panel B has been emphasized
-    for the \textbf{Birth of Stars} traces on the right. \textbf{D. Jaccard
-    similarity timeseries plots.} These panels are in the same format as Panel
-    C, but they display the Jaccard similarity timeseries for the same
+    for the \textit{Birth of Stars} traces on the right. \textbf{D. Jaccard
+    similarity time series plots.} These panels are in the same format as Panel
+    C, but they display the Jaccard similarity time series for the same
     questions. \textbf{E. Question and lecture text.} The text for the example
@@
     from the best-matching intervals of the lectures (computed using topic
-    correlations; see Supp. Tab.~\ref{tab:matches}) are shown on the bottom.}}
+    correlations; see Supp.~Tab.~\ref{tab:matches}) are shown on the bottom.}
 
@@
 
-    \caption{\textbf{Comparing LDA vs. BERT embeddings}. The rows of the
-    display the equivalents of Figures 2C (top row), 4A and B (middle two
-    rows), and 3B (bottom row) computed using LDA (left) and BERT (right).}
+    \caption{\textbf{Comparing LDA vs. BERT embeddings}. The rows display the
+    equivalents of main text Figure 2C (top row), Figures 4A and 4B (middle two
+    rows), and Figure 3B (bottom row) computed using LDA (left) and BERT
+    (right).}
 

### 2023-10-24 paper/main.tex
edits through intro

@@
 ability to answer simple questions about it. However, text embedding
-models~\citep[e.g., ][]{LandDuma97, DeerEtal90, BleiEtal03,
+models~\citep[e.g.,][]{LandDuma97, DeerEtal90, BleiEtal03,
   BleiLaff06, MikoEtal13a, CerEtal18, BrowEtal20, ViswEtal17} also
@@
 feature vectors to two conceptually related documents, \textit{even
-  when the specific words contained in those documents do not fully
+  when the specific words contained in those documents have limited
   overlap}. In this way, ``concepts'' are defined implicitly by the
@@
 Given these insights, what form might a representation of the sum total of a
-person's knowledge take (speculatively)? First, we might require a means of
-systematically describing or representing the nearly infinite set of possible
+person's knowledge take? First, we might require a means of
+systematically describing or representing (at least some subset of) the nearly infinite set of possible
 things a person could know. Second, we might want to account for potential
@@
     \caption{\textbf{Which parts of each lecture are captured by each
-    question?} Each panel displays timeseries plots showing how each question's
+    question?} Each panel displays time series plots showing how each question's
     topic vector correlates with each video timepoint's topic vector (Panel
@@
 matches'' between individual questions and individual moments of each lecture
-(Figs.~\ref{fig:question-correlations},~\ldaVsBERT). The timeseries plot of
+(Figs.~\ref{fig:question-correlations},~\ldaVsBERT). The time series plot of
 individual questions' correlations are different from each other when computed
@@
 similar. This tells us that LDA is capturing some differences in content
-between the questions, whereas BERT is not. The timeseries plots of individual
+between the questions, whereas BERT is not. The time series plots of individual
 questions' correlations have clear ``peaks'' when computed using LDA, but not
@@
 approach. Whereas the LDA-based approach often yields a clear peak in the
-timeseries of correlations between each question and the corresponding lecture,
+time series of correlations between each question and the corresponding lecture,
 the Jaccard similarity-based approach does not. Furthermore, these LDA-based
@@
 linear interpolation (independently for each topic dimension) to resample the
-resulting timeseries to one vector per second. We also used the fitted model to
+resulting time series to one vector per second. We also used the fitted model to
 obtain topic vectors for each question in our pool (see Supp.~Tab.~\questions).

### 2023-10-24 paper/main.tex
dealing with misc editorial requests

--- 2023-10-24 paper/main.tex
@@
 each quiz, and the orders of answer options for each question, were also
-randomized. Our experimental protocol was approved by the Committee for the
-Protection of Human Subjects at Dartmouth College. We used this experiment to
-develop and test our computational framework for estimating knowledge and
-learning.
+randomized. We obtained informed consent from all participants, and our
+experimental protocol was approved by the Committee for the Protection of Human
+Subjects at Dartmouth College. We used this experiment to develop and test our
+computational framework for estimating knowledge and learning.
 
 \subsection*{Analysis}
+
+\subsubsection*{Statistics}
+
+All of the statistical tests performed in our study were two-sided. The 95\%
+confidence intervals we reported for each correlation were estimated by
+generating 10,000 bootstrap distributions of correlation coefficients by
+sampling (with replacement) from the observed data.
 
@@
 words.''). Conceptually, each topic is intended to give larger weights to words
-that are semantically related, as implied by their co-occurring in the same
-documents. After fitting a topic model, each document in the training set, or
-any \textit{new} document that contains at least some of the words in the
-model's vocabulary, may be represented as a $k$-dimensional vector describing
-how much the document (most probably) reflects each topic. To select an
-appropriate $k$ for our model, as a starting point, we identified the minimum
-number of topics that yielded at least one ``unused'' topic (i.e., in which all
-words in the vocabulary were assigned uniform weights) after training. This
-indicated that the number of topics was sufficient to capture the set of latent
-themes present in the two lectures (from which we constructed our document
-corpus, as described below). We found this value to be $k = 15$ topics. We
-found that with a limited number of additional adjustments
+that are semantically related (as inferred from their tendency to co-occur in
+the same document). After fitting a topic model, each document in the training
+set, or any \textit{new} document that contains at least some of the words in
+the model's vocabulary, may be represented as a $k$-dimensional vector
+describing how much the document (most probably) reflects each topic. To select
+an appropriate $k$ for our model, as a starting point, we identified the
+minimum number of topics that yielded at least one ``unused'' topic (i.e., in
+which all words in the vocabulary were assigned uniform weights) after
+training. This indicated that the number of topics was sufficient to capture
+the set of latent themes present in the two lectures (from which we constructed
+our document corpus, as described below). We found this value to be $k = 15$
+topics. We found that with a limited number of additional adjustments
 following~\citep{BoydMimn14}, such as removing corpus-specific stop-words, the

### 2023-10-24 paper/main.tex
updated editorial policy checklist and reporting summary, also split out data and code availability sections as requested by editor

@@
 
-\section*{Data and code availability}
-
-All of the data analyzed in this manuscript, along with all of the code for
-running our experiment and carrying out the analyses may be found at
+\section*{Data availability}
+
+All of the data analyzed in this manuscript may be found at
 https://github.com/Con\-text\-Lab/eff\-ic\-ient-learn\-ing-khan.
+
+\section*{Code availability}
+
+All of the code for running our experiment and carrying out the analyses may be
+found at https://github.com/Con\-text\-Lab/eff\-ic\-ient-learn\-ing-khan.
 

### 2023-10-24 paper/main.tex
reworked 'understanding' statement

--- 2023-10-24 paper/main.tex
@@
 properties of the elements, and other high-level characteristics of
-how they are used~\citep{Mann20, Mann21a}. According to these models,
+how they are used~\citep{Mann20, Mann21a}. 
+To be clear, this is not to say that text embedding models themselves 
+are capable of ``understanding'' deep conceptual meaning in any 
+traditional sense. But rather, their ability to capture the underlying 
+\textit{structure} of text documents beyond their surface-level contents 
+provides a computational framework through which those document's 
+deeper conceptual meaning may be quantified, explored, and understood.
+According to these models,
 the deep conceptual meaning of a document may be captured by a feature

### 2023-10-24 paper/main.tex
U with no tail

--- 2023-10-24 paper/main.tex
@@
 \newcommand{\individualLearningMapsB}{11}
+
+\newcommand{\U}{{\fontfamily{serif}\selectfont\ensuremath{\mathrm{U}}}}
 
@@
 estimated knowledge at the coordinates of \textit{incorrectly} answered
-questions (Fig.~\ref{fig:predictions}). We then used Mann-Whitney $U$-tests to
+questions (Fig.~\ref{fig:predictions}). We then used Mann-Whitney $\U$-tests to
 compare the means of these distributions of estimated knowledge.
@@
     held-out correctly (blue) or incorrectly (red) answered question. The
-    Mann-Whitney $U$-tests reported in each panel are between the distributions
+    Mann-Whitney $\U$-tests reported in each panel are between the distributions
     of estimated knowledge at the coordinates of correctly versus incorrectly
@@
 ``null'' effect persisted when we used \textit{all} of the Quiz 1 questions
-from a given participant to predict a held-out question (``All questions''; $U
+from a given participant to predict a held-out question (``All questions''; $\U
 = 50587, p = 0.723$), when we used questions from one lecture to predict
@@
 \textit{Four Fundamental Forces Questions} using \textit{Birth of Stars}
-questions: $U = 8244, p = 0.184$; predicting knowledge for held-out
-\textit{Birth of Stars} questions: $U = 8202.5, p = 0.161$), and when we used
+questions: $\U = 8244, p = 0.184$; predicting knowledge for held-out
+\textit{Birth of Stars} questions: $\U = 8202.5, p = 0.161$), and when we used
 questions from one lecture to predict knowledge at the embedding coordinate of
 a held-out question about the \textit{same} lecture (``Within-lecture'';
-\textit{Four Fundamental Forces}: $U = 7681.5, p = 0.746$; \textit{Birth of
-Stars}: $U = 8125, p = 0.204$). We believe that this reflects a floor effect:
+\textit{Four Fundamental Forces}: $\U = 7681.5, p = 0.746$; \textit{Birth of
+Stars}: $\U = 8125, p = 0.204$). We believe that this reflects a floor effect:
 when knowledge is low everywhere, there is little signal to differentiate
@@
 to held-out incorrectly answered questions. This held when we included all
-questions in the analysis ($U = 58332, p < 0.001$), when we predicted knowledge
-across-lectures (\textit{Four Fundamental Forces}: $U = 6749.5, p = 0.014$;
-\textit{Birth of Stars}: $U = 8480, p = 0.016$), and when we predicted
+questions in the analysis ($\U = 58332, p < 0.001$), when we predicted knowledge
+across-lectures (\textit{Four Fundamental Forces}: $\U = 6749.5, p = 0.014$;
+\textit{Birth of Stars}: $\U = 8480, p = 0.016$), and when we predicted
 knowledge at the embedding coordinates of held-out \textit{Four Fundamental
 Forces} questions using other \textit{Four Fundamental Forces} questions from
-the same quiz and participant ($U = 7224, p < 0.001$). This difference did
+the same quiz and participant ($\U = 7224, p < 0.001$). This difference did
 \textit{not} hold for within-lecture predictions of \textit{Birth of Stars}
-knowledge ($U = 7419, p = 0.739$). Again, we suggest that this might reflect a
+knowledge ($\U = 7419, p = 0.739$). Again, we suggest that this might reflect a
 floor effect whereby knowledge about the content of the \textit{Birth of Stars}
@@
 answered questions than for held-out incorrectly answered questions. This held
-when we included all questions in the analysis ($U = 38279, p = 0.022$), when
-we carried out across-lecture predictions (\textit{Four Fundamental Forces}: $U
-= 6684.5, p = 0.032$; \textit{Birth of Stars}: $U = 6414.5, p = 0.002$), and
+when we included all questions in the analysis ($\U = 38279, p = 0.022$), when
+we carried out across-lecture predictions (\textit{Four Fundamental Forces}: $\U
+= 6684.5, p = 0.032$; \textit{Birth of Stars}: $\U = 6414.5, p = 0.002$), and
 and when we carried out within-lecture predictions of held-out \textit{Birth of
 Stars} questions using other \textit{Birth of Stars} questions from the same
-quiz and participant ($U = 6126, p = 0.006$). However, we found the
+quiz and participant ($\U = 6126, p = 0.006$). However, we found the
 \textit{opposite} effect when we carried out within-lecture predictions of
 held-out \textit{Four Fundamental Forces} questions using other \textit{Four
-Fundamental Forces} questions from the same quiz and participant ($U = 6734, p
+Fundamental Forces} questions from the same quiz and participant ($\U = 6734, p
 = 0.027$). Specifically, held-out correctly answered Quiz 3 questions about

### 2023-10-24 paper/main.tex
standardized phrasing of lecture 1 title

--- 2023-10-24 paper/main.tex
@@
 (Fig.~\ref{fig:knowledge-timeseries}B). Indeed, we found that participants'
-estimated knowledge about the content of the \textit{Four Fundamental Forces}
+estimated knowledge about the content of \textit{Four Fundamental Forces}
 was substantially higher on Quiz~2 versus Quiz~1 ($t(49) = 8.764,~p < 0.001$)
@@
     the words' relative sizes correspond to their relative weights at the
-    starred location, and their colors indicate their relative weights in the
+    starred location, and their colors indicate their relative weights in
     \textit{Four Fundamental Forces} (blue) versus \textit{Birth of Stars}

### 2023-10-24 paper/main.tex

--- 2023-10-24 paper/main.tex
@@
 
-It is important to clarify that although we use topic model-derived embeddings
-to \textit{characterize} the conceptual content of the lectures and questions,
-we do not claim that the topic model itself \textit{understands} the conceptual
-content of the lectures or questions. Rather, we view the topic model as a tool
-for capturing the \textit{structure} of the conceptual content of the lectures
-and questions in a way that enables us to capture, quantify, and track and
-predict participants' knowledge.
-
 Another, more sensitive, way of summarizing the conceptual content of the

### 2023-10-24 paper/main.tex
added some explanatory text for the predictions analyses; also updated y-axes of predict-knowledge-questions fig

--- 2023-10-24 paper/main.tex
@@
 
+We carried out these analyses in three different ways. First, we used all of
+the questions from a given quiz (and participant) to predict knowledge at the
+embedding coordinate of a held-out question (``All questions'' in
+Fig.~\ref{fig:predictions}). This test was intended to serve as an overall
+baseline for the predictive power of our approach. Second, we used questions
+from one lecture to predict knowledge at the embedding coordinate of a held-out
+question about the \textit{other} lecture from the same quiz and participant
+(``Across-lecture'' in Fig.~\ref{fig:predictions}). This test was intended to
+test the \textit{generalizability} of our approach by asking whether our
+knowledge predictions held across the content areas of the two lectures. Third,
+we used questions from one lecture to predict knowledge at the embedding
+coordinate of a held-out question about the \textit{same} lecture from the same
+quiz and participant (``Within-lecture'' in Fig.~\ref{fig:predictions}). This
+test was intended to test the \textit{specificity} of our approach by asking
+whether our knowledge predictions could distinguish between questions about
+different content covered by the same lecture. We repeated each of these
+analyses using all possible held-out questions for each quiz and participant.
+
 For the initial quizzes participants took (prior to watching either lecture),
@@
 lead our approach to over-estimate knowledge for held-out questions about
-``forgotten'' knowledge that participants answered incorrectly.
+``forgotten'' knowledge that participants answered incorrectly.  Taken together,
+the results in Figure~\ref{fig:predictions} indicate that our approach can
+reliably predict acquired knowledge (especially about recently learned content),
+and that the knowledge predictions are generalizable across the content areas
+spanned by the two lectures and also specific enough to distinguish between
+questions about different content within the same lecture.
 

### 2023-10-24 paper/main.tex
edits through pdf line 345, source line 660

--- 2023-10-24 paper/main.tex
@@
 approach to test this claim. For each question, in turn, we used
-Equation~\ref{eqn:prop} to estimate each participant's knowledge at the given
+Equation~\ref{eqn:prop} to predict each participant's knowledge at the given
 question's embedding space coordinate, using all \textit{other} questions that
 participant answered on the same quiz. For each quiz, we grouped these
-estimates into two distributions: one for the estimated knowledge at the
+predicted knowledge values into two distributions: one for the predicted knowledge at the
 coordinates of \textit{correctly} answered questions, and another for the
-estimated knowledge at the coordinates of \textit{incorrectly} answered
+predicted knowledge at the coordinates of \textit{incorrectly} answered
 questions (Fig.~\ref{fig:predictions}). We then used Mann-Whitney $\U$-tests to
-compare the means of these distributions of estimated knowledge.
+compare the means of these distributions of predicted knowledge.
 
@@
 
-    \caption{\textbf{Estimating knowledge at the embedding coordinates of
+    \caption{\textbf{Predicting knowledge at the embedding coordinates of
     held-out questions.} Separately for each quiz (panel), we plot the
@@
     Mann-Whitney $\U$-tests reported in each panel are between the distributions
-    of estimated knowledge at the coordinates of correctly versus incorrectly
+    of predicted knowledge at the coordinates of correctly and incorrectly
     answered held-out questions. In the top row (``All questions''), we used
     all quiz questions (from each quiz, for each participant) except one to
-    estimate knowledge at the held-out question's embedding coordinate. In the
+    predict knowledge at the held-out question's embedding coordinate. In the
     middle rows (``Across-lecture''), we used all questions about one lecture
-    to estimate knowledge at the embedding coordinate of a held-out question
+    to predict knowledge at the embedding coordinate of a held-out question
     about the \textit{other} lecture. In the bottom row (``Within-lecture''),
-    we used all but one question about one lecture to estimate knowledge at the
+    we used all but one question about one lecture to predict knowledge at the
     embedding coordinate of a held-out question about the \textit{same}
@@
 
+We carried out these analyses in three different ways. First, we used all (but one) of
+the questions from a given quiz (and participant) to predict knowledge at the
+embedding coordinate of a held-out question (``All questions'' in
+Fig.~\ref{fig:predictions}). This test was intended to serve as an overall
+baseline for the predictive power of our approach. Second, we used questions
+about one lecture to predict knowledge at the embedding coordinate of a held-out
+question about the \textit{other} lecture, from the same quiz and participant
+(``Across-lecture'' in Fig.~\ref{fig:predictions}). This test was intended to
+test the \textit{generalizability} of our approach by asking whether our
+knowledge predictions held across the content areas of the two lectures. Third,
+we used questions about one lecture to predict knowledge at the embedding
+coordinate of a held-out question about the \textit{same} lecture, from the same
+quiz and participant (``Within-lecture'' in Fig.~\ref{fig:predictions}). This
+test was intended to test the \textit{specificity} of our approach by asking
+whether our knowledge predictions could distinguish between questions about
+different content covered by the same lecture. We repeated each of these
+analyses using all possible held-out questions for each quiz and participant.
+
 For the initial quizzes participants took (prior to watching either lecture),
-participants' estimated knowledge tended to be low overall, and relatively
+predicted knowledge tended to be low overall, and relatively
 unstructured (Fig.~\ref{fig:predictions}, left column). When we held out
-individual questions and estimated their knowledge at the held-out questions'
-embedding coordinates, we found no reliable differences in the estimates when
+individual questions and predicted their knowledge at the held-out questions'
+embedding coordinates, we found no reliable differences in the predictions when
 the held-out question had been correctly versus incorrectly answered. This
@@
 from a given participant to predict a held-out question (``All questions''; $\U
-= 50587, p = 0.723$), when we used questions from one lecture to predict
+= 50587,~p = 0.723$), when we used questions from one lecture to predict
 knowledge at the embedding coordinate of a held-out question about the
@@
 \textit{Four Fundamental Forces Questions} using \textit{Birth of Stars}
-questions: $\U = 8244, p = 0.184$; predicting knowledge for held-out
-\textit{Birth of Stars} questions: $\U = 8202.5, p = 0.161$), and when we used
+questions: $\U = 8244,~p = 0.184$; predicting knowledge for held-out
+\textit{Birth of Stars} questions: $\U = 8202.5,~p = 0.161$), and when we used
 questions from one lecture to predict knowledge at the embedding coordinate of
 a held-out question about the \textit{same} lecture (``Within-lecture'';
-\textit{Four Fundamental Forces}: $\U = 7681.5, p = 0.746$; \textit{Birth of
-Stars}: $\U = 8125, p = 0.204$). We believe that this reflects a floor effect:
+\textit{Four Fundamental Forces}: $\U = 7681.5,~p = 0.746$; \textit{Birth of
+Stars}: $\U = 8125,~p = 0.204$). We believe that this reflects a floor effect:
 when knowledge is low everywhere, there is little signal to differentiate
@@
 
-After watching \textit{Four Fundamental Forces}, estimated knowledge for
-held-out correctly answered questions (from the second quiz;
-Fig.~\ref{fig:predictions}, middle column) exhibited a positive shift relative
-to held-out incorrectly answered questions. This held when we included all
-questions in the analysis ($\U = 58332, p < 0.001$), when we predicted knowledge
-across-lectures (\textit{Four Fundamental Forces}: $\U = 6749.5, p = 0.014$;
-\textit{Birth of Stars}: $\U = 8480, p = 0.016$), and when we predicted
+After watching \textit{Four Fundamental Forces}, predicted knowledge for
+held-out questions that were answered correctly (from the second quiz;
+Fig.~\ref{fig:predictions}, middle column) exhibited a significantly shift relative
+to held-out questions that were answered incorrectly. This held when we included all
+questions in the analysis ($\U = 58332,~p < 0.001$), when we predicted knowledge
+across-lectures (\textit{Four Fundamental Forces}: $\U = 6749.5,~p = 0.014$;
+\textit{Birth of Stars}: $\U = 8480,~p = 0.016$), and when we predicted
 knowledge at the embedding coordinates of held-out \textit{Four Fundamental
 Forces} questions using other \textit{Four Fundamental Forces} questions from
-the same quiz and participant ($\U = 7224, p < 0.001$). This difference did
-\textit{not} hold for within-lecture predictions of \textit{Birth of Stars}
-knowledge ($\U = 7419, p = 0.739$). Again, we suggest that this might reflect a
+the same quiz and participant ($\U = 7224,~p < 0.001$). This difference did
+\textit{not} hold for within-lecture knowledge predictions at 
+knowledge at embedding space coordinates of \textit{Birth of Stars} questions ($\U = 7419,~p = 0.739$). Again, we suggest that this might reflect a
 floor effect whereby knowledge about the content of the \textit{Birth of Stars}
@@
 
-Finally, after watching \textit{Birth of Stars}, estimated knowledge for
+Finally, after watching \textit{Birth of Stars}, predicted knowledge for
 held-out correctly answered questions (from the third quiz;
-Fig.~\ref{fig:predictions}, right column) was higher for held-out correctly
-answered questions than for held-out incorrectly answered questions. This held
-when we included all questions in the analysis ($\U = 38279, p = 0.022$), when
+Fig.~\ref{fig:predictions}, right column) was higher than for held-out incorrectly answered questions. This held
+when we included all questions in the analysis ($\U = 38279,~p = 0.022$), when
 we carried out across-lecture predictions (\textit{Four Fundamental Forces}: $\U
-= 6684.5, p = 0.032$; \textit{Birth of Stars}: $\U = 6414.5, p = 0.002$), and
-and when we carried out within-lecture predictions of held-out \textit{Birth of
+= 6684.5,~p = 0.032$; \textit{Birth of Stars}: $\U = 6414.5,~p = 0.002$), and
+and when we carried out within-lecture knowledge predictions for held-out \textit{Birth of
 Stars} questions using other \textit{Birth of Stars} questions from the same
-quiz and participant ($\U = 6126, p = 0.006$). However, we found the
-\textit{opposite} effect when we carried out within-lecture predictions of
+quiz and participant ($\U = 6126,~p = 0.006$). However, we found the
+\textit{opposite} effect when we carried out within-lecture knowledge predictions for
 held-out \textit{Four Fundamental Forces} questions using other \textit{Four
-Fundamental Forces} questions from the same quiz and participant ($\U = 6734, p
-= 0.027$). Specifically, held-out correctly answered Quiz 3 questions about
-\textit{Four Fundamental Forces} had reliably \textit{lower} estimated
-knowledge than held-out incorrectly answered questions. Speculatively, we
+Fundamental Forces} questions from the same quiz and participant ($\U = 6734,~p
+= 0.027$). Specifically, on Quiz 3, our knowledge predictions for held-out correctly answered questions about
+\textit{Four Fundamental Forces} were reliably \textit{lower} than those for their incorrectly answered counterparts. Speculatively, we
 suggest that this may reflect participants forgetting some of the \textit{Four
@@
 lead our approach to over-estimate knowledge for held-out questions about
-``forgotten'' knowledge that participants answered incorrectly.
-
-That the knowledge estimates derived from the text embedding space reliably
+``forgotten'' knowledge that participants answered incorrectly.  Taken together,
+the results in Figure~\ref{fig:predictions} indicate that our approach can
+reliably predict acquired knowledge (especially about recently learned content),
+and that the knowledge predictions are generalizable across the content areas
+spanned by the two lectures, while also specific enough to distinguish between
+questions about more subtly different content within the same lecture.
+
+That the knowledge predictions derived from the text embedding space reliably
 distinguish between held-out correctly versus incorrectly answered questions

### 2023-10-25 paper/main.tex
edits through pdf line 364, source line 686

@@
 That the knowledge predictions derived from the text embedding space reliably
-distinguish between held-out correctly versus incorrectly answered questions
-(Fig.~\ref{fig:predictions}) suggests that the text embedding space bears at
-least some relationship to participants' knowledge. But what does that
-relationship look like as we move through the embedding space? For example,
-suppose we know that a participant answers a question (at embedding coordinate
-$X$) correctly. As we move away from $X$ in the embedding space, how does quiz
-performance ``fall off'' with distance? Or, suppose the participant instead
-answered that same question \textit{in}correctly. Again, as we move away from
-$X$ in the embedding space, how do the chances that the participant does
-\textit{not} know about the content change with distance? We reasoned that,
-assuming our space is capturing something about how participants actually
-organize their knowledge, conceptual knowledge right around $X$ should be
-similar to the participant's knowledge of the content at $X$. And at another
-extreme, at some distance (after moving sufficiently far away from $X$), our
-guesses about what participants know (based on their response to the question
-at location $X$) should be no better than guessing based on their overall
-proportion of correctly answered questions—i.e., if $Y$ is very far away from
-$X$, all we can do with the participant's response to $X$ is guess that ``their
-performance on quiz questions about $Y$ is about equal to their average
-performance on quiz questions about any material.''
+distinguish between correctly and incorrectly answered held-out questions
+(Fig.~\ref{fig:predictions}) suggests that spatial relationships within this
+ space can help explain what participants know. But how far does this
+explanatory power extend? For example, suppose we know that a participant
+correctly answered a question at embedding coordinate $x$. As we move farther away
+from $x$ in the embedding space, how does the likelihood that the participant knows about the content at a given location ``fall off'' with distance?
+Conversely, suppose the participant instead answered that same question
+\textit{in}correctly. Again, as we move farther away from $x$ in the embedding space,
+how does the likelihood that the participant does \textit{not} know about a coordinate's
+content change with distance? We reasoned that, assuming our embedding space is capturing
+something about how individuals actually organize 
+their knowledge, a participant's ability to answer questions 
+embedded very close to $x$ should tend to be similar to their 
+ability to answer the question embedded \textit{at} $x$. Whereas 
+at another extreme, once we reach some sufficiently large 
+distance from $x$, our ability to infer whether or not a participant 
+will correctly answer a question based on their ability to answer 
+the question at $x$ should be no better than guessing based on 
+their \textit{overall} proportion of correctly answered questions. In 
+other words, beyond the maximum distance at which the participant's
+ ability to answer the question at $x$ is informative of their ability to 
+ answer a second question at location $y$, then guessing the outcome 
+ at $y$ based on $x$ should be no more successful than guessing 
+ based on a measure that does not consider embedding space distance.
 

### 2023-10-25 paper/main.tex

@@
 held-out questions that were answered correctly (from the second quiz;
-Fig.~\ref{fig:predictions}, middle column) exhibited a significantly shift relative
-to held-out questions that were answered incorrectly. This held when we included all
-questions in the analysis ($\U = 58332,~p < 0.001$), when we predicted knowledge
-across-lectures (\textit{Four Fundamental Forces}: $\U = 6749.5,~p = 0.014$;
-\textit{Birth of Stars}: $\U = 8480,~p = 0.016$), and when we predicted
-knowledge at the embedding coordinates of held-out \textit{Four Fundamental
-Forces} questions using other \textit{Four Fundamental Forces} questions from
-the same quiz and participant ($\U = 7224,~p < 0.001$). This difference did
-\textit{not} hold for within-lecture knowledge predictions at 
-knowledge at embedding space coordinates of \textit{Birth of Stars} questions ($\U = 7419,~p = 0.739$). Again, we suggest that this might reflect a
-floor effect whereby knowledge about the content of the \textit{Birth of Stars}
-material is relatively low everywhere in that region of text embedding space.
+Fig.~\ref{fig:predictions}, middle column) exhibited a significant positive
+shift relative to held-out questions that were answered incorrectly. This held
+when we included all questions in the analysis ($\U = 58332,~p < 0.001$), when
+we predicted knowledge across-lectures (\textit{Four Fundamental Forces}: $\U =
+6749.5,~p = 0.014$; \textit{Birth of Stars}: $\U = 8480,~p = 0.016$), and when
+we predicted knowledge at the embedding coordinates of held-out \textit{Four
+Fundamental Forces} questions using other \textit{Four Fundamental Forces}
+questions from the same quiz and participant ($\U = 7224,~p < 0.001$). This
+difference did \textit{not} hold for within-lecture knowledge predictions at
+knowledge at embedding space coordinates of \textit{Birth of Stars} questions
+($\U = 7419,~p = 0.739$). Again, we suggest that this might reflect a floor
+effect whereby, at that point in the participants' training, their knowledge
+about the content of the \textit{Birth of Stars} material is relatively low
+everywhere in that region of text embedding space.
 
@@
 held-out correctly answered questions (from the third quiz;
-Fig.~\ref{fig:predictions}, right column) was higher than for held-out incorrectly answered questions. This held
-when we included all questions in the analysis ($\U = 38279,~p = 0.022$), when
-we carried out across-lecture predictions (\textit{Four Fundamental Forces}: $\U
-= 6684.5,~p = 0.032$; \textit{Birth of Stars}: $\U = 6414.5,~p = 0.002$), and
-and when we carried out within-lecture knowledge predictions for held-out \textit{Birth of
-Stars} questions using other \textit{Birth of Stars} questions from the same
-quiz and participant ($\U = 6126,~p = 0.006$). However, we found the
-\textit{opposite} effect when we carried out within-lecture knowledge predictions for
-held-out \textit{Four Fundamental Forces} questions using other \textit{Four
-Fundamental Forces} questions from the same quiz and participant ($\U = 6734,~p
-= 0.027$). Specifically, on Quiz 3, our knowledge predictions for held-out correctly answered questions about
-\textit{Four Fundamental Forces} were reliably \textit{lower} than those for their incorrectly answered counterparts. Speculatively, we
-suggest that this may reflect participants forgetting some of the \textit{Four
-Fundamental Forces} content. If this forgetting happens in a relatively
-``random'' way (with respect to spatial distance within the text embedding
-space), then it could explain why some held-out questions about \textit{Four
-Fundamental Forces} were answered incorrectly, even if questions at nearby
-coordinates (i.e., about similar content) were answered correctly. This might
-lead our approach to over-estimate knowledge for held-out questions about
-``forgotten'' knowledge that participants answered incorrectly.  Taken together,
-the results in Figure~\ref{fig:predictions} indicate that our approach can
-reliably predict acquired knowledge (especially about recently learned content),
-and that the knowledge predictions are generalizable across the content areas
-spanned by the two lectures, while also specific enough to distinguish between
-questions about more subtly different content within the same lecture.
+Fig.~\ref{fig:predictions}, right column) was higher than for held-out
+incorrectly answered questions. This held when we included all questions in the
+analysis ($\U = 38279,~p = 0.022$), when we carried out across-lecture
+predictions (\textit{Four Fundamental Forces}: $\U = 6684.5,~p = 0.032$;
+\textit{Birth of Stars}: $\U = 6414.5,~p = 0.002$), and and when we carried out
+within-lecture knowledge predictions for held-out \textit{Birth of Stars}
+questions using other \textit{Birth of Stars} questions from the same quiz and
+participant ($\U = 6126,~p = 0.006$). However, we found the \textit{opposite}
+effect when we carried out within-lecture knowledge predictions for held-out
+\textit{Four Fundamental Forces} questions using other \textit{Four Fundamental
+Forces} questions from the same quiz and participant ($\U = 6734,~p = 0.027$).
+Specifically, on Quiz 3, our knowledge predictions for held-out correctly
+answered questions about \textit{Four Fundamental Forces} were reliably
+\textit{lower} than those for their incorrectly answered counterparts.
+Speculatively, we suggest that this may reflect participants forgetting some of
+the \textit{Four Fundamental Forces} content. If this forgetting happens in a
+relatively ``random'' way (with respect to spatial distance within the text
+embedding space), then it could explain why some held-out questions about
+\textit{Four Fundamental Forces} were answered incorrectly, even if questions
+at nearby coordinates (i.e., about similar content) were answered correctly.
+This might lead our approach to over-estimate knowledge for held-out questions
+about ``forgotten'' knowledge that participants answered incorrectly. Taken
+together, the results in Figure~\ref{fig:predictions} indicate that our
+approach can reliably predict acquired knowledge (especially about recently
+learned content), and that the knowledge predictions are generalizable across
+the content areas spanned by the two lectures, while also specific enough to
+distinguish between questions about more subtly different content within the
+same lecture.
 

### 2023-10-25 paper/main.tex
udpated knowledge map figures

@@
 That the knowledge predictions derived from the text embedding space reliably
-distinguish between correctly and incorrectly answered held-out questions
+distinguish between held-out correctly versus incorrectly answered questions
 (Fig.~\ref{fig:predictions}) suggests that spatial relationships within this
@@
 explanatory power extend? For example, suppose we know that a participant
-correctly answered a question at embedding coordinate $x$. As we move farther away
-from $x$ in the embedding space, how does the likelihood that the participant knows about the content at a given location ``fall off'' with distance?
-Conversely, suppose the participant instead answered that same question
-\textit{in}correctly. Again, as we move farther away from $x$ in the embedding space,
-how does the likelihood that the participant does \textit{not} know about a coordinate's
-content change with distance? We reasoned that, assuming our embedding space is capturing
-something about how individuals actually organize 
-their knowledge, a participant's ability to answer questions 
-embedded very close to $x$ should tend to be similar to their 
-ability to answer the question embedded \textit{at} $x$. Whereas 
-at another extreme, once we reach some sufficiently large 
-distance from $x$, our ability to infer whether or not a participant 
-will correctly answer a question based on their ability to answer 
-the question at $x$ should be no better than guessing based on 
-their \textit{overall} proportion of correctly answered questions. In 
-other words, beyond the maximum distance at which the participant's
- ability to answer the question at $x$ is informative of their ability to 
- answer a second question at location $y$, then guessing the outcome 
- at $y$ based on $x$ should be no more successful than guessing 
- based on a measure that does not consider embedding space distance.
+correctly answered a question at embedding coordinate $x$. As we move farther
+away from $x$ in the embedding space, how does the likelihood that the
+participant knows about the content at a given location ``fall off'' with
+distance? Conversely, suppose the participant instead answered that same
+question \textit{in}correctly. Again, as we move farther away from $x$ in the
+embedding space, how does the likelihood that the participant does \textit{not}
+know about a coordinate's content change with distance? We reasoned that,
+assuming our embedding space is capturing something about how individuals
+actually organize their knowledge, a participant's ability to answer questions
+embedded very close to $x$ should tend to be similar to their ability to answer
+the question embedded \textit{at} $x$. Whereas at another extreme, once we
+reach some sufficiently large distance from $x$, our ability to infer whether
+or not a participant will correctly answer a question based on their ability to
+answer the question at $x$ should be no better than guessing based on their
+\textit{overall} proportion of correctly answered questions. In other words,
+beyond the maximum distance at which the participant's ability to answer the
+question at $x$ is informative of their ability to answer a second question at
+location $y$, then guessing the outcome at $y$ based on $x$ should be no more
+successful than guessing based on a measure that does not consider embedding
+space distance.
 

### 2023-10-25 paper/old2.tex
udpated knowledge map figures

--- 2023-10-25 paper/main.tex
@@
 That the knowledge predictions derived from the text embedding space reliably
-distinguish between correctly and incorrectly answered held-out questions
-(Fig.~\ref{fig:predictions}) suggests that spatial relationships within this
- space can help explain what participants know. But how far does this
+distinguish between held-out correctly versus incorrectly answered questions
+(Fig.~\ref{fig:predictions}) suggests that spatial relationships in the text
+embedding space can help explain what participants know. But how far does this
 explanatory power extend? For example, suppose we know that a participant
-correctly answered a question at embedding coordinate $x$. As we move farther away
-from $x$ in the embedding space, how does the likelihood that the participant knows about the content at a given location ``fall off'' with distance?
-Conversely, suppose the participant instead answered that same question
-\textit{in}correctly. Again, as we move farther away from $x$ in the embedding space,
-how does the likelihood that the participant does \textit{not} know about a coordinate's
-content change with distance? We reasoned that, assuming our embedding space is capturing
-something about how individuals actually organize 
-their knowledge, a participant's ability to answer questions 
-embedded very close to $x$ should tend to be similar to their 
-ability to answer the question embedded \textit{at} $x$. Whereas 
-at another extreme, once we reach some sufficiently large 
-distance from $x$, our ability to infer whether or not a participant 
-will correctly answer a question based on their ability to answer 
-the question at $x$ should be no better than guessing based on 
-their \textit{overall} proportion of correctly answered questions. In 
-other words, beyond the maximum distance at which the participant's
- ability to answer the question at $x$ is informative of their ability to 
- answer a second question at location $y$, then guessing the outcome 
- at $y$ based on $x$ should be no more successful than guessing 
- based on a measure that does not consider embedding space distance.
+answers a question (at embedding coordinate $x$) correctly. As we move away
+from $x$ in the embedding space, how does their knowledge ``fall off'' with
+distance? Or, suppose the participant instead answered that same question
+\textit{in}correctly. Again, as we move away from $x$ in the embedding space,
+how do the chances that the participant does \textit{not} know about the
+content change with distance? We reasoned that, assuming our space is capturing
+something about how participants actually organize their knowledge, conceptual
+knowledge right around $x$ should be similar to the participant's knowledge of
+the content at $x$. And at another extreme, at some distance (after moving
+sufficiently far away from $x$), our guesses about what participants know
+(based on their response to the question at location $x$) should be no better
+than guessing based on their overall proportion of correctly answered
+questions—i.e., if $y$ is very far away from $x$, all we can do with the
+participant's response to $x$ is guess that ``their performance on quiz
+questions about $y$ will be about equal to their average performance on quiz
+questions about any material.''
 

### 2023-10-25 paper/main.tex
working through issues discussed on slack + updated changes doc

@@
 content that is highly similar to (but not precisely the same as) that
-contained in the two lectures. This change in the number of topics overcame an
-undesirable behavior in the UMAP embedding procedure~\citep{McInEtal18a},
-whereby embedding coordinates for the 15-topic model tended to be ``clumped''
-into separated clusters, rather than forming a smooth trajectory through the 2D
-space. When we increased the number of topics to 100, the embedding coordinates
-in the 2D space formed a smooth trajectory through the space, with
-substantially less clumping (Fig.~\ref{fig:knowledge-maps}). We note that we
-used these 2D maps solely for visualization; all relevant comparisons, distance
-computations, and statistical tests we report above were carried out in the
-original 15-dimensional space, using the 15-topic model. Aside from increasing
-the number of topics from 15 to 100, all other procedures and model parameters
-were carried over from the preceding analyses. As in our other analyses, we
-resampled each lecture's topic trajectory to 1~Hz and projected each question
-into a shared text embedding space.
+contained in the two lectures. We note that we used these 2D maps solely for
+visualization; all relevant comparisons, distance computations, and statistical
+tests we report above were carried out in the original 15-dimensional space,
+using the 15-topic model. Aside from increasing the number of topics from 15 to
+100, all other procedures and model parameters were carried over from the
+preceding analyses. As in our other analyses, we resampled each lecture's topic
+trajectory to 1~Hz and projected each question into a shared text embedding
+space.
 
@@
 same order (i.e., \textit{Four Fundamental Forces} followed by \textit{Birth of
-Stars}). While we are not aware of any specific confounds of viewing order, nor
-have are we aware of how or why viewing order might influence our main
-findings, we acknowledge that we did not control for potential order effects in
-our study.
+Stars}).
 
@@
 questions that tested for general conceptual knowledge about basic physics
-(covering material that was not presented in either video). One of our group's
-undergraduate research assistants worked alongside a rotating Masters student
-to develop this set of questions (these researchers are acknowledged in our
-paper for their contribution, although they did not meet the criteria for
-authorship discussed with all team members at the start of the project, as
-determined by J.R.M.) The senior author (J.R.M.) tasked the pair of researchers
-with coming up with ``15 conceptual questions about each lecture, along with 9
-additional questions about general physics knowledge.'' To help broaden the set
-of lecture-specific questions, the researchers were further instructed to work
-through each lecture in small segments, identify what each segment was
-``about'' conceptually, and then write a question about that concept. The
-general physics questions were drawn from the researchers' coursework along
-with internet searches and brainstorming with the project team and other
-members of J.R.M.'s lab. The final set of questions (and response options) was
-reviewed and approved by J.R.M. before we collected or analyzed the text or
-experimental data.
+(covering material that was not presented in either video). To help broaden the
+set of lecture-specific questions, our team worked through each lecture in
+small segments to identify what each segment was ``about'' conceptually, and
+then write a question about that concept. The general physics questions were
+drawn our team's prior coursework and areas of interest, along with internet
+searches and brainstorming with the project team and other members of J.R.M.'s
+lab. The final set of questions (and response options) was reviewed and
+approved by J.R.M. before we collected or analyzed the text or experimental
+data.
 
@@
 Projection~\citep[UMAP; ][]{McInEtal18a, McInEtal18b} to construct a 2D
-projection of the text embedding space. Sampling the original 100-dimensional
-space at high resolution to obtain an adequate set of topic vectors spanning
-the embedding space would be computationally intractable. However, sampling a
-2D grid is trivial.
+projection of the text embedding space. Whereas our main analyses used a
+15-topic embedding space, we used a 100-topic embedding space for these
+visualizations. This change in the number of topics overcame an undesirable
+behavior in the UMAP embedding procedure~\citep{McInEtal18a}, whereby embedding
+coordinates for the 15-topic model tended to be ``clumped'' into separated
+clusters, rather than forming a smooth trajectory through the 2D space. When we
+increased the number of topics to 100, the embedding coordinates in the 2D
+space formed a smooth trajectory through the space, with substantially less
+clumping (Fig.~\ref{fig:knowledge-maps}). Creating a ``map'' by
+sampling this 100-dimensional space at high resolution to obtain an adequate
+set of topic vectors spanning the embedding space would be computationally
+intractable. However, sampling a 2D grid is trivial.
 

### 2023-10-25 paper/main.tex
cha cha cha changes.....

@@
 searches and brainstorming with the project team and other members of J.R.M.'s
-lab. The final set of questions (and response options) was reviewed and
-approved by J.R.M. before we collected or analyzed the text or experimental
-data.
-
-We note that estimating the specific ``amount'' of conceptual understanding
-that each question ``requires'' to answer is somewhat subjective, and might
-even come down to the ``strategy'' a given participant uses to answer the
-question at that particular moment. The full set of questions and answer
-choices may be found in Supplementary Table~\questions.
+lab. Although we attempted to design the questions to test ``conceptual
+knowledge,'' we note that estimating the specific ``amount'' of conceptual
+understanding that each question ``requires'' to answer is somewhat subjective,
+and might even come down to the ``strategy'' a given participant uses to answer
+the question at that particular moment. The full set of questions and answer
+choices may be found in Supplementary Table~\questions.  The final set of
+questions (and response options) was reviewed and approved by J.R.M. before we
+collected or analyzed the text or experimental data.
 

### 2023-10-25 paper/main.tex
more slack discussion-inspired changes-- updating description of putting stop word list together

@@
 lectures participants watched, we first fit a new topic model to the lectures'
-sliding windows with (up to)~$k = 100$~topics. Conceptually, increasing the
+sliding windows with $k = 100$~topics. Conceptually, increasing the
 number of topics used by the model functions to increase the ``resolution'' of
@@
 Dirichlet Allocation; ][]{BleiEtal03} trained on a set of documents, to
-discover a set of (up to) $k$ ``topics'' or ``themes.'' Formally, each topic is
+discover a set of $k$ ``topics'' or ``themes.'' Formally, each topic is
 defined as a distribution of weights over words in the model's vocabulary

### 2023-10-25 paper/main.tex
forgot to commit main.tex/main.pdf

@@
 augmenting the Natural Language Toolkit~\citep[NLTK; ][]{BirdEtal09} English
-stop word list with the following additional words, selected using the approach
-suggested by~\citep{BoydMimn14}: ``actual,'' ``actually,'' ``also,'' ``bit,''
-``could,'' ``e,'' ``even,'' ``first,'' ``follow,'' ``following,'' ``four,''
-``let,'' ``like,'' ``mc,'' ``really,'', ``saw,'' ``see,'' ``seen,'' ``thing,''
-and ``two.'' This yielded sliding windows with an average of 73.8 remaining
-words, and lasting for an average of 62.22~seconds. We treated the text from
-each sliding window as a single ``document,'' and combined these documents
-across the two videos' windows to create a single training corpus for the topic
-model.
+stop word list with the following additional words, selected using one of the
+approaches suggested by~\citep{BoydMimn14}: ``actual,'' ``actually,'' ``also,''
+``bit,'' ``could,'' ``e,'' ``even,'' ``first,'' ``follow,'' ``following,''
+``four,'' ``let,'' ``like,'' ``mc,'' ``really,'', ``saw,'' ``see,'' ``seen,''
+``thing,'' and ``two.'' This yielded sliding windows with an average of 73.8
+remaining words, and lasting for an average of 62.22~seconds. We treated the
+text from each sliding window as a single ``document,'' and combined these
+documents across the two videos' windows to create a single training corpus for
+the topic model.
 

### 2023-10-25 paper/main.tex
(hopefully) last round of edits from JRM

--- 2023-10-25 paper/main.tex
@@
     \caption{\textbf{Predicting knowledge at the embedding coordinates of
-    held-out questions.} Separately for each quiz (panel), we plot the
+    held-out questions.} Separately for each quiz (column), we plot the
     distributions of predicted knowledge at the embedding coordinates of each
     held-out correctly (blue) or incorrectly (red) answered question. The
-    Mann-Whitney $\U$-tests reported in each panel are between the distributions
-    of predicted knowledge at the coordinates of correctly and incorrectly
-    answered held-out questions. In the top row (``All questions''), we used
-    all quiz questions (from each quiz, for each participant) except one to
-    predict knowledge at the held-out question's embedding coordinate. In the
-    middle rows (``Across-lecture''), we used all questions about one lecture
-    to predict knowledge at the embedding coordinate of a held-out question
-    about the \textit{other} lecture. In the bottom row (``Within-lecture''),
-    we used all but one question about one lecture to predict knowledge at the
-    embedding coordinate of a held-out question about the \textit{same}
-    lecture. We repeated each of these analyses using all possible held-out
-    questions for each quiz and participant.}
+    Mann-Whitney $\U$-tests reported in each panel are between the
+    distributions of predicted knowledge at the coordinates of correctly and
+    incorrectly answered held-out questions. In the top row (``All
+    questions''), we used all quiz questions (from each quiz, for each
+    participant) except one to predict knowledge at the held-out question's
+    embedding coordinate. In the middle rows (``Across-lecture''), we used all
+    questions about one lecture to predict knowledge at the embedding
+    coordinate of a held-out question about the \textit{other} lecture. In the
+    bottom row (``Within-lecture''), we used all but one question about one
+    lecture to predict knowledge at the embedding coordinate of a held-out
+    question about the \textit{same} lecture. We repeated each of these
+    analyses using all possible held-out questions for each quiz and
+    participant. The arrows at the tops of each panel indicate whether the
+    average predicted knowledge was higher for held-out correctly answered
+    (left) or incorrectly answered (right) questions.}
 
@@
 
-    \caption{\textbf{Quiz performance falls off gradually in text embedding
-    space.} \textbf{A. Performance versus distance.} For each participant, for
-    each correctly answered question (blue) or incorrectly answered question
-    (red), we computed the proportion of correctly answered questions within a
-    given distance of that question's embedding coordinate. We repeated this
-    analysis for all questions and participants, and separately for each quiz
-    (column). The black lines denote the average proportion correct across
-    \textit{all} questions included in the analysis at the given distance.
-    \textbf{B. Maximum distance for which performance is reliably different
-    from the average.} We used a bootstrap procedure
-    (see~\nameref{subsec:smoothness}) to estimate the point at which the blue
-    and red lines in Panel A reliably diverged from the black line. We repeated
-    this analysis separately for correctly and incorrectly answered questions
-    from each quiz. \textbf{All panels.} Error ribbons denote
+    \caption{\textbf{Knowledge falls off gradually in text embedding space.}
+    \textbf{A. Performance versus distance.} For each participant, for each
+    correctly answered question (blue) or incorrectly answered question (red),
+    we computed the proportion of correctly answered questions within a given
+    distance of that question's embedding coordinate. We used these proportions
+    as a proxy for participants' knowledge about the content within that region
+    of the embedding space. We repeated this analysis for all questions and
+    participants, and separately for each quiz (column). The black lines denote
+    the average proportion correct across \textit{all} questions included in
+    the analysis at the given distance. \textbf{B. Maximum distance for which
+    performance is reliably different from the average.} We used a bootstrap
+    procedure (see~\nameref{subsec:smoothness}) to estimate the point at which
+    the blue and red lines in Panel A reliably diverged from the black line. We
+    repeated this analysis separately for correctly and incorrectly answered
+    questions from each quiz. \textbf{All panels.} Error ribbons denote
     bootstrap-estimated 95\% confidence intervals.}
@@
 explicitly modeling the content of individual lectures or questions is to
-leverage the models' ability to generate text. For example, generative text
+leverage the models' abilities to generate text. For example, generative text
 models like ChatGPT~\citep{ChatGPT} and LLaMa~\citep{TouvEtal23} are already
@@
 Figure~\jaccard~asks ``Which of the following occurs as a cloud of atoms gets
-more dense?''. The LDA-based matches identify lecture timepoints where the
+more dense?'' The LDA-based matches identify lecture timepoints where the
 relevant \textit{topics} are discussed (e.g., when words like ``cloud,''
@@
 augmented by automated tools? How and why do learning needs and goals vary
-across people? How might we lower barriers of access to a high-quality
+across people? How might we lower barriers to receiving a high-quality
 education?
@@
 topics. We found that with a limited number of additional adjustments
-following~\citep{BoydMimn14}, such as removing corpus-specific stop-words, the
+following~\citep{BoydEtal14}, such as removing corpus-specific stop-words, the
 model yielded (subjectively) sensible and coherent topics. The distribution of
@@
 augmenting the Natural Language Toolkit~\citep[NLTK; ][]{BirdEtal09} English
-stop word list with the following additional words, selected using the approach
-suggested by~\citep{BoydMimn14}: ``actual,'' ``actually,'' ``also,'' ``bit,''
-``could,'' ``e,'' ``even,'' ``first,'' ``follow,'' ``following,'' ``four,''
-``let,'' ``like,'' ``mc,'' ``really,'', ``saw,'' ``see,'' ``seen,'' ``thing,''
-and ``two.'' This yielded sliding windows with an average of 73.8 remaining
-words, and lasting for an average of 62.22~seconds. We treated the text from
-each sliding window as a single ``document,'' and combined these documents
-across the two videos' windows to create a single training corpus for the topic
-model.
+stop word list with the following additional words, selected using one of the
+approaches suggested by~\citep{BoydEtal14}: ``actual,'' ``actually,'' ``also,''
+``bit,'' ``could,'' ``e,'' ``even,'' ``first,'' ``follow,'' ``following,''
+``four,'' ``let,'' ``like,'' ``mc,'' ``really,'', ``saw,'' ``see,'' ``seen,''
+``thing,'' and ``two.'' This yielded sliding windows with an average of 73.8
+remaining words, and lasting for an average of 62.22~seconds. We treated the
+text from each sliding window as a single ``document,'' and combined these
+documents across the two videos' windows to create a single training corpus for
+the topic model.
 
@@
 visualizations. This change in the number of topics overcame an undesirable
-behavior in the UMAP embedding procedure~\citep{McInEtal18a}, whereby embedding
+behavior in the UMAP embedding procedure, whereby embedding
 coordinates for the 15-topic model tended to be ``clumped'' into separated
@@
 
-Conceptualization: PCF, ACH, and JRM. Methodology: PCF, ACH, and JRM. Software:
-PCF. Validation: PCF. Formal analysis: PCF. Resources: PCF, ACH, and JRM. Data
-curation: PCF. Writing (original draft): JRM. Writing (review and editing):
-PCF, ACH, and JRM. Visualization: PCF and JRM. Supervision: JRM. Project
-administration: PCF. Funding acquisition: JRM.
+Conceptualization: P.C.F., A.C.H., and J.R.M. Methodology: P.C.F., A.C.H., and
+J.R.M. Software: P.C.F. Validation: P.C.F. Formal analysis: P.C.F. Resources: P.C.F.,
+A.C.H., and J.R.M. Data curation: P.C.F. Writing (original draft): J.R.M. Writing
+(review and editing): P.C.F., A.C.H., and J.R.M. Visualization: P.C.F. and J.R.M.
+Supervision: J.R.M. Project administration: P.C.F. Funding acquisition: J.R.M.
 

### 2023-10-25 paper/main.tex
added knowledge smoothness analyses description

@@
 
-In the analysis reported in Figure~\ref{fig:smoothness}A, we show how
-participants' quiz performance changes as a function of distance to a given
-correctly or incorrectly answered reference question. We used a bootstrap-based
-approach to estimate the maximum distances over which these proportions
-of correctly answered questions could be reliably distinguished from participants'
-overall average proportion of correctly answered questions.
-
-In our bootstrap procedure, we ran 10,000 iterations to estimate the
-relationship between participants' performance and the distance to a given
-reference question. For each of these iterations, for every individual quiz
-($q$), we first determined the across-participants average ``simple''
-proportion correct and its 95\% confidence interval. This interval was
-established by repeatedly (1,000 times) subsampling participants with
-replacement, computing the mean ``simple'' proportion correct for each
-subsample, and then deriving the 2.5\textsuperscript{th} and
-97.5\textsuperscript{th} percentiles from the distribution of these subsample
-means. We used this interval as our benchmark for determining whether the
-proportion of correctly answered questions for a given subset of questions was
-reliably different (at the $p < 0.05$ significance level) from the average
-proportion correct across all questions.
-
-Next, for each participant, we examined all 15 questions they answered on quiz
-$q$. We treated each question as the ``reference question'' in turn. Around
-this reference, we constructed a series of 15-dimensional spheres (starting
-with a radius of 0), where each successive sphere had a radius of 0.01
-(correlation distance) greater than its predecessor. Within each of these
-spheres, we calculated the proportion of questions answered correctly by the
-participant. This yielded two distinct sets of proportion-correct values for
-each binned distance (radius) for a specific participant and quiz: one set of
-values where the reference questions had been answered correctly, and another
-set where the reference questions had been answered incorrectly. From these, we
-established the average proportion correct within each radius for both
-categories of reference questions. Finally, we identified the minimum binned
-distance from the correctly answered reference questions for which the average
-proportion correct intersected the 95\% confidence interval of the simple
-average proportion correct computed earlier. We display the resulting distance
-estimates, for each quiz and reference question status, in
-Figure~\ref{fig:smoothness}B.
+In the analysis reported in Figure~\ref{fig:smoothness}A, we show how participants' ability to correctly answer quiz questions changes as a function of distance from a given correctly or incorrectly answered reference question.
+We used a bootstrap-based approach to estimate the maximum distances over which these proportions of correctly answered questions could be reliably distinguished from participants' overall average proportion of correctly answered questions.
+
+For each of 10,000 iterations, we drew a random subsample (with replacement) of 50 participants from our dataset full dataset.
+Within each iteration, we first computed the 95\% confidence interval (CI) of the across-subsample-participants mean proportion correct on each of the three quizzes, separately. 
+To compute this interval for each quiz, we repeatedly (1,000 times) subsampled participants (with replacement, from the outer subsample for the current iteration) and computed the mean proportion correct each of these inner subsamples.
+We then identified the 2.5\textsuperscript{th} and 97.5\textsuperscript{th} percentiles of the resulting distributions of 1,000 means. 
+These three intervals (one for each quiz) served as our thresholds for confidence that the proportion correct within a given distance from a reference question was reliably different (at the $p < 0.05$ significance level) from the average proportion correct across all questions on the given quiz.
+
+Next, for each participant in the current subsample, and for each of the three quizzes they completed (separately), we iteratively treated each of the 15 questions appearing on the given quiz as the ``reference'' question.
+We constructed a series of concentric 15-dimensional ``spheres'' centered on the reference question's embedding space coordinate, where each successive sphere's radius increased by 0.01 (correlation distance) between 0 and 2, inclusive (i.e., tiling the range of possible correlation distances with 201 spheres in total).
+We then computed the proportion of questions enclosed within each sphere that the participant answered correctly, and averaged these per-radius proportion correct scores across reference questions that were answered correctly, and those that were answered incorrectly.
+This resulted in two number-of-spheres sequences of proportion-correct scores for each subsample participant and quiz: one derived from correctly answered reference questions, and one derived from incorrectly answered reference questions.
+
+We computed the across-subsample-participants mean proportion correct for each radius value (i.e., sphere) and ``correctness'' of reference question. 
+This yielded two sequences of proportion-correct scores for each quiz, analogous to the blue and red lines displayed in Figure~\ref{fig:smoothness}A, but for the present subsample. 
+For each quiz, we then found the minimum distance from the reference question (i.e., sphere radius) at which each of these two sequences of per-radius proportion correct scores intersected the 95\% confidence interval for the overall proportion correct (i.e., analogous to the black error bands in Fig.~\ref{fig:smoothness}A).
+
+This resulted in two ``intersection'' distances for each quiz (for correctly answered and incorrectly answered reference questions). 
+Repeating this full process for each of the 10,000 bootstrap iterations output two distributions of intersection distances for each of the three quizzes. 
+The means and 95\% confidence intervals for these distributions are plotted in Figure~\ref{fig:smoothness}B.
 

### 2023-10-25 paper/supplement.tex
fix table 2 caption

@@
 
-    \caption{\textbf{Topics.} We fit a topic model with (up to) $k = 15$ topics
+    \caption{\textbf{Topics.} We fit a topic model with $k = 15$ topics
     to sliding windows parsed from the two course video transcripts

### 2023-10-25 paper/supplement.tex
cleaned up supplement

@@
 \caption{\textbf{Lecture-specific questions and lecture excerpts.} We used the
-text embeddings of each question about \textit{Four Fundamental Forces} (FFF)
-and \textit{Birth of Stars} to identify corresponding matching intervals of the
+text embeddings for each question about \textit{Four Fundamental Forces} (FFF)
+and \textit{Birth of Stars} (BoS) to identify corresponding matching intervals of the
 lectures. The text of the questions and the best-matching time intervals of the
@@
 Time courses of topic correlations for each question may be found in
-Supplemntary Figures~\ref{fig:forces-peaks} and~\ref{fig:bos-peaks}. Note that
+Supplementary Figures~\ref{fig:forces-peaks} and~\ref{fig:bos-peaks}. Note that
 no matching lecture interval was found for Question 29.} 

### 2024-01-10 paper/main.tex
"supplemental" --> "supplementary"
fixed typos identified by R2 (rev 2)

@@
 predictions (\textit{Four Fundamental Forces}: $\U = 6684.5,~p = 0.032$;
-\textit{Birth of Stars}: $\U = 6414.5,~p = 0.002$), and and when we carried out
+\textit{Birth of Stars}: $\U = 6414.5,~p = 0.002$), and when we carried out
 within-lecture knowledge predictions for held-out \textit{Birth of Stars}
@@
 \textit{conceptualize} similarly the content reflected by nearby embedding
-coordinates. The ``spatial smoothness'' of participants' knowledge (as
-estimated using quiz performance) is being captured by the knowledge maps we
-are inferring from their quiz responses (e.g.,
-Figs.~\ref{fig:smoothness},~\ref{fig:knowledge-maps}). In other words, our
-study shows that knowledge about a given concept implies knowledge about
+coordinates. How participants' knowledge falls off with spatial distance is
+captured by the knowledge maps we infer from their quiz responses
+(e.g., Figs.~\ref{fig:smoothness},~\ref{fig:knowledge-maps}). In other words,
+our study shows that knowledge about a given concept implies knowledge about
 related concepts, and we also show how estimated knowledge falls off with
@@
 intersection of words from $A$ and $B$ divided by the number of unique words in
-the union of words from $A$ and $B$. In a supplemental analysis (Supp.
+the union of words from $A$ and $B$. In a supplementary analysis (Supp.
 Fig.~\jaccard), we compared the LDA-based question-lecture matches we reported
@@
 
-In the analysis reported in Figure~\ref{fig:smoothness}A, we show how participants' ability to correctly answer quiz questions changes as a function of distance from a given correctly or incorrectly answered reference question.
-We used a bootstrap-based approach to estimate the maximum distances over which these proportions of correctly answered questions could be reliably distinguished from participants' overall average proportion of correctly answered questions.
-
-For each of 10,000 iterations, we drew a random subsample (with replacement) of 50 participants from our dataset full dataset.
-Within each iteration, we first computed the 95\% confidence interval (CI) of the across-subsample-participants mean proportion correct on each of the three quizzes, separately. 
-To compute this interval for each quiz, we repeatedly (1,000 times) subsampled participants (with replacement, from the outer subsample for the current iteration) and computed the mean proportion correct each of these inner subsamples.
-We then identified the 2.5\textsuperscript{th} and 97.5\textsuperscript{th} percentiles of the resulting distributions of 1,000 means. 
-These three intervals (one for each quiz) served as our thresholds for confidence that the proportion correct within a given distance from a reference question was reliably different (at the $p < 0.05$ significance level) from the average proportion correct across all questions on the given quiz.
-
-Next, for each participant in the current subsample, and for each of the three quizzes they completed (separately), we iteratively treated each of the 15 questions appearing on the given quiz as the ``reference'' question.
-We constructed a series of concentric 15-dimensional ``spheres'' centered on the reference question's embedding space coordinate, where each successive sphere's radius increased by 0.01 (correlation distance) between 0 and 2, inclusive (i.e., tiling the range of possible correlation distances with 201 spheres in total).
-We then computed the proportion of questions enclosed within each sphere that the participant answered correctly, and averaged these per-radius proportion correct scores across reference questions that were answered correctly, and those that were answered incorrectly.
-This resulted in two number-of-spheres sequences of proportion-correct scores for each subsample participant and quiz: one derived from correctly answered reference questions, and one derived from incorrectly answered reference questions.
-
-We computed the across-subsample-participants mean proportion correct for each radius value (i.e., sphere) and ``correctness'' of reference question. 
-This yielded two sequences of proportion-correct scores for each quiz, analogous to the blue and red lines displayed in Figure~\ref{fig:smoothness}A, but for the present subsample. 
-For each quiz, we then found the minimum distance from the reference question (i.e., sphere radius) at which each of these two sequences of per-radius proportion correct scores intersected the 95\% confidence interval for the overall proportion correct (i.e., analogous to the black error bands in Fig.~\ref{fig:smoothness}A).
-
-This resulted in two ``intersection'' distances for each quiz (for correctly answered and incorrectly answered reference questions). 
-Repeating this full process for each of the 10,000 bootstrap iterations output two distributions of intersection distances for each of the three quizzes. 
-The means and 95\% confidence intervals for these distributions are plotted in Figure~\ref{fig:smoothness}B.
+In the analysis reported in Figure~\ref{fig:smoothness}A, we show how
+participants' ability to correctly answer quiz questions changes as a function
+of distance from a given correctly or incorrectly answered reference question.
+We used a bootstrap-based approach to estimate the maximum distances over which
+these proportions of correctly answered questions could be reliably
+distinguished from participants' overall average proportion of correctly
+answered questions.
+
+For each of 10,000 iterations, we drew a random subsample (with replacement) of
+50 participants from our dataset. Within each iteration, we first computed the
+95\% confidence interval (CI) of the across-subsample-participants mean
+proportion correct on each of the three quizzes, separately. To compute this
+interval for each quiz, we repeatedly (1,000 times) subsampled participants
+(with replacement, from the outer subsample for the current iteration) and
+computed the mean proportion correct each of these inner subsamples. We then
+identified the 2.5\textsuperscript{th} and 97.5\textsuperscript{th} percentiles
+of the resulting distributions of 1,000 means. These three intervals (one for
+each quiz) served as our thresholds for confidence that the proportion correct
+within a given distance from a reference question was reliably different (at
+the $p < 0.05$ significance level) from the average proportion correct across
+all questions on the given quiz.
+
+Next, for each participant in the current subsample, and for each of the three
+quizzes they completed (separately), we iteratively treated each of the 15
+questions appearing on the given quiz as the ``reference'' question. We
+constructed a series of concentric 15-dimensional ``spheres'' centered on the
+reference question's embedding space coordinate, where each successive sphere's
+radius increased by 0.01 (correlation distance) between 0 and 2, inclusive
+(i.e., tiling the range of possible correlation distances with 201 spheres in
+total). We then computed the proportion of questions enclosed within each
+sphere that the participant answered correctly, and averaged these per-radius
+proportion correct scores across reference questions that were answered
+correctly, and those that were answered incorrectly. This resulted in two
+number-of-spheres sequences of proportion-correct scores for each subsample
+participant and quiz: one derived from correctly answered reference questions,
+and one derived from incorrectly answered reference questions.
+
+We computed the across-subsample-participants mean proportion correct for each
+radius value (i.e., sphere) and ``correctness'' of reference question. This
+yielded two sequences of proportion-correct scores for each quiz, analogous to
+the blue and red lines displayed in Figure~\ref{fig:smoothness}A, but for the
+present subsample. For each quiz, we then found the minimum distance from the
+reference question (i.e., sphere radius) at which each of these two sequences
+of per-radius proportion correct scores intersected the 95\% confidence
+interval for the overall proportion correct (i.e., analogous to the black error
+bands in Fig.~\ref{fig:smoothness}A).
+
+This resulted in two ``intersection'' distances for each quiz (for correctly
+answered and incorrectly answered reference questions). Repeating this full
+process for each of the 10,000 bootstrap iterations output two distributions of
+intersection distances for each of the three quizzes. The means and 95\%
+confidence intervals for these distributions are plotted in
+Figure~\ref{fig:smoothness}B.
 
@@
 visualizations. This change in the number of topics overcame an undesirable
-behavior in the UMAP embedding procedure, whereby embedding
-coordinates for the 15-topic model tended to be ``clumped'' into separated
-clusters, rather than forming a smooth trajectory through the 2D space. When we
-increased the number of topics to 100, the embedding coordinates in the 2D
-space formed a smooth trajectory through the space, with substantially less
-clumping (Fig.~\ref{fig:knowledge-maps}). Creating a ``map'' by
-sampling this 100-dimensional space at high resolution to obtain an adequate
-set of topic vectors spanning the embedding space would be computationally
-intractable. However, sampling a 2D grid is trivial.
+behavior in the UMAP embedding procedure, whereby embedding coordinates for the
+15-topic model tended to be ``clumped'' into separated clusters, rather than
+forming a smooth trajectory through the 2D space. When we increased the number
+of topics to 100, the embedding coordinates in the 2D space formed a smooth
+trajectory through the space, with substantially less clumping
+(Fig.~\ref{fig:knowledge-maps}). Creating a ``map'' by sampling this
+100-dimensional space at high resolution to obtain an adequate set of topic
+vectors spanning the embedding space would be computationally intractable.
+However, sampling a 2D grid is trivial.
 

### 2024-02-16 paper/main.tex

@@
 (with replacement, from the outer subsample for the current iteration) and
-computed the mean proportion correct each of these inner subsamples. We then
+computed the mean proportion correct of each of these inner subsamples. We then
 identified the 2.5\textsuperscript{th} and 97.5\textsuperscript{th} percentiles

### 2024-02-17 paper/main.tex
a few typo fixes in intro and early results

--- 2023-10-25 paper/main.tex
@@
 [0.539,~0.958]$). Simultaneously, as reported in Figure~\ref{fig:topics}B, the
-variability in topic expression across \textit{different} videos and
+variabilities in topic expression across \textit{different} videos and
 lecture-specific questions (i.e., Lecture~1 video vs.~Lecture~2 questions;
@@
 narrower range of content. Given the correspondence we found between the
-variability in topic expression across moments of each lecture and questions
+variabilities in topic expression across moments of each lecture and questions
 from its corresponding set (Fig.~\ref{fig:topics}), we wondered whether the
@@
 responses to a small set of multiple-choice questions to estimate how much the
-participant ``knows'' about the concept reflected by any arbitrary coordinate,
-$x$, in text embedding space (e.g., the content reflected by any moment in a
+participant ``knows'' about the concept reflected by any arbitrary coordinate
+$x$ in text embedding space (e.g., the content reflected by any moment in a
 lecture they had watched; see \nameref{subsec:traces}). Essentially, the
@@
     using responses from a single quiz (color). The traces are averaged across
-    participants. \textbf{B. Average estimated knowledge about \textbf{Four
+    participants. \textbf{B. Average estimated knowledge about \textit{Four
     Fundamental Forces}.} Each bar displays the across-timepoint average
@@
 participants' knowledge after watching each lecture. In other words, if
-participants learn about each lecture's content when they watch each lecture,
+participants learn about each lecture's content upon watching it,
 the knowledge estimates should capture that. After watching the \textit{Four
@@
 answer that question correctly or incorrectly. We developed a statistical
-approach to test this claim. For each question, in turn, we used
-Equation~\ref{eqn:prop} to predict each participant's knowledge at the given
-question's embedding space coordinate, using all \textit{other} questions that
-participant answered on the same quiz. For each quiz, we grouped these
-predicted knowledge values into two distributions: one for the predicted knowledge at the
-coordinates of \textit{correctly} answered questions, and another for the
-predicted knowledge at the coordinates of \textit{incorrectly} answered
-questions (Fig.~\ref{fig:predictions}). We then used Mann-Whitney $\U$-tests to
-compare the means of these distributions of predicted knowledge.
+approach to test this claim. 
+For each of the three quizzes, separately, we
+
+%For each question, in turn, we used
+%Equation~\ref{eqn:prop} to predict each participant's knowledge at the given
+%question's embedding space coordinate, using all \textit{other} questions that
+%participant answered on the same quiz. For each quiz, we grouped these
+%predicted knowledge values into two distributions: one for the predicted knowledge at the
+%coordinates of \textit{correctly} answered questions, and another for the
+%predicted knowledge at the coordinates of \textit{incorrectly} answered
+%questions (Fig.~\ref{fig:predictions}). We then used Mann-Whitney $\U$-tests to
+%compare the means of these distributions of predicted knowledge.
 

### 2024-02-17 paper/main.tex

@@
 
-In the analysis reported in Figure~\ref{fig:smoothness}A, we show how participants' ability to correctly answer quiz questions changes as a function of distance from a given correctly or incorrectly answered reference question.
-We used a bootstrap-based approach to estimate the maximum distances over which these proportions of correctly answered questions could be reliably distinguished from participants' overall average proportion of correctly answered questions.
-
-For each of 10,000 iterations, we drew a random subsample (with replacement) of 50 participants from our dataset full dataset.
-Within each iteration, we first computed the 95\% confidence interval (CI) of the across-subsample-participants mean proportion correct on each of the three quizzes, separately. 
-To compute this interval for each quiz, we repeatedly (1,000 times) subsampled participants (with replacement, from the outer subsample for the current iteration) and computed the mean proportion correct each of these inner subsamples.
-We then identified the 2.5\textsuperscript{th} and 97.5\textsuperscript{th} percentiles of the resulting distributions of 1,000 means. 
-These three intervals (one for each quiz) served as our thresholds for confidence that the proportion correct within a given distance from a reference question was reliably different (at the $p < 0.05$ significance level) from the average proportion correct across all questions on the given quiz.
-
-Next, for each participant in the current subsample, and for each of the three quizzes they completed (separately), we iteratively treated each of the 15 questions appearing on the given quiz as the ``reference'' question.
-We constructed a series of concentric 15-dimensional ``spheres'' centered on the reference question's embedding space coordinate, where each successive sphere's radius increased by 0.01 (correlation distance) between 0 and 2, inclusive (i.e., tiling the range of possible correlation distances with 201 spheres in total).
-We then computed the proportion of questions enclosed within each sphere that the participant answered correctly, and averaged these per-radius proportion correct scores across reference questions that were answered correctly, and those that were answered incorrectly.
-This resulted in two number-of-spheres sequences of proportion-correct scores for each subsample participant and quiz: one derived from correctly answered reference questions, and one derived from incorrectly answered reference questions.
-
-We computed the across-subsample-participants mean proportion correct for each radius value (i.e., sphere) and ``correctness'' of reference question. 
-This yielded two sequences of proportion-correct scores for each quiz, analogous to the blue and red lines displayed in Figure~\ref{fig:smoothness}A, but for the present subsample. 
-For each quiz, we then found the minimum distance from the reference question (i.e., sphere radius) at which each of these two sequences of per-radius proportion correct scores intersected the 95\% confidence interval for the overall proportion correct (i.e., analogous to the black error bands in Fig.~\ref{fig:smoothness}A).
-
-This resulted in two ``intersection'' distances for each quiz (for correctly answered and incorrectly answered reference questions). 
-Repeating this full process for each of the 10,000 bootstrap iterations output two distributions of intersection distances for each of the three quizzes. 
-The means and 95\% confidence intervals for these distributions are plotted in Figure~\ref{fig:smoothness}B.
+In the analysis reported in Figure~\ref{fig:smoothness}A, we show how
+participants' ability to correctly answer quiz questions changes as a function
+of distance from a given correctly or incorrectly answered reference question.
+We used a bootstrap-based approach to estimate the maximum distances over which
+these proportions of correctly answered questions could be reliably
+distinguished from participants' overall average proportion of correctly
+answered questions.
+
+For each of 10,000 iterations, we drew a random subsample (with replacement) of
+50 participants from our dataset. Within each iteration, we first computed the
+95\% confidence interval (CI) of the across-subsample-participants mean
+proportion correct on each of the three quizzes, separately. To compute this
+interval for each quiz, we repeatedly (1,000 times) subsampled participants
+(with replacement, from the outer subsample for the current iteration) and
+computed the mean proportion correct of each of these inner subsamples. We then
+identified the 2.5\textsuperscript{th} and 97.5\textsuperscript{th} percentiles
+of the resulting distributions of 1,000 means. These three intervals (one for
+each quiz) served as our thresholds for confidence that the proportion correct
+within a given distance from a reference question was reliably different (at
+the $p < 0.05$ significance level) from the average proportion correct across
+all questions on the given quiz.
+
+Next, for each participant in the current subsample, and for each of the three
+quizzes they completed (separately), we iteratively treated each of the 15
+questions appearing on the given quiz as the ``reference'' question. We
+constructed a series of concentric 15-dimensional ``spheres'' centered on the
+reference question's embedding space coordinate, where each successive sphere's
+radius increased by 0.01 (correlation distance) between 0 and 2, inclusive
+(i.e., tiling the range of possible correlation distances with 201 spheres in
+total). We then computed the proportion of questions enclosed within each
+sphere that the participant answered correctly, and averaged these per-radius
+proportion correct scores across reference questions that were answered
+correctly, and those that were answered incorrectly. This resulted in two
+number-of-spheres sequences of proportion-correct scores for each subsample
+participant and quiz: one derived from correctly answered reference questions,
+and one derived from incorrectly answered reference questions.
+
+We computed the across-subsample-participants mean proportion correct for each
+radius value (i.e., sphere) and ``correctness'' of reference question. This
+yielded two sequences of proportion-correct scores for each quiz, analogous to
+the blue and red lines displayed in Figure~\ref{fig:smoothness}A, but for the
+present subsample. For each quiz, we then found the minimum distance from the
+reference question (i.e., sphere radius) at which each of these two sequences
+of per-radius proportion correct scores intersected the 95\% confidence
+interval for the overall proportion correct (i.e., analogous to the black error
+bands in Fig.~\ref{fig:smoothness}A).
+
+This resulted in two ``intersection'' distances for each quiz (for correctly
+answered and incorrectly answered reference questions). Repeating this full
+process for each of the 10,000 bootstrap iterations output two distributions of
+intersection distances for each of the three quizzes. The means and 95\%
+confidence intervals for these distributions are plotted in
+Figure~\ref{fig:smoothness}B.
 

### 2024-02-17 paper/main.tex
WIP updates to results section for GLMM analyses

@@
 average topic weights from each lecture and question set (averaging across time
-and questions, respectively) reveals a striking correspondence (Supp.
-Fig.~\topicWeights). Specifically, the average topic weights from Lecture~1 are
+and questions, respectively) reveals a striking correspondence 
+(Supp.~Fig.~\topicWeights). Specifically, the average topic weights from Lecture~1 are
 strongly correlated with the average topic weights from Lecture~1 questions
@@
 95\% CI~$= [0.456,~0.920]$). At the same time, the average topic weights from
-the two lectures are \textit{negatively} correlated with their non-matching
+the two lectures are \textit{negatively} correlated with the average topic weights from their non-matching
 question sets (Lecture~1 video vs.~Lecture~2 questions: $r(13) = -0.547,~p =
@@
 We also qualitatively examined the best-matching intervals for each question by
-comparing the question's text to the text of the most-correlated parts of the
+comparing the question's text to the transcribed text from the most-correlated parts of the
 lectures (Supp.~Tab.~\matchTab). Despite that the questions were excluded from
@@
 participants' knowledge. Traditional approaches to estimating how much a
-student ``knows'' about the content of a given lecture entail computing the
+student ``knows'' about the content of a given lecture entail administering some form of assessment (e.g., a quiz) and computing the
 proportion of correctly answered questions. But if two students receive
-identical scores on an exam, might our modeling framework help us to gain more
+identical scores on such an exam, might our modeling framework help us to gain more
 nuanced insights into the \textit{specific} content that each student has
@@
 lecture they had watched; see \nameref{subsec:traces}). Essentially, the
-estimated knowledge at coordinate $x$ is given by the weighted average
+estimated knowledge at coordinate $x$ is given by the weighted
 proportion of quiz questions the participant answered correctly, where the
@@
 presented in each moment of each lecture, we can obtain a detailed time course
-describing how much ``knowledge'' the participant has about the content
+describing how much ``knowledge'' that participant has about the content
 presented at any part of the lecture. As shown in
@@
 content tested by a given question, our estimates of their knowledge should
-carry some predictive information about whether the participant is likely to
-answer that question correctly or incorrectly. We developed a statistical
-approach to test this claim. 
-For each of the three quizzes, separately, we
-
-%For each question, in turn, we used
-%Equation~\ref{eqn:prop} to predict each participant's knowledge at the given
-%question's embedding space coordinate, using all \textit{other} questions that
-%participant answered on the same quiz. For each quiz, we grouped these
-%predicted knowledge values into two distributions: one for the predicted knowledge at the
-%coordinates of \textit{correctly} answered questions, and another for the
-%predicted knowledge at the coordinates of \textit{incorrectly} answered
-%questions (Fig.~\ref{fig:predictions}). We then used Mann-Whitney $\U$-tests to
-%compare the means of these distributions of predicted knowledge.
+carry some predictive information about whether they are likely to answer that 
+question correctly or incorrectly. We developed a statistical approach to test this claim. 
+For each quiz question a participant answered, in turn, we used Equation~\ref{eqn:prop} to estimate their knowledge at the given question's embedding space coordinate, based on other questions that participant answered on the same quiz.
+We repeated this for all participants, and for each of the three quizzes. 
+Then, separately for each quiz, we fit a generalized linear mixed model (GLMM) with a logistic link function to explain the likelihood of correctly answering a question as a function of estimated knowledge for its embedding coordinate, while accounting for random variation among participants and questions (see Sec.~\nameref{subsec:glmm}).
+To assess the predictive value of the knowledge estimates, we performed likelihood-ratio tests comparing each GLMMs to an analogous (i.e., nested) ``null'' model that did not consider estimated knowledge.
 
@@
 
+\subsubsection*{GLMM METHODS SECTION PLACEHOLDER}\label{subsec:glmm}
+
 \subsubsection*{Estimating the ``smoothness'' of knowledge}\label{subsec:smoothness}

### 2024-02-18 paper/main.tex
updated fig 6 caption

@@
 question correctly or incorrectly. We developed a statistical approach to test this claim. 
-For each quiz question a participant answered, in turn, we used Equation~\ref{eqn:prop} to estimate their knowledge at the given question's embedding space coordinate, based on other questions that participant answered on the same quiz.
+For each quiz question a participant answered, in turn, we used Equation~\ref{eqn:prop} to estimate their knowledge at the given question's embedding space coordinate based on other questions that participant answered on the same quiz.
 We repeated this for all participants, and for each of the three quizzes. 
-Then, separately for each quiz, we fit a generalized linear mixed model (GLMM) with a logistic link function to explain the likelihood of correctly answering a question as a function of estimated knowledge for its embedding coordinate, while accounting for random variation among participants and questions (see Sec.~\nameref{subsec:glmm}).
-To assess the predictive value of the knowledge estimates, we performed likelihood-ratio tests comparing each GLMMs to an analogous (i.e., nested) ``null'' model that did not consider estimated knowledge.
+Then, separately for each quiz, we fit a generalized linear mixed model (GLMM) with a logistic link function to explain the likelihood of correctly answering a question as a function of estimated knowledge for its embedding coordinate, while accounting for random variation among participants and questions (see \nameref{subsec:glmm}).
+To assess the predictive value of the knowledge estimates, we compared each GLMMs to an analogous (i.e., nested) ``null'' model that did not consider estimated knowledge using using parametric bootstrap likelihood-ratio tests.
 
@@
     \centering
+    % TODO: adjust width to max possible based on finalized caption
     \includegraphics[width=0.7\textwidth]{figs/predict-knowledge-questions}
-
-    \caption{\textbf{Predicting knowledge at the embedding coordinates of
-    held-out questions.} Separately for each quiz (column), we plot the
-    distributions of predicted knowledge at the embedding coordinates of each
-    held-out correctly (blue) or incorrectly (red) answered question. The
-    Mann-Whitney $\U$-tests reported in each panel are between the
-    distributions of predicted knowledge at the coordinates of correctly and
-    incorrectly answered held-out questions. In the top row (``All
-    questions''), we used all quiz questions (from each quiz, for each
-    participant) except one to predict knowledge at the held-out question's
-    embedding coordinate. In the middle rows (``Across-lecture''), we used all
-    questions about one lecture to predict knowledge at the embedding
-    coordinate of a held-out question about the \textit{other} lecture. In the
-    bottom row (``Within-lecture''), we used all but one question about one
-    lecture to predict knowledge at the embedding coordinate of a held-out
-    question about the \textit{same} lecture. We repeated each of these
-    analyses using all possible held-out questions for each quiz and
-    participant. The arrows at the tops of each panel indicate whether the
-    average predicted knowledge was higher for held-out correctly answered
-    (left) or incorrectly answered (right) questions.}
+    \caption{\textbf{Predicting success on held-out questions using estimated knowledge.}
+    We used generalized linear mixed models (GLMMs) to model the likelihood of correctly answering a quiz question as a function of estimated knowledge for its embedding coordinate (see \nameref{subsec:glmm}).
+    Separately for each quiz (column), we examined this relationship based on three different sets of knowledge estimates: knowledge for each question based on all other questions the same participant answered on the same quiz (``All questions''; top row), knowledge for each question about one lecture based on all questions (from the same participant and quiz) about the \textit{other} lecture (``Across-lecture''; middle rows), and knowledge for each question about one lecture based on all other questions (from the same participant and quiz) about the \textit{same} lecture (``Within-lecture''; bottom rows).
+    The background in each panel displays the relative density of observed correctly (blue) versus incorrectly (red) answered questions over the range of knowledge estimates. 
+    The black curves display the (population-level) GLMM-predicted probabilities of correctly answering a question as a function of estimated knowledge. 
+    Error ribbons denote 95\% confidence intervals.}
 
@@
 
-We carried out these analyses in three different ways. First, we used all (but one) of
-the questions from a given quiz (and participant) to predict knowledge at the
-embedding coordinate of a held-out question (``All questions'' in
-Fig.~\ref{fig:predictions}). This test was intended to serve as an overall
-baseline for the predictive power of our approach. Second, we used questions
-about one lecture to predict knowledge at the embedding coordinate of a held-out
-question about the \textit{other} lecture, from the same quiz and participant
-(``Across-lecture'' in Fig.~\ref{fig:predictions}). This test was intended to
-test the \textit{generalizability} of our approach by asking whether our
-knowledge predictions held across the content areas of the two lectures. Third,
-we used questions about one lecture to predict knowledge at the embedding
-coordinate of a held-out question about the \textit{same} lecture, from the same
-quiz and participant (``Within-lecture'' in Fig.~\ref{fig:predictions}). This
-test was intended to test the \textit{specificity} of our approach by asking
-whether our knowledge predictions could distinguish between questions about
-different content covered by the same lecture. We repeated each of these
-analyses using all possible held-out questions for each quiz and participant.
+We carried out three different versions of the analyses described above, wherein we considered different sources of information in our estimates of participants' knowledge for each quiz question. 
+First, we estimated knowledge at each question's embedding coordinate using \textit{all other} questions answered by the same participant on the same quiz (``All questions''; Fig.~\ref{fig:predictions}, top row).
+This test was intended to assess the overall predictive power of our approach. 
+Second, we estimated knowledge for each question about one lecture using only questions (from the same participant and quiz) about the \textit{other} lecture (``Across-lecture''; Fig.~\ref{fig:predictions}, middle rows).
+This test was intended to assess the \textit{generalizability} of our approach by asking whether our predictions held across the content areas of the two lectures.
+Third, we estimated knowledge for each question about a given lecture using only the other questions (from the same participant and quiz) about that \textit{same} lecture (``Within-lecture''; Fig.~\ref{fig:predictions}, bottom rows).
+This test was intended to assess the \textit{specificity} of our approach by asking whether our predictions could distinguish between questions about different content covered by the same lecture.
 

### 2024-02-19 paper/main.tex
updates to fig 6 text description

@@
 
+Our null hypothesis in performing these analyses is that the knowledge estimates we compute based on the quiz questions' embedding coordinates do \textit{not} provide useful information about participants' abilities to answer those questions.
+What result might we expect to see if this is the case? 
+To provide an intuition for this, consider the expected outcome if we carried out these same analyses using a simple proportion-correct measure in lieu of our knowledge estimates. 
+Suppose a participant correctly answered $n$ out of 13 questions on a given quiz. 
+If we held out a single correctly answered question and computed the proportion of remaining questions answered correctly, that proportion would be $(n - 1) / 12$. 
+Whereas if we held out a single \textit{incorrectly} answered question and did the same, that proportion would be $n / 12$. 
+Thus for a given participant and quiz, a ``knowledge estimate'' computed as the simple (i.e., unweighted) remaining proportion-correct is perfectly inversely related to success on a held-out question: it will always be \textit{lower} for correctly answered questions than for incorrectly answered questions.
+Given that our knowledge estimates are computed as a weighted version of this same proportion-correct score (where each held-in question's weight reflects its embedding-space distance from the held-out question; see Eqn.~\ref{eqn:prop}), if these weights are uninformative (e.g., simply randomly distributed), then we would expect, on average, to see this same inverse relationship.
+It is only if the spatial relationships among the quiz questions' embedding coordinates map onto participants' knowledge in a meaningful way that we would we expect this relationship to be non-negative [PHRASING].
+
+When we fit a GLMM to estimates of participants' knowledge for each Quiz~1 question based on all other Quiz~1 questions, we observed this inverse relationship expected under our null hypothesis. 
+Specifically, higher estimated knowledge at the embedding coordinate of a held-out Quiz~1 question was associated with a lower likelihood of answering the question correctly (odds ratio $(OR) = 0.136$, likelihood-ratio test statistic $(\lambda_{LR}) = 19.749$, 95\%\ $\textnormal{CI} = [14.352,\ 26.545],\ p = 0.001$).
+However, when we repeated this analysis for quizzes 2 and 3, the direction of this relationship reversed: higher estimated knowledge for a given question predicted a greater likelihood of answering it correctly (Quiz~2: $OR = 2.905,\ \lambda_{LR} = 17.333,\ 95\%\ \textnormal{CI} = [14.966,\ 29.309],\ p = 0.002$; Quiz~3: $OR = 3.238,\ \lambda_{LR} = 6.882,\ 95\%\ \textnormal{CI} = [6.228,\ 8.184],\ p = 0.017$).
+Taken together, these results suggest that our knowledge estimations can reliably predict participants' likelihood of success on individual quiz questions, provided they have at least some amount of structured knowledge about the underlying concepts being tested.
+In other words, when participants' correct responses primarily arise from knowledge about the content probed by each question (e.g., after watching one or both lectures), these successes can be predicted from their ability to answer other questions about conceptually similar content (as captured by embedding-space distance).
+However, when a sufficiently large portion of participants' correct responses (presumably) reflect successful random guessing (such as on a multiple-choice quiz taken before viewing either lecture), our approach fails to predict these successes since they do not map onto embedding space distances in a meaningful way.
+
+%When we estimated participants' knowledge for each Quiz~1 question based on all other Quiz~1 questions, we found an inverse relationship.
+Specifically, higher estimated knowledge at the embedding coordinate at a held-out question was associated with a lower likelihood of answering the question correctly ($\textrm{odds ratio}\ (OR) = 0.136,\ \textrm{likelihood-ratio test statistic}\ (\lambda_{LR}) = 19.749,\ \textrm{95\% CI} = [14.352,\ 26.545],\ p = 0.001$).
+However, this inverse relationship in fact represents the expected result under our null hypothesis (that estimated knowledge is \textit{not} predictive of success on a question).
+An intuition for this can be taken from the expected outcome of same analysis based on the simple proportion correct, rather than estimated knowledge.
+Suppose a participant answered $n$ out of 13 quiz questions correctly.
+If we held out a single correctly answered question and computed the proportion of remaining questions answered correctly, that proportion would be $(n - 1) / 12$.
+Whereas if we held out a single incorrectly answered question, the proportion of remaining questions answered correctly would be $n / 12$.
+
+When we
+
+Taken together, the results of these sets of analyses suggest that our knowledge estimations can reliably predict participants' abilities to answer individual quiz questions, generalize across content areas, and distinguish between questions about similar content, provided that a basic set of assumptions about that content (as described above) can be assumed.
+
+% our approach works when participants have a minimal baseline level of knowledge about content predicted and used to predict
+% our approach generalizes when knowledge of content used to predict can be assumed to be a reasonable indicator of knowledge of content predicted
+% our approach has enough specificity to distinguish between content within the same lecture when it was just watched -- maybe when people forget a little bit they forget "randomly"?.
+
+% two conditions: participants have at least some knowledge of content being tested, and knowledge of content used to predict is good indicator of knowledge of content predicted / participants can be expected to have same level of knowledge for content used to predict and content predicted
+
 For the initial quizzes participants took (prior to watching either lecture),
@@
 the held-out question had been correctly versus incorrectly answered. This
-``null'' effect persisted when we used \textit{all} of the Quiz 1 questions
+``null'' effect persisted when we used \textit{all} of the Quiz~1 questions
 from a given participant to predict a held-out question (``All questions''; $\U
@@
 \textit{quiz questions}, not by the embeddings of either lecture (see
-Eqn.~\ref{eqn:rbf-knowledge}). Finally, the knowledge map estimated from Quiz 3
+Eqn.~\ref{eqn:rbf-knowledge}). Finally, the knowledge map estimated from Quiz~3
 responses shows a second increase in knowledge, localized to the region

### 2024-02-19 paper/main.tex
finished first pass at updated GLMM results section

--- 2024-02-18 paper/main.tex
@@
 Then, separately for each quiz, we fit a generalized linear mixed model (GLMM) with a logistic link function to explain the likelihood of correctly answering a question as a function of estimated knowledge for its embedding coordinate, while accounting for random variation among participants and questions (see \nameref{subsec:glmm}).
-To assess the predictive value of the knowledge estimates, we compared each GLMMs to an analogous (i.e., nested) ``null'' model that did not consider estimated knowledge using using parametric bootstrap likelihood-ratio tests.
+To assess the predictive value of the knowledge estimates, we compared each GLMMs to an analogous (i.e., nested) ``null'' model that did not consider estimated knowledge using parametric bootstrap likelihood-ratio tests.
 
@@
 
-For the initial quizzes participants took (prior to watching either lecture),
-predicted knowledge tended to be low overall, and relatively
-unstructured (Fig.~\ref{fig:predictions}, left column). When we held out
-individual questions and predicted their knowledge at the held-out questions'
-embedding coordinates, we found no reliable differences in the predictions when
-the held-out question had been correctly versus incorrectly answered. This
-``null'' effect persisted when we used \textit{all} of the Quiz 1 questions
-from a given participant to predict a held-out question (``All questions''; $\U
-= 50587,~p = 0.723$), when we used questions from one lecture to predict
-knowledge at the embedding coordinate of a held-out question about the
-\textit{other} lecture (``Across-lecture''; predicting knowledge for held-out
-\textit{Four Fundamental Forces Questions} using \textit{Birth of Stars}
-questions: $\U = 8244,~p = 0.184$; predicting knowledge for held-out
-\textit{Birth of Stars} questions: $\U = 8202.5,~p = 0.161$), and when we used
-questions from one lecture to predict knowledge at the embedding coordinate of
-a held-out question about the \textit{same} lecture (``Within-lecture'';
-\textit{Four Fundamental Forces}: $\U = 7681.5,~p = 0.746$; \textit{Birth of
-Stars}: $\U = 8125,~p = 0.204$). We believe that this reflects a floor effect:
-when knowledge is low everywhere, there is little signal to differentiate
-between what is known versus unknown.
-
-After watching \textit{Four Fundamental Forces}, predicted knowledge for
-held-out questions that were answered correctly (from the second quiz;
-Fig.~\ref{fig:predictions}, middle column) exhibited a significant positive
-shift relative to held-out questions that were answered incorrectly. This held
-when we included all questions in the analysis ($\U = 58332,~p < 0.001$), when
-we predicted knowledge across-lectures (\textit{Four Fundamental Forces}: $\U =
-6749.5,~p = 0.014$; \textit{Birth of Stars}: $\U = 8480,~p = 0.016$), and when
-we predicted knowledge at the embedding coordinates of held-out \textit{Four
-Fundamental Forces} questions using other \textit{Four Fundamental Forces}
-questions from the same quiz and participant ($\U = 7224,~p < 0.001$). This
-difference did \textit{not} hold for within-lecture knowledge predictions at
-knowledge at embedding space coordinates of \textit{Birth of Stars} questions
-($\U = 7419,~p = 0.739$). Again, we suggest that this might reflect a floor
-effect whereby, at that point in the participants' training, their knowledge
-about the content of the \textit{Birth of Stars} material is relatively low
-everywhere in that region of text embedding space.
-
-Finally, after watching \textit{Birth of Stars}, predicted knowledge for
-held-out correctly answered questions (from the third quiz;
-Fig.~\ref{fig:predictions}, right column) was higher than for held-out
-incorrectly answered questions. This held when we included all questions in the
-analysis ($\U = 38279,~p = 0.022$), when we carried out across-lecture
-predictions (\textit{Four Fundamental Forces}: $\U = 6684.5,~p = 0.032$;
-\textit{Birth of Stars}: $\U = 6414.5,~p = 0.002$), and when we carried out
-within-lecture knowledge predictions for held-out \textit{Birth of Stars}
-questions using other \textit{Birth of Stars} questions from the same quiz and
-participant ($\U = 6126,~p = 0.006$). However, we found the \textit{opposite}
-effect when we carried out within-lecture knowledge predictions for held-out
-\textit{Four Fundamental Forces} questions using other \textit{Four Fundamental
-Forces} questions from the same quiz and participant ($\U = 6734,~p = 0.027$).
-Specifically, on Quiz 3, our knowledge predictions for held-out correctly
-answered questions about \textit{Four Fundamental Forces} were reliably
-\textit{lower} than those for their incorrectly answered counterparts.
-Speculatively, we suggest that this may reflect participants forgetting some of
-the \textit{Four Fundamental Forces} content. If this forgetting happens in a
-relatively ``random'' way (with respect to spatial distance within the text
-embedding space), then it could explain why some held-out questions about
-\textit{Four Fundamental Forces} were answered incorrectly, even if questions
-at nearby coordinates (i.e., about similar content) were answered correctly.
-This might lead our approach to over-estimate knowledge for held-out questions
-about ``forgotten'' knowledge that participants answered incorrectly. Taken
-together, the results in Figure~\ref{fig:predictions} indicate that our
-approach can reliably predict acquired knowledge (especially about recently
-learned content), and that the knowledge predictions are generalizable across
-the content areas spanned by the two lectures, while also specific enough to
-distinguish between questions about more subtly different content within the
-same lecture.
+%When we estimated participants' knowledge for each Quiz~1 question based on all other Quiz~1 questions, we found an inverse relationship. 
+%Specifically, higher estimated knowledge at the embedding coordinate at a held-out question was associated with a lower likelihood of answering the question correctly ($\textrm{odds ratio}\ (OR) = 0.136,\ \textrm{likelihood-ratio test statistic}\ (\lambda_{LR}) = 19.749,\ \textrm{95\% CI} = [14.352,\ 26.545],\ p = 0.001$).
+%However, this inverse relationship in fact represents the expected result under our null hypothesis (that estimated knowledge is \textit{not} predictive of success on a question). 
+%An intuition for this can be taken from the expected outcome of same analysis based on the simple proportion correct, rather than estimated knowledge. 
+%Suppose a participant answered $n$ out of 13 quiz questions correctly. 
+%If we held out a single correctly answered question and computed the proportion of remaining questions answered correctly, that proportion would be $(n - 1) / 12$. 
+%Whereas if we held out a single incorrectly answered question, the proportion of remaining questions answered correctly would be $n / 12$.
+
+In performing this set of analyses, our null hypothesis is that the knowledge estimates we compute based on the quiz questions' embedding coordinates do \textit{not} provide useful information about participants' abilities to answer those questions.
+What result might we expect to see if this is the case? 
+To provide an intuition for this, consider the expected outcome if we carried out these same analyses using a simple proportion-correct measure in lieu of our knowledge estimates. 
+Suppose a participant correctly answered $n$ out of 13 questions on a given quiz. 
+If we held out a single correctly answered question and computed the proportion of remaining questions answered correctly, that proportion would be $(n - 1) / 12$. 
+Whereas if we held out a single \textit{incorrectly} answered question and did the same, that proportion would be $n / 12$. 
+Thus for a given participant and quiz, a ``knowledge estimate'' computed as the simple (i.e., unweighted) remaining proportion-correct is perfectly inversely related to success on a held-out question: it will always be \textit{lower} for correctly answered questions than for incorrectly answered questions.
+Given that our knowledge estimates are computed as a weighted version of this same proportion-correct score (where each held-in question's weight reflects its embedding-space distance from the held-out question; see Eqn.~\ref{eqn:prop}), if these weights are uninformative (e.g., simply randomly distributed), then we should expect to see this same inverse relationship emerge, on average.
+It is only if the spatial relationships among the quiz questions' embedding coordinates map onto participants' knowledge in a meaningful way that we would we expect this relationship to be non-negative [\textbf{PHRASING}].
+
+When we fit a GLMM to estimates of participants' knowledge for each Quiz~1 question based on all other Quiz~1 questions, we observed this null-hypothesized inverse relationship. 
+Specifically, higher estimated knowledge at the embedding coordinate of a held-out Quiz~1 question was associated with a lower likelihood of answering the question correctly (odds ratio $(OR) = 0.136$, likelihood-ratio test statistic $(\lambda_{LR}) = 19.749$, 95\%\ $\textnormal{CI} = [14.352,\ 26.545],\ p = 0.001$).
+However, when we repeated this analysis for quizzes 2 and 3, the direction of this relationship reversed: higher estimated knowledge for a given question predicted a greater likelihood of answering it correctly (Quiz~2: $OR = 2.905,\ \lambda_{LR} = 17.333,\ 95\%\ \textnormal{CI} = [14.966,\ 29.309],\ p = 0.002$; Quiz~3: $OR = 3.238,\ \lambda_{LR} = 6.882,\ 95\%\ \textnormal{CI} = [6.228,\ 8.184],\ p = 0.017$).
+Taken together, these results suggest that our knowledge estimations can reliably predict participants' likelihood of success on individual quiz questions, provided they have at least some amount of structured knowledge about the underlying concepts being tested.
+In other words, when participants' correct responses primarily arise from knowledge about the content probed by each question (e.g., after watching one or both lectures), these successes can be predicted from their ability to answer other questions about conceptually similar content (as captured by embedding-space distance).
+However, when a sufficiently large portion of participants' correct responses (presumably) reflect successful random guessing (such as on a multiple-choice quiz taken before viewing either lecture), our approach fails to accurately predict these successes since they do not map onto embedding space distances in a meaningful way [\textbf{PHRASING}].
+
+We observed a similar pattern when we fit GLMMs to estimates of participants' knowledge for each question about one lecture derived from other questions about the \textit{same} lecture. 
+Specifically, for questions that participants answered on Quiz~1, prior to watching either lecture, knowledge for the embedding coordinates of \textit{Four Fundamental Forces}-related questions estimated using other \textit{Four Fundamental Forces}-related questions did not reliably predict whether those questions were answered correctly ($OR = 1.891,\ \lambda_{LR} = 2.293,\ 95\%\ \textnormal{CI} = [2.091,\ 2.622],\ p = 0.139$).
+The same was true of knowledge estimates for \textit{Birth of Stars}-related questions based on other \textit{Birth of Stars}-related questions ($OR = 0.722,\ \lambda_{LR} = 5.115,\ 95\%\ \textnormal{CI} = [0.094,\ 0.146],\ p = 0.738$).
+When we recomputed these within-lecture knowledge estimates using questions from Quiz~2---which participants took immediately after viewing \textit{Four Fundamental Forces} but prior to viewing \textit{Birth of Stars}---we found that they now reliably predicted success on \textit{Four Fundamental Forces}-related questions ($OR = 9.023,\ \lambda_{LR} = 18.707,\ 95\%\ \textnormal{CI} = [10.877,\ 22.222],\ p = 0.001$) but not on \textit{Birth of Stars}-related questions ($OR = 0.306,\ \lambda_{LR} = 5.115,\ 95\%\ \textnormal{CI} = [4.624,\ 5.655],\ p = 0.055$).
+Using participants' responses from Quiz~3 (taken immediately after viewing \textit{Birth of Stars}), we found that within-lecture knowledge estimates for \textit{Birth of Stars}-related questions could now reliably predict success on those questions ($OR = 5.467,\ \lambda_{LR} = 10.670,\ 95\%\ \textnormal{CI} = [7.998, 12.532],\ p = 0.006$).
+However, within-lecture knowledge estimates for \textit{Four Fundamental Forces} questions answered on Quiz~3 were no longer directly related to the likelihood of successfully answering them and instead exhibited the inverse relationship we would expect to arise from unstructured knowledge (with respect to the embedding space; $OR = 0.013,\ \lambda_{LR} = 14.648,\ 95\%\ \textnormal{CI} = [10.695, 23.096],\ p = 0.001$).
+Speculatively, we suggest that this may reflect participants forgetting some of the \textit{Four Fundamental Forces} content (e.g., perhaps in favor of prioritizing encoding the just-watched \textit{Birth of Stars} content in preparation for the third quiz).
+If this forgetting happens in a relatively ``random'' way (with respect to spatial distance within the embedding space), then it could explain why some held-out questions about \textit{Four Fundamental Forces} were answered incorrectly, even if questions at nearby coordinates (i.e., about similar content) were answered correctly.
+This might lead our approach to over-estimate knowledge for held-out questions about ``forgotten'' knowledge that participants answered incorrectly.
+% ALTERNATE EXPLANATION -- embedding space is essentially ``saturated'' with correctly answered questions, so just like how on quiz 1 when relatively few questions are correct, most questions ``around'' them will be incorrect, on quiz 3 when relatively few questions are incorrect, most questions nearby will be correct.
+And because of this, on average, when the ``held-out'' question is one of the few incorrect ones, there will tend to be more correct ones ``held in'' than there will be when the held-out question is correct.
+% Also, maybe worth noting: while negative relationship is significant, it's super weak -- per the model, a "1-unit" increase in estimated knowledge corresponds to only a 1.28% decrease in probability of correct answer (p = OR / (1 + OR)).
+For comparison, for quiz3/within-lecture/birth of stars, 1-unit increase in estimated knowledge corresponds to a 84.5% increase in probability.
+So decrease is sig.
+but basically negligible.
+Taken together, these results suggest that our approach can distinguish between questions about different content covered by a single lecture when participants have sufficiently structured knowledge about that lecture's content, though this specificity may decrease further in time from when the lecture in question was viewed.
+
+Finally, when we fit GLMMs to estimates of participants' knowledge for questions about one lecture based on questions (from the same quiz) about the other lecture, we observed a similar but slightly more nuanced pattern.
+Essentially, while the previous set of analyses suggest that our approach's ability to make \textit{specific} predictions within content areas depends on participants having a minimum level of knowledge about the given content, the across-lecture analyses we performed suggest that our ability to \textit{generalize} these predictions across different content areas requires that participants' level of knowledge about the content used to make predictions be reasonably similar to their level of knowledge about the content for which these predictions are made [\textbf{PHRASING}].
+We found that using questions answered on Quiz~1, participants abilities to correctly answer questions about \textit{Four Fundamental Forces} could be predicted from their responses to questions about \textit{Birth of Stars} ($OR = 1.896,\ \lambda_{LR} = 7.205,\ 95\%\ \textnormal{CI} = [6.224, 7.524],\ p = 0.039$) and their ability to correctly answer \textit{Birth of Stars}-related questions could be predicted from their responses to \textit{Four Fundamental Forces}-related questions ($OR = 1.522,\ \lambda_{LR} =  6.448,\ 95\%\ \textnormal{CI} = [5.656, 6.843],\ p = 0.043$).
+We note, however, that these Quiz~1 knowledge estimates suffer from the same ``noise'' due to the (presumably) higher rate of participants successfully guessing correct answers on Quiz~1 as noted above, and as a result provide the weakest signal of any of the knowledge estimates that we found to reliably predict success.
+When we repeated this analysis using questions from Quiz~2, we found participants' responses to \textit{Four Fundamental Forces}-related questions did not reliably predict their success on \textit{Birth of Stars}-related questions ($OR = 1.865,\ \lambda_{LR} = 3.205,\ 95\%\ \textnormal{CI} = [3.027, 3.600],\ p = 0.125$), nor did their responses to \textit{Birth of Stars}-related questions reliably predict their success on \textit{Four Fundamental Forces}-related questions ($OR = 3.490,\ \lambda_{LR} = 3.266,\ 95\%\ \textnormal{CI} = [3.033, 3.866],\ p = 0.094$).
+\textbf{Sentence about why this makes sense given that participants hadn't viewed BoS yet.
+i.e., when predicting held-out FFF questions, correct vs.
+incorrect labels for held-in q's aren't meaningfully structured w.r.t.
+embedding space; when predicting held-out BoS q's, whether or not held-out q was correctly answered isn't meaningfully related to spatial structure of correctly answered q's in embedding space.}
+However, when we again computed these across-lecture knowledge predictions using questions from Quiz~3 (when participants had now viewed \textit{both} lectures, we found that we could again reliably predict success on questions about \textit{Four Fundamental Forces} ($OR = 11.294),\ \lambda_{LR} = 11.055,\ 95\%\ \textnormal{CI} = [9.126, 18.476],\ p = 0.004$) and \textit{Birth of Stars} ($OR = 7.302),\ \lambda_{LR} = 7.068,\ 95\%\ \textnormal{CI} = [6.490, 8.584],\ p = 0.017$).
+Across all three versions of these analyses, our results suggest that our knowledge estimations can reliably predict participants' abilities to answer individual quiz questions, distinguish between questions about similar content, and generalize across content areas, provided that participants' quiz responses reflect a minimum level of ``real'' knowledge about both content on which these predictions are based and that for which they are made [\textbf{PHRASING}].
+
+% our approach works when participants have a minimal baseline level of knowledge about content predicted and used to predict
+% our approach generalizes when knowledge of content used to predict can be assumed to be a reasonable indicator of knowledge of content predicted
+% our approach has enough specificity to distinguish between content within the same lecture when it was just watched -- maybe when people forget a little bit they forget "randomly"?.
+
+% potential new transition/motivation -- in the previous analyses, we identified a particular set of constraints on our estimates of participants' knowledge.
+This made us wonder about another potential constraint: how far away in topic space does the relevance of being able to answer a question extend and influence ability to answer a different question?
 

### 2024-02-19 paper/main.tex
cleanup to new fig 6 results description

@@
 This test was intended to assess the overall predictive power of our approach. 
-Second, we estimated knowledge for each question about one lecture using only questions (from the same participant and quiz) about the \textit{other} lecture (``Across-lecture''; Fig.~\ref{fig:predictions}, middle rows).
+Second, we estimated knowledge for each question about a given lecture using only the other questions (from the same participant and quiz) about that \textit{same} lecture (``Within-lecture''; Fig.~\ref{fig:predictions}, middle rows).
+This test was intended to assess the \textit{specificity} of our approach by asking whether our predictions could distinguish between questions about different content covered by the same lecture.
+Third, we estimated knowledge for each question about one lecture using only questions (from the same participant and quiz) about the \textit{other} lecture (``Across-lecture''; Fig.~\ref{fig:predictions}, bottom rows).
 This test was intended to assess the \textit{generalizability} of our approach by asking whether our predictions held across the content areas of the two lectures.
-Third, we estimated knowledge for each question about a given lecture using only the other questions (from the same participant and quiz) about that \textit{same} lecture (``Within-lecture''; Fig.~\ref{fig:predictions}, bottom rows).
-This test was intended to assess the \textit{specificity} of our approach by asking whether our predictions could distinguish between questions about different content covered by the same lecture.
-
-%When we estimated participants' knowledge for each Quiz~1 question based on all other Quiz~1 questions, we found an inverse relationship. 
-%Specifically, higher estimated knowledge at the embedding coordinate at a held-out question was associated with a lower likelihood of answering the question correctly ($\textrm{odds ratio}\ (OR) = 0.136,\ \textrm{likelihood-ratio test statistic}\ (\lambda_{LR}) = 19.749,\ \textrm{95\% CI} = [14.352,\ 26.545],\ p = 0.001$).
-%However, this inverse relationship in fact represents the expected result under our null hypothesis (that estimated knowledge is \textit{not} predictive of success on a question). 
-%An intuition for this can be taken from the expected outcome of same analysis based on the simple proportion correct, rather than estimated knowledge. 
-%Suppose a participant answered $n$ out of 13 quiz questions correctly. 
-%If we held out a single correctly answered question and computed the proportion of remaining questions answered correctly, that proportion would be $(n - 1) / 12$. 
-%Whereas if we held out a single incorrectly answered question, the proportion of remaining questions answered correctly would be $n / 12$.
 
@@
 Given that our knowledge estimates are computed as a weighted version of this same proportion-correct score (where each held-in question's weight reflects its embedding-space distance from the held-out question; see Eqn.~\ref{eqn:prop}), if these weights are uninformative (e.g., simply randomly distributed), then we should expect to see this same inverse relationship emerge, on average.
-It is only if the spatial relationships among the quiz questions' embedding coordinates map onto participants' knowledge in a meaningful way that we would we expect this relationship to be non-negative [\textbf{PHRASING}].
+It is only if the spatial relationships among the quiz questions' embedding coordinates map onto participants' knowledge in a meaningful way that we would we expect this relationship to be non-negative.
 
@@
 Taken together, these results suggest that our knowledge estimations can reliably predict participants' likelihood of success on individual quiz questions, provided they have at least some amount of structured knowledge about the underlying concepts being tested.
-In other words, when participants' correct responses primarily arise from knowledge about the content probed by each question (e.g., after watching one or both lectures), these successes can be predicted from their ability to answer other questions about conceptually similar content (as captured by embedding-space distance).
-However, when a sufficiently large portion of participants' correct responses (presumably) reflect successful random guessing (such as on a multiple-choice quiz taken before viewing either lecture), our approach fails to accurately predict these successes since they do not map onto embedding space distances in a meaningful way [\textbf{PHRASING}].
+In other words, when participants' correct responses arise primarily from knowledge about the content probed by each question (e.g., after watching one or both lectures), these successes can be predicted from their ability to answer other questions about conceptually similar content (as captured by embedding-space distance).
+However, when a sufficiently large portion of participants' correct responses (presumably) reflect successful random guessing (such as on a multiple-choice quiz taken before viewing either lecture), our approach fails to accurately predict these successes because they are not structured (with respect to spatial distance within the embedding space) in a meaningful way.
 
@@
 but basically negligible.
-Taken together, these results suggest that our approach can distinguish between questions about different content covered by a single lecture when participants have sufficiently structured knowledge about that lecture's content, though this specificity may decrease further in time from when the lecture in question was viewed.
-
-Finally, when we fit GLMMs to estimates of participants' knowledge for questions about one lecture based on questions (from the same quiz) about the other lecture, we observed a similar but slightly more nuanced pattern.
-Essentially, while the previous set of analyses suggest that our approach's ability to make \textit{specific} predictions within content areas depends on participants having a minimum level of knowledge about the given content, the across-lecture analyses we performed suggest that our ability to \textit{generalize} these predictions across different content areas requires that participants' level of knowledge about the content used to make predictions be reasonably similar to their level of knowledge about the content for which these predictions are made [\textbf{PHRASING}].
-We found that using questions answered on Quiz~1, participants abilities to correctly answer questions about \textit{Four Fundamental Forces} could be predicted from their responses to questions about \textit{Birth of Stars} ($OR = 1.896,\ \lambda_{LR} = 7.205,\ 95\%\ \textnormal{CI} = [6.224, 7.524],\ p = 0.039$) and their ability to correctly answer \textit{Birth of Stars}-related questions could be predicted from their responses to \textit{Four Fundamental Forces}-related questions ($OR = 1.522,\ \lambda_{LR} =  6.448,\ 95\%\ \textnormal{CI} = [5.656, 6.843],\ p = 0.043$).
-We note, however, that these Quiz~1 knowledge estimates suffer from the same ``noise'' due to the (presumably) higher rate of participants successfully guessing correct answers on Quiz~1 as noted above, and as a result provide the weakest signal of any of the knowledge estimates that we found to reliably predict success.
+Taken together, these results suggest that our approach can distinguish between questions about different content covered by a single lecture when participants have sufficiently structured knowledge about its contents, though this specificity may decrease further in time from when the lecture in question was viewed.
+
+Finally, when we fit GLMMs to estimates of participants' knowledge for questions about one lecture using questions they answered (on the same quiz) about the \textit{other} lecture, we observed a similar but slightly more nuanced pattern.
+Essentially, while the previous set of within-lecture analyses suggest that the \textit{specificity} of our predictions within a single content area depends on participants having a minimum level of knowledge about that content, these across-lecture analyses suggest that our ability to \textit{generalize} our predictions across different content areas requires that participants' level of knowledge about the content used to make predictions be reasonably similar to their level of knowledge about the content for which these predictions are made.
+Using questions answered on Quiz~1, we found that participants' abilities to correctly answer questions about \textit{Four Fundamental Forces} could be predicted from their responses to questions about \textit{Birth of Stars} ($OR = 1.896,\ \lambda_{LR} = 7.205,\ 95\%\ \textnormal{CI} = [6.224, 7.524],\ p = 0.039$) and similarly, that their ability to correctly answer \textit{Birth of Stars}-related questions could be predicted from their responses to \textit{Four Fundamental Forces}-related questions ($OR = 1.522,\ \lambda_{LR} =  6.448,\ 95\%\ \textnormal{CI} = [5.656, 6.843],\ p = 0.043$).
+We note, however, that these Quiz~1 knowledge estimates are subject to the same increased ``noise'' due to the (presumably) higher incidence of observed correct answers arising from successful random guessing (compared to the other two quizzes) as noted above, and as a result, provide the weakest signal of any of the knowledge estimates that we found reliably predicted success.
 When we repeated this analysis using questions from Quiz~2, we found participants' responses to \textit{Four Fundamental Forces}-related questions did not reliably predict their success on \textit{Birth of Stars}-related questions ($OR = 1.865,\ \lambda_{LR} = 3.205,\ 95\%\ \textnormal{CI} = [3.027, 3.600],\ p = 0.125$), nor did their responses to \textit{Birth of Stars}-related questions reliably predict their success on \textit{Four Fundamental Forces}-related questions ($OR = 3.490,\ \lambda_{LR} = 3.266,\ 95\%\ \textnormal{CI} = [3.033, 3.866],\ p = 0.094$).
@@
 embedding space; when predicting held-out BoS q's, whether or not held-out q was correctly answered isn't meaningfully related to spatial structure of correctly answered q's in embedding space.}
-However, when we again computed these across-lecture knowledge predictions using questions from Quiz~3 (when participants had now viewed \textit{both} lectures, we found that we could again reliably predict success on questions about \textit{Four Fundamental Forces} ($OR = 11.294),\ \lambda_{LR} = 11.055,\ 95\%\ \textnormal{CI} = [9.126, 18.476],\ p = 0.004$) and \textit{Birth of Stars} ($OR = 7.302),\ \lambda_{LR} = 7.068,\ 95\%\ \textnormal{CI} = [6.490, 8.584],\ p = 0.017$).
-Across all three versions of these analyses, our results suggest that our knowledge estimations can reliably predict participants' abilities to answer individual quiz questions, distinguish between questions about similar content, and generalize across content areas, provided that participants' quiz responses reflect a minimum level of ``real'' knowledge about both content on which these predictions are based and that for which they are made [\textbf{PHRASING}].
+However, when we again computed these across-lecture knowledge predictions using questions from Quiz~3 (when participants had now viewed \textit{both} lectures, we found that we could again reliably predict success on questions about both \textit{Four Fundamental Forces} ($OR = 11.294),\ \lambda_{LR} = 11.055,\ 95\%\ \textnormal{CI} = [9.126, 18.476],\ p = 0.004$) and \textit{Birth of Stars} ($OR = 7.302,\ \lambda_{LR} = 7.068,\ 95\%\ \textnormal{CI} = [6.490, 8.584],\ p = 0.017$) using responses to questions questions about the other lecture's content.
+Across all three versions of these analyses, our results suggest that our knowledge estimations can reliably predict participants' abilities to answer individual quiz questions, distinguish between questions about similar content, and generalize across content areas, provided that participants' quiz responses reflect a minimum level of ``real'' knowledge about both content on which these predictions are based and that for which they are made.
 

### 2024-02-19 paper/compile.sh
reworking results section text related to fig 6

@@ -14,5 +14,13 @@ latex -interaction=nonstopmode supplement
 latex -interaction=nonstopmode supplement
 pdflatex -interaction=nonstopmode supplement
 
+latexdiff old.tex main.tex > changes.tex
+latex -interaction=nonstopmode changes
+bibtex changes
+latex -interaction=nonstopmode changes
+latex -interaction=nonstopmode changes
+pdflatex -interaction=nonstopmode changes
+
+
 rm *.cb* *.dvi *.log *.blg *.aux *.fff *.out
 

### 2024-02-19 paper/main.tex

@@
 carry some predictive information about whether they are likely to answer that
-question correctly or incorrectly. We developed a statistical approach to test this claim. 
-For each quiz question a participant answered, in turn, we used Equation~\ref{eqn:prop} to estimate their knowledge at the given question's embedding space coordinate based on other questions that participant answered on the same quiz.
-We repeated this for all participants, and for each of the three quizzes. 
-Then, separately for each quiz, we fit a generalized linear mixed model (GLMM) with a logistic link function to explain the likelihood of correctly answering a question as a function of estimated knowledge for its embedding coordinate, while accounting for random variation among participants and questions (see \nameref{subsec:glmm}).
-To assess the predictive value of the knowledge estimates, we compared each GLMMs to an analogous (i.e., nested) ``null'' model that did not consider estimated knowledge using parametric bootstrap likelihood-ratio tests.
+question correctly or incorrectly. We developed a statistical approach to test
+this claim. For each quiz question a participant answered, in turn, we used
+Equation~\ref{eqn:prop} to estimate their knowledge at the given question's
+embedding space coordinate based on other questions that participant answered
+on the same quiz. We repeated this for all participants, and for each of the
+three quizzes. Then, separately for each quiz, we fit a generalized linear
+mixed model (GLMM) with a logistic link function to explain the likelihood of
+correctly answering a question as a function of estimated knowledge for its
+embedding coordinate, while accounting for random variation among participants
+and questions (see \nameref{subsec:glmm}). To assess the predictive value of
+the knowledge estimates, we compared each GLMMs to an analogous (i.e., nested)
+``null'' model that did not consider estimated knowledge using parametric
+bootstrap likelihood-ratio tests.
 
@@
     \centering
+
     % TODO: adjust width to max possible based on finalized caption
-    \includegraphics[width=0.7\textwidth]{figs/predict-knowledge-questions}
-    \caption{\textbf{Predicting success on held-out questions using estimated knowledge.}
-    We used generalized linear mixed models (GLMMs) to model the likelihood of correctly answering a quiz question as a function of estimated knowledge for its embedding coordinate (see \nameref{subsec:glmm}).
-    Separately for each quiz (column), we examined this relationship based on three different sets of knowledge estimates: knowledge for each question based on all other questions the same participant answered on the same quiz (``All questions''; top row), knowledge for each question about one lecture based on all questions (from the same participant and quiz) about the \textit{other} lecture (``Across-lecture''; middle rows), and knowledge for each question about one lecture based on all other questions (from the same participant and quiz) about the \textit{same} lecture (``Within-lecture''; bottom rows).
-    The background in each panel displays the relative density of observed correctly (blue) versus incorrectly (red) answered questions over the range of knowledge estimates. 
-    The black curves display the (population-level) GLMM-predicted probabilities of correctly answering a question as a function of estimated knowledge. 
-    Error ribbons denote 95\% confidence intervals.}
+    \includegraphics[width=0.75\textwidth]{figs/predict-knowledge-questions}
+    \caption{\textbf{Predicting success on held-out questions using estimated
+    knowledge.} We used generalized linear mixed models (GLMMs) to model the
+    likelihood of correctly answering a quiz question as a function of
+    estimated knowledge for its embedding coordinate (see
+    \nameref{subsec:glmm}). Separately for each quiz (column), we examined this
+    relationship based on three different sets of knowledge estimates:
+    knowledge for each question based on all other questions the same
+    participant answered on the same quiz (``All questions''; top row),
+    knowledge for each question about one lecture based on all questions (from
+    the same participant and quiz) about the \textit{other} lecture
+    (``Across-lecture''; middle rows), and knowledge for each question about
+    one lecture based on all other questions (from the same participant and
+    quiz) about the \textit{same} lecture (``Within-lecture''; bottom rows).
+    The background in each panel displays the kernel density estimates of the
+    relative observed proportions of correctly (blue) versus incorrectly (red)
+    answered questions, for each level of estimated knowledge along the
+    $x$-axis. The black curves display the (population-level) GLMM-predicted
+    probabilities of correctly answering a question as a function of estimated
+    knowledge. Error ribbons denote bootstrap-estimated 95\% confidence
+    intervals. \textbf{JRM NOTE: RE-ORDER ROWS TO MATCH THE TEXT, AND UPDATE
+    CAPTION ACCORDINGLY}}
 
@@
 
-We carried out three different versions of the analyses described above, wherein we considered different sources of information in our estimates of participants' knowledge for each quiz question. 
-First, we estimated knowledge at each question's embedding coordinate using \textit{all other} questions answered by the same participant on the same quiz (``All questions''; Fig.~\ref{fig:predictions}, top row).
-This test was intended to assess the overall predictive power of our approach. 
-Second, we estimated knowledge for each question about a given lecture using only the other questions (from the same participant and quiz) about that \textit{same} lecture (``Within-lecture''; Fig.~\ref{fig:predictions}, middle rows).
-This test was intended to assess the \textit{specificity} of our approach by asking whether our predictions could distinguish between questions about different content covered by the same lecture.
-Third, we estimated knowledge for each question about one lecture using only questions (from the same participant and quiz) about the \textit{other} lecture (``Across-lecture''; Fig.~\ref{fig:predictions}, bottom rows).
-This test was intended to assess the \textit{generalizability} of our approach by asking whether our predictions held across the content areas of the two lectures.
-
-In performing this set of analyses, our null hypothesis is that the knowledge estimates we compute based on the quiz questions' embedding coordinates do \textit{not} provide useful information about participants' abilities to answer those questions.
-What result might we expect to see if this is the case? 
-To provide an intuition for this, consider the expected outcome if we carried out these same analyses using a simple proportion-correct measure in lieu of our knowledge estimates. 
-Suppose a participant correctly answered $n$ out of 13 questions on a given quiz. 
-If we held out a single correctly answered question and computed the proportion of remaining questions answered correctly, that proportion would be $(n - 1) / 12$. 
-Whereas if we held out a single \textit{incorrectly} answered question and did the same, that proportion would be $n / 12$. 
-Thus for a given participant and quiz, a ``knowledge estimate'' computed as the simple (i.e., unweighted) remaining proportion-correct is perfectly inversely related to success on a held-out question: it will always be \textit{lower} for correctly answered questions than for incorrectly answered questions.
-Given that our knowledge estimates are computed as a weighted version of this same proportion-correct score (where each held-in question's weight reflects its embedding-space distance from the held-out question; see Eqn.~\ref{eqn:prop}), if these weights are uninformative (e.g., simply randomly distributed), then we should expect to see this same inverse relationship emerge, on average.
-It is only if the spatial relationships among the quiz questions' embedding coordinates map onto participants' knowledge in a meaningful way that we would we expect this relationship to be non-negative.
-
-When we fit a GLMM to estimates of participants' knowledge for each Quiz~1 question based on all other Quiz~1 questions, we observed this null-hypothesized inverse relationship. 
-Specifically, higher estimated knowledge at the embedding coordinate of a held-out Quiz~1 question was associated with a lower likelihood of answering the question correctly (odds ratio $(OR) = 0.136$, likelihood-ratio test statistic $(\lambda_{LR}) = 19.749$, 95\%\ $\textnormal{CI} = [14.352,\ 26.545],\ p = 0.001$).
-However, when we repeated this analysis for quizzes 2 and 3, the direction of this relationship reversed: higher estimated knowledge for a given question predicted a greater likelihood of answering it correctly (Quiz~2: $OR = 2.905,\ \lambda_{LR} = 17.333,\ 95\%\ \textnormal{CI} = [14.966,\ 29.309],\ p = 0.002$; Quiz~3: $OR = 3.238,\ \lambda_{LR} = 6.882,\ 95\%\ \textnormal{CI} = [6.228,\ 8.184],\ p = 0.017$).
-Taken together, these results suggest that our knowledge estimations can reliably predict participants' likelihood of success on individual quiz questions, provided they have at least some amount of structured knowledge about the underlying concepts being tested.
-In other words, when participants' correct responses arise primarily from knowledge about the content probed by each question (e.g., after watching one or both lectures), these successes can be predicted from their ability to answer other questions about conceptually similar content (as captured by embedding-space distance).
-However, when a sufficiently large portion of participants' correct responses (presumably) reflect successful random guessing (such as on a multiple-choice quiz taken before viewing either lecture), our approach fails to accurately predict these successes because they are not structured (with respect to spatial distance within the embedding space) in a meaningful way.
-
-We observed a similar pattern when we fit GLMMs to estimates of participants' knowledge for each question about one lecture derived from other questions about the \textit{same} lecture. 
-Specifically, for questions that participants answered on Quiz~1, prior to watching either lecture, knowledge for the embedding coordinates of \textit{Four Fundamental Forces}-related questions estimated using other \textit{Four Fundamental Forces}-related questions did not reliably predict whether those questions were answered correctly ($OR = 1.891,\ \lambda_{LR} = 2.293,\ 95\%\ \textnormal{CI} = [2.091,\ 2.622],\ p = 0.139$).
-The same was true of knowledge estimates for \textit{Birth of Stars}-related questions based on other \textit{Birth of Stars}-related questions ($OR = 0.722,\ \lambda_{LR} = 5.115,\ 95\%\ \textnormal{CI} = [0.094,\ 0.146],\ p = 0.738$).
-When we recomputed these within-lecture knowledge estimates using questions from Quiz~2---which participants took immediately after viewing \textit{Four Fundamental Forces} but prior to viewing \textit{Birth of Stars}---we found that they now reliably predicted success on \textit{Four Fundamental Forces}-related questions ($OR = 9.023,\ \lambda_{LR} = 18.707,\ 95\%\ \textnormal{CI} = [10.877,\ 22.222],\ p = 0.001$) but not on \textit{Birth of Stars}-related questions ($OR = 0.306,\ \lambda_{LR} = 5.115,\ 95\%\ \textnormal{CI} = [4.624,\ 5.655],\ p = 0.055$).
-Using participants' responses from Quiz~3 (taken immediately after viewing \textit{Birth of Stars}), we found that within-lecture knowledge estimates for \textit{Birth of Stars}-related questions could now reliably predict success on those questions ($OR = 5.467,\ \lambda_{LR} = 10.670,\ 95\%\ \textnormal{CI} = [7.998, 12.532],\ p = 0.006$).
-However, within-lecture knowledge estimates for \textit{Four Fundamental Forces} questions answered on Quiz~3 were no longer directly related to the likelihood of successfully answering them and instead exhibited the inverse relationship we would expect to arise from unstructured knowledge (with respect to the embedding space; $OR = 0.013,\ \lambda_{LR} = 14.648,\ 95\%\ \textnormal{CI} = [10.695, 23.096],\ p = 0.001$).
-Speculatively, we suggest that this may reflect participants forgetting some of the \textit{Four Fundamental Forces} content (e.g., perhaps in favor of prioritizing encoding the just-watched \textit{Birth of Stars} content in preparation for the third quiz).
-If this forgetting happens in a relatively ``random'' way (with respect to spatial distance within the embedding space), then it could explain why some held-out questions about \textit{Four Fundamental Forces} were answered incorrectly, even if questions at nearby coordinates (i.e., about similar content) were answered correctly.
-This might lead our approach to over-estimate knowledge for held-out questions about ``forgotten'' knowledge that participants answered incorrectly.
-% ALTERNATE EXPLANATION -- embedding space is essentially ``saturated'' with correctly answered questions, so just like how on quiz 1 when relatively few questions are correct, most questions ``around'' them will be incorrect, on quiz 3 when relatively few questions are incorrect, most questions nearby will be correct.
-And because of this, on average, when the ``held-out'' question is one of the few incorrect ones, there will tend to be more correct ones ``held in'' than there will be when the held-out question is correct.
-% Also, maybe worth noting: while negative relationship is significant, it's super weak -- per the model, a "1-unit" increase in estimated knowledge corresponds to only a 1.28% decrease in probability of correct answer (p = OR / (1 + OR)).
-For comparison, for quiz3/within-lecture/birth of stars, 1-unit increase in estimated knowledge corresponds to a 84.5% increase in probability.
-So decrease is sig.
-but basically negligible.
-Taken together, these results suggest that our approach can distinguish between questions about different content covered by a single lecture when participants have sufficiently structured knowledge about its contents, though this specificity may decrease further in time from when the lecture in question was viewed.
-
-Finally, when we fit GLMMs to estimates of participants' knowledge for questions about one lecture using questions they answered (on the same quiz) about the \textit{other} lecture, we observed a similar but slightly more nuanced pattern.
-Essentially, while the previous set of within-lecture analyses suggest that the \textit{specificity} of our predictions within a single content area depends on participants having a minimum level of knowledge about that content, these across-lecture analyses suggest that our ability to \textit{generalize} our predictions across different content areas requires that participants' level of knowledge about the content used to make predictions be reasonably similar to their level of knowledge about the content for which these predictions are made.
-Using questions answered on Quiz~1, we found that participants' abilities to correctly answer questions about \textit{Four Fundamental Forces} could be predicted from their responses to questions about \textit{Birth of Stars} ($OR = 1.896,\ \lambda_{LR} = 7.205,\ 95\%\ \textnormal{CI} = [6.224, 7.524],\ p = 0.039$) and similarly, that their ability to correctly answer \textit{Birth of Stars}-related questions could be predicted from their responses to \textit{Four Fundamental Forces}-related questions ($OR = 1.522,\ \lambda_{LR} =  6.448,\ 95\%\ \textnormal{CI} = [5.656, 6.843],\ p = 0.043$).
-We note, however, that these Quiz~1 knowledge estimates are subject to the same increased ``noise'' due to the (presumably) higher incidence of observed correct answers arising from successful random guessing (compared to the other two quizzes) as noted above, and as a result, provide the weakest signal of any of the knowledge estimates that we found reliably predicted success.
-When we repeated this analysis using questions from Quiz~2, we found participants' responses to \textit{Four Fundamental Forces}-related questions did not reliably predict their success on \textit{Birth of Stars}-related questions ($OR = 1.865,\ \lambda_{LR} = 3.205,\ 95\%\ \textnormal{CI} = [3.027, 3.600],\ p = 0.125$), nor did their responses to \textit{Birth of Stars}-related questions reliably predict their success on \textit{Four Fundamental Forces}-related questions ($OR = 3.490,\ \lambda_{LR} = 3.266,\ 95\%\ \textnormal{CI} = [3.033, 3.866],\ p = 0.094$).
-\textbf{Sentence about why this makes sense given that participants hadn't viewed BoS yet.
-i.e., when predicting held-out FFF questions, correct vs.
-incorrect labels for held-in q's aren't meaningfully structured w.r.t.
-embedding space; when predicting held-out BoS q's, whether or not held-out q was correctly answered isn't meaningfully related to spatial structure of correctly answered q's in embedding space.}
-However, when we again computed these across-lecture knowledge predictions using questions from Quiz~3 (when participants had now viewed \textit{both} lectures, we found that we could again reliably predict success on questions about both \textit{Four Fundamental Forces} ($OR = 11.294),\ \lambda_{LR} = 11.055,\ 95\%\ \textnormal{CI} = [9.126, 18.476],\ p = 0.004$) and \textit{Birth of Stars} ($OR = 7.302,\ \lambda_{LR} = 7.068,\ 95\%\ \textnormal{CI} = [6.490, 8.584],\ p = 0.017$) using responses to questions questions about the other lecture's content.
-Across all three versions of these analyses, our results suggest that our knowledge estimations can reliably predict participants' abilities to answer individual quiz questions, distinguish between questions about similar content, and generalize across content areas, provided that participants' quiz responses reflect a minimum level of ``real'' knowledge about both content on which these predictions are based and that for which they are made.
+We carried out three different versions of the analyses described above,
+wherein we considered different sources of information in our estimates of
+participants' knowledge for each quiz question. First, we estimated knowledge
+at each question's embedding coordinate using \textit{all} other questions
+answered by the same participant on the same quiz (``All questions'';
+Fig.~\ref{fig:predictions}, top row). This test was intended to assess the
+overall predictive power of our approach. Second, we estimated knowledge for
+each question about a given lecture using only the other questions (from the
+same participant and quiz) about that \textit{same} lecture
+(``Within-lecture''; Fig.~\ref{fig:predictions}, middle rows). This test was
+intended to assess the \textit{specificity} of our approach by asking whether
+our predictions could distinguish between questions about different content
+covered by the same lecture. Third, we estimated knowledge for each question
+about one lecture using only questions (from the same participant and quiz)
+about the \textit{other} lecture (``Across-lecture'';
+Fig.~\ref{fig:predictions}, bottom rows). This test was intended to assess the
+\textit{generalizability} of our approach by asking whether our predictions
+held across the content areas of the two lectures.
+
+In performing these analyses, our null hypothesis is that the knowledge
+estimates we compute based on the quiz questions' embedding coordinates do
+\textit{not} provide useful information about participants' abilities to answer
+those questions. What result might we expect to see if this is the case? To
+gain an intuition for this possibility, consider the expected outcome if we
+carried out these same analyses using a simple proportion-correct measure in
+lieu of our knowledge estimates. Suppose a participant correctly answered $n$
+out of $q$ questions on a given quiz. If we hold out a single
+\textit{correctly} answered question, the proportion of remaining questions
+answered correctly would be $\frac{n - 1}{q - 1}$. If we hold out a single
+\textit{incorrectly} answered question, the proportion of remaining questions
+answered correctly would be $\frac{n}{q - 1}$. In this way, the proportion of
+correctly answered remaining questions is always \textit{lower} when the
+held-out question was answered correctly than when it was answered incorrectly.
+Because our knowledge estimates are computed as a weighted version of this same
+proportion-correct score (where each held-in question's weight reflects its
+embedding-space distance from the held-out question; see Eqn.~\ref{eqn:prop}),
+if these weights were uninformative (e.g., randomly distributed), then we
+should expect to see this same inverse relationship between estimated knowledge
+and performance, on average. On the other hand, if the spatial relationships
+among the quiz questions' embeddings \textit{are} predictive of participants'
+knowledge about the questions' content, then we would expect \textit{higher}
+estimated knowledge for held-out correctly (versus incorrectly) answered
+questions.
+
+When we fit a GLMM to estimates of participants' knowledge for each Quiz~1
+question based on all other Quiz~1 questions, we observed an outcome consistent
+with our null hypothesis: higher estimated knowledge at the embedding
+coordinate of a held-out question was associated with a lower likelihood of
+answering the question correctly (odds ratio $(OR) = 0.136$, likelihood-ratio
+test statistic $(\lambda_{LR}) = 19.749$, 95\%\ $\textnormal{CI} = [14.352,\
+26.545],\ p = 0.001$). This outcome suggests that our knowledge estimates do
+\textit{not} provide useful information about participants' Quiz~1 performance
+when we aggregated across all question content areas. We speculated that this
+might either indicate that the knowledge estimates are uninformative in
+general, or about Quiz~1 performance in particular. When we repeated this
+analysis for Quizzes~2 and~3, the direction of this relationship reversed:
+higher estimated knowledge for a given question predicted a greater likelihood
+of answering it correctly (Quiz~2: $OR = 2.905,\ \lambda_{LR} = 17.333,\ 95\%\
+\textnormal{CI} = [14.966,\ 29.309],\ p = 0.002$; Quiz~3: $OR = 3.238,\
+\lambda_{LR} = 6.882,\ 95\%\ \textnormal{CI} = [6.228,\ 8.184],\ p = 0.017$).
+Taken together, these results suggest that our knowledge estimates \textit{do}
+reliably predict participants' likelihood of success on individual quiz
+questions, but only when there is some ``contrast'' in performance between the
+content of different questions. On Quiz~1, before participants have learned the
+content of either lecture, their overall performance is poor (average
+proportion correct: $0.46$), and the specific questions they answer correctly
+not not seem to be structured in a meaningful way with respect to the embedding
+space (e.g., Fig.~\ref{fig:knowledge-maps}A, left panel). On Quizzes~2 and~3,
+after participants have begun their training, their overall performance
+improves (average proportion correct for Quiz~2: 0.60; average proportion
+correct for Quiz~3: 0.79), and the specific content areas they improve on are
+captured by the lecture and question embeddings (and, therefore, our knowledge
+estimates).
+
+We observed a similar pattern of results when we fit GLMMs to estimates of
+participants' knowledge for each question about one lecture derived from other
+questions about the \textit{same} lecture. Specifically, for questions that
+participants answered on Quiz~1, prior to watching either lecture, knowledge
+for the embedding coordinates of \textit{Four Fundamental Forces}-related
+questions estimated using other \textit{Four Fundamental Forces}-related
+questions did not reliably predict whether those questions were answered
+correctly ($OR = 1.891,\ \lambda_{LR} = 2.293,\ 95\%\ \textnormal{CI} =
+[2.091,\ 2.622],\ p = 0.139$). The same was true of knowledge estimates for
+\textit{Birth of Stars}-related questions based on other \textit{Birth of
+Stars}-related questions ($OR = 0.722,\ \lambda_{LR} = 5.115,\ 95\%\
+\textnormal{CI} = [0.094,\ 0.146],\ p = 0.738$). When we recomputed these
+within-lecture knowledge estimates using questions from Quiz~2---which
+participants took immediately after viewing \textit{Four Fundamental Forces}
+but prior to viewing \textit{Birth of Stars}---we found that they now reliably
+predicted success on \textit{Four Fundamental Forces}-related questions ($OR =
+9.023,\ \lambda_{LR} = 18.707,\ 95\%\ \textnormal{CI} = [10.877,\ 22.222],\ p =
+0.001$) but not on \textit{Birth of Stars}-related questions ($OR = 0.306,\
+\lambda_{LR} = 5.115,\ 95\%\ \textnormal{CI} = [4.624,\ 5.655],\ p = 0.055$).
+Using participants' responses from Quiz~3 (taken immediately after viewing
+\textit{Birth of Stars}), we found that within-lecture knowledge estimates for
+\textit{Birth of Stars}-related questions could now reliably predict success on
+those questions ($OR = 5.467,\ \lambda_{LR} = 10.670,\ 95\%\ \textnormal{CI} =
+[7.998, 12.532],\ p = 0.006$). In contrast, within-lecture knowledge estimates
+for \textit{Four Fundamental Forces} questions answered on Quiz~3 were no
+longer directly related to the likelihood of successfully answering them and
+instead exhibited the inverse relationship we would expect to arise from
+unstructured knowledge (with respect to the embedding space; $OR = 0.013,\
+\lambda_{LR} = 14.648,\ 95\%\ \textnormal{CI} = [10.695, 23.096],\ p = 0.001$).
+In principle, this ``prediction failure'' might arise from several possible
+scenarios. One possibility is that the participants are answering nearly all of
+the questions about \textit{Four Fundamental Forces} correctly on Quiz~3, and
+(as with the Quiz~1 questions) there might be insufficient contrast in
+performance across different questions to reliably estimate participants'
+knowledge. However, when we examined participants' performance on Quiz~3
+questions about \textit{Four Fundamental Forces}, we found that they answered
+these questions correctly only 76\% of the time, on average (i.e., unlikely to
+reflect a ``ceiling'' effect). Alternatively, we speculated that participants
+might be forgetting some of the material from the \textit{Four Fundamental
+Forces} lecture, and that this forgetting might be happening in a relatively
+``random'' way with respect to spatial distance within the embedding space.
+This might lead our approach to over-estimate knowledge for held-out questions
+about ``forgotten'' knowledge that participants answered incorrectly. Indeed,
+participants' performance on \textit{Four Fundamental Forces}-related questions
+was slightly (thought not dramatically) lower on Quiz~3 than on Quiz~2 (mean
+proportion correct on Quiz~2: $0.77$). Taken together, these results suggest
+that our approach can distinguish between questions about different content
+covered by a single lecture when participants have sufficiently structured
+knowledge about its contents, though this specificity may decrease further in
+time from when the lecture in question was viewed.
+
+Finally, when we fit GLMMs to estimates of participants' knowledge for
+questions about one lecture using questions they answered (on the same quiz)
+about the \textit{other} lecture, we also observed a (largely) similar pattern.
+On Quiz~1, we found that participants' abilities to correctly answer questions
+about \textit{Four Fundamental Forces} could be predicted from their responses
+to questions about \textit{Birth of Stars} ($OR = 1.896,\ \lambda_{LR} =
+7.205,\ 95\%\ \textnormal{CI} = [6.224, 7.524],\ p = 0.039$) and similarly,
+that their ability to correctly answer \textit{Birth of Stars}-related
+questions could be predicted from their responses to \textit{Four Fundamental
+Forces}-related questions ($OR = 1.522,\ \lambda_{LR} = 6.448,\ 95\%\
+\textnormal{CI} = [5.656, 6.843],\ p = 0.043$). This reflects coarse-scale
+structure in participants' knowledge prior to any training in our experiment.
+When we repeated this analysis using questions from Quiz~2, we found
+participants' responses to \textit{Four Fundamental Forces}-related questions
+did \textit{not} reliably predict their success on \textit{Birth of
+Stars}-related questions ($OR = 1.865,\ \lambda_{LR} = 3.205,\ 95\%\
+\textnormal{CI} = [3.027, 3.600],\ p = 0.125$), nor did their responses to
+\textit{Birth of Stars}-related questions reliably predict their success on
+\textit{Four Fundamental Forces}-related questions ($OR = 3.490,\ \lambda_{LR}
+= 3.266,\ 95\%\ \textnormal{CI} = [3.033, 3.866],\ p = 0.094$). These
+``prediction failures'' appear to come from the fact that any signal derived
+from participants' knowledge about the content of the \textit{Birth of Stars}
+lecture (prior to watching it) is swamped by the much more dramatic increase in
+their knowledge about the content of the \textit{Four Fundamental Forces}
+(which they watched just prior to taking Quiz~2). This is reflected in their
+Quiz~2 performance for questions about each lecture (mean proportion correct
+for \textit{Four Fundamental Forces}-related questions on Quiz~2: $0.77$; mean
+proportion correct for \textit{Birth of Stars}-related questions on Quiz~2:
+$0.36$). When we again carried out these across-lecture knowledge predictions
+using questions from Quiz~3 (when participants had now viewed \textit{both}
+lectures), we could again reliably predict success on questions about both
+\textit{Four Fundamental Forces} ($OR = 11.294),\ \lambda_{LR} = 11.055,\ 95\%\
+\textnormal{CI} = [9.126, 18.476],\ p = 0.004$) and \textit{Birth of Stars}
+($OR = 7.302,\ \lambda_{LR} = 7.068,\ 95\%\ \textnormal{CI} = [6.490, 8.584],\
+p = 0.017$) using responses to questions questions about the other lecture's
+content. Across all three versions of these analyses, our results suggest that
+(by and large) our knowledge estimations can reliably predict participants'
+abilities to answer individual quiz questions, distinguish between questions
+about similar content, and generalize across content areas, provided that
+participants' quiz responses reflect a minimum level of ``real'' knowledge
+about both content on which these predictions are based and that for which they
+are made. Our results also indicate some potential limitations of our approach:
+when the contrast in participants' knowledge within the embedding space is low
+overall, our approach (often) cannot reliably predict their abilities to answer
+individual quiz questions.
 

### 2024-02-19 paper/main.tex
checking in changes to merge upstream

--- 2024-02-19 paper/main.tex
@@
 \documentclass[10pt]{article}
+\usepackage{amsmath}
 \usepackage[utf8]{inputenc}
@@
 \usepackage{xcolor}
+
+\setcitestyle{notesep={; }}
 
@@
 preprocessing) as the sliding windows we defined in our prior
-work~\citep{HeusEtal21} (i.e., 185 words per sliding window).
+work~\citep[][i.e., 185 words per sliding window]{HeusEtal21}.
 
@@
 \subsubsection*{GLMM METHODS SECTION PLACEHOLDER}\label{subsec:glmm}
+
+In the set of analyses reported in Figure~\ref{fig:predictions}, we applied Equation~\ref{eqn:prop} to
+
+estimate participants' knowledge for individual held-out quiz questions (i.e., treating
+
+In the set of analyses reported in Figure~\ref{fig:predictions}, we applied Equation~\ref{eqn:prop} to estimate participants' knowledge at the embedding coordinates of individual held-out quiz questions.
+For each of the three quizzes a participant took,
+
+Equation~\ref{eqn:prop} to estimate participants' knowledge at the embedding coordinate of individual held-out questions, based on other questions
+
+all other questions (``All questions''; Fig.~\ref{fig:predictions}, top row),
+
+(``All questions''; Fig.~\ref{fig:predictions}, top row).
+This test was intended to assess the overall predictive power of our approach. 
+Second, we estimated knowledge for each question about a given lecture using only the other questions (from the same participant and quiz) about that \textit{same} lecture (``Within-lecture''; Fig.~\ref{fig:predictions}, middle rows).
+This test was intended to assess the \textit{specificity} of our approach by asking whether our predictions could distinguish between questions about different content covered by the same lecture.
+Third, we estimated knowledge for each question about one lecture using only questions (from the same participant and quiz) about the \textit{other} lecture (``Across-lecture''; Fig.~\ref{fig:predictions}, bottom rows).
+
+To analyze the predictive value of
+
+To predict individual participants' success on held-out quiz questions, we used Equation~\ref{eqn:prop}
+
+$$
+    \mathtt{accuracy \sim knowledge + (knowledge\ \vert\ participant) + (knowledge\ \vert\ question)}
+$$
+
+%\begin{lstlisting}[language=R]
+%    accuracy \sim knowledge + (knowledge|participant) + (knowledge|question)
+%\end{lstlisting}
+
+note that qID is implicitly nested within levels of lecture
 

### 2024-02-20 paper/main.tex
another revamp of results related to fig. 6 following JRM/PCF discussion

--- 2024-02-19 paper/main.tex
@@
 
+Before presenting our results, it is worth considering three possible
+explanations of why a participant might answer a given question correctly or
+incorrectly. One possibility is that the participant simply \textit{guessed}
+the answer. A second is that they selected an answer by mistake, despite
+``knowing'' the correct answer. In both of these scenarios, the participant's
+knowledge about the question's content should be uninformative about their
+observed response. A third possibility is that the participant's response
+reflects their \textit{actual} knowledge about the question's content. In this
+case, we \textit{might} expect to see a positive relationship between the
+participant's knowledge and their likelihood of answering the question
+correctly. However, in order to see this positive relationship, the
+participant's knowledge must be structured in a way that is reflected (at least
+partially) by the embedding space. In other words, if the participant's
+performance reflects their true kwowledge, but our text embedding space does
+not sufficiently capture the structure of that knowledge, then the knowledge
+estimates we generate will not be predictive of the participant's performance.
+In the extreme, if the embedding space is completely unstructured with respect
+to the content of the quiz questions, then we would expect to see the negative
+relationship between estimated knowledge and performance that we described
+above.
+
 When we fit a GLMM to estimates of participants' knowledge for each Quiz~1
@@
 might either indicate that the knowledge estimates are uninformative in
-general, or about Quiz~1 performance in particular. When we repeated this
-analysis for Quizzes~2 and~3, the direction of this relationship reversed:
-higher estimated knowledge for a given question predicted a greater likelihood
-of answering it correctly (Quiz~2: $OR = 2.905,\ \lambda_{LR} = 17.333,\ 95\%\
-\textnormal{CI} = [14.966,\ 29.309],\ p = 0.002$; Quiz~3: $OR = 3.238,\
-\lambda_{LR} = 6.882,\ 95\%\ \textnormal{CI} = [6.228,\ 8.184],\ p = 0.017$).
-Taken together, these results suggest that our knowledge estimates \textit{do}
-reliably predict participants' likelihood of success on individual quiz
-questions, but only when there is some ``contrast'' in performance between the
-content of different questions. On Quiz~1, before participants have learned the
-content of either lecture, their overall performance is poor (average
-proportion correct: $0.46$), and the specific questions they answer correctly
-not not seem to be structured in a meaningful way with respect to the embedding
-space (e.g., Fig.~\ref{fig:knowledge-maps}A, left panel). On Quizzes~2 and~3,
-after participants have begun their training, their overall performance
-improves (average proportion correct for Quiz~2: 0.60; average proportion
-correct for Quiz~3: 0.79), and the specific content areas they improve on are
-captured by the lecture and question embeddings (and, therefore, our knowledge
-estimates).
-
-We observed a similar pattern of results when we fit GLMMs to estimates of
-participants' knowledge for each question about one lecture derived from other
-questions about the \textit{same} lecture. Specifically, for questions that
-participants answered on Quiz~1, prior to watching either lecture, knowledge
-for the embedding coordinates of \textit{Four Fundamental Forces}-related
-questions estimated using other \textit{Four Fundamental Forces}-related
-questions did not reliably predict whether those questions were answered
-correctly ($OR = 1.891,\ \lambda_{LR} = 2.293,\ 95\%\ \textnormal{CI} =
-[2.091,\ 2.622],\ p = 0.139$). The same was true of knowledge estimates for
-\textit{Birth of Stars}-related questions based on other \textit{Birth of
-Stars}-related questions ($OR = 0.722,\ \lambda_{LR} = 5.115,\ 95\%\
-\textnormal{CI} = [0.094,\ 0.146],\ p = 0.738$). When we recomputed these
-within-lecture knowledge estimates using questions from Quiz~2---which
-participants took immediately after viewing \textit{Four Fundamental Forces}
-but prior to viewing \textit{Birth of Stars}---we found that they now reliably
-predicted success on \textit{Four Fundamental Forces}-related questions ($OR =
-9.023,\ \lambda_{LR} = 18.707,\ 95\%\ \textnormal{CI} = [10.877,\ 22.222],\ p =
-0.001$) but not on \textit{Birth of Stars}-related questions ($OR = 0.306,\
-\lambda_{LR} = 5.115,\ 95\%\ \textnormal{CI} = [4.624,\ 5.655],\ p = 0.055$).
-Using participants' responses from Quiz~3 (taken immediately after viewing
-\textit{Birth of Stars}), we found that within-lecture knowledge estimates for
-\textit{Birth of Stars}-related questions could now reliably predict success on
-those questions ($OR = 5.467,\ \lambda_{LR} = 10.670,\ 95\%\ \textnormal{CI} =
-[7.998, 12.532],\ p = 0.006$). In contrast, within-lecture knowledge estimates
-for \textit{Four Fundamental Forces} questions answered on Quiz~3 were no
-longer directly related to the likelihood of successfully answering them and
-instead exhibited the inverse relationship we would expect to arise from
-unstructured knowledge (with respect to the embedding space; $OR = 0.013,\
-\lambda_{LR} = 14.648,\ 95\%\ \textnormal{CI} = [10.695, 23.096],\ p = 0.001$).
-In principle, this ``prediction failure'' might arise from several possible
-scenarios. One possibility is that the participants are answering nearly all of
-the questions about \textit{Four Fundamental Forces} correctly on Quiz~3, and
-(as with the Quiz~1 questions) there might be insufficient contrast in
-performance across different questions to reliably estimate participants'
-knowledge. However, when we examined participants' performance on Quiz~3
-questions about \textit{Four Fundamental Forces}, we found that they answered
-these questions correctly only 76\% of the time, on average (i.e., unlikely to
-reflect a ``ceiling'' effect). Alternatively, we speculated that participants
-might be forgetting some of the material from the \textit{Four Fundamental
-Forces} lecture, and that this forgetting might be happening in a relatively
-``random'' way with respect to spatial distance within the embedding space.
-This might lead our approach to over-estimate knowledge for held-out questions
-about ``forgotten'' knowledge that participants answered incorrectly. Indeed,
-participants' performance on \textit{Four Fundamental Forces}-related questions
-was slightly (thought not dramatically) lower on Quiz~3 than on Quiz~2 (mean
-proportion correct on Quiz~2: $0.77$). Taken together, these results suggest
-that our approach can distinguish between questions about different content
-covered by a single lecture when participants have sufficiently structured
-knowledge about its contents, though this specificity may decrease further in
-time from when the lecture in question was viewed.
-
-Finally, when we fit GLMMs to estimates of participants' knowledge for
-questions about one lecture using questions they answered (on the same quiz)
-about the \textit{other} lecture, we also observed a (largely) similar pattern.
-On Quiz~1, we found that participants' abilities to correctly answer questions
-about \textit{Four Fundamental Forces} could be predicted from their responses
-to questions about \textit{Birth of Stars} ($OR = 1.896,\ \lambda_{LR} =
-7.205,\ 95\%\ \textnormal{CI} = [6.224, 7.524],\ p = 0.039$) and similarly,
-that their ability to correctly answer \textit{Birth of Stars}-related
-questions could be predicted from their responses to \textit{Four Fundamental
-Forces}-related questions ($OR = 1.522,\ \lambda_{LR} = 6.448,\ 95\%\
-\textnormal{CI} = [5.656, 6.843],\ p = 0.043$). This reflects coarse-scale
-structure in participants' knowledge prior to any training in our experiment.
-When we repeated this analysis using questions from Quiz~2, we found
-participants' responses to \textit{Four Fundamental Forces}-related questions
-did \textit{not} reliably predict their success on \textit{Birth of
-Stars}-related questions ($OR = 1.865,\ \lambda_{LR} = 3.205,\ 95\%\
-\textnormal{CI} = [3.027, 3.600],\ p = 0.125$), nor did their responses to
-\textit{Birth of Stars}-related questions reliably predict their success on
-\textit{Four Fundamental Forces}-related questions ($OR = 3.490,\ \lambda_{LR}
-= 3.266,\ 95\%\ \textnormal{CI} = [3.033, 3.866],\ p = 0.094$). These
-``prediction failures'' appear to come from the fact that any signal derived
-from participants' knowledge about the content of the \textit{Birth of Stars}
+general, or about Quiz~1 performance in particular. This would be expected, for
+example, if participants were guessing about the answers to the Quiz~1
+questions (prior to having watched either lecture). When we repeated this
+analysis for Quizzes~2 and~3, we found that \textit{higher} estimated knowledge
+for a given question predicted a greater likelihood of answering it correctly
+(Quiz~2: $OR = 2.905,\ \lambda_{LR} = 17.333,\ 95\%\ \textnormal{CI} =
+[14.966,\ 29.309],\ p = 0.002$; Quiz~3: $OR = 3.238,\ \lambda_{LR} = 6.882,\
+95\%\ \textnormal{CI} = [6.228,\ 8.184],\ p = 0.017$). Taken together, these
+results suggest that our knowledge estimates reliably predict participants'
+performance on individual held-out quiz questions, but only after participants
+have received at least some training.
+
+We observed a similar pattern of results when used this approach to estimate
+participants' knowledge about held-out questions from one lecture using their
+performance on other questions from the \textit{same} lecture. Specifically,
+for Quiz~1 questions (i.e., prior to watching either), participants' estimated
+knowledge for the embedding coordinates of held-out \textit{Four Fundamental
+Forces}-related questions estimated using other \textit{Four Fundamental
+Forces}-related questions did not reliably predict whether those questions were
+answered correctly ($OR = 1.891,\ \lambda_{LR} = 2.293,\ 95\%\ \textnormal{CI}
+= [2.091,\ 2.622],\ p = 0.139$). The same was true of knowledge estimates for
+held-out \textit{Birth of Stars}-related questions based on other \textit{Birth
+of Stars}-related questions ($OR = 0.722,\ \lambda_{LR} = 5.115,\ 95\%\
+\textnormal{CI} = [0.094,\ 0.146],\ p = 0.738$). As in our analysis that
+included all questions, we speculate that these ``null'' results might reflect
+some degree of random guessing on Quiz~1. When we repeated these within-lecture
+analyses using questions from Quiz~2 (which participants took immediately after
+viewing \textit{Four Fundamental Forces} but prior to viewing \textit{Birth of
+Stars}), we found that they now reliably predicted success on \textit{Four
+Fundamental Forces}-related questions ($OR = 9.023,\ \lambda_{LR} = 18.707,\
+95\%\ \textnormal{CI} = [10.877,\ 22.222],\ p = 0.001$) but not on
+\textit{Birth of Stars}-related questions ($OR = 0.306,\ \lambda_{LR} = 5.115,\
+95\%\ \textnormal{CI} = [4.624,\ 5.655],\ p = 0.055$). Here, we speculate that
+participants might have been guessing about the \textit{Birth of Stars} content
+(e.g., prior to having watched it), whereas they might have been drawing on
+some structured knowledge about the \textit{Four Fundamental Forces} content
+(e.g., from having just watched it). When we applied this approach to Quiz~3
+responses (given immediately after viewing \textit{Birth of Stars}), we found
+that within-lecture knowledge estimates for \textit{Birth of Stars}-related
+questions could now reliably predict success on those questions ($OR = 5.467,\
+\lambda_{LR} = 10.670,\ 95\%\ \textnormal{CI} = [7.998, 12.532],\ p = 0.006$).
+However, within-lecture knowledge estimates for \textit{Four Fundamental
+Forces} questions answered on Quiz~3 were no longer directly related to the
+likelihood of successfully answering them and instead exhibited the inverse
+relationship we would expect to arise from unstructured knowledge (with respect
+to the embedding space; $OR = 0.013,\ \lambda_{LR} = 14.648,\ 95\%\
+\textnormal{CI} = [10.695, 23.096],\ p = 0.001$). Speculatively, we suggest
+that this may reflect participants forgetting some of the \textit{Four
+Fundamental Forces} content (e.g., perhaps in favor of prioritizing encoding
+the just-watched \textit{Birth of Stars} content in preparation for the third
+quiz). If this forgetting happens in a relatively ``random'' way (with respect
+to spatial distance within the embedding space), then it could explain why some
+held-out questions about \textit{Four Fundamental Forces} were answered
+incorrectly, even if questions at nearby coordinates (i.e., about similar
+content) were answered correctly. This might lead our approach to over-estimate
+knowledge for held-out questions about ``forgotten'' knowledge that
+participants answered incorrectly. Taken together, these within-lecture results
+suggest that our approach can distinguish between questions about different
+content covered by a single lecture when participants have sufficiently
+structured knowledge about its contents, though this specificity may decrease
+with time since the relevant material was learned.
+
+Finally, we used this approach to estimate participants' knowledge about
+held-out questions from one lecture using their performance on other questions
+from the \textit{other} lecture. Here we again observed a similar pattern of
+results, though with some notable differences. On Quiz~1, we found that
+participants' abilities to correctly answer questions about \textit{Four
+Fundamental Forces} could be predicted from their responses to questions about
+\textit{Birth of Stars} ($OR = 1.896,\ \lambda_{LR} = 7.205,\ 95\%\
+\textnormal{CI} = [6.224, 7.524],\ p = 0.039$) and similarly, that their
+ability to correctly answer \textit{Birth of Stars}-related questions could be
+predicted from their responses to \textit{Four Fundamental Forces}-related
+questions ($OR = 1.522,\ \lambda_{LR} = 6.448,\ 95\%\ \textnormal{CI} = [5.656,
+6.843],\ p = 0.043$). Given the results from our analyses that included all
+questions and within-lecture predictions, we were surprised to find that the
+knowledge estimates could reliably (if weakly) predict participants'
+performance across content from different lectures. It is possible that this
+result reflects a combination of random guessing prior to training (leading to
+a weak effect size), in combination with some coarse-scale structured knowledge
+that participants had about the content prior to watching either lecture. When
+we repeated this analysis using questions from Quiz~2, we found participants'
+responses to \textit{Four Fundamental Forces}-related questions did
+\textit{not} reliably predict their success on \textit{Birth of Stars}-related
+questions ($OR = 1.865,\ \lambda_{LR} = 3.205,\ 95\%\ \textnormal{CI} = [3.027,
+3.600],\ p = 0.125$), nor did their responses to \textit{Birth of
+Stars}-related questions reliably predict their success on \textit{Four
+Fundamental Forces}-related questions ($OR = 3.490,\ \lambda_{LR} = 3.266,\
+95\%\ \textnormal{CI} = [3.033, 3.866],\ p = 0.094$). These ``prediction
+failures'' appear to come from the fact that any signal derived from
+participants' knowledge about the content of the \textit{Birth of Stars}
 lecture (prior to watching it) is swamped by the much more dramatic increase in
@@
 about both content on which these predictions are based and that for which they
-are made. Our results also indicate some potential limitations of our approach:
-when the contrast in participants' knowledge within the embedding space is low
-overall, our approach (often) cannot reliably predict their abilities to answer
-individual quiz questions.
+are made. Our results also indicate some important limitations of our approach:
+if participants' quiz performance does not reflect what they know (e.g., when
+they ``guess''), or if their knowledge is not structured in a way that is
+reflected by the embedding space, then our knowledge estimates will not be
+predictive of their performance.
 

### 2024-02-20 paper/main.tex
checking in updates to merge from upstream

--- 2024-02-19 paper/main.tex
@@
     participant answered on the same quiz (``All questions''; top row),
-    knowledge for each question about one lecture based on all questions (from
-    the same participant and quiz) about the \textit{other} lecture
-    (``Across-lecture''; middle rows), and knowledge for each question about
-    one lecture based on all other questions (from the same participant and
-    quiz) about the \textit{same} lecture (``Within-lecture''; bottom rows).
+    knowledge for each question about one lecture based on all other questions 
+    (from the same participant and quiz) about the \textit{same} lecture 
+    (``Within-lecture''; middle rows), and knowledge for each question about 
+    one lecture based on all questions (from the same participant and quiz) 
+    about the \textit{other} lecture (``Across-lecture''; bottom rows).
     The background in each panel displays the kernel density estimates of the
@@
     probabilities of correctly answering a question as a function of estimated
-    knowledge. Error ribbons denote bootstrap-estimated 95\% confidence
-    intervals. \textbf{JRM NOTE: RE-ORDER ROWS TO MATCH THE TEXT, AND UPDATE
-    CAPTION ACCORDINGLY}}
+    knowledge. Error ribbons denote the 95\% confidence
+    intervals.}
 
@@
 \textit{correctly} answered question, the proportion of remaining questions
-answered correctly would be $\frac{n - 1}{q - 1}$. If we hold out a single
+answered correctly would be $\frac{n - 1}{q - 1}$. Whereas if we hold out a single
 \textit{incorrectly} answered question, the proportion of remaining questions
@@
 embedding-space distance from the held-out question; see Eqn.~\ref{eqn:prop}),
-if these weights were uninformative (e.g., randomly distributed), then we
+if these weights are uninformative (e.g., randomly distributed), then we
 should expect to see this same inverse relationship between estimated knowledge
@@
 proportion correct: $0.46$), and the specific questions they answer correctly
-not not seem to be structured in a meaningful way with respect to the embedding
+do not seem to be structured in a meaningful way with respect to the embedding
 space (e.g., Fig.~\ref{fig:knowledge-maps}A, left panel). On Quizzes~2 and~3,
@@
 
-In the set of analyses reported in Figure~\ref{fig:predictions}, we applied Equation~\ref{eqn:prop} to
-
-estimate participants' knowledge for individual held-out quiz questions (i.e., treating
-
-In the set of analyses reported in Figure~\ref{fig:predictions}, we applied Equation~\ref{eqn:prop} to estimate participants' knowledge at the embedding coordinates of individual held-out quiz questions.
-For each of the three quizzes a participant took,
-
-Equation~\ref{eqn:prop} to estimate participants' knowledge at the embedding coordinate of individual held-out questions, based on other questions
-
-all other questions (``All questions''; Fig.~\ref{fig:predictions}, top row),
-
-(``All questions''; Fig.~\ref{fig:predictions}, top row).
-This test was intended to assess the overall predictive power of our approach. 
-Second, we estimated knowledge for each question about a given lecture using only the other questions (from the same participant and quiz) about that \textit{same} lecture (``Within-lecture''; Fig.~\ref{fig:predictions}, middle rows).
-This test was intended to assess the \textit{specificity} of our approach by asking whether our predictions could distinguish between questions about different content covered by the same lecture.
-Third, we estimated knowledge for each question about one lecture using only questions (from the same participant and quiz) about the \textit{other} lecture (``Across-lecture''; Fig.~\ref{fig:predictions}, bottom rows).
-
-To analyze the predictive value of
-
-To predict individual participants' success on held-out quiz questions, we used Equation~\ref{eqn:prop}
+In the set of analyses reported in Figure~\ref{fig:predictions}, we assessed whether estimates of participants' knowledge at the embedding coordinates of individual quiz questions could reliably predict their ability to correctly answer those questions.
+In essence, we treated each question a given participant answered on a given quiz as a ``lecture'' consisting of a single timepoint, and used Equation~\ref{eqn:prop} to estimate the participant's knowledge for its embedding coordinate based on their performance on all \textit{other} questions they answered on that same quiz (``All questions''; Fig.~\ref{fig:predictions}, top row).
+We also computed analogous knowledge estimates for each lecture-related question based on all other questions (answered by the same participant, on the same quiz) about the same lecture (``Within-lecture''; Fig.~\ref{fig:predictions}, middle rows) and based on all questions about the other of the two lectures (``Across-lecture''; Fig.~\ref{fig:predictions}, bottom rows).
+
+In each version of this analysis (i.e., row in Fig.~\ref{fig:predictions}), and separately for each of the three quizzes (i.e., column in Fig.~\ref{fig:predictions}),  we then fit a generalized linear mixed model (GLMM) with a logistic link function to the set of knowledge estimates for all questions answered by all participants on the given quiz.
+Our models were implemented in \texttt{R} using the \texttt{lme4} package \citep{BateEtal15}.
+
+%In each versions of this analysis (i.e., row in Fig.~\ref{fig:predictions}), and separately for each of the three quizzes (i.e., column in Fig.~\ref{fig:predictions}),  we then fit a generalized linear mixed model (GLMM) with a logistic link function to the set of
+
+%In the set of analyses reported in Figure~\ref{fig:predictions}, we used generalized linear mixed models (GLMMs) to analyze whether estimates of participants' knowledge at the embedding coordinates of individual held-out questions could reliably predict their ability to answer those questions correctly.
 
@@
 
-%\begin{lstlisting}[language=R]
-%    accuracy \sim knowledge + (knowledge|participant) + (knowledge|question)
-%\end{lstlisting}
-
 note that qID is implicitly nested within levels of lecture
+
+$$
+\begin{aligned}
+  \operatorname{accuracy}_{i}  &\sim \operatorname{Binomial}(n = 1, \operatorname{prob}_{\operatorname{accuracy} = \operatorname{correct}} = \widehat{P}) \\
+    \log\left[\frac{\hat{P}}{1 - \hat{P}} \right] &=\alpha_{j[i],k[i]} \\    
+\left(
+  \begin{array}{c} 
+    \begin{aligned}
+      &\alpha_{j} \\
+      &\gamma_{1j}
+    \end{aligned}
+  \end{array}
+\right)
+  &\sim N \left(
+\left(
+  \begin{array}{c} 
+    \begin{aligned}
+      &\gamma_{0}^{\alpha} + \gamma_{1k[i]}^{\alpha}(\operatorname{knowledge}) \\
+      &\mu_{\gamma_{1j}}
+    \end{aligned}
+  \end{array}
+\right)
+, 
+\left(
+  \begin{array}{cc}
+     \sigma^2_{\alpha_{j}} & \rho_{\alpha_{j}\gamma_{1j}} \\ 
+     \rho_{\gamma_{1j}\alpha_{j}} & \sigma^2_{\gamma_{1j}}
+  \end{array}
+\right)
+ \right)
+    \text{, for participant j = 1,} \dots \text{,J} \\    
+\left(
+  \begin{array}{c} 
+    \begin{aligned}
+      &\alpha_{k} \\
+      &\gamma_{1k}
+    \end{aligned}
+  \end{array}
+\right)
+  &\sim N \left(
+\left(
+  \begin{array}{c} 
+    \begin{aligned}
+      &\mu_{\alpha_{k}} \\
+      &\mu_{\gamma_{1k}}
+    \end{aligned}
+  \end{array}
+\right)
+, 
+\left(
+  \begin{array}{cc}
+     \sigma^2_{\alpha_{k}} & \rho_{\alpha_{k}\gamma_{1k}} \\ 
+     \rho_{\gamma_{1k}\alpha_{k}} & \sigma^2_{\gamma_{1k}}
+  \end{array}
+\right)
+ \right)
+    \text{, for question k = 1,} \dots \text{,K}
+\end{aligned}
+$$
 

### 2024-02-20 paper/main.tex

--- 2024-02-20 paper/main.tex
@@
     participant answered on the same quiz (``All questions''; top row),
-    knowledge for each question about one lecture based on all questions (from
-    the same participant and quiz) about the \textit{other} lecture
-    (``Across-lecture''; middle rows), and knowledge for each question about
-    one lecture based on all other questions (from the same participant and
-    quiz) about the \textit{same} lecture (``Within-lecture''; bottom rows).
+    knowledge for each question about one lecture based on all other questions
+    (from the same participant and quiz) about the \textit{same} lecture
+    (``Within-lecture''; middle rows), and knowledge for each question about
+    one lecture based on all questions (from the same participant and quiz)
+    about the \textit{other} lecture (``Across-lecture''; bottom rows).
     The background in each panel displays the kernel density estimates of the
@@
 \subsubsection*{GLMM METHODS SECTION PLACEHOLDER}\label{subsec:glmm}
+
+In the set of analyses reported in Figure~\ref{fig:predictions}, we assessed whether estimates of participants' knowledge at the embedding coordinates of individual quiz questions could reliably predict their ability to correctly answer those questions.
+In essence, we treated each question a given participant answered on a given quiz as a ``lecture'' consisting of a single timepoint, and used Equation~\ref{eqn:prop} to estimate the participant's knowledge for its embedding coordinate based on their performance on all \textit{other} questions they answered on that same quiz (``All questions''; Fig.~\ref{fig:predictions}, top row).
+We also computed analogous knowledge estimates for each lecture-related question based on all other questions (answered by the same participant, on the same quiz) about the same lecture (``Within-lecture''; Fig.~\ref{fig:predictions}, middle rows) and based on all questions about the other of the two lectures (``Across-lecture''; Fig.~\ref{fig:predictions}, bottom rows).
+
+In each version of this analysis (i.e., row in Fig.~\ref{fig:predictions}), and separately for each of the three quizzes (i.e., column in Fig.~\ref{fig:predictions}),  we then fit a generalized linear mixed model (GLMM) with a logistic link function to the set of knowledge estimates for all questions answered by all participants on the given quiz.
+Our models were implemented in \texttt{R} using the \texttt{lme4} package \citep{BateEtal15}.
+
+%In each versions of this analysis (i.e., row in Fig.~\ref{fig:predictions}), and separately for each of the three quizzes (i.e., column in Fig.~\ref{fig:predictions}),  we then fit a generalized linear mixed model (GLMM) with a logistic link function to the set of
+
+%In the set of analyses reported in Figure~\ref{fig:predictions}, we used generalized linear mixed models (GLMMs) to analyze whether estimates of participants' knowledge at the embedding coordinates of individual held-out questions could reliably predict their ability to answer those questions correctly.
+
+$$
+    \mathtt{accuracy \sim knowledge + (knowledge\ \vert\ participant) + (knowledge\ \vert\ question)}
+$$
+
+note that qID is implicitly nested within levels of lecture
+
+$$
+\begin{aligned}
+  \operatorname{accuracy}_{i}  &\sim \operatorname{Binomial}(n = 1, \operatorname{prob}_{\operatorname{accuracy} = \operatorname{correct}} = \widehat{P}) \\
+    \log\left[\frac{\hat{P}}{1 - \hat{P}} \right] &=\alpha_{j[i],k[i]} \\
+\left(
+  \begin{array}{c}
+    \begin{aligned}
+      &\alpha_{j} \\
+      &\gamma_{1j}
+    \end{aligned}
+  \end{array}
+\right)
+  &\sim N \left(
+\left(
+  \begin{array}{c}
+    \begin{aligned}
+      &\gamma_{0}^{\alpha} + \gamma_{1k[i]}^{\alpha}(\operatorname{knowledge}) \\
+      &\mu_{\gamma_{1j}}
+    \end{aligned}
+  \end{array}
+\right)
+,
+\left(
+  \begin{array}{cc}
+     \sigma^2_{\alpha_{j}} & \rho_{\alpha_{j}\gamma_{1j}} \\
+     \rho_{\gamma_{1j}\alpha_{j}} & \sigma^2_{\gamma_{1j}}
+  \end{array}
+\right)
+ \right)
+    \text{, for participant j = 1,} \dots \text{,J} \\
+\left(
+  \begin{array}{c}
+    \begin{aligned}
+      &\alpha_{k} \\
+      &\gamma_{1k}
+    \end{aligned}
+  \end{array}
+\right)
+  &\sim N \left(
+\left(
+  \begin{array}{c}
+    \begin{aligned}
+      &\mu_{\alpha_{k}} \\
+      &\mu_{\gamma_{1k}}
+    \end{aligned}
+  \end{array}
+\right)
+,
+\left(
+  \begin{array}{cc}
+     \sigma^2_{\alpha_{k}} & \rho_{\alpha_{k}\gamma_{1k}} \\
+     \rho_{\gamma_{1k}\alpha_{k}} & \sigma^2_{\gamma_{1k}}
+  \end{array}
+\right)
+ \right)
+    \text{, for question k = 1,} \dots \text{,K}
+\end{aligned}
+$$
 

### 2024-02-20 paper/main.tex
checking in WIP updates to GLMM-related methods section

@@
 topics. We found that with a limited number of additional adjustments
-following~\citep{BoydEtal14}, such as removing corpus-specific stop-words, the
+following~\citet{BoydEtal14}, such as removing corpus-specific stop-words, the
 model yielded (subjectively) sensible and coherent topics. The distribution of
@@
 stop word list with the following additional words, selected using one of the
-approaches suggested by~\citep{BoydEtal14}: ``actual,'' ``actually,'' ``also,''
+approaches suggested by~\citet{BoydEtal14}: ``actual,'' ``actually,'' ``also,''
 ``bit,'' ``could,'' ``e,'' ``even,'' ``first,'' ``follow,'' ``following,''
@@
 In essence, we treated each question a given participant answered on a given quiz as a ``lecture'' consisting of a single timepoint, and used Equation~\ref{eqn:prop} to estimate the participant's knowledge for its embedding coordinate based on their performance on all \textit{other} questions they answered on that same quiz (``All questions''; Fig.~\ref{fig:predictions}, top row).
-We also computed analogous knowledge estimates for each lecture-related question based on all other questions (answered by the same participant, on the same quiz) about the same lecture (``Within-lecture''; Fig.~\ref{fig:predictions}, middle rows) and based on all questions about the other of the two lectures (``Across-lecture''; Fig.~\ref{fig:predictions}, bottom rows).
-
-In each version of this analysis (i.e., row in Fig.~\ref{fig:predictions}), and separately for each of the three quizzes (i.e., column in Fig.~\ref{fig:predictions}),  we then fit a generalized linear mixed model (GLMM) with a logistic link function to the set of knowledge estimates for all questions answered by all participants on the given quiz.
-Our models were implemented in \texttt{R} using the \texttt{lme4} package \citep{BateEtal15}.
-
-%In each versions of this analysis (i.e., row in Fig.~\ref{fig:predictions}), and separately for each of the three quizzes (i.e., column in Fig.~\ref{fig:predictions}),  we then fit a generalized linear mixed model (GLMM) with a logistic link function to the set of
-
-%In the set of analyses reported in Figure~\ref{fig:predictions}, we used generalized linear mixed models (GLMMs) to analyze whether estimates of participants' knowledge at the embedding coordinates of individual held-out questions could reliably predict their ability to answer those questions correctly.
-
-$$
+Additionally, for each lecture-related question (i.e., excluding questions about general physics knowledge), we computed analogous knowledge estimates based on all other questions the participant answered on the same quiz about (1) the same lecture as the target question (``Within-lecture''; Fig.~\ref{fig:predictions}, middle rows), and (2) the other of the two lectures (``Across-lecture''; Fig.~\ref{fig:predictions}, bottom rows).
+%For each lecture-related question (i.e., excluding questions about general physics knowledge), we also computed analogous knowledge estimates based on two subsets of the other questions the participant answered on the same quiz: (1) all other questions about the same lecture as the target question (``Within-lecture''; Fig.~\ref{fig:predictions}, middle rows), and (2) all questions about the other of the two lectures (``Across-lecture''; Fig.~\ref{fig:predictions}, bottom rows).
+%For each lecture-related question (i.e., excluding questions about general physics knowledge), we also computed analogous knowledge estimates based on:~(1) all other questions the participant answered on the same quiz about the same lecture as the target question (``Within-lecture''; Fig.~\ref{fig:predictions}, middle rows), and (2) all questions they answered on the same quiz about the other of the two lectures (``Across-lecture''; Fig.~\ref{fig:predictions}, bottom rows).
+%We also computed analogous knowledge estimates for each lecture-related question based on (1) all other questions answered by the same participant, on the same quiz about the same lecture as the target question (``Within-lecture''; Fig.~\ref{fig:predictions}, middle rows) and (2) all questions from the same participant and quiz about the other of the two lectures (``Across-lecture''; Fig.~\ref{fig:predictions}, bottom rows).
+
+In each version of this analysis (i.e., row in Fig.~\ref{fig:predictions}), and separately for each of the three quizzes (i.e., column in Fig.~\ref{fig:predictions}),  we then fit a generalized linear mixed model (GLMM) with a logistic link function to the set of knowledge estimates for all questions that participants answered on the given quiz.
+We implemented these models in \texttt{R} using the \texttt{lme4} package~\citep{BateEtal15a} and fit them following guidance from~\citet{BateEtal15b} and \citet{MatuEtal17}.
+Specifically, we initially fit each model with the maximal random effects structure afforded our data, which we identified as:
+\[
     \mathtt{accuracy \sim knowledge + (knowledge\ \vert\ participant) + (knowledge\ \vert\ question)}
-$$
-
-note that qID is implicitly nested within levels of lecture
-
-$$
-\begin{aligned}
-  \operatorname{accuracy}_{i}  &\sim \operatorname{Binomial}(n = 1, \operatorname{prob}_{\operatorname{accuracy} = \operatorname{correct}} = \widehat{P}) \\
-    \log\left[\frac{\hat{P}}{1 - \hat{P}} \right] &=\alpha_{j[i],k[i]} \\
-\left(
-  \begin{array}{c}
-    \begin{aligned}
-      &\alpha_{j} \\
-      &\gamma_{1j}
-    \end{aligned}
-  \end{array}
-\right)
-  &\sim N \left(
-\left(
-  \begin{array}{c}
-    \begin{aligned}
-      &\gamma_{0}^{\alpha} + \gamma_{1k[i]}^{\alpha}(\operatorname{knowledge}) \\
-      &\mu_{\gamma_{1j}}
-    \end{aligned}
-  \end{array}
-\right)
-,
-\left(
-  \begin{array}{cc}
-     \sigma^2_{\alpha_{j}} & \rho_{\alpha_{j}\gamma_{1j}} \\
-     \rho_{\gamma_{1j}\alpha_{j}} & \sigma^2_{\gamma_{1j}}
-  \end{array}
-\right)
- \right)
-    \text{, for participant j = 1,} \dots \text{,J} \\
-\left(
-  \begin{array}{c}
-    \begin{aligned}
-      &\alpha_{k} \\
-      &\gamma_{1k}
-    \end{aligned}
-  \end{array}
-\right)
-  &\sim N \left(
-\left(
-  \begin{array}{c}
-    \begin{aligned}
-      &\mu_{\alpha_{k}} \\
-      &\mu_{\gamma_{1k}}
-    \end{aligned}
-  \end{array}
-\right)
-,
-\left(
-  \begin{array}{cc}
-     \sigma^2_{\alpha_{k}} & \rho_{\alpha_{k}\gamma_{1k}} \\
-     \rho_{\gamma_{1k}\alpha_{k}} & \sigma^2_{\gamma_{1k}}
-  \end{array}
-\right)
- \right)
-    \text{, for question k = 1,} \dots \text{,K}
-\end{aligned}
-$$
+\]
+Here, ``\texttt{accuracy}'' is a binary value indicating whether each target question was answered correctly or incorrectly, ``\texttt{knowledge}'' is estimated knowledge at each target question's embedding coordinate, ``\texttt{participant}'' is a unique identifier assigned to each participant, and ``\texttt{question}'' is a unique identifier assigned to each quiz question.
+For models we fit using knowledge estimates for target questions about multiple content areas (i.e., in the ``All questions'' version of the analysis), we also included an additional random effect term, $\mathtt{(knowledge\ \vert\ lecture)}$, where ``\texttt{lecture}'' is a categorical value denoting whether the target question was about \textit{Four Fundamental Forces}, \textit{Birth of Stars}, or general physics knowledge.
+Note that with our coding scheme, identifiers for each \texttt{question} are implicitly nested within levels of \texttt{lecture} and do not require explicit nesting in our model formula.
+
+As necessary, we then iteratively removed random effects from the maximal model until it successfully converged with a full rank (i.e., non-singular) random effects variance-covariance matrix. 
+%When inspecting the model's random effect estimates revealed multiple terms estimated at the boundary of their parameter space (i.e., variance components of 0 or correlation terms of  $\pm 1$), we found that the order in which we eliminated these terms typically did not affect which terms did and did not need to be removed in order for the model to converge to a non-degenerate solution.
+When this required eliminating multiple terms whose estimates reached the boundary of their parameter space (i.e., variance components of 0 or correlation terms of  $\pm 1$), we found (qualitatively) that the order in which we did so typically did not affect the set of terms that needed to be removed in order for the model to converge to a non-degenerate solution.
+However, in order to ensure consistency in our approach across the 15 separate GLMMs we fit in this set of analyses, we established a general approach to selecting a boundary-estimated parameter to eliminate for each stepwise reduction of the model's complexity, broadly adapted from~\citet{BateEtal15b}.
+First, we constrained any correlation terms estimated at the boundary (i.e., $\pm 1$) to 0 and re-fit the model.
+This typically resulted in the variance component for the slope or intercept (or possibly both) associated with the zero-constrained correlation being estimated as 0, suggesting which terms we should consider removing.
+Second, when choosing which of two variance components to remove from the model, we prioritized removing higher-order terms before removing lower-order terms.
+In other words, if the variance components for a random slope and a random intercept were both estimated as 0, we chose to remove the random slope.
+Additionally, if constraining a correlation term to 0 allowed the model to converge with a full rank variance-covariance matrix, we left the correlation term constrained rather than removing the associated slope and/or intercept component.
+Third, to choose which of two zero-estimated variance components of the \textit{same} order to remove from the model, we took one of two approaches.
+If the two components were both random slopes, performed a Principal Components Analysis (PCA) on the random effects variance-covariance matrix, and compared the proportion of variance explained by the second component from each of the two random effect groupings.
+If one If one explains a substantially smaller proportion of variance than the other, we dropped its corresponding random slope.
+Alternatively, if the difference in variance explained by the two is (qualitatively) small, or if the two variance components we wanted to choose between were random intercepts rather than slopes, we removed the one whose absence resulted in the greater decrease in the Akaike information criterion (AIC).
+
+%$$
+%\begin{aligned}
+%  \operatorname{accuracy}_{i}  &\sim \operatorname{Binomial}(n = 1, \operatorname{prob}_{\operatorname{accuracy} = \operatorname{correct}} = \widehat{P}) \\
+%    \log\left[\frac{\hat{P}}{1 - \hat{P}} \right] &=\alpha_{j[i],k[i]} \\
+%\left(
+%  \begin{array}{c}
+%    \begin{aligned}
+%      &\alpha_{j} \\
+%      &\gamma_{1j}
+%    \end{aligned}
+%  \end{array}
+%\right)
+%  &\sim N \left(
+%\left(
+%  \begin{array}{c}
+%    \begin{aligned}
+%      &\gamma_{0}^{\alpha} + \gamma_{1k[i]}^{\alpha}(\operatorname{knowledge}) \\
+%      &\mu_{\gamma_{1j}}
+%    \end{aligned}
+%  \end{array}
+%\right)
+%,
+%\left(
+%  \begin{array}{cc}
+%     \sigma^2_{\alpha_{j}} & \rho_{\alpha_{j}\gamma_{1j}} \\
+%     \rho_{\gamma_{1j}\alpha_{j}} & \sigma^2_{\gamma_{1j}}
+%  \end{array}
+%\right)
+% \right)
+%    \text{, for participant j = 1,} \dots \text{,J} \\
+%\left(
+%  \begin{array}{c}
+%    \begin{aligned}
+%      &\alpha_{k} \\
+%      &\gamma_{1k}
+%    \end{aligned}
+%  \end{array}
+%\right)
+%  &\sim N \left(
+%\left(
+%  \begin{array}{c}
+%    \begin{aligned}
+%      &\mu_{\alpha_{k}} \\
+%      &\mu_{\gamma_{1k}}
+%    \end{aligned}
+%  \end{array}
+%\right)
+%,
+%\left(
+%  \begin{array}{cc}
+%     \sigma^2_{\alpha_{k}} & \rho_{\alpha_{k}\gamma_{1k}} \\
+%     \rho_{\gamma_{1k}\alpha_{k}} & \sigma^2_{\gamma_{1k}}
+%  \end{array}
+%\right)
+% \right)
+%    \text{, for question k = 1,} \dots \text{,K}
+%\end{aligned}
+%$$
 

### 2024-02-20 paper/compile.sh
moving bibliography

@@ -19,7 +19,7 @@ latex -interaction=nonstopmode changes
 bibtex changes
 latex -interaction=nonstopmode changes
 latex -interaction=nonstopmode changes
-pdflatex -interaction=nonstopmode changes
+pdflatex -interaction=nonstopmode changes3
 
 
 rm *.cb* *.dvi *.log *.blg *.aux *.fff *.out

### 2024-02-20 paper/compile.sh
recompiled changes doc, moved bibliography file

@@ -19,7 +19,7 @@ latex -interaction=nonstopmode changes
 bibtex changes
 latex -interaction=nonstopmode changes
 latex -interaction=nonstopmode changes
-pdflatex -interaction=nonstopmode changes3
+pdflatex -interaction=nonstopmode changes
 
 
 rm *.cb* *.dvi *.log *.blg *.aux *.fff *.out

### 2024-02-20 paper/main.tex
checkpoint before pulling from jeremymanning/master

@@
 Alternatively, if the difference in variance explained by the two is (qualitatively) small, or if the two variance components we wanted to choose between were random intercepts rather than slopes, we removed the one whose absence resulted in the greater decrease in the Akaike information criterion (AIC).
+Finally, once we identify the maximal random effects structure for which the data can yield a full rank variance-covariance matrix, we take no additional steps to further reduce the model's complexity.
+We chose this stopping criterion to roughly approximate a ``middle ground'' between approaches to model specification and selection that emphasize maximalism at the cost of potential singular fits~\citep[e.g.,~][]{BarrEtal13}, and those that emphasize parsimony at the cost of potentially increased Type I error rates~\citep[e.g.,~][]{BateEtal15b}.
+
+To assess the predictive value of these
+
+Next, in order to assess the predictive value of the knowledge estimates
+
+In order to assess the predictive value of the knowledge estimates we used to fit each GLMM, we then fit a \textit{second} model to the same data as each of the 15
+
+In order to assess whether the knowledge estimates we used to fit each GLMM could reliably predict participants' success on held-out questions, we then fit a second GLMM to the observations
 

### 2024-02-21 paper/main.tex
progress on WIP GLMM methods section

--- 2024-02-20 paper/main.tex
@@
 
-As necessary, we then iteratively removed random effects from the maximal model until it successfully converged with a full rank (i.e., non-singular) random effects variance-covariance matrix. 
+When necessary, we then iteratively removed random effects from the maximal model until it successfully converged with a full rank (i.e., non-singular) random effects variance-covariance matrix. 
 %When inspecting the model's random effect estimates revealed multiple terms estimated at the boundary of their parameter space (i.e., variance components of 0 or correlation terms of  $\pm 1$), we found that the order in which we eliminated these terms typically did not affect which terms did and did not need to be removed in order for the model to converge to a non-degenerate solution.
-When this required eliminating multiple terms whose estimates reached the boundary of their parameter space (i.e., variance components of 0 or correlation terms of  $\pm 1$), we found (qualitatively) that the order in which we did so typically did not affect the set of terms that needed to be removed in order for the model to converge to a non-degenerate solution.
-However, in order to ensure consistency in our approach across the 15 separate GLMMs we fit in this set of analyses, we established a general approach to selecting a boundary-estimated parameter to eliminate for each stepwise reduction of the model's complexity, broadly adapted from~\citet{BateEtal15b}.
-First, we constrained any correlation terms estimated at the boundary (i.e., $\pm 1$) to 0 and re-fit the model.
-This typically resulted in the variance component for the slope or intercept (or possibly both) associated with the zero-constrained correlation being estimated as 0, suggesting which terms we should consider removing.
-Second, when choosing which of two variance components to remove from the model, we prioritized removing higher-order terms before removing lower-order terms.
-In other words, if the variance components for a random slope and a random intercept were both estimated as 0, we chose to remove the random slope.
-Additionally, if constraining a correlation term to 0 allowed the model to converge with a full rank variance-covariance matrix, we left the correlation term constrained rather than removing the associated slope and/or intercept component.
-Third, to choose which of two zero-estimated variance components of the \textit{same} order to remove from the model, we took one of two approaches.
-If the two components were both random slopes, performed a Principal Components Analysis (PCA) on the random effects variance-covariance matrix, and compared the proportion of variance explained by the second component from each of the two random effect groupings.
-If one If one explains a substantially smaller proportion of variance than the other, we dropped its corresponding random slope.
-Alternatively, if the difference in variance explained by the two is (qualitatively) small, or if the two variance components we wanted to choose between were random intercepts rather than slopes, we removed the one whose absence resulted in the greater decrease in the Akaike information criterion (AIC).
+When this required eliminating multiple terms whose estimates reached the boundary of their parameter space (i.e., variance components of 0 or correlation terms of  $\pm 1$), we found (qualitatively) that the order in which we did so typically did not change the set of terms that needed to be removed in order for the model to converge to a non-degenerate solution.
+However, in order to ensure we fit all of the models for these analyses in a consistent way, we devised some simple heuristics for choosing which boundary-estimated parameter to eliminate in each stepwise reduction of the model's complexity, based on a combination of popular approaches~\citep{BarrEtal13,BateEtal15b,MatuEtal17}.
+First, we constrained any correlation terms estimated at their boundaries (i.e., $\pm 1$) to 0 and re-fit the model.
+This usually resulted in the variance component for the associated random slope (or occasionally the intercept, or even both) being estimated as 0, and suggested which terms we should consider removing.
+Second, when choosing which of two zero-variance terms to remove from the model, we prioritized removing higher-order terms before lower-order terms.
+In other words, if the estimated variance for both a random intercept and a random slope were 0, we chose to remove the random slope term before re-fitting the model and evaluating whether or not to remove the intercept.
+%Additionally, if constraining a boundary-estimated correlation term to 0 allowed the model to converge with a full rank covariance matrix, we left the correlation term constrained rather than removing the associated slope and/or intercept component.
+Third, when choosing which of two boundary-estimated variance components of the \textit{same} order to exclude from the model first, we took one of two approaches.
+If the two components were random slopes with small but non-zero coefficients (e.g., on the order of $10^{-4}$ or less), we performed a Principal Components Analysis (PCA) on the random effects variance-covariance matrix and compared the variance explained by the two terms' corresponding PCs.
+If one explained a substantially smaller proportion of variance than the other (loosely defined), we dropped its corresponding random slope.
+Alternatively, if both slopes' principal components explained a similar amount of variance, or if the two terms we wanted to compare were random intercepts rather than slopes, we removed the one whose exclusion resulted in the greater decrease in the Akaike information criterion (AIC).
+Fourth, after removing either a slope or intercept from one random effect grouping, we re-introduced any correlation terms we had previously constrained to 0 for other random effect groupings to check if they could now be estimated.
+Finally, once the model successfully converged with a full rank covariance matrix, we did not remove random effects for any other reasons (e.g., to lowered AIC, increase log-likelihood, etc.). 
+We chose this stopping criterion as a conceptual ``middle ground'' between two popular but opposing approaches to model selection that advocate for either retaining the maximal model that allows convergence, regardless of singular fits~\citep[at the potential cost of decreased power; e.g.,~][]{BarrEtal13} or performing additional hypothesis tests on individual parameters and removing non-significant components to achieve a parsimonious model~\citep[at the potential cost of increased Type I error rates; e.g.,~][]{BateEtal15b}.
+%We chose this stopping criterion as a conceptual ``middle ground'' between two popular but opposing approaches to model selection that advocate (respectively) for either retaining the maximal model that allows convergence, regardless of singular fits~\citep[at the potential cost of decreased power; e.g.,~][]{BarrEtal13} or testing individual parameters achieving a parsimonious model by discarding all parameters that don't significantly decrease goodness of fit ~\citep[at the potential cost of increased Type I error rates; e.g.,~][]{BateEtal15b}.
+Our threshold for inclusion of random effects is intended to achieve a reasonable balance between these trade-offs.
+
+To assess the predictive value of our knowledge estimates for individual quiz questions, we used the same sets of observations used to fit each GLMM to fit a second set of ``null'' models (similarly with a logistic link function).
+We fit these models with the formula:
+\[
+    \mathtt{accuracy \sim (1\ \vert\ participant) + (1\ \vert\ question)}
+\]
+
+%In order to assess the predictive value of the knowledge estimates, we then fit a second set of ``null'' models to the same sets of observations used to fit our full GLMMs. These 
+%
+%
+%used the same sets of observations used to fit these GLMMs to fit a second set of ``null'' models. 
+%
+%
+%
+%Next, in order to assess the predictive value of the knowledge estimates 
+%
+%
+%
+%In order to assess the predictive value of the knowledge estimates we used to fit each GLMM, we then fit a \textit{second} model to the same data as each of the 15 
+%
+%In order to assess whether the knowledge estimates we used to fit each GLMM could reliably predict participants' success on held-out questions, we then fit a second GLMM to the observations
 

### 2024-02-21 paper/main.tex
a few more JRM edits

@@
 properties of the elements, and other high-level characteristics of
-how they are used~\citep{Mann20, Mann21a}.
+how they are used~\citep{Mann23b, Mann21a}.
 To be clear, this is not to say that text embedding models themselves
@@
 \textit{structure} of text documents beyond their surface-level contents
-provides a computational framework through which those document's
-deeper conceptual meaning may be quantified, explored, and understood.
+provides a computational framework through which those documents'
+deeper conceptual meanings may be quantified, explored, and understood.
 According to these models,
@@
 and questions (see \nameref{subsec:glmm}). To assess the predictive value of
-the knowledge estimates, we compared each GLMMs to an analogous (i.e., nested)
+the knowledge estimates, we compared each GLMM to an analogous (i.e., nested)
 ``null'' model that did not consider estimated knowledge using parametric
@@
     one lecture based on all questions (from the same participant and quiz)
-    about the \textit{other} lecture (``Across-lecture''; bottom rows).
-    The background in each panel displays the kernel density estimates of the
-    relative observed proportions of correctly (blue) versus incorrectly (red)
-    answered questions, for each level of estimated knowledge along the
-    $x$-axis. The black curves display the (population-level) GLMM-predicted
-    probabilities of correctly answering a question as a function of estimated
-    knowledge. Error ribbons denote the 95\% confidence
-    intervals.}
+    about the \textit{other} lecture (``Across-lecture''; bottom rows). The
+    backgrounds in each panel display kernel density estimates of the relative
+    observed proportions of correctly (blue) versus incorrectly (red) answered
+    questions, for each level of estimated knowledge along the $x$-axis. The
+    black curves display the (population-level) GLMM-predicted probabilities of
+    correctly answering a question as a function of estimated knowledge. Error
+    ribbons denote 95\% confidence intervals.}
 
@@
 those questions. What result might we expect to see if this is the case? To
-gain an intuition for this possibility, consider the expected outcome if we
+gain an intuition for this scenario, consider the expected outcome if we
 carried out these same analyses using a simple proportion-correct measure in
@@
 \textit{correctly} answered question, the proportion of remaining questions
-answered correctly would be $\frac{n - 1}{q - 1}$. Whereas if we hold out a single
-\textit{incorrectly} answered question, the proportion of remaining questions
-answered correctly would be $\frac{n}{q - 1}$. In this way, the proportion of
-correctly answered remaining questions is always \textit{lower} when the
-held-out question was answered correctly than when it was answered incorrectly.
-Because our knowledge estimates are computed as a weighted version of this same
-proportion-correct score (where each held-in question's weight reflects its
-embedding-space distance from the held-out question; see Eqn.~\ref{eqn:prop}),
-if these weights are uninformative (e.g., randomly distributed), then we
-should expect to see this same inverse relationship between estimated knowledge
-and performance, on average. On the other hand, if the spatial relationships
-among the quiz questions' embeddings \textit{are} predictive of participants'
-knowledge about the questions' content, then we would expect \textit{higher}
-estimated knowledge for held-out correctly (versus incorrectly) answered
-questions.
+answered correctly would be $\frac{n - 1}{q - 1}$. Whereas if we hold out a
+single \textit{incorrectly} answered question, the proportion of remaining
+questions answered correctly would be $\frac{n}{q - 1}$. In this way, the
+proportion of correctly answered remaining questions is always \textit{lower}
+when the held-out question was answered correctly than when it was answered
+incorrectly. Because our knowledge estimates are computed as a weighted version
+of this same proportion-correct score (where each held-in question's weight
+reflects its embedding-space distance from the held-out question; see
+Eqn.~\ref{eqn:prop}), if these weights are uninformative (e.g., randomly
+distributed), then we should expect to see this same inverse relationship
+between estimated knowledge and performance, on average. On the other hand, if
+the spatial relationships among the quiz questions' embeddings \textit{are}
+predictive of participants' knowledge about the questions' content, then we
+would expect \textit{higher} estimated knowledge for held-out correctly (versus
+incorrectly) answered questions.
 
@@
 partially) by the embedding space. In other words, if the participant's
-performance reflects their true kwowledge, but our text embedding space does
+performance reflects their true knowledge, but our text embedding space does
 not sufficiently capture the structure of that knowledge, then the knowledge
@@
 Finally, we used this approach to estimate participants' knowledge about
-held-out questions from one lecture using their performance on other questions
-from the \textit{other} lecture. Here we again observed a similar pattern of
+held-out questions from one lecture using their performance on questions from
+the \textit{other} lecture. Here we again observed a similar pattern of
 results, though with some notable differences. On Quiz~1, we found that
@@
 result reflects a combination of random guessing prior to training (leading to
-a weak effect size), in combination with some coarse-scale structured knowledge
-that participants had about the content prior to watching either lecture. When
-we repeated this analysis using questions from Quiz~2, we found participants'
+a weak effect size), alongside some coarse-scale structured knowledge that
+participants had about the content prior to watching either lecture. When we
+repeated this analysis using questions from Quiz~2, we found participants'
 responses to \textit{Four Fundamental Forces}-related questions did
@@
 proportion correct for \textit{Birth of Stars}-related questions on Quiz~2:
-$0.36$). When we again carried out these across-lecture knowledge predictions
-using questions from Quiz~3 (when participants had now viewed \textit{both}
+$0.36$). When we carried out these across-lecture knowledge predictions using
+questions from Quiz~3 (when participants had now viewed \textit{both}
 lectures), we could again reliably predict success on questions about both
@@
 ($OR = 7.302,\ \lambda_{LR} = 7.068,\ 95\%\ \textnormal{CI} = [6.490, 8.584],\
-p = 0.017$) using responses to questions questions about the other lecture's
-content. Across all three versions of these analyses, our results suggest that
-(by and large) our knowledge estimations can reliably predict participants'
-abilities to answer individual quiz questions, distinguish between questions
-about similar content, and generalize across content areas, provided that
-participants' quiz responses reflect a minimum level of ``real'' knowledge
-about both content on which these predictions are based and that for which they
-are made. Our results also indicate some important limitations of our approach:
-if participants' quiz performance does not reflect what they know (e.g., when
-they ``guess''), or if their knowledge is not structured in a way that is
-reflected by the embedding space, then our knowledge estimates will not be
-predictive of their performance.
+p = 0.017$) using responses to questions about the other lecture's content.
+Across all three versions of these analyses, our results suggest that (by and
+large) our knowledge estimates can reliably predict participants' abilities to
+answer individual quiz questions, distinguish between questions about similar
+content, and generalize across content areas, provided that participants' quiz
+responses reflect a minimum level of ``real'' knowledge about both content on
+which these predictions are based and that for which they are made. Our results
+also indicate some important limitations of our approach: if participants' quiz
+performance does not reflect what they know (e.g., when they ``guess''), or if
+their knowledge is not structured in a way that is reflected by the embedding
+space, then our knowledge estimates will not be predictive of their
+performance.
 

### 2024-02-21 paper/main.tex
checking in updates to methods

--- 2024-02-21 paper/main.tex
@@
 
-In the set of analyses reported in Figure~\ref{fig:predictions}, we assessed whether estimates of participants' knowledge at the embedding coordinates of individual quiz questions could reliably predict their ability to correctly answer those questions.
+In the set of analyses reported in Figure~\ref{fig:predictions}, we assessed whether estimates of participants' knowledge at the embedding coordinates of individual quiz questions could be used to reliably predict their ability to correctly answer those questions.
 In essence, we treated each question a given participant answered on a given quiz as a ``lecture'' consisting of a single timepoint, and used Equation~\ref{eqn:prop} to estimate the participant's knowledge for its embedding coordinate based on their performance on all \textit{other} questions they answered on that same quiz (``All questions''; Fig.~\ref{fig:predictions}, top row).
@@
 We implemented these models in \texttt{R} using the \texttt{lme4} package~\citep{BateEtal15a} and fit them following guidance from~\citet{BateEtal15b} and \citet{MatuEtal17}.
-Specifically, we initially fit each model with the maximal random effects structure afforded our data, which we identified as:
+Specifically, we initially fit each model with the maximal random effects structure afforded by our design, which we identified as:
 \[
@@
 
-When necessary, we then iteratively removed random effects from the maximal model until it successfully converged with a full rank (i.e., non-singular) random effects variance-covariance matrix. 
+We then iteratively removed random effects from the maximal model until it successfully converged with a full rank (i.e., non-singular) random effects variance-covariance matrix. 
 %When inspecting the model's random effect estimates revealed multiple terms estimated at the boundary of their parameter space (i.e., variance components of 0 or correlation terms of  $\pm 1$), we found that the order in which we eliminated these terms typically did not affect which terms did and did not need to be removed in order for the model to converge to a non-degenerate solution.
-When this required eliminating multiple terms whose estimates reached the boundary of their parameter space (i.e., variance components of 0 or correlation terms of  $\pm 1$), we found (qualitatively) that the order in which we did so typically did not change the set of terms that needed to be removed in order for the model to converge to a non-degenerate solution.
-However, in order to ensure we fit all of the models for these analyses in a consistent way, we devised some simple heuristics for choosing which boundary-estimated parameter to eliminate in each stepwise reduction of the model's complexity, based on a combination of popular approaches~\citep{BarrEtal13,BateEtal15b,MatuEtal17}.
+When this required eliminating multiple terms whose estimates reached the boundary of their parameter space (i.e., variance components of 0 or correlation terms of  $\pm 1$), we found that the order in which we did so typically did not change the set of terms that needed to be removed in order for the model to converge to a non-degenerate solution.
+However, in order to ensure we fit all models used in these analyses in a consistent way, we devised some simple heuristics for choosing which boundary-estimated parameter to eliminate in each stepwise reduction of the model's complexity, based on a combination of popular approaches~\citep{BarrEtal13,BateEtal15b,MatuEtal17}.
 First, we constrained any correlation terms estimated at their boundaries (i.e., $\pm 1$) to 0 and re-fit the model.
@@
 Fourth, after removing either a slope or intercept from one random effect grouping, we re-introduced any correlation terms we had previously constrained to 0 for other random effect groupings to check if they could now be estimated.
-Finally, once the model successfully converged with a full rank covariance matrix, we did not remove random effects for any other reasons (e.g., to lowered AIC, increase log-likelihood, etc.). 
+Finally, once the model successfully converged with a full rank covariance matrix, we did not remove random effects for any other reasons (e.g., to lower AIC, increase log-likelihood, etc.). 
 We chose this stopping criterion as a conceptual ``middle ground'' between two popular but opposing approaches to model selection that advocate for either retaining the maximal model that allows convergence, regardless of singular fits~\citep[at the potential cost of decreased power; e.g.,~][]{BarrEtal13} or performing additional hypothesis tests on individual parameters and removing non-significant components to achieve a parsimonious model~\citep[at the potential cost of increased Type I error rates; e.g.,~][]{BateEtal15b}.
@@
 
-To assess the predictive value of our knowledge estimates for individual quiz questions, we used the same sets of observations used to fit each GLMM to fit a second set of ``null'' models (similarly with a logistic link function).
+%To assess the predictive value of our knowledge estimates for individual quiz questions, we used the same sets of observations used to fit each GLMM to fit a second set of ``null'' models (similarly with a logistic link function).
 We fit these models with the formula:
+To assess the predictive value of our knowledge estimates, we compared each GLMM's ability to discriminate between correctly and incorrectly answered questions to that of an analogous model that did not consider estimated knowledge.
+Specifically, we used the same sets of observations with which we fit each ``full'' model to fit a second ``null'' model, with the formula:
 \[

### 2024-02-21 paper/main.tex
commented out some "extraneous" (?) details about pruning maximal models.  (i left in the text so we can revert easily if needed.)

@@
 
-\subsubsection*{GLMM METHODS SECTION PLACEHOLDER}\label{subsec:glmm}
-
-In the set of analyses reported in Figure~\ref{fig:predictions}, we assessed whether estimates of participants' knowledge at the embedding coordinates of individual quiz questions could be used to reliably predict their ability to correctly answer those questions.
-In essence, we treated each question a given participant answered on a given quiz as a ``lecture'' consisting of a single timepoint, and used Equation~\ref{eqn:prop} to estimate the participant's knowledge for its embedding coordinate based on their performance on all \textit{other} questions they answered on that same quiz (``All questions''; Fig.~\ref{fig:predictions}, top row).
-Additionally, for each lecture-related question (i.e., excluding questions about general physics knowledge), we computed analogous knowledge estimates based on all other questions the participant answered on the same quiz about (1) the same lecture as the target question (``Within-lecture''; Fig.~\ref{fig:predictions}, middle rows), and (2) the other of the two lectures (``Across-lecture''; Fig.~\ref{fig:predictions}, bottom rows).
+\subsubsection*{Generalized linear mixed models}\label{subsec:glmm}
+
+In the set of analyses reported in Figure~\ref{fig:predictions}, we assessed
+whether estimates of participants' knowledge at the embedding coordinates of
+individual quiz questions could be used to reliably predict their ability to
+correctly answer those questions. In essence, we treated each question a given
+participant answered on a given quiz as a ``lecture'' consisting of a single
+timepoint, and used Equation~\ref{eqn:prop} to estimate the participant's
+knowledge for its embedding coordinate based on their performance on all
+\textit{other} questions they answered on that same quiz (``All questions'';
+Fig.~\ref{fig:predictions}, top row). Additionally, for each lecture-related
+question (i.e., excluding questions about general physics knowledge), we
+computed analogous knowledge estimates based on all other questions the
+participant answered on the same quiz about (1) the same lecture as the target
+question (``Within-lecture''; Fig.~\ref{fig:predictions}, middle rows), and (2)
+the other of the two lectures (``Across-lecture''; Fig.~\ref{fig:predictions},
+bottom rows).
+
 %For each lecture-related question (i.e., excluding questions about general physics knowledge), we also computed analogous knowledge estimates based on two subsets of the other questions the participant answered on the same quiz: (1) all other questions about the same lecture as the target question (``Within-lecture''; Fig.~\ref{fig:predictions}, middle rows), and (2) all questions about the other of the two lectures (``Across-lecture''; Fig.~\ref{fig:predictions}, bottom rows).
@@
 
-In each version of this analysis (i.e., row in Fig.~\ref{fig:predictions}), and separately for each of the three quizzes (i.e., column in Fig.~\ref{fig:predictions}),  we then fit a generalized linear mixed model (GLMM) with a logistic link function to the set of knowledge estimates for all questions that participants answered on the given quiz.
-We implemented these models in \texttt{R} using the \texttt{lme4} package~\citep{BateEtal15a} and fit them following guidance from~\citet{BateEtal15b} and \citet{MatuEtal17}.
-Specifically, we initially fit each model with the maximal random effects structure afforded by our design, which we identified as:
+In each version of this analysis (i.e., row in Fig.~\ref{fig:predictions}), and
+separately for each of the three quizzes (i.e., column in
+Fig.~\ref{fig:predictions}), we then fit a generalized linear mixed model
+(GLMM) with a logistic link function to the set of knowledge estimates for all
+questions that participants answered on the given quiz. We implemented these
+models in \texttt{R} using the \texttt{lme4} package~\citep{BateEtal15a} and
+fit them following guidance from~\citet{BateEtal15b} and \citet{MatuEtal17}.
+Specifically, we initially fit each model with the maximal random effects
+structure afforded by our design, which we identified as:
 \[
@@
 \]
-Here, ``\texttt{accuracy}'' is a binary value indicating whether each target question was answered correctly or incorrectly, ``\texttt{knowledge}'' is estimated knowledge at each target question's embedding coordinate, ``\texttt{participant}'' is a unique identifier assigned to each participant, and ``\texttt{question}'' is a unique identifier assigned to each quiz question.
-For models we fit using knowledge estimates for target questions about multiple content areas (i.e., in the ``All questions'' version of the analysis), we also included an additional random effect term, $\mathtt{(knowledge\ \vert\ lecture)}$, where ``\texttt{lecture}'' is a categorical value denoting whether the target question was about \textit{Four Fundamental Forces}, \textit{Birth of Stars}, or general physics knowledge.
-Note that with our coding scheme, identifiers for each \texttt{question} are implicitly nested within levels of \texttt{lecture} and do not require explicit nesting in our model formula.
-
-We then iteratively removed random effects from the maximal model until it successfully converged with a full rank (i.e., non-singular) random effects variance-covariance matrix. 
-%When inspecting the model's random effect estimates revealed multiple terms estimated at the boundary of their parameter space (i.e., variance components of 0 or correlation terms of  $\pm 1$), we found that the order in which we eliminated these terms typically did not affect which terms did and did not need to be removed in order for the model to converge to a non-degenerate solution.
-When this required eliminating multiple terms whose estimates reached the boundary of their parameter space (i.e., variance components of 0 or correlation terms of  $\pm 1$), we found that the order in which we did so typically did not change the set of terms that needed to be removed in order for the model to converge to a non-degenerate solution.
-However, in order to ensure we fit all models used in these analyses in a consistent way, we devised some simple heuristics for choosing which boundary-estimated parameter to eliminate in each stepwise reduction of the model's complexity, based on a combination of popular approaches~\citep{BarrEtal13,BateEtal15b,MatuEtal17}.
-First, we constrained any correlation terms estimated at their boundaries (i.e., $\pm 1$) to 0 and re-fit the model.
-This usually resulted in the variance component for the associated random slope (or occasionally the intercept, or even both) being estimated as 0, and suggested which terms we should consider removing.
-Second, when choosing which of two zero-variance terms to remove from the model, we prioritized removing higher-order terms before lower-order terms.
-In other words, if the estimated variance for both a random intercept and a random slope were 0, we chose to remove the random slope term before re-fitting the model and evaluating whether or not to remove the intercept.
-%Additionally, if constraining a boundary-estimated correlation term to 0 allowed the model to converge with a full rank covariance matrix, we left the correlation term constrained rather than removing the associated slope and/or intercept component.
-Third, when choosing which of two boundary-estimated variance components of the \textit{same} order to exclude from the model first, we took one of two approaches.
-If the two components were random slopes with small but non-zero coefficients (e.g., on the order of $10^{-4}$ or less), we performed a Principal Components Analysis (PCA) on the random effects variance-covariance matrix and compared the variance explained by the two terms' corresponding PCs.
-If one explained a substantially smaller proportion of variance than the other (loosely defined), we dropped its corresponding random slope.
-Alternatively, if both slopes' principal components explained a similar amount of variance, or if the two terms we wanted to compare were random intercepts rather than slopes, we removed the one whose exclusion resulted in the greater decrease in the Akaike information criterion (AIC).
-Fourth, after removing either a slope or intercept from one random effect grouping, we re-introduced any correlation terms we had previously constrained to 0 for other random effect groupings to check if they could now be estimated.
-Finally, once the model successfully converged with a full rank covariance matrix, we did not remove random effects for any other reasons (e.g., to lower AIC, increase log-likelihood, etc.). 
-We chose this stopping criterion as a conceptual ``middle ground'' between two popular but opposing approaches to model selection that advocate for either retaining the maximal model that allows convergence, regardless of singular fits~\citep[at the potential cost of decreased power; e.g.,~][]{BarrEtal13} or performing additional hypothesis tests on individual parameters and removing non-significant components to achieve a parsimonious model~\citep[at the potential cost of increased Type I error rates; e.g.,~][]{BateEtal15b}.
-%We chose this stopping criterion as a conceptual ``middle ground'' between two popular but opposing approaches to model selection that advocate (respectively) for either retaining the maximal model that allows convergence, regardless of singular fits~\citep[at the potential cost of decreased power; e.g.,~][]{BarrEtal13} or testing individual parameters achieving a parsimonious model by discarding all parameters that don't significantly decrease goodness of fit ~\citep[at the potential cost of increased Type I error rates; e.g.,~][]{BateEtal15b}.
-Our threshold for inclusion of random effects is intended to achieve a reasonable balance between these trade-offs.
+where ``\texttt{accuracy}'' is a binary value indicating whether each target
+question was answered correctly or incorrectly, ``\texttt{knowledge}'' is
+estimated knowledge at each target question's embedding coordinate,
+``\texttt{participant}'' is a unique identifier assigned to each participant,
+and ``\texttt{question}'' is a unique identifier assigned to each quiz
+question. For models we fit using knowledge estimates for target questions
+about multiple content areas (i.e., in the ``All questions'' version of the
+analysis), we also included an additional random effect term,
+$\mathtt{(knowledge\ \vert\ lecture)}$, where ``\texttt{lecture}'' is a
+categorical value denoting whether the target question was about \textit{Four
+Fundamental Forces}, \textit{Birth of Stars}, or general physics knowledge.
+Note that with our coding scheme, identifiers for each \texttt{question} are
+implicitly nested within levels of \texttt{lecture} and do not require explicit
+nesting in our model formula.
+
+% We then iteratively removed random effects from the maximal model until it
+% successfully converged with a full rank (i.e., non-singular) random effects
+% variance-covariance matrix.
+
+%% JRM NOTE: do we need this next paragraph?  Commenting out for now...
+% %When inspecting the model's random effect estimates revealed multiple terms estimated at the boundary of their parameter space (i.e., variance components of 0 or correlation terms of  $\pm 1$), we found that the order in which we eliminated these terms typically did not affect which terms did and did not need to be removed in order for the model to converge to a non-degenerate solution.
+% When this required eliminating multiple terms whose estimates reached the boundary of their parameter space (i.e., variance components of 0 or correlation terms of  $\pm 1$), we found that the order in which we did so typically did not change the set of terms that needed to be removed in order for the model to converge to a non-degenerate solution.
+% However, in order to ensure we fit all models used in these analyses in a consistent way, we devised some simple heuristics for choosing which boundary-estimated parameter to eliminate in each stepwise reduction of the model's complexity, based on a combination of popular approaches~\citep{BarrEtal13,BateEtal15b,MatuEtal17}.
+% First, we constrained any correlation terms estimated at their boundaries (i.e., $\pm 1$) to 0 and re-fit the model.
+% This usually resulted in the variance component for the associated random slope (or occasionally the intercept, or even both) being estimated as 0, and suggested which terms we should consider removing.
+% Second, when choosing which of two zero-variance terms to remove from the model, we prioritized removing higher-order terms before lower-order terms.
+% In other words, if the estimated variance for both a random intercept and a random slope were 0, we chose to remove the random slope term before re-fitting the model and evaluating whether or not to remove the intercept.
+% %Additionally, if constraining a boundary-estimated correlation term to 0 allowed the model to converge with a full rank covariance matrix, we left the correlation term constrained rather than removing the associated slope and/or intercept component.
+% Third, when choosing which of two boundary-estimated variance components of the \textit{same} order to exclude from the model first, we took one of two approaches.
+% If the two components were random slopes with small but non-zero coefficients (e.g., on the order of $10^{-4}$ or less), we performed a Principal Components Analysis (PCA) on the random effects variance-covariance matrix and compared the variance explained by the two terms' corresponding PCs.
+% If one explained a substantially smaller proportion of variance than the other (loosely defined), we dropped its corresponding random slope.
+% Alternatively, if both slopes' principal components explained a similar amount of variance, or if the two terms we wanted to compare were random intercepts rather than slopes, we removed the one whose exclusion resulted in the greater decrease in the Akaike information criterion (AIC).
+% Fourth, after removing either a slope or intercept from one random effect grouping, we re-introduced any correlation terms we had previously constrained to 0 for other random effect groupings to check if they could now be estimated.
+% Finally, once the model successfully converged with a full rank covariance matrix, we did not remove random effects for any other reasons (e.g., to lower AIC, increase log-likelihood, etc.). 
+% We chose this stopping criterion as a conceptual ``middle ground'' between two popular but opposing approaches to model selection that advocate for either retaining the maximal model that allows convergence, regardless of singular fits~\citep[at the potential cost of decreased power; e.g.,~][]{BarrEtal13} or performing additional hypothesis tests on individual parameters and removing non-significant components to achieve a parsimonious model~\citep[at the potential cost of increased Type I error rates; e.g.,~][]{BateEtal15b}.
+% %We chose this stopping criterion as a conceptual ``middle ground'' between two popular but opposing approaches to model selection that advocate (respectively) for either retaining the maximal model that allows convergence, regardless of singular fits~\citep[at the potential cost of decreased power; e.g.,~][]{BarrEtal13} or testing individual parameters achieving a parsimonious model by discarding all parameters that don't significantly decrease goodness of fit ~\citep[at the potential cost of increased Type I error rates; e.g.,~][]{BateEtal15b}.
+% Our threshold for inclusion of random effects is intended to achieve a reasonable balance between these trade-offs.
 
@@
 We fit these models with the formula:
-To assess the predictive value of our knowledge estimates, we compared each GLMM's ability to discriminate between correctly and incorrectly answered questions to that of an analogous model that did not consider estimated knowledge.
-Specifically, we used the same sets of observations with which we fit each ``full'' model to fit a second ``null'' model, with the formula:
+
+To assess the predictive value of our knowledge estimates, we compared each
+GLMM's ability to discriminate between correctly and incorrectly answered
+questions to that of an analogous model that did not consider estimated
+knowledge. Specifically, we used the same sets of observations with which we
+fit each ``full'' model to fit a second ``null'' model, with the formula:
 \[
@@
 \]
+where the terms are as defined above.
 

### 2024-02-22 paper/main.tex
finished GLMM methods section

@@
 implicitly nested within levels of \texttt{lecture} and do not require explicit
-nesting in our model formula.
-
-% We then iteratively removed random effects from the maximal model until it
-% successfully converged with a full rank (i.e., non-singular) random effects
-% variance-covariance matrix.
+nesting in our model formula. We then iteratively removed random effects from 
+the maximal model until it successfully converged with a full rank (i.e., non-singular) 
+random effects variance-covariance matrix.
 
@@
 GLMM's ability to discriminate between correctly and incorrectly answered
-questions to that of an analogous model that did not consider estimated
+questions to that of an analogous model that did \textit{not} consider estimated
 knowledge. Specifically, we used the same sets of observations with which we
@@
 \]
-where the terms are as defined above.
-
-%In order to assess the predictive value of the knowledge estimates, we then fit a second set of ``null'' models to the same sets of observations used to fit our full GLMMs. These 
-%
-%
-%used the same sets of observations used to fit these GLMMs to fit a second set of ``null'' models. 
-%
-%
-%
-%Next, in order to assess the predictive value of the knowledge estimates 
-%
-%
-%
-%In order to assess the predictive value of the knowledge estimates we used to fit each GLMM, we then fit a \textit{second} model to the same data as each of the 15 
-%
-%In order to assess whether the knowledge estimates we used to fit each GLMM could reliably predict participants' success on held-out questions, we then fit a second GLMM to the observations
-
-%$$
-%\begin{aligned}
-%  \operatorname{accuracy}_{i}  &\sim \operatorname{Binomial}(n = 1, \operatorname{prob}_{\operatorname{accuracy} = \operatorname{correct}} = \widehat{P}) \\
-%    \log\left[\frac{\hat{P}}{1 - \hat{P}} \right] &=\alpha_{j[i],k[i]} \\
-%\left(
-%  \begin{array}{c}
-%    \begin{aligned}
-%      &\alpha_{j} \\
-%      &\gamma_{1j}
-%    \end{aligned}
-%  \end{array}
-%\right)
-%  &\sim N \left(
-%\left(
-%  \begin{array}{c}
-%    \begin{aligned}
-%      &\gamma_{0}^{\alpha} + \gamma_{1k[i]}^{\alpha}(\operatorname{knowledge}) \\
-%      &\mu_{\gamma_{1j}}
-%    \end{aligned}
-%  \end{array}
-%\right)
-%,
-%\left(
-%  \begin{array}{cc}
-%     \sigma^2_{\alpha_{j}} & \rho_{\alpha_{j}\gamma_{1j}} \\
-%     \rho_{\gamma_{1j}\alpha_{j}} & \sigma^2_{\gamma_{1j}}
-%  \end{array}
-%\right)
-% \right)
-%    \text{, for participant j = 1,} \dots \text{,J} \\
-%\left(
-%  \begin{array}{c}
-%    \begin{aligned}
-%      &\alpha_{k} \\
-%      &\gamma_{1k}
-%    \end{aligned}
-%  \end{array}
-%\right)
-%  &\sim N \left(
-%\left(
-%  \begin{array}{c}
-%    \begin{aligned}
-%      &\mu_{\alpha_{k}} \\
-%      &\mu_{\gamma_{1k}}
-%    \end{aligned}
-%  \end{array}
-%\right)
-%,
-%\left(
-%  \begin{array}{cc}
-%     \sigma^2_{\alpha_{k}} & \rho_{\alpha_{k}\gamma_{1k}} \\
-%     \rho_{\gamma_{1k}\alpha_{k}} & \sigma^2_{\gamma_{1k}}
-%  \end{array}
-%\right)
-% \right)
-%    \text{, for question k = 1,} \dots \text{,K}
-%\end{aligned}
-%$$
+where ``\texttt{accuracy}'', ``\texttt{participant}'', and ``\texttt{question}'' are as defined above. 
+As with our full models, the null models we fit for the “All questions” version of the analysis for each quiz contained an additional term, $\mathtt{(1\ \vert\ lecture)}$, where ``\texttt{lecture}'' are as defined above.
+We then compared each full model to its reduced (null) equivalent using a likelihood-ratio test (LRT). 
+Because the typical asymptotic $\chi^2_d$ approximation of the null distribution for the LRT statistic ($\lambda_{LR}$) is anti-conservative for models that differ in their random slope terms~\citep{GoldSimo00,ScheEtal08b,SnijBosk11}, we computed $p$-values for these tests using a parametric bootstrapping procedure~\citep{HaleHojs14}.
+For each of 1,000 bootstraps, we used the fitted null model to simulate a sample of observations of equal size to our original sample.
+We then re-fit both the null and full models to this simulated sample and compared them via an LRT.
+This yielded a distribution of $\lambda_{LR}$ statistics we may expect to observe under our null hypothesis.
+Following~\citep{DaviHink97,NortEtal02}, we computed a corrected $p$-value for our observed $\lambda_{LR}$ as $\frac{r + 1}{n + 1}$, where $r$ is the number of simulated model comparisons that yielded a $\lambda_{LR}$ greater than or equal to our observed value and $n$ is the number of simulations we ran (1,000).
 

### 2024-02-22 paper/main.tex
minor typo fix

@@
 where ``\texttt{accuracy}'', ``\texttt{participant}'', and ``\texttt{question}'' are as defined above. 
-As with our full models, the null models we fit for the “All questions” version of the analysis for each quiz contained an additional term, $\mathtt{(1\ \vert\ lecture)}$, where ``\texttt{lecture}'' are as defined above.
+As with our full models, the null models we fit for the “All questions” version of the analysis for each quiz contained an additional term, $\mathtt{(1\ \vert\ lecture)}$, where ``\texttt{lecture}'' is as defined above.
 We then compared each full model to its reduced (null) equivalent using a likelihood-ratio test (LRT). 

### 2024-02-22 paper/main.tex
minor fixes to GLMM methods section

@@
 
-%To assess the predictive value of our knowledge estimates for individual quiz questions, we used the same sets of observations used to fit each GLMM to fit a second set of ``null'' models (similarly with a logistic link function).
-We fit these models with the formula:
-
 To assess the predictive value of our knowledge estimates, we compared each
@@
 We then compared each full model to its reduced (null) equivalent using a likelihood-ratio test (LRT). 
-Because the typical asymptotic $\chi^2_d$ approximation of the null distribution for the LRT statistic ($\lambda_{LR}$) is anti-conservative for models that differ in their random slope terms~\citep{GoldSimo00,ScheEtal08b,SnijBosk11}, we computed $p$-values for these tests using a parametric bootstrapping procedure~\citep{HaleHojs14}.
+Because the typical asymptotic $\chi^2_d$ approximation of the null distribution for the LRT statistic ($\lambda_{LR}$) is anti-conservative for models that differ in their random slope terms~\citep{GoldSimo00,ScheEtal08b,SnijBosk11}, we computed $p$-values for these tests using a parametric bootstrap procedure~\citep{DaviHink97,HaleHojs14}.
 For each of 1,000 bootstraps, we used the fitted null model to simulate a sample of observations of equal size to our original sample.
@@
 This yielded a distribution of $\lambda_{LR}$ statistics we may expect to observe under our null hypothesis.
-Following~\citep{DaviHink97,NortEtal02}, we computed a corrected $p$-value for our observed $\lambda_{LR}$ as $\frac{r + 1}{n + 1}$, where $r$ is the number of simulated model comparisons that yielded a $\lambda_{LR}$ greater than or equal to our observed value and $n$ is the number of simulations we ran (1,000).
+Following~\citet{Ewen03}, we computed a corrected $p$-value for our observed $\lambda_{LR}$ as $\frac{r}{n}$, where $r$ is the number of simulated model comparisons that yielded a $\lambda_{LR}$ greater than or equal to our observed value and $n$ is the number of simulations we ran (1,000).
 

### 2024-02-22 paper/main.tex
saved out updated fig, fix fonts in illustrator, updated fig 6 stats in paper

@@
 test statistic $(\lambda_{LR}) = 19.749$, 95\%\ $\textnormal{CI} = [14.352,\
-26.545],\ p = 0.001$). This outcome suggests that our knowledge estimates do
+26.545],\ p < 0.001$). This outcome suggests that our knowledge estimates do
 \textit{not} provide useful information about participants' Quiz~1 performance
@@
 (Quiz~2: $OR = 2.905,\ \lambda_{LR} = 17.333,\ 95\%\ \textnormal{CI} =
-[14.966,\ 29.309],\ p = 0.002$; Quiz~3: $OR = 3.238,\ \lambda_{LR} = 6.882,\
-95\%\ \textnormal{CI} = [6.228,\ 8.184],\ p = 0.017$). Taken together, these
+[14.966,\ 29.309],\ p = 0.001$; Quiz~3: $OR = 3.238,\ \lambda_{LR} = 6.882,\
+95\%\ \textnormal{CI} = [6.228,\ 8.184],\ p = 0.016$). Taken together, these
 results suggest that our knowledge estimates reliably predict participants'
@@
 answered correctly ($OR = 1.891,\ \lambda_{LR} = 2.293,\ 95\%\ \textnormal{CI}
-= [2.091,\ 2.622],\ p = 0.139$). The same was true of knowledge estimates for
+= [2.091,\ 2.622],\ p = 0.138$). The same was true of knowledge estimates for
 held-out \textit{Birth of Stars}-related questions based on other \textit{Birth
@@
 Fundamental Forces}-related questions ($OR = 9.023,\ \lambda_{LR} = 18.707,\
-95\%\ \textnormal{CI} = [10.877,\ 22.222],\ p = 0.001$) but not on
+95\%\ \textnormal{CI} = [10.877,\ 22.222],\ p < 0.001$) but not on
 \textit{Birth of Stars}-related questions ($OR = 0.306,\ \lambda_{LR} = 5.115,\
-95\%\ \textnormal{CI} = [4.624,\ 5.655],\ p = 0.055$). Here, we speculate that
+95\%\ \textnormal{CI} = [4.624,\ 5.655],\ p = 0.054$). Here, we speculate that
 participants might have been guessing about the \textit{Birth of Stars} content
@@
 questions could now reliably predict success on those questions ($OR = 5.467,\
-\lambda_{LR} = 10.670,\ 95\%\ \textnormal{CI} = [7.998, 12.532],\ p = 0.006$).
+\lambda_{LR} = 10.670,\ 95\%\ \textnormal{CI} = [7.998, 12.532],\ p = 0.005$).
 However, within-lecture knowledge estimates for \textit{Four Fundamental
@@
 to the embedding space; $OR = 0.013,\ \lambda_{LR} = 14.648,\ 95\%\
-\textnormal{CI} = [10.695, 23.096],\ p = 0.001$). Speculatively, we suggest
+\textnormal{CI} = [10.695, 23.096],\ p < 0.001$). Speculatively, we suggest
 that this may reflect participants forgetting some of the \textit{Four
@@
 \textit{Birth of Stars} ($OR = 1.896,\ \lambda_{LR} = 7.205,\ 95\%\
-\textnormal{CI} = [6.224, 7.524],\ p = 0.039$) and similarly, that their
+\textnormal{CI} = [6.224, 7.524],\ p = 0.038$) and similarly, that their
 ability to correctly answer \textit{Birth of Stars}-related questions could be
@@
 questions ($OR = 1.522,\ \lambda_{LR} = 6.448,\ 95\%\ \textnormal{CI} = [5.656,
-6.843],\ p = 0.043$). Given the results from our analyses that included all
+6.843],\ p = 0.042$). Given the results from our analyses that included all
 questions and within-lecture predictions, we were surprised to find that the
@@
 questions ($OR = 1.865,\ \lambda_{LR} = 3.205,\ 95\%\ \textnormal{CI} = [3.027,
-3.600],\ p = 0.125$), nor did their responses to \textit{Birth of
+3.600],\ p = 0.124$), nor did their responses to \textit{Birth of
 Stars}-related questions reliably predict their success on \textit{Four
 Fundamental Forces}-related questions ($OR = 3.490,\ \lambda_{LR} = 3.266,\
-95\%\ \textnormal{CI} = [3.033, 3.866],\ p = 0.094$). These ``prediction
+95\%\ \textnormal{CI} = [3.033, 3.866],\ p = 0.093$). These ``prediction
 failures'' appear to come from the fact that any signal derived from
@@
 \textit{Four Fundamental Forces} ($OR = 11.294),\ \lambda_{LR} = 11.055,\ 95\%\
-\textnormal{CI} = [9.126, 18.476],\ p = 0.004$) and \textit{Birth of Stars}
+\textnormal{CI} = [9.126, 18.476],\ p = 0.003$) and \textit{Birth of Stars}
 ($OR = 7.302,\ \lambda_{LR} = 7.068,\ 95\%\ \textnormal{CI} = [6.490, 8.584],\
-p = 0.017$) using responses to questions about the other lecture's content.
+p = 0.016$) using responses to questions about the other lecture's content.
 Across all three versions of these analyses, our results suggest that (by and
@@
 performance.
-
-% our approach works when participants have a minimal baseline level of knowledge about content predicted and used to predict
-% our approach generalizes when knowledge of content used to predict can be assumed to be a reasonable indicator of knowledge of content predicted
-% our approach has enough specificity to distinguish between content within the same lecture when it was just watched -- maybe when people forget a little bit they forget "randomly"?.
-
-% potential new transition/motivation -- in the previous analyses, we identified a particular set of constraints on our estimates of participants' knowledge.
-This made us wonder about another potential constraint: how far away in topic space does the relevance of being able to answer a question extend and influence ability to answer a different question?
 

### 2024-02-22 paper/main.tex
checking in minor edits

--- 2024-02-22 paper/main.tex
@@
 incorrectly. One possibility is that the participant simply \textit{guessed}
-the answer. A second is that they selected an answer by mistake, despite
-``knowing'' the correct answer. In both of these scenarios, the participant's
-knowledge about the question's content should be uninformative about their
-observed response. A third possibility is that the participant's response
-reflects their \textit{actual} knowledge about the question's content. In this
-case, we \textit{might} expect to see a positive relationship between the
-participant's knowledge and their likelihood of answering the question
-correctly. However, in order to see this positive relationship, the
-participant's knowledge must be structured in a way that is reflected (at least
-partially) by the embedding space. In other words, if the participant's
-performance reflects their true knowledge, but our text embedding space does
-not sufficiently capture the structure of that knowledge, then the knowledge
-estimates we generate will not be predictive of the participant's performance.
-In the extreme, if the embedding space is completely unstructured with respect
-to the content of the quiz questions, then we would expect to see the negative
-relationship between estimated knowledge and performance that we described
-above.
+the answer. A second is that they selected the incorrect answer by mistake,
+despite ``knowing'' the correct answer (or vice versa). In both of these
+scenarios, the participant's knowledge about the question's content should be
+uninformative about their observed response. A third possibility is that the
+participant's response reflects their \textit{actual} knowledge about the
+question's content. In this case, we \textit{might} expect to see a positive
+relationship between the participant's knowledge and their likelihood of
+answering the question correctly. However, in order to see this positive
+relationship, the participant's knowledge must be structured in a way that is
+reflected (at least partially) by the embedding space. In other words, if the
+participant's performance reflects their true knowledge, but our text embedding
+space does not sufficiently capture the structure of that knowledge, then the
+knowledge estimates we generate will not be predictive of the participant's
+performance. In the extreme, if the embedding space is completely unstructured
+with respect to the content of the quiz questions, then we would expect to see
+the negative relationship between estimated knowledge and performance that we
+described above.
 
@@
 participants' knowledge about the content of the \textit{Birth of Stars}
-lecture (prior to watching it) is swamped by the much more dramatic increase in
+lecture (prior to watching it) is overwhelmed by the much more dramatic increase in
 their knowledge about the content of the \textit{Four Fundamental Forces}
@@
 responses reflect a minimum level of ``real'' knowledge about both content on
-which these predictions are based and that for which they are made. Our results
-also indicate some important limitations of our approach: if participants' quiz
-performance does not reflect what they know (e.g., when they ``guess''), or if
-their knowledge is not structured in a way that is reflected by the embedding
-space, then our knowledge estimates will not be predictive of their
-performance.
+which these predictions are based and that for which they are made.
 

### 2024-02-22 paper/main.tex
changed italics in one sentence

--- 2024-02-22 paper/main.tex
@@
 questions (prior to having watched either lecture). When we repeated this
-analysis for Quizzes~2 and~3, we found that \textit{higher} estimated knowledge
-for a given question predicted a greater likelihood of answering it correctly
+analysis for Quizzes~2 and~3, we found that higher estimated knowledge
+for a given question predicted a \textit{greater} likelihood of answering it correctly
 (Quiz~2: $OR = 2.905,\ \lambda_{LR} = 17.333,\ 95\%\ \textnormal{CI} =
